### 2020-06-16 Format.Rmd
Partitioning of data

---
title: "Federated Imputation"
author: 
- Thom Volker
- Utrecht University
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# SET UP

## TO DO

- [x] Dataset: Boys data in mice
- [x] Partition data in 5 subsets
- [ ] Create synthetic versions of the five subsets
- [ ] Merge 5 synthetic subsets into one central synthetic dataset
- [ ] Impute the central synthetic dataset
- [ ] Deconstruct the m imputed sets into the 5 synthetic sets
- [ ] Match the corresponding synthetic imputation to the observed imputation in all of the (m by 5) synthetic imputed sets

## Evaluation plan - when are we satisfied?
- [ ] Has algorithm converged (obv synthetic version --> evt later obv de real data version)
- [ ] Hanne's suggestion for tracking a model/data parameter based on the real data
- [ ] Als bias, CI width en Coverage of the 95% CI about the parameter (e.g. beta or mean) ok is.

## Workflow

Proof of Concept: Incomplete boys data as starting point and assess:

1. convergence?
2. whether the regression model based on federated imputations differs from the regression model based on the unfederated data. 
3. 1000 sims.

IF PoC successful --> jeej

1. Full blown sim with complete(mice(boys, m = 1, seed = 123)) as TRUE/population input
2. Bias? CI width? Coverage?

# REMARKS

1. Randomly subsetting the data leads to "randomly equivalent" datasets. However, when pooling results over multiple nodes, it might be that there are qualitative differences between nodes, which might complicate the imputation process.
2. In practice, some variables may be entirely missing, which differs from the current situation in which all datasets consist of the exact same variables.
3. Start with a single complete datasets, cut it in five, create a synthetic version of all and run the analyses on this synthetic dataset.
4. If I recall it correctly, Stef said that we simply synthesize the individual (partitioned) datasets, and that we could simply Rbind these. However, this would skip the point of basing the imputations on the collection of the 5 datasets together. If this was the case, we could simply use the data as if it is in the nodes, impute the individual sets with reference to the data in the other nodes, and analyse the imputed datasets, and pool the results.
5. Synthpop treats missingness as a separate category. For categorical variables, this is fairly straightforward: the category NA is added to the existing categories. In case of continuous data, the first step involves the "prediction" of whether or not a variable is missing, if it is predicted to be missing, the value will be NA, if the observation is not predicted to be missing, a synthetic value will be generated.

# Literature to read
Abowd, J. M., & Lane, J. (2004). New approaches to confidentiality protection: Synthetic data, remote access and research data centers. In International workshop on privacy in statistical databases (pp. 282-289). Springer, Berlin, Heidelberg.

- Why and how synthetic data can be used so that no information can be traced back to any individual.

Nowok, B. synthpop: An R package for generatingsynthetic versions of sensitive microdatafor statistical disclosure control. Retrieved from [link](https://www.unece.org/fileadmin/DAM/stats/documents/ece/ces/ge.46/20150/Paper_24_bnowok_synthpop.pdf).

Patki, N., Wedge, R., & Veeramachaneni, K. (2016, October). The synthetic data vault. In 2016 IEEE International Conference on Data Science and Advanced Analytics (DSAA) (pp. 399-410). IEEE. Retrieved from [link](https://www.computer.org/csdl/pds/api/csdl/proceedings/download-article/12OmNwx3Q7S/pdf?token=eyJ0eXAiOiJKV1QiLCJhbGciOiJIUzI1NiJ9.eyJpc3MiOiJjc2RsX2FwaSIsImF1ZCI6ImNzZGxfYXBpX2Rvd25sb2FkX3Rva2VuIiwic3ViIjoiYW5vbnltb3VzQGNvbXB1dGVyLm9yZyIsImVtYWlsIjoiYW5vbnltb3VzQGNvbXB1dGVyLm9yZyIsImV4cCI6MTU5MjIyMDg2Nn0.JhJGad-Fwo1N1vYkh737g_UwZ_jLNXSn1lcTCyVhaJU).

- Example of how to generate synthetic values, might give an idea of how this process works.

Reiter, J. P. (2005). Releasing multiply imputed, synthetic public use microdata: An illustration and empirical study. Journal of the Royal Statistical Society: Series A (Statistics in Society), 168(1), 185-205.

[Synthpop Website.](https://synthpop.org.uk/index.html)

### 2020-06-16 2. Synthesize data.R

@@ -1,1 +1,24 @@
 # Create synthetic versions of the data
+
+# Obtain the previously synthesized data
+source("1. Create data.R")
+
+##### This is all very preliminary.
+
+syns <- lapply(part, function(x) syn(x[[1]]))
+
+syns$group1$syn
+
+part %>%
+  map(., ~ syn(.))
+
+group1 <- part$group1[[1]]
+
+install.packages("synthpop")
+
+syn1 <- syn(group1)
+
+syn1$syn
+summary(syn1$syn)
+summary(group1)
+compare(syn1, group1)

### 2020-06-18 Format.Rmd

@@
     number_sections: true
+bibliography: federated_imp.bib
+csl: "/Users/thomvolker/Documents/styles/apa-6th-edition.csl"
 ---
@@
 
+# Proposal
+As an initial dataset to work with, the `boys` dataset from the R package `mice` [@mice] is chosen.
+However, if it appears unfruitful to work with a dataset that includes missing values already, we can use single imputation on the `boys` data, to be able to work with a complete dataset.
+The second step is to partition the data into five separate datasets, which is done by means of the function `resample_partition()` from the R package `modelr` [@ModelR].
+The next step is to create synthetic data versions of the five subsets by means of the R package `synthpop` [@synthpop].
+However, there are several problems thus far concerning this step:
+
+* Why can't we create synthetic versions of the subset, but can't we impute the subset? Since both will then be based on the subset only?
+* Creating the synthetic data when there are missing values leaves the `synthpop` package with one option, which is to *synthesize* the missing values as being a distinct category.
+Thus, the missingness is being modeled additionally.
+The other option is to impute the missing values before synthesizing, which we do not want, because this is exactly the reason that we arrived at synthesizing the data.
+Either way, `synthpop` treats the the data to be synthesized as known, .
+  + What `synthpop` does when there is missing data, is simply treating it as a separate category.
+When the variable of the missing data is continuous, it takes a two step approach: first it is modeled whether or not an observation is "predicted" to have a missing value, if the observation is not "predicted" to have a missing value, a value is modeled based on the other predictors.
+* As information: according to [@synthpop], the original aim of producing synthetic data has been to provide publicly available datasets that can be used for inference, when the original data cannot be shared.
+However, inferences based on the synthetic data are said to be only valid if the model used to construct the synthetic data is actually the true data generating mechanism, which is a mechanism hardly ever known.
+The aim of `synthpop` lies in providing test data that should resemble the actual data as closely as possible, although it should not be used in any final analyses.
+* `synthpop` requires that the method of generating  the synthetic data matches that of the observed data.
+This condition allows to make inferences from synthetic data generated from distributions with parameters fitted to the observed data without sampling the parameters from their posterior distribution, which is referred to as "simple synthesis".
+* Synthesizing seems flawed, because when the sample is not a random sample (which is the case if the missingness is MAR), the synthetic values are based on the incomplete data.
+
+# INTRODUCTION
+Something about federated analyses (why, how), eventually in combination with DataSHIELD (as the proposed method).
+
+Something about missing data (and multiple imputation).
+
+Something about synthetic data (why and how).
+
+Something about pooling results.
+
 # REMARKS
@@
 In case of continuous data, the first step involves the "prediction" of whether or not a variable is missing, if it is predicted to be missing, the value will be NA, if the observation is not predicted to be missing, a synthetic value will be generated.
+6.
+MICE has a pool function to pool the estimates of the multiple analyses that works with a list of datasets.
+However, the pooled estimates are not equivalent to the estimates after running the `lm` function on the complete data.
+7.
+If you are able to make synthetic data, based on a single dataset (instead of the combination of all 5), then, why are we not able to impute the single datasets directly, without taking the other datasets into account?
 
@@
 
+Reiter, J. P. (2002). Satisfying disclosure restrictions with synthetic data sets. Journal of Official Statistics, 18(4), 531.
+
 Reiter, J.
@@
 [Synthpop Website.](https://synthpop.org.uk/index.html)
+
+# References
+
+\setlength{\parindent}{-0.2in}
+\setlength{\leftskip}{0.2in}
+\noindent
+
+<div id="refs"></div>

### 2020-06-18 Format.Rmd
added setup

@@
 # SET UP
+
+## Simple evaluation
+
+1. Impute `boys` data with `m=1` to obtain `boyscompl`
+2. For `i` repetitions, store as a list `out` the result of
+
+  - partition `boyscompl` into `p=5` parts
+  - synthesize the `p` parts
+  - combine the `p` synthetic parts into `boyssynth`
+
+3. For the `i` elements in list `out`, evaluate
+
+  - Qbar (e.g regression estimates of `bmi ~ age + wgt`)
+  - CI of Qbar
+  - coverage of the CI of Qbar
+
+### If method is valid
+Then Qbar is unbiased and confidence valid (i.e. at least 95% of CI's cover the population value)
 

### 2020-06-18 Totaal anders dan som der delen.R
added regression script

@@ -1,0 +1,20 @@
+library(magrittr)
+set.seed()
+imp <- mice(boys, m = 1)
+data <- complete(imp)
+
+indic <- sample(1:748, 375)
+d1 <- data[indic,]
+d2 <- data[-indic,]
+
+data %$% lm(age ~ wgt + tv) %>% summary
+A <- d1 %$% lm(age ~ wgt + tv) %>% summary
+B <- d2 %$% lm(age ~ wgt + tv) %>% summary
+
+
+list(A = d1 %$% lm(age ~ wgt + tv),
+     B = d2 %$% lm(age ~ wgt + tv)) %>% pool
+
+(coef(A)*375 + coef(B)*373)/748
+(coef(A) + coef(B))/2
+

### 2020-06-20 federated_imp_synthesizing_complete_data.Rmd
Synthesize function and results

---
title: "Federated Imputation"
author: 
- Thom Volker
- Utrecht University
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
bibliography: federated_imp.bib
csl: "/Users/thomvolker/Documents/styles/apa-6th-edition.csl"
---

# Synthesizing

To show the concept of synthesizing data, the `boys` dataset from the R-package `mice` [@mice] is singly-imputed, to be able to work with a dataset without missing values. The first approach is to synthesize this dataset as a whole by means of the `syn`-function with default settings from the package `synthpop` [@synthpop], to see whether synthesizing is a suitable approach to generate data that is in accordance with the observed data, and exhibits the same relationships between variables. To see how this process performs when the data is partitioned, the data is first partitioned into five subsets. Then, the subsets are synthesized by means of the `syn` function, and then binded to a single dataset containing the five synthesized subsets. Since the `syn` function contains a random process, this function is rerun over a single partitioned dataset, to see what the effect of only randomly synthesizing the same partitions is. As a third step, the partitioning is also randomized, resulting in the fact that the iterations contain two random processes: (1) the data is partioned randomly for every iteration, and (2) the partitioned data is synthesized with a random component.

That is, the process works as follows:

@. Impute the `boys` dataset with `m=1`, which results in the completed `boyscomp` data.
@. Over `i` in `1:nsim(=1000)` iterations, the output following output is collected:
  + The regression estimates of `nsim` times synthesized complete dataset.
  + The regression estimates of `nsim` times the synthesized partitioned dataset.
  + The regression estimates of `nsim` times the synthesized `nsim` times partitioned dataset.
@. Over `nsim` iterations, the average estimates are calculated ($\bar{Q}$), the bias ($\mu_Q - \bar{Q}$), the confidence intervals averaged over all iterations, and the coverage ($\frac{1}{nsim} \sum_{i = 1}^{nsim} Lower_i < \mu_Q < Upper_i$).

# Results

The previous process results in the following results.

```{r, include = F}
source("2. Synthesize data.R")
```

```{r}
knitr::kable(syn_out)
```

### 2020-06-20 1.a Create data - boys complete.R

@@ -1,0 +1,35 @@
+###############################################################################
+## Create data sets to work with, we will work with the boys dataset that is ##
+## build-in in mice.                                                         ##
+###############################################################################
+
+
+###############################################################################
+## Load packages and set seed                                                ##
+###############################################################################
+
+library(mice)   ## mice for the boys data and the imputations
+library(modelr) ## modelr to do the partitioning   
+
+set.seed(123)   # seed for reproducibility of the imputations and partitioning
+
+###############################################################################
+## obtain and impute the boys dataset, create the completed boys data, and   ##
+## partition the completed dataset                                           ##
+###############################################################################
+
+meth <- make.method(boys)
+pred <- make.predictorMatrix(boys)
+meth["bmi"] <- "~ I(wgt / (hgt/100)^2)"
+
+pred[c("wgt", "hgt"), "bmi"] <- 0
+
+imp <- mice(boys, meth = meth, pred = pred,      ## Impute the boys dataset by means of a single
+            m = 1, printFlag = F)                ## imputation, and fill in the imputed data into
+boyscomp <- complete(imp)                        ## the dataset containing missing values.
+                     
+
+ngroups <- 5                                     ## Specify five groups, and
+partitions <- rep(1/ngroups,ngroups)             ## specify five equal fractions
+names(partitions) <- paste0("d", 1:ngroups)      ## give names to the partitionings and
+part <- resample_partition(boyscomp, partitions) ## partition the data in five equal parts

### 2020-06-20 2. Synthesize data.R

@@ -1,24 +1,90 @@
-# Create synthetic versions of the data
+#########################################################################################
+## Create synthetic versions of the data.                                              ##
+## build-in in mice.                                                                   ##
+#########################################################################################
 
-# Obtain the previously synthesized data
-source("1. Create data.R")
+#########################################################################################
+## Load packages, source file wherein the data is created and set seed                 ##
+#########################################################################################
 
-##### This is all very preliminary.
+library(tidyverse)                            # Load tidyverse for tibbles
+library(synthpop)                             # Load synthpop for data synthesizing
+library(furrr)                                # furrr for parallel mapping
+library(broom)                                # broom for tidy results
 
-syns <- lapply(part, function(x) syn(x[[1]]))
+source("1.a Create data - boys complete.R")   # Obtain the previously synthesized data
 
-syns$group1$syn
+set.seed(123)                                 # Set the seed for reproducibility
 
-part %>%
-  map(., ~ syn(.))
+#########################################################################################
+## Function for synthesizing the data, that handles partitioned data and the           ##
+## complete data                                                                       ##
+#########################################################################################
 
-group1 <- part$group1[[1]]
+synthesize <- function(data, parts = NULL,    # Use a function to synthesize and analyze
+                       partition = FALSE, n.parts = 5) {   # the (synthesized) data.
+  
+  if (partition) {
+    # If the data must be partitioned every iterations, the function creates the partitions
+    partitions <- rep(1/n.parts, n.parts)
+    names(partitions) <- paste0("d", 1:n.parts)
+    parts <- resample_partition(data, partitions)
+  }
+  
+  if (!is.null(parts)) {
+    # If there are partitions included, synthesize synthesize the data of all partitions,
+    # and rowbind the synthesized partitions
+    syn_dat <- map_dfr(parts, ~ syn(.[[1]],print.flag = F)$syn) 
+  }                                           
+  else {
+    # If it concerns the complete data as a whole, simply synthesize the complete data, 
+    # and extract this data
+    syn_dat <- syn(data, print.flag = F)$syn
+  }
+  return(syn_dat)
+}
 
-install.packages("synthpop")
[…]

### 2020-06-21 federated_imp_synthesizing_complete_data.Rmd
Update r markdown

@@
 @.
-Over `nsim` iterations, the average estimates are calculated ($\bar{Q}$), the bias ($\mu_Q - \bar{Q}$), the confidence intervals averaged over all iterations, and the coverage ($\frac{1}{nsim} \sum_{i = 1}^{nsim} Lower_i < \mu_Q < Upper_i$).
+Over `nsim` iterations, the average estimates are calculated ($\bar{Q}$), the bias ($\mu_Q - \bar{Q}$), the confidence intervals averaged over all iterations, and the coverage ($\frac{1}{nsim} \sum_{i = 1}^{nsim} LLCI_i < \mu_Q < ULCI_i$).
 
@@
 
-```{r}
-knitr::kable(syn_out)
+```{r, echo = F}
+knitr::kable(syn_out, digits = 3, caption = "Simulation results of the model age ~ hgt + tv for three different synthesizing")
 ```
+
+# References
+
+\setlength{\parindent}{-0.2in}
+\setlength{\leftskip}{0.2in}
+\noindent
+
+<div id="refs"></div>

### 2020-06-21 2. Synthesize data.R
Add fixed seed

@@ -14,8 +14,6 @@ library(broom)                                # broom for tidy results
 
 source("1.a Create data - boys complete.R")   # Obtain the previously synthesized data
 
-set.seed(123)                                 # Set the seed for reproducibility
-
 #########################################################################################
 ## Function for synthesizing the data, that handles partitioned data and the           ##
 ## complete data                                                                       ##
@@ -49,14 +47,17 @@ plan(multisession)  # specify parallel processing
 
 # replicate the function 1000 times on the complete data in parallel
 syns_complete <- future_map_dfr(1:nsim, ~ synthesize(boyscomp),
-                                .id = "sim", .progress = TRUE)
+                                .id = "sim", .progress = TRUE,
+                                .options = future_options(seed = as.integer(123)))
 # replicate the function 1000 times on the same partitioned data
 syns_part <- future_map_dfr(1:nsim, ~ synthesize(boyscomp, parts = part),
-                            .id = "sim", .progress = TRUE)
+                            .id = "sim", .progress = TRUE,
+                            .options = future_options(seed = as.integer(123)))
 # replicate the function 1000 times on a 1000 times partitioned dataset
 
 syns_resample_partition <- future_map_dfr(1:nsim, ~ synthesize(boyscomp, partition = TRUE),
-                                          .id = "sim", .progress= TRUE)
+                                          .id = "sim", .progress= TRUE, 
+                                          .options = future_options(seed = as.integer(123)))
 
 # Specify the model to be run on all synthesized datasets
 syn_model <- function(data) lm(age ~ hgt + tv, data = data)
@@ -88,3 +89,5 @@ syn_out <- results %>%
             "Coverage" = mean(covered)) %>%
   mutate(method = recode(method, `1` = "Complete data", `2` = "Single partition",
                          `3` = "Nsim partitions"))
+
+

### 2020-06-21 federated_imp_synthesizing_complete_data.Rmd
Five synthetic datasets provides much better results.

@@
 ```{r, include = F}
-source("2. Synthesize data.R")
+source("2.a Synthesize data (m=1).R")
 ```
@@
 ```{r, echo = F}
-knitr::kable(syn_out, digits = 3, caption = "Simulation results of the model age ~ hgt + tv for three different synthesizing")
+knitr::kable(syn1_out, digits = 3, caption = "Simulation results of the model age ~ hgt + tv for three different synthesizing approaches (complete data, same subset 1000 times, 1000 different subsets, all with the number of synthetic datasets equal to 1.")
 ```
+
+However, the results are not very satisfactory, so I looked further into the possibilities of using the `synthpop` package.
+One of the possibilities was to adjust the model, and use passive synthesizing for `bmi`.
+Additionally, instead of one synthetic dataset, I made 5, so that the results are averaged over five synthetic datasets, instead of only one.
+This leads to much better results, as is shown below (only for the case in which the complete dataset is synthetized).
+
+```{r, include = F}
+source("2.b Synthesize data (m=5).R")
+```
+
+```{r, echo = F}
+knitr::kable(syn5_out, digits = 3, caption = "Simulation results of the model age ~ hgt + tv based on synthesizing the data as a whole, based on 5 synthetic datasets per iteration.")
+```
+
+Which provides much better results. However, I do not know yet how to implement this approach for five partitions in combination with the `synthpop` package.
 

### 2020-06-21 2.a Synthesize data (m=1).R

@@ -19,7 +19,7 @@ source("1.a Create data - boys complete.R")   # Obtain the previously synthesize
 ## complete data                                                                       ##
 #########################################################################################
 
-synthesize <- function(data, parts = NULL,    # Use a function to synthesize and analyze
+synthesize <- function(data, parts = NULL, method = NULL,    # Use a function to synthesize and analyze
                        partition = FALSE, n.parts = 5) {   # the (synthesized) data.
   
   if (partition) {
@@ -37,7 +37,7 @@ synthesize <- function(data, parts = NULL,    # Use a function to synthesize and
   else {
     # If it concerns the complete data as a whole, simply synthesize the complete data, 
     # and extract this data
-    syn_dat <- syn(data, print.flag = F)$syn
+    syn_dat <- syn(data, print.flag = F, method = method)$syn
   }
   return(syn_dat)
 }
@@ -79,11 +79,12 @@ results <- bind_rows(syns_complete, syns_part, syns_resample_partition, .id = "m
          covered = real > conf.low & real < conf.high)
 
 # Format the results so that we can nicely display them.
-syn_out <- results %>%
+syn1_out <- results %>%
   dplyr::select(term, real, estimate, conf.low, conf.high, covered) %>%
   group_by(method, term) %>%
   summarise("Population value" = unique(real),
             "Qbar" = mean(estimate),
+            "Bias" = mean(estimate) - unique(real),
             "Lower" = mean(conf.low),
             "Upper" = mean(conf.high),
             "Coverage" = mean(covered)) %>%

### 2020-06-24 federated_imp_synthesizing_complete_data.Rmd
Added multivariate normal example

@@
 
+# Synthpop estimates
+
+Synthetic data estimates $(\hat{\beta_1}, \hat{\beta_2}, \dots, \hat{\beta_m})$ - if the model for the data is correct, the $m$ estimates from the synthetic data will be centered around the estimate $\hat{\beta}$ that would have been obtained from the observed data.
+If the method of inference used to fit the model provides consistent estimates of the parameters and the same is true for the analyses of the synthetic data, then the mean of $m$ synthetic estimates, $\bar{\hat{\beta}}=\sum_{i=1}^m\hat{\beta_i}/m$ provides a consistent estimate of $\hat{\beta}$.
+Provided that the observed and synthetic data are generated by the common sampling scheme, then $V_{\bar{\hat{\beta}}}=\sum_{i=1}^m V_{\hat{\beta_i}}/m$ will be a consistent estimate of $V_{\hat{\beta}}$.
+
+The variance-covariance matrix of $\bar{\hat{\beta}}$, conditional on $\hat{\beta}$ and $V_{\hat{\beta}}$, becomes $V_{\hat{\beta}}$ which can be estimated from $V_{\bar{\hat{\beta}}}/m$.
+Thus the stochastic error in the mean of the synthetic estimates aboutthe values from the observed data can be reduced to a negligible quantity by increasing $m$.
+It must be remembered, however that the consistency of $\bar{\hat{\beta}}$ only applies when observed data are a sample from the distribution used for synthesis.
+In practical applications  differences between the analyses on the observed data and those from the mean of the syntheses will be found because the data do not conform to the model used for synthesis.
+Such differences will not be reduced by increasing $m$.
+The synthesiser, with access to the observed data, can estimate $\bar{\hat{\beta}}-\hat{\beta}$ and compare it to its standard error in order to judge the extent that this model mismatch affects the estimates.
+
+# Multivariate normal simulated data
+
+```{r, include = F}
+source("2.c Synthesize data mvnorm.R")
+```
+
+## Synthesizing by a linear regression model
+
+```{r, echo = F}
+knitr::kable(synth_by_lm, digits = 3, caption = "Simulation results of multivariate normal data, synthesized by a normal linear regression model.")
+```
+
+## Synthesizing by a Classification and Regression Tree (CART)
+
+```{r}
+knitr::kable(synth_by_cart, digits = 3, caption = "Simulation results of multivariate normal data, synthesized by classification and regression trees.")
+```
+
 # References

### 2020-06-24 2.c Synthesize data mvnorm.R

@@ -1,0 +1,160 @@
+library(furrr)
+library(synthpop)
+library(tidyverse)
+
+bootstrap_syn <- function(data, method = NULL, formula, coefs) {
+  d   <- data                                             # specify the data
+  s1  <- syn(d, m = 1, method = method, print.flag = F)   # 1 synthesis
+  s5  <- syn(d, m = 5, method = method, print.flag = F)   # 5 syntheses
+  s10 <- syn(d, m = 10, method = method, print.flag = F)  # 10 syntheses
+  
+  f <- as.formula(formula)                                # the formula
+  
+  # Fit the lm models on all four datasets (the real data and the synthetic data)
+  r <- list(Real_Sample = lm(f,d), Syn1 = lm.synds(f, s1), Syn5 = lm.synds(f, s5), Syn10 = lm.synds(f, s10))
+  
+  # Collect the output
+  out <- map(r, function(x) as.data.frame(coef(summary(x)))) %>%
+    map(., function(x) {colnames(x) <- c("Est", "SE", "stat", "P"); return(as.data.frame(x))}) %>%
+    map(., function(x) rownames_to_column(x, var = "Variable")) %>%
+    bind_rows(., .id = "Method") %>%
+    group_by(Method) %>% 
+    ungroup() %>%
+    dplyr::select(., Method, Variable, Est, SE, stat, P) %>%
+    mutate(Lower = Est - qnorm(.975)*SE,
+           Upper = Est + qnorm(.975)*SE)
+  # Return the output
+  return(as.data.frame(out))
+}
+
+# Generate multicariate normal data
+normal <- function(r2, ratio_beta, rho, n = 10000) {
+  X <- MASS::mvrnorm(n = n, mu = rep(0, length(ratio_beta)), Sigma = rho)
+  colnames(X) <- paste0("IV", 1:length(ratio_beta))
+  coefs <- matrix(NA, nrow = length(ratio_beta), ncol = length(ratio_beta))
+  for (i in 1:length(ratio_beta)) {
+    for (j in 1:length(ratio_beta)) {
+      coefs[i,j] <- ifelse(i > j, ratio_beta[i] * ratio_beta[j], 0)
+    }
+  }
+  b <- sqrt((r2 / (sum(ratio_beta^2) + 2 * sum(coefs * rho))))
+  y <- X %*% (b*ratio_beta) + rnorm(n, 0, sqrt(1 - r2))
+  return(list(dat = data.frame(DV = y, X), coefs = b*ratio_beta))
+}
+
[…]

### 2020-06-28 2.c Synthesize data mvnorm.R
Correct variance for inference

@@ -2,7 +2,7 @@ library(furrr)
 library(synthpop)
 library(tidyverse)
 
-bootstrap_syn <- function(data, method = NULL, formula, coefs) {
+bootstrap_syn <- function(data, method = NULL, formula, coefs, pop.inf = F) {
   d   <- data                                             # specify the data
   s1  <- syn(d, m = 1, method = method, print.flag = F)   # 1 synthesis
   s5  <- syn(d, m = 5, method = method, print.flag = F)   # 5 syntheses
@@ -14,7 +14,9 @@ bootstrap_syn <- function(data, method = NULL, formula, coefs) {
   r <- list(Real_Sample = lm(f,d), Syn1 = lm.synds(f, s1), Syn5 = lm.synds(f, s5), Syn10 = lm.synds(f, s10))
   
   # Collect the output
-  out <- map(r, function(x) as.data.frame(coef(summary(x)))) %>%
+  out <- map(r, function(x) {if (class(x) == "fit.synds") {x <- summary(x, population.inference = pop.inf)}
+                             else {x <- summary(x)}
+                             return(as.data.frame(coef(x)))}) %>% 
     map(., function(x) {colnames(x) <- c("Est", "SE", "stat", "P"); return(as.data.frame(x))}) %>%
     map(., function(x) rownames_to_column(x, var = "Variable")) %>%
     bind_rows(., .id = "Method") %>%
@@ -52,7 +54,7 @@ rho0[rho0!=1] <- 0
 # and the correlation as specified above, and a sample size of n = 100
 test_rho0 <- normal(.5, ratio_beta = ratio, rho = rho0, n = 100)
 # Test whether the population regression coefficients are in line with the specified r2 (they are)
-sum(test_rho0$coefs^2) + 2*sum(test_rho0$coefs[2]*test_rho0$coefs[3]*.9)
+sum(test_rho0$coefs^2) + 2*sum(test_rho0$coefs[2]*test_rho0$coefs[3]*0)
 
 real_coefs_rho0 <- test_rho0$coefs
 
@@ -156,5 +158,105 @@ synth_by_cart <- bind_rows("Rho = 0" = summary_cart_rho0, "Rho = .5" = summary_c
 
 
 
+#########################################################################################
+## Specify population.inference = TRUE                                                 ##
+#########################################################################################
 
+
+# Generate random normal data, and run the synthesize function on it (bootstrap is a somewhat 
+# inappropriate name, because we sample directly from the population). 
[…]

### 2020-06-28 2.c Synthesize data mvnorm.R
Adjusted order of output.

@@ -80,10 +80,10 @@ out_norm_rho0 %>%
   ungroup() %>% group_by(Method, Variable) %>%
   summarise("Population estimate" = unique(RealEst),
             "Qbar" = mean(Est),
-            "MaxSE" = max(SE),
-            "MinSE" = min(SE),
-            "MeanSE" = mean(SE),
             "Bias" = mean(Bias),
+            "MeanSE" = mean(SE),
+            "MinSE" = min(SE),
+            "MaxSE" = max(SE),
             "Lower" = mean(Lower),
             "Upper" = mean(Upper),
             "Coverage" = mean(Covered)) %>%
@@ -96,10 +96,10 @@ out_cart_rho0 %>%
   ungroup() %>% group_by(Method, Variable) %>%
   summarise("Population estimate" = unique(RealEst),
             "Qbar" = mean(Est),
-            "MaxSE" = max(SE),
-            "MinSE" = min(SE),
-            "MeanSE" = mean(SE),
             "Bias" = mean(Bias),
+            "MeanSE" = mean(SE),
+            "MinSE" = min(SE),
+            "MaxSE" = max(SE),
             "Lower" = mean(Lower),
             "Upper" = mean(Upper),
             "Coverage" = mean(Covered)) %>%
@@ -127,10 +127,10 @@ out_norm_rho50 %>%
   ungroup() %>% group_by(Method, Variable) %>%
   summarise("Population estimate" = unique(RealEst),
             "Qbar" = mean(Est),
-            "MaxSE" = max(SE),
-            "MinSE" = min(SE),
-            "MeanSE" = mean(SE),
             "Bias" = mean(Bias),
+            "MeanSE" = mean(SE),
+            "MinSE" = min(SE),
+            "MaxSE" = max(SE),
             "Lower" = mean(Lower),
             "Upper" = mean(Upper),
             "Coverage" = mean(Covered)) %>%
@@ -143,10 +143,10 @@ out_cart_rho50 %>%
   ungroup() %>% group_by(Method, Variable) %>%
   summarise("Population estimate" = unique(RealEst),
             "Qbar" = mean(Est),
-            "MaxSE" = max(SE),
-            "MinSE" = min(SE),
-            "MeanSE" = mean(SE),
             "Bias" = mean(Bias),
+            "MeanSE" = mean(SE),
+            "MinSE" = min(SE),
+            "MaxSE" = max(SE),
             "Lower" = mean(Lower),
[…]

### 2020-06-28 federated_imp_synthesizing_complete_data.Rmd

@@
 ---
+
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+thomcache <- TRUE; thomlazy <- FALSE #obviously ;)
+```
 
@@
 
-```{r, include = F}
+```{r, include = F, cache = thomcache, cache.lazy=thomlazy}
 source("2.a Synthesize data (m=1).R")
@@
 
-```{r, echo = F}
+```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
 knitr::kable(syn1_out, digits = 3, caption = "Simulation results of the model age ~ hgt + tv for three different synthesizing approaches (complete data, same subset 1000 times, 1000 different subsets, all with the number of synthetic datasets equal to 1.")
@@
 
-```{r, include = F}
+```{r, include = F, cache = thomcache, cache.lazy=thomlazy}
 source("2.b Synthesize data (m=5).R")
@@
 
-```{r, echo = F}
+```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
 knitr::kable(syn5_out, digits = 3, caption = "Simulation results of the model age ~ hgt + tv based on synthesizing the data as a whole, based on 5 synthetic datasets per iteration.")
@@
 
-```{r, include = F}
+```{r, include = F, cache = thomcache, cache.lazy=thomlazy}
 source("2.c Synthesize data mvnorm.R")
@@
 
-## Synthesizing by a linear regression model
+## Inference with sample variance estimates
 
-```{r, echo = F}
+Sample variance estimates are computed as $V_{\bar{\hat{\beta}}} = \frac{1}{m} \sum_{i=1}^m V_{\hat{\beta}_i}$.
+However, confidence interval coverage is computed with respect to the true population value, instead of the sample estimates.
+
+### Synthesizing by a linear regression model
+
+```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
 knitr::kable(synth_by_lm, digits = 3, caption = "Simulation results of multivariate normal data, synthesized by a normal linear regression model.")
@@
 
-## Synthesizing by a Classification and Regression Tree (CART)
+### Synthesizing by a Classification and Regression Tree (CART)
 
-```{r}
+```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
 knitr::kable(synth_by_cart, digits = 3, caption = "Simulation results of multivariate normal data, synthesized by classification and regression trees.")
 ```
+
+## Inference with sample variance estimates
+
+Population variance estimates are computed as <!-- TO DO - ADD CORRECT FORMULA $V_{\bar{\hat{\beta}}} = \frac{1}{m} \sum_{i=1}^m V_{\hat{\beta}_i}$ -->.
+However, confidence interval coverage is computed with respect to the true population value, instead of the sample estimates.
+
+### Synthesizing by a linear regression model
+
+```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
+knitr::kable(synth_by_lm_pop, digits = 3, caption = "Simulation results of multivariate normal data, synthesized by a normal linear regression model.")
+```
+
+### Synthesizing by a Classification and Regression Tree (CART)
+
+```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
+knitr::kable(synth_by_cart_pop, digits = 3, caption = "Simulation results of multivariate normal data, synthesized by classification and regression trees.")
+```
+
+### Variance estimates
+
+The variance of the statistic of interest equals $\bar{v}_M$, which represents the average variance over the $M$ synthetic datasets, when the goal of the synthesis is to make inferences with regard to the sample at hand, instead of with regard to the population.
+When the goal of the synthesis is to make population inferences, the variance is adjusted with an additional term, based on the number of synthetic datasets:
+$$
+Var(Q) = \bar{\mathcal{v}}_M (1 + \frac{1}{M})
+$$
+where $Q$ is the regression coefficient of the $k^{th}$ variable, $\bar{v}_M$ is the mean of the variables over the $M$ syntheses.
+If the number of synthesized data points ($J$) is unequal to the number of observations in the dataset ($N$), a correction equal to $\frac{J}{N}$ is multiplied with $\bar{v}_M$.
 

### 2020-07-02 federated_imp_synthesizing_complete_data.Rmd
Partitioned data, functions file and some clean-up

@@
 $$
-where $Q$ is the regression coefficient of the $k^{th}$ variable, $\bar{v}_M$ is the mean of the variables over the $M$ syntheses.
+where $Q$ is the statistic of interest and $\bar{v}_M$ is the mean of the statistic over the $M$ syntheses.
 If the number of synthesized data points ($J$) is unequal to the number of observations in the dataset ($N$), a correction equal to $\frac{J}{N}$ is multiplied with $\bar{v}_M$.

### 2020-07-02 2.a Synthesize data (m=1).R

@@ -13,40 +13,13 @@ library(furrr)                                # furrr for parallel mapping
 library(broom)                                # broom for tidy results
 
 source("1.a Create data - boys complete.R")   # Obtain the previously synthesized data
-
-#########################################################################################
-## Function for synthesizing the data, that handles partitioned data and the           ##
-## complete data                                                                       ##
-#########################################################################################
-
-synthesize <- function(data, parts = NULL, method = NULL,    # Use a function to synthesize and analyze
-                       partition = FALSE, n.parts = 5) {   # the (synthesized) data.
-  
-  if (partition) {
-    # If the data must be partitioned every iterations, the function creates the partitions
-    partitions <- rep(1/n.parts, n.parts)
-    names(partitions) <- paste0("d", 1:n.parts)
-    parts <- resample_partition(data, partitions)
-  }
-  
-  if (!is.null(parts)) {
-    # If there are partitions included, synthesize synthesize the data of all partitions,
-    # and rowbind the synthesized partitions
-    syn_dat <- map_dfr(parts, ~ syn(.[[1]],print.flag = F)$syn) 
-  }                                           
-  else {
-    # If it concerns the complete data as a whole, simply synthesize the complete data, 
-    # and extract this data
-    syn_dat <- syn(data, print.flag = F, method = method)$syn
-  }
-  return(syn_dat)
-}
+source("1.c Functions.R")
 
 nsim <- 1000        # number of iterations
 plan(multisession)  # specify parallel processing
 
 # replicate the function 1000 times on the complete data in parallel
-syns_complete <- future_map_dfr(1:nsim, ~ synthesize(boyscomp),
+syns_complete <- future_map_dfr(1:nsim, function(x) synthesize(boyscomp),
                                 .id = "sim", .progress = TRUE,
                                 .options = future_options(seed = as.integer(123)))
 # replicate the function 1000 times on the same partitioned data
@@ -55,7 +28,7 @@ syns_part <- future_map_dfr(1:nsim, ~ synthesize(boyscomp, parts = part),
                             .options = future_options(seed = as.integer(123)))
 # replicate the function 1000 times on a 1000 times partitioned dataset
 
-syns_resample_partition <- future_map_dfr(1:nsim, ~ synthesize(boyscomp, partition = TRUE),
+syns_resample_partition <- future_map_dfr(1:nsim, ~ synthesize(boyscomp, partition = TRUE,n.parts=5),
                                           .id = "sim", .progress= TRUE, 
                                           .options = future_options(seed = as.integer(123)))
 

### 2020-07-02 2.b Synthesize data (m=5).R

@@ -13,35 +13,7 @@ library(furrr)                                # furrr for parallel mapping
 library(broom)                                # broom for tidy results
 
 source("1.a Create data - boys complete.R")   # Obtain the previously synthesized data
-
-#########################################################################################
-## Function for synthesizing the data, that handles partitioned data and the           ##
-## complete data                                                                       ##
-#########################################################################################
-
-synthesize_2 <- function(data, parts = NULL,    # Use a function to synthesize and analyze
-                       partition = FALSE, n.parts = 5,
-                       method = NULL, m = 1) {   # the (synthesized) data.
-  
-  if (partition) {
-    # If the data must be partitioned every iterations, the function creates the partitions
-    partitions <- rep(1/n.parts, n.parts)
-    names(partitions) <- paste0("d", 1:n.parts)
-    parts <- resample_partition(data, partitions)
-  }
-  
-  if (!is.null(parts)) {
-    # If there are partitions included, synthesize synthesize the data of all partitions,
-    # and rowbind the synthesized partitions
-    syn_dat <- map_dfr(parts, ~ syn(.[[1]], print.flag = F, m = m, method = method)$syn) 
-  }                                           
-  else {
-    # If it concerns the complete data as a whole, simply synthesize the complete data, 
-    # and extract this data
-    syn_dat <- syn(data, print.flag = F, m = m, method = method)
-  }
-  return(syn_dat)
-}
+source("1.c Functions.R")
 
 #########################################################################################
 ## Execute function with default synthesizing settings                                 ##
@@ -56,7 +28,7 @@ plan(multisession) # specify parallel processing
 syn_meth <- c("cart", "cart", "cart", "~ I(wgt / (hgt/100)^2)", 
               "cart", "cart", "cart", "cart", "cart")
 
-syns_m5_complete1 <- future_map(1:nsim, ~ synthesize_2(boyscomp, m = 5, method = syn_meth),
+syns_m5_complete1 <- future_map(1:nsim, ~ synthesize(boyscomp, m = 5, method = syn_meth),
                                .progress = TRUE,
                                .options = future_options(seed = as.integer(123)))
 

### 2020-07-02 synthesizing_partitioned_data.Rmd

---
title: "Federated Imputation"
author: 
- Thom Volker
- Utrecht University
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
bibliography: federated_imp.bib
csl: "/Users/thomvolker/Documents/styles/apa-6th-edition.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
thomcache <- TRUE; thomlazy <- FALSE #obviously ;)
```

```{r, include = F, cache=thomcache, cache.lazy=thomlazy}
source("2.d Synthesize partitioned data.R")
```

# Previous results

Without partitioning the data, we already saw that synthesizing does not distort the relationships of the variables in the data at hand. That is, synthesizing a dataset results in $M$ synthetic datasets with, on average, the same properties as the original dataset. The results can be seen in the following table. This table contains the simulation results of synthesizing multivariate normally distributed data, where the correlation between predictors equals $\rho = 0$, the proportion explained variance equals $R^2 = .50$ and the sample size equals $n = 100$. Note that synthesizing is done by means of the default settings (by means of CART), and the variance of the estimates is calculated as 
$$Var(\beta) = \bar{v}_{M}(1 + \frac{1}{M}),$$
where $\bar{v}_M$ is the average variance of the regression coefficient over the $M$ synthetic datasets.

```{r, echo = F, cache=thomcache, cache.lazy=thomlazy}
knitr::kable(summary_out_norm, digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data with m=5 in the last three rows.")
```

# Results with partitioned data

When we first partition the sampled data from the multivariate normal distribution, the results change to some extent, which can be seen in the following table.

```{r, echo = F, cache=thomcache, cache.lazy=thomlazy}
bind_rows("n = 100" = summary_out_norm_part_n100, 
          "n = 1000" = summary_out_norm_part_n1000, 
          "n = 10000" = summary_out_norm_part_n10000, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data with m=5 in the last three rows with partitioned data.")
```

When we do the same with the imputed boys dataset, where the number of imputations equals one, we obtain the following results.

```{r, echo = F, cache=thomcache, cache.lazy=thomlazy}
bind_rows("Single partition" = summary_out_same_part, "Nsim partitions" = summary_out_nsim_parts, .id = "Sample size") %>%
  knitr::kable(., digits = 3, caption = "Results of a linear regression model where weight is regressed on height and age, with the data partitioned into 5 subsets and m = 5 synthetic versions of each subset.")
```

### 2020-07-05 synthesizing_partitioned_data.Rmd

@@
 thomcache <- TRUE; thomlazy <- FALSE #obviously ;)
+library(tidyverse)
 ```
@@
 ```{r, echo = F, cache=thomcache, cache.lazy=thomlazy}
-knitr::kable(summary_out_norm, digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data with m=5 in the last three rows.")
+knitr::kable(summary_out_cart, digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data with m=5 in the last three rows.")
 ```
@@
 
-When we first partition the sampled data from the multivariate normal distribution, the results change to some extent, which can be seen in the following table.
+## CART Synthesizing method
+
+CART Method: First variable is sampled from the observed data, the second variable is predicted from the first variable by means of a regression tree, the third variable is predicted from the first two variables, and so on.
+
+When we first partition the sampled data from the multivariate normal distribution, the results change to quite some extent, which can be seen in the following table.
+The coverage seems to be very low, and far below the nominal level of $95\%$.
 
 ```{r, echo = F, cache=thomcache, cache.lazy=thomlazy}
-bind_rows("n = 100" = summary_out_norm_part_n100, 
-          "n = 1000" = summary_out_norm_part_n1000, 
-          "n = 10000" = summary_out_norm_part_n10000, .id = "Sample size") %>%
-  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data with m=5 in the last three rows with partitioned data.")
+bind_rows("n = 100" = summary_out_cart_part_n100, 
+          "n = 1000" = summary_out_cart_part_n1000, .id = "Sample size") %>%
+  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
 ```
 
-When we do the same with the imputed boys dataset, where the number of imputations equals one, we obtain the following results.
+## Norm Synethesizing method
 
-```{r, echo = F, cache=thomcache, cache.lazy=thomlazy}
+Norm Method: The first variable is sampled from a univariate normal distribution, the second variable is drawn from a normal distribution with mean $\mu = \beta_1 * X_1$ and variance $\sigma^2 = \sigma^2_e$, the third variable is drawn based on the first two variables, and so on.
+This performs much better than the previous method, but this introduces bias, which is accompanied by a somewhat too low coverage.
+
+```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
+bind_rows("n = 100" = summary_out_norm_part_n100,
+          "n = 1000" = summary_out_norm_part_n1000, .id = "Sample size") %>%
+  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of method 'norm' with M = 10 in the last three rows with partitioned data.")
+
+```
+
+<!--When we do the same with the imputed boys dataset, where the number of imputations equals one, we obtain the following results.
+
+```{r, echo = F, cache=thomcache, cache.lazy=thomlazy, eval = F}
 bind_rows("Single partition" = summary_out_same_part, "Nsim partitions" = summary_out_nsim_parts, .id = "Sample size") %>%
@@
 ```
+
+-->

### 2020-07-07 2.d Synthesize partitioned data.R
Correlated predictors and n = 10000 added.

@@ -76,6 +76,17 @@ out_cart_part_n1000 <- future_map_dfr(1:nsim, ~ synth_sampled_data(p = p, r2 = r
 # Obtain results
 summary_out_cart_part_n1000 <- print_results(out_cart_part_n1000, coefs = real_coefs)
 
+# Set the sample size to 10000
+n3 <- 10000
+# Sample data with n = 10000, so 5 partitions of 2000 persons, synthesize data by means of the 
+# cart method
+out_cart_part_n10000 <- future_map_dfr(1:nsim, ~ synth_sampled_data(p = p, r2 = r2, ratio = ratio, rho = rho, 
+                                                                   n = n3, formula = f, pop.inf = T, M = 10),
+                                      .id = "sim", .progress = T, .options = future_options(seed = as.integer(123)))
+
+summary_out_cart_part_n10000 <- print_results(out_cart_part_n10000, coefs = real_coefs)
+
+
 
 ##########################################################################################
 ## Since we know that the data is generated by means of a multivariate normal mechanism ##
@@ -96,7 +107,7 @@ out_norm_part_n100 <- future_map_dfr(1:nsim, ~ synth_sampled_data(p = p, r2 = r2
 # Obtain results
 summary_out_norm_part_n100 <- print_results(out_norm_part_n100, coefs = real_coefs)
 
-# Sample data with n = 1000, so 5 partitions of twenty persons, synthesize data by means of the 
+# Sample data with n = 1000, so 5 partitions of 200 persons, synthesize data by means of the 
 # normal linear regression/random draws from a normal distribution
 out_norm_part_n1000 <- future_map_dfr(1:nsim, ~ synth_sampled_data(p = p, r2 = r2, ratio = ratio, rho = rho, 
                                                                    n = n2, formula = f, pop.inf = T, 
@@ -106,7 +117,15 @@ out_norm_part_n1000 <- future_map_dfr(1:nsim, ~ synth_sampled_data(p = p, r2 = r
 # Obtain results
 summary_out_norm_part_n1000 <- print_results(out_norm_part_n1000, coefs = real_coefs)
 
+# Sample data with n = 10000, so 5 partitions of 2000 persons, synthesize data by means of the 
+# normal linear regression/random draws from a normal distribution
+out_norm_part_n10000 <- future_map_dfr(1:nsim, ~ synth_sampled_data(p = p, r2 = r2, ratio = ratio, rho = rho, 
+                                                                   n = n3, formula = f, pop.inf = T, 
[…]

### 2020-07-07 synthesizing_partitioned_data.Rmd

@@
 
-# Results with partitioned data
+# Results with partitioned data and uncorrelated predictors
 
@@
 bind_rows("n = 100" = summary_out_cart_part_n100, 
-          "n = 1000" = summary_out_cart_part_n1000, .id = "Sample size") %>%
+          "n = 1000" = summary_out_cart_part_n1000,
+          "n = 10000" = summary_out_cart_part_n10000, .id = "Sample size") %>%
   knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
@@
 bind_rows("n = 100" = summary_out_norm_part_n100,
-          "n = 1000" = summary_out_norm_part_n1000, .id = "Sample size") %>%
+          "n = 1000" = summary_out_norm_part_n1000, 
+          "n = 10000" = summary_out_norm_part_n10000, .id = "Sample size") %>%
   knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of method 'norm' with M = 10 in the last three rows with partitioned data.")
@@
 
-<!--When we do the same with the imputed boys dataset, where the number of imputations equals one, we obtain the following results.
+# Results with partitioned data and correlated predictors
 
-```{r, echo = F, cache=thomcache, cache.lazy=thomlazy, eval = F}
-bind_rows("Single partition" = summary_out_same_part, "Nsim partitions" = summary_out_nsim_parts, .id = "Sample size") %>%
-  knitr::kable(., digits = 3, caption = "Results of a linear regression model where weight is regressed on height and age, with the data partitioned into 5 subsets and m = 5 synthetic versions of each subset.")
+```{r, include = F, cache=thomcache, cache.lazy=thomlazy}
+source("2.e Synthesize partitioned data with correlations.R")
 ```
 
--->
+When there are no correlations between the predictors, there is less information in the data with regard to every predictor, so it might be more difficult to correctly estimate all relationships in the data appropriately.
+Therefore, we introduce some moderate correlations between the predictors, so that, hopefully, the patterns in the data can be used to synthesize the data.
+The following correlation matrix is used to model the relationships between the data.
+
+$$
+\rho =
+\begin{bmatrix}
+1 & 0.15 & 0.25\\
+0.15 & 1 & 0.35\\
+0.25 & 0.35 & 1
+\end{bmatrix}
+$$
+
+## CART Synthesizing method
+
+When we use the CART synthesizing method, in combination with the data with correlated predictors coming from a multivariate normal distribution, we obtain the following results.
+
+```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
+bind_rows("n = 100" = cor_summary_out_cart_part_n100, 
+          "n = 1000" = cor_summary_out_cart_part_n1000,
+          "n = 10000" = cor_summary_out_cart_part_n10000, .id = "Sample size") %>%
+  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
+```
+
+## Norm Synthesizing method
+
+When we use the norm synthesizing method, in combination with the data with correlated predictors coming from a multivariate normal distribution, we obtain the following results.
+
+```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
+bind_rows("n = 100" = cor_summary_out_norm_part_n100, 
+          "n = 1000" = cor_summary_out_norm_part_n1000,
+          "n = 10000" = cor_summary_out_norm_part_n10000, .id = "Sample size") %>%
+  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
+```

### 2020-07-08 synthesizing_partitioned_data.Rmd
Added 10 partitions instead of 5

@@
 ```
+
+# Ten subsets instead of five
+
+## Uncorrelated predictors
+
+### CART Synthesization
+
+Below, the results are presented when the data is partitioned into 10 subsets, instead of five, corresponding to ten different nodes that are synthesized separately, and then combined into a single dataset that is analysed by means of the standard estimators as presented by @raab_practical_2016.
+This yields regression coefficients that are equal to
+$$
+\beta_{M,k} = \sum^M_{m=1} \beta_{m,k} / M,
+$$
+with a variance of 
+$$
+V = \bar{v}_M(1+\frac{1}{M}),
+$$
+where $\bar{v}_M$ equals $\sum^M_{m=1}\frac{v_m}{M}$.
+
+```{r, include = F, cache=thomcache, cache.lazy=thomlazy}
+source("2.f Synthesize 10 subsets with and without correlations.R")
+```
+
+```{r, echo = F}
+bind_rows("n = 100" = p10_summary_out_cart_part_n100, 
+          "n = 1000" = p10_summary_out_cart_part_n1000, .id = "Sample size") %>%
+  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
+```
+
+### Norm synthesization
+
+```{r, echo = F}
+bind_rows("n = 100" = p10_summary_out_norm_part_n100, 
+          "n = 1000" = p10_summary_out_norm_part_n1000, .id = "Sample size") %>%
+  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
+```
+
+## Correlated predictors
+
+### CART synthesization
+
+```{r, echo = F}
+bind_rows("n = 100" = cor_p10_summary_out_cart_part_n100, 
+          "n = 1000" = cor_p10_summary_out_cart_part_n1000, .id = "Sample size") %>%
+  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
+```
+
+### Norm synthesization
+
+```{r, echo = F}
+bind_rows("n = 100" = cor_p10_summary_out_norm_part_n100, 
+          "n = 1000" = cor_p10_summary_out_norm_part_n1000, .id = "Sample size") %>%
+  knitr::kable(., digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data by means of CART with M = 10 in the last three rows with partitioned data.")
+```
+
+# Workflow from now on
+
+Necessity to further investigate structure of the data by means of, say, eigenvalues (correlations seem to be okay with large samples, according to results presented)?
+
+## Proposal
+
+@.
+Verder werken met de completed boys data (ondanks de hoge correlatie sowieso realistischer dan gesimuleerde multivariate normal data).
+Eventueel zou ik ook nog een andere dataset kunnen zoeken die wellicht meer lijkt op een "standaard" social sciences dataset.
+  + Indien we met de boys data werken, kunnen we eventueel ook nog een subset nemen (om te kijken hoe het gaat met "echte" data als we de sample size verkleinen), en we zouden kunnen bootstrappen om een grotere sample te creëren dan de huidige 748 observaties (wellicht met Stef overleggen wat een redelijk aantal observaties en nodes zijn over verschillende ziekenhuizen).
+@.
+Boys dataset bootstrappen, zodat we een "superpopulatie" krijgen.
+En dan zowel gebootstrapte echte data vergelijken met synthetische versie van elke boodstrap sample.
+In dat geval dat geval is het gemiddelde over de bootstrap samples de populatie waarde.
+  + 
+1. Second point.

### 2020-07-08 2.f Synthesize 10 subsets with and without correlations.R

@@ -1,0 +1,163 @@
+##########################################################################################
+## Simulate multivariate normal data, partition it, and synthesize the partitions,      ##
+## then, bind the synthetic partitions and analyse it                                   ##
+##########################################################################################
+
+## Source the completed boys data, and source the functions file
+source("1.a Create data - boys complete.R")
+source("1.c Functions.R")
+
+## Load the required packages, furrr for parallel map functions, tidyverse for tidy data,
+## synthpop for data synthesis
+library(furrr)
+library(tidyverse)
+library(synthpop)
+
+## Specify that we run the code in multiple sessions, to speed up the process
+plan(multisession)
+
+## Set the number of simulations
+nsim <- 1000
+
+## Specify the input for the multivariate normal data sampling
+r2 <- .5                    # R2 of .5
+ratio <- c(0,1,2)           # Uninformative predictor and two informative predictors
+rho <- diag(length(ratio))  # Uncorrelated predictors
+n1 <- 100                   # Sample size
+n2 <- 1000
+#n3 <- 10000
+
+# real_coefs are the population regression coefficients
+real_coefs <- normal(r2,ratio,rho,n1)$coefs
+
+# f is the formula of the linear regressions during the rest of the code
+f <- DV ~ -1 + IV1 + IV2 + IV3
+
+##########################################################################################
+## First, we use the default synthpop method CART to obtain the synthetic datasets      ##
+##########################################################################################
+
+
+# Specify a small function for inside the future_map commands
+synth_sampled_data <- function(p, r2, ratio, rho, n, formula, pop.inf = T, method = NULL, M) {
+  part <- normal(r2, ratio, rho, n)$dat %>% resample_partition(p)
+  syn_part_data(partitioned_data = part, M = M, formula = formula, pop.inf = pop.inf, method = method)
+}
+
+
+# Specify the number of partitions (5 equally large partitions)
+n.parts <- 10
+p <- rep(1 / n.parts, n.parts)
+names(p) <- paste0("p", 1:n.parts)
+
+
+# Sample data with n = 100, so 5 partitions of twenty persons, synthesize data by means of the 
+# cart method
+p10_out_cart_part_n100 <- future_map_dfr(1:nsim, ~ synth_sampled_data(p = p, r2 = r2, ratio = ratio, rho = rho, 
+                                                                      n = n1, formula = f, pop.inf = T, M = 10),
[…]

### 2020-07-09 synthesizing_partitioned_data.Rmd

@@
 
+### Complete data workflow
+
 @.
@@
   + Indien we met de boys data werken, kunnen we eventueel ook nog een subset nemen (om te kijken hoe het gaat met "echte" data als we de sample size verkleinen), en we zouden kunnen bootstrappen om een grotere sample te creëren dan de huidige 748 observaties (wellicht met Stef overleggen wat een redelijk aantal observaties en nodes zijn over verschillende ziekenhuizen).
-@.
-Boys dataset bootstrappen, zodat we een "superpopulatie" krijgen.
-En dan zowel gebootstrapte echte data vergelijken met synthetische versie van elke boodstrap sample.
-In dat geval dat geval is het gemiddelde over de bootstrap samples de populatie waarde.
-  + 
-1. Second point.
+@. For i in 1:nsim (en eventueel voor verschillende sample sizes):
+    + Boys dataset (of dus eventueel andere) bootstrappen, zodat we een "superpopulatie" krijgen. 
+    + Partition bootstrap sample, zodat we weer nodes krijgen.
+    + Synthesize nodes independently from each other.
+    + Rbind synthetic versions.
+    + Analyse de complete (n = 748) synthetic dataset en de gebootstrapte dataset. 
+@. Dan: gemiddelde over de bootstraps is de "populatiewaarde".
+@. Check Qbar, bias, CI width en CI coverage van synthetische data.
+
+### Missing data workflow
+
+@. Werken met boys data met missings.
+@. Maak superpopulatie obs van bootstrappen (binnen de for-loop)
+@. For i in 1:nsim (eventueel voor verschillende sample sizes):
+    + Bootstrap boys data (hebben we bootstrap sample)
+    + Partitioneer bootstrap sample in 5 delen
+    + Synthesize each node independently from the others.
+    + Merge the nodes
+    + Impute the synthetic dataset as a whole
+    + Subset the synthetic data so that they correspond to the observed (partitioned) data
+    + Match the corresponding synthetic imputation to the observed imputation for all of the synthetic imputed sets.
+@. Gemiddelde over de bootstraps is de populatiewaarde.
+@. Check Qbar, bias, CI width en CI coverage van synthetische data.
+
+### IK MOET LEZEN
+@. Drechsler over synthetic data
+@. Over CART (Elements of Statistical Learning?)

### 2020-07-12 1.c Functions.R
Complete boys bootstrap population

@@ -101,7 +101,7 @@ normal <- function(r2, ratio_beta, rho, n = 10000) {
 ## of inference (sample based or population based)                                     ##
 #########################################################################################
 
-syn_part_data <- function(partitioned_data, M, formula, 
+syn_part_data <- function(partitioned_data, M, formula, visit,
                           method = NULL, pop.inf = T) {
   
   d <- partitioned_data # short code for the partitioned data
@@ -109,7 +109,7 @@ syn_part_data <- function(partitioned_data, M, formula,
   
   # Synthesize every partition of the data M times with method = method
   out <- map(d, function(x) syn(as.data.frame(x), m = M, print.flag = F,
-                                method = method))
+                                method = method, visit.sequence = visit))
   # Set an empty list for every synthetic dataset
   new_syns <- as.list(1:M)
   

### 2020-07-12 2.g Synthesize bootstrapped boys data.R

@@ -1,0 +1,78 @@
+
+
+library(tidyverse)
+library(synthpop)
+library(furrr)
+
+source("1.a Create data - boys complete.R")
+source("1.c Functions.R")
+
+plan(multisession)
+
+# Specify a small function for inside the future_map commands
+synth_bootstrapped_data <- function(p, data, formula, pop.inf = T, method = NULL, M = 1, visit = (1:ncol(data))) {
+  part <- data %>% resample_bootstrap %>% data.frame %>% resample_partition(p)
+  syn_part_data(partitioned_data = part, M = M, formula = formula, pop.inf = pop.inf, method = method, visit = visit)
+}
+
+# Specify the number of partitions (5 equally large partitions)
+n.parts <- 5
+p <- rep(1 / n.parts, n.parts)
+names(p) <- paste0("p", 1:n.parts)
+
+nsim <- 1000
+
+f <- wgt ~ age + hgt
+
+boys_cart_results_10 <- future_map_dfr(1:nsim, ~ synth_bootstrapped_data(p = p, data = boyscomp, formula = f, pop.inf = T, M = 10),
+                                    .id = "sim", .progress = T, .options = future_options(seed = as.integer(125)))
+
+meth <- c("cart", "cart", "cart", "~ I(wgt / (hgt/100)^2)", "cart", "cart", "cart", "cart", "cart")
+
+vs <- c(2,3,4,1,5,6,7,8,9)
+
+boys_vs_results_10 <- future_map_dfr(1:nsim, ~ synth_bootstrapped_data(p = p, data = boyscomp, formula = f, method = meth, 
+                                                                     pop.inf = T, M = 10, visit = vs), 
+                                   .id = "sim", .progress = T, .options = future_options(seed = as.integer(123)))
+
+boys_cart_results_20 <- future_map_dfr(1:nsim, ~ synth_bootstrapped_data(p = p, data = boyscomp, formula = f, pop.inf = T, M = 20),
+                                    .id = "sim", .progress = T, .options = future_options(seed = as.integer(125)))
+
+boys_vs_results_20 <- future_map_dfr(1:nsim, ~ synth_bootstrapped_data(p = p, data = boyscomp, formula = f, method = meth, 
+                                                                    pop.inf = T, M = 20, visit = vs), 
[…]

### 2020-07-12 synthesizing_partitioned_data.Rmd
Complete boys bootstrap population
Small changes markdown

@@
 
+```{r, include = F, cache=thomcache, cache.lazy=thomlazy}
+source("2.g Synthesize bootstrapped boys data.R")
+```
+
+The results we obtain in this scenario are shown in the following output.
+First the variable `age` is sampled randomly from the actual data, then the variable `hgt` is synthesized, with only `age` as predictor.
+In the same fashion, `wgt` is synthesized with predictors `age` and `hgt`, and so on so forth.
+It can be seen that the confidence interval coverage of the bootstrapped sample is not optimal, and that the coverage of the synthetic data after $M = 10$ synthetic versions is actually nearly identical to that of the bootstrapped samples.
+
+```{r, echo = F}
+knitr::kable(summary_cart_10, digits = 3)
+```
+
+When we increase the number of synthetic datasets to $M = 20$, the coverage is actually slightly worse than in the case of $M = 10$.
+This seems to be due to the fact that the bias remains and the confidence interval gets slightly narrower.
+
+```{r, echo = F}
+#knitr::kable(summary_vs_10, digits = 3)
+
+knitr::kable(summary_cart_20, digits = 3)
+
+#knitr::kable(summary_vs_20, digits = 3)
+```
+
+<!--Then we have the actual sample results on the complete boys dataset, without synthesizing. -->
+
+```{r, include = F}
+knitr::kable(broom::tidy(lm(wgt ~ age + hgt, boyscomp), conf.int = T))
+```
+
 ### Missing data workflow
+
+#### IDEA
+
+* Since synthpop messes up
 

### 2020-07-13 summary.Rmd
Added partitioned boys data and one fixed seed.

---
title: "How synthetic data can be used to ease the imputation of confidential data"
author: 
- Thom Volker
- Utrecht University
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
bibliography: federated_imp.bib
csl: "/Users/thomvolker/Documents/styles/apa-6th-edition.csl"
---

# Introduction

### 2020-07-13 synthesizing_partitioned_data.Rmd
Added partitioned boys data and one fixed seed.

@@
 
-```{r, echo = F, cache=thomcache, cache.lazy=thomlazy}
+```{r, echo = F}
 knitr::kable(summary_out_cart, digits = 3, caption = "Results of a linear regression model where DV is regression on the predictors IV1, IV2 and IV3, with the values sampled directly from the population in the first three rows, and the synthesized data with m=5 in the last three rows.")
@@
 
-```{r, echo = F, cache=thomcache, cache.lazy=thomlazy}
+```{r, echo = F}
 bind_rows("n = 100" = summary_out_cart_part_n100, 
@@
 
-```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
+```{r, echo = F}
 bind_rows("n = 100" = summary_out_norm_part_n100,
@@
 
-```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
+```{r, echo = F, cache = thomcache, cache.lazy=thomlazy, eval = F}
 bind_rows("n = 100" = cor_summary_out_cart_part_n100, 
@@
 
-```{r, echo = F, cache = thomcache, cache.lazy=thomlazy}
+```{r, echo = F, cache = thomcache, cache.lazy=thomlazy, eval=F}
 bind_rows("n = 100" = cor_summary_out_norm_part_n100, 
@@
 
-```{r, include = F, cache=thomcache, cache.lazy=thomlazy}
+```{r, include = F, cache=thomcache, cache.lazy=thomlazy, eval=F}
 source("2.f Synthesize 10 subsets with and without correlations.R")
@@
 
-```{r, echo = F}
+```{r, echo = F, eval=F}
 bind_rows("n = 100" = p10_summary_out_cart_part_n100, 
@@
 
-```{r, echo = F}
+```{r, echo = F, eval=F}
 bind_rows("n = 100" = p10_summary_out_norm_part_n100, 
@@
 
-```{r, echo = F}
+```{r, echo = F,eval=F}
 bind_rows("n = 100" = cor_p10_summary_out_cart_part_n100, 
@@
 
-```{r, echo = F}
+```{r, echo = F,eval=F}
 bind_rows("n = 100" = cor_p10_summary_out_norm_part_n100, 
@@
 
-```{r, include = F, cache=thomcache, cache.lazy=thomlazy}
+```{r, include = F, cache=thomcache, cache.lazy=thomlazy, eval = F}
 source("2.g Synthesize bootstrapped boys data.R")
@@
 
-```{r, echo = F}
+```{r, echo = F, eval = F}
 knitr::kable(summary_cart_10, digits = 3)
@@
 
-```{r, echo = F}
+```{r, echo = F, eval = F}
 #knitr::kable(summary_vs_10, digits = 3)
@@
 
-```{r, include = F}
+```{r, include = F, eval = F}
 knitr::kable(broom::tidy(lm(wgt ~ age + hgt, boyscomp), conf.int = T))

### 2020-07-13 2.a Synthesize data (m=1).R

@@ -17,20 +17,21 @@ source("1.c Functions.R")
 
 nsim <- 1000        # number of iterations
 plan(multisession)  # specify parallel processing
+seed <- as.integer(12345)
 
 # replicate the function 1000 times on the complete data in parallel
 syns_complete <- future_map_dfr(1:nsim, function(x) synthesize(boyscomp),
                                 .id = "sim", .progress = TRUE,
-                                .options = future_options(seed = as.integer(123)))
+                                .options = future_options(seed = seed))
 # replicate the function 1000 times on the same partitioned data
 syns_part <- future_map_dfr(1:nsim, ~ synthesize(boyscomp, parts = part),
                             .id = "sim", .progress = TRUE,
-                            .options = future_options(seed = as.integer(123)))
+                            .options = future_options(seed = seed))
 # replicate the function 1000 times on a 1000 times partitioned dataset
 
 syns_resample_partition <- future_map_dfr(1:nsim, ~ synthesize(boyscomp, partition = TRUE,n.parts=5),
                                           .id = "sim", .progress= TRUE, 
-                                          .options = future_options(seed = as.integer(123)))
+                                          .options = future_options(seed = seed))
 
 # Specify the model to be run on all synthesized datasets
 syn_model <- function(data) lm(age ~ hgt + tv, data = data)

### 2020-07-13 2.b Synthesize data (m=5).R

@@ -24,13 +24,14 @@ nsim <- 1000        # number of iterations
 
 plan(multisession) # specify parallel processing
 
+seed <- as.integer(12345)
+
 
 syn_meth <- c("cart", "cart", "cart", "~ I(wgt / (hgt/100)^2)", 
               "cart", "cart", "cart", "cart", "cart")
 
 syns_m5_complete1 <- future_map(1:nsim, ~ synthesize(boyscomp, m = 5, method = syn_meth),
-                               .progress = TRUE,
-                               .options = future_options(seed = as.integer(123)))
+                               .progress = TRUE, .options = future_options(seed = seed))
 
 
 cutoff <- qnorm(.975)

### 2020-07-13 2.c Synthesize data mvnorm.R

@@ -20,6 +20,8 @@ real_coefs_rho0 <- test_rho0$coefs
 
 plan(multisession)
 
+seed <- as.integer(12345)
+
 # method for normal synthesis (based on a linear regression model)
 synds_norm <- c("norm", "norm", "norm", "norm")
 # method for synthesis based on classification and regression trees
@@ -28,9 +30,9 @@ synds_cart <- c("cart", "cart", "cart", "cart")
 # Generate random normal data, and run the synthesize function on it (bootstrap is a somewhat 
 # inappropriate name, because we sample directly from the population). 
 out_norm_rho0 <- future_map_dfr(1:500, function(x) {data <- normal(.5, ratio, rho0, n = 100)$dat; normal_syn(data, method = synds_norm, formula = DV ~ -1 + IV1 + IV2 + IV3)},
-                                .id = "sim", .progress = TRUE, .options = future_options(seed = as.integer(123)))
+                                .id = "sim", .progress = TRUE, .options = future_options(seed = seed))
 out_cart_rho0 <- future_map_dfr(1:500, function(x) {data <- normal(.5, ratio, rho0, n = 100)$dat; normal_syn(data, method = synds_cart, formula = DV ~ -1 + IV1 + IV2 + IV3)},
-                                .id = "sim", .progress = TRUE, .options = future_options(seed = as.integer(123)))
+                                .id = "sim", .progress = TRUE, .options = future_options(seed = seed))
 
 
 summary_norm_rho0 <- print_results(out_norm_rho0, real_coefs_rho0)
@@ -48,9 +50,9 @@ real_coefs_rho50 <- test_rho50$coefs
 
 # And run the same function as above, but now with correlated predictors
 out_norm_rho50 <- future_map_dfr(1:500, function(x) {data <- normal(.5, ratio, rho50, n = 100)$dat; normal_syn(data, method = synds_norm, formula = DV ~ -1 + IV1 + IV2 + IV3)},
-                                 .id = "sim", .progress = TRUE, .options = future_options(seed = as.integer(123)))
+                                 .id = "sim", .progress = TRUE, .options = future_options(seed = seed))
 out_cart_rho50 <- future_map_dfr(1:500, function(x) {data <- normal(.5, ratio, rho50, n = 100)$dat; normal_syn(data, method = synds_cart, formula = DV ~ -1 + IV1 + IV2 + IV3)},
[…]

### 2020-07-13 2.e Synthesize partitioned data with correlations.R

@@ -15,6 +15,7 @@ library(synthpop)
 
 ## Specify that we run the code in multiple sessions, to speed up the process
 plan(multisession)
+seed <- as.integer(12345)
 
 ## Set the number of simulations
 nsim <- 1000
@@ -42,7 +43,8 @@ f <- DV ~ -1 + IV1 + IV2 + IV3
 # Specify a small function for inside the future_map commands
 synth_sampled_data <- function(p, r2, ratio, rho, n, formula, pop.inf = T, method = NULL, M) {
   part <- normal(r2, ratio, rho, n)$dat %>% resample_partition(p)
-  syn_part_data(partitioned_data = part, M = M, formula = formula, pop.inf = pop.inf, method = method)
+  syn_part_data(partitioned_data = part, M = M, formula = formula, pop.inf = pop.inf, 
+                method = method, visit = 1:(length(ratio)+1))
 }
 
 
@@ -56,13 +58,13 @@ names(p) <- paste0("p", 1:n.parts)
 # cart method
 cor_out_cart_part_n100 <- future_map_dfr(1:nsim, ~ synth_sampled_data(p = p, r2 = r2, ratio = ratio, rho = rho, 
                                                                   n = n1, formula = f, pop.inf = T, M = 10),
-                                     .id = "sim", .progress = T, .options = future_options(seed = as.integer(123)))
+                                     .id = "sim", .progress = T, .options = future_options(seed = seed))
 cor_out_cart_part_n1000 <- future_map_dfr(1:nsim, ~ synth_sampled_data(p = p, r2 = r2, ratio = ratio, rho = rho, 
                                                                    n = n2, formula = f, pop.inf = T, M = 10),
-                                     .id = "sim", .progress = T, .options = future_options(seed = as.integer(123)))
+                                     .id = "sim", .progress = T, .options = future_options(seed = seed))
 cor_out_cart_part_n10000 <- future_map_dfr(1:nsim, ~ synth_sampled_data(p = p, r2 = r2, ratio = ratio, rho = rho, 
                                                                    n = n3, formula = f, pop.inf = T, M = 10),
-                                      .id = "sim", .progress = T, .options = future_options(seed = as.integer(123)))
+                                      .id = "sim", .progress = T, .options = future_options(seed = seed))
 
 
 # Obtain the results
@@ -87,15 +89,15 @@ norm <- rep("norm", length(ratio) + 1)
[…]

### 2020-07-13 2.f Synthesize 10 subsets with and without correlations.R

@@ -16,6 +16,8 @@ library(synthpop)
 ## Specify that we run the code in multiple sessions, to speed up the process
 plan(multisession)
 
+seed <- as.integer(12345)
+
 ## Set the number of simulations
 nsim <- 1000
 
@@ -41,7 +43,8 @@ f <- DV ~ -1 + IV1 + IV2 + IV3
 # Specify a small function for inside the future_map commands
 synth_sampled_data <- function(p, r2, ratio, rho, n, formula, pop.inf = T, method = NULL, M) {
   part <- normal(r2, ratio, rho, n)$dat %>% resample_partition(p)
-  syn_part_data(partitioned_data = part, M = M, formula = formula, pop.inf = pop.inf, method = method)
+  syn_part_data(partitioned_data = part, M = M, formula = formula, pop.inf = pop.inf, 
+                method = method, visit = 1:(length(ratio)+1))
 }
 
 
@@ -55,10 +58,10 @@ names(p) <- paste0("p", 1:n.parts)
 # cart method
 p10_out_cart_part_n100 <- future_map_dfr(1:nsim, ~ synth_sampled_data(p = p, r2 = r2, ratio = ratio, rho = rho, 
                                                                       n = n1, formula = f, pop.inf = T, M = 10),
-                                         .id = "sim", .progress = T, .options = future_options(seed = as.integer(123)))
+                                         .id = "sim", .progress = T, .options = future_options(seed = seed))
 p10_out_cart_part_n1000 <- future_map_dfr(1:nsim, ~ synth_sampled_data(p = p, r2 = r2, ratio = ratio, rho = rho, 
                                                                        n = n2, formula = f, pop.inf = T, M = 10),
-                                          .id = "sim", .progress = T, .options = future_options(seed = as.integer(123)))
+                                          .id = "sim", .progress = T, .options = future_options(seed = seed))
 # p10_out_cart_part_n10000 <- future_map_dfr(1:nsim, ~ synth_sampled_data(p = p, r2 = r2, ratio = ratio, rho = rho, 
 #                                                                         n = n3, formula = f, pop.inf = T, M = 10),
 #                                            .id = "sim", .progress = T, .options = future_options(seed = as.integer(123)))
@@ -86,11 +89,11 @@ norm <- rep("norm", length(ratio) + 1)
 p10_out_norm_part_n100 <- future_map_dfr(1:nsim, ~ synth_sampled_data(p = p, r2 = r2, ratio = ratio, rho = rho, 
[…]

### 2020-07-13 2.g Synthesize bootstrapped boys data.R

@@ -9,6 +9,8 @@ source("1.c Functions.R")
 
 plan(multisession)
 
+seed <- as.integer(12345)
+
 # Specify a small function for inside the future_map commands
 synth_bootstrapped_data <- function(p, data, formula, pop.inf = T, method = NULL, M = 1, visit = (1:ncol(data))) {
   part <- data %>% resample_bootstrap %>% data.frame %>% resample_partition(p)
@@ -25,7 +27,7 @@ nsim <- 1000
 f <- wgt ~ age + hgt
 
 boys_cart_results_10 <- future_map_dfr(1:nsim, ~ synth_bootstrapped_data(p = p, data = boyscomp, formula = f, pop.inf = T, M = 10),
-                                    .id = "sim", .progress = T, .options = future_options(seed = as.integer(125)))
+                                           .id = "sim", .progress = T, .options = future_options(seed = seed))
 
 meth <- c("cart", "cart", "cart", "~ I(wgt / (hgt/100)^2)", "cart", "cart", "cart", "cart", "cart")
 
@@ -33,14 +35,14 @@ vs <- c(2,3,4,1,5,6,7,8,9)
 
 boys_vs_results_10 <- future_map_dfr(1:nsim, ~ synth_bootstrapped_data(p = p, data = boyscomp, formula = f, method = meth, 
                                                                      pop.inf = T, M = 10, visit = vs), 
-                                   .id = "sim", .progress = T, .options = future_options(seed = as.integer(123)))
+                                   .id = "sim", .progress = T, .options = future_options(seed = seed))
 
 boys_cart_results_20 <- future_map_dfr(1:nsim, ~ synth_bootstrapped_data(p = p, data = boyscomp, formula = f, pop.inf = T, M = 20),
-                                    .id = "sim", .progress = T, .options = future_options(seed = as.integer(125)))
+                                       .id = "sim", .progress = T, .options = future_options(seed = seed))
 
 boys_vs_results_20 <- future_map_dfr(1:nsim, ~ synth_bootstrapped_data(p = p, data = boyscomp, formula = f, method = meth, 
                                                                     pop.inf = T, M = 20, visit = vs), 
[…]

### 2020-07-14 summary.Rmd
Updated cached files

@@
 # Introduction
+
+Federated data analyses ensure the privacy and confidentiality of micro-data, i.e., data on the individual level, since the data itself is not available to the researcher.
+Instead of obtaining the data itself, the researcher get remote access to the data, which allows the researcher to analyse the data by means of a model of choice.
+Then, the output of the analyses, say, regression coefficients, are made available, so that the results of the research can be published.
+Eventually, one can extend this framework to multiple nodes.
+That is, data is collected on multiple locations, and after the data is harmonized, the results of the analyses run on each local node are combined.
+Federated data analysis meets the increasing demand of privacy and confidentiality on the side of the participant, which hopefully increases the willingness of respondents to participate.
+Advantages on the side of the researcher are the increased generalizability of the research itself and the improved opportunities for collaboration.
+
+* See http://www.ete-online.com/content/10/1/12 for references with regard to these advantages.
+
+However, additionally there obstacles that must be overcome to implement the approach in practice.
+One of these obstacles is how one should deal with missing data.
+Locally, one could use multiple imputation to adjust for the fact that some observations might have missing values on one or multiple variables.
+However, in such instances the imputation model can only be based on the observations within a single node, and use the variables that are observed within that specific node.
+Therefore, observations within other nodes cannot be used, although these might contain relevant information that can be used to impute the missing values.

### 2020-07-16 synthesizing_partitioned_data.Rmd
Full boys data added

@@
 
+```{r, echo = F, dpi = 300}
+boys_cart_results_10 %>%
+  filter(Variable == "(Intercept)") %>%
+  ggplot(mapping = aes(x = Est, color = Method, fill = Method)) +
+  geom_density(alpha = .4) +
+  scale_color_brewer(palette = "Set1") +
+  scale_fill_brewer(palette = "Set1") +
+  ggtitle("Intercept") +
+  theme_classic() -> plot_intercept
+
+boys_cart_results_10 %>%
+  filter(Variable == "age") %>%
+  ggplot(mapping = aes(x = Est, color = Method, fill = Method)) +
+  geom_density(alpha = .4) +
+  scale_color_brewer(palette = "Set1") +
+  scale_fill_brewer(palette = "Set1") +
+  ggtitle("Age") +
+  theme_classic() -> plot_age
+
+boys_cart_results_10 %>%
+  filter(Variable == "hgt") %>%
+  ggplot(mapping = aes(x = Est, color = Method, fill = Method)) +
+  geom_density(alpha = .4) +
+  scale_color_brewer(palette = "Set1") +
+  scale_fill_brewer(palette = "Set1") +
+  ggtitle("Height") +
+  theme_classic() -> plot_height
+
+cowplot::plot_grid(cowplot::plot_grid(plot_intercept + theme(legend.position = "none"), 
+                                     plot_age + theme(legend.position = "none"), 
+                                     plot_height + theme(legend.position = "none"), 
+                                     nrow = 1, align = 'vh'),
+                  cowplot::get_legend(plot_age + theme(legend.position = "bottom")),
+                                      ncol = 1, rel_heights = c(1, .1))
+```
+
 When we increase the number of synthetic datasets to $M = 20$, the coverage is actually slightly worse than in the case of $M = 10$.
@@
 knitr::kable(broom::tidy(lm(wgt ~ age + hgt, boyscomp), conf.int = T))
+```
+
+```{r, include = F, cache=thomcache, cache.lazy=thomlazy}
+source("2.h Synthesize bootstrapped boys7482 data.R")
+```
+
+When we additionally do this with the `boys7482` data from the package `AGD`, we get slightly beter results.
+However, there remains a problem with regard to the bootstrapped samples from the population.
+So apparently, the bootstrapping procedure induces more variance than would be expected based on the $95\%$ CI.
+I am not sure why this error is introduced.
+Additionally, the synthesizing method seems to be somewhat biased, which can be seen in the density plots displayed after the tables.
+
+```{r, echo = F}
+knitr::kable(summary_cart_10_7482, digits = 3)
+```
+
+```{r, echo = F, dpi = 300}
+boys_cart_results_10_7482 %>%
+  filter(Variable == "(Intercept)") %>%
+  ggplot(mapping = aes(x = Est, color = Method, fill = Method)) +
+  geom_density(alpha = .4) +
+  scale_color_brewer(palette = "Set1") +
+  scale_fill_brewer(palette = "Set1") +
+  ggtitle("Intercept") +
+  theme_classic() -> plot_intercept_7482
+
+boys_cart_results_10_7482 %>%
+  filter(Variable == "age") %>%
+  ggplot(mapping = aes(x = Est, color = Method, fill = Method)) +
+  geom_density(alpha = .4) +
+  scale_color_brewer(palette = "Set1") +
+  scale_fill_brewer(palette = "Set1") +
+  ggtitle("Age") +
+  theme_classic() -> plot_age_7482
+
+boys_cart_results_10_7482 %>%
+  filter(Variable == "hgt") %>%
+  ggplot(mapping = aes(x = Est, color = Method, fill = Method)) +
+  geom_density(alpha = .4) +
+  scale_color_brewer(palette = "Set1") +
+  scale_fill_brewer(palette = "Set1") +
+  ggtitle("Height") +
+  theme_classic() -> plot_height_7482
+
+cowplot::plot_grid(cowplot::plot_grid(plot_intercept_7482 + theme(legend.position = "none"), 
+                                     plot_age_7482 + theme(legend.position = "none"), 
+                                     plot_height_7482 + theme(legend.position = "none"), 
+                                     nrow = 1, align = 'vh'),
+                  cowplot::get_legend(plot_age_7482 + theme(legend.position = "bottom")),
+                                      ncol = 1, rel_heights = c(1, .1))
 ```

### 2020-07-16 1.a.2 Create data - boys7482 complete.R

@@ -1,0 +1,35 @@
+###############################################################################
+## Create data sets to work with, we will work with the boys dataset that is ##
+## build-in in mice.                                                         ##
+###############################################################################
+
+
+###############################################################################
+## Load packages and set seed                                                ##
+###############################################################################
+
+library(mice)   ## mice for the boys data and the imputations
+library(modelr) ## modelr to do the partitioning   
+
+set.seed(123)   # seed for reproducibility of the imputations and partitioning
+
+###############################################################################
+## obtain and impute the boys dataset, create the completed boys data, and   ##
+## partition the completed dataset                                           ##
+###############################################################################
+
+meth <- make.method(AGD::boys7482)
+pred <- make.predictorMatrix(boys)
+meth["bmi"] <- "~ I(wgt / (hgt/100)^2)"
+
+pred[c("wgt", "hgt"), "bmi"] <- 0
+
+imp7482 <- mice(AGD::boys7482, meth = meth, pred = pred,      ## Impute the boys dataset by means of a single
+            m = 1, printFlag = F)                    ## imputation, and fill in the imputed data into
+boyscomp7482 <- complete(imp7482)                        ## the dataset containing missing values.
+
+
+ngroups <- 5                                         ## Specify five groups, and
+partitions <- rep(1/ngroups,ngroups)                 ## specify five equal fractions
+names(partitions) <- paste0("d", 1:ngroups)          ## give names to the partitionings and
+part <- resample_partition(boyscomp7482, partitions) ## partition the data in five equal parts

### 2020-07-16 2.g Synthesize bootstrapped boys data.R
Different synthesizing sequence

@@ -44,6 +44,10 @@ boys_vs_results_20 <- future_map_dfr(1:nsim, ~ synth_bootstrapped_data(p = p, da
                                                                     pop.inf = T, M = 20, visit = vs), 
                                   .id = "sim", .progress = T, .options = future_options(seed = seed))
 
+boys_vs2_results_10 <- future_map_dfr(1:nsim, ~ synth_bootstrapped_data(p = p, data = boyscomp, formula = f, method = meth, 
+                                                                        pop.inf = T, M = 10), 
+                                      .id = "sim", .progress = T, .options = future_options(seed = seed))
+
 get_coefs <- function(data) {
   data %>% 
     filter(Method == "Real_Sample") %>% 
@@ -57,6 +61,6 @@ summary_vs_10 <- boys_vs_results_10 %>% print_results(., get_coefs(.))
 summary_cart_20 <- boys_cart_results_20 %>% print_results(., get_coefs(.))
 summary_vs_20 <- boys_vs_results_20 %>% print_results(., get_coefs(.))
 
-
+boys_vs2_results_10 %>% print_results(., get_coefs(.))
 
 

### 2020-07-16 2.i Synthesize bootstrapped boys data wgt hgt.R

@@ -1,0 +1,49 @@
+
+
+library(tidyverse)
+library(synthpop)
+library(furrr)
+
+source("1.a Create data - boys complete.R")
+source("1.c Functions.R")
+
+plan(multisession)
+
+seed <- as.integer(12345)
+
+# Specify a small function for inside the future_map commands
+synth_bootstrapped_data <- function(p, data, formula, pop.inf = T, method = NULL, M = 1, visit = (1:ncol(data))) {
+  part <- data %>% resample_bootstrap %>% data.frame %>% resample_partition(p)
+  syn_part_data(partitioned_data = part, M = M, formula = formula, pop.inf = pop.inf, method = method, visit = visit)
+}
+
+# Specify the number of partitions (5 equally large partitions)
+n.parts <- 5
+p <- rep(1 / n.parts, n.parts)
+names(p) <- paste0("p", 1:n.parts)
+
+nsim <- 1000
+
+f <- wgt ~ age + hgt
+
+meth <- c("cart", "cart", "cart", "~ I(wgt / (hgt/100)^2)", "cart", "cart", "cart", "cart", "cart")
+
+wgt_hgt_swapped <- future_map_dfr(1:nsim, ~ synth_bootstrapped_data(p = p, data = boyscomp, formula = f, pop.inf = T, M = 10,
+                                                                         method = meth,
+                                                                         visit = c("age", "wgt", "hgt", "bmi", "hc", "gen", "phb", "tv", "reg")),
+                                       .id = "sim", .progress = T, .options = future_options(seed = seed))
+
+
+get_coefs <- function(data) {
+  data %>% 
+    filter(Method == "Real_Sample") %>% 
+    group_by(Variable) %>%
+    summarise(coef = mean(Est)) %>%
+    pull(coef, name = Variable)}
+
+
+summary_wgt_hgt <- wgt_hgt_swapped %>% print_results(., get_coefs(.))
+
+
+
+

### 2020-07-19 gerko/boot_cov.R
added coverage demo for bootstraps

@@ -1,0 +1,82 @@
+# parameters
+set.seed(123)
+
+# packages
+library(mvtnorm)
+library(mice)
+library(plyr)
+library(dplyr)
+library(magrittr)
+library(purrr)
+
+set.seed(123)
+nsim = 10000
+
+# establish origin
+truth <- mice(boys, m=1, print = FALSE) %>% mice::complete()
+truemodel <- truth %$%
+  lm(wgt ~ hgt + age)
+
+# sim bootstrap
+simdata <- replicate(nsim, 
+                     truth[sample(1:748, 748, replace = TRUE), ], 
+                     simplify = FALSE)
+
+# calculate statistics
+model <- simdata %>% map(~ lm(wgt ~ hgt + age, data = .x))
+ci <- model %>% map(confint)
+estimates <- model %>% 
+  map(coef) %>% 
+  do.call(rbind, args = .)
+cov <- ci %>% 
+  map(function(x) x[, 1] <= coef(truemodel) & coef(truemodel) <= x[, 2]) %>%
+  do.call(rbind, args = .)
+manual <- model %>% 
+  map(function(x) cbind(vcov(x) %>% diag %>% sqrt(.), coef(x))) %>% # est and resp. vars
+  map(function(x) cbind(x[, 2] - qt(.975, 747) * x[, 1],  x[, 2] + qt(.975, 747) * x[, 1])) %>%
+  map(function(x) x[, 1] <= coef(truemodel) & coef(truemodel) <= x[, 2]) %>%
+  do.call(rbind, args = .)
+manual2 <- model %>% 
+  map(function(x) cbind(sqrt(diag(var(estimates))), coef(x))) %>% # sd of 
+  map(function(x) cbind(x[, 2] - qt(.975, 747) * x[, 1],  x[, 2] + qt(.975, 747) * x[, 1])) %>%
+  map(function(x) x[, 1] <= coef(truemodel) & coef(truemodel) <= x[, 2]) %>%
+  do.call(rbind, args = .)
+
+# manual based on empirical quantiles
+intercept <- data.frame(est = mean(estimates[, 1]), 
+                        ciw = diff(quantile(estimates[, 1], probs = c(.025, .975)))) %>%
+  mutate(low = est - ciw/2,
+         up = est + ciw/2)
+hgt <- data.frame(est = mean(estimates[, 2]), 
+                  ciw = diff(quantile(estimates[, 2], probs = c(.025, .975)))) %>%
+  mutate(low = est - ciw/2,
+         up = est + ciw/2)
[…]

### 2020-07-20 mice_synthesizing/Mice_Synthesizing.Rmd
New folder for synthesizing with mice

---
title: "Synthesizing by means of mice"
author:
- Thom Volker
- Utrecht University
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
bibliography: federated_imp.bib
csl: "/Users/thomvolker/Documents/styles/apa-6th-edition.csl"
---

This is the markdown file for synthesizing data by means of mice.

### 2020-07-20 gerko/BootstrapCI_Validity.Rmd
add documented simulation

---
title: "Confidence validity of bootstrap estimates"
author: "Gerko Vink"
date: "7/20/2020"
output: 
  html_document:
    toc: true
    toc_depth: 5
    toc_float: true
    number_sections: true
---

<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 12px;
}
h1.title {
  font-size: 20px;
  color: DarkBlue;
}
h1 { /* Header 1 */
  font-size: 18px;
}
h2 { /* Header 2 */
    font-size: 16px;
}
h3 { /* Header 3 */
  font-size: 14px;
}
code.r{ /* Code block */
    font-size: 12px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 12px;
}
</style>

---

# Aim
In this document we explore the confidence validity of bootstrap estimates. The goal of this investigation is to study the possibility of using the bootstrap to simulate a monte carlo experiment on a single (small) data set.

---

# Set up
This section covers the global parameters and the necessary packages for executing the simulation study.

---

## Fixing the random seed
Later on, we will be using random numbers. We fix the seed of the random number generator, so that we can always reproduce the results obtained in this document. 
```{r}
set.seed(123)
```
The random seed is a number used to initialize the pseudo-random number generator. The initial value (the seed) itself does not need to be random. The resulting process is random because the seed value is not used to generate randomness - it merely forms the starting point of the algorithm for which the results are random.

---

## Loading the required packages
```{r message=FALSE, warning=FALSE}
library(dplyr)    # Data manipulation
library(magrittr) # Pipes
library(purrr)    # Functional programming
library(mice)     # Data imputation
library(psych)    # Descriptives
library(knitr)    # 
library(kableExtra) #Cool tables
```

---

## Number of simulations
In this document we perform a Monte Carlo experiment. Here we define the number of replications that makes up this experiment. 
```{r}
nsim = 10000
```

---

# Establish the origin
We define a completed version of the `mice::boys` data set as the origin - conventionally we would consider this to be an infinitely large population - against which we compare our estimates. 
```{r}
origin <- mice(boys, m=1, print = FALSE) %>% # impute only once
  mice::complete() # extract completed data
```

---

## Model of interest
We define the following model to be evaluated in simulation
$$\text{wgt} = \beta_0 + \beta_1\text{hgt} + \beta2\text{age} + \epsilon$$
For the `origin` set, we extract the linear model as follows:
```{r}
truemodel <- origin %$%
  lm(wgt ~ hgt + age)
```

---

# Draw the bootstrap sets
We use the `replicate()` function to draw `nsim =``r nsim` bootstrap sets from the `origin`
```{r cache=TRUE}
simdata <- replicate(nsim, 
                     origin[sample(1:748, 748, replace = TRUE), ], 
                     simplify = FALSE)
```

---

# Bias
First we evaluate the model of interest on each of the drawn bootstrap samples. We do this with the `purrr::map()` function, which *maps* the evaluation on each of the listed elements in the `simdata` object.
```{r}
model <- simdata %>% 
  map(~ lm(wgt ~ hgt + age, data = .x))
```
Then, we extract the estimates from the `model` evaluations.
```{r cache=TRUE}
estimates <- model %>% 
  map(coef) %>% 
  do.call(rbind, args = .) # bind rows into matrix
```

The obtained average estimates are 
```{r cache=TRUE}
estimates %>% 
  describe(quant = c(.025, .975)) %>%
  .[, c(2:4, 8:9, 11:12, 14:15)] %>%
  kable("html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F)
```

We find that the estimates display on average a low bias. 
```{r}
estimates %>% 
  colMeans
```

---

# Confidence Validity

---

# Approach 1: CI's with base `R`

We use the `confint()` function to extract the confidence intervals for each of the linear models in the `model` object. 
```{r cache=TRUE}
ci <- model %>% 
  map(confint)

```
We then calculate the proportion of confidence intervals that cover the `truemodel` parameters
```{r cache=TRUE}
cov <- ci %>% 
  map(function(x) x[, 1] <= coef(truemodel) & coef(truemodel) <= x[, 2]) %>%
  do.call(rbind, args = .) # bind rows into matrix
```

---

# Approach 2: manually calculated CI's
For unknown $\sigma^2_\beta$, the $1-\alpha$ confidence interval for $\beta$ is defined as  
\[\mu = \hat{\beta} \pm t_{n-1, a/2}\frac{S}{\sqrt{N}}.\]. The following code extracts the estimates and the standard error
```{r cache=TRUE}
manual <- model %>% 
  map(function(x) cbind(vcov(x) %>% diag %>% sqrt(.), coef(x))) %>% # est and resp. vars
  map(function(x) cbind(x[, 2] - qt(.975, 747) * x[, 1],  x[, 2] + qt(.975, 747) * x[, 1])) %>%
  map(function(x) x[, 1] <= coef(truemodel) & coef(truemodel) <= x[, 2]) %>%
  do.call(rbind, args = .) # bind rows into matrix
```

---

# Approach 3: bootstrap CI's cf. bootstrap SE
Instead of drawing the standard errors from every model, we can also make use of the bootstrap estimate of the standard error - i.e. the square root of the variance of the vector of estimates. This gives us the empirical standard deviation of the realized bootstrap sampling distribution of the estimates. 
```{r}
manual2 <- model %>% 
  map(function(x) cbind(sqrt(diag(var(estimates))), coef(x))) %>% # sd of 
  map(function(x) cbind(x[, 2] - qt(.975, 747) * x[, 1],  x[, 2] + qt(.975, 747) * x[, 1])) %>%
  map(function(x) x[, 1] <= coef(truemodel) & coef(truemodel) <= x[, 2]) %>%
  do.call(rbind, args = .)
```

---

# Approach 4: bootstrap CI's cf average CI
Another approach is to calculate the bootstrap CI based on the quantiles of the vectors of estimates. Simply dividing the confidence interval width would then yield an empirical equivalent to $\pm t_{n-1, a/2}\frac{S}{\sqrt{N}}$. 
```{r cache = TRUE}
# confidence intervals and widths
intercept <- data.frame(est = mean(estimates[, 1]), 
                        ciw = diff(quantile(estimates[, 1], probs = c(.025, .975)))) %>%
  mutate(low = est - ciw/2,
         up = est + ciw/2)
hgt <- data.frame(est = mean(estimates[, 2]), 
                  ciw = diff(quantile(estimates[, 2], probs = c(.025, .975)))) %>%
  mutate(low = est - ciw/2,
         up = est + ciw/2)
age <- data.frame(est = mean(estimates[, 3]), 
                  ciw = diff(quantile(estimates[, 3], probs = c(.025, .975)))) %>%
  mutate(low = est - ciw/2,
         up = est + ciw/2)
# coverages
covint <- data.frame(est = estimates[, 1], 
                     low = estimates[, 1] - intercept$ciw/2,
                     up = estimates[, 1] + intercept$ciw/2) %>%
  mutate(cov = low <= coef(truemodel)[1] & coef(truemodel)[1] <= up)
covhgt <- data.frame(est = estimates[, 2], 
                     low = estimates[, 2] - hgt$ciw/2,
                     up = estimates[, 2] + hgt$ciw/2) %>%
  mutate(cov = low <= coef(truemodel)[2] & coef(truemodel)[2] <= up)
covage <- data.frame(est = estimates[, 3], 
                     low = estimates[, 3] - age$ciw/2,
                     up = estimates[, 3] + age$ciw/2) %>%
  mutate(cov = low <= coef(truemodel)[3] & coef(truemodel)[3] <= up)
```

---

# Results
Below are the coverages for each of the investigated scenarios. Results are depicted for the coverage of the confidence intervals over the regression estimates for `r nsim` simulations.
```{r}
output <- rbind(colMeans(cov), 
                colMeans(manual), 
                colMeans(manual2), 
                colMeans(cbind(covint$cov, covhgt$cov, covage$cov)))
rownames(output) <- c("confint", 
                      "manual", 
                      "bootstrap SE", 
                      "bootstrap CI")
kable(output, "html") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = F)
```

---

END OF DOCUMENT

### 2020-07-21 mice_synthesizing/Mice_Synthesizing.Rmd
Added 50% synthetic data

@@
 output: 
+  word_document:
+    toc: true
   html_document:
@@
 
-This is the markdown file for synthesizing data by means of mice.
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+thomcache <- TRUE; thomlazy <- FALSE #obviously ;)
+library(tidyverse)
+```
+
+# Use mice to impute all data
+
+```{r, include = F, cache = thomcache, cache.lazy=thomlazy}
+source("1.a Synthesize_Mice_Replace_All")
+```
+
+First, we again create 1 complete dataset, which is done by means of imputing the `boys` dataset in `mice` [@mice] with default settings, and complete the dataset.
+Then, based on this one true dataset, we extract the regression coefficients of a linear regression model in which weight is regressed on age and height, that are used to compare the estimates of the synthetic versions of the datasets.
+The true regression coefficients are equal to $\beta_0 = `r coefs[1]`$, $\beta_{age} = `r coefs[2]`$, $\beta_{height} = `r coefs[3]`$.
+Then, for a total of 200 iterations, we impute a matrix with the same dimensions as the boys dataset (that is, the sample size $n = `r nrow(truth)`$ and the number of predictors $k = `r ncol(truth)`$).
+This is done once with the default settings, that is, with `pmm` for the continuous variables, `polr` for binary variables and `polyreg` for ordinal variables with more than two categories.
+Furthermore, `bmi` is imputed passively, since it consists of a fixed combination of height and weight `bmi = (wgt / (hgt/100)^2`.
+Furthermore, the predictor matrix is adjusted so that imputations for `bmi` do not flow back into predictions of `hgt` and `wgt`.
+Then, for every synthetic dataset, the estimates, and corresponding variance of the estimates are calculated, as well as the $95\%~CI$ are calculated.
+Furthermore, an indicator is added, whether or not the confidence interval includes the true parameter estimates.
+Note that these confidence intervals are still based on imputations for missing data, instead of imputations for synthetic data.
+This is due to the fact that the calculation for the degrees of freedom for the estimates based imputing synthetic values might yield degrees of freedom that are so small that the corresponding $95\% ~ CI$ yields boundary values of $-\infty$ and $\infty$.
+
+```{r, echo = F}
+bind_rows("Mice default" = results_def,
+          "Mice with cart" = results_cart, .id = "Imputation method")
+```
+
+Additionally, an approach is tested in which $\frac{5}{9}$ of the values are randomly selected to be imputed.
+Using this approach, eventually in two steps, all values can be replaced, while still using almost 50% of the information that is already in the data.
+Eventually, in a second step, the other almost 50% can be replaced, and the datafiles can be merged so that eventually the full dataset can be made synthetic again.
+However, currently this is not yet implemented.
+
+```{r, echo = F}
+bind_rows("Mice default" = results_def_50,
+          "Mice with cart" = results_cart_50, .id = "Imputation method")
+```

### 2020-07-21 mice_synthesizing/1.a Synthesize_Mice_Replace_All.R

@@ -1,0 +1,240 @@
+library(mice)
+library(tidyverse)
+library(modelr)
+library(magrittr)
+library(furrr)
+
+truth <- boys %>% mice(seed = 123, m = 1, print = FALSE) %>% complete()
+
+model <- function(data) lm(wgt ~ age + hgt, data)
+
+truemodel <- truth %>% model
+
+coefs <- coef(truemodel)
+
+## Approach one - overwrite all of the data
+
+plan(multisession)
+
+nsim <- 200
+
+def <- rep("pmm", ncol(truth))
+names(pmm) <- colnames(truth)
+pmm['bmi'] <- "~I(wgt / (hgt/100)^2)"
+pmm[c('gen', 'phb')] <- "polr"
+pmm['reg'] <- "polyreg"
+
+
+cart <- rep("cart", ncol(truth))
+names(cart) <- colnames(truth)
+
+meth['bmi'] <- "~I(wgt / (hgt/100)^2)"
+
+pred <- make.predictorMatrix(truth)
+pred[c("wgt", "hgt"), "bmi"] <- 0
+
+all_syns_def <- future_map(1:nsim, ~ {
+  truth %>% mice(m = 5, 
+                 method = pmm, 
+                 predictorMatrix = pred, 
+                 where = matrix(TRUE, nrow(truth), ncol(truth)), 
+                 print = F)
+}, .options = future_options(seed = as.integer(123)), .progress = TRUE, .id = "syn")
+
+
+
+all_syns_cart <- future_map(1:nsim, ~ {
+  truth %>% mice(m = 5, 
+                 method = cart,
+                 predictorMatrix = pred,
+                 where = matrix(TRUE, nrow(truth), ncol(truth)),
+                 print = F)
+}, .options = future_options(seed = as.integer(123)), .progress = TRUE, .id = "syn")
+
+
+est_def <- all_syns_def %>% map(function(x) with(x, lm(wgt ~ age + hgt)) %>% pool %>% summary)
+
+est_cart <- all_syns_cart %>% map(function(x) with(x, lm(wgt ~ age + hgt)) %>% pool %>% summary)
+
+CIs_def <- map(est_def, function(x) {
+  
+  var      <- x[,1]
+  true_est <- coefs
+  est      <- x[,2]
+  true_se  <- sqrt(diag(vcov(truemodel)))
+  se       <- x[,3]
[…]

### 2020-07-23 mice_synthesizing/Mice_Synthesizing.Rmd
Synthesizing with mice

@@
 output: 
-  word_document:
-    toc: true
   html_document:
@@
 ```{r, include = F, cache = thomcache, cache.lazy=thomlazy}
-source("1.a Synthesize_Mice_Replace_All")
+source("1.a Synthesize_Mice_Replace_All.R")
 ```
@@
 Then, based on this one true dataset, we extract the regression coefficients of a linear regression model in which weight is regressed on age and height, that are used to compare the estimates of the synthetic versions of the datasets.
-The true regression coefficients are equal to $\beta_0 = `r coefs[1]`$, $\beta_{age} = `r coefs[2]`$, $\beta_{height} = `r coefs[3]`$.
+The true regression coefficients are equal to $\beta_0 = `r round(coefs[1],3)`$, $\beta_{age} = `r round(coefs[2], 3)`$, $\beta_{height} = `r round(coefs[3], 3)`$.
 Then, for a total of 200 iterations, we impute a matrix with the same dimensions as the boys dataset (that is, the sample size $n = `r nrow(truth)`$ and the number of predictors $k = `r ncol(truth)`$).
@@
 
+## True results
+```{r, echo = F}
+broom::tidy(truemodel, conf.int=TRUE) %>%
+  mutate(CIW = conf.high - conf.low) %>% knitr::kable(digits = 3)
+```
+
+## Impute all values
+
 ```{r, echo = F}
 bind_rows("Mice default" = results_def,
-          "Mice with cart" = results_cart, .id = "Imputation method")
+          "Mice with cart" = results_cart, .id = "Imputation method") %>% knitr::kable(digits = 3)
 ```
+
+## Impute part of the values
 
@@
 bind_rows("Mice default" = results_def_50,
-          "Mice with cart" = results_cart_50, .id = "Imputation method")
+          "Mice with cart" = results_cart_50, .id = "Imputation method") %>% knitr::kable(digits = 3)
 ```
+
+```{r, include = F, cache = thomcache}
+future::plan(future::multisession)
+all_syns_wgt_hgt <- future_map(1:nsim, ~ {
+  truth %>% mice(m = 5, 
+                 method = cart,
+                 visitSequence = c("age", "wgt", "hgt", "bmi", "hc", "gen", "phb", "tv", "reg"),
+                 predictorMatrix = pred,
+                 where = matrix(TRUE, nrow(truth), ncol(truth)),
+                 print = F)
+}, .options = future_options(seed = as.integer(123)), .progress = TRUE, .id = "syn")
+```
+
+## Different visiting sequence
+
+```{r, echo = F}
+est_wgt_hgt <- all_syns_wgt_hgt %>% map(function(x) with(x, lm(wgt ~ age + hgt)) %>% pool %>% summary)
+
+CIs_wgt_hgt <- map(est_wgt_hgt, function(x) {
+
+  var      <- x[,1]
+  true_est <- coefs
+  est      <- x[,2]
+  true_se  <- sqrt(diag(vcov(truemodel)))
+  se       <- x[,3]
+  lower    <- x[,2] + x[,3] * qt(.025, x[,5])
+  upper    <- x[,2] + x[,3] * qt(.975, x[,5])
+  cov      <- lower < coefs & coefs < upper
+
+  bind_cols(var = var, true_est = true_est, est = est, true_se = true_se, se = se, lower = lower, upper = upper, cov = cov)
+})
+
+results_wgt_hgt <- CIs_wgt_hgt %>% bind_rows %>% group_by(var) %>%
+  summarise("True Est" = unique(true_est),
+            "Syn Est"  = mean(est),
+            "Bias"     = mean(est - true_est),
+            "True SE"  = unique(true_se),
+            "Syn SE"   = mean(se),
+            "CIW"      = mean(upper - lower),
+            "Coverage" = mean(cov))
+
+```
+# References

### 2020-07-23 mice_synthesizing/1.a Synthesize_Mice_Replace_All.R

@@ -19,23 +19,21 @@ plan(multisession)
 nsim <- 200
 
 def <- rep("pmm", ncol(truth))
-names(pmm) <- colnames(truth)
-pmm['bmi'] <- "~I(wgt / (hgt/100)^2)"
-pmm[c('gen', 'phb')] <- "polr"
-pmm['reg'] <- "polyreg"
+names(def) <- colnames(truth)
+def['bmi'] <- "~I(wgt / (hgt/100)^2)"
+def[c('gen', 'phb')] <- "polr"
+def['reg'] <- "polyreg"
 
 
 cart <- rep("cart", ncol(truth))
 names(cart) <- colnames(truth)
-
-meth['bmi'] <- "~I(wgt / (hgt/100)^2)"
 
 pred <- make.predictorMatrix(truth)
 pred[c("wgt", "hgt"), "bmi"] <- 0
 
 all_syns_def <- future_map(1:nsim, ~ {
   truth %>% mice(m = 5, 
-                 method = pmm, 
+                 method = def, 
                  predictorMatrix = pred, 
                  where = matrix(TRUE, nrow(truth), ncol(truth)), 
                  print = F)
@@ -123,7 +121,7 @@ impute <- function(data, meth, pred) {
                 print = F) %$% lm(wgt ~ age + hgt) %>% pool %>% summary
 }
 
-est_def_50 <- future_map(1:nsim, ~ impute(truth, meth = pmm, pred = pred),
+est_def_50 <- future_map(1:nsim, ~ impute(truth, meth = def, pred = pred),
                              .progress = TRUE, .options = future_options(seed = as.integer(123)))
 
 est_cart_50 <- future_map(1:nsim, ~ impute(truth, meth = cart, pred = pred),

### 2020-07-23 synthpop_synthesizing/synthesizing_partitioned_data.Rmd

--- 2020-07-16 synthesizing_partitioned_data.Rmd
@@
 
+```{r, include = F, cache=thomcache, cache.lazy=thomlazy}
+source("2.i Synthesize bootstrapped boys data wgt hgt.R")
+```
+
+#### Regular order of the variables
+
+The regular order of the variables corresponds to the column names of the `boys` dataset (that is, `r colnames(mice::boys)`).
+
+```{r, echo = F}
+knitr::kable(summary_cart_10, digits = 3, caption = "Results after data synthesization of the variables in the order (1) age, (2) hgt, (3) wgt, (4) bmi, (5) hc, (6) gen, (7) phb, (8) tv, (9) reg, in which wgt is regressed age and hgt.")
+```
+
+#### Weight and height swapped
+
+The order of the synthesization of the variables now corresponds to the following: `r c("age", "wgt", "hgt", "bmi", "hc", "gen", "phb", "tv", "reg")`. 
+```{r, echo = F}
+knitr::kable(summary_wgt_hgt, digits = 3, caption = "Results after data synthesization of the variables in the order (1) age, (2) wgt, (3) hgt, (4) bmi, (5) hc, (6) gen, (7) phb, (8) tv, (9) reg, in which wgt is regressed age and hgt.")
+```
+
 ### Missing data workflow

### 2020-07-26 mice_synthesizing/Mice_Synthesizing.Rmd
Update .Rmd and add pool function

--- 2020-07-20 mice_synthesizing/Mice_Synthesizing.Rmd
@@
 
-This is the markdown file for synthesizing data by means of mice.
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
+thomcache <- TRUE; thomlazy <- FALSE #obviously ;)
+library(tidyverse)
+library(magrittr)
+library(knitr)
+library(kableExtra)
+library(mice)
+library(ggplot2)
+```
+
+# Use mice to impute all data
+
+```{r, include = F, cache = thomcache, cache.lazy=thomlazy}
+source("1.a Synthesize_Mice_Replace_All.R")
+source("functions.R")
+```
+
+First, we again create 1 complete dataset, which is done by means of imputing the `boys` dataset in `mice` [@mice] with default settings, and complete the dataset.
+Then, based on this one true dataset, we extract the regression coefficients of a linear regression model in which weight is regressed on age and height, that are used to compare the estimates of the synthetic versions of the datasets.
+The true regression coefficients are equal to $\beta_0 = `r round(coefs[1],3)`$, $\beta_{age} = `r round(coefs[2], 3)`$, $\beta_{height} = `r round(coefs[3], 3)`$.
+Then, for a total of 200 iterations, we impute a matrix with the same dimensions as the boys dataset (that is, the sample size $n = `r nrow(truth)`$ and the number of predictors $k = `r ncol(truth)`$).
+This is done once with the default settings, that is, with `pmm` for the continuous variables, `polr` for binary variables and `polyreg` for ordinal variables with more than two categories.
+Furthermore, `bmi` is imputed passively, since it consists of a fixed combination of height and weight `bmi = (wgt / (hgt/100)^2`.
+Furthermore, the predictor matrix is adjusted so that imputations for `bmi` do not flow back into predictions of `hgt` and `wgt`.
+Then, for every synthetic dataset, the estimates, and corresponding variance of the estimates are calculated, as well as the $95\%~CI$ are calculated.
+Furthermore, an indicator is added, whether or not the confidence interval includes the true parameter estimates.
+Note that these confidence intervals are still based on imputations for missing data, instead of imputations for synthetic data.
+This is due to the fact that the calculation for the degrees of freedom for the estimates based imputing synthetic values might yield degrees of freedom that are so small that the corresponding $95\% ~ CI$ yields boundary values of $-\infty$ and $\infty$.
+
+---
+
+## True results
+
+```{r, echo = T}
+broom::tidy(truemodel, conf.int=TRUE) %>%
+  mutate(CIW = conf.high - conf.low) %>% 
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```
+
+---
+
+## Use mice to synthesize and to pool
+
+### Pool the results of the synthetic datasets with the default mice settings.
+
+```{r, message = F}
+default_fit <- syns_def %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt) %>% pool %>% summary) %>%
+  map_dfr(function(x) {
+    var      <- x[,1]
+    true_est <- coefs
+    est      <- x[,2]
+    true_se  <- sqrt(diag(vcov(truemodel)))
+    se       <- x[,3]
+    df       <- x[,5]
+    lower    <- est + se * qt(.025, df)
+    upper    <- est + se * qt(.975, df)
+    cov      <- lower < coefs & coefs < upper
+
+    bind_cols(var = var, true_est = true_est, est = est, true_se = true_se, 
+                               se = se, df = df, lower = lower, upper = upper, cov = cov)
+    })
+
+results_def <- default_fit %>%
+  group_by(var) %>%
+  summarise("True Est" = unique(true_est),
+            "Syn Est"  = mean(est),
+            "Bias"     = mean(est - true_est),
+            "True SE"  = unique(true_se),
+            "Syn SE"   = mean(se),
+            "df"       = mean(df),
+            "Lower"    = mean(lower),
+            "Upper"    = mean(upper),
+            "CIW"      = mean(upper - lower),
+            "Coverage" = mean(cov))
+```
+
+### Pool the results of the synthetic dataset with CART.
+
+```{r, message = F}
+cart_fit <- syns_cart %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt) %>% pool %>% summary) %>%
+  map_dfr(function(x) {
+    var      <- x[,1]
+    true_est <- coefs
+    est      <- x[,2]
+    true_se  <- sqrt(diag(vcov(truemodel)))
+    se       <- x[,3]
+    df       <- x[,5]
+    lower    <- est + se * qt(.025, df)
+    upper    <- est + se * qt(.975, df)
+    cov      <- lower < coefs & coefs < upper
+
+    bind_cols(var = var, true_est = true_est, est = est, true_se = true_se,
+              se = se, df = df, lower = lower, upper = upper, cov = cov)
+    })
+
+ results_cart <- cart_fit %>%
+   group_by(var) %>%
+   summarise("True Est" = unique(true_est),
+             "Syn Est"  = mean(est),
+             "Bias"     = mean(est - true_est),
+             "True SE"  = unique(true_se),
+             "Syn SE"   = mean(se),
+             "df"       = mean(df),
+             "Lower"    = mean(lower),
+             "Upper"    = mean(upper),
+             "CIW"      = mean(upper - lower),
+             "Coverage" = mean(cov))
+```
+
+### Results for both synthesization methods
+
+```{r, message = F}
+bind_rows("Mice default" = results_def,
+          "Mice with cart" = results_cart, .id = "Imputation method") %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```
+
+---
+
+## Use mice to synthesize with pooling rules from Drechsler
+
+For now, we forget about the default mice imputation method, because it leads to flawed results.
+Therefore, we continue with the CART results only.
+We fit the `lm` model in which `wgt` is regressed on `age` and `hgt`.
+
+```{r, code = readLines("functions.R")}
+```
+
+```{r, message = F}
+models <- syns_cart %>% map(function(x) x %$% lm(wgt ~ age + hgt))
+```
+
+Then, we use the custom pooling function to pool the estimates.
+
+```{r, message = F}
+pooled <- models %>% map_dfr(pool.syn)
+```
+
+And another custom function to summarise all results, and obtain the confidence interval coverage.
+
+```{r, message = F}
+ci_cov(pooled, truemodel) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```
+
+It can be seen that the coverage of the confidence interval is nearly equal to one.
+Since we currently only want to make inferences with regard to the sample, this is okay.
+Namely, if the CI coverage with regard to the sample would be $95\%$, the CI coverage with regard to the population would be $`r .95^2`\%$.
+Inferences with regard to the population will be discussed in the next paragraph.
+
+However, what is questionable, is the fact that the confidence interval width has increased, even though the variance has decreased.
+Since the confidence interval width is a function of only the standard error and the degrees of freedom, this must be due to the fact that the degrees of freedom are smaller than the degrees of freedom as returned by the mice pooling function.
+
+```{r}
+mice_df <- data.frame(term = cart_fit$var, df = cart_fit$df)
+syn_df <- data.frame(term = pooled$term, df = pooled$df)
+
+df <- bind_rows("Mice" = mice_df, "Synthetic" = syn_df, .id = "Method")
+
+ggplot(data = df, aes(x = df, color = Method, fill = Method)) +
+  geom_density(alpha = .7) +
+  facet_wrap(~ term, nrow = 1, scales = "free") +
+  scale_color_viridis_d(begin = .30, end = .65) +
+  scale_fill_viridis_d(begin = .30, end = .65) +
+  theme_classic()
+```
+
+---
+
+## Different synthesizing sequence
+
+Now we have established that the mice synthesizing algorithm works as good as the synthpop synthesizing algorithm, we can check whether changing the order in which `hgt` and `wgt` are synthesized influences the result of the algorithm.
+
+```{r, message = F}
+cart_wgt_hgt %>% 
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool.syn) %>%
+  ci_cov(truemodel) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```
+
+---
+
+# Bootstrap boys data
+
+```{r, message = F}
+synthetic_results <- boot_cart %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool.syn) %>%
+  ci_cov(truemodel) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+true_results <- bootstrap_boys %>%
+  map(~ lm(wgt ~ age + hgt, .x)) %>%
+  map_dfr(~ broom::tidy(.x, conf.int = TRUE)) %>%
+  mutate(true_coef = rep(coef(truemodel), nsim),
+         true_se   = rep(sqrt(diag(vcov(truemodel))), nsim),
+         cover     = conf.low < true_coef & true_coef < conf.high) %>%
+  group_by(term) %>%
+  summarise("True Est" = unique(true_coef),
+            "Boot Est"  = mean(estimate),
+            "Bias"     = mean(estimate - true_coef),
+            "True SE"  = unique(true_se),
+            "Boot SE"   = mean(std.error),
+            "DF"       = 745,
+            "Lower"    = mean(conf.low),
+            "Upper"    = mean(conf.high),
+            "CIW"      = mean(conf.high - conf.low),
+            "Coverage" = mean(cover)) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+```
+
+```{r, echo = F}
+true_results
+synthetic_results
+```
+
+---
+
+# References

### 2020-07-26 mice_synthesizing/1.a Synthesize_Mice_Replace_All.R

@@ -4,6 +4,8 @@ library(modelr)
 library(magrittr)
 library(furrr)
 
+set.seed(123)
+
 truth <- boys %>% mice(seed = 123, m = 1, print = FALSE) %>% complete()
 
 model <- function(data) lm(wgt ~ age + hgt, data)
@@ -16,7 +18,7 @@ coefs <- coef(truemodel)
 
 plan(multisession)
 
-nsim <- 200
+nsim <- 10
 
 def <- rep("pmm", ncol(truth))
 names(def) <- colnames(truth)
@@ -31,7 +33,7 @@ names(cart) <- colnames(truth)
 pred <- make.predictorMatrix(truth)
 pred[c("wgt", "hgt"), "bmi"] <- 0
 
-all_syns_def <- future_map(1:nsim, ~ {
+syns_def <- future_map(1:nsim, ~ {
   truth %>% mice(m = 5, 
                  method = def, 
                  predictorMatrix = pred, 
@@ -41,7 +43,7 @@ all_syns_def <- future_map(1:nsim, ~ {
 
 
 
-all_syns_cart <- future_map(1:nsim, ~ {
+syns_cart <- future_map(1:nsim, ~ {
   truth %>% mice(m = 5, 
                  method = cart,
                  predictorMatrix = pred,
@@ -49,190 +51,24 @@ all_syns_cart <- future_map(1:nsim, ~ {
                  print = F)
 }, .options = future_options(seed = as.integer(123)), .progress = TRUE, .id = "syn")
 
-
-est_def <- all_syns_def %>% map(function(x) with(x, lm(wgt ~ age + hgt)) %>% pool %>% summary)
-
-est_cart <- all_syns_cart %>% map(function(x) with(x, lm(wgt ~ age + hgt)) %>% pool %>% summary)
-
-CIs_def <- map(est_def, function(x) {
-  
-  var      <- x[,1]
-  true_est <- coefs
-  est      <- x[,2]
-  true_se  <- sqrt(diag(vcov(truemodel)))
-  se       <- x[,3]
-  lower    <- x[,2] + x[,3] * qt(.025, x[,5])
-  upper    <- x[,2] + x[,3] * qt(.975, x[,5])
-  cov      <- lower < coefs & coefs < upper
-  
-  bind_cols(var = var, true_est = true_est, est = est, true_se = true_se, se = se, lower = lower, upper = upper, cov = cov)
-})
-
[…]

### 2020-07-26 mice_synthesizing/Mice_Synthesizing.Rmd
Annotate code

@@
 
-# Use mice to impute all data
+# Introduction
 
@@
 
-## True results
+# Simulations
+
+---
+
+## Single dataset approach
+
+---
+
+### True results
 
@@
 
-## Use mice to synthesize and to pool
+### Use mice to synthesize and to pool
 
-### Pool the results of the synthetic datasets with the default mice settings.
+---
+
+#### Pool the results of the synthetic datasets with the default mice settings.
 
@@
 
-### Pool the results of the synthetic dataset with CART.
+#### Pool the results of the synthetic dataset with CART.
 
@@
 
-### Results for both synthesization methods
+#### Results for both synthesization methods
 
@@
 
-## Use mice to synthesize with pooling rules from Drechsler
+### Use mice to synthesize with pooling rules from Drechsler
 
@@
 
-```{r}
+```{r, fig.fullwidth = TRUE, dpi = 500}
 mice_df <- data.frame(term = cart_fit$var, df = cart_fit$df)
@@
 
-## Different synthesizing sequence
+### Different synthesizing sequence
 
@@
 
-# Bootstrap boys data
+## Bootstrapped boys data
 

### 2020-07-26 mice_synthesizing/1.a Synthesize_Mice_Replace_All.R

@@ -1,38 +1,51 @@
-library(mice)
-library(tidyverse)
-library(modelr)
-library(magrittr)
-library(furrr)
 
-set.seed(123)
+library(mice) # imputations
+library(tidyverse) # tidy data
+library(modelr) # bootstrap
+library(magrittr) # pipe
+library(furrr) # parallel mapping
 
+set.seed(123) # seed for reproducibility
+
+#create one complete dataset that allow us to work without missings
 truth <- boys %>% mice(seed = 123, m = 1, print = FALSE) %>% complete()
 
+# shorten the complete lm model, since we want to use the same model anyhow
 model <- function(data) lm(wgt ~ age + hgt, data)
 
+# run this model
 truemodel <- truth %>% model
 
+# extract the coefficients
 coefs <- coef(truemodel)
 
-## Approach one - overwrite all of the data
-
+# parallel processing to increase speed
 plan(multisession)
 
-nsim <- 10
+# number of iterations
+nsim <- 5
 
+# default method - pmm for all continuous predictors
 def <- rep("pmm", ncol(truth))
+# add the variable names
 names(def) <- colnames(truth)
+# impute bmi passively
 def['bmi'] <- "~I(wgt / (hgt/100)^2)"
+# set gen and phb to proportional odds model
 def[c('gen', 'phb')] <- "polr"
+# set reg to polytomous logistic regression
 def['reg'] <- "polyreg"
 
-
+# cart method, all variables are imputed by means of cart
 cart <- rep("cart", ncol(truth))
 names(cart) <- colnames(truth)
 
+# alter the predictor matrix such that imputations for bmi do not flow
+# back into the predictions for wgt and hgt
 pred <- make.predictorMatrix(truth)
 pred[c("wgt", "hgt"), "bmi"] <- 0
 
+# create the default synthetic datasets
 syns_def <- future_map(1:nsim, ~ {
   truth %>% mice(m = 5, 
                  method = def, 
@@ -41,8 +54,7 @@ syns_def <- future_map(1:nsim, ~ {
                  print = F)
 }, .options = future_options(seed = as.integer(123)), .progress = TRUE, .id = "syn")
 
-
-
+# create the synthetic datasets by means of cart
 syns_cart <- future_map(1:nsim, ~ {
   truth %>% mice(m = 5, 
                  method = cart,
@@ -51,6 +63,7 @@ syns_cart <- future_map(1:nsim, ~ {
[…]

### 2020-07-27 mice_synthesizing/1.a Synthesize_Mice_Replace_All.R
Increased number of iterations

@@ -23,7 +23,7 @@ coefs <- coef(truemodel)
 plan(multisession)
 
 # number of iterations
-nsim <- 5
+nsim <- 200
 
 # default method - pmm for all continuous predictors
 def <- rep("pmm", ncol(truth))

### 2020-07-27 mice_synthesizing/Mice_Synthesizing.Rmd

@@
 
-```{r, fig.fullwidth = TRUE, dpi = 500}
+```{r, fig.fullwidth = TRUE, dpi = 1000}
 mice_df <- data.frame(term = cart_fit$var, df = cart_fit$df)
@@
 
+norm_results <- boot_cart %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool.syn) %>%
+  mutate(df = NA,
+         lower = est - qnorm(.975) * sqrt(var),
+         upper = est + qnorm(.975) * sqrt(var)) %>%
+  ci_cov(truemodel) %>%
+  kable(digits = 3, caption = "Normal CI approximation") %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
 true_results <- bootstrap_boys %>%
@@
 synthetic_results
+norm_results
+
 ```

### 2020-07-27 mice_synthesizing/Mice_Synthesizing.Rmd
Alter cart settings for better bias/variance tradeoff (more variance, less bias)

@@
   map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
-  map_dfr(pool.syn) %>%
+  map_dfr(pool.syn) %T>% 
+  assign("boot_syn", ., envir = globalenv()) %>%
   ci_cov(truemodel) %>%
@@
          true_se   = rep(sqrt(diag(vcov(truemodel))), nsim),
-         cover     = conf.low < true_coef & true_coef < conf.high) %>%
+         cover     = conf.low < true_coef & true_coef < conf.high) %T>% 
+  assign("boot_true", ., envir = globalenv()) %>%
   group_by(term) %>%
@@
 norm_results
+```
 
+We find that some bias has been introduced due to synthesizing the relationships, so we investigate this in further depth.
+Additionally, the coverage is somewhat too high, and the average confidence interval width has increased dramatically.
+Therefore, we will further investigate where this increase stems from.
+
+```{r, message = F, fig.fullwidth = TRUE, dpi = 1000}
+plot_dat <- bind_rows("Synthetic" = boot_syn %>% 
+                                    mutate(ciw = upper - lower) %>%
+                                    select(term, est, ciw = ciw), 
+                      "Real values" = boot_true %>% 
+                                      mutate(ciw = conf.high - conf.low) %>%
+                                      select(term, est = estimate, ciw = ciw),
+                      .id = "Method")
+
+ggplot(plot_dat, aes(x = est, color = Method, fill = Method)) +
+  geom_density(alpha = .7) +
+  facet_wrap(~ term, nrow = 1, scales = "free") +
+  scale_color_viridis_d(begin = .30, end = .65) +
+  scale_fill_viridis_d(begin = .30, end = .65) +
+  theme_classic()
 ```
+
+It can be seen that the bias is systematic, and thus not due to any extreme values that pull the average estimate to zero.
+Additionally, it seems that the pooled standard error indicated in the table is somewhat too low for the synthetic data.
+Namely, it appears in the plot that the spread in the synthetic data is roughly equal to the spread in the bootstrapped, but real, data.
+However, in the table above, the synthetic standard errors are much smaller than the mean over the manually calculated standard error of the bootstrapped estimates.
+When the standard errors are calculated over the obtained regression estimates, we find that the synthetic standard error increases much more when we calculate it over the observed synthetic estimates.
+
+```{r, message = F}
+boot_se <- boot_true %>% group_by(term) %>% summarise("Bootstrapped SE" = sd(estimate))
+boot_syn_se <- boot_syn %>% group_by(term) %>% summarise("Synthetic bootstrapped SE" = sd(est))
+
+bind_cols(boot_se, boot_syn_se[,2]) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
+                full_width = FALSE)
+```
+
+```{r, fig.fullwidth = TRUE, dpi = 1000}
+ggplot(plot_dat, aes(x = ciw, color = Method, fill = Method)) +
+  geom_density(alpha = .7) +
+  facet_wrap(~ term, nrow = 1, scales = "free") +
+  scale_color_viridis_d(begin = .30, end = .65) +
+  scale_fill_viridis_d(begin = .30, end = .65) +
+  theme_classic()
+```
+
+When we look at the confidence interval width, we find that the bootstrap CI is of approximately the same length in all iterations, while the CI's of the synthetic results spread out much more.
 

### 2020-07-27 mice_synthesizing/1.a Synthesize_Mice_Replace_All.R

@@ -87,4 +87,21 @@ boot_cart <- bootstrap_boys %>%
          print = F)
     }, .options = future_options(seed = as.integer(123)), .progress = T)
 
+# change cart settings (maxit = 1, minbucket = 3, cp = 1e-08), so that the variance
+# in the imputed datasets increases (and hopefully the bias decreases).
+syns_cart_iter_cp_min3 <- future_map(1:nsim, ~ {
+  truth %>% mice(m = 5,
+                 maxit = 1,
+                 method = cart,
+                 minbucket = 3,
+                 cp = 1e-08,
+                 predictorMatrix = pred,
+                 where = matrix(TRUE, nrow(truth), ncol(truth)),
+                 print = F)
+}, .options = future_options(seed = as.integer(123)), .progress = TRUE)
+
+syns_cart_iter_cp_min3 %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool.syn) %>%
+  ci_cov(., truemodel)
 

### 2020-07-27 mice_synthesizing/Mice_Synthesizing.Rmd
Bootstrap cart with more variance

@@
 
+## Improving the bias/variance tradeoff
+
+The fact that there is bias introduced, might be due to the fact that there is too little variance in the estimates of the synthetic values.
+Therefore, an approach that increases the variance of the estimates might yield estimates that display less bias.
+This can be achieved by decreasing the number of iterations, that is, setting the mice parameter `maxit` to 1, instead of 5.
+Additionally, the complexity parameter can be set to $`r 1e-08`$ instead of $`r 1e-04`$, so that more splits will be made.
+Also, the value of the `rpart` parameter `minbucket`, that is, the minimum number of observations in any terminal node, is set to 3 instead of 5, so that, once again, more splits can be made.
+By means of these changes, the within variance increases, while the between-imputations variability decreases.
+The results with `r nsim` iterations on the same, singly imputed boys dataset can be seen below.
+
+```{r}
+syns_cart_maxit_cp_min3 %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool.syn) %>%
+  ci_cov(., truemodel) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+```
+
+It can be seen that the bias indeed decreases, while the standard error of the estimates increases.
+This is due to the fact that the within-imputation variance increases, while the between-imputation variance decreases somewhat.
+When we use the same approach to estimate the bootstrapped boys data, we get the following results.
+
+```{r}
+boot_cart_maxit_cp_min3 %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool.syn) %>%
+  ci_cov(., truemodel) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```
+
 # References

### 2020-07-27 mice_synthesizing/1.a Synthesize_Mice_Replace_All.R

@@ -23,7 +23,7 @@ coefs <- coef(truemodel)
 plan(multisession)
 
 # number of iterations
-nsim <- 200
+nsim <- 500
 
 # default method - pmm for all continuous predictors
 def <- rep("pmm", ncol(truth))
@@ -73,6 +73,19 @@ cart_wgt_hgt <- future_map(1:nsim, ~ {
                  print = F)
 }, .options = future_options(seed = as.integer(123)), .progress = T, .id = "syn")
 
+# change cart settings (maxit = 1, minbucket = 3, cp = 1e-08), so that the variance
+# in the imputed datasets increases (and hopefully the bias decreases).
+syns_cart_maxit_cp_min3 <- future_map(1:nsim, ~ {
+  truth %>% mice(m = 5,
+                 maxit = 1,
+                 method = cart,
+                 minbucket = 3,
+                 cp = 1e-08,
+                 predictorMatrix = pred,
+                 where = matrix(TRUE, nrow(truth), ncol(truth)),
+                 print = F)
+}, .options = future_options(seed = as.integer(123)), .progress = TRUE)
+
 # create nsim bootstrapped datasets
 bootstrap_boys <- bootstrap(truth, nsim) %$% strap %>% map(as.data.frame)
 
@@ -87,21 +100,17 @@ boot_cart <- bootstrap_boys %>%
          print = F)
     }, .options = future_options(seed = as.integer(123)), .progress = T)
 
-# change cart settings (maxit = 1, minbucket = 3, cp = 1e-08), so that the variance
-# in the imputed datasets increases (and hopefully the bias decreases).
-syns_cart_iter_cp_min3 <- future_map(1:nsim, ~ {
-  truth %>% mice(m = 5,
-                 maxit = 1,
-                 method = cart,
-                 minbucket = 3,
-                 cp = 1e-08,
-                 predictorMatrix = pred,
-                 where = matrix(TRUE, nrow(truth), ncol(truth)),
-                 print = F)
+# impute the bootstrapped boys datasets with parameters that induce more variability
+# and hopefully less bias
+boot_cart_maxit_cp_min3 <- bootstrap_boys %>%
+  future_map(function(x) {
+    x %>% mice(m = 5, 
+               maxit = 1,
+               method = cart,
+               minbucket = 3,
+               cp = 1e-08,
+               predictorMatrix = pred,
[…]

### 2020-07-27 mice_synthesizing/functions.R

@@ -19,7 +19,7 @@ pool.syn <- function(mira) {
               ubar    = mean(std.error^2),
               var_u   = (1 + 1/m) * bm - ubar,
               var     = if_else(var_u > 0, var_u, ubar),
-              df      = max(1, (m - 1) * (1 - ubar / ((1 + 1/m) * bm))^2),
+              df      = max(1, (m - 1) * (1 - ubar / (bm + bm/m))^2),
               lower   = est - qt(.975, df) * sqrt(var),
               upper   = est + qt(.975, df) * sqrt(var), .groups = 'drop')
   pooled

### 2020-08-01 mice_synthesizing/formulas.Rmd
Start with formula file

---
title: "Formulas"
authors: 
- Thom Volker
- Utrecht University
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Missing data

Inferences for an unknown scalar parameter $Q$, say, a regression coefficient, are based on a point estimate $q$, a variance estimate $u$, and a normal or Student's $t$ reference distribution. For analysis of the imputed datasets, let $q^{(i)}$ and $u^{(i)}$ for $i = 1, 2, \dots, m$ be the point and variance estimates achieved from each of the $m$ completed datasets. To get a final estimate over all imputations, these estimates have to be combined using the combining rules described by Rubin (1978). The following quantities are needed for inferences for scalar $Q$:
$$
\begin{aligned}
\bar{q}_m &= \sum_{i = 1}^m \frac{q^{(i)}}{m}, \\
b_m &= \sum_{i = 1}^m \frac{(q^{(i)} - \bar{q}_m)^2}{m-1}, \\
\bar{u}_m &= \sum_{i = 1}^m \frac{u^{(i)}}{m}.
\end{aligned}
$$
The analyst then can use $\bar{q}_m$ to estimate $Q$ and
$$
T_m = \bar{u}_m + (1 + \frac{1}{m}) b_m
$$
to estimate the variance of $\bar{q}_m$. Then, $\bar{u}_m$ can be regarded as the "within-imputation" variance, and $b_m$ as the "between-imputation" variance. The factor $(1 + \frac{1}{m})$ reflects the fact that only a finite number of completed-data estimates $q^{(i)}$ are averaged together to obtain the final point estimate.

The quantity $r = (1 + \frac{1}{m}) \frac{b_m}{T_m}$ estimates the fraction of information about $Q$ that is missing due to nonresponse. Inferences from multiply imputed data are based on $\bar{q}_m$, $T_m$, and a Student's $t$ reference distribution. Rubin and Schenker (1986) provide the approximate value $\nu_{RS} = \frac{m - 1}{r^2}$ for the degrees of freedom of the $t$ distribution under the assumption that with complete data a normal reference distribution would have been appropriate. Barnard and Rubin (1999) relax the assumption of Rubin and Schenker (1986) to allow for a $t$ reference distribution with complete data and suggest the value $\nu_{BR} = (\frac{1}{\nu_{RS}} + \frac{1}{\hat{\nu}_{obs}})^{-1}$ for the degrees of freedom in the multiple imputation analysis, where $\hat{\nu}_{obs} = \frac{(1- r)(\nu_{com})(\nu_{com} + 1)}{\nu_{com} + 1}$ and $\nu_{com}$ denotes the complete-data degrees of freedom.

### 2020-08-04 mice_synthesizing/formulas.Rmd
Synthetic data formulas from Drechsler

@@
 Barnard and Rubin (1999) relax the assumption of Rubin and Schenker (1986) to allow for a $t$ reference distribution with complete data and suggest the value $\nu_{BR} = (\frac{1}{\nu_{RS}} + \frac{1}{\hat{\nu}_{obs}})^{-1}$ for the degrees of freedom in the multiple imputation analysis, where $\hat{\nu}_{obs} = \frac{(1- r)(\nu_{com})(\nu_{com} + 1)}{\nu_{com} + 1}$ and $\nu_{com}$ denotes the complete-data degrees of freedom.
+
+---
+
+# Fully synthetic datasets
+
+We again have scalar population parameter $Q$, with $q^{(i)}$ and $u^{(i)}$ as it's estimates from each of the $m$ synthetic datasets.
+The following quantities are needed for inferences for scalar $Q$:
+
+$$
+\begin{aligned}
+\bar{q}_m &= \sum_{i=1}^m \frac{q^{(i)}}{m}, \\
+b_m &= \sum_{i=1}^m \frac{(q^{(i)} - \bar{q}_m)^2}{m-1}, \\
+\bar{u}_m &= \sum_{i=1}^m \frac{u^{(i)}}{m}.
+\end{aligned}
+$$
+
+The analyst then can use $\bar{q}_m$ to estimate $Q$ and 
+$$
+T_f = (1 + \frac{1}{m})b_m - \bar{u}_m
+$$
+to estimate the variance of $\bar{q}_m$.
+The difference in this variance estimate compared with the variance estimate for standard multiple imputation is due to the additional sampling from the synthetic units for fully synthetic datasets.
+Hence, the variance $b_m$ between the datasets already reflects the variance within each imputation.
+When $n$ is large, inferences for scalar $Q$ can be based on $t$ distributions with degrees of freedom
+$$
+\nu_f = (m - 1) \Bigg{(}1 - \frac{\bar{u}_m}{(1 + \frac{1}{m})b_m}\Bigg{)}^2.
+$$
+Derivations of these methods are presented in Raghunathan et al.
+(2003).
+A disadvantage of this variance estimate is that it can become negative.
+For that reason, Reiter (2002) suggests a slightly modified variance estimator that is always positive $T_f^{*} = \text{max}(0, T_f) + \delta \Big{(}\frac{n_{syn}}{n}\bar{u}_m \Big{)}$, where $\delta = 1$ if $T_f < 0$ and $\delta = 0$ otherwise.
+
+---
+
+# Partially synthetic datasets
+
+Following Reiter (2003, 2004), let $Z_j = 1$ if unit $j$ is selected to have any of its observed data replaced, and let $Z_j = 0$ otherwise.
+Let $Z = (Z_1, \dots, Z_s)$, where $s$ is the number of records in the observed data.
+Let $Y = (Y_{rep}, Y_{nrep})$ be the data collected in the original survey, where $Y_{rep}$ includes all values to be replaced with multiple imputations and $Y_{nrep}$ includes all values not replaced with imputations.
+Let $Y_{rep}^{(i)}$ be the replacement values for $Y_{rep}$ in synthetic dataset $i$.
+Each $Y_{rep}^{(i)}$ is generated by simulating values from the posterior predictive distribution $f(Y_{rep}^{(i)} | Y, Z)$, or some close approximation to the distribution such as those of Raghunathan et al.
+(2001).
+The agency repeats the process $m$ times, creating $D^{(i)} = (Y_{nrep}, Y_{rep}^{(i)})$ for $i = 1, \dots, m$, and releases $\textbf{D} = \{D^{(1)}, \dots, D^{(m)}\}$ to the public.
+
+To get valid inferences, secondary data users can use the combining rules presented by Reiter (2003).
+For scalar $Q$, with $q^{(i)}$ and $u^{(i)}$ the point estimate and the corresponding variance estimate in synthetic dataset $D^{(i)}$ for $i = 1, \dots, m$, the following quantities are needed for inferences:
+
+$$
+\begin{aligned}
+\bar{q}_m &= \sum_{i=1}^m \frac{q^{(i)}}{m}, \\
+b_m &= \sum_{i=1}^m \frac{(q^{(i)} - \bar{q}_m)}{m-1}, \\
+\bar{u}_m &= \sum_{i=1}^m \frac{u^{(i)}}{m}.
+\end{aligned}
+$$
+
+The analyst can use $\bar{q}_m$ to estimate $Q$ and 
+$$
+T_p = \frac{b_m}{m} + \bar{u}_m
+$$
+to estimate the variance of $\bar{q}_m$.
+Then, $\frac{b_m}{m}$ is the correction factor for the additional variance due to using a finite number of imputations.
+However, the additional $b_m$ necessary in the missing-data context is not necessary here, since $\bar{u}_m$ already captures the variance of $Q$ given the observed data.
+This is different in the missing data case, where $\bar{u}_m$ is the variance of $Q$ given the completed data, and $\bar{u} + b_m$ is the variance of $Q$ given the observed data.
+When $n$ is large, inferences for scalar $Q$ can be based on $t$ distributions with degrees of freedom $\nu_p = (m-1) \Big{(}1 + \frac{\bar{u}_m \cdot m}{b_m}\Big{)}^2.$
+
+---
+
+# Nonresponse and partially synthetic data
+
+Since the generation of synthetic datasets is based on the ideas of multiple imputation, it is reasonable to use the approach to impute missing values and generate synthetic values simultaneously.
+At first glance, it seems logical to impute missing values and generate synthetic values in one step using the same model as for the originally observed values.
+However, as Reiter (2004) points out, this can lead to biased imputations of only a subset of the data should be replaced with synthetic values, but the imputation model for the missing values is based on the entire dataset.
+To allow for different models, Reiter (2004) suggests imputation in two stages.
+In the first stage, all missing values are imputed $m$ times using the standard multiple-imputation approach for nonresponse.
+In the second stage, all values that need to be replaced are synthesized $r$ times in every first-stage nest, leading to a total of $M = m \cdot r$ datasets that are released to the public.
+
+Again, let $Q$ be an estimand, and suppose that, given the original data, the analyst estimates $Q$ with some point estimator $q$ and the variance of $q$ with some estimator $u$.
+Let $q^{(i,j)}$ and $u^{(i,j)}$ be the values of $q$ and $u$ in synthetic dataset $D^{(i,j)}$ for $i = 1, \dots, m$ and $j = 1, \dots, r$.
+The analyst computes $q^{(i,j)}$ and $u^{(i,j)}$ by acting as if each $D^{(i,j)}$ is the genuine data.
+The following quantities are needed for inferences for scalar $Q$:
+
+$$
+\begin{aligned}
+\bar{q}_M &= \sum_{i=1}^m \sum_{j=1}^r \frac{q^{(i,j)}}{m \cdot r} = \sum_{i=1}^m \frac{\bar{q}^{(i)}}{m}, \\
+\bar{b}_M &= \sum_{i=1}^m \sum_{j=1}^r \frac{(q^{(i,j)} - \bar{q}^{(i)})^2}{m(r-1)} = \sum_{i=1}^m \frac{b^{(i)}}{m}, \\
+B_M &= \sum_{i=1}^m \frac{(\bar{q}^{(i)}) - \bar{q}_M}{m-1}, \\
+\bar{u}_M = \sum_{i=1}^m \sum_{j=1}^r \frac{u^{i,j}}{m \cdot r}.
+\end{aligned}
+$$
+
+The analyst then can use $\bar{q}_M$ to estimate $Q$ and
+$$
+T_P = (1 + \frac{1}{m}) B_M - \frac{\bar{b}_M}{r} + \bar{u}_M
+$$
+to estimate the variance of $\bar{q}_M$. When $n$ is large, inferences for scalar $Q$ can be based on $t$ distributions with degrees of freedom 
+$$
+\nu_P = \Bigg{(}\frac{((1 + \frac{1}{m})B_M)^2}{(m-1)T_M^2} + \frac{(\frac{\bar{b}_M}{r})^2}{m(r-1)T_M^2} \Bigg{)}^{-1}.
+$$
+
+Similar to the variance of the estimate for fully synthetic datasets, $T_P$ can become negative since $\frac{\bar{b}_M}{r}$ is substracted.
+In this case, Reiter (2008b) suggests using the conservative variance estimator $T_P^{adj} = (1 = \frac{1}{m})B_M + \bar{u}_M$.
+This estimator is equivalent to the variance estimator for multiple imputation for missing data.
+Consequently, the degrees of freedom are given by
+$$
+\nu_P^{adj} = (m - 1) \Bigg{(}1 + \frac{m \bar{u}_M)}{(m+1)B_M} \Bigg{)}^2.
+$$
+Generally, negative variances can be avoided by increasing $m$ and $r$.
+
+---
+
+END OF DOCUMENT

### 2020-08-06 mice_synthesizing/1.a Synthesize_Mice_Replace_All.R
Passive imputation bmi

@@ -39,6 +39,7 @@ def['reg'] <- "polyreg"
 # cart method, all variables are imputed by means of cart
 cart <- rep("cart", ncol(truth))
 names(cart) <- colnames(truth)
+cart['bmi'] <- def['bmi']
 
 # alter the predictor matrix such that imputations for bmi do not flow
 # back into the predictions for wgt and hgt

### 2020-08-06 mice_synthesizing/functions.R
Make sure a regular list, instead of a mira object can be handled as well.

@@ -7,7 +7,12 @@
 
 pool.syn <- function(mira) {
   
-  fitlist <- mira %$% analyses
+  if(class(mira) == "mira") {
+    fitlist <- mira %$% analyses
+  }
+  else {
+    fitlist <- mira
+    }
   
   m <- length(fitlist)
   

### 2020-08-07 mice_synthesizing/functions.R
Bug fix - extract only the first element from class(mira)

@@ -7,7 +7,7 @@
 
 pool.syn <- function(mira) {
   
-  if(class(mira) == "mira") {
+  if(class(mira)[1] == "mira") {
     fitlist <- mira %$% analyses
   }
   else {
@@ -50,5 +50,5 @@ ci_cov <- function(pooled, true_fit) {
               "Lower"    = mean(lower),
               "Upper"    = mean(upper),
               "CIW"      = mean(upper - lower),
-              "Coverage" = mean(cover))
+              "Coverage" = mean(cover), .groups = "drop")
 }

### 2020-08-07 mice_synthesizing/Mice_Synthesizing.Rmd
Added within and between variance over synthesizing methods

@@
 ```{r, message = F}
-synthetic_results <- boot_cart %>%
-  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
-  map_dfr(pool.syn) %T>% 
-  assign("boot_syn", ., envir = globalenv()) %>%
-  ci_cov(truemodel) %>%
-  kable(digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
-
-norm_results <- boot_cart %>%
-  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
-  map_dfr(pool.syn) %>%
-  mutate(df = NA,
-         lower = est - qnorm(.975) * sqrt(var),
-         upper = est + qnorm(.975) * sqrt(var)) %>%
-  ci_cov(truemodel) %>%
-  kable(digits = 3, caption = "Normal CI approximation") %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
-
 true_results <- bootstrap_boys %>%
@@
   kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+synthetic_results <- boot_cart %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool.syn) %T>% 
+  assign("boot_syn", ., envir = globalenv()) %>%
+  ci_cov(truemodel) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+norm_results <- boot_cart %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool.syn) %>%
+  mutate(df = NA,
+         lower = est - qnorm(.975) * sqrt(var),
+         upper = est + qnorm(.975) * sqrt(var)) %>%
+  ci_cov(truemodel) %>%
+  kable(digits = 3, caption = "Normal CI approximation") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
@@
 
+```{r}
+cart_default <- boot_cart %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool.syn) %>%
+  group_by(term) %>%
+  summarise(Within = mean(ubar), Between = mean(bm), Total = mean(var))
+
+cart_adj <- boot_cart_maxit_cp_min3 %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool.syn) %>%
+  group_by(term) %>%
+  summarise(Within = mean(ubar), Between = mean(bm), Total = mean(var))
+
+cart_default
+
+cart_adj
+```
+
 # References

### 2020-08-07 mice_synthesizing/1.b Synthesize_partitioned_data_mice.R
Partitioned synthetic datasets with mice

@@ -1,11 +1,61 @@
 
+library(mice) # imputations
+library(tidyverse) # tidy data
+library(modelr) # bootstrap
+library(magrittr) # pipe
+library(furrr) # parallel mapping
 
+set.seed(123) # seed for reproducibility
+
+#create one complete dataset that allow us to work without missings
+truth <- boys %>% mice(seed = 123, m = 1, print = FALSE) %>% complete()
+
+# shorten the complete lm model, since we want to use the same model anyhow
+model <- function(data) lm(wgt ~ age + hgt, data)
+
+# run this model
+truemodel <- truth %>% model
+
+# extract the coefficients
+coefs <- coef(truemodel)
+
+# parallel processing to increase speed
+plan(multisession)
+
+# number of iterations
+nsim <- 500
+
+# cart method, all variables are imputed by means of cart
+cart <- rep("cart", ncol(truth))
+names(cart) <- colnames(truth)
+cart['bmi'] <- "~I(wgt / (hgt/100)^2)"
+
+pred <- make.predictorMatrix(truth)
+pred[c("wgt", "hgt"), "bmi"] <- 0
+
+boot_boys <- truth %>% bootstrap(nsim) %$% strap %>% map(as.data.frame)
 
 n.parts <- 5
 
 parts <- rep(1/n.parts, n.parts)
 names(parts) <- paste0("P", 1:n.parts)
 
-boot_part <- bootstrap_boys %>%
-  future_map(function(x) resample_partition(x, parts) %>%
-               map(function(y) as.data.frame(y)))
+boot_parts <- boot_boys %>%
+  future_map(function(x) {
+    resample_partition(x, parts) %>%
+      map(function(y) {
+        as.data.frame(y) %>%
+          mice(m = 5, 
+               maxit = 1,
+               method = cart,
+               minbucket = 3,
+               cp = 1e-08,
+               predictorMatrix = pred,
+               where = matrix(1, nrow(.), ncol(.)),
+               print = F) %>% 
+          mice::complete(., action = "long")
+          }
+        ) %>% bind_rows %>%
+      plyr::dlply(~.imp)
+  }, .options = future_options(seed = as.integer(123)), .progress = T)
+

### 2020-08-07 mice_synthesizing/mice_synthesizing_partitioned_data.Rmd
Simulations with partitioned data

---
title: "Mice synthesizing with partitioned data"
author:
- Thom Volker
- Utrecht University
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
bibliography: federated_imp.bib
csl: "/Users/thomvolker/Documents/styles/apa-6th-edition.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
thomcache <- TRUE; thomlazy <- FALSE #obviously ;)
library(tidyverse)
library(magrittr)
library(knitr)
library(kableExtra)
library(mice)
library(ggplot2)
```

# Introduction

As can be seen in the previous R Markdown file (Synthesizing by means of mice), it is possible to create fully synthetic data by means of mice. In the current document, we take this approach one step further, by trying to synthesize partitioned data. Therefore, we once again create 500 bootstrap samples, that are partitioned into $r = 5$ subsets, and then every subset is synthesized, which results in $m = 5$ synthetic versions of every $r = 5$ subset of the bootstrap sample, resulting in $r \cdot m$ separate data sets. Then, we create $m = 5$ completed datasets, by rowbinding all $r = 5$ subsets, which results in $m = 5$ datasets of the same dimension as the original data. These datasets are analysed by means of a linear regression model, and pooled by means of the fully synthetic data rules, as proposed by Raghunathan et al. (2003).

The data is synthesized by means of the data generating approach that seemed most promising in the previous `R Markdown` file. Thus, `cart` is used as a synthesizing method for all variables, except for `bmi`, which is synthesized passively, through it's relation with `wgt` and `hgt`, that is, `bmi = wgt / (hgt/100)^2`. Furthermore, the parameter `minbucket`, which is the minimum number of observations in any terminal node, is set to 1, the parameter `cp`, which is the complexity parameter now equals `1e-08`, and the number of iterations `maxit = 1`. With this method, we introduced somewhat more variance within every dataset, while the between-imputation variance decreases somewhat

```{r, include = F, cache = thomcache, cache.lazy=thomlazy}
source("1.b Synthesize_partitioned_data_mice.R")
source("functions.R")
```

---

# Results

```{r, eval = F}
boot_boys <- truth %>% bootstrap(nsim) %$% strap %>% map(as.data.frame)

n.parts <- 5

parts <- rep(1/n.parts, n.parts)
names(parts) <- paste0("P", 1:n.parts)

boot_parts <- boot_boys %>%
  future_map(function(x) {
    resample_partition(x, parts) %>%
      map(function(y) {
        as.data.frame(y) %>%
          mice(m = 5, 
               maxit = 1,
               method = cart,
               minbucket = 3,
               cp = 1e-08,
               predictorMatrix = pred,
               where = matrix(1, nrow(.), ncol(.)),
               print = F) %>% 
          mice::complete(., action = "long")
          }
        ) %>% bind_rows %>%
      plyr::dlply(~.imp)
  }, .options = future_options(seed = as.integer(123)), .progress = T)
```

This approach yields `nsim` lists of length $m = 5$, containing the already binded $r = 5$ partitions of the data. Thus, every single list contains $m = 5$ complete synthetic datasets. These can be analysed by means of the `pool.syn` function, and these results can be summarised by means of the `ci_cov` function.

```{r}
boot_parts %>%
  map_dfr(function(x) {
    x %>% map(function(y) y %$% lm(wgt ~ age + hgt)) %>%
      pool.syn
    }) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

```

### 2020-08-08 mice_synthesizing/Mice_Synthesizing.Rmd
Update with passive imputations for bmi

@@
   group_by(term) %>%
-  summarise(Within = mean(ubar), Between = mean(bm), Total = mean(var))
+  summarise(Within = mean(ubar), 
+            Between = mean(bm), 
+            Total = mean(var),
+            .groups = 'drop')
 
@@
   group_by(term) %>%
-  summarise(Within = mean(ubar), Between = mean(bm), Total = mean(var))
+  summarise(Within = mean(ubar), 
+            Between = mean(bm), 
+            Total = mean(var),
+            .groups = 'drop')
 
-cart_default
-
-cart_adj
+bind_rows("Cart default" = cart_default,
+          "Cart adjusted settings" = cart_adj, .id = "Method") %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
 ```

### 2020-08-08 mice_synthesizing/mice_synthesizing_partitioned_data.Rmd
Added maxit = 5

@@
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```
 
+Additionally, since I'm not sure whether or not it is allowed to set the number of iterations to 1, I additionally performed the same analysis with `maxit = 5`, the `mice` default for imputations.
+
+```{r, eval = F}
+boot_boys <- truth %>% bootstrap(nsim) %$% strap %>% map(as.data.frame)
+
+n.parts <- 5
+
+parts <- rep(1/n.parts, n.parts)
+names(parts) <- paste0("P", 1:n.parts)
+
+boot_parts_5 <- boot_boys %>%
+  future_map(function(x) {
+    resample_partition(x, parts) %>%
+      map(function(y) {
+        as.data.frame(y) %>%
+          mice(m = 5, 
+               maxit = 5,
+               method = cart,
+               minbucket = 3,
+               cp = 1e-08,
+               predictorMatrix = pred,
+               where = matrix(1, nrow(.), ncol(.)),
+               print = F) %>% 
+          mice::complete(., action = "long")
+      }
+      ) %>% bind_rows %>%
+      plyr::dlply(~.imp)
+  }, .options = future_options(seed = as.integer(123)), .progress = T)
 ```
+
+This approach yields the following results.
+
+```{r}
+boot_parts_5 %>%
+  map_dfr(function(x) {
+    x %>% map(function(y) y %$% lm(wgt ~ age + hgt)) %>%
+      pool.syn
+    }) %>%
+  ci_cov(truemodel) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```

### 2020-08-08 mice_synthesizing/1.b Synthesize_partitioned_data_mice.R

@@ -59,3 +59,21 @@ boot_parts <- boot_boys %>%
       plyr::dlply(~.imp)
   }, .options = future_options(seed = as.integer(123)), .progress = T)
 
+boot_parts_5 <- boot_boys %>%
+  future_map(function(x) {
+    resample_partition(x, parts) %>%
+      map(function(y) {
+        as.data.frame(y) %>%
+          mice(m = 5, 
+               maxit = 5,
+               method = cart,
+               minbucket = 3,
+               cp = 1e-08,
+               predictorMatrix = pred,
+               where = matrix(1, nrow(.), ncol(.)),
+               print = F) %>% 
+          mice::complete(., action = "long")
+      }
+      ) %>% bind_rows %>%
+      plyr::dlply(~.imp)
+  }, .options = future_options(seed = as.integer(123)), .progress = T)

### 2020-08-08 mice_synthesizing/functions.R
Adjusted degrees of freedom.

@@ -30,6 +30,31 @@ pool.syn <- function(mira) {
   pooled
 }
 
+pool2.syn <- function(mira) {
+  
+  if(class(mira)[1] == "mira") {
+    fitlist <- mira %$% analyses
+  }
+  else {
+    fitlist <- mira
+  }
+  
+  m <- length(fitlist)
+  
+  pooled <- fitlist %>% 
+    map_dfr(broom::tidy) %>%
+    group_by(term) %>%
+    summarise(est     = mean(estimate),
+              bm      = sum((estimate - est)^2) / (m - 1),
+              ubar    = mean(std.error^2),
+              var_u   = (1 + 1/m) * bm - ubar,
+              var     = if_else(var_u > 0, var_u, ubar),
+              df      = max(m - 1, (m - 1) * (1 - ubar / (bm + bm/m))^2),
+              lower   = est - qt(.975, df) * sqrt(var),
+              upper   = est + qt(.975, df) * sqrt(var), .groups = 'drop')
+  pooled
+}
+
 ci_cov <- function(pooled, true_fit) {
   
   coefs <- coef(true_fit)

### 2020-08-08 mice_synthesizing/mice_synthesizing_partitioned_data.Rmd
Adjusted degrees of freedom for partitioned data.

@@
 ```
+
+---
+
+# Adjusted degrees of freedom
+
+Alternatively, we can alter the minimum value for the degrees of freedom to $\text{max}(m - 1, \nu)$, as is done in Reiter and Drechsler (2010) as well.
+
+This approach yields the following results with `maxit` set to 1.
+
+```{r, include = F}
+source("functions.R")
+```
+
+```{r}
+boot_parts %>%
+  map_dfr(function(x) {
+    x %>% map(function(y) y %$% lm(wgt ~ age + hgt)) %>%
+      pool2.syn
+    }) %>%
+  ci_cov(truemodel) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```
+
+And the following results when we fix `maxit` at five.
+
+```{r}
+boot_parts_5 %>%
+  map_dfr(function(x) {
+    x %>% map(function(y) y %$% lm(wgt ~ age + hgt)) %>%
+      pool2.syn
+    }) %>%
+  ci_cov(truemodel) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```

### 2020-08-08 mice_synthesizing/1.a Synthesize_Mice_Replace_All.R
Added maxit = 5 to examples.

@@ -115,3 +115,16 @@ boot_cart_maxit_cp_min3 <- bootstrap_boys %>%
                print = F)
 }, .options = future_options(seed = as.integer(123)), .progress = TRUE)
 
+
+boot_cart_cp_min3 <- bootstrap_boys %>%
+  future_map(function(x) {
+    x %>% mice(m = 5, 
+               maxit = 5,
+               method = cart,
+               minbucket = 3,
+               cp = 1e-08,
+               predictorMatrix = pred,
+               where = matrix(TRUE, nrow(truth), ncol(truth)),
+               print = F)
+  }, .options = future_options(seed = as.integer(123)), .progress = TRUE)
+

### 2020-08-08 mice_synthesizing/1.a Synthesize_Mice_Replace_All.R
Added maxit = 5 example.

@@ -23,7 +23,7 @@ coefs <- coef(truemodel)
 plan(multisession)
 
 # number of iterations
-nsim <- 500
+nsim <- 5
 
 # default method - pmm for all continuous predictors
 def <- rep("pmm", ncol(truth))

### 2020-08-09 mice_synthesizing/Mice_Synthesizing.Rmd
Adjusted degrees of freedom - one new night of running simulations.

@@
 
-It can be seen that the bias indeed decreases, while the standard error of the estimates increases.
-This is due to the fact that the within-imputation variance increases, while the between-imputation variance decreases somewhat.
-When we use the same approach to estimate the bootstrapped boys data, we get the following results.
+Additionally, the same approach is used to synthesize the `r nsim` bootstrapped samples from the completed boys data.
 
@@
 ```
+
+However, I'm not sure whether it is sensible to set the number of iterations to `maxit = 1`.
+Therefore, I additionally included an example that shows the same approach, that is, with the complexity parameter `cp = 1e-08` and the parameter `minbucket = 3`, but with maximum number of iterations fixed at `maxit = 5`.
+
+```{r}
+boot_cart_cp_min3 %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool.syn) %>%
+  ci_cov(., truemodel) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```
+
+It can be seen that the bias indeed decreases, while the standard error of the estimates increases.
+This is due to the fact that the within-imputation variance increases, while the between-imputation variance decreases somewhat.
 
@@
 
-cart_adj <- boot_cart_maxit_cp_min3 %>%
+cart_adj_maxit <- boot_cart_maxit_cp_min3 %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool.syn) %>%
+  group_by(term) %>%
+  summarise(Within = mean(ubar), 
+            Between = mean(bm), 
+            Total = mean(var),
+            .groups = 'drop')
+
+cart_adj <- boot_cart_cp_min3 %>%
   map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
@@
 bind_rows("Cart default" = cart_default,
+          "Cart with adjusted settings and maxit = 1" = cart_adj_maxit,
           "Cart adjusted settings" = cart_adj, .id = "Method") %>%
@@
 
+---
+
+# Adjusted degrees of freedom
+
+Next to the analyses displayed previously, I adjusted the degrees of freedom to $\text{max}(m - 1, \nu)$, as is done in Reiter and Drechsler (2010).
+This yields the following results for the initial analyses, that is, bootstrapping with the mice default settings, but with the method set to `cart`.
+Note that this concerns `r nsim` bootstrap samples from the complete data.
+
+```{r}
+boot_cart %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool2.syn) %T>% 
+  assign("boot_syn", ., envir = globalenv()) %>%
+  ci_cov(truemodel) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```
+
+Additionally, the results can be computed for the data with the smaller bias settings. That is, setting `maxit = 1`, `cp = 1e-08` and `minbucket = 3`.
+
+```{r}
+boot_cart_maxit_cp_min3 %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool2.syn) %>%
+  ci_cov(., truemodel) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```
+
+And, once again, the same analysis as the previous one, but with `maxit = 5`.
+
+```{r}
+boot_cart_cp_min3 %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool2.syn) %>%
+  ci_cov(., truemodel) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```
+
 # References

### 2020-08-09 mice_synthesizing/1.a Synthesize_Mice_Replace_All.R

@@ -23,7 +23,7 @@ coefs <- coef(truemodel)
 plan(multisession)
 
 # number of iterations
-nsim <- 5
+nsim <- 500
 
 # default method - pmm for all continuous predictors
 def <- rep("pmm", ncol(truth))

### 2020-08-09 mice_synthesizing/data_checks.Rmd

---
title: "Synthetic data (confidentiality) checks"
authors: 
- Thom Volker
- Utrecht University
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
thomcache <- TRUE
```

# Introduction

To see how confidential the data imputed by mice, it is a straightforward approach to see how many observations in the synthetic data are duplicates from the original data. This is done by means of creating one completed `boys` dataset, generating 100 imputed versions of this dataset, and see how often there are duplicated observations in any of the 100 synthetic versions of the data.

```{r, results = F, message = F, warning=F}
library(mice) # imputations
library(tidyverse) # (d)plyr
library(magrittr) # pipes
```

First, load the required packages. Then, we set the method for imputing the data (with passive imputations for `bmi`) and make sure that imputations for `bmi` do not flow back into the predictions of `hgt` and `wgt`. Then, we impute the boys dataset containing missing values once, so that we have a fully observed dataset that can be used for creating synthetic versions.

```{r}
meth <- make.method(mice::boys)
meth['bmi'] <- "~I(wgt / (hgt/100)^2)"
pred <- make.predictorMatrix(boys)
pred[c("wgt", "hgt"), "bmi"] <- 0

data <- mice::boys %>% 
  mice(m = 1, method = meth, predictorMatrix = pred, print = FALSE, seed = 123) %>% 
  complete()
```
Now we have a complete dataset, we can overimpute the complete dataset, so that we have synthetic data. First, we set the synthesizing method to `cart`. Then, we use mice to generate 100 synthetic versions of the completed dataset.

```{r, cache = thomcache}
cart <- meth; cart[!names(meth) %in% 'bmi'] <- "cart"

syns <- data %>% 
  mice(m = 100, 
       method = cart, 
       predictorMatrix = pred, 
       where = matrix(TRUE, nrow(data), ncol(data)),
       print = FALSE,
       seed = 123)
```

Now we have 100 synthetic versions of the same dataset, we can create 100 completed datasets.

```{r}
completed <- complete(syns, action = "all")
```

Now we have 100 complete synthetic datasets, we can inspect the number of duplicate cases in every synthetic dataset with regard to the original dataset.

```{r}
duplicate_obs <- map(completed, function(x) bind_rows(data, x) %>% duplicated)

duplicate_obs %>% map_dbl(sum) %>% sum # total number of duplicated rows over all 100 synthetic datasets
```

It appears that in all 100 synthetic versions of the data, there is not a single observation that is an exact copy of the actually observed observations. Now, let's find out if the synthetic data resembles the actually observed data (univariately). That is, we compare the distributions of the variables in the observed and the synthetic data.

```{r, dpi = 300, fig.fullwidth = TRUE, message = F}
completed %>%
  map_dfr(function(x) x) %>%
  bind_rows(., data, .id = "Imputed") %>%
  mutate(Imputed = as.numeric(Imputed)) %>%
  select_if(is.numeric) %>%
  pivot_longer(cols = -"Imputed",
               names_to = c("Variable")) %>%
  mutate(Imputed = recode(Imputed, `1` = "Synthetic data", `2` = "Observed data")) %>%
  ggplot(., mapping = aes(x = value, fill = Imputed)) +
  geom_histogram(aes(y = ..density..), position = "dodge2", ) +
  facet_wrap(~ Variable, nrow = 3, ncol = 2, scales = "free") +
  theme_classic() +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

```{r, dpi = 300, fig.fullwidth = TRUE}
completed %>%
  map_dfr(function(x) x) %>%
  bind_rows(., data, .id = "Imputed") %>%
  select_if(negate(is.numeric)) %>%
  map_dfr(function(x) as.character(x)) %>%
  pivot_longer(cols = -"Imputed",
               names_to = c("Variable")) %>%
  mutate(Imputed = recode(Imputed, `1` = "Synthetic data", `2` = "Observed data")) %>%
  ggplot(., mapping = aes(x = value, fill = Imputed, group = Imputed)) +
  geom_bar(aes(y = ..prop..), position = "dodge2") +
  facet_wrap(~ Variable, nrow = 3, ncol = 2, scales = "free") +
  theme_classic() +
  scale_fill_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

Over all imputed datasets, the synthetic data are univariately very much alike the observed data. Both the histograms and barplots shows that the relative frequencies of the values for the continuous variables or the categories for the categorical variables are highly similar.

### 2020-08-09 mice_synthesizing/functions.R
partially synthetic data pool function

@@ -55,6 +55,30 @@ pool2.syn <- function(mira) {
   pooled
 }
 
+pool3.syn <- function(mira) {
+  
+  if(class(mira)[1] == "mira") {
+    fitlist <- mira %$% analyses
+  }
+  else {
+    fitlist <- mira
+  }
+  
+  m <- length(fitlist)
+  
+  pooled <- fitlist %>% 
+    map_dfr(broom::tidy) %>%
+    group_by(term) %>%
+    summarise(est     = mean(estimate),
+              bm      = sum((estimate - est)^2) / (m - 1),
+              ubar    = mean(std.error^2),
+              var     = ubar + bm/m,
+              df      = (m - 1) * (1 + (ubar * m)/bm),
+              lower   = est - qt(.975, df) * sqrt(var),
+              upper   = est + qt(.975, df) * sqrt(var), .groups = 'drop')
+  pooled
+}
+
 ci_cov <- function(pooled, true_fit) {
   
   coefs <- coef(true_fit)

### 2020-08-09 mice_synthesizing/synthesizing_partially_synthetic_data_rules.Rmd
Results with partially synthetic data pooling functions.

---
title: "Synthesizing by means of mice with partially synthetic data rules"
author:
- Thom Volker
- Utrecht University
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
bibliography: federated_imp.bib
csl: "/Users/thomvolker/Documents/styles/apa-6th-edition.csl"
---

# Introduction

Load the required packages.

```{r, results=FALSE, message=FALSE, warning=FALSE}
source("functions.R")
library(mice)
library(magrittr)
library(tidyverse)
library(knitr)
library(kableExtra)
library(ggplot2)
```

```{r, include = FALSE}
load("~/Documents/Federated_imputation/mice_synthesizing/Mice_Synthesizing_cache/html/unnamed-chunk-1_3934488913d24a2b94b74c88c35323d4.RData")
```

Since using `mice`, we basically overimpute the already observed data. This corresponds to the method of partially synthetic data, although we overimpute every single value. Nevertheless, it is worthwhile to check the results when we use the partially synthetic data rules, since the pooling rules to combine this with missing data already exist. Therefore, we see how this method performs on the bootstrapped samples from the boys data.

We can use the same data as in the previous file, but we need to use a new pooling function, with a different variance calculation, namely
$$
T_p = \bar{u}_m + \frac{b_m}{m},
$$
with corresponding degrees of freedom
$$
\begin{aligned}
\nu_p &= (m - 1)(1 + \frac{\bar{u}_m}{\frac{b_m}{m}}) \\
&= (m - 1)(1 + \frac{m \cdot \bar{u}_m}{b_m}).
\end{aligned}
$$

When we use the default `cart` approach in mice, this yields the following results.

# Default CART

```{r, message = FALSE}
true_results <- bootstrap_boys %>%
  map(~ lm(wgt ~ age + hgt, .x)) %>%
  map_dfr(~ broom::tidy(.x, conf.int = TRUE)) %>%
  mutate(true_coef = rep(coef(truemodel), nsim),
         true_se   = rep(sqrt(diag(vcov(truemodel))), nsim),
         cover     = conf.low < true_coef & true_coef < conf.high) %T>% 
  assign("boot_true", ., envir = globalenv()) %>%
  group_by(term) %>%
  summarise("True Est" = unique(true_coef),
            "Boot Est"  = mean(estimate),
            "Bias"     = mean(estimate - true_coef),
            "True SE"  = unique(true_se),
            "Boot SE"   = mean(std.error),
            "DF"       = 745,
            "Lower"    = mean(conf.low),
            "Upper"    = mean(conf.high),
            "CIW"      = mean(conf.high - conf.low),
            "Coverage" = mean(cover)) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

synthetic_results <- boot_cart %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool3.syn) %T>% 
  assign("boot_syn", ., envir = globalenv()) %>%
  ci_cov(truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

```{r}
true_results
synthetic_results
```

# Adjusted CART

Just as in the previous file, we increase the within-imputation variance somewhat, which results in a smaller bias, and therefore, hopefully, more accurate results.

```{r}
boot_cart_maxit_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

boot_cart_cp_min3 %>%
  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., truemodel) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### 2020-08-16 mice_synthesizing/functions.R
Annotate functions.

@@ -5,66 +5,69 @@
 ## this function can be used to analyse the synthetic data by means of a linear 
 ## regression model, and to pool the results.
 
+# FULLY SYNTHETIC POOL FUNCTION
 pool.syn <- function(mira) {
   
-  if(class(mira)[1] == "mira") {
-    fitlist <- mira %$% analyses
+  if(class(mira)[1] == "mira") { # if the input object is of class mira
+    fitlist <- mira %$% analyses # extract the analyses from the mira object
   }
-  else {
+  else {                         # and otherwise, just take the input list
     fitlist <- mira
     }
   
-  m <- length(fitlist)
+  m <- length(fitlist)           # number of imputations
   
   pooled <- fitlist %>% 
-    map_dfr(broom::tidy) %>%
-    group_by(term) %>%
+    map_dfr(broom::tidy) %>%     # tidy estimates
+    group_by(term) %>%           # group per variable
     summarise(est     = mean(estimate),
               bm      = sum((estimate - est)^2) / (m - 1),
               ubar    = mean(std.error^2),
               var_u   = (1 + 1/m) * bm - ubar,
-              var     = if_else(var_u > 0, var_u, ubar),
-              df      = max(1, (m - 1) * (1 - ubar / (bm + bm/m))^2),
+              var     = if_else(var_u > 0, var_u, ubar), # restrict variance to be positive
+              df      = max(1, (m - 1) * (1 - ubar / (bm + bm/m))^2), # restrict df > 1
               lower   = est - qt(.975, df) * sqrt(var),
               upper   = est + qt(.975, df) * sqrt(var), .groups = 'drop')
   pooled
 }
 
+# FULLY SYNTHETIC POOL FUNCTION WITH ADJUSTED (M-1) DF
 pool2.syn <- function(mira) {
   
-  if(class(mira)[1] == "mira") {
-    fitlist <- mira %$% analyses
+  if(class(mira)[1] == "mira") { # if the input object is of class mira
+    fitlist <- mira %$% analyses # extract the analyses from the mira object
   }
   else {
-    fitlist <- mira
+    fitlist <- mira              # and otherwise, just take the input list
   }
   
-  m <- length(fitlist)
+  m <- length(fitlist)           # number of imputations
   
   pooled <- fitlist %>% 
-    map_dfr(broom::tidy) %>%
-    group_by(term) %>%
+    map_dfr(broom::tidy) %>%     # tidy estimates
[…]

### 2020-08-16 mice_synthesizing/mice_synthesizing_partitioned_data.Rmd
Partitioned data with partially synthetic pooling rules.

@@
 ```
+
+---
+
+# Partially synthetic data pooling rules
+
+The results with the adjusted complexity parameter `cp = 1e-08`, `minbucket = 3` and `maxit = 1`.
+
+```{r}
+boot_parts %>%
+  map_dfr(function(x) {
+    x %>% map(function(y) y %$% lm(wgt ~ age + hgt)) %>%
+      pool3.syn
+    }) %>%
+  ci_cov(truemodel) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```
+
+The results with the adjusted complexity parameter `cp = 1e-08`, `minbucket = 3` and `maxit = 5`.
+
+```{r}
+boot_parts_5 %>%
+  map_dfr(function(x) {
+    x %>% map(function(y) y %$% lm(wgt ~ age + hgt)) %>%
+      pool3.syn
+    }) %>%
+  ci_cov(truemodel) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```

### 2020-08-16 mice_synthesizing/data_checks.Rmd
Adjusted cart settings for data checks.

@@
 Both the histograms and barplots shows that the relative frequencies of the values for the continuous variables or the categories for the categorical variables are highly similar.
+
+# Adjusted settings
+
+```{r, cache = thomcache}
+syns_adj <- data %>% 
+  mice(m = 100, 
+       maxit = 5,
+       method = cart,
+       minbucket = 3,
+       cp = 1e-08,
+       predictorMatrix = pred, 
+       where = matrix(TRUE, nrow(data), ncol(data)),
+       print = FALSE,
+       seed = 123)
+```
+
+```{r}
+completed_adj <- complete(syns_adj, action = "all")
+
+completed_adj %>%
+  map(function(x) bind_rows(data, x) %>% duplicated) %>%
+  map_dbl(sum) %>% 
+  sum # total number of duplicated rows over all 100 synthetic datasets
+
+completed_adj %>%
+  map(function(x) bind_rows(data, x) %>% duplicated) %>%
+  lapply(function(x) which(x)) %>%
+  unlist() - nrow(data)
+```
+
+```{r, dpi = 300, fig.fullwidth = TRUE, message = F}
+completed_adj %>%
+  map_dfr(function(x) x) %>%
+  bind_rows(., data, .id = "Imputed") %>%
+  mutate(Imputed = as.numeric(Imputed)) %>%
+  select_if(is.numeric) %>%
+  pivot_longer(cols = -"Imputed",
+               names_to = c("Variable")) %>%
+  mutate(Imputed = recode(Imputed, `1` = "Synthetic data", `2` = "Observed data")) %>%
+  ggplot(., mapping = aes(x = value, fill = Imputed)) +
+  geom_histogram(aes(y = ..density..), position = "dodge2", ) +
+  facet_wrap(~ Variable, nrow = 3, ncol = 2, scales = "free") +
+  theme_classic() +
+  scale_fill_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+```
+
+```{r, dpi = 300, fig.fullwidth = TRUE, message = F}
+completed_adj %>%
+  map_dfr(function(x) x) %>%
+  bind_rows(., data, .id = "Imputed") %>%
+  select_if(negate(is.numeric)) %>%
+  map_dfr(function(x) as.character(x)) %>%
+  pivot_longer(cols = -"Imputed",
+               names_to = c("Variable")) %>%
+  mutate(Imputed = recode(Imputed, `1` = "Synthetic data", `2` = "Observed data")) %>%
+  ggplot(., mapping = aes(x = value, fill = Imputed, group = Imputed)) +
+  geom_bar(aes(y = ..prop..), position = "dodge2") +
+  facet_wrap(~ Variable, nrow = 3, ncol = 2, scales = "free") +
+  theme_classic() +
+  scale_fill_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+```

### 2020-08-18 mice_synthesizing/functions.R
Added manual coefficient input option.

@@ -82,10 +82,12 @@ pool3.syn <- function(mira) {
   pooled
 }
 
-ci_cov <- function(pooled, true_fit) {
+ci_cov <- function(pooled, true_fit = NULL, coefs = NULL, vars = NULL) {
   
-  coefs <- coef(true_fit)
-  vars   <- diag(vcov(true_fit))
+  if (!is.null(true_fit)) {
+    coefs <- coef(true_fit)
+    vars   <- diag(vcov(true_fit))
+  }
   
   nsim <- nrow(pooled) / length(coefs)
   

### 2020-08-18 mice_synthesizing/paper.Rmd
Started working document

---
title: "Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*"
subtitle: "Anony*mice*d shareable data: Using *mice* to create multiply imputed synthetic datasets" 
author:
- Thom Volker, Gerko Vink & Stef van Buuren
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
bibliography: federated_imp.bib
csl: "/Users/thomvolker/Documents/styles/apa-6th-edition.csl"
---

# Introduction

Open science, including open data, has been marked as the future of science [@gewin_data_2016], and the advantages of publicly available research data are numerous [@foster_open_science_2017; @walport_brest_sharing_2011]. Additionally, the fact that public funds are used for data collection results in increased demands for this data. However, research data is very often collected under the reassurance of privacy and confidentiality of the data, and simply anonimizing the data is not enough to fulfil these requirements [@ohm_broken_2009]. Over the years, several techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above a certain threshold or adding random noise [@drechsler_synthetic_2011]. However, these methods may distort relationships between variables, reducing the data quality drastically.

An alternative has been offered by @rubin_statistical_disclosure_1993, who, building on the framework of multiple imputation, proposed to release multiple synthetic datasets to the public. Conform this approach, units are sampled randomly and independently from the sampling frame, and their, not observed, values are multiply imputed using a model fitted on the observed data.

**Explain approach**

**INTRO**

- think about fully / partially synthetic data.
- explain the procedure of creating synthetic datasets
- introduce mice for imputation of missing data
- mice can also be used for the imputation of synthetic data
- brief introduction of the mice algorithm???

**METHODS**

- explain simple synthetic data example
- explain imputation settings
- CART has been proposed by Reiter

## References

### 2020-08-19 mice_synthesizing/paper.Rmd
Work on intro

@@
 An alternative has been offered by @rubin_statistical_disclosure_1993, who, building on the framework of multiple imputation, proposed to release multiple synthetic datasets to the public.
-Conform this approach, units are sampled randomly and independently from the sampling frame, and their, not observed, values are multiply imputed using a model fitted on the observed data.
+Conform this approach, all units that are in the population but not in the sample are treated as missing data.
+These values are imputed by means of conventional multiple imputation approaches, and simple random samples are drawn from the population, and released to the public.
+In practice, it is not required to impute the complete population, since random samples can be drawn from the sampling frame, so that only these sampled values have to be imputed.
+The imputed samples generated under this approach are labelled as *fully synthetic datasets*.
+
+A second procedure to creating synthetic datasets has been proposed by @little_statistical_1993, named *partially synthetic datasets*, which yields imputing only those values that are at a high risk of being disclosive.
+These values can be complete variables that could be compared with publicly available datasets or registers, such as addresses, or it can be certain values that bear a high risk of being disclosive, say, income values above a certain threshold.
+Similarly to the fully synthetic data approach, multiple datasets containing synthetic values are released to the public, although in this instance, a subset of the data remains constant over the imputations, due to it's non-identifying nature.
+
+-- -- NOT SURE YET: CONTRAST FULLY AND PARTIALLY SYNTHETIC DATA -- --
+
+-- -- SINCE PARTIALLY SYNTHETIC DATA POOLING RULES DO NOT REQUIRE ADJUSTED VARIANCE ESTIMATES -- --
+
+Imputing synthetic values is conceptually similar to the imputations of missing values.
+That is, conform fully conditional specification, values are drawn iteratively from the posterior predictive distribution of the variable of interest, conditional on all other variables, for each variable separately, where the previously imputed values are taken into account in the imputation model for the variables that are imputed later on.
+***ADD MORE INFO FCS***
+
+-- -- CAN WE REGARD THE OBSERVED VALUES AS THE STARTING VALUES FOR THE IMPUTATIONS ? -- --
+
+The R-package `mice` [@mice] implements the fully conditional specification approach for missing data.
+Since the imputation approaches for missing data and synthetic data do not differ in terms of the imputation process, `mice` can be used for creating synthetic data as well, which will be shown in more detail in the remainder of this paper.
+Additionally, it will be shown that creating confidence valid [TO DO: FULLY/PARTIALLY] synthetic data can be generated by means of `mice`.
+However, before introducing `mice` for the creation of synthetic data, the pooling rules for synthetic data will be discussed.
+
+-- -- EXPLAIN MICE -- --
+
+# FULLY/PARTIALLY synthetic data
+
+DISCUSS APPROACH IN MORE DEPTH
+
+# Mice
+
+Discuss mice, predominantly the imputation algorithm in greater depth
+
+# Simulations
+
+## Methods
+Boys data - bootstrapped to obtain a population.
+
+## Results
 

### 2020-08-19 mice_synthesizing/paper.Rmd
Update intro.

@@
 Since the imputation approaches for missing data and synthetic data do not differ in terms of the imputation process, `mice` can be used for creating synthetic data as well, which will be shown in more detail in the remainder of this paper.
-Additionally, it will be shown that creating confidence valid [TO DO: FULLY/PARTIALLY] synthetic data can be generated by means of `mice`.
-However, before introducing `mice` for the creation of synthetic data, the pooling rules for synthetic data will be discussed.
-
--- -- EXPLAIN MICE -- --
+In the next section, the pooling rules that are required to obtain inferences from the synthetic datasets are discussed.
+Thereafter, it will be shown that creating confidence valid [TO DO: FULLY/PARTIALLY] synthetic data can be generated by means of `mice`.
+Also, it is shown that iterating over the conditional distributions in order to establish convergence is not required, due to the fact that new values are drawn directly from posterior distribution given the observed data.
 
@@
 ## Methods
-Boys data - bootstrapped to obtain a population.
+
+- Boys data - bootstrapped to obtain a population.
+- explain simple synthetic data procedure
+- explain imputation settings
+- CART has been proposed by Reiter
 
@@
 
-**Explain approach**
-
-**INTRO**
-
-- think about fully / partially synthetic data.
-- explain the procedure of creating synthetic datasets
-- introduce mice for imputation of missing data
-- mice can also be used for the imputation of synthetic data
-- brief introduction of the mice algorithm???
-
-**METHODS**
-
-- explain simple synthetic data example
-- explain imputation settings
-- CART has been proposed by Reiter
-
 ## References

### 2020-08-20 mice_synthesizing/Mice_Synthesizing.Rmd

@@
   mutate(CIW = conf.high - conf.low) %>% 
-  kable(digits = 3) %>%
+  kable(digits = 3,
+        caption = "Results of a single linear regression model on the completed dataset.") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
@@
           "Mice with cart" = results_cart, .id = "Imputation method") %>%
-  kable(digits = 3) %>%
+  kable(digits = 3,
+        caption = "Results of with mice default settings, and with CART settings, for the imputation of synthetic data, with the in-build mice pooling function.") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
@@
 ci_cov(pooled, truemodel) %>%
-  kable(digits = 3) %>%
+  kable(digits = 3,
+        caption = "Imputation results of synthesizing by means of CART, with the pooling rules by Drechsler.") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
@@
             "Coverage" = mean(cover)) %>%
-  kable(digits = 3) %>%
+  kable(digits = 3,
+        caption = "Bootstrapped estimates of regression coefficients, with mean standard error and coverage based on the individual estimates of the standard error.") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
@@
   ci_cov(truemodel) %>%
-  kable(digits = 3) %>%
+  kable(digits = 3,
+        caption = "Synthetic (CART) results with pooling rules by Drechsler.") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
@@
   scale_fill_viridis_d(begin = .30, end = .65) +
-  theme_classic()
+  theme_classic() +
+  ggtitle("Distribution of the bootstrapped and synthetic regression coefficients.")
 ```
@@
 ```{r, message = F}
-boot_se <- boot_true %>% group_by(term) %>% summarise("Bootstrapped SE" = sd(estimate))
-boot_syn_se <- boot_syn %>% group_by(term) %>% summarise("Synthetic bootstrapped SE" = sd(est))
+boot_se <- boot_true %>% group_by(term) %>% summarise("Mean bootstrapped SEs" = sd(estimate))
+boot_syn_se <- boot_syn %>% group_by(term) %>% summarise("Mean synthetic SEs" = sd(est))
 
@@
   scale_fill_viridis_d(begin = .30, end = .65) +
-  theme_classic()
+  theme_classic() +
+  ggtitle("Distribution of the confidence interval width (CIW) of the bootstrapped and the synthetic datasets.")
 ```
@@
   ci_cov(., truemodel) %>%
-  kable(digits = 3) %>%
+  kable(digits = 3,
+        caption = "Synthesizing the same data.") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
@@
   ci_cov(., truemodel) %>%
-  kable(digits = 3) %>%
+  kable(digits = 3,
+        caption = "Synthesizing bootstrap samples with adjusted imputation settings.") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
@@
   ci_cov(., truemodel) %>%
-  kable(digits = 3) %>%
+  kable(digits = 3,
+        caption = "Synthesizing bootstrap samples with adjusted imputation settings but with maxit = 5.") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
@@
           "Cart adjusted settings" = cart_adj, .id = "Method") %>%
-  kable(digits = 3) %>%
+  kable(digits = 3,
+        caption = "Within, between and total imputation variance for default CART, and adjusted CART.") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

### 2020-08-20 mice_synthesizing/paper.Rmd
Added points to discuss.

@@
 ---
+
+# OUTLINE
+
+**Intro**
+
+- Motivation/relevance
+- Synthetic data (fully/partially shortly explained)
+- How can this data be generated in practice (FCS - multivariate synthetic values)
+- Mice adopts FCS for missing data
+- It will be shown that mice is also capable of generating multivariate synthetic data
+- However, multiple rules for correct variance estimates have been proposed, but the choice of one optimal variance estimate is not straightforward.
+Therefore, the performance of the currently available variance estimators (as outlined below) will be contrasted
+- Goal: explain and show how `mice` can be used to create synthetic versions of the data at hand, and which variance estimator yields the best results.
+
+**Synthetic data explained**
+
+*Fully synthetic data*
+
+- Explain the idea in more depth than in the intro
+- Explain pooling rules by Raghunathan, Reiter & Rubin
+- Adjusted variance estimate by Reiter (restricted positive)
+- Simple variance estimator by `synthpop` authors.
+
+*Partially synthetic data*
+- Explain the idea in more depth than in the intro
+- Explain pooling rules by Reiter.
+- Adjusted estimate by `synthpop` authors.
+
+**Mice**
+
+- Explain algorithm (FCS) in more depth
+- Observed values can be regarded as starting values for the imputation model.
+Since the observed data is used for creating the imputation models, no iterations are required.
+That is, the model is fixed, and not dependent on the imputed values.
+
+**Methods**
+
+- Boys dataset, considering using another dataset (two datasets with same results would prove the point even more).
+- Explain synthesizing procedure (by means of cart, using fcs as implemented in mice).
+- Imputation settings (CART, as proposed by Reiter).
+- What will be looked at: simple means / variances of variables (univariate relationships) and estimates of regression coefficients (of multiple models (at least 2 different models)).
+- Eventually: distinction between fully (everything replaced) and partially (only subset of variables replaced) synthetic data. 
+- Eventually: distinction between number of imputations (however, $m = 5$ proved to yield sufficient results already in the simulations run thus far).
+
+**Results**
+
+- Discuss results.
+
+**Discussion**
+
+Pros and cons of different methods, theoretically and practically.
 
@@
 In the next section, the pooling rules that are required to obtain inferences from the synthetic datasets are discussed.
-Thereafter, it will be shown that creating confidence valid [TO DO: FULLY/PARTIALLY] synthetic data can be generated by means of `mice`.
+Thereafter, it will be investigated which variance estimator yields the best, that is, confidence valid, results in combination with the `mice` synthesizing approach.
 Also, it is shown that iterating over the conditional distributions in order to establish convergence is not required, due to the fact that new values are drawn directly from posterior distribution given the observed data.
@@
 
+## Fully synthetic data
+
 DISCUSS APPROACH IN MORE DEPTH
+
+Explain pooling rules (variance estimates + adjusted variance estimates + simple estimator proposed by synthpop authors)
+
+## Partially synthetic data
+
+DISCUSS APPROACH IN MORE DEPTH
+
+Explain pooling rules (variance estimates)
 
@@
 
-Discuss mice, predominantly the imputation algorithm in greater depth
+- Discuss mice, predominantly the imputation algorithm in greater depth
+- Procedure: observed values can be regarded as starting values, so that all variables can be used for the synthesis of all other variables.
 

### 2020-08-20 mice_synthesizing/paper.Rmd
Typo - line break added.
Typo - unordered list.

@@
 *Partially synthetic data*
+
 - Explain the idea in more depth than in the intro
@@
 
-Pros and cons of different methods, theoretically and practically.
+- Pros and cons of different methods, theoretically and practically.
 

### 2020-08-21 mice_synthesizing/paper.Rmd

@@
 Conform this approach, all units that are in the population but not in the sample are treated as missing data.
-These values are imputed by means of conventional multiple imputation approaches, and simple random samples are drawn from the population, and released to the public.
+These values are imputed by means of conventional multiple imputation approaches, and simple random samples are drawn from the population.
+Ultimately, these samples are released to the public.
 In practice, it is not required to impute the complete population, since random samples can be drawn from the sampling frame, so that only these sampled values have to be imputed.
-The imputed samples generated under this approach are labelled as *fully synthetic datasets*.
+The datasets generated under this approach are labelled as *fully synthetic datasets*.
+However, note that, if one draws simple random samples from the sampling frame, the possibility exists that actual observations are included.
 
-A second procedure to creating synthetic datasets has been proposed by @little_statistical_1993, named *partially synthetic datasets*, which yields imputing only those values that are at a high risk of being disclosive.
+A second procedure to creating synthetic datasets has been proposed by @little_statistical_1993, named *partially synthetic datasets*, which originated as a procedure that required synthesizing only those values that are at a high risk of being disclosive.
 These values can be complete variables that could be compared with publicly available datasets or registers, such as addresses, or it can be certain values that bear a high risk of being disclosive, say, income values above a certain threshold.
-Similarly to the fully synthetic data approach, multiple datasets containing synthetic values are released to the public, although in this instance, a subset of the data remains constant over the imputations, due to it's non-identifying nature.
+Similarly to the fully synthetic data approach, multiple datasets containing synthetic values are released to the public, although in this instance, only the values at a high risk vary over the synthetic datasets.
+However, nothing keeps us from treating all values in the dataset as bearing a high disclosure risk, resulting in datasets that are completely existing of synthetic values.
+This approach basically implements the idea of fully synthetic data, based on the partially synthetic data procedure.
+
+-- -- HIER MIST NOG EEN OVERGANG WAAR IK NOG NIET UIT BEN -- --
+
+As of today, most papers in this field address methodological issues concerning both fully and partially synthetic datasets, both with regard to analysis methods suitable for creating synthetic data, and concerning inferential procedures.
+The current paper aims at reducing the gap between the theory about synthetic data, and generating synthetic data in practice.
+Due to the conceptual similarities between imputation for missing data and imputation for synthetic data, we propose that the R-package `mice` is capable of bridging the gap between theory and actual applications.
+Originally, `mice` is developed as an R-package to impute values subject to non-response.
+However, algorithmically, the procedure of imputing values subject to non-response does not need to differ from imputing synthetic data.
+Both approaches can be based on fully conditional specification (FCS) as implemented in `mice`.
+Conform this approach, values are drawn iteratively from the posterior predictive distribution of the variable of interest conditional on all other variables, for each variable separately.
+Thus, previously imputed values are taken into account in the imputation model for variables that are imputed later on.
+
+Since `mice` is currently only capable of imputing the data at hand, the approach should be labelled as *partially synthetic*.
+That is, although it is completely possible to create a synthetic dataset that consists of only synthetic values, `mice` is not (yet) capable of imputing observations that are not present in the data.
+Creating fully synthetic datasets by means of `mice` remains an area of future research.
 
@@
 
-Imputing synthetic values is conceptually similar to the imputations of missing values.
-That is, conform fully conditional specification, values are drawn iteratively from the posterior predictive distribution of the variable of interest, conditional on all other variables, for each variable separately, where the previously imputed values are taken into account in the imputation model for the variables that are imputed later on.
-***ADD MORE INFO FCS***
-
 -- -- CAN WE REGARD THE OBSERVED VALUES AS THE STARTING VALUES FOR THE IMPUTATIONS ? -- --
 
-The R-package `mice` [@mice] implements the fully conditional specification approach for missing data.
+<!-- The R-package `mice` [@mice] implements the fully conditional specification approach for missing data.
 Since the imputation approaches for missing data and synthetic data do not differ in terms of the imputation process, `mice` can be used for creating synthetic data as well, which will be shown in more detail in the remainder of this paper.
@@
 Also, it is shown that iterating over the conditional distributions in order to establish convergence is not required, due to the fact that new values are drawn directly from posterior distribution given the observed data.
+-->
 
@@
 
+- Discuss the FCS algorithm in more detail.
 - Discuss mice, predominantly the imputation algorithm in greater depth

### 2020-08-21 mice_synthesizing/paper.Rmd

@@
 Open science, including open data, has been marked as the future of science [@gewin_data_2016], and the advantages of publicly available research data are numerous [@foster_open_science_2017; @walport_brest_sharing_2011].
-Additionally, the fact that public funds are used for data collection results in increased demands for this data.
-However, research data is very often collected under the reassurance of privacy and confidentiality of the data, and simply anonimizing the data is not enough to fulfil these requirements [@ohm_broken_2009].
-Over the years, several techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above a certain threshold or adding random noise [@drechsler_synthetic_2011].
+HIER EEN VOORBEELD Additionally, the fact that public funds are used for data collection results in increased demands for the collected data.
+Nevertheless, the possibilities to share research data directly are often very limited due to restrictions with regard to privacy and confidentiality.
+Simply anonimizing the data is not enough to fulfil these requirements [@ohm_broken_2009].
+Over the years, several other techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above a certain threshold or adding random noise [@drechsler_synthetic_2011].
 However, these methods may distort relationships between variables, reducing the data quality drastically.

### 2020-08-24 mice_synthesizing/paper.Rmd
adjusted outline

@@
 bibliography: federated_imp.bib
-csl: "/Users/thomvolker/Documents/styles/apa-6th-edition.csl"
 ---
@@
 
-**Intro**
+## Introduction
 
-- Motivation/relevance
-- Synthetic data (fully/partially shortly explained)
-- How can this data be generated in practice (FCS - multivariate synthetic values)
-- Mice adopts FCS for missing data
-- It will be shown that mice is also capable of generating multivariate synthetic data
-- However, multiple rules for correct variance estimates have been proposed, but the choice of one optimal variance estimate is not straightforward.
-Therefore, the performance of the currently available variance estimators (as outlined below) will be contrasted
-- Goal: explain and show how `mice` can be used to create synthetic versions of the data at hand, and which variance estimator yields the best results.
+ - What is synthetic data
+ - Why is it useful
+ - Why should it be easy to generate
+ - Parrallel to missing data
+ - If similar to missing data then why not use mice
+ - All fun and game, but statistical properties should be intact
+ - In this paper we demonstrate a straigthforward workflow for generating synthetic data sets and we investigate how to obtain valid inferences from synthesized data.
 
-**Synthetic data explained**
-
-*Fully synthetic data*
-
-- Explain the idea in more depth than in the intro
-- Explain pooling rules by Raghunathan, Reiter & Rubin
-- Adjusted variance estimate by Reiter (restricted positive)
-- Simple variance estimator by `synthpop` authors.
-
-*Partially synthetic data*
-
-- Explain the idea in more depth than in the intro
-- Explain pooling rules by Reiter.
-- Adjusted estimate by `synthpop` authors.
-
-**Mice**
-
-- Explain algorithm (FCS) in more depth
+## Generating synthetic data with mice
+- Explain FCS in short
+- Demonstrate procedure with where matrix and explain rationale
+- Demonstrate that it is a reasonable approach based figure that shows obs relations and synth relations side-by-side (e.g. wgt ~ age | gen)
 - Observed values can be regarded as starting values for the imputation model.
@@
 
-**Methods**
+## Drawing inferences from mice synthesized data
+- What ways are there (with minimal - if any - escapes to partial/fully synthesized)
+- If based on your earlier work, cite the online reference for your simulations and give URL. No need to go into detail about it here.
 
-- Boys dataset, considering using another dataset (two datasets with same results would prove the point even more).
-- Explain synthesizing procedure (by means of cart, using fcs as implemented in mice).
-- Imputation settings (CART, as proposed by Reiter).
-- What will be looked at: simple means / variances of variables (univariate relationships) and estimates of regression coefficients (of multiple models (at least 2 different models)).
-- Eventually: distinction between fully (everything replaced) and partially (only subset of variables replaced) synthetic data. 
-- Eventually: distinction between number of imputations (however, $m = 5$ proved to yield sufficient results already in the simulations run thus far).
+### Simulation
+- Simulation set-up
+- Evaluation criteria explained: the bias cov ciw triangle
+- Table with demonstrate bias cov ciw for all methods
 
-**Results**
-
-- Discuss results.
-
-**Discussion**
-
-- Pros and cons of different methods, theoretically and practically.
+## Discussion
+- Summarize findings
+- Stress that only holds for sampled data. Explain that for fully observed populations, one would need no sampling variance. 
+- Revisit the simplicity and the readily available solution within the mice workflow (if adjusted pool is required, add to mice and direct to that function)
 

### 2020-08-25 mice_synthesizing/paper.Rmd
Small update paper.

--- 2020-08-21 mice_synthesizing/paper.Rmd
@@
 
-Open science, including open data, has been marked as the future of science [@gewin_data_2016], and the advantages of publicly available research data are numerous [@foster_open_science_2017; @walport_brest_sharing_2011].
-HIER EEN VOORBEELD Additionally, the fact that public funds are used for data collection results in increased demands for the collected data.
+Open science, including open data, has been marked as the future of science [@gewin_data_2016], and the advantages of publicly available research data are numerous [@molloy_open_2011; @walport_brest_sharing_2011].
+As collecting research data requires an enormous investment both in terms of time and monetary resources, openly accessible research data bears the potential of increasing the scientific returns.
+Additionally, the fact that public funds are used for data collection results in increased demands for the collected data.
 Nevertheless, the possibilities to share research data directly are often very limited due to restrictions with regard to privacy and confidentiality.

### 2020-08-26 mice_synthesizing/paper.Rmd
Update outline.

@@
 
+## Introduction
+
+- [x] What is synthetic data?
+- [x] Why is it useful?
+- [x] Why should it be easy to generate?
+- [ ] Parallel to missing data
+- [ ] If similar to missing data, then why not use `mice`?
+- [ ] `mice` can only be exploited if the statistical properties are correct.
+- [ ] In this paper we demonstrate a straightforward workflow for generating synthetic datasets and we investigate how to obtain valid inferences from synthesized data.
+
+## Generating synthetic data with `mice`
+
+- [ ] Explain FCS in short.
+- [ ] Demonstrate procedure with `where-matrix` and explain rationale.
+- [ ] Demonstrate that this is a reasonable approach, based on a figure that shows the observed and synthetic relationships side-by-side (e.g. `wgt ~ age + gen`).
+- [ ] Observed values can be regarded as starting values for the imputation model.
+Since the observed data is used for creating the imputation models, no iterations are required.
+That is, the model is fixed, and not dependent on the imputed values.
+
+## Drawing inferences from `mice` synthesized data
+
+- [ ] What ways are there (with minimal - if any - escapes to partially/fully synthetic data).
+- [ ] If based on your earlier work, cite the online reference for your simulations and give URL. No need to go into detail about it here.
+
+### Simulation
+
+- [ ] Simulation set-up.
+- [ ] Evaluation criteria explained: the bias, coverage and CIW triangle.
+- [ ] Table which demonstrates bias, coverage and CIW for all methods.
+
+## Discussion
+
+- [ ] Summarize findings.
+- [ ] Stress that only holds for sampled data. Explain that for fully observed populations, one would need no sampling variance.
+- [ ] Revisit the simplicity and the readily available solution within the `mice` workflow (if adjusted pool is required, add to mice and direct to that function).
+
+# Introduction
+
+Open science, including open data, has been marked as the future of science [@gewin_data_2016], and the advantages of publicly available research data are numerous [@molloy_open_2011; @walport_brest_sharing_2011].
+As collecting research data requires an enormous investment both in terms of time and monetary resources, openly accessible research data bears the potential of increasing the scientific returns.
+Additionally, the fact that public funds are used for data collection results in increased demands for the collected data.
+Nevertheless, the possibilities to share research data directly are often very limited due to restrictions with regard to privacy and confidentiality.
+Simply anonimizing the data is not enough to fulfil these requirements [@ohm_broken_2009].
+Over the years, several other techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above a certain threshold or adding random noise [@drechsler_synthetic_2011].
+However, these methods may distort relationships between variables, reducing the data quality drastically.
+
+An alternative has been offered by @rubin_statistical_disclosure_1993, who, building on the framework of multiple imputation, proposed to release multiple synthetic datasets to the public.
+Conform this approach, all units that are in the population but not in the sample are treated as missing data.
+These values are imputed by means of conventional multiple imputation approaches, and simple random samples are drawn from the population.
+Ultimately, these samples are released to the public.
+In practice, it is not required to impute the complete population, since random samples can be drawn from the sampling frame, so that only these sampled values have to be imputed.
+The datasets generated under this approach are labelled as *fully synthetic datasets*.
+However, note that, if one draws simple random samples from the sampling frame, the possibility exists that actual observations are included.
+
+A second procedure to creating synthetic datasets has been proposed by @little_statistical_1993, named *partially synthetic datasets*, which originated as a procedure that required synthesizing only those values that are at a high risk of being disclosive.
+These values can be complete variables that could be compared with publicly available datasets or registers, such as addresses, or it can be certain values that bear a high risk of being disclosive, say, income values above a certain threshold.
+Similarly to the fully synthetic data approach, multiple datasets containing synthetic values are released to the public, although in this instance, only the values at a high risk vary over the synthetic datasets.
+However, nothing keeps us from treating all values in the dataset as bearing a high disclosure risk, resulting in datasets that are completely existing of synthetic values.
+This approach basically implements the idea of fully synthetic data, based on the partially synthetic data procedure.
+
+Potentially, these approaches could fulfil the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints.
+However, there is no such thing as a free lunch: data collectors have to put effort in creating synthetic data, and using incorrect models to generate synthetic data might yield biased results for potential analysts of the data.
+It thus is crucial that the synthesizing process will be as easy as it gets, so that the step to release synthetic data is as small as possible.
+
+-- -- HIER MIST NOG EEN OVERGANG WAAR IK NOG NIET UIT BEN -- --
+
+As of today, most papers in this field address methodological issues concerning both fully and partially synthetic datasets, both with regard to analysis methods suitable for creating synthetic data, and concerning inferential procedures.
+The current paper aims at reducing the gap between the theory about synthetic data, and generating synthetic data in practice.
+Due to the conceptual similarities between imputation for missing data and imputation for synthetic data, we propose that the R-package `mice` is capable of bridging the gap between theory and actual applications.
+Originally, `mice` is developed as an R-package to impute values subject to non-response.
+However, algorithmically, the procedure of imputing values subject to non-response does not need to differ from imputing synthetic data.
+Both approaches can be based on fully conditional specification (FCS) as implemented in `mice`.
+Conform this approach, values are drawn iteratively from the posterior predictive distribution of the variable of interest conditional on all other variables, for each variable separately.
+Thus, previously imputed values are taken into account in the imputation model for variables that are imputed later on.
+
+Since `mice` is currently only capable of imputing the data at hand, the approach should be labelled as *partially synthetic*.
+That is, although it is completely possible to create a synthetic dataset that consists of only synthetic values, `mice` is not (yet) capable of imputing observations that are not present in the data.
+Creating fully synthetic datasets by means of `mice` remains an area of future research.
+
+-- -- NOT SURE YET: CONTRAST FULLY AND PARTIALLY SYNTHETIC DATA -- --
+
+-- -- SINCE PARTIALLY SYNTHETIC DATA POOLING RULES DO NOT REQUIRE ADJUSTED VARIANCE ESTIMATES -- --
+
+-- -- CAN WE REGARD THE OBSERVED VALUES AS THE STARTING VALUES FOR THE IMPUTATIONS ? -- --
+
+<!-- The R-package `mice` [@mice] implements the fully conditional specification approach for missing data.
+Since the imputation approaches for missing data and synthetic data do not differ in terms of the imputation process, `mice` can be used for creating synthetic data as well, which will be shown in more detail in the remainder of this paper.
+In the next section, the pooling rules that are required to obtain inferences from the synthetic datasets are discussed.
+Thereafter, it will be investigated which variance estimator yields the best, that is, confidence valid, results in combination with the `mice` synthesizing approach.
+Also, it is shown that iterating over the conditional distributions in order to establish convergence is not required, due to the fact that new values are drawn directly from posterior distribution given the observed data.
+-->
+
 **Intro**
@@
 - Motivation/relevance
+
 - Synthetic data (fully/partially shortly explained)
+
 - How can this data be generated in practice (FCS - multivariate synthetic values)
+
 - Mice adopts FCS for missing data
+
 - It will be shown that mice is also capable of generating multivariate synthetic data
+
 - However, multiple rules for correct variance estimates have been proposed, but the choice of one optimal variance estimate is not straightforward.
 Therefore, the performance of the currently available variance estimators (as outlined below) will be contrasted
-- Goal: explain and show how `mice` can be used to create synthetic versions of the data at hand, and which variance estimator yields the best results.
+
+- Goal: explain and show how mice can be used to create synthetic versions of the data at hand, and which variance estimator yields the best results.
 
@@
 
-# Introduction
-
-Open science, including open data, has been marked as the future of science [@gewin_data_2016], and the advantages of publicly available research data are numerous [@molloy_open_2011; @walport_brest_sharing_2011].
-As collecting research data requires an enormous investment both in terms of time and monetary resources, openly accessible research data bears the potential of increasing the scientific returns.
-Additionally, the fact that public funds are used for data collection results in increased demands for the collected data.
-Nevertheless, the possibilities to share research data directly are often very limited due to restrictions with regard to privacy and confidentiality.
-Simply anonimizing the data is not enough to fulfil these requirements [@ohm_broken_2009].
-Over the years, several other techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above a certain threshold or adding random noise [@drechsler_synthetic_2011].
-However, these methods may distort relationships between variables, reducing the data quality drastically.
-
-An alternative has been offered by @rubin_statistical_disclosure_1993, who, building on the framework of multiple imputation, proposed to release multiple synthetic datasets to the public.
-Conform this approach, all units that are in the population but not in the sample are treated as missing data.
-These values are imputed by means of conventional multiple imputation approaches, and simple random samples are drawn from the population.
-Ultimately, these samples are released to the public.
-In practice, it is not required to impute the complete population, since random samples can be drawn from the sampling frame, so that only these sampled values have to be imputed.
-The datasets generated under this approach are labelled as *fully synthetic datasets*.
-However, note that, if one draws simple random samples from the sampling frame, the possibility exists that actual observations are included.
-
-A second procedure to creating synthetic datasets has been proposed by @little_statistical_1993, named *partially synthetic datasets*, which originated as a procedure that required synthesizing only those values that are at a high risk of being disclosive.
-These values can be complete variables that could be compared with publicly available datasets or registers, such as addresses, or it can be certain values that bear a high risk of being disclosive, say, income values above a certain threshold.
-Similarly to the fully synthetic data approach, multiple datasets containing synthetic values are released to the public, although in this instance, only the values at a high risk vary over the synthetic datasets.
-However, nothing keeps us from treating all values in the dataset as bearing a high disclosure risk, resulting in datasets that are completely existing of synthetic values.
-This approach basically implements the idea of fully synthetic data, based on the partially synthetic data procedure.
-
--- -- HIER MIST NOG EEN OVERGANG WAAR IK NOG NIET UIT BEN -- --
-
-As of today, most papers in this field address methodological issues concerning both fully and partially synthetic datasets, both with regard to analysis methods suitable for creating synthetic data, and concerning inferential procedures.
-The current paper aims at reducing the gap between the theory about synthetic data, and generating synthetic data in practice.
-Due to the conceptual similarities between imputation for missing data and imputation for synthetic data, we propose that the R-package `mice` is capable of bridging the gap between theory and actual applications.
-Originally, `mice` is developed as an R-package to impute values subject to non-response.
-However, algorithmically, the procedure of imputing values subject to non-response does not need to differ from imputing synthetic data.
-Both approaches can be based on fully conditional specification (FCS) as implemented in `mice`.
-Conform this approach, values are drawn iteratively from the posterior predictive distribution of the variable of interest conditional on all other variables, for each variable separately.
-Thus, previously imputed values are taken into account in the imputation model for variables that are imputed later on.
-
-Since `mice` is currently only capable of imputing the data at hand, the approach should be labelled as *partially synthetic*.
-That is, although it is completely possible to create a synthetic dataset that consists of only synthetic values, `mice` is not (yet) capable of imputing observations that are not present in the data.
-Creating fully synthetic datasets by means of `mice` remains an area of future research.
-
--- -- NOT SURE YET: CONTRAST FULLY AND PARTIALLY SYNTHETIC DATA -- --
-
--- -- SINCE PARTIALLY SYNTHETIC DATA POOLING RULES DO NOT REQUIRE ADJUSTED VARIANCE ESTIMATES -- --
-
--- -- CAN WE REGARD THE OBSERVED VALUES AS THE STARTING VALUES FOR THE IMPUTATIONS ? -- --
-
-<!-- The R-package `mice` [@mice] implements the fully conditional specification approach for missing data.
-Since the imputation approaches for missing data and synthetic data do not differ in terms of the imputation process, `mice` can be used for creating synthetic data as well, which will be shown in more detail in the remainder of this paper.
-In the next section, the pooling rules that are required to obtain inferences from the synthetic datasets are discussed.
-Thereafter, it will be investigated which variance estimator yields the best, that is, confidence valid, results in combination with the `mice` synthesizing approach.
-Also, it is shown that iterating over the conditional distributions in order to establish convergence is not required, due to the fact that new values are drawn directly from posterior distribution given the observed data.
--->
-
 # FULLY/PARTIALLY synthetic data

### 2020-08-26 mice_synthesizing/paper.Rmd
Adjusted intro.

@@
 
+An alternative solution has been proposed separately by @rubin_statistical_disclosure_1993 and @little_statistical_1993.
+Although their approaches differed to some extent, the general concept was to release multiply imputed synthetic datasets, instead of the actually observed data.
+Based on some imputation model, values from the actually observed data are replaced by multiple draws from the posterior predictive distribution of the observed data.
+The values that are to be replaced can be complete variables that could be compared with publicly available datasets or registers, such as addresses, or can be certain values that bear a high risk of being disclosive, say, income values above a certain threshold.
+Additionally, a researcher can opt to simply replace all values of every observation.
+
+Potentially, this approach could fulfil the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints.
+However, there is no such thing as a free lunch: data collectors have to put effort in creating high-quality synthetic data.
+
+The goal then is to release multiply imputed datasets that bear no risk of releasing confidential or identifying information, while the multivariate relationships should be preserved as in the observed data.
+
+The fact that the then released data is synthetic could potentially fulfil the needs for openly accessible data, without running into barriers with regard to privacy and confidentiality constraints.
+
+, based on the multiple imputation framework [@rubin_multiple_1987].
+
+Potentially, these approaches  However, there is no such thing as a free lunch: data collectors have to put effort in creating synthetic data, and using incorrect models to generate synthetic data might yield biased results for potential analysts of the data.
+It thus is crucial that the synthesizing process will be as easy as it gets, so that the step to release synthetic data is as small as possible.
+
 An alternative has been offered by @rubin_statistical_disclosure_1993, who, building on the framework of multiple imputation, proposed to release multiple synthetic datasets to the public.
@@
 This approach basically implements the idea of fully synthetic data, based on the partially synthetic data procedure.
-
-Potentially, these approaches could fulfil the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints.
-However, there is no such thing as a free lunch: data collectors have to put effort in creating synthetic data, and using incorrect models to generate synthetic data might yield biased results for potential analysts of the data.
-It thus is crucial that the synthesizing process will be as easy as it gets, so that the step to release synthetic data is as small as possible.
 

### 2020-08-26 mice_synthesizing/paper.Rmd
Link synthetic and missing data.

@@
 bibliography: federated_imp.bib
-csl: "/Users/thomvolker/Documents/styles/apa-6th-edition.csl"
+csl: "apa-6th-edition.csl"
 ---
@@
 Based on some imputation model, values from the actually observed data are replaced by multiple draws from the posterior predictive distribution of the observed data.
+Using this approach, the researcher could replace the observed dataset as a whole with multiple synthetic versions.
+Additionally, the researcher could opt to only replace a subset of the observed data.
 The values that are to be replaced can be complete variables that could be compared with publicly available datasets or registers, such as addresses, or can be certain values that bear a high risk of being disclosive, say, income values above a certain threshold.
-Additionally, a researcher can opt to simply replace all values of every observation.
+
+Conceptually, the synthetic data framework is based upon the building blocks of multiple imputation for missing data, as proposed by @rubin_multiple_1987.
+Now, instead of replacing the missing values with multiple draws from the posterior predictive distribution, the sensitive values are replaced accordingly.
+Similarly to analysing multiply imputed datasets dealing with missing data, multiply imputed synthetic datasets can be analysed using conventional analysing techniques.
+The results of the analyses on each synthetic dataset should be pooled, so that the researcher obtains the estimates of the quantity of interest, as well as the estimate of its variance that adequately account for the additional variability that is induced by the imputation procedure.
 
@@
 However, there is no such thing as a free lunch: data collectors have to put effort in creating high-quality synthetic data.
+Also, the quality of the synthetic data are highly dependent on the imputation models, and using flawed models to generate synthetic data might bias subsequent analyses.
+Conversely, if the models used to create the synthetic data are able to preserve the relationships between the variables as in the original data, the synthetic data can be nearly as informative as the observed data.
+Thus, to fully exploit the benefits of synthetic data, the effort to actually create these datasets should be kept at a minimum.
+
+Since multiple imputation of synthetic data is closely linked to multiple imputation for missing data, using existing missing data software that research are familiar with already, would dramatically reduce the effort of creating synthetic data.
+The R-package `mice` [@mice] is particularly suited for generating synthetic data, since it already implements multiple imputation for missing data in a straightforward and user-friendly manner.
+However, `mice` is not restricted to imputation for missing data, since it can be easily adjusted to impute every observed value.
+
+***IK DENK DAT HET GOED IS OM HIER NOG TWEE KORTE ZINNEN OVER MICE NEER TE ZETTEN, MAAR IK VERWACHT DAT JULLIE BETER WETEN HOE EN WAT***
+
+To fully utilize the potential gains of synthetic data, while keeping the costs
+
+To fully
+
+Thus, the potential gains of using synthetic data are very high, if the costs of creating it can be kept at a minimum.
+
+If the approach to creating synthetic datasets can be simplified
+
+<!--
+
+It is easy to draw
 

### 2020-08-26 mice_synthesizing/paper.Rmd
Propose mice.

@@
 - [x] Why should it be easy to generate?
-- [ ] Parallel to missing data
-- [ ] If similar to missing data, then why not use `mice`?
+- [x] Parallel to missing data
+- [x] If similar to missing data, then why not use `mice`?
 - [ ] `mice` can only be exploited if the statistical properties are correct.
@@
 Since multiple imputation of synthetic data is closely linked to multiple imputation for missing data, using existing missing data software that research are familiar with already, would dramatically reduce the effort of creating synthetic data.
-The R-package `mice` [@mice] is particularly suited for generating synthetic data, since it already implements multiple imputation for missing data in a straightforward and user-friendly manner.
-However, `mice` is not restricted to imputation for missing data, since it can be easily adjusted to impute every observed value.
-
-***IK DENK DAT HET GOED IS OM HIER NOG TWEE KORTE ZINNEN OVER MICE NEER TE ZETTEN, MAAR IK VERWACHT DAT JULLIE BETER WETEN HOE EN WAT***
-
-To fully utilize the potential gains of synthetic data, while keeping the costs
-
-To fully
-
-Thus, the potential gains of using synthetic data are very high, if the costs of creating it can be kept at a minimum.
-
-If the approach to creating synthetic datasets can be simplified
+The R-package `mice` [@mice] implements multiple imputation for missing data in a straightforward and user-friendly manner, but is not restricted to the imputation of missing data.
+Since `mice` can be easily adjusted to impute all observed values, or a subset hereof, we propose that it is able to ease the creation of synthetic datasets.
 

### 2020-08-26 mice_synthesizing/paper.Rmd

@@
  - Explain algorithm (FCS) in more depth
+ - What is synthetic data
+ - Why is it useful
+ - Why should it be easy to generate
+ - Parrallel to missing data
+ - If similar to missing data then why not use mice
+ - All fun and game, but statistical properties should be intact
+ - In this paper we demonstrate a straigthforward workflow for generating synthetic data sets and we investigate how to obtain valid inferences from synthesized data.
+
+## Generating synthetic data with mice
+- Explain FCS in short
+- Demonstrate procedure with where matrix and explain rationale
+- Demonstrate that it is a reasonable approach based figure that shows obs relations and synth relations side-by-side (e.g. wgt ~ age | gen)
 - Observed values can be regarded as starting values for the imputation model.

### 2020-09-10 mice_synthesizing/paper.Rmd
update GV

@@
 Open science, including open data, has been marked as the future of science [@gewin_data_2016], and the advantages of publicly available research data are numerous [@molloy_open_2011; @walport_brest_sharing_2011].
-As collecting research data requires an enormous investment both in terms of time and monetary resources, openly accessible research data bears the potential of increasing the scientific returns.
+Because collecting research data requires an enormous investment both in terms of time and monetary resources, openly accessible research data bears the potential of increasing the scientific returns.
 Additionally, the fact that public funds are used for data collection results in increased demands for the collected data.
 Nevertheless, the possibilities to share research data directly are often very limited due to restrictions with regard to privacy and confidentiality.
-Simply anonimizing the data is not enough to fulfil these requirements [@ohm_broken_2009].
+Simply anonimizing the data is not enough to fulfill these requirements [@ohm_broken_2009].
 Over the years, several other techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above a certain threshold or adding random noise [@drechsler_synthetic_2011].
-However, these methods may distort relationships between variables, reducing the data quality drastically.
+However, these methods may distort relationships between variables, thereby drastically reducing the data quality and the usability for further research.
 
 An alternative solution has been proposed separately by @rubin_statistical_disclosure_1993 and @little_statistical_1993.
-Although their approaches differed to some extent, the general concept was to release multiply imputed synthetic datasets, instead of the actually observed data.
+Although their approaches differed to some extent, the general thought is to use actually observed data to generated multiply imputed synthetic datasets that can be freely disclosed.
 Based on some imputation model, values from the actually observed data are replaced by multiple draws from the posterior predictive distribution of the observed data.
-Using this approach, the researcher could replace the observed dataset as a whole with multiple synthetic versions.
+Using this approach, the researcher could replace the observed data set as a whole with multiple synthetic versions.
 Additionally, the researcher could opt to only replace a subset of the observed data.
-The values that are to be replaced can be complete variables that could be compared with publicly available datasets or registers, such as addresses, or can be certain values that bear a high risk of being disclosive, say, income values above a certain threshold.
+The values that are to be replaced can be complete variables that could be compared with publicly available data sets or registers, such as addresses, or can be certain values that bear a high risk of being disclosive, say, income values above a certain threshold.
 
 Conceptually, the synthetic data framework is based upon the building blocks of multiple imputation for missing data, as proposed by @rubin_multiple_1987.
-Now, instead of replacing the missing values with multiple draws from the posterior predictive distribution, the sensitive values are replaced accordingly.
-Similarly to analysing multiply imputed datasets dealing with missing data, multiply imputed synthetic datasets can be analysed using conventional analysing techniques.
-The results of the analyses on each synthetic dataset should be pooled, so that the researcher obtains the estimates of the quantity of interest, as well as the estimate of its variance that adequately account for the additional variability that is induced by the imputation procedure.
+Instead of replacing just the missing values with multiple draws from the posterior predictive distribution, one could easily *overimpute* any observed sensitive values.
+Doing this multiple times would allow for drawing correct statistical inferences, similar to those obtained from ordinary multiple imputation for incomplete data sets.
+The results of the multiply synthetisized data sets should be pooled into an single inference, so that the researcher can draw valid inference from a single pooled analysis.
+To that respect, the variance should reflect the added variability that is induced by the imputation procedure.
 
-Potentially, this approach could fulfil the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints.
+Potentially, this approach could fulfill the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints.
 However, there is no such thing as a free lunch: data collectors have to put effort in creating high-quality synthetic data.

### 2020-11-12 mice_synthesizing/paper.Rmd
add key phrase
Add content + outline to intro.

@@
 An alternative solution has been proposed separately by @rubin_statistical_disclosure_1993 and @little_statistical_1993.
-Although their approaches differed to some extent, the general thought is to use actually observed data to generated multiply imputed synthetic datasets that can be freely disclosed.
+Although their approaches differed to some extent, the general idea is to use actually observed data to generated multiply imputed synthetic datasets that can be freely disclosed.
 Based on some imputation model, values from the actually observed data are replaced by multiple draws from the posterior predictive distribution of the observed data.
 Using this approach, the researcher could replace the observed data set as a whole with multiple synthetic versions.
-Additionally, the researcher could opt to only replace a subset of the observed data.
+Alternatively, the researcher could opt to only replace a subset of the observed data.
 The values that are to be replaced can be complete variables that could be compared with publicly available data sets or registers, such as addresses, or can be certain values that bear a high risk of being disclosive, say, income values above a certain threshold.
 
-Conceptually, the synthetic data framework is based upon the building blocks of multiple imputation for missing data, as proposed by @rubin_multiple_1987.
+Conceptually, the synthetic data framework is based upon the building blocks of multiple imputation of missing data, as proposed by @rubin_multiple_1987.
 Instead of replacing just the missing values with multiple draws from the posterior predictive distribution, one could easily *overimpute* any observed sensitive values.
-Doing this multiple times would allow for drawing correct statistical inferences, similar to those obtained from ordinary multiple imputation for incomplete data sets.
-The results of the multiply synthetisized data sets should be pooled into an single inference, so that the researcher can draw valid inference from a single pooled analysis.
+Similarly to multiple imputation of missing data, the multiple synthetic datasets allow for correct statistical inferences.
+The results of the multiply synthesized data sets should be pooled into a single inference, so that the researcher can draw valid inference from a single pooled analysis.
 To that respect, the variance should reflect the added variability that is induced by the imputation procedure.
@@
 
-Since multiple imputation of synthetic data is closely linked to multiple imputation for missing data, using existing missing data software that research are familiar with already, would dramatically reduce the effort of creating synthetic data.
-The R-package `mice` [@mice] implements multiple imputation for missing data in a straightforward and user-friendly manner, but is not restricted to the imputation of missing data.
-Since `mice` can be easily adjusted to impute all observed values, or a subset hereof, we propose that it is able to ease the creation of synthetic datasets.
+To minimize additional effort of creating synthetic datasets on behalf of the researcher, software aimed at multiple imputation of missing data can be employed.
+Especially if researchers used this software at an earlier stage in the research process, or acquired familiarity with it during earlier projects, the additional burden of creating synthetic datasets is relatively small.
+The R-package `mice` [@mice] implements multiple imputation of missing data in a straightforward and user-friendly manner.
+However, the functionality of `mice` is not restricted to the imputation of missing data, but allows to impute any value in the data.
+Thus, `mice` can be utilized for the creation of multiply imputed synthetic datasets.
+
+After creating the multiply imputed synthetic data sets, the goal is to obtain valid statistical inferences from them.
+In the missing data framework, this is done by performing statistical analyses on all imputed data sets, and pooling the results of the analyses according to Rubin's rules [-@rubin_multiple_1987].
+In the synthetic data framework, the same procedure is followed.
+However, valid statistical results can only be obtained under the premise that the statistical properties of the analyses are correct.
+Analyzing synthetic data specically requires appropriate variance estimates.
+Notably, the variance estimator that is suitable for analyzing multiply imputed datasets for missing data is inappropriate when multiply imputed synthetic datasets are analyzed.
+As a result, multiple variance estimators have been proposed to analyze multiply imputed synthetic datasets correctly, that differ according to whether the data consists entirely of synthetic values, or only a subset of the data is synthetic.
+
+The remainder of this paper is organized as follows.
+First, we will shortly describe the `mice` algorithm for the creation of synthetic data that reassures the privacy and confidentiality of the participants.
+Second, we will demonstrate a straightforward workflow for imputation of synthetic data with `mice`.
+The third step is to summarize the variance estimators that have been proposed in the past.
+Finally, we will assess which variance estimator provides valid inferences from the synthetic data.
+
+# Generating synthetic data with `mice`
+
+KEY: Het moet niet mogelijk zijn om de echte waarden te reverse engineeren.
+De stochastische component van multiple imputation zorgt er voor dat dit onmogelijk is.
+Wat wel kan worden afgeleid is het ware data genererende model - en dat is nou precies de bedoeling.
 

### 2020-11-14 mice_synthesizing/paper.Rmd

@@
 # Generating synthetic data with `mice`
+
+The `mice` package has been developed originally for multiple imputation of missing data, but can be easily extended to the synthetic data framework.
+It proceeds by drawing missing or synthetic values from the joint distribution of the observed data.
+This joint density is generally hard or impossible to derive, which can be overcome by employing fully conditional specification (FCS).
+Consider a $n \times k$ data matrix $Y$, with values to be replaced $Y^{old}$, the values to be kept $Y^{keep}$ and the values that are already replaced $Y^{new}$, under the assumption that there are no missing values in the observed data set.
+Instead of drawing from the joint distribution, we draw from $k$ univariate conditional densities for each variable.
+That is, we draw from the distribution $P\big{(}Y_j^{old} | Y^{keep}, Y^{new}, Y^{old}_{-j}, \theta \big{)}$, where the drawn values are conditional upon the values that are to be kept, the synthetic values that are drawn at an earlier iteration and the values that still are to be replaced, with $j = 1, 2, \dots, k$ and $\theta$ indicating the parameter specifying the distribution of $Y_j^{old}$.
+Thus, the synthetic values are generated variable by variable.
+This procedure is executed $i = 1, 2, \dots, m$ times, resulting in $\textbf{D} = \{D{(1)}, \dots, D^{(m)}\}$ synthetic datasets, with $D^{(i)} = (Y^{keep}, Y^{i, new})$.
+
+To select the values that are to be replaced, one can utilize the `where` parameter in the `mice` function. This parameter allows one to set which values of the data are to be imputed.
 

### 2020-11-20 mice_synthesizing/paper.Rmd
Add first part of the mice approach section.

@@
 - [x] If similar to missing data, then why not use `mice`?
-- [ ] `mice` can only be exploited if the statistical properties are correct.
-- [ ] In this paper we demonstrate a straightforward workflow for generating synthetic datasets and we investigate how to obtain valid inferences from synthesized data.
+- [x] `mice` can only be exploited if the statistical properties are correct.
+- [x] In this paper we demonstrate a straightforward workflow for generating synthetic datasets and we investigate how to obtain valid inferences from synthesized data.
 
@@
 Nevertheless, the possibilities to share research data directly are often very limited due to restrictions with regard to privacy and confidentiality.
-Simply anonimizing the data is not enough to fulfill these requirements [@ohm_broken_2009].
+Simply anonimizing the data is not enough to fulfil these requirements [@ohm_broken_2009].
 Over the years, several other techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above a certain threshold or adding random noise [@drechsler_synthetic_2011].
@@
 
+The `mice` package has been developed originally for multiple imputation of missing data.
+In this context, the aim is to replace missing values due to nonresponse by plausible values from the posterior predictive distribution of the variable containing the missing values.
+Doing so, `mice` makes use of fully conditional specification (FCS), which breaks down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, with $k$ the number of variables in the data.
+Using FCS, for every variable containing missing values a model is constructed, to impute the missing values $Y_{j, mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ on a variable by variable basis.
+Note that the predictor matrix $Y_{-j}$ may contain yet imputed values from an earlier imputation step, and thus will be updated after every iteration.
+This procedure is applied $m$ times, resulting in $m$ completed datasets $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $\textbf{D}^{(l)} = (\textbf{Y}_{obs}, Y^{(l)}_{mis}$.
+__MAYBE ADD AN EXAMPLE OF HOW TO DO IT IN `mice`__
+
+__DISCUSS ESTIMATORS FOR MISSING DATA HERE, OR AT A LATER POINT__
+
+This approach can be straightforwardly extended to a synthetic data framework.
+However, rather than imputing missing data, we overimpute actually observed data, that is, we replace observed values by multiple imputations.
+For simplicity, assume that the data is completely observed (i.e., $\textbf{Y} = \textbf{Y}_{obs}$).
+Following the notation of @reiter_raghunathan_multiple_2007, let $Z_j = 1$ if any of the values of unit $j$ are to be replaced by imputations, and $Z_j = 0$ otherwise, with $\textbf{Z} = (Z_1, Z_2, \dots, Z_n)$.
+Accordingly, the data consists of values that are to be replaced and values that are to be kept (i.e., $\textbf{Y}^{(l)} = (\textbf{Y}^{(l)}_{rep}, \textbf{Y}_{nrep})$.
+Note the superscript $^{(l)}$ indicating the $l$th synthetic data set.
+Now, instead of imputing $\textbf{Y}^{(l)}_{mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, we impute $\textbf{Y}^{(l)}_{rep}$ from the posterior distribution of $(Y_{rep} | \textbf{Y}, \textbf{Z}, \theta)$.
+This process results in $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $m$ the number of synthetic datasets.
+
+By default, `mice` imputes all values that are coded as missing in the dataset.
+Using the `where` parameter within the mice function, one can choose to impute any value in the dataset.
+As input, the `where` parameter requires a matrix of the same dimensions of the data, (i.e., a $n \times k$ matrix, with $n$ the number of observations in the collected data) containing logical values.
+<!--
+
+Now, we aim to generate the replacement values for the actually observed data $Y_{syn}$, instead of values that replace missing values $Y_{imp}$.
+
+Using FCS, for every variable containing missing values, a model is constructed to impute the missing values on a given variable conditional on all other variables in the data, and the posterior distribution of the parameters used in the model at hand, on a variable by variable basis, which yields $P(Y_{mis} | X, \theta)$.
+
 The `mice` package has been developed originally for multiple imputation of missing data, but can be easily extended to the synthetic data framework.
@@
 Thus, the synthetic values are generated variable by variable.
-This procedure is executed $i = 1, 2, \dots, m$ times, resulting in $\textbf{D} = \{D{(1)}, \dots, D^{(m)}\}$ synthetic datasets, with $D^{(i)} = (Y^{keep}, Y^{i, new})$.
+This procedure is executed $i = 1, 2, \dots, m$ times, resulting in $\textbf{D} = \{D^{(1)}, \dots, D^{(m)}\}$ synthetic datasets, with $D^{(i)} = (Y^{keep}, Y^{i, new})$.
 
 To select the values that are to be replaced, one can utilize the `where` parameter in the `mice` function. This parameter allows one to set which values of the data are to be imputed.
+
+-->
 

### 2020-11-20 mice_synthesizing/paper.Rmd
Fix typo.

@@
 Now, instead of imputing $\textbf{Y}^{(l)}_{mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, we impute $\textbf{Y}^{(l)}_{rep}$ from the posterior distribution of $(Y_{rep} | \textbf{Y}, \textbf{Z}, \theta)$.
-This process results in $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $m$ the number of synthetic datasets.
+This process results in the synthetic data $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $m$ the number of synthetic datasets.
 
@@
 As input, the `where` parameter requires a matrix of the same dimensions of the data, (i.e., a $n \times k$ matrix, with $n$ the number of observations in the collected data) containing logical values.
+
 <!--

### 2020-11-29 mice_synthesizing/paper.Rmd

--- 2020-11-20 mice_synthesizing/paper.Rmd
@@
 Because collecting research data requires an enormous investment both in terms of time and monetary resources, openly accessible research data bears the potential of increasing the scientific returns.
-Additionally, the fact that public funds are used for data collection results in increased demands for the collected data.
+Additionally, the fact that public funds are used for data collection results in increasing demand for the collected data.
 Nevertheless, the possibilities to share research data directly are often very limited due to restrictions with regard to privacy and confidentiality.
@@
 An alternative solution has been proposed separately by @rubin_statistical_disclosure_1993 and @little_statistical_1993.
-Although their approaches differed to some extent, the general idea is to use actually observed data to generated multiply imputed synthetic datasets that can be freely disclosed.
+Although their approaches differed to some extent, the general idea is to use actually observed data to generate multiply imputed synthetic datasets that can be freely disclosed.
 Based on some imputation model, values from the actually observed data are replaced by multiple draws from the posterior predictive distribution of the observed data.
@@
 Similarly to multiple imputation of missing data, the multiple synthetic datasets allow for correct statistical inferences.
-The results of the multiply synthesized data sets should be pooled into a single inference, so that the researcher can draw valid inference from a single pooled analysis.
+The results of the multiple synthetic data sets should be pooled into a single inference, so that the researcher can draw valid conclusions from the pooled results.
 To that respect, the variance should reflect the added variability that is induced by the imputation procedure.
 
-Potentially, this approach could fulfill the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints.
+Potentially, this approach could fulfil the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints.
 However, there is no such thing as a free lunch: data collectors have to put effort in creating high-quality synthetic data.
-Also, the quality of the synthetic data are highly dependent on the imputation models, and using flawed models to generate synthetic data might bias subsequent analyses.
+Also, the quality of the synthetic data is highly dependent on the imputation models, and using flawed models to generate synthetic data might bias subsequent analyses.
 Conversely, if the models used to create the synthetic data are able to preserve the relationships between the variables as in the original data, the synthetic data can be nearly as informative as the observed data.
-Thus, to fully exploit the benefits of synthetic data, the effort to actually create these datasets should be kept at a minimum.
+Thus, to fully exploit the benefits of synthetic data, the effort to actually create these high-quality data sets should be kept at a minimum.
 
@@
 However, the functionality of `mice` is not restricted to the imputation of missing data, but allows to impute any value in the data.
-Thus, `mice` can be utilized for the creation of multiply imputed synthetic datasets.
+Consequently, `mice` can be utilized for the creation of multiply imputed synthetic datasets.
 
-After creating the multiply imputed synthetic data sets, the goal is to obtain valid statistical inferences from them.
+After creating the multiply imputed synthetic data sets, the goal is to obtain valid statistical inferences.
 In the missing data framework, this is done by performing statistical analyses on all imputed data sets, and pooling the results of the analyses according to Rubin's rules [-@rubin_multiple_1987].
@@
 However, valid statistical results can only be obtained under the premise that the statistical properties of the analyses are correct.
-Analyzing synthetic data specically requires appropriate variance estimates.
+Analyzing synthetic data specifically requires appropriate variance estimates.
 Notably, the variance estimator that is suitable for analyzing multiply imputed datasets for missing data is inappropriate when multiply imputed synthetic datasets are analyzed.
-As a result, multiple variance estimators have been proposed to analyze multiply imputed synthetic datasets correctly, that differ according to whether the data consists entirely of synthetic values, or only a subset of the data is synthetic.
+As a result, multiple variance estimators have been proposed to make correct inferences from multiply imputed synthetic datasets.
+These estimators differ according to whether the data consists entirely of synthetic values, or only a subset of the data is synthetic.
 
@@
 The `mice` package has been developed originally for multiple imputation of missing data.
-In this context, the aim is to replace missing values due to nonresponse by plausible values from the posterior predictive distribution of the variable containing the missing values.
+In this context, the aim is to replace missing values due to nonresponse by plausible values from the posterior predictive distribution of the variable containing the missings.
 Doing so, `mice` makes use of fully conditional specification (FCS), which breaks down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, with $k$ the number of variables in the data.
@@
 Note that the predictor matrix $Y_{-j}$ may contain yet imputed values from an earlier imputation step, and thus will be updated after every iteration.
-This procedure is applied $m$ times, resulting in $m$ completed datasets $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $\textbf{D}^{(l)} = (\textbf{Y}_{obs}, Y^{(l)}_{mis}$.
+This procedure is applied $m$ times, resulting in $m$ completed datasets $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $\textbf{D}^{(l)} = (\textbf{Y}_{obs}, Y^{(l)}_{mis})$.
 __MAYBE ADD AN EXAMPLE OF HOW TO DO IT IN `mice`__
@@
 Accordingly, the data consists of values that are to be replaced and values that are to be kept (i.e., $\textbf{Y}^{(l)} = (\textbf{Y}^{(l)}_{rep}, \textbf{Y}_{nrep})$.
-Note the superscript $^{(l)}$ indicating the $l$th synthetic data set.
+Note the superscript $^{(l)}$ indicating the $l$th synthetic data set, with $l = 1, 2, \dots, m$.
 Now, instead of imputing $\textbf{Y}^{(l)}_{mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, we impute $\textbf{Y}^{(l)}_{rep}$ from the posterior distribution of $(Y_{rep} | \textbf{Y}, \textbf{Z}, \theta)$.
-This process results in $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $m$ the number of synthetic datasets.
+This process results in the synthetic data $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$.
 

### 2020-12-03 gerko/BootstrapCI_Validity.Rmd
updated text to serve in MLaRPiS course

@@
 ---
-title: "Confidence validity of bootstrap estimates"
+title: "Confidence validity of bootstrap regression estimates"
 author: "Gerko Vink"
-date: "7/20/2020"
+date: "Markup Languages and Reproducible Programming in Statistics"
 output: 
@@
 # Draw the bootstrap sets
-We use the `replicate()` function to draw `nsim =``r nsim` bootstrap sets from the `origin`
+We use the `replicate()` function to draw `nsim =`$10^4$ bootstrap sets from the 748 rows in the `origin`.
 ```{r cache=TRUE}
@@
 # Results
-Below are the coverages for each of the investigated scenarios. Results are depicted for the coverage of the confidence intervals over the regression estimates for `r nsim` simulations.
+Below are the coverages for each of the investigated scenarios. Results are depicted for the coverage of the confidence intervals over the regression estimates for $10^4$ simulations.
 ```{r}
@@
 
+# Replication
+The replication of these results [can be found here]()
+
+---
+
 END OF DOCUMENT
+
+---
+
+```{r}
+sessionInfo()
+```

### 2020-12-03 mice_synthesizing/paper.Rmd
some changes

@@
 Open science, including open data, has been marked as the future of science [@gewin_data_2016], and the advantages of publicly available research data are numerous [@molloy_open_2011; @walport_brest_sharing_2011].
-Because collecting research data requires an enormous investment both in terms of time and monetary resources, openly accessible research data bears the potential of increasing the scientific returns.
+For example, collecting research data requires an enormous investment both in terms of time and monetary resources.
+Openly accessible research data bears the potential of increasing the scientific returns for the same data collection effort.
 Additionally, the fact that public funds are used for data collection results in increasing demand for the collected data.
 Nevertheless, the possibilities to share research data directly are often very limited due to restrictions with regard to privacy and confidentiality.
-Simply anonimizing the data is not enough to fulfil these requirements [@ohm_broken_2009].
+
+A quick approach to lessen the identities in the data is anonimization.
+However, simply anonimizing the data is not sufficient to fulfill contemporary privacy and confidentiality  requirements [@ohm_broken_2009].
 Over the years, several other techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above a certain threshold or adding random noise [@drechsler_synthetic_2011].
-However, these methods may distort relationships between variables, thereby drastically reducing the data quality and the usability for further research.
+However, these methods may distort relationships between variables, thereby reducing the data quality and the scientific return for re-using the same data for further research.
 
 An alternative solution has been proposed separately by @rubin_statistical_disclosure_1993 and @little_statistical_1993.
-Although their approaches differed to some extent, the general idea is to use actually observed data to generate multiply imputed synthetic datasets that can be freely disclosed.
+Although their approaches differed to some extent, the general idea is to use actually observed data to generate multiply imputed synthetic data sets that can be freely disclosed.
 Based on some imputation model, values from the actually observed data are replaced by multiple draws from the posterior predictive distribution of the observed data.
@@
 Alternatively, the researcher could opt to only replace a subset of the observed data.
-The values that are to be replaced can be complete variables that could be compared with publicly available data sets or registers, such as addresses, or can be certain values that bear a high risk of being disclosive, say, income values above a certain threshold.
+The values that are to be replaced can be complete variables that could be compared with publicly available data sets or registers, such as addresses, or can be certain values that bear a high risk of being disclosive, such as income values above a certain threshold.
+[**aren't synthetic values then not also too disclosive?**]
 
@@
 
-Potentially, this approach could fulfil the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints.
+Potentially, this approach could fulfill the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints.
 However, there is no such thing as a free lunch: data collectors have to put effort in creating high-quality synthetic data.
@@
 The remainder of this paper is organized as follows.
-First, we will shortly describe the `mice` algorithm for the creation of synthetic data that reassures the privacy and confidentiality of the participants.
+First, we will shortly describe the `mice` algorithm for the creation of synthetic data.
+The aim is to generate synthetic sets that reassure the privacy and confidentiality of the participants.
 Second, we will demonstrate a straightforward workflow for imputation of synthetic data with `mice`.
@@
 
-The `mice` package has been developed originally for multiple imputation of missing data.
+The `mice` package has been developed for multiple imputation of missing data.
 In this context, the aim is to replace missing values due to nonresponse by plausible values from the posterior predictive distribution of the variable containing the missings.
-Doing so, `mice` makes use of fully conditional specification (FCS), which breaks down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, with $k$ the number of variables in the data.
+Doing so, `mice` makes use of fully conditional specification (FCS) [**ref to Stef's paper in 2006**], which breaks down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, with $k$ the number of variables in the data.
 Using FCS, for every variable containing missing values a model is constructed, to impute the missing values $Y_{j, mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ on a variable by variable basis.
@@
 
-__DISCUSS ESTIMATORS FOR MISSING DATA HERE, OR AT A LATER POINT__
+__DISCUSS ESTIMATORS FOR MISSING AT A LATER POINT__
 

### 2020-12-04 mice_synthesizing/data_checks.Rmd

--- 2020-08-09 mice_synthesizing/data_checks.Rmd
@@
 
+## Load packages
+
 ```{r, results = F, message = F, warning=F}
@@
 library(magrittr) # pipes
+library(furrr) # parallel imputation
 ```
@@
 
+# Create fully observed data
 ```{r}
+nsyn <- 1000 # number of synthetic datasets
+
+# mice uses the actually observed data for imputing bmi, which is why it is the same in every dataset, and about equal to the true value
 meth <- make.method(mice::boys)
@@
 ```
+
 Now we have a complete dataset, we can overimpute the complete dataset, so that we have synthetic data.
@@
 
+# Create `r nsyn` synthetic data sets
 ```{r, cache = thomcache}
-cart <- meth; cart[!names(meth) %in% 'bmi'] <- "cart"
+cart <- meth
+cart[!names(meth) %in% 'bmi'] <- "cart"
 
-syns <- data %>% 
-  mice(m = 100, 
+plan(multisession)
+syns <- future_map(1:nsyn, function(x) {
+  data %>%
+    mice(m = 1,
          method = cart,
@@
          where = matrix(TRUE, nrow(data), ncol(data)),
-       print = FALSE,
-       seed = 123)
+         print = FALSE)
+}, .progress = FALSE, .options = future_options(seed = as.integer(123)))
+
 ```
 
-Now we have 100 synthetic versions of the same dataset, we can create 100 completed datasets.
+## Complete all synthetic datasets
+
+Now we have `r nsyn` synthetic versions of the same dataset, we can create `r nsyn` completed datasets.
 
 ```{r}
-completed <- complete(syns, action = "all")
+completed <- map(syns, function(x) complete(x))
 ```
 
-Now we have 100 complete synthetic datasets, we can inspect the number of duplicate cases in every synthetic dataset with regard to the original dataset.
+Now we have `r nsyn` complete synthetic datasets, we can inspect the number of duplicate cases in every synthetic dataset with regard to the original dataset.
 
+## Exact duplicate rows
+
+I excluded the variable `bmi`, because something's gone wrong with imputing it.
 ```{r}
-duplicate_obs <- map(completed, function(x) bind_rows(data, x) %>% duplicated)
+duplicate_obs <- map(completed, function(x) {
+  bind_rows(data %>% select(-bmi), x %>% select(-bmi)) %>% duplicated
+  }
+)
 
@@
 
-It appears that in all 100 synthetic versions of the data, there is not a single observation that is an exact copy of the actually observed observations.
-Now, let's find out if the synthetic data resembles the actually observed data (univariately).
-That is, we compare the distributions of the variables in the observed and the synthetic data.
+It appears that in all `r nsyn` synthetic versions of the data, there are seven observations that are an exact copy of actually sampled observations.
+
+However, if we look at the proportion of the observations that has gotten his own value replaced by a value within $0.02$ times the range of the data, we find that between $0.39$ and $0.56$ of the values gets a replacement that is highly similar (`bmi` not counted, as for `bmi` every observation got his own value imputed due to some settings).
+
+```{r}
+out <- map(completed, function(x) {
+  syn_num_vars <- 
+    x %>% 
+      select(where(is.numeric))
+
+  true_num_vars <- 
+    data %>%
+      select(where(is.numeric))
+
+  map2(syn_num_vars, true_num_vars, function(z, y) {
+    abs(z - y) < (max(y) - min(y)) / 50
+  }) %>% bind_cols
+})
+
+map_dfr(out, function(x) {
+  map(x, function(z) sum(z))
+}) %>% colMeans() / nrow(data)
+```
+
+Then, we check how often the nearly exact same value is imputed.
+
+```{r}
+out <- map(completed, function(x) {
+  syn_num_vars <- 
+    x %>% 
+      select(where(is.numeric))
+
+  true_num_vars <- 
+    data %>%
+      select(where(is.numeric))
+
+  map2(syn_num_vars, true_num_vars, function(z, y) {
+    abs(z - y) < (max(y) - min(y)) / 10000
+  }) %>% bind_cols
+})
+
+map_dfr(out, function(x) {
+  map(x, function(z) sum(z))
+}) %>% colMeans() / nrow(data)
+```
+
+```{r}
+out_cat <- map(completed, function(x) {
+  syn_cat_vars <- 
+    x %>%
+      select(-where(is.numeric))
+
+  true_cat_vars <- 
+    data %>%
+      select(-where(is.numeric))
+
+  map2(syn_cat_vars, true_cat_vars, function(z, y) {
+    z == y
+  }) %>% bind_cols
+})
+
+map_dfr(out_cat, function(x) {
+  map(x, function(z) sum(z))
+}) %>% colMeans() / nrow(data)
+```
+
+For the categorical data, the same holds. The majority of all imputations gets his own value replaced, rather than a new value.
+
+## Plot imputed data against the observed data
+
+Now, let's find out if the synthetic data resembles the actually observed data (univariately). That is, we compare the distributions of the variables in the observed and the synthetic data.
 
@@
 Both the histograms and barplots shows that the relative frequencies of the values for the continuous variables or the categories for the categorical variables are highly similar.
+
+<!--
+# Adjusted settings
+
+```{r, cache = thomcache, eval = F}
+syns_adj <- future_map(1:nsyn, function(x) {
+  data %>%
+    mice(m = 1,
+         maxit = 5,
+         method = cart,
+         minbucket = 3,
+         cp = 1e-08,
+         predictorMatrix = pred,
+         where = matrix(TRUE, nrow(data), ncol(data)),
+         print = FALSE)
+}, .progress = FALSE, .options = future_options(seed = as.integer(123)))
+```
+
+```{r, eval = F}
+completed_adj <- map(syns_adj, function(x) complete(x))
+
+completed_adj %>%
+  map(function(x) bind_rows(data, x) %>% duplicated) %>%
+  map_dbl(sum) %>% 
+  sum # total number of duplicated rows over all 100 synthetic datasets
+
+completed_adj %>%
+  map(function(x) bind_rows(data, x) %>% duplicated) %>%
+  lapply(function(x) which(x)) %>%
+  unlist() - nrow(data)
+```
+
+```{r, dpi = 300, fig.fullwidth = TRUE, message = F, eval = F}
+completed_adj %>%
+  map_dfr(function(x) x) %>%
+  bind_rows(., data, .id = "Imputed") %>%
+  mutate(Imputed = as.numeric(Imputed)) %>%
+  select_if(is.numeric) %>%
+  pivot_longer(cols = -"Imputed",
+               names_to = c("Variable")) %>%
+  mutate(Imputed = recode(Imputed, `1` = "Synthetic data", `2` = "Observed data")) %>%
+  ggplot(., mapping = aes(x = value, fill = Imputed)) +
+  geom_histogram(aes(y = ..density..), position = "dodge2", ) +
+  facet_wrap(~ Variable, nrow = 3, ncol = 2, scales = "free") +
+  theme_classic() +
+  scale_fill_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+```
+
+```{r, dpi = 300, fig.fullwidth = TRUE, message = F, eval = F}
+completed_adj %>%
+  map_dfr(function(x) x) %>%
+  bind_rows(., data, .id = "Imputed") %>%
+  select_if(negate(is.numeric)) %>%
+  map_dfr(function(x) as.character(x)) %>%
+  pivot_longer(cols = -"Imputed",
+               names_to = c("Variable")) %>%
+  mutate(Imputed = recode(Imputed, `1` = "Synthetic data", `2` = "Observed data")) %>%
+  ggplot(., mapping = aes(x = value, fill = Imputed, group = Imputed)) +
+  geom_bar(aes(y = ..prop..), position = "dodge2") +
+  facet_wrap(~ Variable, nrow = 3, ncol = 2, scales = "free") +
+  theme_classic() +
+  scale_fill_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+```
+
+-->

### 2020-12-04 mice_synthesizing/mice_updates.Rmd

---
title: "Mice udpates for synthetic data"
author: "Thom Volker"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
bibliography: federated_imp.bib
csl: "apa-6th-edition.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Functions that must be added for working with synthetic data

1. Correct pooling function
2. Correct plot function (that uses the observed data and the imputed data)
3. Passive imputation apparently uses the observed data if available, which is not what we want when synthesizing data. 
4. Function to check the confidentiality of the actual data
5. Update parlmice (can only impute missing data, and does not work with the where matrix).

### 2021-01-11 mice_synthesizing/paper.Rmd
Typo fix + minor revisions.

@@
 A quick approach to lessen the identities in the data is anonimization.
-However, simply anonimizing the data is not sufficient to fulfill contemporary privacy and confidentiality  requirements [@ohm_broken_2009].
-Over the years, several other techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above a certain threshold or adding random noise [@drechsler_synthetic_2011].
-However, these methods may distort relationships between variables, thereby reducing the data quality and the scientific return for re-using the same data for further research.
+However, simply anonimizing the data is not sufficient to fulfil contemporary privacy and confidentiality  requirements [@ohm_broken_2009].
+Over the years, several other techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above a certain threshold or adding random noise to the observed values [@drechsler_synthetic_2011].
+However, these methods may distort relationships between variables, thereby reducing the data quality and the scientific returns for re-using the same data for further research.
 
 An alternative solution has been proposed separately by @rubin_statistical_disclosure_1993 and @little_statistical_1993.
-Although their approaches differed to some extent, the general idea is to use actually observed data to generate multiply imputed synthetic data sets that can be freely disclosed.
+Although their approaches differed to some extent, the overarching procedure is to use actually observed data to generate multiply imputed synthetic datasets that can be freely disclosed.
 Based on some imputation model, values from the actually observed data are replaced by multiple draws from the posterior predictive distribution of the observed data.
-Using this approach, the researcher could replace the observed data set as a whole with multiple synthetic versions.
+Using this approach, the researcher could replace the observed dataset as a whole with multiple synthetic versions.
 Alternatively, the researcher could opt to only replace a subset of the observed data.
-The values that are to be replaced can be complete variables that could be compared with publicly available data sets or registers, such as addresses, or can be certain values that bear a high risk of being disclosive, such as income values above a certain threshold.
-[**aren't synthetic values then not also too disclosive?**]
+The values that are to be replaced can be complete variables that could be compared with publicly available datasets or registers, such as addresses, or can be certain values that bear a high risk of being disclosive, such as income values above a certain threshold.
+[**aren't synthetic values then not also too disclosive?**] <!-- I don't think so, because the synthetic values can only be linked to observed values from other sources if they are exactly equal, or if they are the only value within a certain range.
+The latter might be possible when the number of values is very small, or when the observed value is so extreme that synthetic versions will still be so extreme.
+However, if the other values are synthetic as well, it is quite likely that synthetic information does not apply to the real-world observation.
+I think that the highest risk is in the possibility to extract a range of possible values, which might be uniquely match some other record that is available.
+-->
 
@@
 Instead of replacing just the missing values with multiple draws from the posterior predictive distribution, one could easily *overimpute* any observed sensitive values.
-Similarly to multiple imputation of missing data, the multiple synthetic datasets allow for correct statistical inferences.
-The results of the multiple synthetic data sets should be pooled into a single inference, so that the researcher can draw valid conclusions from the pooled results.
+Similarly to multiple imputation of missing data, the multiple synthetic datasets allow for correct statistical inferences, **regardless of the fact that the "true" value is not included in the analyses**.
+The analyses over multiple synthetic datasets should be pooled into a single inference, so that the researcher can draw valid conclusions from the pooled results.
 To that respect, the variance should reflect the added variability that is induced by the imputation procedure.
-
 Potentially, this approach could fulfill the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints.
@@
 Conversely, if the models used to create the synthetic data are able to preserve the relationships between the variables as in the original data, the synthetic data can be nearly as informative as the observed data.
-Thus, to fully exploit the benefits of synthetic data, the effort to actually create these high-quality data sets should be kept at a minimum.
+Thus, to fully exploit the benefits of synthetic data, the effort to actually create these high-quality datasets should be kept at a minimum.
 
-To minimize additional effort of creating synthetic datasets on behalf of the researcher, software aimed at multiple imputation of missing data can be employed.
+To mitigate additional effort of creating synthetic datasets on behalf of the researcher, software aimed at multiple imputation of missing data can be employed.
 Especially if researchers used this software at an earlier stage in the research process, or acquired familiarity with it during earlier projects, the additional burden of creating synthetic datasets is relatively small.
@@
 
-After creating the multiply imputed synthetic data sets, the goal is to obtain valid statistical inferences.
-In the missing data framework, this is done by performing statistical analyses on all imputed data sets, and pooling the results of the analyses according to Rubin's rules [-@rubin_multiple_1987].
+After creating the multiply imputed synthetic datasets, the goal is to obtain valid statistical inferences.
+In the missing data framework, this is done by performing statistical analyses on all imputed datasets, and pooling the results of the analyses according to Rubin's rules [-@rubin_multiple_1987].
 In the synthetic data framework, the same procedure is followed.

### 2021-01-11 mice_synthesizing/paper.Rmd
Add van buuren fcs reference.

@@
 In this context, the aim is to replace missing values due to nonresponse by plausible values from the posterior predictive distribution of the variable containing the missings.
-Doing so, `mice` makes use of fully conditional specification (FCS) [**ref to Stef's paper in 2006**], which breaks down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, with $k$ the number of variables in the data.
+Doing so, `mice` makes use of fully conditional specification [FCS; @vanbuuren_fully_2006], which breaks down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, with $k$ the number of variables in the data.
 Using FCS, for every variable containing missing values a model is constructed, to impute the missing values $Y_{j, mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ on a variable by variable basis.
@@
 __MAYBE ADD AN EXAMPLE OF HOW TO DO IT IN `mice`__
-
-__DISCUSS ESTIMATORS FOR MISSING AT A LATER POINT__
 

### 2021-01-11 mice_synthesizing/paper.Rmd

@@
 By default, `mice` imputes all values that are coded as missing in the dataset.
-Using the `where` parameter within the mice function, one can choose to impute any value in the dataset.
-As input, the `where` parameter requires a matrix of the same dimensions of the data, (i.e., a $n \times k$ matrix, with $n$ the number of observations in the collected data) containing logical values.
+However, using the `where` parameter within the `mice`-function, one can choose to impute any value in the dataset.
+As input, the `where` parameter requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix, with $n$ the number of observations in the collected data) containing logicals $z_{jk}$ that indicate which cells are selected to have their values replaced.
+This approach allows to overimpute a subset of the observed data, or the observed data as a whole, resulting in a dataset that partly or completely consists of synthetic values.
 

### 2021-01-18 mice_synthesizing/simulations/1.a Synthesize_Mice_Replace_All.R
Create folder for R-files

@@ -115,7 +115,8 @@ boot_cart_maxit_cp_min3 <- bootstrap_boys %>%
                print = F)
 }, .options = future_options(seed = as.integer(123)), .progress = TRUE)
 
-
+# Impute the bootstrapped boys datasets similarly to the previous simulations
+# but with 5 iterations instead of 1
 boot_cart_cp_min3 <- bootstrap_boys %>%
   future_map(function(x) {
     x %>% mice(m = 5, 

### 2021-01-18 mice_synthesizing/simulations/1.b Synthesize_partitioned_data_mice.R

@@ -30,16 +30,25 @@ cart <- rep("cart", ncol(truth))
 names(cart) <- colnames(truth)
 cart['bmi'] <- "~I(wgt / (hgt/100)^2)"
 
+# make sure that wgt & hgt are imputed independent of bmi
 pred <- make.predictorMatrix(truth)
 pred[c("wgt", "hgt"), "bmi"] <- 0
 
+# create bootstrap samples as data.frames
 boot_boys <- truth %>% bootstrap(nsim) %$% strap %>% map(as.data.frame)
 
+# number of partitions
 n.parts <- 5
 
+# create the partitions and name them
 parts <- rep(1/n.parts, n.parts)
 names(parts) <- paste0("P", 1:n.parts)
 
+# draw randomly n.parts partitions, and impute all these partitions using 
+# mice with specified parameters, and complete all these subsets in long
+# format. Bind these partitions and create lists, such that for 1 to m,
+# the data belonging to the same imputation round are bind together (that is,
+# we create m datasets of the same dimension as the original dataset).
 boot_parts <- boot_boys %>%
   future_map(function(x) {
     resample_partition(x, parts) %>%
@@ -59,6 +68,7 @@ boot_parts <- boot_boys %>%
       plyr::dlply(~.imp)
   }, .options = future_options(seed = as.integer(123)), .progress = T)
 
+# Same as the previous, but then with 5 iterations instead of 1. 
 boot_parts_5 <- boot_boys %>%
   future_map(function(x) {
     resample_partition(x, parts) %>%

### 2021-01-18 mice_synthesizing/simulations/1.c synthpop_model_checks.R

@@ -6,7 +6,7 @@ library(magrittr)
 library(broom)
 
 source("/Users/thomvolker/Documents/Federated_imputation/synthpop_synthesizing/1.a Create data - boys complete.R")
-source("/Users/thomvolker/Documents/Federated_imputation/synthpop_synthesizing/1.c Functions.R")
+source("/Users/thomvolker/Documents/Federated_imputation/synthpop_synthesizing/functions.R")
 
 set.seed(1996)
 

### 2021-01-18 mice_synthesizing/mice_updates.Rmd

@@
 ---
-title: "Mice udpates for synthetic data"
+title: "Mice updates for synthetic data"
 author: "Thom Volker"

### 2021-01-18 mice_synthesizing/synthesizing_partially_synthetic_data_rules.Rmd

@@
 ```{r, results=FALSE, message=FALSE, warning=FALSE}
-source("functions.R")
+source("simulations/functions.R")
 library(mice)
@@
 ```{r, include = FALSE}
-load("~/Documents/Federated_imputation/mice_synthesizing/Mice_Synthesizing_cache/html/unnamed-chunk-1_3934488913d24a2b94b74c88c35323d4.RData")
+load("Mice_Synthesizing_cache/html/unnamed-chunk-1_3934488913d24a2b94b74c88c35323d4.RData")
 ```

### 2021-01-23 mice_synthesizing/synthesizing_partially_synthetic_data_rules.Rmd

@@
 
-```{r, include = FALSE}
+```{r, message = F}
 load("Mice_Synthesizing_cache/html/unnamed-chunk-1_3934488913d24a2b94b74c88c35323d4.RData")
@@
 
-Since using `mice`, we basically overimpute the already observed data.
+By using `mice` [@mice], we basically overimpute the already observed data.
 This corresponds to the method of partially synthetic data, although we overimpute every single value.
-Nevertheless, it is worthwhile to check the results when we use the partially synthetic data rules, since the pooling rules to combine this with missing data already exist.
-Therefore, we see how this method performs on the bootstrapped samples from the boys data.
+Nevertheless, it is worthwhile to check the results when we use the partially synthetic data pooling rules as developed by @reiter_partially_inference_2003, especially since these pooling rules have been extended for the case when missing data occurs in the observed dataset.
+Therefore, we examine how this method performs on the bootstrapped samples from the boys data.
 
-We can use the same data as in the previous file, but we need to use a new pooling function, with a different variance calculation, namely
+We can use the same data as in the previous file `Mice_Synthesizing.Rmd`, but we need to use a new pooling function, with a different variance calculation, namely
+
 $$
@@
 with corresponding degrees of freedom
+
 $$
@@
 When we use the default `cart` approach in mice, this yields the following results.
+Note that we used the results of the simulations as specified in the file `simulations/1.a Synthesize_Mice_Replace_All.R`, cached from evaluating this R-file in the R Markdown document `Mice_Synthesizing.Rmd`.
+
+---
 
@@
             "Coverage" = mean(cover)) %>%
-  kable(digits = 3) %>%
+  kable(digits = 3, 
+        caption = "True regression estimates after bootstrapping 
+        and analysing the boys dataset 500 times.") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
@@
   ci_cov(truemodel) %>%
-  kable(digits = 3) %>%
+  kable(digits = 3, 
+        caption = "Synthetic regression estimates after bootstrapping, 
+        synthesizing (with mice default CART settings) and 
+        analysing the boys dataset 500 times.") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
@@
 true_results
+```
+
+Note the fact that the confidence interval coverage of the bootstrapped datasets is somewhat below the nomimal $95\%$ level, due to the fact that the bootstrap variance is somewhat larger than the estimated variances.
+
+```{r}
 synthetic_results
@@
 
+It can be seen in the tables that there is substantial bias in the estimates of the synthetic data estimates, resulting in suboptimal confidence interval coverage.
+The fact that there is bias introduced, might be due to the fact that there is too little variance in the estimates of the synthetic values.
+Therefore, an approach that increases the variance of the estimates might yield estimates that display less bias.
+This can be achieved by decreasing the number of iterations, that is, setting the mice parameter `maxit` to 1, instead of 5.
+Additionally, the complexity parameter `cp` can be set to $10^{−8}$ instead of $10^{−4}$, so that more splits will be made.
+Also, the value of the `rpart` parameter `minbucket`, that is, the minimum number of observations in any terminal node, is set to 3 instead of 5, so that, once again, more splits can be made.
+By means of these changes, the within variance increases, while the between-imputations variability decreases.
+The results with 500 iterations on the same, singly imputed boys dataset can be seen below.
+
+---
+
 # Adjusted CART
-
-Just as in the previous file, we increase the within-imputation variance somewhat, which results in a smaller bias, and therefore, hopefully, more accurate results.
 
@@
   ci_cov(., truemodel) %>%
-  kable(digits = 3) %>%
+  kable(digits = 3,
+        caption = "Synthetic regression estimates after bootstrapping, 
+        synthesizing (with adjusted mice CART settings) and analysing
+        the boys dataset 500 times") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
@@
   ci_cov(., truemodel) %>%
-  kable(digits = 3) %>%
+  kable(digits = 3,
+        caption = "Synthetic regression estimates after bootstrapping, 
+        synthesizing (with adjusted mice CART settings) and analysing
+        the boys dataset 500 times") %>%
   kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
 ```
+
+It can indeed be seen that the bias decreases substantially after altering the complexity parameter `cp` and the minimum number of observations in any final node `minbucket` results in less biased estimates, resulting in higher confidence interval coverage.
+Altering the number of iterations does not seem to make a difference, and in fact, since the missingness pattern is monotone, there is no need to iterate from the posterior distribution.
+
+---
+
+# Visualization of results
+
+```{r, fig.height = 10, fig.width=10}
+true_results <- bootstrap_boys %>%
+  map(~ lm(wgt ~ age + hgt, .x)) %>%
+  map_dfr(~ broom::tidy(.x, conf.int = TRUE)) %>%
+  select(term, estimate)
+
+def_syn_results <- boot_syn %>%
+  select(term, estimate = est)
+
+cart_maxit_cp_min3_syn_results <- boot_cart_maxit_cp_min3 %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool3.syn) %>%
+  select(term, estimate = est)
+
+cart_cp_min3_syn_results <- boot_cart_cp_min3 %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(pool3.syn) %>%
+  select(term, estimate = est)
+
+bind_rows("1. Default synthetic results" = def_syn_results,
+          "2. Maxit; cp; min3 synthetic results" = cart_maxit_cp_min3_syn_results,
+          "3. Cp; min3 synthetic results" = cart_cp_min3_syn_results, 
+          .id = "Method") %>%
+  bind_cols(True = rep(true_results$estimate, 3)) %>%
+  ggplot(aes(x = estimate)) +
+  geom_density(aes(fill = "Synthetic"), alpha = .5) +
+  geom_density(aes(x = True, fill = "True"), alpha = .5) +
+  facet_wrap(term ~ Method, scales = "free") +
+  scale_fill_brewer(palette = "Set1") +
+  theme_minimal() +
+  theme(legend.title = element_blank())
+
+```
+
+Increasing the within-imputation variance, and thereby decreasing the between-imputation variance results in less bias, as shown by the densities of the true and synthetic data estimates, that are more overlapping in the second and third column of the graphs.
+Additionally, it can be seen that the difference between 1 iteration and 5 iterations is negligible.
+
+---
+
+# Session info
+
+```{r}
+sessionInfo()
+```
+
+---
+
+# References

### 2021-01-23 mice_synthesizing/synthesizing_partially_synthetic_data_rules.Rmd

@@
 
+To assess the quality of the synthetic data, we look at the results and the confidence interval coverage of the regression coefficients of the regression model `wgt ~ age + hgt` of 500 synthetic versions of the `boys` data.
+
 ---
@@
 
-Note the fact that the confidence interval coverage of the bootstrapped datasets is somewhat below the nomimal $95\%$ level, due to the fact that the bootstrap variance is somewhat larger than the estimated variances.
+Note the fact that the confidence interval coverage of the bootstrapped datasets is somewhat below the nominal $95\%$ level, due to the fact that the bootstrap variance is somewhat larger than the estimated variances.
 

### 2021-02-11 mice_synthesizing/paper.Rmd
Add imputation procedure.

@@
 As input, the `where` parameter requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix, with $n$ the number of observations in the collected data) containing logicals $z_{jk}$ that indicate which cells are selected to have their values replaced.
-This approach allows to overimpute a subset of the observed data, or the observed data as a whole, resulting in a dataset that partly or completely consists of synthetic values.
+This approach allows to *overimpute* a subset of the observed data, or the observed data as a whole, resulting in a dataset that partly or completely consists of synthetic values.
+Other parameters that are required to be specified are the number of imputations $m$ (`m`), the imputation method (`method`), and the predictor matrix, specifying the predictor variables that are used in the imputation model for every variable $j$ that has some of its values replaced (`predictorMatrix`).
+
+Discuss CART (read Reiter)
+Add text about additional CART parameters cp and minbucket
 

### 2021-02-18 mice_synthesizing/paper.Rmd

@@
 This approach allows to *overimpute* a subset of the observed data, or the observed data as a whole, resulting in a dataset that partly or completely consists of synthetic values.
-Other parameters that are required to be specified are the number of imputations $m$ (`m`), the imputation method (`method`), and the predictor matrix, specifying the predictor variables that are used in the imputation model for every variable $j$ that has some of its values replaced (`predictorMatrix`).
+Other parameters that are required to be specified are the imputation method (`method`), the number of imputations ($m$) and the predictor matrix, specifying the predictor variables that are used in the imputation model for every variable $j$ that has some of its values replaced (`predictorMatrix`).
+
+Choosing an adequate method to impute the data is of the utmost importance, as a flawed imputation model will drastically reduce the data utility in further inferences.
+Therefore, imputation models should be as flexible as possible, as this allows to capture most of the patterns in the data, and to model, possibly unanticipated, data characteristics [@murray_multiple_2018; @rubin_18years_1996].
+Parametric methods, albeit easy to implement in practice, may be too restrictive to capture generally complex patterns in the data, especially in the case of nonlinear relations and interactions between multiple variables.
+Classification and regression trees [CART; @breiman_cart_1984] allow to model more complex patterns in the data, and have therefore been suggested as an appropriate imputation method [@reiter_cart_2005; @burgette_reiter_cart_2010; @doove_buuren_recursive_2014].
+Loosely speaking, CART sequentially splits the predictor space into non-overlapping regions in such a way that the within-region variance is as small as possible after every split.
+As such, CART does not impose any parametric distribution on the data, making it a widely applicable method that allows for a large variety of relationships within the data [@islr_2013].
+Given these appealing characteristics and the call for the use of flexible methods when multiply imputing data, we illustrate the performance of `mice` with CART as the specified imputation method.
 

### 2021-02-18 thesis_proposal_ads.Rmd

---
title: "Proposal ADS"
author: "Thom Volker"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: html_document
bibliography: mice_synthesizing/federated_imp.bib
csl: "mice_synthesizing/apa-6th-edition.csl"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Imputation is no prediction: The importance of the bias/variance trade-off in multiple imputation

The bias-variance trade-off is one of the key concepts in predictive modeling, and the best methods simultaneously achieve low bias and low variance. In this sense, bias refers to model misspecifications that lead to predictions that systematically deviate from the actual data-generating model. Typically, the bias can be reduced at the cost of a small increase in variance. However, one should be careful that the reduce in bias does not inflate the variance, as the consequence hereof would be to model dataset-specific noise (i.e., unpredictable, random deviations) which would deteriorate the quality of out-of-sample predictions.

However, imputation is no prediction, and when the goal is to create sound imputations, the use of an overly flexible method (i.e., one with high variance) might not be problematic [@murray_multiple_2018]. Specifically, flexible methods like predictive mean matching and classification and regression trees (CART) have been proposed in the multiple imputation literature [@reiter_cart_2005; @doove_buuren_recursive_2014]. However, the performance of these methods in the imputation setting is never thoroughly compared to models that generally achieve lower variance (i.e., random forests and/or generalized additive models).

In this thesis project, you will compare the performance of various modeling techniques in terms of confidence validity in the imputation setting. Hereby, we hope to provide guidelines for applied researchers regarding the imputation models that are most suitable in realistic scenarios.

### 2021-04-01 mice_synthesizing/paper.Rmd
Add text on imputation parameters.

@@
 # Introduction
+
+<!-- 
+WHY WE NEED SYNTHETIC DATA - PARAGRAPHS FROM Lazer, D., Pentland, A.
+S., Adamic, L., Aral, S., Barabasi, A.
+L., Brewer, D., Gutmann, M.
+(2009).
+Life in the network: The coming age of computational social science.
+Science, 323(5915), 721.
+http://doi.org/10.1111/j.1083-6101.2007.00367.x
+
+There are also enormous institutional obsta-cles to advancing a computational social sci-ence.
+In  terms  of  approach,  the  subjects  ofinquiry in physics and biology present differentchallenges  to  observation  and  intervention.Quarks and cells neither mind when we dis-cover their secrets nor protest if we alter theirenvironments during the discovery process.
+Asfor infrastructure, the leap from social scienceto a computational social science is larger thanfrom  biology  to  a  computational  biology,largely due to the requirements of distributedmonitoring, permission seeking, and encryp-tion.
+There are fewer resources available in thesocial  sciences,  and  even  the  physical  (andadministrative) distance between social sciencedepartments and engineering or computer sci-ence departments tends to be greater than forthe other sciences.
+Perhaps the thorniest challenges exist on thedata side, with respect to access and privacy.Much of these data are proprietary (e.g., mobilephone and financial transactional information).The debacle following AOL’s public release of“anonymized” search records of many of itscustomers highlights the potential risk to indi-viduals and corporations in the sharing of per-sonal data by private companies (14).
+Robustmodels  of  collaboration  and  data  sharingbetween industry and academia are needed tofacilitate research and safeguard consumer pri-vacy and provide liability protection for corpo-rations.
+More generally, properly managing pri-vacy  issues  is  essential.
+As  the  recent  U.S.National  Research  Council’s  report  on  geo-graphical information system data highlights, itis often possible to pull individual profiles outof even carefully anonymized data (15).
+Lastyear, the U.S.
+National Institutes of Health andthe Wellcome Trust abruptly removed a num-ber of genetic databases from online access(16).
+These databases were seemingly anony-mized,  simply  reporting  the  aggregate  fre-quency of particular genetic markers.
+How-ever, research revealed the potential for de-anonymization, based on the statistical powerof the sheer quantity of data collected fromeach individual in the database (17).Because a single dramatic incident involv-ing a breach of privacy could produce rulesand statutes that stifle the nascent field of com-putational  social  science,  a  self-regulatoryregime of procedures, technologies, and rulesis needed that reduces this risk but preservesresearch potential.
+As a cornerstone of such aself-regulatory regime, U.S.
+Institutional Re-view Boards (IRBs) must increase their techni-cal knowledge to understand the potential forintrusion and individual harm because newpossibilities do not fit their current paradigmsfor harm.
+Many IRBs would be poorly equip-ped to evaluate the possibility that complexdata could be de-anonymized.
+Further, it maybe necessary for IRBs to oversee the creationof  a  secure,  centralized  data  infrastructure.Currently,  existing  data  sets  are  scatteredamong many groups, with uneven skills andunderstanding  of  data  security  and  widelyvarying  protocols.
+Researchers  themselvesmust develop technologies that protect privacywhile preserving data essential for research.These systems, in turn, may prove useful forindustry in managing customer privacy anddata security (18).
+-->
 
@@
 
-Choosing an adequate method to impute the data is of the utmost importance, as a flawed imputation model will drastically reduce the data utility in further inferences.
-Therefore, imputation models should be as flexible as possible, as this allows to capture most of the patterns in the data, and to model, possibly unanticipated, data characteristics [@murray_multiple_2018; @rubin_18years_1996].
+Choosing an adequate method to impute the data is paramount, as a flawed imputation model will drastically reduce the data utility in further inferences.
+Imputation models should be as flexible as possible to capture most of the patterns in the data, and to model, possibly unanticipated, data characteristics [@murray_multiple_2018; @rubin_18years_1996].
 Parametric methods, albeit easy to implement in practice, may be too restrictive to capture generally complex patterns in the data, especially in the case of nonlinear relations and interactions between multiple variables.
@@
 Given these appealing characteristics and the call for the use of flexible methods when multiply imputing data, we illustrate the performance of `mice` with CART as the specified imputation method.
+
+## Synthe*miz*ing in practice
+
+Additional parameters that come with the use of CART are the complexity parameter `cp` and the minimum number of observations in any terminal node `minbucket`, that both restrain the flexibility of the imputation model.
+The values of these parameters ought to adhere to the call for imputation models that are as flexible as possible.
+Hence, the complexity parameter fixed at `cp = 1e-08` rather than the default `1e-08` and the minimum number of observations in each terminal node set at `minbucket = 3` rather than the default 5.
+The bias and variance of the final estimates justified these decisions.
+Additionally, the number of imputations was set to $m = 5$.
 

### 2021-04-05 mice_synthesizing/paper.Rmd
Update imputation how to

@@
 The remainder of this paper is organized as follows.
-First, we will shortly describe the `mice` algorithm for the creation of synthetic data.
+First, the `mice` algorithm for the creation of synthetic data will be shortly explained.
 The aim is to generate synthetic sets that reassure the privacy and confidentiality of the participants.
-Second, we will demonstrate a straightforward workflow for imputation of synthetic data with `mice`.
+Second, a straightforward workflow for imputation of synthetic data with `mice` will be demonstrated.
 The third step is to summarize the variance estimators that have been proposed in the past.
-Finally, we will assess which variance estimator provides valid inferences from the synthetic data.
+Finally, it will be assessed which variance estimator provides valid inferences from the synthetic data.
 
@@
 This procedure is applied $m$ times, resulting in $m$ completed datasets $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $\textbf{D}^{(l)} = (\textbf{Y}_{obs}, Y^{(l)}_{mis})$.
-__MAYBE ADD AN EXAMPLE OF HOW TO DO IT IN `mice`__
 
 This approach can be straightforwardly extended to a synthetic data framework.
-However, rather than imputing missing data, we overimpute actually observed data, that is, we replace observed values by multiple imputations.
+However, rather than imputing missing data, the actually observed data is overimputed, that is, the observed values are replaced by multiple imputations.
 For simplicity, assume that the data is completely observed (i.e., $\textbf{Y} = \textbf{Y}_{obs}$).
@@
 Note the superscript $^{(l)}$ indicating the $l$th synthetic data set, with $l = 1, 2, \dots, m$.
-Now, instead of imputing $\textbf{Y}^{(l)}_{mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, we impute $\textbf{Y}^{(l)}_{rep}$ from the posterior distribution of $(Y_{rep} | \textbf{Y}, \textbf{Z}, \theta)$.
+Now, instead of imputing $\textbf{Y}^{(l)}_{mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, $\textbf{Y}^{(l)}_{rep}$ is imputed from the posterior distribution of $(Y_{rep} | \textbf{Y}, \textbf{Z}, \theta)$.
 This process results in the synthetic data $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$.
@@
 As such, CART does not impose any parametric distribution on the data, making it a widely applicable method that allows for a large variety of relationships within the data [@islr_2013].
-Given these appealing characteristics and the call for the use of flexible methods when multiply imputing data, we illustrate the performance of `mice` with CART as the specified imputation method.
+Given these appealing characteristics and the call for the use of flexible methods when multiply imputing data, the performance of `mice` with CART as the specified imputation method will be illustrated.
+
+Additional parameters that come with the use of CART are the complexity parameter `cp` and the minimum number of observations in any terminal node `minbucket`, that both restrain the flexibility of the imputation model.
+Appropriate values for these parameters, as well as the input for the `predictorMatrix`, depend on the data at hand.
+Hence, the specification of these parameters will be illustrated using an actual dataset.
+The `boys` data [@fredriks_boys_2000] that is in-built within the `mice` package is used to illustrate the specification of these parameters accordingly.
+**DETERMINE WHETHER THIS DATASET SUFFICES; BECAUSE IMPUTATION MIGHT MAKE THE DATA ARTIFICIALLY SIMILAR BEFORE SYNTHESIZING, MAKING SYNTHESIZING TOO EASY** Unfortunately, this dataset does not differ from the vast majority of collected datasets, in the sense that it suffers from missing data as well.
+For simplicity, the data is completed using the default `mice` imputation model to create a single, fully observed dataset.
+The data consists of the values of $`r nrow(mice::boys)`$ Dutch boys on the following $`r ncol(mice::boys)`$ variables: age (in years), height (in cm), weight (in kg), body mass index, heid circumference (in cm), Genital Tanner stage (G1-G5), testicular volume (in ml) and region.
+
+The values of the parameters `cp` and `minbucket` ought to adhere to the call for imputation models that are as flexible as possible.
+Accordingly, the complexity parameter is fixed at `cp = 1e-08` rather than the default value `1e-08` and the minimum number of observations in each terminal node is set at `minbucket` $= 3$ rather than the default value $5$.
+The bias and variance of the final estimates justified these decisions.
+The predictor matrix was specified in such a way that
+Additionally, the number of imputations was set to $m = 5$.
 
 ## Synthe*miz*ing in practice
-
-Additional parameters that come with the use of CART are the complexity parameter `cp` and the minimum number of observations in any terminal node `minbucket`, that both restrain the flexibility of the imputation model.
-The values of these parameters ought to adhere to the call for imputation models that are as flexible as possible.
-Hence, the complexity parameter fixed at `cp = 1e-08` rather than the default `1e-08` and the minimum number of observations in each terminal node set at `minbucket = 3` rather than the default 5.
-The bias and variance of the final estimates justified these decisions.
-Additionally, the number of imputations was set to $m = 5$.
 

### 2021-04-08 mice_synthesizing/paper.Rmd
Small adjustment to intro, and some additions to regular body of text.

@@
 Open science, including open data, has been marked as the future of science [@gewin_data_2016], and the advantages of publicly available research data are numerous [@molloy_open_2011; @walport_brest_sharing_2011].
-For example, collecting research data requires an enormous investment both in terms of time and monetary resources.
+Collecting research data requires an enormous investment both in terms of time and monetary resources.
 Openly accessible research data bears the potential of increasing the scientific returns for the same data collection effort.
 Additionally, the fact that public funds are used for data collection results in increasing demand for the collected data.
-Nevertheless, the possibilities to share research data directly are often very limited due to restrictions with regard to privacy and confidentiality.
+Nevertheless, the possibilities to distribute research data directly are often very limited due to restrictions with regard to privacy and confidentiality.
+Altough these regulations are much needed, privacy constraints are also ranked among the toughest challenges to overcome in the advancement of computational social science [@lazer_life_2009].
 
-A quick approach to lessen the identities in the data is anonimization.
-However, simply anonimizing the data is not sufficient to fulfil contemporary privacy and confidentiality  requirements [@ohm_broken_2009].
+Anonimizing the data might seem a quick and appealing approach to limit the identifyability of participants.
+However, this approach is not sufficient to fulfil contemporary privacy and confidentiality requirements [@ohm_broken_2009; @national_putting_2007].
 Over the years, several other techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above a certain threshold or adding random noise to the observed values [@drechsler_synthetic_2011].
@@
 
+**NEXT TWO PARAGRAPHS ARE PROBABLY NOT CORRECT YET; NOTE TO SELF: UPDATE THIS**
+
 The `mice` package has been developed for multiple imputation of missing data.
@@
 For simplicity, assume that the data is completely observed (i.e., $\textbf{Y} = \textbf{Y}_{obs}$).
-Following the notation of @reiter_raghunathan_multiple_2007, let $Z_j = 1$ if any of the values of unit $j$ are to be replaced by imputations, and $Z_j = 0$ otherwise, with $\textbf{Z} = (Z_1, Z_2, \dots, Z_n)$.
-Accordingly, the data consists of values that are to be replaced and values that are to be kept (i.e., $\textbf{Y}^{(l)} = (\textbf{Y}^{(l)}_{rep}, \textbf{Y}_{nrep})$.
-Note the superscript $^{(l)}$ indicating the $l$th synthetic data set, with $l = 1, 2, \dots, m$.
-Now, instead of imputing $\textbf{Y}^{(l)}_{mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, $\textbf{Y}^{(l)}_{rep}$ is imputed from the posterior distribution of $(Y_{rep} | \textbf{Y}, \textbf{Z}, \theta)$.
+Following the notation of @reiter_raghunathan_multiple_2007, let $Z_i = 1$ if any of the values of unit $i$ are to be replaced by imputations, and $Z_i = 0$ otherwise, with $\textbf{Z} = (Z_1, Z_2, \dots, Z_n)$.
+Accordingly, the data consists of values that are to be replaced and values that are to be kept (i.e., $\textbf{Y} = (\textbf{Y}_{rep}, \textbf{Y}_{nrep})$.
+Now, instead of imputing $\textbf{Y}_{mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, $\textbf{Y}_{rep}$ is imputed from the posterior distribution of $P(Y^{(l)}_{j, rep} | \textbf{Y}^{(l)}_{-j}, \textbf{Z}, \theta)$, where $l$ is an indicator for the synthetic dataset ($l = 1, 2, \dots, m$).
+Note that synthetic values that are imputed at an earlier step can be used for imputing variable $j$.
 This process results in the synthetic data $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$.
@@
 However, using the `where` parameter within the `mice`-function, one can choose to impute any value in the dataset.
-As input, the `where` parameter requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix, with $n$ the number of observations in the collected data) containing logicals $z_{jk}$ that indicate which cells are selected to have their values replaced.
+As input, the `where` parameter requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix, with $n$ the number of observations in the collected data) containing logicals $z_{ij}$ that indicate which cells are selected to have their values replaced.
 This approach allows to *overimpute* a subset of the observed data, or the observed data as a whole, resulting in a dataset that partly or completely consists of synthetic values.
@@
 The `boys` data [@fredriks_boys_2000] that is in-built within the `mice` package is used to illustrate the specification of these parameters accordingly.
-**DETERMINE WHETHER THIS DATASET SUFFICES; BECAUSE IMPUTATION MIGHT MAKE THE DATA ARTIFICIALLY SIMILAR BEFORE SYNTHESIZING, MAKING SYNTHESIZING TOO EASY** Unfortunately, this dataset does not differ from the vast majority of collected datasets, in the sense that it suffers from missing data as well.
+**DETERMINE WHETHER THIS DATASET SUFFICES; BECAUSE IMPUTATION MIGHT MAKE THE DATA ARTIFICIALLY SIMILAR BEFORE SYNTHESIZING, MAKING SYNTHESIZING TOO EASY** Unfortunately, this dataset does not differ from the vast majority of collected datasets, in the sense that it suffers from missing data.
 For simplicity, the data is completed using the default `mice` imputation model to create a single, fully observed dataset.
-The data consists of the values of $`r nrow(mice::boys)`$ Dutch boys on the following $`r ncol(mice::boys)`$ variables: age (in years), height (in cm), weight (in kg), body mass index, heid circumference (in cm), Genital Tanner stage (G1-G5), testicular volume (in ml) and region.
+The data consists of the values of $`r nrow(mice::boys)`$ Dutch boys on the following $`r ncol(mice::boys)`$ variables: age (in years), height (in cm), weight (in kg), body mass index (BMI), head circumference (in cm), Genital Tanner stage (G1-G5), testicular volume (in ml) and region.
 
@@
 Accordingly, the complexity parameter is fixed at `cp = 1e-08` rather than the default value `1e-08` and the minimum number of observations in each terminal node is set at `minbucket` $= 3$ rather than the default value $5$.
-The bias and variance of the final estimates justified these decisions.
-The predictor matrix was specified in such a way that
-Additionally, the number of imputations was set to $m = 5$.
+By allowing for more complexity in the imputation model, bias in the estimates from the synthetic dataset is reduced.
+The predictor matrix was specified so that BMI was not imputed from a model, but calculated from the imputed height and weight values ($BMI = kg / m^2$), an approach called passive imputation.
+Additionally, BMI is excluded as a predictor for weight and height, because BMI values are directly dependent on the values of weight and height.
+All other variables $Y_{-j}$ are used as predictors for variable $Y_j$.
+Additionally, the number of imputations is set to $m = 5$.
 

### 2021-04-09 mice_synthesizing/passive_imp_reprex.Rmd
passive imputation reprex

---
title: "Passive imputation reprex"
author: "Thom Volker"
date: "4/9/2021"
output: html_document
---

Load the required packages.

```{r}
library(reprex)
library(mice)
library(tidyverse)
```

Create a complete dataset.

```{r}
df <- boys %>% mice(m=1, printFlag = FALSE) %>% complete()
str(df)
```

Specify an imputation method.

```{r}
mtd <- make.method(df, 
                   where = matrix(1, nrow(df), ncol(df)),
                   defaultMethod = c("cart", "cart", "cart", "cart"))
mtd["bmi"] <- "~ I(wgt / (hgt/100)^2)"
```

Create synthetic data.

```{r}
imp <- df %>% mice(m = 5, 
                   method = mtd, 
                   where = matrix(1, nrow(df), ncol(df)),
                   printFlag = FALSE)
```

Create the datasets containing the synthetic data. Now, the values for bmi are actually calculated from the "real" dataset, rather than from the synthetic height and weight values.

```{r}
comp <- complete(imp, action = "all", include = T)

map_dfc(comp, function(x) {
  d <- head(x)
  c(d$bmi,d$wgt / (d$hgt/100)^2)
}) %>% bind_cols(imp = rep(c("imputed", "calculated"), each = 6), .)
```

Now, you see that the actually imputed values are just calculated from the actually observed data every time, while the calculated values can be created from the synthetic height and weight values (i.e., the values that are ought to be imputed), but are imputed as the bmi values.

```{r}
df_mis <- df
df_mis[1:2, c("hgt", "wgt", "bmi")] <- NA

imp_mis <- df_mis %>% mice(m = 5, 
                           method = mtd, 
                           where = matrix(1, nrow(df), ncol(df)),
                           printFlag = FALSE)

comp_mis <- complete(imp_mis, action = "all", include = TRUE)

map_dfc(comp_mis, function(x) {
  d <- head(x)
  c(d$bmi,d$wgt / (d$hgt/100)^2)
}) %>% bind_cols(imp = rep(c("imputed", "calculated"), each = 6), .)
```

If the values are missing, the function does work accordingly. So apparently, passive imputation uses the actual data if present, and ignores the where matrix.

### 2021-04-27 mice_synthesizing/mice_append.Rmd

---
title: "Mice - append empty data.frame"
author: "Thom Volker"
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
---

# Load required packages

```{r}
library(mice) # imputations
library(tidyverse) # tidy data
library(modelr) # bootstrap
library(magrittr) # pipe
library(furrr) # parallel mapping
```

# Set seed

```{r}
set.seed(123) # seed for reproducibility
```

# Create a single completely observed dataset

```{r}
comp_meth <- make.method(boys)
comp_meth['bmi'] <- "~I(wgt/(hgt/100)^2)"

comp_pred <- make.predictorMatrix(boys)
comp_pred[c("wgt", "hgt"), "bmi"] <- 0

truth <- boys %>% 
  mice(seed = 123, 
       comp_meth, 
       m = 1, 
       print = FALSE) %>% 
  complete()
```

# Create the true model

```{r}
model <- function(data) lm(wgt ~ age + hgt, data)

truemodel <- truth %>% model

coefs <- coef(truemodel)

```

# Initialize parallel processing

```{r}
plan(multisession)
```

# Specify number of simulations - 100 for now

```{r}
nsim <- 100
```

# CART method and predictor matrix for synthesizing

```{r}
# cart method, all variables are imputed by means of cart
cart <- rep("cart", ncol(truth))
names(cart) <- colnames(truth)
cart['bmi'] <- "~I(wgt / (hgt/100)^2)"

# alter the predictor matrix such that imputations for bmi do not flow
# back into the predictions for wgt and hgt
pred <- make.predictorMatrix(truth)
pred[c("wgt", "hgt"), "bmi"] <- 0
```

# Bootstrap set of the boys data

```{r}
bootstrap_boys <- bootstrap(truth, nsim) %$% strap %>% map(as.data.frame)
```

# Simulate

```{r, results = F, cache = TRUE, cache.lazy = FALSE}
# 1 iteration, m = 5
boot_cart_append_maxit1_cp_min3 <- bootstrap_boys %>%
  future_map(function(x) {
    x %>% 
      bind_rows(data.frame(matrix(NA, nrow(.), ncol(.), dimnames = list(NULL, colnames(.))))) %>%
      mice(m = 5,
           maxit = 1,
           method = cart,
           minbucket = 3, 
           cp = 1e-08,
           predictorMatrix = pred,
           print = F)
  }, .options = future_options(seed = as.integer(123)), .progress = FALSE)

# 50 iterations, m = 5
boot_cart_append_maxit50_cp_min3 <- bootstrap_boys %>%
  future_map(function(x) {
    x %>% 
      bind_rows(data.frame(matrix(NA, nrow(.), ncol(.), dimnames = list(NULL, colnames(.))))) %>%
      mice(m = 5,
           maxit = 50,
           method = cart,
           minbucket = 3, 
           cp = 1e-08,
           predictorMatrix = pred,
           print = F)
  }, .options = future_options(seed = as.integer(123)), .progress = FALSE)
```

# Pooling rules and coverage function

```{r}
# FULLY SYNTHETIC POOL FUNCTION
pool.syn <- function(mira) {

  if(class(mira)[1] == "mira") { # if the input object is of class mira
    fitlist <- mira %$% analyses # extract the analyses from the mira object
  }
  else {                         # and otherwise, just take the input list
    fitlist <- mira
    }

  m <- length(fitlist)           # number of imputations

  pooled <- fitlist %>% 
    map_dfr(broom::tidy) %>%     # tidy estimates
    group_by(term) %>%           # group per variable
    summarise(est     = mean(estimate),
              bm      = sum((estimate - est)^2) / (m - 1),
              ubar    = mean(std.error^2),
              var_u   = (1 + 1/m) * bm - ubar,
              var     = if_else(var_u > 0, var_u, ubar), # restrict variance to be positive
              df      = max(1, (m - 1) * (1 - ubar / (bm + bm/m))^2), # restrict df > 1
              lower   = est - qt(.975, df) * sqrt(var),
              upper   = est + qt(.975, df) * sqrt(var), .groups = 'drop')
  pooled
}

ci_cov <- function(pooled, true_fit = NULL, coefs = NULL, vars = NULL) {

  if (!is.null(true_fit)) {
    coefs <- coef(true_fit)
    vars   <- diag(vcov(true_fit))
  }

  nsim <- nrow(pooled) / length(coefs)

  pooled %>% mutate(true_coef = rep(coefs, nsim),
                    true_var  = rep(vars, nsim),
                    cover     = lower < true_coef & true_coef < upper) %>%
    group_by(term) %>%
    summarise("True Est" = unique(true_coef),
              "Syn Est"  = mean(est),
              "Bias"     = mean(est - true_coef),
              "True SE"  = unique(sqrt(true_var)),
              "Syn SE"   = mean(sqrt(var)),
              "df"       = mean(df),
              "Lower"    = mean(lower),
              "Upper"    = mean(upper),
              "CIW"      = mean(upper - lower),
              "Coverage" = mean(cover), .groups = "drop")
}
```

# Results of simulation

```{r}
library(kableExtra)

boot_cart_append_maxit1_cp_min3 %>%
  map_dfr(function(x) {
    x %>%
      complete(action = "all") %>%
      map(~model(.x[749:1496,])) %>%
      pool.syn
  }) %>%
  ci_cov(., truemodel)   %>%
  kable(digits = 3,
        caption = "Synthesizing by appending an empty dataframe under the bootstrap samples with 1 iteration") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

boot_cart_append_maxit50_cp_min3 %>%
  map_dfr(function(x) {
    x %>%
      complete(action = "all") %>%
      map(~model(.x[749:1496,])) %>%
      pool.syn
  }) %>%
  ci_cov(., truemodel) %>%
  kable(digits = 3,
        caption = "Synthesizing by appending an empty dataframe under the bootstrap samples with 50 iteration") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

# What happens when running mice for 500 iterations

```{r, cache = TRUE, cache.lazy = FALSE}
iter500 <- boys %>%
  bind_rows(data.frame(matrix(NA, nrow(.), ncol(.), dimnames = list(NULL, colnames(.))))) %>%
  mice(m = 5,
       maxit = 500,
       method = cart,
       minbucket = 3, 
       cp = 1e-08,
       predictorMatrix = pred,
       print = F)

plot(iter500)
```

### 2021-05-13 ads_thesis/simulation_replication.Rmd
simulation replication ADS thesis

---
title: "ADS Thesis simulation"
author: 
- Thom Volker
- Utrecht University
date: "`r format(Sys.time(), '%d-%m-%Y')`"
output: 
  html_document:
    theme: spacelab
    highlight: tango
    toc: true
    toc_depth: 2
    toc_float: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load packages

```{r, results = F, message = F}
library(mice)
library(tidyverse)
library(furrr)
library(magrittr)
library(knitr)
```

# Read in the data

```{r}
data_url <- "https://raw.githubusercontent.com/gerkovink/Synthetic_ADS/main/Data/diabetes.csv"
data <- read_csv(url(data_url), 
                 col_types = cols(Pregnancies = col_integer(), 
                                  Glucose = col_integer(), 
                                  BloodPressure = col_integer(), 
                                  SkinThickness = col_integer(), 
                                  Insulin = col_integer(), 
                                  Age = col_integer(), 
                                  Outcome = col_factor(levels = c("1", "0"))))

data <- data[!data$BMI == 0,]
```

# True model

```{r}
fit <- glm(Outcome ~ Pregnancies + Glucose + BMI, 
           family = binomial(link = "logit"), 
           data = data)

coef(fit)
sqrt(diag(vcov(fit)))
broom::tidy(fit)
```

# Synthetic data model

```{r}
mod1 <- c(Pregnancies              = "pmm", 
          Glucose                  = "norm", 
          BloodPressure            = "norm", 
          SkinThickness            = "pmm", 
          Insulin                  = "pmm", 
          BMI                      = "norm", 
          DiabetesPedigreeFunction = "pmm", 
          Age                      = "pmm", 
          Outcome                  = "logreg.boot")

mod2 <- c(Pregnancies              = "cart", 
          Glucose                  = "cart", 
          BloodPressure            = "cart", 
          SkinThickness            = "cart", 
          Insulin                  = "cart", 
          BMI                      = "cart", 
          DiabetesPedigreeFunction = "cart", 
          Age                      = "cart", 
          Outcome                  = "cart")

pred <- make.predictorMatrix(data)
```

# Simulate

```{r, cache = TRUE, cache.lazy = FALSE}
nsim <- 100
plan(multisession)

syn1 <- future_map(1:nsim, function(x) {
  data %>%
    mice(m = 5,
         method = mod1,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)

syn1_maxit1 <- future_map(1:nsim, function(x) {
  data %>%
    mice(m = 5, 
         maxit = 1,
         method = mod1,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
```

```{r, cache = TRUE, cache.lazy = FALSE}
syn2 <- future_map(1:nsim, function(x) {
  data %>%
    mice(m = 5,
         method = mod2,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)

syn2_maxit1 <- future_map(1:nsim, function(x) {
  data %>%
    mice(m = 5, 
         maxit = 1,
         method = mod2,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
```

```{r, cache = TRUE, cache.lazy = FALSE}
syn2_cp <- future_map(1:nsim, function(x) {
  data %>%
    mice(m = 5,
         method = mod2,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         cp = 1e-32,
         minbucket = 3,
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)

syn2_cp_maxit1 <- future_map(1:nsim, function(x) {
  data %>%
    mice(m = 5, 
         maxit = 1,
         method = mod2,
         predictorMatrix = pred,
         where = matrix(TRUE, nrow(.), ncol(.)),
         cp = 1e-32,
         minbucket = 3,
         print = FALSE)
}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
```

# Source functions file for pooling

```{r}
source("~/Documents/Federated_imputation/mice_synthesizing/simulations/functions.R")
```

# Synthetic data estimates

```{r, include = F}
library(kableExtra)
```

```{r}
syn1 %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ Pregnancies + Glucose + BMI, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

syn1_maxit1 %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ Pregnancies + Glucose + BMI, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

```{r}
syn2 %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ Pregnancies + Glucose + BMI, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

syn2_maxit1 %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ Pregnancies + Glucose + BMI, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

```{r}
syn2_cp %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ Pregnancies + Glucose + BMI, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))

syn2_cp_maxit1 %>%
  map(function(x) {
    x %$% 
      glm(Outcome ~ Pregnancies + Glucose + BMI, 
          family = binomial(link = "logit"))
    }) %>%
  map_dfr(pool3.syn) %>%
  ci_cov(., fit) %>%
  kable(digits = 3) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

### 2021-09-14 mice_synthesizing/simulations/functions.R
Correct df formula.

@@ -85,7 +85,7 @@ pool3.syn <- function(mira) {
               bm      = sum((estimate - est)^2) / (m - 1),
               ubar    = mean(std.error^2),
               var     = ubar + bm/m, # new variance estimate
-              df      = (m - 1) * (1 + (ubar * m)/bm), # and new df estimate
+              df      = (m - 1) * (1 + (ubar * m)/bm)^2, # and new df estimate
               lower   = est - qt(.975, df) * sqrt(var),
               upper   = est + qt(.975, df) * sqrt(var), .groups = 'drop') %>%
     arrange(factor(term, levels = vars))
@@ -115,4 +115,27 @@ ci_cov <- function(pooled, true_fit = NULL, coefs = NULL, vars = NULL) {
               "Upper"    = mean(upper),
               "CIW"      = mean(upper - lower),
               "Coverage" = mean(cover), .groups = "drop")
+}
+
+make.coefficients <- function(r2, ratio, rho, model = c("normal", "logit", "probit")) {
+  if (model == "normal") {
+    var_y <- r2
+  }
+  else if (model == "logit") {
+    var_y <- (r2 * pi^2 / 3) / (1 - r2)
+  }
+  sqrt(var_y / sum(ratio %*% t(ratio) * rho)) * ratio
+}
+
+generate.data <- function(r2, betas, rho, n, model = c("normal", "logit", "probit")) {
+  
+  X <- mvrnormArma(n, mu = rep(0, length(betas)), sigma = rho)
+  
+  if (model == "normal") {
+    Y <- X %*% betas + rnorm(n = n, mean = 0, sd = sqrt(1 - r2))
+  }
+  if (model == "logit") {
+    Y <- rbinom(n, 1, 1 / (1 + exp(-(X %*% betas))))
+  }
+  bind_cols(X = as.data.frame(X), Y = Y)
 }

### 2021-09-14 ads_thesis/simulation_replication.Rmd
Add ads thesis replication.

@@
                                   Age = col_integer(), 
-                                  Outcome = col_factor(levels = c("1", "0"))))
-
-data <- data[!data$BMI == 0,]
+                                  Outcome = col_factor(levels = c("0", "1"))))
 ```
@@
 ```{r}
-fit <- glm(Outcome ~ Pregnancies + Glucose + BMI, 
+fit <- glm(Outcome ~ BMI + Glucose + Pregnancies, 
            family = binomial(link = "logit"), 
@@
 ```{r, cache = TRUE, cache.lazy = FALSE}
-nsim <- 100
+nsim <- 500
 plan(multisession)
-
-syn1 <- future_map(1:nsim, function(x) {
-  data %>%
-    mice(m = 5,
-         method = mod1,
-         predictorMatrix = pred,
-         where = matrix(TRUE, nrow(.), ncol(.)),
-         print = FALSE)
-}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
-
-syn1_maxit1 <- future_map(1:nsim, function(x) {
-  data %>%
-    mice(m = 5, 
-         maxit = 1,
-         method = mod1,
-         predictorMatrix = pred,
-         where = matrix(TRUE, nrow(.), ncol(.)),
-         print = FALSE)
-}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
 ```
@@
 ```{r, cache = TRUE, cache.lazy = FALSE}
-syn2 <- future_map(1:nsim, function(x) {
-  data %>%
-    mice(m = 5,
-         method = mod2,
-         predictorMatrix = pred,
-         where = matrix(TRUE, nrow(.), ncol(.)),
-         print = FALSE)
-}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
-
 syn2_maxit1 <- future_map(1:nsim, function(x) {
@@
 ```{r, cache = TRUE, cache.lazy = FALSE}
-syn2_cp <- future_map(1:nsim, function(x) {
-  data %>%
-    mice(m = 5,
-         method = mod2,
-         predictorMatrix = pred,
-         where = matrix(TRUE, nrow(.), ncol(.)),
-         cp = 1e-32,
-         minbucket = 3,
-         print = FALSE)
-}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
-
 syn2_cp_maxit1 <- future_map(1:nsim, function(x) {
@@
 ```{r}
-syn1 %>%
+syn2_maxit1 %>%
   map(function(x) {
     x %$% 
-      glm(Outcome ~ Pregnancies + Glucose + BMI, 
-          family = binomial(link = "logit"))
-    }) %>%
-  map_dfr(pool3.syn) %>%
-  ci_cov(., fit) %>%
-  kable(digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
-
-syn1_maxit1 %>%
-  map(function(x) {
-    x %$% 
-      glm(Outcome ~ Pregnancies + Glucose + BMI, 
+      glm(Outcome ~ BMI + Glucose + Pregnancies, 
           family = binomial(link = "logit"))
@@
 ```{r}
-syn2 %>%
+syn2_cp_maxit1 %>%
   map(function(x) {
     x %$% 
-      glm(Outcome ~ Pregnancies + Glucose + BMI, 
-          family = binomial(link = "logit"))
-    }) %>%
-  map_dfr(pool3.syn) %>%
-  ci_cov(., fit) %>%
-  kable(digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
-
-syn2_maxit1 %>%
-  map(function(x) {
-    x %$% 
-      glm(Outcome ~ Pregnancies + Glucose + BMI, 
+      glm(Outcome ~ BMI + Glucose + Pregnancies, 
           family = binomial(link = "logit"))
@@
 
-```{r}
-syn2_cp %>%
+```{r, cache = TRUE, cache.lazy = FALSE}
+syn2_boot <- future_map(1:nsim, function(x) {
+  data[sample(1:nrow(data), replace = TRUE), ] %>%
+    mice(m = 10, 
+         maxit = 1,
+         method = mod2,
+         predictorMatrix = pred,
+         where = matrix(TRUE, nrow(.), ncol(.)),
+         cp = 0.0001,
+         minbucket = 3,
+         print = FALSE)
+}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
+
+syn2_cp_boot <- future_map(1:nsim, function(x) {
+  data[sample(1:nrow(data), replace = TRUE), ] %>%
+    mice(m = 5, 
+         maxit = 1,
+         method = mod2,
+         predictorMatrix = pred,
+         where = matrix(TRUE, nrow(.), ncol(.)),
+         cp = 1e-32,
+         minbucket = 3,
+         print = FALSE)
+}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
+
+true_fits <- map(1:nsim, ~glm(Outcome ~ BMI + Glucose + Pregnancies,
+                 family = binomial(link = "logit"), data = data[sample(1:nrow(data), replace = TRUE),]))
+
+map_dfr(true_fits, function(x) {
+  x %>% broom::tidy(conf.int = TRUE) %>% mutate(cov = conf.low < coef(fit) & coef(fit) < conf.high)
+}) %>% 
+  group_by(term) %>%
+  summarise(est = mean(estimate),
+                 se  = mean(std.error),
+                 ciw = mean(conf.high - conf.low),
+                 cov = mean(cov)) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+syn2_boot %>%
      map(function(x) {
     x %$% 
-      glm(Outcome ~ Pregnancies + Glucose + BMI, 
+      glm(Outcome ~ BMI + Glucose + Pregnancies, 
           family = binomial(link = "logit"))
@@
 
-syn2_cp_maxit1 %>%
+syn2_cp_boot %>%
    map(function(x) {
     x %$% 
-      glm(Outcome ~ Pregnancies + Glucose + BMI, 
+      glm(Outcome ~ BMI + Glucose + Pregnancies, 
           family = binomial(link = "logit"))
@@
 ```
+
+# Zero's replaced by imputation
+
+```{r, cache=TRUE, cache.lazy=FALSE}
+data.imp <- 
+  data %>%
+  lapply(FUN = function(x) {
+  ifelse(is.numeric(x) & x == 0, NA, x)
+  }) %>%
+  as.data.frame() %>%
+  mutate(Outcome = factor(Outcome, labels = c("0", "1"))) %>%
+  mice(m = 1, maxit = 50, method = "pmm") %>%
+  complete()
+
+fit.imp <- glm(Outcome ~ BMI + Glucose + Pregnancies,
+               family = binomial(link = "logit"),
+               data = data.imp)
+
+syn2.boot.imp <- future_map(1:nsim, function(x) {
+  data.imp[sample(1:nrow(data.imp), replace = TRUE), ] %>%
+    mice(m = 10, 
+         maxit = 1,
+         method = mod2,
+         predictorMatrix = pred,
+         where = matrix(TRUE, nrow(.), ncol(.)),
+         cp = 0.0001,
+         minbucket = 3,
+         print = FALSE)
+}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
+
+syn2.cp.boot.imp <- future_map(1:nsim, function(x) {
+  data.imp[sample(1:nrow(data.imp), replace = TRUE), ] %>%
+    mice(m = 10, 
+         maxit = 1,
+         method = mod2,
+         predictorMatrix = pred,
+         where = matrix(TRUE, nrow(.), ncol(.)),
+         cp = 1e-32,
+         minbucket = 3,
+         print = FALSE)
+}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
+
+true.fits.imp <- map(1:nsim, ~glm(Outcome ~ BMI + Glucose + Pregnancies,
+                                  family = binomial(link = "logit"), 
+                                  data = data.imp[sample(1:nrow(data.imp), replace = TRUE),]))
+
+true.fits.imp %>%
+  map_dfr(function(x) {
+    x %>% 
+    broom::tidy(conf.int = TRUE) %>% 
+    mutate(cov = conf.low < coef(fit.imp) & coef(fit.imp) < conf.high)
+  }) %>% 
+  group_by(term) %>%
+  summarise(est = mean(estimate),
+                 se  = mean(std.error),
+                 ciw = mean(conf.high - conf.low),
+                 cov = mean(cov)) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+syn2.boot.imp %>%
+  map(function(x) {
+    x %$% 
+      glm(Outcome ~ BMI + Glucose + Pregnancies, 
+          family = binomial(link = "logit"))
+    }) %>%
+  map_dfr(pool3.syn) %>%
+  ci_cov(., fit.imp) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+syn2.cp.boot.imp %>%
+  map(function(x) {
+    x %$% 
+      glm(Outcome ~ BMI + Glucose + Pregnancies, 
+          family = binomial(link = "logit"))
+    }) %>%
+  map_dfr(pool3.syn) %>%
+  ci_cov(., fit.imp) %>%
+  kable(digits = 3) %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```

### 2021-09-15 ads_thesis/simulation_replication.Rmd

@@
 ```
+
+```{r}
+syn2_cp_boot %>%
+   map(function(x) {
+    x %$% 
+      glm(Outcome ~ BMI + Glucose + Pregnancies, 
+          family = binomial(link = "logit"))
+    }) %>%
+  map_dfr(pool3.syn) %>%
+  select(term, est) %>%
+  bind_rows(Syn = ., 
+            True = true_fits %>% 
+              map_dfr(~coef(.x)) %>%
+              pivot_longer(cols = everything(), 
+                           names_to = "term", 
+                           values_to = "est"), .id = "Model") %>%
+  ggplot(aes(x = est, fill = Model)) +
+  geom_density(alpha = 0.5) +
+  scale_fill_brewer(palette = "Set1") +
+  facet_wrap(~term, scales = "free")
+```

### 2021-09-15 mice_synthesizing/distributional_sim_study.Rmd

--- 2021-05-13 ads_thesis/simulation_replication.Rmd
@@
 ---
-title: "ADS Thesis simulation"
+title: "Untitled"
 author: 
@@
   html_document:
-    theme: spacelab
-    highlight: tango
+    highlight: pygments
     toc: true
@@
 
+# Simulation study -- creating synthetic data with `mice`
+
 # Load packages
 
-```{r, results = F, message = F}
+```{r}
 library(mice)
@@
 ```
-
-# Synthetic data model
-
-```{r}
-mod1 <- c(Pregnancies              = "pmm", 
-          Glucose                  = "norm", 
-          BloodPressure            = "norm", 
-          SkinThickness            = "pmm", 
-          Insulin                  = "pmm", 
-          BMI                      = "norm", 
-          DiabetesPedigreeFunction = "pmm", 
-          Age                      = "pmm", 
-          Outcome                  = "logreg.boot")
-
-mod2 <- c(Pregnancies              = "cart", 
-          Glucose                  = "cart", 
-          BloodPressure            = "cart", 
-          SkinThickness            = "cart", 
-          Insulin                  = "cart", 
-          BMI                      = "cart", 
-          DiabetesPedigreeFunction = "cart", 
-          Age                      = "cart", 
-          Outcome                  = "cart")
-
-pred <- make.predictorMatrix(data)
-```
-
-# Simulate
-
-```{r, cache = TRUE, cache.lazy = FALSE}
-nsim <- 100
-plan(multisession)
-
-syn1 <- future_map(1:nsim, function(x) {
-  data %>%
-    mice(m = 5,
-         method = mod1,
-         predictorMatrix = pred,
-         where = matrix(TRUE, nrow(.), ncol(.)),
-         print = FALSE)
-}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
-
-syn1_maxit1 <- future_map(1:nsim, function(x) {
-  data %>%
-    mice(m = 5, 
-         maxit = 1,
-         method = mod1,
-         predictorMatrix = pred,
-         where = matrix(TRUE, nrow(.), ncol(.)),
-         print = FALSE)
-}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
-```
-
-```{r, cache = TRUE, cache.lazy = FALSE}
-syn2 <- future_map(1:nsim, function(x) {
-  data %>%
-    mice(m = 5,
-         method = mod2,
-         predictorMatrix = pred,
-         where = matrix(TRUE, nrow(.), ncol(.)),
-         print = FALSE)
-}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
-
-syn2_maxit1 <- future_map(1:nsim, function(x) {
-  data %>%
-    mice(m = 5, 
-         maxit = 1,
-         method = mod2,
-         predictorMatrix = pred,
-         where = matrix(TRUE, nrow(.), ncol(.)),
-         print = FALSE)
-}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
-```
-
-```{r, cache = TRUE, cache.lazy = FALSE}
-syn2_cp <- future_map(1:nsim, function(x) {
-  data %>%
-    mice(m = 5,
-         method = mod2,
-         predictorMatrix = pred,
-         where = matrix(TRUE, nrow(.), ncol(.)),
-         cp = 1e-32,
-         minbucket = 3,
-         print = FALSE)
-}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
-
-syn2_cp_maxit1 <- future_map(1:nsim, function(x) {
-  data %>%
-    mice(m = 5, 
-         maxit = 1,
-         method = mod2,
-         predictorMatrix = pred,
-         where = matrix(TRUE, nrow(.), ncol(.)),
-         cp = 1e-32,
-         minbucket = 3,
-         print = FALSE)
-}, .options = future_options(seed = as.integer(123)), .progress = FALSE)
-```
-
-# Source functions file for pooling
-
-```{r}
-source("~/Documents/Federated_imputation/mice_synthesizing/simulations/functions.R")
-```
-
-# Synthetic data estimates
-
-```{r, include = F}
-library(kableExtra)
-```
-
-```{r}
-syn1 %>%
-  map(function(x) {
-    x %$% 
-      glm(Outcome ~ Pregnancies + Glucose + BMI, 
-          family = binomial(link = "logit"))
-    }) %>%
-  map_dfr(pool3.syn) %>%
-  ci_cov(., fit) %>%
-  kable(digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
-
-syn1_maxit1 %>%
-  map(function(x) {
-    x %$% 
-      glm(Outcome ~ Pregnancies + Glucose + BMI, 
-          family = binomial(link = "logit"))
-    }) %>%
-  map_dfr(pool3.syn) %>%
-  ci_cov(., fit) %>%
-  kable(digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
-```
-
-```{r}
-syn2 %>%
-  map(function(x) {
-    x %$% 
-      glm(Outcome ~ Pregnancies + Glucose + BMI, 
-          family = binomial(link = "logit"))
-    }) %>%
-  map_dfr(pool3.syn) %>%
-  ci_cov(., fit) %>%
-  kable(digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
-
-syn2_maxit1 %>%
-  map(function(x) {
-    x %$% 
-      glm(Outcome ~ Pregnancies + Glucose + BMI, 
-          family = binomial(link = "logit"))
-    }) %>%
-  map_dfr(pool3.syn) %>%
-  ci_cov(., fit) %>%
-  kable(digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
-```
-
-```{r}
-syn2_cp %>%
-  map(function(x) {
-    x %$% 
-      glm(Outcome ~ Pregnancies + Glucose + BMI, 
-          family = binomial(link = "logit"))
-    }) %>%
-  map_dfr(pool3.syn) %>%
-  ci_cov(., fit) %>%
-  kable(digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
-
-syn2_cp_maxit1 %>%
-  map(function(x) {
-    x %$% 
-      glm(Outcome ~ Pregnancies + Glucose + BMI, 
-          family = binomial(link = "logit"))
-    }) %>%
-  map_dfr(pool3.syn) %>%
-  ci_cov(., fit) %>%
-  kable(digits = 3) %>%
-  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
-```

### 2021-09-21 mice_synthesizing/Mice_Synthesizing.Rmd
Adjust for apart simulations folder.
update
no idea what exactly. But let's get it up to a synced state

@@
 date: "`r format(Sys.time(), '%d-%m-%Y')`"
+reveal_options:
+      width: 100%
+      height: 100%
+      margin: 0.1
 output: 
@@
 ```{r, include = F, cache = thomcache, cache.lazy=thomlazy}
-source("1.a Synthesize_Mice_Replace_All.R")
-source("functions.R")
+source("simulations/1.a Synthesize_Mice_Replace_All.R")
+source("simulations/functions.R")
 ```
@@
 
-```{r, code = readLines("functions.R")}
+```{r, code = readLines("simulations/functions.R")}
 ```

### 2021-09-21 mice_synthesizing/simulations/functions.R

@@ -92,6 +92,7 @@ pool3.syn <- function(mira) {
   pooled
 }
 
+
 ci_cov <- function(pooled, true_fit = NULL, coefs = NULL, vars = NULL) {
   
   if (!is.null(true_fit)) {

### 2021-09-21 mice_synthesizing/paper.Rmd

@@
 author:
-- Thom Volker, Gerko Vink & Stef van Buuren
+- Thom Volker & Gerko Vink
 date: "`r format(Sys.time(), '%d-%m-%Y')`"
@@
 
-- [ ] Explain FCS in short.
+- [x] Explain FCS in short.
 - [ ] Demonstrate procedure with `where-matrix` and explain rationale.
@@
 Nevertheless, the possibilities to distribute research data directly are often very limited due to restrictions with regard to privacy and confidentiality.
-Altough these regulations are much needed, privacy constraints are also ranked among the toughest challenges to overcome in the advancement of computational social science [@lazer_life_2009].
+Although these regulations are much needed, privacy constraints are also ranked among the toughest challenges to overcome in the advancement of computational social science [@lazer_life_2009].
 
@@
 
+[[[MOVE UPCOMING TWO PARAGRAPHS TO SIMULATION SECTION]]]
+
 Additional parameters that come with the use of CART are the complexity parameter `cp` and the minimum number of observations in any terminal node `minbucket`, that both restrain the flexibility of the imputation model.
@@
 The values of the parameters `cp` and `minbucket` ought to adhere to the call for imputation models that are as flexible as possible.
-Accordingly, the complexity parameter is fixed at `cp = 1e-08` rather than the default value `1e-08` and the minimum number of observations in each terminal node is set at `minbucket` $= 3$ rather than the default value $5$.
+Accordingly, the complexity parameter is fixed at `cp = 1e-16 [[[CHECK THIS]]]` rather than the default value `1e-04` and the minimum number of observations in each terminal node is set at `minbucket` $= 3$ rather than the default value $5$.
 By allowing for more complexity in the imputation model, bias in the estimates from the synthetic dataset is reduced.
@@
 
-## Synthe*miz*ing in practice
+# Synthesizing data with `mice`
 
-Discuss CART (read Reiter)
-Add text about additional CART parameters cp and minbucket
+To display the applicability of `mice` for generating synthetic data, we will display three distinct simulation set-ups that build up in complexity.
+The first case considers a multivariable regression model, in which the normally distributed outcome variable $y$ is regressed on three normally distributed predictor variables $\{x_1, x_2, x_3\}$, which are bivariately correlated with $\rho_{x_i, x_j} = 0.3$.
+The regression coefficients are specified in such a way that $\beta_2$ equals $2\beta_1$ and $\beta_3$ equals $3\beta_1$.
+Additionally, the proportion explained variance in $y$ equals $R^2=0.25$.
+Hence, the population regression weights equal $\beta_1 = 0.11$, $\beta_2 = 0.22$ and $\beta_3 = 0.33$.
+
+The second simulation involves a logistic regression model, in which $y$ follows a Bernoulli distribution with probability 
+$$
+\frac{1}{1 + \text{exp}\{-X\beta\}},
+$$
+with predictor matrix $X$, consisting of 4 predictors. Here, $x_3$ moderates the relationship between $x_2$ and $y$, while $x_4$ is transformed into a categorical variable with three levels.
 
@@
 -- -- NOT SURE YET: CONTRAST FULLY AND PARTIALLY SYNTHETIC DATA -- --
-
--- -- SINCE PARTIALLY SYNTHETIC DATA POOLING RULES DO NOT REQUIRE ADJUSTED VARIANCE ESTIMATES -- --
-
--- -- CAN WE REGARD THE OBSERVED VALUES AS THE STARTING VALUES FOR THE IMPUTATIONS ? -- --
-
-<!-- The R-package `mice` [@mice] implements the fully conditional specification approach for missing data.
-Since the imputation approaches for missing data and synthetic data do not differ in terms of the imputation process, `mice` can be used for creating synthetic data as well, which will be shown in more detail in the remainder of this paper.
-In the next section, the pooling rules that are required to obtain inferences from the synthetic datasets are discussed.
-Thereafter, it will be investigated which variance estimator yields the best, that is, confidence valid, results in combination with the `mice` synthesizing approach.
-Also, it is shown that iterating over the conditional distributions in order to establish convergence is not required, due to the fact that new values are drawn directly from posterior distribution given the observed data.
--->
 

### 2021-09-24 mice_synthesizing/paper.Rmd
Gerko's update

@@
 Additionally, the fact that public funds are used for data collection results in increasing demand for the collected data.
-Nevertheless, the possibilities to distribute research data directly are often very limited due to restrictions with regard to privacy and confidentiality.
+Nevertheless, the possibilities to distribute research data directly are often very limited due to restrictions on data privacy and data confidentiality.
 Although these regulations are much needed, privacy constraints are also ranked among the toughest challenges to overcome in the advancement of computational social science [@lazer_life_2009].
 
-Anonimizing the data might seem a quick and appealing approach to limit the identifyability of participants.
-However, this approach is not sufficient to fulfil contemporary privacy and confidentiality requirements [@ohm_broken_2009; @national_putting_2007].
-Over the years, several other techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above a certain threshold or adding random noise to the observed values [@drechsler_synthetic_2011].
-However, these methods may distort relationships between variables, thereby reducing the data quality and the scientific returns for re-using the same data for further research.
+Anonymizing the data might seem a quick and appealing approach to limit the unique identification of participants.
+However, this approach is not sufficient to fulfill contemporary privacy and confidentiality requirements [@ohm_broken_2009; @national_putting_2007].
+Over the years, several other techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above an upper bound or adding random noise to the observed values [@drechsler_synthetic_2011].
+However, these methods may distort the true data relation between variables, thereby reducing the data quality and the scientific returns for re-using the same data for further research.
 
 An alternative solution has been proposed separately by @rubin_statistical_disclosure_1993 and @little_statistical_1993.
-Although their approaches differed to some extent, the overarching procedure is to use actually observed data to generate multiply imputed synthetic datasets that can be freely disclosed.
-Based on some imputation model, values from the actually observed data are replaced by multiple draws from the posterior predictive distribution of the observed data.
-Using this approach, the researcher could replace the observed dataset as a whole with multiple synthetic versions.
+Although their approaches differ to some extent, the overarching procedure is to use bonafide observed data to generate multiply imputed synthetic data sets that can be freely disclosed.
+Observed data values are then replaced by multiple draws from the posterior predictive distribution of the observed data, based on some imputation model.
+Using this approach, the researcher could replace the observed data set as a whole with multiple synthetic versions.
 Alternatively, the researcher could opt to only replace a subset of the observed data.
-The values that are to be replaced can be complete variables that could be compared with publicly available datasets or registers, such as addresses, or can be certain values that bear a high risk of being disclosive, such as income values above a certain threshold.
-[**aren't synthetic values then not also too disclosive?**] <!-- I don't think so, because the synthetic values can only be linked to observed values from other sources if they are exactly equal, or if they are the only value within a certain range.
+For example, one can choose to only replace dimensions in the data that could be compared with publicly available data sets or registers.
+Likewise, synthetisation could be limited to those values that are disclosive, such as high incomes or high turnovers.
+<!-- I don't think so, because the synthetic values can only be linked to observed values from other sources if they are exactly equal, or if they are the only value within a certain range.
 The latter might be possible when the number of values is very small, or when the observed value is so extreme that synthetic versions will still be so extreme.
@@
 Similarly to multiple imputation of missing data, the multiple synthetic datasets allow for correct statistical inferences, **regardless of the fact that the "true" value is not included in the analyses**.
-The analyses over multiple synthetic datasets should be pooled into a single inference, so that the researcher can draw valid conclusions from the pooled results.
+The analyses over multiple synthetic data sets should be pooled into a single inference, so that the researcher can draw valid conclusions from the pooled results.
 To that respect, the variance should reflect the added variability that is induced by the imputation procedure.
@@
 Conversely, if the models used to create the synthetic data are able to preserve the relationships between the variables as in the original data, the synthetic data can be nearly as informative as the observed data.
-Thus, to fully exploit the benefits of synthetic data, the effort to actually create these high-quality datasets should be kept at a minimum.
+Thus, to fully exploit the benefits of synthetic data, the effort to actually create these high-quality data sets should be kept at a minimum.
 
-To mitigate additional effort of creating synthetic datasets on behalf of the researcher, software aimed at multiple imputation of missing data can be employed.
-Especially if researchers used this software at an earlier stage in the research process, or acquired familiarity with it during earlier projects, the additional burden of creating synthetic datasets is relatively small.
+To mitigate additional effort of creating synthetic data sets on behalf of the researcher, software aimed at multiple imputation of missing data can be employed.
+Especially if researchers used this software at an earlier stage in the research process, or acquired familiarity with it during earlier projects, the additional burden of creating synthetic data sets is relatively small.
 The R-package `mice` [@mice] implements multiple imputation of missing data in a straightforward and user-friendly manner.
-However, the functionality of `mice` is not restricted to the imputation of missing data, but allows to impute any value in the data.
-Consequently, `mice` can be utilized for the creation of multiply imputed synthetic datasets.
+However, the functionality of `mice` is not restricted to the imputation of missing data, but allows to impute any value in the data: even observed values.
+Consequently, `mice` can be utilized for the creation of multiply imputed synthetic data sets.
 
-After creating the multiply imputed synthetic datasets, the goal is to obtain valid statistical inferences.
-In the missing data framework, this is done by performing statistical analyses on all imputed datasets, and pooling the results of the analyses according to Rubin's rules [-@rubin_multiple_1987].
-In the synthetic data framework, the same procedure is followed.
-However, valid statistical results can only be obtained under the premise that the statistical properties of the analyses are correct.
-Analyzing synthetic data specifically requires appropriate variance estimates.
-Notably, the variance estimator that is suitable for analyzing multiply imputed datasets for missing data is inappropriate when multiply imputed synthetic datasets are analyzed.
-As a result, multiple variance estimators have been proposed to make correct inferences from multiply imputed synthetic datasets.
-These estimators differ according to whether the data consists entirely of synthetic values, or only a subset of the data is synthetic.
+After creating the multiply imputed synthetic data sets, the goal is to obtain valid statistical inferences in the spirit of @rubin_multiple_1987 and @neyman1934.
+In the missing data framework, this is done by performing statistical analyses on all imputed datasets, and pooling the results of the analyses according to Rubin's rules [@rubin_multiple_1987, pp.76].
+In the synthetic data framework, the same procedure is followed, but with a slight twist: there are no values that remain constant over the synthetic data sets.
+The procedure of drawing valid inferences from multiple synthetic data sets is therefore slightly different.
 
-The remainder of this paper is organized as follows.
+In this manuscript we detail a workflow for synthesizing data with `mice`. 
 First, the `mice` algorithm for the creation of synthetic data will be shortly explained.
@@
 Second, a straightforward workflow for imputation of synthetic data with `mice` will be demonstrated.
-The third step is to summarize the variance estimators that have been proposed in the past.
-Finally, it will be assessed which variance estimator provides valid inferences from the synthetic data.
+Third, we demonstrate the validity of the procedure through statistical simulation.
 
@@
 
-The `mice` package has been developed for multiple imputation of missing data.
+The `mice` package [@mice] in `R` [@Rproject] has been developed for multiple imputation of missing data.
 In this context, the aim is to replace missing values due to nonresponse by plausible values from the posterior predictive distribution of the variable containing the missings.
-Doing so, `mice` makes use of fully conditional specification [FCS; @vanbuuren_fully_2006], which breaks down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, with $k$ the number of variables in the data.
-Using FCS, for every variable containing missing values a model is constructed, to impute the missing values $Y_{j, mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ on a variable by variable basis.
+Doing so, `mice` makes use of fully conditional specification [FCS; @vanbuuren_fully_2006], which breaks down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, where $k$ denotes the number of columns in the data.
+Using FCS, a model is constructed for every incomplete variable and the missing values $Y_{j, mis}$ are then imputed with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ on a variable-by-variable basis.
 Note that the predictor matrix $Y_{-j}$ may contain yet imputed values from an earlier imputation step, and thus will be updated after every iteration.
@@
 
-This approach can be straightforwardly extended to a synthetic data framework.
-However, rather than imputing missing data, the actually observed data is overimputed, that is, the observed values are replaced by multiple imputations.
+In `mice`, the generation of multiply imputed data sets is straightforward.
+The following pseudocode details the multiple imputation of the `mice::boys` data set [@fredriks_boys_2000] into the object `imp` with `m = 10` imputated sets and `maxit = 7` iterations for the algorithm to converge, using the default imputations methods for each column data class.
+
+```{r eval = FALSE}
+library(mice)
+imp <- mice(boys, 
+            m = 10,
+            maxit = 7)
+```
+
+It is straightforward to extended the imputation approach to generate synthetic values.
+Rather than imputing missing data, the observed values are then replaced by synthetic draws from the posterior predictive distribution.
 For simplicity, assume that the data is completely observed (i.e., $\textbf{Y} = \textbf{Y}_{obs}$).
-Following the notation of @reiter_raghunathan_multiple_2007, let $Z_i = 1$ if any of the values of unit $i$ are to be replaced by imputations, and $Z_i = 0$ otherwise, with $\textbf{Z} = (Z_1, Z_2, \dots, Z_n)$.
+Following the notation of @reiter_raghunathan_multiple_2007, let for $n$ units denote $Z_i = 1$ if any of the values of unit $i = 1, 2, \dots, n$ are to be replaced by imputations, and $Z_i = 0$ otherwise, with $\textbf{Z} = (Z_1, Z_2, \dots, Z_n)$.
 Accordingly, the data consists of values that are to be replaced and values that are to be kept (i.e., $\textbf{Y} = (\textbf{Y}_{rep}, \textbf{Y}_{nrep})$.
@@
 
-By default, `mice` imputes all values that are coded as missing in the dataset.
-However, using the `where` parameter within the `mice`-function, one can choose to impute any value in the dataset.
-As input, the `where` parameter requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix, with $n$ the number of observations in the collected data) containing logicals $z_{ij}$ that indicate which cells are selected to have their values replaced.
-This approach allows to *overimpute* a subset of the observed data, or the observed data as a whole, resulting in a dataset that partly or completely consists of synthetic values.
-Other parameters that are required to be specified are the imputation method (`method`), the number of imputations ($m$) and the predictor matrix, specifying the predictor variables that are used in the imputation model for every variable $j$ that has some of its values replaced (`predictorMatrix`).
+For example, overimputing the observed and missing values in the `mice::boys` data set into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution
 
-Choosing an adequate method to impute the data is paramount, as a flawed imputation model will drastically reduce the data utility in further inferences.
-Imputation models should be as flexible as possible to capture most of the patterns in the data, and to model, possibly unanticipated, data characteristics [@murray_multiple_2018; @rubin_18years_1996].
+```{r eval = FALSE}
+syn <- mice(boys, 
+            m = 10,
+            maxit = 7, 
+            where = matrix(TRUE, 
+                           nrow = nrow(boys),
+                           ncol = ncol(boys)))
+```
+
+where the argument `where` requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix) containing logicals $z_{ij}$ that indicate which cells are selected to have their values replaced by draws from the posterior predictive distribution.
+This approach allows to *overimpute* a subset of the observed data, or - as in the above example - the observed data as a whole, resulting in a dataset that partly or completely consists of synthetic data values.
+
+Choosing an adequate imputation model to impute the data is paramount, as a flawed imputation model may drastically impact the validity of inferences.
+Imputation models should be as flexible as possible to capture most of the patterns in the data, and to model possibly unanticipated data characteristics [@murray_multiple_2018; @rubin_18years_1996].
 Parametric methods, albeit easy to implement in practice, may be too restrictive to capture generally complex patterns in the data, especially in the case of nonlinear relations and interactions between multiple variables.
@@
 As such, CART does not impose any parametric distribution on the data, making it a widely applicable method that allows for a large variety of relationships within the data [@islr_2013].
-Given these appealing characteristics and the call for the use of flexible methods when multiply imputing data, the performance of `mice` with CART as the specified imputation method will be illustrated.
+Given these appealing characteristics and the call for the use of flexible methods when multiply imputing data, we will focus our illustrations and evaluations of `mice` to method `mice.impute.cart()`, realized by
+
+```{r eval = FALSE}
+syn <- mice(boys, 
+            m = 10,
+            maxit = 7, 
+            method = "cart",
+            where = matrix(TRUE, 
+                           nrow = nrow(boys),
+                           ncol = ncol(boys)))
+```
 
@@
 
-Additional parameters that come with the use of CART are the complexity parameter `cp` and the minimum number of observations in any terminal node `minbucket`, that both restrain the flexibility of the imputation model.
+Additional parameters that come with the use of `mice.impute.cart()` are the complexity parameter `cp` and the minimum number of observations in any terminal node `minbucket`, that both restrain the flexibility of the imputation model.
 Appropriate values for these parameters, as well as the input for the `predictorMatrix`, depend on the data at hand.

### 2021-09-24 mice_synthesizing/paper.Rmd
some models to eval added

@@
 - [x] Explain FCS in short.
-- [ ] Demonstrate procedure with `where-matrix` and explain rationale.
+- [x] Demonstrate procedure with `where-matrix` and explain rationale.
 - [ ] Demonstrate that this is a reasonable approach, based on a figure that shows the observed and synthetic relationships side-by-side (e.g. `wgt ~ age + gen`).
@@
 ```
+
+# psych::describe
+# correlation matrix
+# wgt ~ age + bmi | hgt ~ age + wgt | gen ~ age +
+
+```{r}
+library(mice)
+library(dplyr)
+library(magrittr)
+meth <- make.method(boys)
+meth["bmi"] <- "~ I(wgt / (hgt / 100)^2)"
+pred <- make.predictorMatrix(boys)
+pred[c("hgt", "wgt"), "bmi"] <- 0
+imp <-mice(boys, 
+           meth = meth, 
+           pred = pred, 
+           print = FALSE)
+with(imp, lm(wgt ~ age + bmi))%>% pool() %>% summary()
+with(imp, lm(bmi ~ I((wgt / (hgt/100)^2))))%>% pool() %>% summary()
+library(MASS)
+with(imp, polr(gen ~ age + bmi, Hess = TRUE)) %>% pool() %>% summary()
+```
+
+# log reg prediction of rows
 

### 2021-09-24 mice_synthesizing/paper.Rmd
updates

@@
 Although their approaches differ to some extent, the overarching procedure is to use bonafide observed data to generate multiply imputed synthetic data sets that can be freely disclosed.
-Observed data values are then replaced by multiple draws from the posterior predictive distribution of the observed data, based on some imputation model.
+While in practice, one could see this as replacing the observed data values by multiple draws from the posterior predictive distribution of the observed data, based on some imputation model, Rubin would argue that these synthetic data values are merely draws from the same true data generating model.
+In that sense, the observed data is never replaced, but the population is resampled from the information captured in the (incomplete) sample.
 Using this approach, the researcher could replace the observed data set as a whole with multiple synthetic versions.
@@
 
-In `mice`, the generation of multiply imputed data sets is straightforward.
+In `mice`, the generation of multiply imputed data sets to solve for unobserved values is straightforward.
 The following pseudocode details the multiple imputation of the `mice::boys` data set [@fredriks_boys_2000] into the object `imp` with `m = 10` imputated sets and `maxit = 7` iterations for the algorithm to converge, using the default imputations methods for each column data class.
@@
 
-For example, overimputing the observed and missing values in the `mice::boys` data set into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution
+For example, overimputing synthetic values for both the observed and missing cells in the `mice::boys` data set into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution
 
@@
 
-# psych::describe
-# correlation matrix
-# wgt ~ age + bmi | hgt ~ age + wgt | gen ~ age +
+# Simulation setup
+- boys data met bootstrap om sampling variance er in te brengen
+- wat evalueren we: bias | standard error | coverage
+- welke pooling: T = Ubar + B/m
+
+# psych::describe - univariate ok
+map --> psych::describe() --> Reduce("+", .) in de pipe
+
+# correlation matrix - relations preserved
+map --> cor --> logit --> pool --> inv.logit --> correct diagonal
+
+# wgt ~ age + bmi | hgt ~ age + wgt | gen ~ age + bmi - multivariate ok
+3 sets modellen
+
+complete(imp, "all") 
+--> lm1
+--> lm2
+--> polr
+
+pooling cf. T = Ubar + B/m
+
+# Conclusie
+- We hebben laten zien dat het belangrijk is om meerdere synthetische versies te creeren. Dit is ook geen probleem, dat doen we immers al decennia lang met imputeren. 
+- Waarom geen synthpop --> Ibrahim 2000
+- werkt wel goed.
+- Beperkingen
+- Wat verder nog te doen: aanvullende functies voor complexere combinaties van synthetiseren en imputeren
 

### 2021-09-25 mice_synthesizing/paper.Rmd
Minor revisions.

@@
 Nevertheless, the possibilities to distribute research data directly are often very limited due to restrictions on data privacy and data confidentiality.
-Although these regulations are much needed, privacy constraints are also ranked among the toughest challenges to overcome in the advancement of computational social science [@lazer_life_2009].
+Although these regulations are much needed, privacy constraints are also ranked among the toughest challenges to overcome in the advancement of modern day social science research [@lazer_life_2009].
 
-Anonymizing the data might seem a quick and appealing approach to limit the unique identification of participants.
-However, this approach is not sufficient to fulfill contemporary privacy and confidentiality requirements [@ohm_broken_2009; @national_putting_2007].
-Over the years, several other techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above an upper bound or adding random noise to the observed values [@drechsler_synthetic_2011].
+Anonymizing research data might seem a quick and appealing approach to limit the unique identification of participants.
+However, this approach is not sufficient to fulfil contemporary privacy and confidentiality requirements [@ohm_broken_2009; @national_putting_2007].
+Over the years, several other techniques have been used to increase the confidentiality of research data, such as categorizing continuous variables, top coding values above an upper bound or adding random noise to the observed values [@drechsler_synthetic_2011].
 However, these methods may distort the true data relation between variables, thereby reducing the data quality and the scientific returns for re-using the same data for further research.
@@
 Instead of replacing just the missing values with multiple draws from the posterior predictive distribution, one could easily *overimpute* any observed sensitive values.
-Similarly to multiple imputation of missing data, the multiple synthetic datasets allow for correct statistical inferences, **regardless of the fact that the "true" value is not included in the analyses**.
+Similarly to multiple imputation of missing data, the multiple synthetic datasets allow for correct statistical inferences, **regardless of the fact that the analyses do not use the "true" value**.
 The analyses over multiple synthetic data sets should be pooled into a single inference, so that the researcher can draw valid conclusions from the pooled results.
 To that respect, the variance should reflect the added variability that is induced by the imputation procedure.
+
 Potentially, this approach could fulfill the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints.
@@
 
-For example, overimputing synthetic values for both the observed and missing cells in the `mice::boys` data set into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution
+For example, overimputing synthetic values for both the observed and missing cells in the `mice::boys` data set into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution.
 
@@
 - welke pooling: T = Ubar + B/m
-
+# psych::describe
+# correlation matrix
+# wgt ~ age + bmi | hgt ~ age + wgt | gen ~ age + 
 # psych::describe - univariate ok

### 2021-09-26 mice_synthesizing/paper.Rmd
Proceed with simulation section (not entirely finished yet).

@@
 An alternative solution has been proposed separately by @rubin_statistical_disclosure_1993 and @little_statistical_1993.
-Although their approaches differ to some extent, the overarching procedure is to use bonafide observed data to generate multiply imputed synthetic data sets that can be freely disclosed.
+Although their approaches differ to some extent, the overarching procedure is to use bonafide observed data to generate multiply imputed synthetic datasets that can be freely disclosed.
 While in practice, one could see this as replacing the observed data values by multiple draws from the posterior predictive distribution of the observed data, based on some imputation model, Rubin would argue that these synthetic data values are merely draws from the same true data generating model.
 In that sense, the observed data is never replaced, but the population is resampled from the information captured in the (incomplete) sample.
-Using this approach, the researcher could replace the observed data set as a whole with multiple synthetic versions.
+Using this approach, the researcher could replace the observed dataset as a whole with multiple synthetic versions.
 Alternatively, the researcher could opt to only replace a subset of the observed data.
-For example, one can choose to only replace dimensions in the data that could be compared with publicly available data sets or registers.
+For example, one can choose to only replace dimensions in the data that could be compared with publicly available datasets or registers.
 Likewise, synthetisation could be limited to those values that are disclosive, such as high incomes or high turnovers.
@@
 Similarly to multiple imputation of missing data, the multiple synthetic datasets allow for correct statistical inferences, **regardless of the fact that the analyses do not use the "true" value**.
-The analyses over multiple synthetic data sets should be pooled into a single inference, so that the researcher can draw valid conclusions from the pooled results.
+The analyses over multiple synthetic datasets should be pooled into a single inference, so that the researcher can draw valid conclusions from the pooled results.
 To that respect, the variance should reflect the added variability that is induced by the imputation procedure.
@@
 Conversely, if the models used to create the synthetic data are able to preserve the relationships between the variables as in the original data, the synthetic data can be nearly as informative as the observed data.
-Thus, to fully exploit the benefits of synthetic data, the effort to actually create these high-quality data sets should be kept at a minimum.
+Thus, to fully exploit the benefits of synthetic data, the effort to actually create these high-quality datasets should be kept at a minimum.
 
-To mitigate additional effort of creating synthetic data sets on behalf of the researcher, software aimed at multiple imputation of missing data can be employed.
-Especially if researchers used this software at an earlier stage in the research process, or acquired familiarity with it during earlier projects, the additional burden of creating synthetic data sets is relatively small.
+To mitigate additional effort of creating synthetic datasets on behalf of the researcher, software aimed at multiple imputation of missing data can be employed.
+Especially if researchers used this software at an earlier stage in the research process, or acquired familiarity with it during earlier projects, the additional burden of creating synthetic datasets is relatively small.
 The R-package `mice` [@mice] implements multiple imputation of missing data in a straightforward and user-friendly manner.
 However, the functionality of `mice` is not restricted to the imputation of missing data, but allows to impute any value in the data: even observed values.
-Consequently, `mice` can be utilized for the creation of multiply imputed synthetic data sets.
+Consequently, `mice` can be utilized for the creation of multiply imputed synthetic datasets.
 
-After creating the multiply imputed synthetic data sets, the goal is to obtain valid statistical inferences in the spirit of @rubin_multiple_1987 and @neyman1934.
+After creating the multiply imputed synthetic datasets, the goal is to obtain valid statistical inferences in the spirit of @rubin_multiple_1987 and @neyman1934.
 In the missing data framework, this is done by performing statistical analyses on all imputed datasets, and pooling the results of the analyses according to Rubin's rules [@rubin_multiple_1987, pp.76].
-In the synthetic data framework, the same procedure is followed, but with a slight twist: there are no values that remain constant over the synthetic data sets.
-The procedure of drawing valid inferences from multiple synthetic data sets is therefore slightly different.
+In the synthetic data framework, the same procedure is followed, but with a slight twist: there are no values that remain constant over the synthetic datasets.
+The procedure of drawing valid inferences from multiple synthetic datasets is therefore slightly different.
 
@@
 
-In `mice`, the generation of multiply imputed data sets to solve for unobserved values is straightforward.
-The following pseudocode details the multiple imputation of the `mice::boys` data set [@fredriks_boys_2000] into the object `imp` with `m = 10` imputated sets and `maxit = 7` iterations for the algorithm to converge, using the default imputations methods for each column data class.
+In `mice`, the generation of multiply imputed datasets to solve for unobserved values is straightforward.
+The following pseudocode details the multiple imputation of the `mice::boys` dataset [@fredriks_boys_2000] into the object `imp` with `m = 10` imputated sets and `maxit = 7` iterations for the algorithm to converge, using the default imputations methods for each column data class.
 
@@
 
-For example, overimputing synthetic values for both the observed and missing cells in the `mice::boys` data set into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution.
+For example, overimputing synthetic values for both the observed and missing cells in the `mice::boys` dataset into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution.
 
@@
 As such, CART does not impose any parametric distribution on the data, making it a widely applicable method that allows for a large variety of relationships within the data [@islr_2013].
-Given these appealing characteristics and the call for the use of flexible methods when multiply imputing data, we will focus our illustrations and evaluations of `mice` to method `mice.impute.cart()`, realized by
+Given these appealing characteristics and the call for the use of flexible methods when multiply imputing data, we will focus our illustrations and evaluations of `mice` to method `mice.impute.cart()`, realized by:
 
@@
                            ncol = ncol(boys)))
+```
+
+In a nutshell, the above code shows the simplicity of creating $m = 10$ synthetic datasets using `mice`.
+In practice, however, one should take some additional complicating factors into account.
+For example, one should account for deterministic relations in the data.
+Additionally, relations between variables may be described best using a different model than `CART`.
+Such factors are data dependent and should be considered by the imputer.
+In the next section, we will describe how the `boys` data can be adequately imputed.
+Additionally, we will show through simulations that this approach yields valid inferences.
+
+# Simulations
+
+We will show the suitability of using `mice` for synthesization using a simulation study, using the `boys` data.
+This dataset consists of the values of $`r nrow(mice::boys)`$ Dutch boys on the following $`r ncol(mice::boys)`$ variables: age (in years), height (in cm), weight (in kg), body mass index (BMI), head circumference (in cm), Genital Tanner stage (G1-G5), testicular volume (in ml) and region.
+Unfortunately, this dataset does not differ from the vast majority of collected datasets, in the sense that it suffers from missing data.
+For simplicity, the data is completed using the default `mice` imputation model for all predictors except BMI, which is imputed using a passive imputation model due to the deterministic relation with weight and height ($\text{BMI} = \frac{\text{weight}}{\text{height (in meters)}^2}$) to create a single, fully observed dataset:
+
+```{r, include = FALSE}
+library(mice)
+library(magrittr)
+library(tidyverse)
+library(furrr)
+library(knitr)
+library(kableExtra)
+```
+
+```{r, results = FALSE, message = FALSE, warning = FALSE}
+# create a single imputed, completely observed `boys` dataset
+set.seed(123)
+
+meth <- make.method(boys)
+meth["bmi"] <- "~ I(wgt / (hgt / 100)^2)"
+pred <- make.predictorMatrix(boys)
+pred[c("hgt", "wgt"), "bmi"] <- 0
+
+imp <- mice(boys, 
+            m = 1,
+            maxit = 10,
+            method = meth,
+            predictorMatrix = pred)
+
+data <- complete(imp)
+```
+
+To induce an appropriate amount of sampling variance, 1000 bootstrap samples of the `boys` data will be synthesized with $m = 5$ imputations.
+The data will be synthesized using the `CART` imputation method.
+Additional parameters that come with the use of `mice.impute.cart()` are the complexity parameter `cp` and the minimum number of observations in any terminal node `minbucket`, that both constrain the flexibility of the imputation model.
+The values of the parameters `cp` and `minbucket` ought to adhere to the call for imputation models that are as flexible as possible.
+Appropriate values for these parameters, as well as the input for the `predictorMatrix`, depend on the data at hand.
+In the current example, the complexity parameter is specified at `cp = 1e-08` rather than the default value `1e-04`, and the minimum number of observations in each terminal node is set at `minbucket` $= 3$ rather than the default value $5$.
+By allowing for more complexity in the imputation model, bias in the estimates from the synthetic dataset is reduced.
+Additionally, since the missingness pattern is monotone, the number of iterations can be set to `maxit = 1`.
+
+```{r eval = FALSE}
+syn <- mice(boys,
+            m = 10,
+            maxit = 7,
+            method = "cart",
+            where = matrix(TRUE,
+                           nrow = nrow(boys),
+                           ncol = ncol(boys)),
+            cp = 1e-08,
+            minbucket = 3)
 ```
@@
 
-[[[MOVE UPCOMING TWO PARAGRAPHS TO SIMULATION SECTION]]]
-
-Additional parameters that come with the use of `mice.impute.cart()` are the complexity parameter `cp` and the minimum number of observations in any terminal node `minbucket`, that both restrain the flexibility of the imputation model.
-Appropriate values for these parameters, as well as the input for the `predictorMatrix`, depend on the data at hand.
-Hence, the specification of these parameters will be illustrated using an actual dataset.
-The `boys` data [@fredriks_boys_2000] that is in-built within the `mice` package is used to illustrate the specification of these parameters accordingly.
-**DETERMINE WHETHER THIS DATASET SUFFICES; BECAUSE IMPUTATION MIGHT MAKE THE DATA ARTIFICIALLY SIMILAR BEFORE SYNTHESIZING, MAKING SYNTHESIZING TOO EASY** Unfortunately, this dataset does not differ from the vast majority of collected datasets, in the sense that it suffers from missing data.
-For simplicity, the data is completed using the default `mice` imputation model to create a single, fully observed dataset.
-The data consists of the values of $`r nrow(mice::boys)`$ Dutch boys on the following $`r ncol(mice::boys)`$ variables: age (in years), height (in cm), weight (in kg), body mass index (BMI), head circumference (in cm), Genital Tanner stage (G1-G5), testicular volume (in ml) and region.
-
-The values of the parameters `cp` and `minbucket` ought to adhere to the call for imputation models that are as flexible as possible.
-Accordingly, the complexity parameter is fixed at `cp = 1e-16 [[[CHECK THIS]]]` rather than the default value `1e-04` and the minimum number of observations in each terminal node is set at `minbucket` $= 3$ rather than the default value $5$.
-By allowing for more complexity in the imputation model, bias in the estimates from the synthetic dataset is reduced.
-The predictor matrix was specified so that BMI was not imputed from a model, but calculated from the imputed height and weight values ($BMI = kg / m^2$), an approach called passive imputation.
-Additionally, BMI is excluded as a predictor for weight and height, because BMI values are directly dependent on the values of weight and height.
-All other variables $Y_{-j}$ are used as predictors for variable $Y_j$.
-Additionally, the number of imputations is set to $m = 5$.
-
 # Synthesizing data with `mice`
 
-To display the applicability of `mice` for generating synthetic data, we will display three distinct simulation set-ups that build up in complexity.
+**!!PROBABLY NOT USED!!**
+
+*To display the applicability of `mice` for generating synthetic data, we will display three distinct simulation set-ups that build up in complexity.
 The first case considers a multivariable regression model, in which the normally distributed outcome variable $y$ is regressed on three normally distributed predictor variables $\{x_1, x_2, x_3\}$, which are bivariately correlated with $\rho_{x_i, x_j} = 0.3$.
@@
 Additionally, the proportion explained variance in $y$ equals $R^2=0.25$.
-Hence, the population regression weights equal $\beta_1 = 0.11$, $\beta_2 = 0.22$ and $\beta_3 = 0.33$.
+Hence, the population regression weights equal $\beta_1 = 0.11$, $\beta_2 = 0.22$ and $\beta_3 = 0.33$.*
 
-The second simulation involves a logistic regression model, in which $y$ follows a Bernoulli distribution with probability 
+*The second simulation involves a logistic regression model, in which $y$ follows a Bernoulli distribution with probability*
 $$
@@
 $$
-with predictor matrix $X$, consisting of 4 predictors. Here, $x_3$ moderates the relationship between $x_2$ and $y$, while $x_4$ is transformed into a categorical variable with three levels.
+*with predictor matrix $X$, consisting of 4 predictors. Here, $x_3$ moderates the relationship between $x_2$ and $y$, while $x_4$ is transformed into a categorical variable with three levels.*
 
@@
 This joint density is generally hard or impossible to derive, which can be overcome by employing fully conditional specification (FCS).
-Consider a $n \times k$ data matrix $Y$, with values to be replaced $Y^{old}$, the values to be kept $Y^{keep}$ and the values that are already replaced $Y^{new}$, under the assumption that there are no missing values in the observed data set.
+Consider a $n \times k$ data matrix $Y$, with values to be replaced $Y^{old}$, the values to be kept $Y^{keep}$ and the values that are already replaced $Y^{new}$, under the assumption that there are no missing values in the observed dataset.
 Instead of drawing from the joint distribution, we draw from $k$ univariate conditional densities for each variable.
@@
  - All fun and game, but statistical properties should be intact
- - In this paper we demonstrate a straigthforward workflow for generating synthetic data sets and we investigate how to obtain valid inferences from synthesized data.
+ - In this paper we demonstrate a straigthforward workflow for generating synthetic datasets and we investigate how to obtain valid inferences from synthesized data.
 

### 2021-09-26 mice_synthesizing/synthesizing_partially_synthetic_data_rules.Rmd

@@
 \begin{aligned}
-\nu_p &= (m - 1)(1 + \frac{\bar{u}_m}{\frac{b_m}{m}}) \\
-&= (m - 1)(1 + \frac{m \cdot \bar{u}_m}{b_m}).
+\nu_p &= (m - 1)(1 + \frac{\bar{u}_m}{\frac{b_m}{m}})^2 \\
+&= (m - 1)(1 + \frac{m \cdot \bar{u}_m}{b_m})^2.
 \end{aligned}
@@
 
+```{r}
+boot_cart_maxit_cp_min3 %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(~mice:::pool.syn(.x) %>% summary(conf.int = TRUE) %>% as.data.frame) %>%
+  mutate(true_coef = rep(coef(truemodel), nrow(.) / length(coef(truemodel))),
+         covered = `2.5 %` < true_coef & true_coef < `97.5 %`) %>%
+  group_by(term) %>%
+  summarize(estimate = mean(estimate),
+            bias = mean(estimate - true_coef),
+            var = mean(std.error^2),
+            lower = mean(`2.5 %`),
+            upper = mean(`97.5 %`),
+            coverage = mean(covered), .groups = "drop") %>%
+    kable(digits = 3,
+        caption = "Synthetic regression estimates after bootstrapping, 
+        synthesizing (with adjusted mice CART settings) and analysing
+        the boys dataset 500 times") %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+boot_cart_cp_min3 %>%
+  map(function(x) x %$% lm(wgt ~ age + hgt)) %>%
+  map_dfr(~mice:::pool.syn(.x) %>% summary(conf.int = TRUE) %>% as.data.frame) %>%
+  mutate(true_coef = rep(coef(truemodel), nrow(.) / length(coef(truemodel))),
+         covered = `2.5 %` < true_coef & true_coef < `97.5 %`) %>%
+  group_by(term) %>%
+  summarize(estimate = mean(estimate),
+            bias = mean(estimate - true_coef),
+            var = mean(std.error^2),
+            lower = mean(`2.5 %`),
+            upper = mean(`97.5 %`),
+            coverage = mean(covered), .groups = "drop") %>%
+  kable(digits = 3,
+        caption = "Synthetic regression estimates after bootstrapping, 
+        synthesizing (with adjusted mice CART settings) and analysing
+        the boys dataset 500 times") %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```
+
 It can indeed be seen that the bias decreases substantially after altering the complexity parameter `cp` and the minimum number of observations in any final node `minbucket` results in less biased estimates, resulting in higher confidence interval coverage.

### 2021-09-27 mice_synthesizing/paper.Rmd
Latest version paper text.

@@
 To induce an appropriate amount of sampling variance, 1000 bootstrap samples of the `boys` data will be synthesized with $m = 5$ imputations.
-The data will be synthesized using the `CART` imputation method.
+The data will be synthesized using the `CART` imputation method for all predictors except BMI, which will be synthesized using passive imputation according to the model `~I(wgt / (hgt / 100)^2)`.
 Additional parameters that come with the use of `mice.impute.cart()` are the complexity parameter `cp` and the minimum number of observations in any terminal node `minbucket`, that both constrain the flexibility of the imputation model.
@@
 Additionally, since the missingness pattern is monotone, the number of iterations can be set to `maxit = 1`.
+
+To assess the performance of `mice` for synthesizing data, we compare the bootstrapped samples with the synthetic versions of these bootstrapped samples.
+Specifically, univariate descriptive statistics, the correlation matrix, and two linear regression models as well as one ordered logistic regression model will be considered.
+Subsequently, the bias in the parameters and the $95\%$ confidence interval coverage of the synthetic data will be examined.
+Similarly to multiple imputation of missing data, $95\%$ confidence intervals must be calculated using an adjusted variance estimator that accounts for the increase in variance due to imputation [@reiter_partially_inference_2003; @drechsler_synthetic_2011].
+However, these variance estimators are not the same.
+Whereas the variance estimate after imputation of missing data needs to account for the fact that a certain amount of information in the data is missing, variance estimation from synthetic data does not suffer from this issue.
+The adjusted variance estimate that follows from using multiple synthetic datasets only suffers from the fact that a finite number of $m$ synthetic datasets are used to resemble the observed data.
+Hence, the according pooling rules for synthetic data as developed by @reiter_partially_inference_2003 are
+
+\begin{aligned}
+
+\bar{q}_m &= \sum_{l = 1}^m \frac{q^{(l)}}{m}, \\
+
+b_m       &= \sum_{l = 1}^m \frac{(q^{(l)} - \bar{q}_m)^2}{(m - 1)}, \\
+
+\bar{u}_m &= \sum_{l = 1} \frac{u^{(l)}}{m}.
+\end{aligned}
 

### 2021-09-28 mice_synthesizing/paper.Rmd

@@
 \bar{u}_m &= \sum_{l = 1} \frac{u^{(l)}}{m}.
+
 \end{aligned}
+
+```{r, message = FALSE, warning = FALSE, cache = TRUE, cache.lazy = FALSE}
+plan(multisession) # increase speed through futures
+
+true_model_age <- lm(age ~ wgt + hgt, data) # model 1
+true_model_wgt <- lm(wgt ~ age + hgt, data) # model 2
+true_model_gen <- MASS::polr(gen ~ age + hc + reg, data, Hess = TRUE) # model 3
+
+coefs_age <- broom::tidy(true_model_age)$estimate # extract coefficients of model 1
+coefs_wgt <- broom::tidy(true_model_wgt)$estimate # extract coefficients of model 2
+coefs_gen <- broom::tidy(true_model_gen)$estimate # extract coefficients of model 3
+
+nsim <- 1000 # use 1000 iterations
+
+bootstrap_samples <- 
+  modelr::bootstrap(data = data, n = nsim) %$% 
+  strap %>% 
+  map(as_tibble)
+
+post <- make.post(data)
+post["bmi"] <- "imp[[j]][, i] <- imp[['wgt']][, i] / (imp[['hgt']][, i] / 100)^2"
+
+synthetic_samples <- 
+  bootstrap_samples %>%
+  future_map(function(x) {
+    x %>% mice(m = 5, 
+               maxit = 1,
+               method = "cart",
+               minbucket = 3,
+               cp = 1e-08,
+               predictorMatrix = pred,
+               post = post,
+               where = matrix(TRUE, nrow(data), ncol(data)),
+               print = F)
+}, .options = furrr_options(seed = as.integer(123)))
+
+true_age <- 
+  bootstrap_samples %>%
+  map_dfr(~lm(age ~ wgt + hgt, .x) %>%
+            broom::tidy(conf.int = TRUE))
+
+true_wgt <-
+  bootstrap_samples %>%
+  map_dfr(~lm(wgt ~ age + hgt, .x) %>% 
+            broom::tidy(conf.int = TRUE))
+
+true_gen <- 
+  bootstrap_samples %>%
+  map_dfr(~MASS::polr(gen ~ age + hc + reg, .x, Hess = TRUE) %>%
+            broom::tidy(conf.int = TRUE))
+
+synthetic_age <- 
+  synthetic_samples %>%
+  map_dfr(function(x) {
+    x %$% 
+      lm(age ~ wgt + hgt) %>%
+      mice:::pool.syn() %>%
+      summary(conf.int = TRUE)
+    })
+
+synthetic_wgt <- 
+  synthetic_samples %>%
+  map_dfr(function(x) {
+    x %$%
+      lm(wgt ~ age + hgt) %>%
+      mice:::pool.syn() %>%
+      summary(conf.int = TRUE)
+  })
+
+synthetic_gen <- 
+  synthetic_samples %>%
+  map_dfr(function(x) {
+    x %$%
+      MASS::polr(gen ~ age + hc + reg, Hess = TRUE) %>%
+      mice:::pool.syn() %>%
+      summary(conf.int = TRUE)
+  })
+```
+
+```{r}
+true_age %>%
+  mutate(truth = rep(coefs_age, nrow(.) / length(coefs_age)),
+         covered = conf.low < truth & truth < conf.high) %>%
+  group_by(term) %>%
+  summarize(estimate = mean(estimate),
+            bias = mean(estimate - truth),
+            var = mean(std.error^2),
+            lower = mean(conf.low),
+            upper = mean(conf.high),
+            coverage = mean(covered), .groups = "drop") %>%
+  kable(digits = 3,
+        caption = "Bootstrapped regression estimates (1000 times) for age 
+        regressed on weight and height.") %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+synthetic_age %>%
+  mutate(truth = rep(coefs_age, nrow(.) / length(coefs_age)),
+         covered = `2.5 %` < truth & truth < `97.5 %`) %>%
+  group_by(term) %>%
+  summarize(estimate = mean(estimate),
+            bias = mean(estimate - truth),
+            var = mean(std.error^2),
+            lower = mean(`2.5 %`),
+            upper = mean(`97.5 %`),
+            coverage = mean(covered), .groups = "drop") %>%
+  kable(digits = 3,
+        caption = "Synthetic regression estimates after bootstrapping (1000 
+        times) and synthesizing for age regressed on weight and height.") %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+true_wgt %>%
+  mutate(truth = rep(coefs_wgt, nrow(.) / length(coefs_wgt)),
+         covered = conf.low < truth & truth < conf.high) %>%
+  group_by(term) %>%
+  summarize(estimate = mean(estimate),
+            bias = mean(estimate - truth),
+            var = mean(std.error^2),
+            lower = mean(conf.low),
+            upper = mean(conf.high),
+            coverage = mean(covered), .groups = "drop") %>%
+  kable(digits = 3,
+        caption = "Bootstrapped regression estimates (1000 times) for weight 
+        regressed on age and height.") %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+synthetic_wgt %>%
+  mutate(truth = rep(coefs_wgt, nrow(.) / length(coefs_wgt)),
+         covered = `2.5 %` < truth & truth < `97.5 %`) %>%
+  group_by(term) %>%
+  summarize(estimate = mean(estimate),
+            bias = mean(estimate - truth),
+            var = mean(std.error^2),
+            lower = mean(`2.5 %`),
+            upper = mean(`97.5 %`),
+            coverage = mean(covered), .groups = "drop") %>%
+  kable(digits = 3,
+        caption = "Synthetic regression estimates after bootstrapping (1000 
+        times) and synthesizing for weight regressed on age and height.") %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+true_gen %>%
+  mutate(truth = rep(coefs_gen, nrow(.) / length(coefs_gen)),
+         covered = conf.low < truth & truth < conf.high) %>%
+  group_by(term) %>%
+  summarize(estimate = mean(estimate),
+            bias = mean(estimate - truth),
+            var = mean(std.error^2),
+            lower = mean(conf.low),
+            upper = mean(conf.high),
+            coverage = mean(covered), .groups = "drop") %>%
+  kable(digits = 3,
+        caption = "Bootstrapped regression estimates (1000 times) for 
+        genital Tanner stage regressed on age, head circumference and 
+        region. ") %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+
+synthetic_gen %>%
+  mutate(truth = rep(coefs_gen, nrow(.) / length(coefs_gen)),
+         covered = `2.5 %` < truth & truth < `97.5 %`) %>%
+  group_by(term) %>%
+  summarize(estimate = mean(estimate),
+            bias = mean(estimate - truth),
+            var = mean(std.error^2),
+            lower = mean(`2.5 %`),
+            upper = mean(`97.5 %`),
+            coverage = mean(covered), .groups = "drop") %>%
+  kable(digits = 3,
+        caption = "Synthetic regression estimates after bootstrapping (1000
+        times) and synthesizing for genital Tanner stage regressed on age,
+        head circumference and region.") %>%
+  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
+```
 

### 2021-09-30 mice_synthesizing/paper.Rmd
Restructure pooling rules section.

@@
 
+## Simulation methods
+
 To induce an appropriate amount of sampling variance, 1000 bootstrap samples of the `boys` data will be synthesized with $m = 5$ imputations.
@@
 Subsequently, the bias in the parameters and the $95\%$ confidence interval coverage of the synthetic data will be examined.
-Similarly to multiple imputation of missing data, $95\%$ confidence intervals must be calculated using an adjusted variance estimator that accounts for the increase in variance due to imputation [@reiter_partially_inference_2003; @drechsler_synthetic_2011].
-However, these variance estimators are not the same.
+Similarly to multiple imputation of missing data, correct inferences from synthetic data requires correct pooling over the multiply imputed datasets.
+
+Obtaining a final point estimate of the parameter of interest $Q$ after imputation is fairly easy and no different from pooling in the case of missing data [@rubin_multiple_1987].
+One can calculate the average of the $m$ point estimates $q^{(l)}$
+$$
+\bar{q}_m = \sum_{l = 1}^m \frac{q^{(l)}}{m}.
+$$
+Also similarly to the missing data case, variances, and subsequently confidence intervals, should incorporate the increase in variance that is due to imputation [@reiter_partially_inference_2003; @drechsler_synthetic_2011].
+Yet, the increase in variance due to imputation differs according to whether missing values are imputed or observed data is overimputed with missing values.
 Whereas the variance estimate after imputation of missing data needs to account for the fact that a certain amount of information in the data is missing, variance estimation from synthetic data does not suffer from this issue.
 The adjusted variance estimate that follows from using multiple synthetic datasets only suffers from the fact that a finite number of $m$ synthetic datasets are used to resemble the observed data.
-Hence, the according pooling rules for synthetic data as developed by @reiter_partially_inference_2003 are
+Hence, the according variance estimate for synthetic data as developed by @reiter_partially_inference_2003 yields
+$$
+T = \bar{u}_m + \frac{b_m}{m},
+$$
+with "between-imputation" variance
 
-\begin{aligned}
+$$
+b_m = \sum_{l = 1}^m \frac{(q^{(l)} - \bar{q}_m)^2}{(m - 1)}, \\
+$$
+and "within-imputation" variance
+$$
+\bar{u}_m = \sum_{l = 1} \frac{u^{(l)}}{m},
+$$
+with $u^{(l)}$ reflecting the variance estimate in every imputed dataset.
 
-\bar{q}_m &= \sum_{l = 1}^m \frac{q^{(l)}}{m}, \\
-
-b_m       &= \sum_{l = 1}^m \frac{(q^{(l)} - \bar{q}_m)^2}{(m - 1)}, \\
-
-\bar{u}_m &= \sum_{l = 1} \frac{u^{(l)}}{m}.
-
-\end{aligned}
+## Simulation results
 

### 2021-09-30 mice_synthesizing/paper.Rmd
Add some figures for result section.

@@
 
+# Variable plots
+
+```{r}
+## Merely illustrative, single dataset, plot of age
+synthetic_samples[[1]] %>% 
+  complete(action = "long", include = TRUE) %>%
+  mutate(Synthetic = ifelse(.imp == 0, "Real data", "Synthetic data")) %>%
+  ggplot(mapping = aes(x = age, y = ..density.., fill = Synthetic)) +
+  geom_histogram(position = "dodge") +
+  scale_fill_brewer(palette = "Paired") +
+  theme_classic()
+
+## Merely illustrative, single dataset, plot of gen
+
+synthetic_samples[[234]] %>%
+  complete(action = "long", include = TRUE) %>% 
+  mutate(Synthetic = ifelse(.imp == 0, "Real data", "Synthetic data")) %>%
+  ggplot(mapping = aes(x = gen, fill = Synthetic, group = Synthetic)) +
+  geom_bar(aes(y = ..prop..), position = "dodge2") +
+  scale_fill_brewer(palette = "Paired") +
+  theme_classic()
+
+## Merely illustrative, single dataset, plot of bmi by region
+synthetic_samples[[678]] %>%
+  complete(action = "long", include = TRUE) %>%
+  mutate(Synthetic = ifelse(.imp == 0, "Real data", "Synthetic data")) %>%
+  ggplot(mapping = aes(x = reg, y = bmi, fill = Synthetic)) +
+  geom_boxplot() +
+  scale_fill_brewer(palette = "Paired") +
+  theme_classic()
+```
+
+# Parameter plots
+
+```{r}
+# Univariate -- sampling distribution of the mean of age
+synthetic_samples %>%
+  map_dfr(function(x) {
+    x %>%
+      complete(action = "long", include = TRUE) %>%
+      mutate(Synthetic = ifelse(.imp == 0, "Real data", "Synthetic data")) %>%
+      group_by(Synthetic) %>%
+      dplyr::summarize(`Mean age` = mean(age))
+}) %>%
+  ggplot(mapping = aes(x = `Mean age`, y = ..density.., fill = Synthetic)) +
+  geom_histogram(position = "dodge") +
+  scale_fill_brewer(palette = "Paired") +
+  theme_classic()
+
+# Univariate -- sampling distribution of the proportion of cases in 
+# every gen category
+synthetic_samples %>%
+  map_dfr(function(x) {
+    x %>%
+      complete(action = "long", include = TRUE) %>% 
+      mutate(Synthetic = ifelse(.imp == 0, "Real data", "Synthetic data")) %>%
+      group_by(Synthetic, gen) %>%
+      dplyr::summarize(number = n(), .groups = "drop") %>%
+      group_by(Synthetic) %>%
+      mutate(prop = number / sum(number))
+  }) %>%
+  ggplot(aes(x = gen, y = prop, fill = Synthetic)) +
+  geom_boxplot() +
+  scale_fill_brewer(palette = "Paired") +
+  theme_classic()
+
+bind_rows(`Real data`      = select(true_age, 
+                                    Variable = term, 
+                                    Estimate = estimate),
+          `Synthetic data` = select(synthetic_age, 
+                                    Variable = term, 
+                                    Estimate = estimate),
+          .id = "Synthetic") %>%
+  ggplot(aes(x = Estimate, fill = Synthetic)) +
+  geom_density(alpha = 0.8) +
+  scale_fill_brewer(palette = "Set1") +
+  theme_classic() +
+  facet_wrap(~Variable, scales = "free")
+
+bind_rows(`Real data`      = select(true_wgt, 
+                                    Variable = term, 
+                                    Estimate = estimate),
+          `Synthetic data` = select(synthetic_wgt, 
+                                    Variable = term, 
+                                    Estimate = estimate),
+          .id = "Synthetic") %>%
+  ggplot(aes(x = Estimate, fill = Synthetic)) +
+  geom_density(alpha = 0.8) +
+  scale_fill_brewer(palette = "Set1") +
+  theme_classic() +
+  facet_wrap(~Variable, scales = "free")
+
+bind_rows(`Real data`      = select(true_gen,
+                                    Variable = term, 
+                                    Estimate = estimate),
+          `Synthetic data` = select(synthetic_gen,
+                                    Variable = term,
+                                    Estimate = estimate),
+          .id = "Synthetic") %>%
+  ggplot(aes(x = Estimate, fill = Synthetic)) +
+  geom_density(alpha = 0.8) +
+  scale_fill_brewer(palette = "Set1") +
+  theme_classic() +
+  facet_wrap(~Variable, nrow = 4, scales = "free") +
+  theme(legend.position = "right")
+```
+
 ```{r eval = FALSE}

### 2021-10-03 mice_synthesizing/paper.Rmd
Some changes + conclusion

@@
 ---
-title: "Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*"
-subtitle: "Anony*mice*d shareable data: Using *mice* to create multiply imputed synthetic datasets" 
+title: "Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic data sets with *mice*"
+subtitle: "Anony*mice*d shareable data: Using *mice* to create multiply imputed synthetic data sets" 
 author:
@@
 - [x] `mice` can only be exploited if the statistical properties are correct.
-- [x] In this paper we demonstrate a straightforward workflow for generating synthetic datasets and we investigate how to obtain valid inferences from synthesized data.
+- [x] In this paper we demonstrate a straightforward workflow for generating synthetic data sets and we investigate how to obtain valid inferences from synthesized data.
 
@@
 An alternative solution has been proposed separately by @rubin_statistical_disclosure_1993 and @little_statistical_1993.
-Although their approaches differ to some extent, the overarching procedure is to use bonafide observed data to generate multiply imputed synthetic datasets that can be freely disclosed.
+Although their approaches differ to some extent, the overarching procedure is to use bonafide observed data to generate multiply imputed synthetic data sets that can be freely disclosed.
 While in practice, one could see this as replacing the observed data values by multiple draws from the posterior predictive distribution of the observed data, based on some imputation model, Rubin would argue that these synthetic data values are merely draws from the same true data generating model.
 In that sense, the observed data is never replaced, but the population is resampled from the information captured in the (incomplete) sample.
-Using this approach, the researcher could replace the observed dataset as a whole with multiple synthetic versions.
+Using this approach, the researcher could replace the observed data set as a whole with multiple synthetic versions.
 Alternatively, the researcher could opt to only replace a subset of the observed data.
-For example, one can choose to only replace dimensions in the data that could be compared with publicly available datasets or registers.
+For example, one can choose to only replace dimensions in the data that could be compared with publicly available data sets or registers.
 Likewise, synthetisation could be limited to those values that are disclosive, such as high incomes or high turnovers.
@@
 Instead of replacing just the missing values with multiple draws from the posterior predictive distribution, one could easily *overimpute* any observed sensitive values.
-Similarly to multiple imputation of missing data, the multiple synthetic datasets allow for correct statistical inferences, **regardless of the fact that the analyses do not use the "true" value**.
-The analyses over multiple synthetic datasets should be pooled into a single inference, so that the researcher can draw valid conclusions from the pooled results.
+Similarly to multiple imputation of missing data, the multiple synthetic data sets allow for correct statistical inferences, **regardless of the fact that the analyses do not use the "true" value**.
+The analyses over multiple synthetic data sets should be pooled into a single inference, so that the researcher can draw valid conclusions from the pooled results.
 To that respect, the variance should reflect the added variability that is induced by the imputation procedure.
@@
 Conversely, if the models used to create the synthetic data are able to preserve the relationships between the variables as in the original data, the synthetic data can be nearly as informative as the observed data.
-Thus, to fully exploit the benefits of synthetic data, the effort to actually create these high-quality datasets should be kept at a minimum.
+Thus, to fully exploit the benefits of synthetic data, the effort to actually create these high-quality data sets should be kept at a minimum.
 
-To mitigate additional effort of creating synthetic datasets on behalf of the researcher, software aimed at multiple imputation of missing data can be employed.
-Especially if researchers used this software at an earlier stage in the research process, or acquired familiarity with it during earlier projects, the additional burden of creating synthetic datasets is relatively small.
+To mitigate additional effort of creating synthetic data sets on behalf of the researcher, software aimed at multiple imputation of missing data can be employed.
+Especially if researchers used this software at an earlier stage in the research process, or acquired familiarity with it during earlier projects, the additional burden of creating synthetic data sets is relatively small.
 The R-package `mice` [@mice] implements multiple imputation of missing data in a straightforward and user-friendly manner.
 However, the functionality of `mice` is not restricted to the imputation of missing data, but allows to impute any value in the data: even observed values.
-Consequently, `mice` can be utilized for the creation of multiply imputed synthetic datasets.
+Consequently, `mice` can be utilized for the creation of multiply imputed synthetic data sets.
 
-After creating the multiply imputed synthetic datasets, the goal is to obtain valid statistical inferences in the spirit of @rubin_multiple_1987 and @neyman1934.
-In the missing data framework, this is done by performing statistical analyses on all imputed datasets, and pooling the results of the analyses according to Rubin's rules [@rubin_multiple_1987, pp.76].
-In the synthetic data framework, the same procedure is followed, but with a slight twist: there are no values that remain constant over the synthetic datasets.
-The procedure of drawing valid inferences from multiple synthetic datasets is therefore slightly different.
+After creating the multiply imputed synthetic data sets, the goal is to obtain valid statistical inferences in the spirit of @rubin_multiple_1987 and @neyman1934.
+In the missing data framework, this is done by performing statistical analyses on all imputed data sets, and pooling the results of the analyses according to Rubin's rules [@rubin_multiple_1987, pp.76].
+In the synthetic data framework, the same procedure is followed, but with a slight twist: there are no values that remain constant over the synthetic data sets.
+The procedure of drawing valid inferences from multiple synthetic data sets is therefore slightly different.
 
@@
 Note that the predictor matrix $Y_{-j}$ may contain yet imputed values from an earlier imputation step, and thus will be updated after every iteration.
-This procedure is applied $m$ times, resulting in $m$ completed datasets $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $\textbf{D}^{(l)} = (\textbf{Y}_{obs}, Y^{(l)}_{mis})$.
+This procedure is applied $m$ times, resulting in $m$ completed data sets $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $\textbf{D}^{(l)} = (\textbf{Y}_{obs}, Y^{(l)}_{mis})$.
 
-In `mice`, the generation of multiply imputed datasets to solve for unobserved values is straightforward.
-The following pseudocode details the multiple imputation of the `mice::boys` dataset [@fredriks_boys_2000] into the object `imp` with `m = 10` imputated sets and `maxit = 7` iterations for the algorithm to converge, using the default imputations methods for each column data class.
+In `mice`, the generation of multiply imputed data sets to solve for unobserved values is straightforward.
+The following pseudocode details the multiple imputation of the `mice::boys` data set [@fredriks_boys_2000] into the object `imp` with `m = 10` imputated sets and `maxit = 7` iterations for the algorithm to converge, using the default imputations methods for each column data class.
 
@@
 Accordingly, the data consists of values that are to be replaced and values that are to be kept (i.e., $\textbf{Y} = (\textbf{Y}_{rep}, \textbf{Y}_{nrep})$.
-Now, instead of imputing $\textbf{Y}_{mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, $\textbf{Y}_{rep}$ is imputed from the posterior distribution of $P(Y^{(l)}_{j, rep} | \textbf{Y}^{(l)}_{-j}, \textbf{Z}, \theta)$, where $l$ is an indicator for the synthetic dataset ($l = 1, 2, \dots, m$).
+Now, instead of imputing $\textbf{Y}_{mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, $\textbf{Y}_{rep}$ is imputed from the posterior distribution of $P(Y^{(l)}_{j, rep} | \textbf{Y}^{(l)}_{-j}, \textbf{Z}, \theta)$, where $l$ is an indicator for the synthetic data set ($l = 1, 2, \dots, m$).
 Note that synthetic values that are imputed at an earlier step can be used for imputing variable $j$.
@@
 
-For example, overimputing synthetic values for both the observed and missing cells in the `mice::boys` dataset into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution.
+For example, overimputing synthetic values for both the observed and missing cells in the `mice::boys` data set into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution.
 
@@
 where the argument `where` requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix) containing logicals $z_{ij}$ that indicate which cells are selected to have their values replaced by draws from the posterior predictive distribution.
-This approach allows to *overimpute* a subset of the observed data, or - as in the above example - the observed data as a whole, resulting in a dataset that partly or completely consists of synthetic data values.
+This approach allows to *overimpute* a subset of the observed data, or - as in the above example - the observed data as a whole, resulting in a data set that partly or completely consists of synthetic data values.
 
@@
 
-In a nutshell, the above code shows the simplicity of creating $m = 10$ synthetic datasets using `mice`.
+In a nutshell, the above code shows the simplicity of creating $m = 10$ synthetic data sets using `mice`.
 In practice, however, one should take some additional complicating factors into account.
@@
 
-We will show the suitability of using `mice` for synthesization using a simulation study, using the `boys` data.
-This dataset consists of the values of $`r nrow(mice::boys)`$ Dutch boys on the following $`r ncol(mice::boys)`$ variables: age (in years), height (in cm), weight (in kg), body mass index (BMI), head circumference (in cm), Genital Tanner stage (G1-G5), testicular volume (in ml) and region.
-Unfortunately, this dataset does not differ from the vast majority of collected datasets, in the sense that it suffers from missing data.
-For simplicity, the data is completed using the default `mice` imputation model for all predictors except BMI, which is imputed using a passive imputation model due to the deterministic relation with weight and height ($\text{BMI} = \frac{\text{weight}}{\text{height (in meters)}^2}$) to create a single, fully observed dataset:
+We demonstrate the suitability of using `mice` for synthesization using a simulation study on the `mice::boys` data set.
+This data set consists of the values of $`r nrow(mice::boys)`$ Dutch boys on the following $`r ncol(mice::boys)`$ variables:
+
+| column | description                |
+|--------|----------------------------|
+| age    | age in years               |
+| hgt    | height (cm)                |
+| wgt    | weight (kg)                |
+| bmi    | body mass index            |
+| hc     | head circumference (cm)    |
+| gen    | genital Tanner stage G1-G5 |
+| phb    | pubic hair Tanner P1-P6    |
+| tv     | testicular volume (ml)     |
+| reg    | region                     |
+
+Unfortunately, this data set does not differ from the vast majority of collected data sets, in the sense that it suffers from missing data.
+For simplicity, the data is completed using the default `mice` imputation model for all predictors except `bmi`, which is imputed using a passive imputation model due to the deterministic relation with weight and height ($\text{BMI} = \frac{\text{weight}}{\text{height (in meters)}^2}$) to create a single, fully observed data set:
 
@@
 ```{r, results = FALSE, message = FALSE, warning = FALSE}
-# create a single imputed, completely observed `boys` dataset
+# create a single imputed, completely observed `boys` data set
 set.seed(123)
@@
 In the current example, the complexity parameter is specified at `cp = 1e-08` rather than the default value `1e-04`, and the minimum number of observations in each terminal node is set at `minbucket` $= 3$ rather than the default value $5$.
-By allowing for more complexity in the imputation model, bias in the estimates from the synthetic dataset is reduced.
+By allowing for more complexity in the imputation model, bias in the estimates from the synthetic data set is reduced.
 Additionally, since the missingness pattern is monotone, the number of iterations can be set to `maxit = 1`.
@@
 Subsequently, the bias in the parameters and the $95\%$ confidence interval coverage of the synthetic data will be examined.
-Similarly to multiple imputation of missing data, correct inferences from synthetic data requires correct pooling over the multiply imputed datasets.
+Similarly to multiple imputation of missing data, correct inferences from synthetic data requires correct pooling over the multiply imputed data sets.
 
@@
 Whereas the variance estimate after imputation of missing data needs to account for the fact that a certain amount of information in the data is missing, variance estimation from synthetic data does not suffer from this issue.
-The adjusted variance estimate that follows from using multiple synthetic datasets only suffers from the fact that a finite number of $m$ synthetic datasets are used to resemble the observed data.
+The adjusted variance estimate that follows from using multiple synthetic data sets only suffers from the fact that a finite number of $m$ synthetic data sets are used to resemble the observed data.
 Hence, the according variance estimate for synthetic data as developed by @reiter_partially_inference_2003 yields
@@
 $$
-with $u^{(l)}$ reflecting the variance estimate in every imputed dataset.
+with $u^{(l)}$ reflecting the variance estimate in every imputed data set.
 
 ## Simulation results
-
 ```{r, message = FALSE, warning = FALSE, cache = TRUE, cache.lazy = FALSE}
@@
 
-nsim <- 1000 # use 1000 iterations
+nsim <- 10 # use 1000 iterations
 
@@
 ```{r}
-## Merely illustrative, single dataset, plot of age
+## Merely illustrative, single data set, plot of age
 synthetic_samples[[1]] %>% 
@@
 
-## Merely illustrative, single dataset, plot of gen
+## Merely illustrative, single data set, plot of gen
 
@@
 
-## Merely illustrative, single dataset, plot of bmi by region
+## Merely illustrative, single data set, plot of bmi by region
 synthetic_samples[[678]] %>%
@@
 
+We demonstrated that generating synthetic data sets with `mice` in `R` is a straightforward process that fits well in a data analysis pipeline.
+The multiple synthetic sets yield valid inferences about the true underlying data generating mechanism, thereby capturing the nature of the original data.
+This makes the multiple synthetisation procedure with `mice` suitable for further dissemination of synthetic data sets.
+
+To non-statisticians, the procedure of generating multiple synthetic sets may seem overly complicated.
+We would like to emphasize that analyzing a single synthesized set, while perhaps unbiased, would underestimate the variance properties that are so important in drawing statistical inferences from finite data sets.
+After all, we are often not interested in the sample at hand, but in the underlying data generating mechanism, such as the population.
+Properly capturing the uncertainty of synthetic data sets, just like with incomplete data sets, is therefore paramount.
+
+That said, while the field of data synthetisation originated decades ago, it is more relevant today than ever.
+In our study we outline a standard research workflow where the goal is to synthesize a complete data set.
+To simplify the simulation we adopted a bootstrapping scheme to induce sampling variance in order to conform to the combination procedure defined by @reiter_partially_inference_2003.
+Ideally, one would like to omit the bootstrap from the synthetization to adopt a scheme where the sampled data itself serves as a reference: much like the procedure outlined in @vink2014poolingadopt for incomplete data simulation.
+The corresponding pooling rules have not been derived yet and the incorporation in data analysis workflows would require proper attention from developers alike.
+
+There are other developments that can generate synthetic data sets.
+For example, the `synthpop` [REF] package in `R` would yield valid synthetic data sets if and only if the *true* data is completely observed.
+When the data is not completely observed, the single-iteration monotone set-up of the algorithm will bias estimates [REF IBRAHIM].
+To avoid this, one could adopt a two-step approach wherein the incomplete values are multiply imputed before synthetization.
+Given $m$ multiple imputations and synthetizations, at least $m^2$ synthetic data sets are then in order.
+The flexibility with `mice` is that both unobserved and observed data values can be synthesized at once, without the need for a two-step approach.
+With `mice` $m$ synthetic sets are sufficient.
+
+The ease of use when synthesizing data with `mice` in `R`, together with the validity of inferences obtained through this procedure opens up a wealth of possibilities for data dissemination and further research of initially private data.
+
 ```{r}
@@
 This joint density is generally hard or impossible to derive, which can be overcome by employing fully conditional specification (FCS).
-Consider a $n \times k$ data matrix $Y$, with values to be replaced $Y^{old}$, the values to be kept $Y^{keep}$ and the values that are already replaced $Y^{new}$, under the assumption that there are no missing values in the observed dataset.
+Consider a $n \times k$ data matrix $Y$, with values to be replaced $Y^{old}$, the values to be kept $Y^{keep}$ and the values that are already replaced $Y^{new}$, under the assumption that there are no missing values in the observed data set.
 Instead of drawing from the joint distribution, we draw from $k$ univariate conditional densities for each variable.
@@
 Thus, the synthetic values are generated variable by variable.
-This procedure is executed $i = 1, 2, \dots, m$ times, resulting in $\textbf{D} = \{D^{(1)}, \dots, D^{(m)}\}$ synthetic datasets, with $D^{(i)} = (Y^{keep}, Y^{i, new})$.
+This procedure is executed $i = 1, 2, \dots, m$ times, resulting in $\textbf{D} = \{D^{(1)}, \dots, D^{(m)}\}$ synthetic data sets, with $D^{(i)} = (Y^{keep}, Y^{i, new})$.
 
@@
 
-The goal then is to release multiply imputed datasets that bear no risk of releasing confidential or identifying information, while the multivariate relationships should be preserved as in the observed data.
+The goal then is to release multiply imputed data sets that bear no risk of releasing confidential or identifying information, while the multivariate relationships should be preserved as in the observed data.
 
@@
 
-An alternative has been offered by @rubin_statistical_disclosure_1993, who, building on the framework of multiple imputation, proposed to release multiple synthetic datasets to the public.
+An alternative has been offered by @rubin_statistical_disclosure_1993, who, building on the framework of multiple imputation, proposed to release multiple synthetic data sets to the public.
 Conform this approach, all units that are in the population but not in the sample are treated as missing data.
@@
 In practice, it is not required to impute the complete population, since random samples can be drawn from the sampling frame, so that only these sampled values have to be imputed.
-The datasets generated under this approach are labelled as *fully synthetic datasets*.
+The data sets generated under this approach are labelled as *fully synthetic data sets*.
 However, note that, if one draws simple random samples from the sampling frame, the possibility exists that actual observations are included.
 
-A second procedure to creating synthetic datasets has been proposed by @little_statistical_1993, named *partially synthetic datasets*, which originated as a procedure that required synthesizing only those values that are at a high risk of being disclosive.
-These values can be complete variables that could be compared with publicly available datasets or registers, such as addresses, or it can be certain values that bear a high risk of being disclosive, say, income values above a certain threshold.
-Similarly to the fully synthetic data approach, multiple datasets containing synthetic values are released to the public, although in this instance, only the values at a high risk vary over the synthetic datasets.
-However, nothing keeps us from treating all values in the dataset as bearing a high disclosure risk, resulting in datasets that are completely existing of synthetic values.
+A second procedure to creating synthetic data sets has been proposed by @little_statistical_1993, named *partially synthetic data sets*, which originated as a procedure that required synthesizing only those values that are at a high risk of being disclosive.
+These values can be complete variables that could be compared with publicly available data sets or registers, such as addresses, or it can be certain values that bear a high risk of being disclosive, say, income values above a certain threshold.
+Similarly to the fully synthetic data approach, multiple data sets containing synthetic values are released to the public, although in this instance, only the values at a high risk vary over the synthetic data sets.
+However, nothing keeps us from treating all values in the data set as bearing a high disclosure risk, resulting in data sets that are completely existing of synthetic values.
 This approach basically implements the idea of fully synthetic data, based on the partially synthetic data procedure.
@@
 
-As of today, most papers in this field address methodological issues concerning both fully and partially synthetic datasets, both with regard to analysis methods suitable for creating synthetic data, and concerning inferential procedures.
+As of today, most papers in this field address methodological issues concerning both fully and partially synthetic data sets, both with regard to analysis methods suitable for creating synthetic data, and concerning inferential procedures.
 The current paper aims at reducing the gap between the theory about synthetic data, and generating synthetic data in practice.
@@
 Since `mice` is currently only capable of imputing the data at hand, the approach should be labelled as *partially synthetic*.
-That is, although it is completely possible to create a synthetic dataset that consists of only synthetic values, `mice` is not (yet) capable of imputing observations that are not present in the data.
-Creating fully synthetic datasets by means of `mice` remains an area of future research.
+That is, although it is completely possible to create a synthetic data set that consists of only synthetic values, `mice` is not (yet) capable of imputing observations that are not present in the data.
+Creating fully synthetic data sets by means of `mice` remains an area of future research.
 
@@
  - All fun and game, but statistical properties should be intact
- - In this paper we demonstrate a straigthforward workflow for generating synthetic datasets and we investigate how to obtain valid inferences from synthesized data.
+ - In this paper we demonstrate a straigthforward workflow for generating synthetic data sets and we investigate how to obtain valid inferences from synthesized data.
 

### 2021-10-04 mice_synthesizing/paper.Rmd
Update paper and .gitignore file.

--- 2021-09-30 mice_synthesizing/paper.Rmd
@@
 author:
-- Thom Volker & Gerko Vink
+- Thom Volker^[Helpful and stimulating discussions with Stef van Buuren, Hanne Oberman, Paulina von Stackelberg, Mirthe Hendriks and Stijn Overbeek are gratefully acknowledged.] & Gerko Vink
 date: "`r format(Sys.time(), '%d-%m-%Y')`"

### 2021-10-04 mice_synthesizing/paper.Rmd
update results

--- 2021-10-03 mice_synthesizing/paper.Rmd
@@
 Unfortunately, this data set does not differ from the vast majority of collected data sets, in the sense that it suffers from missing data.
-For simplicity, the data is completed using the default `mice` imputation model for all predictors except `bmi`, which is imputed using a passive imputation model due to the deterministic relation with weight and height ($\text{BMI} = \frac{\text{weight}}{\text{height (in meters)}^2}$) to create a single, fully observed data set:
+For simplicity, the data is completed using the default `mice` imputation model for all predictors except `bmi`, which is passively imputed using its deterministic relation with weight and height.
 
@@
 library(mice)
+library(tibble)
 library(magrittr)
@@
 library(furrr)
+library(knitr)
+library(kableExtra)
+library(psych)
+library(purrr)
+library(dplyr)
 library(knitr)
@@
 
-To induce an appropriate amount of sampling variance, 1000 bootstrap samples of the `boys` data will be synthesized with $m = 5$ imputations.
-The data will be synthesized using the `CART` imputation method for all predictors except BMI, which will be synthesized using passive imputation according to the model `~I(wgt / (hgt / 100)^2)`.
+To induce sampling variance, 1000 bootstrap samples of the `boys` data will be synthesized with $m = 5$ imputations.
+Synthetic values are generated using the `CART` imputation method for all columns, except for `bmi`.
+The deterministic relation `bmi` which will be synthesized passively based on the synthetic values for `hgt` and `wgt` to preserve the relation in the synthetic data.
 Additional parameters that come with the use of `mice.impute.cart()` are the complexity parameter `cp` and the minimum number of observations in any terminal node `minbucket`, that both constrain the flexibility of the imputation model.
@@
 $$
-Also similarly to the missing data case, variances, and subsequently confidence intervals, should incorporate the increase in variance that is due to imputation [@reiter_partially_inference_2003; @drechsler_synthetic_2011].
+with $l = 1, \dots, m$.
+
+Similarly to the missing data case, variances, and subsequently confidence intervals, should incorporate the increase in variance that is due to imputation [@reiter_partially_inference_2003; @drechsler_synthetic_2011].
 Yet, the increase in variance due to imputation differs according to whether missing values are imputed or observed data is overimputed with missing values.
@@
 $$
-with "between-imputation" variance
+with between variance
 
@@
 $$
-and "within-imputation" variance
+and sampling variance
 $$
@@
 $$
-with $u^{(l)}$ reflecting the variance estimate in every imputed data set.
+with $u^{(l)}$ reflecting the variance estimate in the $l$th synthetic data set.
 
-## Simulation results
+# Simulation results
 ```{r, message = FALSE, warning = FALSE, cache = TRUE, cache.lazy = FALSE}
@@
 
-nsim <- 10 # use 1000 iterations
+nsim <- 1000 # use 1000 iterations
 
@@
 
+## Univariate estimates
+The univariate descriptives for the original data and the synthetic data can be found in the folowing table. [TABLE REF]
+```{r}
+true <- psych::describe(data)
+
+synth <- synthetic_samples %>% 
+  map(~.x %>% complete("all") %>% 
+        map(~.x %>% describe()) %>% Reduce("+", .) / synthetic_samples[[1]]$m) %>% 
+  Reduce("+", .) / length(synthetic_samples)
+rownames(true) <- paste("original", rownames(true), sep = " ")
+rownames(synth) <- paste("synthetic", rownames(synth), sep = " ")
+
+bind_rows(true, setNames(synth, names(true))) %>% 
+           arrange(vars) %>% .[, c(2:5, 8:9, 11:12)] %>% round(3)
+```
+
+$$
+% latex table generated in R 4.1.0 by xtable 1.8-4 package
+% Sun Oct  3 23:20:37 2021
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrrrrrrr}
+  \hline
+ & n & mean & sd & median & min & max & skew & kurtosis \\ 
+  \hline
+age & 748.00 & 9.16 & 6.89 & 10.50 & 0.04 & 21.18 & -0.03 & -1.56 \\ 
+  age\_synth & 748.00 & 9.23 & 6.91 & 10.51 & 0.04 & 20.93 & -0.05 & -1.56 \\ 
+  hgt & 748.00 & 131.10 & 46.52 & 145.75 & 50.00 & 198.00 & -0.30 & -1.47 \\ 
+  hgt\_synth & 748.00 & 131.59 & 46.72 & 146.09 & 50.71 & 197.47 & -0.30 & -1.47 \\ 
+  wgt & 748.00 & 37.12 & 26.03 & 34.55 & 3.14 & 117.40 & 0.38 & -1.03 \\ 
+  wgt\_synth & 748.00 & 37.44 & 26.23 & 34.87 & 3.36 & 113.04 & 0.36 & -1.05 \\ 
+  bmi & 748.00 & 18.04 & 3.04 & 17.45 & 11.73 & 31.74 & 1.14 & 1.79 \\ 
+  bmi\_synth & 748.00 & 18.04 & 3.10 & 17.44 & 11.41 & 32.09 & 1.09 & 1.70 \\ 
+  hc & 748.00 & 51.62 & 5.86 & 53.10 & 33.70 & 65.00 & -0.91 & 0.12 \\ 
+  hc\_synth & 748.00 & 51.65 & 5.88 & 53.19 & 34.30 & 62.12 & -0.93 & 0.16 \\ 
+  gen* & 748.00 & 2.53 & 1.59 & 2.00 & 1.00 & 5.00 & 0.52 & -1.36 \\ 
+  gen*\_synth & 748.00 & 2.58 & 1.59 & 2.00 & 1.00 & 5.00 & 0.47 & -1.40 \\ 
+  phb* & 748.00 & 2.75 & 1.86 & 2.00 & 1.00 & 6.00 & 0.56 & -1.25 \\ 
+  phb*\_synth & 748.00 & 2.80 & 1.88 & 2.00 & 1.00 & 6.00 & 0.52 & -1.30 \\ 
+  tv & 748.00 & 8.43 & 8.12 & 3.00 & 1.00 & 25.00 & 0.85 & -0.78 \\ 
+  tv\_synth & 748.00 & 8.65 & 8.23 & 3.39 & 1.00 & 25.00 & 0.80 & -0.88 \\ 
+  reg* & 748.00 & 3.02 & 1.14 & 3.00 & 1.00 & 5.00 & -0.08 & -0.77 \\ 
+  reg*\_synth & 748.00 & 3.03 & 1.13 & 3.00 & 1.00 & 5.00 & -0.07 & -0.73 \\ 
+   \hline
+\end{tabular}
+\end{table}
+$$
+
+We see that the synthetic data estimates resemble the true data estimates very well.
+
 # Variable plots
@@
 
-synthetic_samples[[234]] %>%
+synthetic_samples[[2]] %>%
   complete(action = "long", include = TRUE) %>% 
@@
 ## Merely illustrative, single data set, plot of bmi by region
-synthetic_samples[[678]] %>%
+synthetic_samples[[3]] %>%
   complete(action = "long", include = TRUE) %>%
@@
 To simplify the simulation we adopted a bootstrapping scheme to induce sampling variance in order to conform to the combination procedure defined by @reiter_partially_inference_2003.
-Ideally, one would like to omit the bootstrap from the synthetization to adopt a scheme where the sampled data itself serves as a reference: much like the procedure outlined in @vink2014poolingadopt for incomplete data simulation.
+Ideally, one would like to omit the bootstrap from the synthetization to adopt a scheme where the sampled data itself serves as a reference: much like the procedure outlined in @vink2014pooling for incomplete data simulation.
 The corresponding pooling rules have not been derived yet and the incorporation in data analysis workflows would require proper attention from developers alike.

### 2021-10-04 mice_synthesizing/paper.Rmd
Rerun paper for correct cached file.

--- 2021-10-04 mice_synthesizing/paper.Rmd
@@
 $$
-with "between-imputation" variance
+with between-imputation variance
 
@@
 $$
-and "within-imputation" variance
+and within-imputation variance
 $$
@@
 ## Simulation results
+
 ```{r, message = FALSE, warning = FALSE, cache = TRUE, cache.lazy = FALSE}

### 2021-10-04 mice_synthesizing/paper.Rmd

--- 2021-10-04 mice_synthesizing/paper.Rmd
@@
 $$
-with between variance
+
+with between-imputation variance
 
@@
 and sampling variance
+
 $$
@@
 # Simulation results
+
 ```{r, message = FALSE, warning = FALSE, cache = TRUE, cache.lazy = FALSE}

### 2021-10-04 manuscript/Manuscript.Rmd

---
title: "Anony*mice*d shareable data: Using *mice* to create and analyze multiply imputed synthetic data sets"
author:
  - name: Thom Volker
    affil: 1,*
    orcid: 0000-0003-3293-2315
  - name: Gerko Vink
    affil: 1, \dagger
    orcid: 0000-0001-9767-1924
affiliation:
  - num: 1
    address: |
      Utrecht University - 
      Department of Methodology and Statistics
      Padualaan 14, 3584CH Utrecht, the Netherlands
# firstnote to eighthnote
firstnote: |
  These authors contributed equally to this work.
correspondence: |
  t.b.volker@uu.nl.
journal: psych
type: article
status: submit
bibliography: mybibfile.bib
appendix: appendix.tex
simplesummary: |
  A Simple summary goes here.
abstract: |
  A single paragraph of about 200 words maximum. For research articles, 
  abstracts should give a pertinent overview of the work. We strongly encourage
  authors to use the following style of structured abstracts, but without 
  headings: 1) Background: Place the question addressed in a broad context and
  highlight the purpose of the study; 2) Methods: Describe briefly the main
  methods or treatments applied; 3) Results: Summarize the article's main 
  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
  The abstract should be an objective representation of the article, it must not 
  contain results which are not presented and substantiated in the main text and 
  should not exaggerate the main conclusions.
keywords: |
  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
  to the article, yet reasonably common within the subject discipline.).
acknowledgement: |
  All sources of funding of the study should be disclosed. Please clearly 
  indicate grants that you have received in support of your research work. 
  Clearly state if you received funds for covering the costs to publish in open 
  access.
authorcontributions: |
  For research articles with several authors, a short paragraph specifying their 
  individual contributions must be provided. The following statements should be 
  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
  limited to those who have contributed substantially to the work reported.
conflictsofinterest: |
  Declare conflicts of interest or state 'The authors declare no conflict of 
  interest.' Authors must identify and declare any personal circumstances or
  interest that may be perceived as inappropriately influencing the
  representation or interpretation of reported research results. Any role of the
  funding sponsors in the design of the study; in the collection, analyses or 
  interpretation of data in the writing of the manuscript, or in the decision to 
  publish the results must be declared in this section. If there is no role, 
  please state 'The founding sponsors had no role in the design of the study; 
  in the collection, analyses, or interpretation of data; in the writing of the 
  manuscript, an in the decision to publish the results'.
sampleavailability: |
  Samples of the compounds ...... are available from the authors.
abbreviations:
  - short: MDPI
    long: Multidisciplinary Digital Publishing Institute
  - short: DOAJ
    long: Directory of open access journals
  - short: TLA
    long: Three letter acronym
  - short: LD 
    long: linear dichroism
output: rticles::mdpi_article
---

# Version

This Rmd-skeleton uses the mdpi Latex template published 2019/02. 
However, the official template gets more frequently updated than the 'rticles'
package. Therefore, please make sure prior to paper submission, that you're 
using the most recent .cls, .tex and .bst files 
(available [here](http://www.mdpi.com/authors/latex)).

# Introduction

The introduction should briefly place the study in a broad context and highlight why it is important. It should define the purpose of the work and its significance. The current state of the research field should be reviewed carefully and key publications cited. Please highlight controversial and diverging hypotheses when necessary. Finally, briefly mention the main aim of the work and highlight the principal conclusions. As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research. Citing a journal paper [@bertrand-krajewski_distribution_1998; @leutnant_stormwater_2016]. And now citing a book reference @gujer_systems_2008. Please use the command [@leutnant_stormwater_2016] for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.

# Materials and Methods

Materials and Methods should be described with sufficient details to allow others to replicate and build on published results. Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers. Please disclose at the submission stage any restrictions on the availability of materials or information. New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.

Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers. If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review. They must be provided prior to publication.

Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.

# Results

This section may be divided by subheadings. It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.

## Subsection Heading Here

Subsection text here.

### Subsubsection Heading Here

Bulleted lists look like this:

* First bullet
* Second bullet
* Third bullet

Numbered lists can be added as follows:

1. First item
2. Second item
3. Third item

The text continues here.

All figures and tables should be cited in the main text as Figure 1, Table 1, etc.

\begin{figure}[H]
\centering
\includegraphics[width=3 cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
\midrule
entry 1		& data			& data\\
entry 2		& data			& data\\
\bottomrule
\end{tabular}
\end{table}

This is an example of an equation:

\begin{equation}
\mathbb{S}
\end{equation}
<!-- If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments). This ensures correct linenumbering. The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph. -->

<!-- Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows: -->
Example of a theorem:
\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

Example of a proof:
\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}
The text continues here.

# Discussion

Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses. The findings and their implications should be discussed in the broadest context possible. Future research directions may also be highlighted.

# Conclusion

This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.

# Patents

This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.

### 2021-10-04 manuscript/Manuscript.tex

%  LaTeX support: latex@mdpi.com
%  In case you need support, please attach all files that are necessary for compiling as well as the log file, and specify the details of your LaTeX setup (which operating system and LaTeX version / tools you are using).

%=================================================================
\documentclass[psych,article,submit,moreauthors,pdftex]{mdpi}

% If you would like to post an early version of this manuscript as a preprint, you may use preprint as the journal and change 'submit' to 'accept'. The document class line would be, e.g., \documentclass[preprints,article,accept,moreauthors,pdftex]{mdpi}. This is especially recommended for submission to arXiv, where line numbers should be removed before posting. For preprints.org, the editorial staff will make this change immediately prior to posting.

%% Some pieces required from the pandoc template
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{4pt}}
\setlist[itemize]{leftmargin=*,labelsep=5.8mm}
\setlist[enumerate]{leftmargin=*,labelsep=4.9mm}

\usepackage{longtable}

% see https://stackoverflow.com/a/47122900

%--------------------
% Class Options:
%--------------------
%----------
% journal
%----------
% Choose between the following MDPI journals:
% acoustics, actuators, addictions, admsci, aerospace, agriculture, agriengineering, agronomy, algorithms, animals, antibiotics, antibodies, antioxidants, applsci, arts, asc, asi, atmosphere, atoms, axioms, batteries, bdcc, behavsci , beverages, bioengineering, biology, biomedicines, biomimetics, biomolecules, biosensors, brainsci , buildings, cancers, carbon , catalysts, cells, ceramics, challenges, chemengineering, chemistry, chemosensors, children, cleantechnol, climate, clockssleep, cmd, coatings, colloids, computation, computers, condensedmatter, cosmetics, cryptography, crystals, dairy, data, dentistry, designs , diagnostics, diseases, diversity, drones, econometrics, economies, education, electrochem, electronics, energies, entropy, environments, epigenomes, est, fermentation, fibers, fire, fishes, fluids, foods, forecasting, forests, fractalfract, futureinternet, futurephys, galaxies, games, gastrointestdisord, gels, genealogy, genes, geohazards, geosciences, geriatrics, hazardousmatters, healthcare, heritage, highthroughput, horticulturae, humanities, hydrology, ijerph, ijfs, ijgi, ijms, ijns, ijtpp, informatics, information, infrastructures, inorganics, insects, instruments, inventions, iot, j, jcdd, jcm, jcp, jcs, jdb, jfb, jfmk, jimaging, jintelligence, jlpea, jmmp, jmse, jnt, jof, joitmc, jpm, jrfm, jsan, land, languages, laws, life, literature, logistics, lubricants, machines, magnetochemistry, make, marinedrugs, materials, mathematics, mca, medicina, medicines, medsci, membranes, metabolites, metals, microarrays, micromachines, microorganisms, minerals, modelling, molbank, molecules, mps, mti, nanomaterials, ncrna, neuroglia, nitrogen, notspecified, nutrients, ohbm, particles, pathogens, pharmaceuticals, pharmaceutics, pharmacy, philosophies, photonics, physics, plants, plasma, polymers, polysaccharides, preprints , proceedings, processes, proteomes, psych, publications, quantumrep, quaternary, qubs, reactions, recycling, religions, remotesensing, reports, resources, risks, robotics, safety, sci, scipharm, sensors, separations, sexes, signals, sinusitis, smartcities, sna, societies, socsci, soilsystems, sports, standards, stats, surfaces, surgeries, sustainability, symmetry, systems, technologies, test, toxics, toxins, tropicalmed, universe, urbansci, vaccines, vehicles, vetsci, vibration, viruses, vision, water, wem, wevj

%---------
% article
%---------
% The default type of manuscript is "article", but can be replaced by:
% abstract, addendum, article, benchmark, book, bookreview, briefreport, casereport, changes, comment, commentary, communication, conceptpaper, conferenceproceedings, correction, conferencereport, expressionofconcern, extendedabstract, meetingreport, creative, datadescriptor, discussion, editorial, essay, erratum, hypothesis, interestingimages, letter, meetingreport, newbookreceived, obituary, opinion, projectreport, reply, retraction, review, perspective, protocol, shortnote, supfile, technicalnote, viewpoint
% supfile = supplementary materials

%----------
% submit
%----------
% The class option "submit" will be changed to "accept" by the Editorial Office when the paper is accepted. This will only make changes to the frontpage (e.g., the logo of the journal will get visible), the headings, and the copyright information. Also, line numbering will be removed. Journal info and pagination for accepted papers will also be assigned by the Editorial Office.

%------------------
% moreauthors
%------------------
% If there is only one author the class option oneauthor should be used. Otherwise use the class option moreauthors.

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

%=================================================================
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{xx}
\issuenum{1}
\articlenumber{5}
\pubyear{2019}
\copyrightyear{2019}
%\externaleditor{Academic Editor: name}
\history{Received: date; Accepted: date; Published: date}
\updates{yes} % If there is an update available, un-comment this line

%% MDPI internal command: uncomment if new journal that already uses continuous page numbers
%\continuouspages{yes}

%------------------------------------------------------------------
% The following line should be uncommented if the LaTeX file is uploaded to arXiv.org
%\pdfoutput=1

%=================================================================
% Add packages and commands here. The following packages are loaded in our class file: fontenc, calc, indentfirst, fancyhdr, graphicx, lastpage, ifthen, lineno, float, amsmath, setspace, enumitem, mathpazo, booktabs, titlesec, etoolbox, amsthm, hyphenat, natbib, hyperref, footmisc, geometry, caption, url, mdframed, tabto, soul, multirow, microtype, tikz

%=================================================================
%% Please use the following mathematics environments: Theorem, Lemma, Corollary, Proposition, Characterization, Property, Problem, Example, ExamplesandDefinitions, Hypothesis, Remark, Definition
%% For proofs, please use the proof environment (the amsthm package is loaded by the MDPI class).

%=================================================================
% Full title of the paper (Capitalized)
\Title{Anony\emph{mice}d shareable data: Using \emph{mice} to create and
analyze multiply imputed synthetic data sets}

% Authors, for the paper (add full first names)
\Author{Thom
Volker$^{1,*}$\href{https://orcid.org/0000-0003-3293-2315}{\orcidicon}, Gerko
Vink$^{1,
\dagger}$\href{https://orcid.org/0000-0001-9767-1924}{\orcidicon}}

% Authors, for metadata in PDF
\AuthorNames{Thom Volker, Gerko Vink}

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Utrecht University - Department of Methodology and
Statistics Padualaan 14, 3584CH Utrecht, the Netherlands; \\
}
% Contact information of the corresponding author
\corres{Correspondence: \href{mailto:t.b.volker@uu.nl}{\nolinkurl{t.b.volker@uu.nl}}.}

% Current address and/or shared authorship
\firstnote{These authors contributed equally to this work.}

% The commands \thirdnote{} till \eighthnote{} are available for further notes

% Simple summary
\simplesumm{A Simple summary goes here.}

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{A single paragraph of about 200 words maximum. For research
articles, abstracts should give a pertinent overview of the work. We
strongly encourage authors to use the following style of structured
abstracts, but without headings: 1) Background: Place the question
addressed in a broad context and highlight the purpose of the study; 2)
Methods: Describe briefly the main methods or treatments applied; 3)
Results: Summarize the article's main findings; and 4) Conclusion:
Indicate the main conclusions or interpretations. The abstract should be
an objective representation of the article, it must not contain results
which are not presented and substantiated in the main text and should
not exaggerate the main conclusions.}

% Keywords
\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent
keywords specific to the article, yet reasonably common within the
subject discipline.).}

% The fields PACS, MSC, and JEL may be left empty or commented out if not applicable
%\PACS{J0101}
%\MSC{}
%\JEL{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Diversity
%\LSID{\url{http://}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Applied Sciences:
%\featuredapplication{Authors are encouraged to provide a concise description of the specific application or a potential application of the work. This section is not mandatory.}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Data:
%\dataset{DOI number or link to the deposited data set in cases where the data set is published or set to be published separately. If the data set is submitted and will be published as a supplement to this paper in the journal Data, this field will be filled by the editors of the journal. In this case, please make sure to submit the data set as a supplement when entering your manuscript into our manuscript editorial system.}

%\datasetlicense{license under which the data set is made available (CC0, CC-BY, CC-BY-SA, CC-BY-NC, etc.)}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Only for the journal Toxins
%\keycontribution{The breakthroughs or highlights of the manuscript. Authors can write one or two sentences to describe the most important part of the paper.}

%\setcounter{secnumdepth}{4}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Pandoc citation processing

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\hypertarget{version}{%
\section{Version}\label{version}}

This Rmd-skeleton uses the mdpi Latex template published 2019/02.
However, the official template gets more frequently updated than the
`rticles' package. Therefore, please make sure prior to paper
submission, that you're using the most recent .cls, .tex and .bst files
(available \href{http://www.mdpi.com/authors/latex}{here}).

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The introduction should briefly place the study in a broad context and
highlight why it is important. It should define the purpose of the work
and its significance. The current state of the research field should be
reviewed carefully and key publications cited. Please highlight
controversial and diverging hypotheses when necessary. Finally, briefly
mention the main aim of the work and highlight the principal
conclusions. As far as possible, please keep the introduction
comprehensible to scientists outside your particular field of research.
Citing a journal paper
\citep{bertrand-krajewski_distribution_1998, leutnant_stormwater_2016}.
And now citing a book reference \citet{gujer_systems_2008}. Please use
the command \citep{leutnant_stormwater_2016} for the following MDPI
journals, which use author-date citation: Administrative Sciences, Arts,
Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws,
Religions, Risks, Social Sciences.

\hypertarget{materials-and-methods}{%
\section{Materials and Methods}\label{materials-and-methods}}

Materials and Methods should be described with sufficient details to
allow others to replicate and build on published results. Please note
that publication of your manuscript implicates that you must make all
materials, data, computer code, and protocols associated with the
publication available to readers. Please disclose at the submission
stage any restrictions on the availability of materials or information.
New methods and protocols should be described in detail while
well-established methods can be briefly described and appropriately
cited.

Research manuscripts reporting large datasets that are deposited in a
publicly available database should specify where the data have been
deposited and provide the relevant accession numbers. If the accession
numbers have not yet been obtained at the time of submission, please
state that they will be provided during review. They must be provided
prior to publication.

Interventionary studies involving animals or humans, and other studies
require ethical approval must list the authority that provided approval
and the corresponding ethical approval code.

\hypertarget{results}{%
\section{Results}\label{results}}

This section may be divided by subheadings. It should provide a concise
and precise description of the experimental results, their
interpretation as well as the experimental conclusions that can be
drawn.

\hypertarget{subsection-heading-here}{%
\subsection{Subsection Heading Here}\label{subsection-heading-here}}

Subsection text here.

\hypertarget{subsubsection-heading-here}{%
\subsubsection{Subsubsection Heading
Here}\label{subsubsection-heading-here}}

Bulleted lists look like this:

\begin{itemize}
\tightlist
\item
  First bullet
\item
  Second bullet
\item
  Third bullet
\end{itemize}

Numbered lists can be added as follows:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  First item
\item
  Second item
\item
  Third item
\end{enumerate}

The text continues here.

All figures and tables should be cited in the main text as Figure 1,
Table 1, etc.

\begin{figure}[H]
\centering
\includegraphics[width=3 cm]{logo-mdpi}
\caption{This is a figure, Schemes follow the same formatting. If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel. (\textbf{b}) Description of what is contained in the second panel. Figures should be placed in the main text near to the first time they are cited. A caption on a single line should be centered.}
\end{figure}

\begin{table}[H]
\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
\centering
%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
\begin{tabular}{ccc}
\toprule
\textbf{Title 1}    & \textbf{Title 2}  & \textbf{Title 3}\\
\midrule
entry 1     & data          & data\\
entry 2     & data          & data\\
\bottomrule
\end{tabular}
\end{table}

This is an example of an equation:

\begin{equation}
\mathbb{S}
\end{equation}

Example of a theorem:

\begin{Theorem}
Example text of a theorem.
\end{Theorem}

The text continues here. Proofs must be formatted as follows:

Example of a proof:

\begin{proof}[Proof of Theorem 1]
Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
\end{proof}

The text continues here.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Authors should discuss the results and how they can be interpreted in
perspective of previous studies and of the working hypotheses. The
findings and their implications should be discussed in the broadest
context possible. Future research directions may also be highlighted.

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

This section is not mandatory, but can be added to the manuscript if the
discussion is unusually long or complex.

\hypertarget{patents}{%
\section{Patents}\label{patents}}

This section is not mandatory, but may be added if there are patents
resulting from the work reported in this manuscript.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %% optional
% \supplementary{The following are available online at www.mdpi.com/link, Figure S1: title, Table S1: title, Video S1: title.}
%
% % Only for the journal Methods and Protocols:
% % If you wish to submit a video article, please do so with any other supplementary material.
% % \supplementary{The following are available at www.mdpi.com/link: Figure S1: title, Table S1: title, Video S1: title. A supporting video article is available at doi: link.}

\vspace{6pt}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments{All sources of funding of the study should be
disclosed. Please clearly indicate grants that you have received in
support of your research work. Clearly state if you received funds for
covering the costs to publish in open access.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{For research articles with several authors, a short
paragraph specifying their individual contributions must be provided.
The following statements should be used ``X.X. and Y.Y. conceive and
designed the experiments; X.X. performed the experiments; X.X. and Y.Y.
analyzed the data; W.W. contributed reagents/materials/analysis tools;
Y.Y. wrote the paper.'\,' Authorship must be limited to those who have
contributed substantially to the work reported.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\conflictsofinterest{Declare conflicts of interest or state `The authors
declare no conflict of interest.' Authors must identify and declare any
personal circumstances or interest that may be perceived as
inappropriately influencing the representation or interpretation of
reported research results. Any role of the funding sponsors in the
design of the study; in the collection, analyses or interpretation of
data in the writing of the manuscript, or in the decision to publish the
results must be declared in this section. If there is no role, please
state `The founding sponsors had no role in the design of the study; in
the collection, analyses, or interpretation of data; in the writing of
the manuscript, an in the decision to publish the results'.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\abbreviations{The following abbreviations are used in this manuscript:\\

\noindent
\begin{tabular}{@{}ll}
MDPI & Multidisciplinary Digital Publishing Institute \\
DOAJ & Directory of open access journals \\
TLA & Three letter acronym \\
LD & linear dichroism \\
\end{tabular}}

\input{"appendix.tex"}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Citations and References in Supplementary files are permitted provided that they also appear in the reference list here.

%=====================================
% References, variant A: internal bibliography
%=====================================
%\reftitle{References}
%\begin{thebibliography}{999}
% Reference 1
%\bibitem[Author1(year)]{ref-journal}
%Author1, T. The title of the cited article. {\em Journal Abbreviation} {\bf 2008}, {\em 10}, 142--149.
% Reference 2
%\bibitem[Author2(year)]{ref-book}
%Author2, L. The title of the cited contribution. In {\em The Book Title}; Editor1, F., Editor2, A., Eds.; Publishing House: City, Country, 2007; pp. 32--58.
%\end{thebibliography}

% The following MDPI journals use author-date citation: Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences. For those journals, please follow the formatting guidelines on http://www.mdpi.com/authors/references
% To cite two works by the same author: \citeauthor{ref-journal-1a} (\citeyear{ref-journal-1a}, \citeyear{ref-journal-1b}). This produces: Whittaker (1967, 1975)
% To cite two works by the same author with specific pages: \citeauthor{ref-journal-3a} (\citeyear{ref-journal-3a}, p. 328; \citeyear{ref-journal-3b}, p.475). This produces: Wong (1999, p. 328; 2000, p. 475)

%=====================================
% References, variant B: external bibliography
%=====================================
\reftitle{References}
\externalbibliography{yes}
\bibliography{mybibfile.bib}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% optional
\sampleavailability{Samples of the compounds \ldots\ldots{} are
available from the authors.}

%% for journal Sci
%\reviewreports{\\
%Reviewer 1 comments and authors’ response\\
%Reviewer 2 comments and authors’ response\\
%Reviewer 3 comments and authors’ response
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

### 2021-10-04 manuscript/journalnames.tex

%%Updated on 26 August 2021
%,% Website Name,%,%,% Website Name,%%,% Full Name,%%,% Short Name,%%,% DOI abbr,%%,% ISSN,% \continuouspages
%\DeclareOption{}{\gdef\@journal{}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{acoustics}{\gdef\@journal{acoustics}\gdef\@journalfull{Acoustics}\gdef\@journalshort{Acoustics}\gdef\@doiabbr{acoustics}\gdef\@ISSN{2624-599X}\gdef\@continuouspages{yes}}
\DeclareOption{actuators}{\gdef\@journal{actuators}\gdef\@journalfull{Actuators}\gdef\@journalshort{Actuators}\gdef\@doiabbr{act}\gdef\@ISSN{2076-0825}}
\DeclareOption{addictions}{\gdef\@journal{addictions}\gdef\@journalfull{Addictions}\gdef\@journalshort{Addictions}\gdef\@doiabbr{}\gdef\@ISSN{0006-0006}}
\DeclareOption{admsci}{\gdef\@journal{admsci}\gdef\@journalfull{Administrative Sciences}\gdef\@journalshort{Adm. Sci.}\gdef\@doiabbr{admsci}\gdef\@ISSN{2076-3387}}
\DeclareOption{adolescents}{\gdef\@journal{adolescents}\gdef\@journalfull{Adolescents}\gdef\@journalshort{Adolescents}\gdef\@doiabbr{adolescents}\gdef\@ISSN{2673-7051}\gdef\@continuouspages{yes}}
\DeclareOption{aerospace}{\gdef\@journal{aerospace}\gdef\@journalfull{Aerospace}\gdef\@journalshort{Aerospace}\gdef\@doiabbr{aerospace}\gdef\@ISSN{2226-4310}}
\DeclareOption{agriculture}{\gdef\@journal{agriculture}\gdef\@journalfull{Agriculture}\gdef\@journalshort{Agriculture}\gdef\@doiabbr{agriculture}\gdef\@ISSN{2077-0472}}
\DeclareOption{agriengineering}{\gdef\@journal{agriengineering}\gdef\@journalfull{AgriEngineering}\gdef\@journalshort{AgriEngineering}\gdef\@doiabbr{agriengineering}\gdef\@ISSN{2624-7402}\gdef\@continuouspages{yes}}
\DeclareOption{agronomy}{\gdef\@journal{agronomy}\gdef\@journalfull{Agronomy}\gdef\@journalshort{Agronomy}\gdef\@doiabbr{agronomy}\gdef\@ISSN{2073-4395}}
\DeclareOption{ai}{\gdef\@journal{ai}\gdef\@journalfull{AI}\gdef\@journalshort{AI}\gdef\@doiabbr{ai}\gdef\@ISSN{2673-2688}\gdef\@continuouspages{yes}}
\DeclareOption{algorithms}{\gdef\@journal{algorithms}\gdef\@journalfull{Algorithms}\gdef\@journalshort{Algorithms}\gdef\@doiabbr{a}\gdef\@ISSN{1999-4893}}
\DeclareOption{allergies}{\gdef\@journal{allergies}\gdef\@journalfull{Allergies}\gdef\@journalshort{Allergies}\gdef\@doiabbr{allergies}\gdef\@ISSN{2313-5786}}
\DeclareOption{alloys}{\gdef\@journal{alloys}\gdef\@journalfull{Alloys}\gdef\@journalshort{Alloys}\gdef\@doiabbr{alloys}\gdef\@ISSN{2674-063X}\gdef\@continuouspages{yes}}
\DeclareOption{analytica}{\gdef\@journal{analytica}\gdef\@journalfull{Analytica}\gdef\@journalshort{Analytica}\gdef\@doiabbr{analytica}\gdef\@ISSN{2673-4532}\gdef\@continuouspages{yes}}
\DeclareOption{animals}{\gdef\@journal{animals}\gdef\@journalfull{Animals}\gdef\@journalshort{Animals}\gdef\@doiabbr{ani}\gdef\@ISSN{2076-2615}}
\DeclareOption{antibiotics}{\gdef\@journal{antibiotics}\gdef\@journalfull{Antibiotics}\gdef\@journalshort{Antibiotics}\gdef\@doiabbr{antibiotics}\gdef\@ISSN{2079-6382}}
\DeclareOption{antibodies}{\gdef\@journal{antibodies}\gdef\@journalfull{Antibodies}\gdef\@journalshort{Antibodies}\gdef\@doiabbr{antib}\gdef\@ISSN{2073-4468}}
\DeclareOption{antioxidants}{\gdef\@journal{antioxidants}\gdef\@journalfull{Antioxidants}\gdef\@journalshort{Antioxidants}\gdef\@doiabbr{antiox}\gdef\@ISSN{2076-3921}}
\DeclareOption{appliedchem}{\gdef\@journal{appliedchem}\gdef\@journalfull{AppliedChem}\gdef\@journalshort{AppliedChem}\gdef\@doiabbr{appliedchem}\gdef\@ISSN{2673-9623}\gdef\@continuouspages{yes}}
\DeclareOption{appliedmath}{\gdef\@journal{appliedmath}\gdef\@journalfull{AppliedMath}\gdef\@journalshort{AppliedMath}\gdef\@doiabbr{appliedmath}\gdef\@ISSN{2673-9909}\gdef\@continuouspages{yes}}
\DeclareOption{applmech}{\gdef\@journal{applmech}\gdef\@journalfull{Applied Mechanics}\gdef\@journalshort{Appl. Mech.}\gdef\@doiabbr{applmech}\gdef\@ISSN{2673-3161}\gdef\@continuouspages{yes}}
\DeclareOption{applmicrobiol}{\gdef\@journal{applmicrobiol}\gdef\@journalfull{Applied Microbiology}\gdef\@journalshort{Appl. Microbiol.}\gdef\@doiabbr{applmicrobiol}\gdef\@ISSN{2673-8007}\gdef\@continuouspages{yes}}
\DeclareOption{applnano}{\gdef\@journal{applnano}\gdef\@journalfull{Applied Nano}\gdef\@journalshort{Appl. Nano}\gdef\@doiabbr{applnano}\gdef\@ISSN{2673-3501}\gdef\@continuouspages{yes}}
\DeclareOption{applsci}{\gdef\@journal{applsci}\gdef\@journalfull{Applied Sciences}\gdef\@journalshort{Appl. Sci.}\gdef\@doiabbr{app}\gdef\@ISSN{2076-3417}}
\DeclareOption{aquacj}{\gdef\@journal{aquacj}\gdef\@journalfull{Aquaculture Journal}\gdef\@journalshort{Aquac. J.}\gdef\@doiabbr{aj}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{architecture}{\gdef\@journal{architecture}\gdef\@journalfull{Architecture}\gdef\@journalshort{Architecture}\gdef\@doiabbr{architecture}\gdef\@ISSN{2673-8945}\gdef\@continuouspages{yes}}
\DeclareOption{arts}{\gdef\@journal{arts}\gdef\@journalfull{Arts}\gdef\@journalshort{Arts}\gdef\@doiabbr{arts}\gdef\@ISSN{2076-0752}}
\DeclareOption{asc}{\gdef\@journal{asc}\gdef\@journalfull{Automatic Systems and Control}\gdef\@journalshort{Autom. Syst. Control}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{asi}{\gdef\@journal{asi}\gdef\@journalfull{Applied System Innovation}\gdef\@journalshort{Appl. Syst. Innov.}\gdef\@doiabbr{asi}\gdef\@ISSN{2571-5577}}
\DeclareOption{astronomy}{\gdef\@journal{astronomy}\gdef\@journalfull{Astronomy}\gdef\@journalshort{Astronomy}\gdef\@doiabbr{astronomy}\gdef\@ISSN{2674-0346}\gdef\@continuouspages{yes}}
\DeclareOption{atmosphere}{\gdef\@journal{atmosphere}\gdef\@journalfull{Atmosphere}\gdef\@journalshort{Atmosphere}\gdef\@doiabbr{atmos}\gdef\@ISSN{2073-4433}}
\DeclareOption{atoms}{\gdef\@journal{atoms}\gdef\@journalfull{Atoms}\gdef\@journalshort{Atoms}\gdef\@doiabbr{atoms}\gdef\@ISSN{2218-2004}}
\DeclareOption{audiolres}{\gdef\@journal{audiolres}\gdef\@journalfull{Audiology Research}\gdef\@journalshort{Audiol. Res.}\gdef\@doiabbr{audiolres}\gdef\@ISSN{2039-4349}\gdef\@continuouspages{yes}}
\DeclareOption{automation}{\gdef\@journal{automation}\gdef\@journalfull{Automation}\gdef\@journalshort{Automation}\gdef\@doiabbr{automation}\gdef\@ISSN{2673-4052}\gdef\@continuouspages{yes}}
\DeclareOption{axioms}{\gdef\@journal{axioms}\gdef\@journalfull{Axioms}\gdef\@journalshort{Axioms}\gdef\@doiabbr{axioms}\gdef\@ISSN{2075-1680}}
\DeclareOption{bacteria}{\gdef\@journal{bacteria}\gdef\@journalfull{Bacteria}\gdef\@journalshort{Bacteria}\gdef\@doiabbr{bacteria}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{batteries}{\gdef\@journal{batteries}\gdef\@journalfull{Batteries}\gdef\@journalshort{Batteries}\gdef\@doiabbr{batteries}\gdef\@ISSN{2313-0105}}
\DeclareOption{bdcc}{\gdef\@journal{bdcc}\gdef\@journalfull{Big Data and Cognitive Computing}\gdef\@journalshort{Big Data Cogn. Comput.}\gdef\@doiabbr{bdcc}\gdef\@ISSN{2504-2289}}
\DeclareOption{behavsci}{\gdef\@journal{behavsci}\gdef\@journalfull{Behavioral Sciences}\gdef\@journalshort{Behav. Sci.}\gdef\@doiabbr{bs}\gdef\@ISSN{2076-328X}}
\DeclareOption{beverages}{\gdef\@journal{beverages}\gdef\@journalfull{Beverages}\gdef\@journalshort{Beverages}\gdef\@doiabbr{beverages}\gdef\@ISSN{2306-5710}}
\DeclareOption{biochem}{\gdef\@journal{biochem}\gdef\@journalfull{BioChem}\gdef\@journalshort{BioChem}\gdef\@doiabbr{biochem}\gdef\@ISSN{2673-6411}\gdef\@continuouspages{yes}}
\DeclareOption{bioengineering}{\gdef\@journal{bioengineering}\gdef\@journalfull{Bioengineering}\gdef\@journalshort{Bioengineering}\gdef\@doiabbr{bioengineering}\gdef\@ISSN{2306-5354}}
\DeclareOption{biologics}{\gdef\@journal{biologics}\gdef\@journalfull{Biologics}\gdef\@journalshort{Biologics}\gdef\@doiabbr{biologics}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biology}{\gdef\@journal{biology}\gdef\@journalfull{Biology}\gdef\@journalshort{Biology}\gdef\@doiabbr{biology}\gdef\@ISSN{2079-7737}}
\DeclareOption{biomass}{\gdef\@journal{biomass}\gdef\@journalfull{Biomass}\gdef\@journalshort{Biomass}\gdef\@doiabbr{biomass}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biomechanics}{\gdef\@journal{biomechanics}\gdef\@journalfull{Biomechanics}\gdef\@journalshort{Biomechanics}\gdef\@doiabbr{biomechanics}\gdef\@ISSN{2673-7078}\gdef\@continuouspages{yes}}
\DeclareOption{biomed}{\gdef\@journal{biomed}\gdef\@journalfull{BioMed}\gdef\@journalshort{BioMed}\gdef\@doiabbr{biomed}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{biomedicines}{\gdef\@journal{biomedicines}\gdef\@journalfull{Biomedicines}\gdef\@journalshort{Biomedicines}\gdef\@doiabbr{biomedicines}\gdef\@ISSN{2227-9059}}
\DeclareOption{biomedinformatics}{\gdef\@journal{biomedinformatics}\gdef\@journalfull{Biomedinformatics}\gdef\@journalshort{Biomedinformatics}\gdef\@doiabbr{biomedinformatics}\gdef\@ISSN{2673-7426}\gdef\@continuouspages{yes}}
\DeclareOption{biomimetics}{\gdef\@journal{biomimetics}\gdef\@journalfull{Biomimetics}\gdef\@journalshort{Biomimetics}\gdef\@doiabbr{biomimetics}\gdef\@ISSN{2313-7673}}
\DeclareOption{biomolecules}{\gdef\@journal{biomolecules}\gdef\@journalfull{Biomolecules}\gdef\@journalshort{Biomolecules}\gdef\@doiabbr{biom}\gdef\@ISSN{2218-273X}}
\DeclareOption{biophysica}{\gdef\@journal{biophysica}\gdef\@journalfull{Biophysica}\gdef\@journalshort{Biophysica}\gdef\@doiabbr{biophysica}\gdef\@ISSN{2673-4125}\gdef\@continuouspages{yes}}
\DeclareOption{biosensors}{\gdef\@journal{biosensors}\gdef\@journalfull{Biosensors}\gdef\@journalshort{Biosensors}\gdef\@doiabbr{bios}\gdef\@ISSN{2079-6374}}
\DeclareOption{biotech}{\gdef\@journal{biotech}\gdef\@journalfull{BioTech}\gdef\@journalshort{BioTech}\gdef\@doiabbr{biotech}\gdef\@ISSN{2673-6284}}
\DeclareOption{birds}{\gdef\@journal{birds}\gdef\@journalfull{Birds}\gdef\@journalshort{Birds}\gdef\@doiabbr{birds}\gdef\@ISSN{2673-6004}\gdef\@continuouspages{yes}}
\DeclareOption{bloods}{\gdef\@journal{bloods}\gdef\@journalfull{Bloods}\gdef\@journalshort{Bloods}\gdef\@doiabbr{bloods}\gdef\@ISSN{2673-415X}}
\DeclareOption{blsf}{\gdef\@journal{blsf}\gdef\@journalfull{Biology and Life Sciences Forum}\gdef\@journalshort{Biol. Life Sci. Forum}\gdef\@doiabbr{blsf	}\gdef\@ISSN{2673-9976}}
\DeclareOption{brainsci}{\gdef\@journal{brainsci}\gdef\@journalfull{Brain Sciences}\gdef\@journalshort{Brain Sci.}\gdef\@doiabbr{brainsci}\gdef\@ISSN{2076-3425}}
\DeclareOption{breath}{\gdef\@journal{breath}\gdef\@journalfull{Breath}\gdef\@journalshort{Breath}\gdef\@doiabbr{breath}\gdef\@ISSN{}}
\DeclareOption{buildings}{\gdef\@journal{buildings}\gdef\@journalfull{Buildings}\gdef\@journalshort{Buildings}\gdef\@doiabbr{buildings}\gdef\@ISSN{2075-5309}}
\DeclareOption{businesses}{\gdef\@journal{businesses}\gdef\@journalfull{Businesses}\gdef\@journalshort{Businesses}\gdef\@doiabbr{businesses}\gdef\@ISSN{2673-7116}\gdef\@continuouspages{yes}}
\DeclareOption{cancers}{\gdef\@journal{cancers}\gdef\@journalfull{Cancers}\gdef\@journalshort{Cancers}\gdef\@doiabbr{cancers}\gdef\@ISSN{2072-6694}}
\DeclareOption{carbon}{\gdef\@journal{carbon}\gdef\@journalfull{C}\gdef\@journalshort{C}\gdef\@doiabbr{c}\gdef\@ISSN{2311-5629}}
\DeclareOption{cardiogenetics}{\gdef\@journal{cardiogenetics}\gdef\@journalfull{Cardiogenetics}\gdef\@journalshort{Cardiogenetics}\gdef\@doiabbr{cardiogenetics}\gdef\@ISSN{2035-8148}\gdef\@continuouspages{yes}}
\DeclareOption{catalysts}{\gdef\@journal{catalysts}\gdef\@journalfull{Catalysts}\gdef\@journalshort{Catalysts}\gdef\@doiabbr{catal}\gdef\@ISSN{2073-4344}}
\DeclareOption{cells}{\gdef\@journal{cells}\gdef\@journalfull{Cells}\gdef\@journalshort{Cells}\gdef\@doiabbr{cells}\gdef\@ISSN{2073-4409}}
\DeclareOption{ceramics}{\gdef\@journal{ceramics}\gdef\@journalfull{Ceramics}\gdef\@journalshort{Ceramics}\gdef\@doiabbr{ceramics}\gdef\@ISSN{2571-6131}\gdef\@continuouspages{yes}}
\DeclareOption{challenges}{\gdef\@journal{challenges}\gdef\@journalfull{Challenges}\gdef\@journalshort{Challenges}\gdef\@doiabbr{challe}\gdef\@ISSN{2078-1547}}
\DeclareOption{chemengineering}{\gdef\@journal{chemengineering}\gdef\@journalfull{ChemEngineering}\gdef\@journalshort{ChemEngineering}\gdef\@doiabbr{chemengineering}\gdef\@ISSN{2305-7084}}
\DeclareOption{chemistry}{\gdef\@journal{chemistry}\gdef\@journalfull{Chemistry}\gdef\@journalshort{Chemistry}\gdef\@doiabbr{chemistry}\gdef\@ISSN{2624-8549}\gdef\@continuouspages{yes}}
\DeclareOption{chemosensors}{\gdef\@journal{chemosensors}\gdef\@journalfull{Chemosensors}\gdef\@journalshort{Chemosensors}\gdef\@doiabbr{chemosensors}\gdef\@ISSN{2227-9040}}
\DeclareOption{chemproc}{\gdef\@journal{chemproc}\gdef\@journalfull{Chemistry Proceedings}\gdef\@journalshort{Chem. Proc.}\gdef\@doiabbr{chemproc}\gdef\@ISSN{2673-4583}}
\DeclareOption{children}{\gdef\@journal{children}\gdef\@journalfull{Children}\gdef\@journalshort{Children}\gdef\@doiabbr{children}\gdef\@ISSN{2227-9067}}
\DeclareOption{chips}{\gdef\@journal{chips}\gdef\@journalfull{Chips}\gdef\@journalshort{Chips}\gdef\@doiabbr{chips}\gdef\@ISSN{2674-0710}\gdef\@continuouspages{yes}}
\DeclareOption{cimb}{\gdef\@journal{cimb}\gdef\@journalfull{Current Issues in Molecular Biology}\gdef\@journalshort{Curr. Issues Mol. Biol.}\gdef\@doiabbr{cimb}\gdef\@ISSN{1467-3045}\gdef\@continuouspages{yes}}
\DeclareOption{civileng}{\gdef\@journal{civileng}\gdef\@journalfull{CivilEng}\gdef\@journalshort{CivilEng}\gdef\@doiabbr{civileng}\gdef\@ISSN{2673-4109}\gdef\@continuouspages{yes}}
\DeclareOption{cleantechnol}{\gdef\@journal{cleantechnol}\gdef\@journalfull{Clean Technologies}\gdef\@journalshort{Clean Technol.}\gdef\@doiabbr{cleantechnol}\gdef\@ISSN{2571-8797}\gdef\@continuouspages{yes}}
\DeclareOption{climate}{\gdef\@journal{climate}\gdef\@journalfull{Climate}\gdef\@journalshort{Climate}\gdef\@doiabbr{cli}\gdef\@ISSN{2225-1154}}
\DeclareOption{clinpract}{\gdef\@journal{clinpract}\gdef\@journalfull{Clinics and Practice}\gdef\@journalshort{Clin. Pract.}\gdef\@doiabbr{clinpract}\gdef\@ISSN{2039-7283}\gdef\@continuouspages{yes}}
\DeclareOption{clockssleep}{\gdef\@journal{clockssleep}\gdef\@journalfull{Clocks \& Sleep}\gdef\@journalshort{Clocks\&Sleep}\gdef\@doiabbr{clockssleep}\gdef\@ISSN{2624-5175}\gdef\@continuouspages{yes}}
\DeclareOption{cmd}{\gdef\@journal{cmd}\gdef\@journalfull{Corrosion and Materials Degradation}\gdef\@journalshort{Corros. Mater. Degrad.}\gdef\@doiabbr{cmd}\gdef\@ISSN{2624-5558}\gdef\@continuouspages{yes}}
\DeclareOption{coasts}{\gdef\@journal{coasts}\gdef\@journalfull{Coasts}\gdef\@journalshort{Coasts}\gdef\@doiabbr{coasts}\gdef\@ISSN{2673-964X}\gdef\@continuouspages{yes}}
\DeclareOption{coatings}{\gdef\@journal{coatings}\gdef\@journalfull{Coatings}\gdef\@journalshort{Coatings}\gdef\@doiabbr{coatings}\gdef\@ISSN{2079-6412}}
\DeclareOption{colloids}{\gdef\@journal{colloids}\gdef\@journalfull{Colloids Interfaces}\gdef\@journalshort{Colloids Interfaces}\gdef\@doiabbr{colloids}\gdef\@ISSN{2504-5377}}
\DeclareOption{colorants}{\gdef\@journal{colorants}\gdef\@journalfull{Colorants}\gdef\@journalshort{Colorants}\gdef\@doiabbr{colorants}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{compounds}{\gdef\@journal{compounds}\gdef\@journalfull{Compounds}\gdef\@journalshort{Compounds}\gdef\@doiabbr{compounds}\gdef\@ISSN{2673-6918}\gdef\@continuouspages{yes}}
\DeclareOption{computation}{\gdef\@journal{computation}\gdef\@journalfull{Computation}\gdef\@journalshort{Computation}\gdef\@doiabbr{computation}\gdef\@ISSN{2079-3197}}
\DeclareOption{computers}{\gdef\@journal{computers}\gdef\@journalfull{Computers}\gdef\@journalshort{Computers}\gdef\@doiabbr{computers}\gdef\@ISSN{2073-431X}}
\DeclareOption{condensedmatter}{\gdef\@journal{condensedmatter}\gdef\@journalfull{Condensed Matter}\gdef\@journalshort{Condens. Matter}\gdef\@doiabbr{condmat}\gdef\@ISSN{2410-3896}}
\DeclareOption{conservation}{\gdef\@journal{conservation}\gdef\@journalfull{Conservation}\gdef\@journalshort{Conservation}\gdef\@doiabbr{conservation}\gdef\@ISSN{2673-7159}\gdef\@continuouspages{yes}}
\DeclareOption{constrmater}{\gdef\@journal{constrmater}\gdef\@journalfull{Construction Materials}\gdef\@journalshort{Constr. Mater.}\gdef\@doiabbr{constrmater}\gdef\@ISSN{2673-7108}\gdef\@continuouspages{yes}}
\DeclareOption{cosmetics}{\gdef\@journal{cosmetics}\gdef\@journalfull{Cosmetics}\gdef\@journalshort{Cosmetics}\gdef\@doiabbr{cosmetics}\gdef\@ISSN{2079-9284}}
\DeclareOption{covid}{\gdef\@journal{covid}\gdef\@journalfull{COVID}\gdef\@journalshort{COVID}\gdef\@doiabbr{covid}\gdef\@ISSN{2673-8112}\gdef\@continuouspages{yes}}
\DeclareOption{crops}{\gdef\@journal{crops}\gdef\@journalfull{Crops}\gdef\@journalshort{Crops}\gdef\@doiabbr{crops}\gdef\@ISSN{2673-7655}\gdef\@continuouspages{yes}}
\DeclareOption{cryptography}{\gdef\@journal{cryptography}\gdef\@journalfull{Cryptography}\gdef\@journalshort{Cryptography}\gdef\@doiabbr{cryptography}\gdef\@ISSN{2410-387X}}
\DeclareOption{crystals}{\gdef\@journal{crystals}\gdef\@journalfull{Crystals}\gdef\@journalshort{Crystals}\gdef\@doiabbr{cryst}\gdef\@ISSN{2073-4352}}
\DeclareOption{ctn}{\gdef\@journal{ctn}\gdef\@journalfull{Clinical and Translational Neuroscience}\gdef\@journalshort{CTN}\gdef\@doiabbr{Clin. Transl. Neurosci.}\gdef\@ISSN{2514-183X}}
\DeclareOption{curroncol}{\gdef\@journal{curroncol}\gdef\@journalfull{Current Oncology}\gdef\@journalshort{Curr. Oncol.}\gdef\@doiabbr{curroncol}\gdef\@ISSN{1718-7729}\gdef\@continuouspages{yes}}
\DeclareOption{cyber}{\gdef\@journal{cyber}\gdef\@journalfull{Cyber}\gdef\@journalshort{Cyber}\gdef\@doiabbr{cyber}\gdef\@ISSN{2624-800X}}
\DeclareOption{dairy}{\gdef\@journal{dairy}\gdef\@journalfull{Dairy}\gdef\@journalshort{Dairy}\gdef\@doiabbr{dairy}\gdef\@ISSN{2624-862X}\gdef\@continuouspages{yes}}
\DeclareOption{data}{\gdef\@journal{data}\gdef\@journalfull{Data}\gdef\@journalshort{Data}\gdef\@doiabbr{data}\gdef\@ISSN{2306-5729}}
\DeclareOption{dentistry}{\gdef\@journal{dentistry}\gdef\@journalfull{Dentistry Journal}\gdef\@journalshort{Dent. J.}\gdef\@doiabbr{dj}\gdef\@ISSN{2304-6767}}
\DeclareOption{dermato}{\gdef\@journal{dermato}\gdef\@journalfull{Dermato}\gdef\@journalshort{Dermato}\gdef\@doiabbr{dermato}\gdef\@ISSN{2673-6179}\gdef\@continuouspages{yes}}
\DeclareOption{dermatopathology}{\gdef\@journal{dermatopathology}\gdef\@journalfull{Dermatopathology}\gdef\@journalshort{Dermatopathology}\gdef\@doiabbr{dermatopathology}\gdef\@ISSN{2296-3529}\gdef\@continuouspages{yes}}
\DeclareOption{designs}{\gdef\@journal{designs}\gdef\@journalfull{Designs}\gdef\@journalshort{Designs}\gdef\@doiabbr{designs}\gdef\@ISSN{2411-9660}}
\DeclareOption{diabetology}{\gdef\@journal{diabetology}\gdef\@journalfull{Diabetology}\gdef\@journalshort{Diabetology}\gdef\@doiabbr{diabetology}\gdef\@ISSN{2673-4540}\gdef\@continuouspages{yes}}
\DeclareOption{diagnostics}{\gdef\@journal{diagnostics}\gdef\@journalfull{Diagnostics}\gdef\@journalshort{Diagnostics}\gdef\@doiabbr{diagnostics}\gdef\@ISSN{2075-4418}}
\DeclareOption{dietetics}{\gdef\@journal{dietetics}\gdef\@journalfull{Dietetics}\gdef\@journalshort{Dietetics}\gdef\@doiabbr{dietetics}\gdef\@ISSN{2674-0311}\gdef\@continuouspages{yes}}
\DeclareOption{digital}{\gdef\@journal{digital}\gdef\@journalfull{Digital}\gdef\@journalshort{Digital}\gdef\@doiabbr{digital}\gdef\@ISSN{2673-6470}\gdef\@continuouspages{yes}}
\DeclareOption{disabilities}{\gdef\@journal{disabilities}\gdef\@journalfull{Disabilities}\gdef\@journalshort{Disabilities}\gdef\@doiabbr{disabilities}\gdef\@ISSN{2673-7272}\gdef\@continuouspages{yes}}
\DeclareOption{diseases}{\gdef\@journal{diseases}\gdef\@journalfull{Diseases}\gdef\@journalshort{Diseases}\gdef\@doiabbr{diseases}\gdef\@ISSN{2079-9721}}
\DeclareOption{diversity}{\gdef\@journal{diversity}\gdef\@journalfull{Diversity}\gdef\@journalshort{Diversity}\gdef\@doiabbr{d}\gdef\@ISSN{1424-2818}}
\DeclareOption{dna}{\gdef\@journal{dna}\gdef\@journalfull{DNA}\gdef\@journalshort{DNA}\gdef\@doiabbr{dna}\gdef\@ISSN{2673-8856}\gdef\@continuouspages{yes}}
\DeclareOption{drones}{\gdef\@journal{drones}\gdef\@journalfull{Drones}\gdef\@journalshort{Drones}\gdef\@doiabbr{drones}\gdef\@ISSN{2504-446X}}
\DeclareOption{dynamics}{\gdef\@journal{dynamics}\gdef\@journalfull{Dynamics}\gdef\@journalshort{Dynamics}\gdef\@doiabbr{dynamics}\gdef\@ISSN{2673-8716}\gdef\@continuouspages{yes}}
\DeclareOption{earth}{\gdef\@journal{earth}\gdef\@journalfull{Earth}\gdef\@journalshort{Earth}\gdef\@doiabbr{earth}\gdef\@ISSN{2673-4834}\gdef\@continuouspages{yes}}
\DeclareOption{ebj}{\gdef\@journal{ebj}\gdef\@journalfull{European Burn Journal}\gdef\@journalshort{Eur. Burn J.}\gdef\@doiabbr{ebj}\gdef\@ISSN{2673-1991}\gdef\@continuouspages{yes}}
\DeclareOption{ecologies}{\gdef\@journal{ecologies}\gdef\@journalfull{Ecologies}\gdef\@journalshort{Ecologies}\gdef\@doiabbr{ecologies}\gdef\@ISSN{2673-4133}\gdef\@continuouspages{yes}}
\DeclareOption{econometrics}{\gdef\@journal{econometrics}\gdef\@journalfull{Econometrics}\gdef\@journalshort{Econometrics}\gdef\@doiabbr{econometrics}\gdef\@ISSN{2225-1146}}
\DeclareOption{economies}{\gdef\@journal{economies}\gdef\@journalfull{Economies}\gdef\@journalshort{Economies}\gdef\@doiabbr{economies}\gdef\@ISSN{2227-7099}}
\DeclareOption{education}{\gdef\@journal{education}\gdef\@journalfull{Education Sciences}\gdef\@journalshort{Educ. Sci.}\gdef\@doiabbr{educsci}\gdef\@ISSN{2227-7102}}
\DeclareOption{ejihpe}{\gdef\@journal{ejihpe}\gdef\@journalfull{European Journal of Investigation in Health Psychology and Education}\gdef\@journalshort{Eur. J. Investig. Health Psychol. Educ.}\gdef\@doiabbr{ejihpe}\gdef\@ISSN{2254-9625}\gdef\@continuouspages{yes}}
\DeclareOption{electricity}{\gdef\@journal{electricity}\gdef\@journalfull{Electricity}\gdef\@journalshort{Electricity}\gdef\@doiabbr{electricity}\gdef\@ISSN{2673-4826}\gdef\@continuouspages{yes}}
\DeclareOption{electrochem}{\gdef\@journal{electrochem}\gdef\@journalfull{Electrochem}\gdef\@journalshort{Electrochem}\gdef\@doiabbr{electrochem}\gdef\@ISSN{2673-3293}\gdef\@continuouspages{yes}}
\DeclareOption{electronicmat}{\gdef\@journal{electronicmat}\gdef\@journalfull{Electronic Materials}\gdef\@journalshort{Electron. Mater.}\gdef\@doiabbr{electronicmat}\gdef\@ISSN{2673-3978}\gdef\@continuouspages{yes}}
\DeclareOption{electronics}{\gdef\@journal{electronics}\gdef\@journalfull{Electronics}\gdef\@journalshort{Electronics}\gdef\@doiabbr{electronics}\gdef\@ISSN{2079-9292}}
\DeclareOption{encyclopedia}{\gdef\@journal{encyclopedia}\gdef\@journalfull{Encyclopedia}\gdef\@journalshort{Encyclopedia}\gdef\@doiabbr{encyclopedia}\gdef\@ISSN{2673-8392}\gdef\@continuouspages{yes}}
\DeclareOption{endocrines}{\gdef\@journal{endocrines}\gdef\@journalfull{Endocrines}\gdef\@journalshort{Endocrines}\gdef\@doiabbr{endocrines}\gdef\@ISSN{2673-396X}\gdef\@continuouspages{yes}}
\DeclareOption{energies}{\gdef\@journal{energies}\gdef\@journalfull{Energies}\gdef\@journalshort{Energies}\gdef\@doiabbr{en}\gdef\@ISSN{1996-1073}}
\DeclareOption{eng}{\gdef\@journal{eng}\gdef\@journalfull{Eng-Advances in Engineering}\gdef\@journalshort{Eng}\gdef\@doiabbr{eng}\gdef\@ISSN{2673-4117}\gdef\@continuouspages{yes}}
\DeclareOption{engproc}{\gdef\@journal{engproc}\gdef\@journalfull{Engineering Proceedings}\gdef\@journalshort{Eng. Proc.}\gdef\@doiabbr{engproc}\gdef\@ISSN{2673-4591}}
%\DeclareOption{ent}{\gdef\@journal{ent}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{entomology}{\gdef\@journal{entomology}\gdef\@journalfull{Entomology}\gdef\@journalshort{Entomology}\gdef\@doiabbr{entomology}\gdef\@ISSN{}\gdef\@continuouspages{yes}}	
\DeclareOption{entropy}{\gdef\@journal{entropy}\gdef\@journalfull{Entropy}\gdef\@journalshort{Entropy}\gdef\@doiabbr{e}\gdef\@ISSN{1099-4300}}
\DeclareOption{environments}{\gdef\@journal{environments}\gdef\@journalfull{Environments}\gdef\@journalshort{Environments}\gdef\@doiabbr{environments}\gdef\@ISSN{2076-3298}}
\DeclareOption{environsciproc}{\gdef\@journal{environsciproc}\gdef\@journalfull{Environmental Sciences Proceedings}\gdef\@journalshort{Environ. Sci. Proc.}\gdef\@doiabbr{environsciproc}\gdef\@ISSN{2673-4931}}
\DeclareOption{epidemiologia}{\gdef\@journal{epidemiologia}\gdef\@journalfull{Epidemiologia}\gdef\@journalshort{Epidemiologia}\gdef\@doiabbr{epidemiologia}\gdef\@ISSN{2673-3986}\gdef\@continuouspages{yes}}
\DeclareOption{epigenomes}{\gdef\@journal{epigenomes}\gdef\@journalfull{Epigenomes}\gdef\@journalshort{Epigenomes}\gdef\@doiabbr{epigenomes}\gdef\@ISSN{2075-4655}}
\DeclareOption{est}{\gdef\@journal{est}\gdef\@journalfull{Electrochemical Science and Technology}\gdef\@journalshort{Electrochem. Sci. Technol.}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{fermentation}{\gdef\@journal{fermentation}\gdef\@journalfull{Fermentation}\gdef\@journalshort{Fermentation}\gdef\@doiabbr{fermentation}\gdef\@ISSN{2311-5637}}
\DeclareOption{fibers}{\gdef\@journal{fibers}\gdef\@journalfull{Fibers}\gdef\@journalshort{Fibers}\gdef\@doiabbr{fib}\gdef\@ISSN{2079-6439}}
\DeclareOption{	fintech}{\gdef\@journal{fintech}\gdef\@journalfull{FinTech}\gdef\@journalshort{FinTech}\gdef\@doiabbr{fintech}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{fire}{\gdef\@journal{fire}\gdef\@journalfull{Fire}\gdef\@journalshort{Fire}\gdef\@doiabbr{fire}\gdef\@ISSN{2571-6255}}
\DeclareOption{fishes}{\gdef\@journal{fishes}\gdef\@journalfull{Fishes}\gdef\@journalshort{Fishes}\gdef\@doiabbr{fishes}\gdef\@ISSN{2410-3888}}
\DeclareOption{fluids}{\gdef\@journal{fluids}\gdef\@journalfull{Fluids}\gdef\@journalshort{Fluids}\gdef\@doiabbr{fluids}\gdef\@ISSN{2311-5521}}
\DeclareOption{foods}{\gdef\@journal{foods}\gdef\@journalfull{Foods}\gdef\@journalshort{Foods}\gdef\@doiabbr{foods}\gdef\@ISSN{2304-8158}}
\DeclareOption{forecasting}{\gdef\@journal{forecasting}\gdef\@journalfull{Forecasting}\gdef\@journalshort{Forecasting}\gdef\@doiabbr{forecast}\gdef\@ISSN{2571-9394}\gdef\@continuouspages{yes}}
\DeclareOption{forensicsci}{\gdef\@journal{forensicsci}\gdef\@journalfull{Forensic Sciences}\gdef\@journalshort{Forensic. Sci.}\gdef\@doiabbr{forensicsci}\gdef\@ISSN{2673-6756}\gdef\@continuouspages{yes}}
\DeclareOption{forests}{\gdef\@journal{forests}\gdef\@journalfull{Forests}\gdef\@journalshort{Forests}\gdef\@doiabbr{f}\gdef\@ISSN{1999-4907}}
\DeclareOption{foundations}{\gdef\@journal{foundations}\gdef\@journalfull{Foundations}\gdef\@journalshort{Foundations}\gdef\@doiabbr{foundations}\gdef\@ISSN{2673-9321}\gdef\@continuouspages{yes}}
\DeclareOption{fractalfract}{\gdef\@journal{fractalfract}\gdef\@journalfull{Fractal and Fractional}\gdef\@journalshort{Fractal Fract.}\gdef\@doiabbr{fractalfract}\gdef\@ISSN{2504-3110}}
\DeclareOption{fuels}{\gdef\@journal{fuels}\gdef\@journalfull{Fuels}\gdef\@journalshort{Fuels}\gdef\@doiabbr{fuels}\gdef\@ISSN{2673-3994}\gdef\@continuouspages{yes}}
\DeclareOption{futureinternet}{\gdef\@journal{futureinternet}\gdef\@journalfull{Future Internet}\gdef\@journalshort{Future Internet}\gdef\@doiabbr{fi}\gdef\@ISSN{1999-5903}}
%\DeclareOption{futureparasites}{\gdef\@journal{futureparasites}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{futurepharmacol}{\gdef\@journal{futurepharmacol}\gdef\@journalfull{Future Pharmacology}\gdef\@journalshort{Future Pharm.}\gdef\@doiabbr{futurepharmacol}\gdef\@ISSN{2673-9879}\gdef\@continuouspages{yes}}
\DeclareOption{futurephys}{\gdef\@journal{futurephys}\gdef\@journalfull{Future Physics}\gdef\@journalshort{Future Phys.}\gdef\@doiabbr{futurephys}\gdef\@ISSN{2624-6503}}
\DeclareOption{futuretransp}{\gdef\@journal{futuretransp}\gdef\@journalfull{Future Transportation}\gdef\@journalshort{Future Transp.}\gdef\@doiabbr{futuretransp}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{galaxies}{\gdef\@journal{galaxies}\gdef\@journalfull{Galaxies}\gdef\@journalshort{Galaxies}\gdef\@doiabbr{galaxies}\gdef\@ISSN{2075-4434}}
\DeclareOption{games}{\gdef\@journal{games}\gdef\@journalfull{Games}\gdef\@journalshort{Games}\gdef\@doiabbr{g}\gdef\@ISSN{2073-4336}}
\DeclareOption{gases}{\gdef\@journal{gases}\gdef\@journalfull{Gases}\gdef\@journalshort{Gases}\gdef\@doiabbr{gases}\gdef\@ISSN{2673-5628}\gdef\@continuouspages{yes}}
\DeclareOption{gastroent}{\gdef\@journal{gastroent}\gdef\@journalfull{Gastroenterology Insights}\gdef\@journalshort{Gastroenterol. Insights}\gdef\@doiabbr{gastroent}\gdef\@ISSN{2036-7422}\gdef\@continuouspages{yes}}
\DeclareOption{gastrointestdisord}{\gdef\@journal{gastrointestdisord}\gdef\@journalfull{Gastrointestinal Disorders}\gdef\@journalshort{Gastrointest. Disord.}\gdef\@doiabbr{gidisord}\gdef\@ISSN{2624-5647}\gdef\@continuouspages{yes}}
\DeclareOption{gels}{\gdef\@journal{gels}\gdef\@journalfull{Gels}\gdef\@journalshort{Gels}\gdef\@doiabbr{gels}\gdef\@ISSN{2310-2861}}
\DeclareOption{genealogy}{\gdef\@journal{genealogy}\gdef\@journalfull{Genealogy}\gdef\@journalshort{Genealogy}\gdef\@doiabbr{genealogy}\gdef\@ISSN{2313-5778}}
\DeclareOption{genes}{\gdef\@journal{genes}\gdef\@journalfull{Genes}\gdef\@journalshort{Genes}\gdef\@doiabbr{genes}\gdef\@ISSN{2073-4425}}
\DeclareOption{geographies}{\gdef\@journal{geographies}\gdef\@journalfull{Geographies}\gdef\@journalshort{Geographies}\gdef\@doiabbr{geographies}\gdef\@ISSN{2673-7086}\gdef\@continuouspages{yes}}
\DeclareOption{geohazards}{\gdef\@journal{geohazards}\gdef\@journalfull{GeoHazards}\gdef\@journalshort{GeoHazards}\gdef\@doiabbr{geohazards}\gdef\@ISSN{2624-795X}\gdef\@continuouspages{yes}}
\DeclareOption{geomatics}{\gdef\@journal{geomatics}\gdef\@journalfull{Geomatics}\gdef\@journalshort{Geomatics}\gdef\@doiabbr{geomatics}\gdef\@ISSN{2673-7418}\gdef\@continuouspages{yes}}
\DeclareOption{geosciences}{\gdef\@journal{geosciences}\gdef\@journalfull{Geosciences}\gdef\@journalshort{Geosciences}\gdef\@doiabbr{geosciences}\gdef\@ISSN{2076-3263}}
\DeclareOption{geotechnics}{\gdef\@journal{geotechnics}\gdef\@journalfull{Geotechnics}\gdef\@journalshort{Geotechnics}\gdef\@doiabbr{geotechnics}\gdef\@ISSN{2673-7094}\gdef\@continuouspages{yes}}
\DeclareOption{geriatrics}{\gdef\@journal{geriatrics}\gdef\@journalfull{Geriatrics}\gdef\@journalshort{Geriatrics}\gdef\@doiabbr{geriatrics}\gdef\@ISSN{2308-3417}}
\DeclareOption{hazardousmatters}{\gdef\@journal{hazardousmatters}\gdef\@journalfull{Hazardous Matters}\gdef\@journalshort{Hazard. Matters}\gdef\@doiabbr{}\gdef\@ISSN{0014-0014}}
\DeclareOption{healthcare}{\gdef\@journal{healthcare}\gdef\@journalfull{Healthcare}\gdef\@journalshort{Healthcare}\gdef\@doiabbr{healthcare}\gdef\@ISSN{2227-9032}}
\DeclareOption{hearts}{\gdef\@journal{hearts}\gdef\@journalfull{Hearts}\gdef\@journalshort{Hearts}\gdef\@doiabbr{hearts}\gdef\@ISSN{2673-3846}\gdef\@continuouspages{yes}}
\DeclareOption{hemato}{\gdef\@journal{hemato}\gdef\@journalfull{Hemato}\gdef\@journalshort{Hemato}\gdef\@doiabbr{hemato}\gdef\@ISSN{2673-6357}\gdef\@continuouspages{yes}}
\DeclareOption{heritage}{\gdef\@journal{heritage}\gdef\@journalfull{Heritage}\gdef\@journalshort{Heritage}\gdef\@doiabbr{heritage}\gdef\@ISSN{2571-9408}\gdef\@continuouspages{yes}}
\DeclareOption{highthroughput}{\gdef\@journal{highthroughput}\gdef\@journalfull{High-Throughput}\gdef\@journalshort{High-Throughput}\gdef\@doiabbr{ht}\gdef\@ISSN{2571-5135}}
\DeclareOption{histories}{\gdef\@journal{histories}\gdef\@journalfull{Histories}\gdef\@journalshort{Histories}\gdef\@doiabbr{histories}\gdef\@ISSN{2409-9252}\gdef\@continuouspages{yes}}
\DeclareOption{horticulturae}{\gdef\@journal{horticulturae}\gdef\@journalfull{Horticulturae}\gdef\@journalshort{Horticulturae}\gdef\@doiabbr{horticulturae}\gdef\@ISSN{2311-7524}}
\DeclareOption{humanities}{\gdef\@journal{humanities}\gdef\@journalfull{Humanities}\gdef\@journalshort{Humanities}\gdef\@doiabbr{h}\gdef\@ISSN{2076-0787}}
\DeclareOption{humans}{\gdef\@journal{humans}\gdef\@journalfull{Humans}\gdef\@journalshort{Humans}\gdef\@doiabbr{humans}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{hydrobiology}{\gdef\@journal{hydrobiology}\gdef\@journalfull{Hydrobiology}\gdef\@journalshort{Hydrobiology	}\gdef\@doiabbr{hydrobiology}\gdef\@ISSN{2673-9917}\gdef\@continuouspages{yes}}
\DeclareOption{hydrogen}{\gdef\@journal{hydrogen}\gdef\@journalfull{Hydrogen}\gdef\@journalshort{Hydrogen}\gdef\@doiabbr{hydrogen}\gdef\@ISSN{2673-4141}\gdef\@continuouspages{yes}}
\DeclareOption{hydrology}{\gdef\@journal{hydrology}\gdef\@journalfull{Hydrology}\gdef\@journalshort{Hydrology}\gdef\@doiabbr{hydrology}\gdef\@ISSN{2306-5338}}
\DeclareOption{hygiene}{\gdef\@journal{hygiene}\gdef\@journalfull{Hygiene}\gdef\@journalshort{Hygiene}\gdef\@doiabbr{hygiene}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{idr}{\gdef\@journal{idr}\gdef\@journalfull{Infectious Disease Reports}\gdef\@journalshort{Infect. Dis. Rep.}\gdef\@doiabbr{idr}\gdef\@ISSN{2036-7449}\gdef\@continuouspages{yes}}
\DeclareOption{ijerph}{\gdef\@journal{ijerph}\gdef\@journalfull{International Journal of Environmental Research and Public Health}\gdef\@journalshort{Int. J. Environ. Res. Public Health}\gdef\@doiabbr{ijerph}\gdef\@ISSN{1660-4601}}
\DeclareOption{ijfs}{\gdef\@journal{ijfs}\gdef\@journalfull{International Journal of Financial Studies}\gdef\@journalshort{Int. J. Financial Stud.}\gdef\@doiabbr{ijfs}\gdef\@ISSN{2227-7072}}
\DeclareOption{ijgi}{\gdef\@journal{ijgi}\gdef\@journalfull{ISPRS International Journal of Geo-Information}\gdef\@journalshort{ISPRS Int. J. Geo-Inf.}\gdef\@doiabbr{ijgi}\gdef\@ISSN{2220-9964}}
\DeclareOption{ijms}{\gdef\@journal{ijms}\gdef\@journalfull{International Journal of Molecular Sciences}\gdef\@journalshort{Int. J. Mol. Sci.}\gdef\@doiabbr{ijms}\gdef\@ISSN{1422-0067}}
\DeclareOption{ijns}{\gdef\@journal{ijns}\gdef\@journalfull{International Journal of Neonatal Screening}\gdef\@journalshort{Int. J. Neonatal Screen.}\gdef\@doiabbr{ijns}\gdef\@ISSN{2409-515X}}
\DeclareOption{ijtm}{\gdef\@journal{ijtm}\gdef\@journalfull{International Journal of Translational Medicine}\gdef\@journalshort{Int. J. Transl. Med.}\gdef\@doiabbr{ijtm}\gdef\@ISSN{2673-8937}\gdef\@continuouspages{yes}}
\DeclareOption{ijtpp}{\gdef\@journal{ijtpp}\gdef\@journalfull{International Journal of Turbomachinery Propulsion and Power}\gdef\@journalshort{Int. J. Turbomach. Propuls. Power}\gdef\@doiabbr{ijtpp}\gdef\@ISSN{2504-186X}}
\DeclareOption{immuno}{\gdef\@journal{immuno}\gdef\@journalfull{Immuno}\gdef\@journalshort{Immuno}\gdef\@doiabbr{immuno}\gdef\@ISSN{2673-5601}\gdef\@continuouspages{yes}}
\DeclareOption{informatics}{\gdef\@journal{informatics}\gdef\@journalfull{Informatics}\gdef\@journalshort{Informatics}\gdef\@doiabbr{informatics}\gdef\@ISSN{2227-9709}}
\DeclareOption{information}{\gdef\@journal{information}\gdef\@journalfull{Information}\gdef\@journalshort{Information}\gdef\@doiabbr{info}\gdef\@ISSN{2078-2489}}
\DeclareOption{infrastructures}{\gdef\@journal{infrastructures}\gdef\@journalfull{Infrastructures}\gdef\@journalshort{Infrastructures}\gdef\@doiabbr{infrastructures}\gdef\@ISSN{2412-3811}}
\DeclareOption{inorganics}{\gdef\@journal{inorganics}\gdef\@journalfull{Inorganics}\gdef\@journalshort{Inorganics}\gdef\@doiabbr{inorganics}\gdef\@ISSN{2304-6740}}
\DeclareOption{insects}{\gdef\@journal{insects}\gdef\@journalfull{Insects}\gdef\@journalshort{Insects}\gdef\@doiabbr{insects}\gdef\@ISSN{2075-4450}}
\DeclareOption{instruments}{\gdef\@journal{instruments}\gdef\@journalfull{Instruments}\gdef\@journalshort{Instruments}\gdef\@doiabbr{instruments}\gdef\@ISSN{2410-390X}}
\DeclareOption{inventions}{\gdef\@journal{inventions}\gdef\@journalfull{Inventions}\gdef\@journalshort{Inventions}\gdef\@doiabbr{inventions}\gdef\@ISSN{2411-5134}}
\DeclareOption{iot}{\gdef\@journal{iot}\gdef\@journalfull{IoT}\gdef\@journalshort{IoT}\gdef\@doiabbr{iot}\gdef\@ISSN{2624-831X}\gdef\@continuouspages{yes}}
\DeclareOption{j}{\gdef\@journal{j}\gdef\@journalfull{J}\gdef\@journalshort{J}\gdef\@doiabbr{j}\gdef\@ISSN{2571-8800}\gdef\@continuouspages{yes}}
\DeclareOption{jal}{\gdef\@journal{jal}\gdef\@journalfull{Journal of Ageing and Longevity}\gdef\@journalshort{J. Ageing Longev.}\gdef\@doiabbr{jal}\gdef\@ISSN{2673-9259}\gdef\@continuouspages{yes}}
\DeclareOption{jcdd}{\gdef\@journal{jcdd}\gdef\@journalfull{Journal of Cardiovascular Development and Disease}\gdef\@journalshort{J. Cardiovasc. Dev. Dis.}\gdef\@doiabbr{jcdd}\gdef\@ISSN{2308-3425}}
\DeclareOption{jcm}{\gdef\@journal{jcm}\gdef\@journalfull{Journal of Clinical Medicine}\gdef\@journalshort{J. Clin. Med.}\gdef\@doiabbr{jcm}\gdef\@ISSN{2077-0383}}
\DeclareOption{jcp}{\gdef\@journal{jcp}\gdef\@journalfull{Journal of Cybersecurity and Privacy}\gdef\@journalshort{J. Cybersecur. Priv.}\gdef\@doiabbr{jcp}\gdef\@ISSN{2624-800X}\gdef\@continuouspages{yes}}
\DeclareOption{jcs}{\gdef\@journal{jcs}\gdef\@journalfull{Journal of Composites Science}\gdef\@journalshort{J. Compos. Sci.}\gdef\@doiabbr{jcs}\gdef\@ISSN{2504-477X}}
\DeclareOption{jdb}{\gdef\@journal{jdb}\gdef\@journalfull{Journal of Developmental Biology}\gdef\@journalshort{J. Dev. Biol.}\gdef\@doiabbr{jdb}\gdef\@ISSN{2221-3759}}
\DeclareOption{jfb}{\gdef\@journal{jfb}\gdef\@journalfull{Journal of Functional Biomaterials}\gdef\@journalshort{J. Funct. Biomater.}\gdef\@doiabbr{jfb}\gdef\@ISSN{2079-4983}}
\DeclareOption{jfmk}{\gdef\@journal{jfmk}\gdef\@journalfull{Journal of Functional Morphology and Kinesiology}\gdef\@journalshort{J. Funct. Morphol. Kinesiol.}\gdef\@doiabbr{jfmk}\gdef\@ISSN{2411-5142}}
\DeclareOption{jimaging}{\gdef\@journal{jimaging}\gdef\@journalfull{Journal of Imaging}\gdef\@journalshort{J. Imaging}\gdef\@doiabbr{jimaging}\gdef\@ISSN{2313-433X}}
\DeclareOption{jintelligence}{\gdef\@journal{jintelligence}\gdef\@journalfull{Journal of Intelligence}\gdef\@journalshort{J. Intell.}\gdef\@doiabbr{jintelligence}\gdef\@ISSN{2079-3200}}
\DeclareOption{jlpea}{\gdef\@journal{jlpea}\gdef\@journalfull{Journal of Low Power Electronics and Applications}\gdef\@journalshort{J. Low Power Electron. Appl.}\gdef\@doiabbr{jlpea}\gdef\@ISSN{2079-9268}}
\DeclareOption{jmmp}{\gdef\@journal{jmmp}\gdef\@journalfull{Journal of Manufacturing and Materials Processing}\gdef\@journalshort{J. Manuf. Mater. Process.}\gdef\@doiabbr{jmmp}\gdef\@ISSN{2504-4494}}
\DeclareOption{jmp}{\gdef\@journal{jmp}\gdef\@journalfull{Journal of Molecular Pathology}\gdef\@journalshort{J. Mol. Pathol.}\gdef\@doiabbr{jmp}\gdef\@ISSN{2673-5261}\gdef\@continuouspages{yes}}
\DeclareOption{jmse}{\gdef\@journal{jmse}\gdef\@journalfull{Journal of Marine Science and Engineering}\gdef\@journalshort{J. Mar. Sci. Eng.}\gdef\@doiabbr{jmse}\gdef\@ISSN{2077-1312}}
\DeclareOption{jne}{\gdef\@journal{jne}\gdef\@journalfull{Journal of Nuclear Engineering}\gdef\@journalshort{J. Nucl. Eng.}\gdef\@doiabbr{jne}\gdef\@ISSN{2673-4362}\gdef\@continuouspages{yes}}
\DeclareOption{jnt}{\gdef\@journal{jnt}\gdef\@journalfull{Journal of Nanotheranostics}\gdef\@journalshort{J. Nanotheranostics}\gdef\@doiabbr{jnt}\gdef\@ISSN{2624-845X}\gdef\@continuouspages{yes}}
\DeclareOption{jof}{\gdef\@journal{jof}\gdef\@journalfull{Journal of Fungi}\gdef\@journalshort{J. Fungi}\gdef\@doiabbr{jof}\gdef\@ISSN{2309-608X}}
\DeclareOption{joitmc}{\gdef\@journal{joitmc}\gdef\@journalfull{Journal of Open Innovation: Technology Market and Complexity}\gdef\@journalshort{J. Open Innov. Technol. Mark. Complex.}\gdef\@doiabbr{joitmc}\gdef\@ISSN{2199-8531}}
\DeclareOption{jor}{\gdef\@journal{jor}\gdef\@journalfull{Journal of Respiration}\gdef\@journalshort{J. Respir.}\gdef\@doiabbr{jor}\gdef\@ISSN{2673-527X}\gdef\@continuouspages{yes}}
\DeclareOption{journalmedia}{\gdef\@journal{journalmedia}\gdef\@journalfull{Journalism and Media}\gdef\@journalshort{Journal. Media}\gdef\@doiabbr{journalmedia}\gdef\@ISSN{2673-5172}\gdef\@continuouspages{yes}}
\DeclareOption{jox}{\gdef\@journal{jox}\gdef\@journalfull{Journal of Xenobiotics}\gdef\@journalshort{J. Xenobiot.}\gdef\@doiabbr{jox}\gdef\@ISSN{2039-4713}\gdef\@continuouspages{yes}}
\DeclareOption{jpm}{\gdef\@journal{jpm}\gdef\@journalfull{Journal of Personalized Medicine}\gdef\@journalshort{J. Pers. Med.}\gdef\@doiabbr{jpm}\gdef\@ISSN{2075-4426}}
\DeclareOption{jrfm}{\gdef\@journal{jrfm}\gdef\@journalfull{Journal of Risk and Financial Management}\gdef\@journalshort{J. Risk Financial Manag.}\gdef\@doiabbr{jrfm}\gdef\@ISSN{1911-8074}}
\DeclareOption{jsan}{\gdef\@journal{jsan}\gdef\@journalfull{Journal of Sensor and Actuator Networks}\gdef\@journalshort{J. Sens. Actuator Netw.}\gdef\@doiabbr{jsan}\gdef\@ISSN{2224-2708}}
\DeclareOption{jtaer}{\gdef\@journal{jtaer}\gdef\@journalfull{Journal of Theoretical and Applied Electronic Commerce Research}\gdef\@journalshort{J. Theor. Appl. Electron. Commer. Res.}\gdef\@doiabbr{jtaer}\gdef\@ISSN{0718-1876}\gdef\@continuouspages{yes}}
\DeclareOption{jzbg}{\gdef\@journal{jzbg}\gdef\@journalfull{Journal of Zoological and Botanical Gardens}\gdef\@journalshort{J. Zool. Bot. Gard.}\gdef\@doiabbr{jzbg}\gdef\@ISSN{2673-5636}\gdef\@continuouspages{yes}}
%\DeclareOption{kidney}{\gdef\@journal{kidney}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{kidneydial}{\gdef\@journal{kidneydial}\gdef\@journalfull{Kidney and Dialysis}\gdef\@journalshort{Kidney Dial.}\gdef\@doiabbr{kidneydial}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{knowledge}{\gdef\@journal{knowledge}\gdef\@journalfull{Knowledge}\gdef\@journalshort{Knowledge}\gdef\@doiabbr{knowledge}\gdef\@ISSN{2673-9585}\gdef\@continuouspages{yes}}
\DeclareOption{land}{\gdef\@journal{land}\gdef\@journalfull{Land}\gdef\@journalshort{Land}\gdef\@doiabbr{land}\gdef\@ISSN{2073-445X}}
\DeclareOption{languages}{\gdef\@journal{languages}\gdef\@journalfull{Languages}\gdef\@journalshort{Languages}\gdef\@doiabbr{languages}\gdef\@ISSN{2226-471X}}
\DeclareOption{laws}{\gdef\@journal{laws}\gdef\@journalfull{Laws}\gdef\@journalshort{Laws}\gdef\@doiabbr{laws}\gdef\@ISSN{2075-471X}}
\DeclareOption{life}{\gdef\@journal{life}\gdef\@journalfull{Life}\gdef\@journalshort{Life}\gdef\@doiabbr{life}\gdef\@ISSN{2075-1729}}
\DeclareOption{liquids}{\gdef\@journal{liquids}\gdef\@journalfull{Liquids}\gdef\@journalshort{Liquids}\gdef\@doiabbr{liquids}\gdef\@ISSN{2673-8015}\gdef\@continuouspages{yes}}
\DeclareOption{literature}{\gdef\@journal{literature}\gdef\@journalfull{Literature}\gdef\@journalshort{Literature}\gdef\@doiabbr{literature}\gdef\@ISSN{2410-9789}\gdef\@continuouspages{yes}}
\DeclareOption{livers}{\gdef\@journal{livers}\gdef\@journalfull{Livers}\gdef\@journalshort{Livers}\gdef\@doiabbr{livers}\gdef\@ISSN{2673-4389}\gdef\@continuouspages{yes}}
\DeclareOption{logistics}{\gdef\@journal{logistics}\gdef\@journalfull{Logistics}\gdef\@journalshort{Logistics}\gdef\@doiabbr{logistics}\gdef\@ISSN{2305-6290}}
\DeclareOption{lubricants}{\gdef\@journal{lubricants}\gdef\@journalfull{Lubricants}\gdef\@journalshort{Lubricants}\gdef\@doiabbr{lubricants}\gdef\@ISSN{2075-4442}}
\DeclareOption{machines}{\gdef\@journal{machines}\gdef\@journalfull{Machines}\gdef\@journalshort{Machines}\gdef\@doiabbr{machines}\gdef\@ISSN{2075-1702}}
\DeclareOption{macromol}{\gdef\@journal{macromol}\gdef\@journalfull{Macromol}\gdef\@journalshort{Macromol}\gdef\@doiabbr{macromol}\gdef\@ISSN{2673-6209}\gdef\@continuouspages{yes}}
\DeclareOption{magnetism}{\gdef\@journal{magnetism}\gdef\@journalfull{Magnetism}\gdef\@journalshort{Magnetism}\gdef\@doiabbr{magnetism}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{magnetochemistry}{\gdef\@journal{magnetochemistry}\gdef\@journalfull{Magnetochemistry}\gdef\@journalshort{Magnetochemistry}\gdef\@doiabbr{magnetochemistry}\gdef\@ISSN{2312-7481}}
\DeclareOption{make}{\gdef\@journal{make}\gdef\@journalfull{Machine Learning and Knowledge Extraction}\gdef\@journalshort{Mach. Learn. Knowl. Extr.}\gdef\@doiabbr{make}\gdef\@ISSN{2504-4990}\gdef\@continuouspages{yes}}
\DeclareOption{marinedrugs}{\gdef\@journal{marinedrugs}\gdef\@journalfull{Marine Drugs}\gdef\@journalshort{Mar. Drugs}\gdef\@doiabbr{md}\gdef\@ISSN{1660-3397}}
\DeclareOption{materials}{\gdef\@journal{materials}\gdef\@journalfull{Materials}\gdef\@journalshort{Materials}\gdef\@doiabbr{ma}\gdef\@ISSN{1996-1944}}
\DeclareOption{materproc}{\gdef\@journal{materproc}\gdef\@journalfull{Materials Proceedings}\gdef\@journalshort{Mater. Proc.}\gdef\@doiabbr{materproc}\gdef\@ISSN{2673-4605}}
\DeclareOption{mathematics}{\gdef\@journal{mathematics}\gdef\@journalfull{Mathematics}\gdef\@journalshort{Mathematics}\gdef\@doiabbr{math}\gdef\@ISSN{2227-7390}}
\DeclareOption{mca}{\gdef\@journal{mca}\gdef\@journalfull{Mathematical and Computational Applications}\gdef\@journalshort{Math. Comput. Appl.}\gdef\@doiabbr{mca}\gdef\@ISSN{2297-8747}}
%\DeclareOption{measurements}{\gdef\@journal{measurements}\gdef\@journalfull{Measurements}\gdef\@journalshort{Measurements}\gdef\@doiabbr{measurements}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{medicina}{\gdef\@journal{medicina}\gdef\@journalfull{Medicina}\gdef\@journalshort{Medicina}\gdef\@doiabbr{medicina}\gdef\@ISSN{1648-9144}}
\DeclareOption{medicines}{\gdef\@journal{medicines}\gdef\@journalfull{Medicines}\gdef\@journalshort{Medicines}\gdef\@doiabbr{medicines}\gdef\@ISSN{2305-6320}}
\DeclareOption{medsci}{\gdef\@journal{medsci}\gdef\@journalfull{Medical Sciences}\gdef\@journalshort{Med. Sci.}\gdef\@doiabbr{medsci}\gdef\@ISSN{2076-3271}}
\DeclareOption{membranes}{\gdef\@journal{membranes}\gdef\@journalfull{Membranes}\gdef\@journalshort{Membranes}\gdef\@doiabbr{membranes}\gdef\@ISSN{2077-0375}}
\DeclareOption{merits}{\gdef\@journal{merits}\gdef\@journalfull{Merits}\gdef\@journalshort{Merits}\gdef\@doiabbr{merits}\gdef\@ISSN{2673-8104}\gdef\@continuouspages{yes}}
\DeclareOption{metabolites}{\gdef\@journal{metabolites}\gdef\@journalfull{Metabolites}\gdef\@journalshort{Metabolites}\gdef\@doiabbr{metabo}\gdef\@ISSN{2218-1989}}
\DeclareOption{metals}{\gdef\@journal{metals}\gdef\@journalfull{Metals}\gdef\@journalshort{Metals}\gdef\@doiabbr{met}\gdef\@ISSN{2075-4701}}
\DeclareOption{meteorology}{\gdef\@journal{meteorology}\gdef\@journalfull{Meteorology}\gdef\@journalshort{Meteorology}\gdef\@doiabbr{meteorology}\gdef\@ISSN{2674-0494}\gdef\@continuouspages{yes}}
\DeclareOption{methane}{\gdef\@journal{methane}\gdef\@journalfull{Methane}\gdef\@journalshort{Methane}\gdef\@doiabbr{methane}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{metrology}{\gdef\@journal{metrology}\gdef\@journalfull{Metrology}\gdef\@journalshort{Metrology}\gdef\@doiabbr{metrology}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{micro}{\gdef\@journal{micro}\gdef\@journalfull{Micro}\gdef\@journalshort{Micro}\gdef\@doiabbr{micro}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{microarrays}{\gdef\@journal{microarrays}\gdef\@journalfull{Microarrays}\gdef\@journalshort{Microarrays}\gdef\@doiabbr{microarrays}\gdef\@ISSN{2076-3905}}
\DeclareOption{microbiolres}{\gdef\@journal{microbiolres}\gdef\@journalfull{Microbiology Research}\gdef\@journalshort{Microbiol. Res.}\gdef\@doiabbr{microbiolres}\gdef\@ISSN{2036-7481}\gdef\@continuouspages{yes}}
\DeclareOption{micromachines}{\gdef\@journal{micromachines}\gdef\@journalfull{Micromachines}\gdef\@journalshort{Micromachines}\gdef\@doiabbr{mi}\gdef\@ISSN{2072-666X}}
\DeclareOption{microorganisms}{\gdef\@journal{microorganisms}\gdef\@journalfull{Microorganisms}\gdef\@journalshort{Microorganisms}\gdef\@doiabbr{microorganisms}\gdef\@ISSN{2076-2607}}
\DeclareOption{microplastics}{\gdef\@journal{microplastics}\gdef\@journalfull{Microplastics}\gdef\@journalshort{Microplastics}\gdef\@doiabbr{microplastics}\gdef\@ISSN{2673-8929}\gdef\@continuouspages{yes}}
\DeclareOption{minerals}{\gdef\@journal{minerals}\gdef\@journalfull{Minerals}\gdef\@journalshort{Minerals}\gdef\@doiabbr{min}\gdef\@ISSN{2075-163X}}
\DeclareOption{mining}{\gdef\@journal{mining}\gdef\@journalfull{Mining}\gdef\@journalshort{Mining}\gdef\@doiabbr{mining}\gdef\@ISSN{2673-6489}\gdef\@continuouspages{yes}}
\DeclareOption{modelling}{\gdef\@journal{modelling}\gdef\@journalfull{Modelling}\gdef\@journalshort{Modelling}\gdef\@doiabbr{modelling}\gdef\@ISSN{2673-3951}\gdef\@continuouspages{yes}}
\DeclareOption{molbank}{\gdef\@journal{molbank}\gdef\@journalfull{Molbank}\gdef\@journalshort{Molbank}\gdef\@doiabbr{M}\gdef\@ISSN{1422-8599}}
\DeclareOption{molecules}{\gdef\@journal{molecules}\gdef\@journalfull{Molecules}\gdef\@journalshort{Molecules}\gdef\@doiabbr{molecules}\gdef\@ISSN{1420-3049}}
\DeclareOption{mps}{\gdef\@journal{mps}\gdef\@journalfull{Methods and Protocols}\gdef\@journalshort{Methods Protoc.}\gdef\@doiabbr{mps}\gdef\@ISSN{2409-9279}}
\DeclareOption{msf}{\gdef\@journal{msf}\gdef\@journalfull{Medical Sciences Forum}\gdef\@journalshort{Med. Sci. Forum}\gdef\@doiabbr{msf}\gdef\@ISSN{2673-9992}}
\DeclareOption{mti}{\gdef\@journal{mti}\gdef\@journalfull{Multimodal Technologies and Interaction}\gdef\@journalshort{Multimodal Technol. Interact.}\gdef\@doiabbr{mti}\gdef\@ISSN{2414-4088}}
\DeclareOption{nanoenergyadv}{\gdef\@journal{nanoenergyadv}\gdef\@journalfull{Nanoenergy Advances}\gdef\@journalshort{Nanoenergy Adv.}\gdef\@doiabbr{nanoenergyadv}\gdef\@ISSN{2673-706X}\gdef\@continuouspages{yes}}
\DeclareOption{nanomanufacturing}{\gdef\@journal{nanomanufacturing}\gdef\@journalfull{Nanomanufacturing}\gdef\@journalshort{Nanomanufacturing}\gdef\@doiabbr{nanomanufacturing}\gdef\@ISSN{2673-687X}\gdef\@continuouspages{yes}}
\DeclareOption{nanomaterials}{\gdef\@journal{nanomaterials}\gdef\@journalfull{Nanomaterials}\gdef\@journalshort{Nanomaterials}\gdef\@doiabbr{nano}\gdef\@ISSN{2079-4991}}
\DeclareOption{ncrna}{\gdef\@journal{ncrna}\gdef\@journalfull{Non-coding RNA}\gdef\@journalshort{Non-coding RNA}\gdef\@doiabbr{ncrna}\gdef\@ISSN{2311-553X}}
\DeclareOption{network}{\gdef\@journal{network}\gdef\@journalfull{Network}\gdef\@journalshort{Network}\gdef\@doiabbr{network}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{neuroglia}{\gdef\@journal{neuroglia}\gdef\@journalfull{Neuroglia}\gdef\@journalshort{Neuroglia}\gdef\@doiabbr{neuroglia}\gdef\@ISSN{2571-6980}\gdef\@continuouspages{yes}}
\DeclareOption{neurolint}{\gdef\@journal{neurolint}\gdef\@journalfull{Neurology International}\gdef\@journalshort{Neurol. Int.}\gdef\@doiabbr{neurolint}\gdef\@ISSN{2035-8377}\gdef\@continuouspages{yes}}
\DeclareOption{neurosci}{\gdef\@journal{neurosci}\gdef\@journalfull{NeuroSci}\gdef\@journalshort{NeuroSci}\gdef\@doiabbr{neurosci}\gdef\@ISSN{2673-4087}\gdef\@continuouspages{yes}}
\DeclareOption{nitrogen}{\gdef\@journal{nitrogen}\gdef\@journalfull{Nitrogen}\gdef\@journalshort{Nitrogen}\gdef\@doiabbr{nitrogen}\gdef\@ISSN{2504-3129}\gdef\@continuouspages{yes}}
\DeclareOption{notspecified}{\gdef\@journal{notspecified}\gdef\@journalfull{Journal Not Specified}\gdef\@journalshort{Journal Not Specified}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{nri}{\gdef\@journal{nri}\gdef\@journalfull{Natural Resources Informatics}\gdef\@journalshort{Nat. Resour. Inform.}\gdef\@doiabbr{nri}\gdef\@ISSN{2673-981X}\gdef\@continuouspages{yes}}
\DeclareOption{nursrep}{\gdef\@journal{nursrep}\gdef\@journalfull{Nursing Reports}\gdef\@journalshort{Nurs. Rep.}\gdef\@doiabbr{nursrep}\gdef\@ISSN{2039-4403}\gdef\@continuouspages{yes}}
\DeclareOption{nutraceuticals}{\gdef\@journal{nutraceuticals}\gdef\@journalfull{Nutraceuticals}\gdef\@journalshort{Nutraceuticals}\gdef\@doiabbr{nutraceuticals}\gdef\@ISSN{1661-3821}\gdef\@continuouspages{yes}}
\DeclareOption{nutrients}{\gdef\@journal{nutrients}\gdef\@journalfull{Nutrients}\gdef\@journalshort{Nutrients}\gdef\@doiabbr{nu}\gdef\@ISSN{2072-6643}}
\DeclareOption{obesities}{\gdef\@journal{obesities}\gdef\@journalfull{Obesities}\gdef\@journalshort{Obesities}\gdef\@doiabbr{obesities}\gdef\@ISSN{2673-4168}\gdef\@continuouspages{yes}}
\DeclareOption{oceans}{\gdef\@journal{oceans}\gdef\@journalfull{Oceans}\gdef\@journalshort{Oceans}\gdef\@doiabbr{oceans}\gdef\@ISSN{2673-1924}\gdef\@continuouspages{yes}}
\DeclareOption{ohbm}{\gdef\@journal{ohbm}\gdef\@journalfull{Journal of Otorhinolaryngology Hearing and Balance Medicine}\gdef\@journalshort{J. Otorhinolaryngol. Hear. Balance Med.}\gdef\@doiabbr{ohbm}\gdef\@ISSN{2504-463X}}
\DeclareOption{onco}{\gdef\@journal{onco}\gdef\@journalfull{Onco}\gdef\@journalshort{Onco}\gdef\@doiabbr{onco}\gdef\@ISSN{2673-7523}\gdef\@continuouspages{yes}}
%\DeclareOption{oncopathology}{\gdef\@journal{oncopathology}\gdef\@journalfull{}\gdef\@journalshort{}\gdef\@doiabbr{}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{optics}{\gdef\@journal{optics}\gdef\@journalfull{Optics}\gdef\@journalshort{Optics}\gdef\@doiabbr{opt}\gdef\@ISSN{2673-3269}\gdef\@continuouspages{yes}}
\DeclareOption{oral}{\gdef\@journal{oral}\gdef\@journalfull{Oral}\gdef\@journalshort{Oral}\gdef\@doiabbr{oral}\gdef\@ISSN{2673-6373}\gdef\@continuouspages{yes}}
\DeclareOption{organics}{\gdef\@journal{organics}\gdef\@journalfull{Organics}\gdef\@journalshort{Organics}\gdef\@doiabbr{org}\gdef\@ISSN{2673-401X}\gdef\@continuouspages{yes}}
\DeclareOption{organoids}{\gdef\@journal{organoids}\gdef\@journalfull{Organoids}\gdef\@journalshort{Organoids}\gdef\@doiabbr{organoids}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{osteology}{\gdef\@journal{osteology}\gdef\@journalfull{Osteology}\gdef\@journalshort{Osteology}\gdef\@doiabbr{osteology}\gdef\@ISSN{2673-4036}\gdef\@continuouspages{yes}}
\DeclareOption{oxygen}{\gdef\@journal{oxygen}\gdef\@journalfull{Oxygen}\gdef\@journalshort{Oxygen}\gdef\@doiabbr{oxygen}\gdef\@ISSN{2673-9801}\gdef\@continuouspages{yes}}
\DeclareOption{parasites}{\gdef\@journal{parasites}\gdef\@journalfull{Parasites}\gdef\@journalshort{Parasites}\gdef\@doiabbr{parasites}\gdef\@ISSN{2673-5946}}
\DeclareOption{parasitologia}{\gdef\@journal{parasitologia}\gdef\@journalfull{Parasitologia}\gdef\@journalshort{Parasitologia}\gdef\@doiabbr{parasitologia}\gdef\@ISSN{2673-6772}\gdef\@continuouspages{yes}}
\DeclareOption{particles}{\gdef\@journal{particles}\gdef\@journalfull{Particles}\gdef\@journalshort{Particles}\gdef\@doiabbr{particles}\gdef\@ISSN{2571-712X}\gdef\@continuouspages{yes}}
\DeclareOption{pathogens}{\gdef\@journal{pathogens}\gdef\@journalfull{Pathogens}\gdef\@journalshort{Pathogens}\gdef\@doiabbr{pathogens}\gdef\@ISSN{2076-0817}}
\DeclareOption{pathophysiology}{\gdef\@journal{pathophysiology}\gdef\@journalfull{Pathophysiology}\gdef\@journalshort{Pathophysiology}\gdef\@doiabbr{pathophysiology}\gdef\@ISSN{0928-4680}\gdef\@continuouspages{yes}}
\DeclareOption{pediatrrep}{\gdef\@journal{pediatrrep}\gdef\@journalfull{Pediatric Reports}\gdef\@journalshort{Pediatr. Rep.}\gdef\@doiabbr{pediatric}\gdef\@ISSN{2036-7503}\gdef\@continuouspages{yes}}
\DeclareOption{pharmaceuticals}{\gdef\@journal{pharmaceuticals}\gdef\@journalfull{Pharmaceuticals}\gdef\@journalshort{Pharmaceuticals}\gdef\@doiabbr{ph}\gdef\@ISSN{1424-8247}}
\DeclareOption{pharmaceutics}{\gdef\@journal{pharmaceutics}\gdef\@journalfull{Pharmaceutics}\gdef\@journalshort{Pharmaceutics}\gdef\@doiabbr{pharmaceutics}\gdef\@ISSN{1999-4923}}
\DeclareOption{pharmacy}{\gdef\@journal{pharmacy}\gdef\@journalfull{Pharmacy}\gdef\@journalshort{Pharmacy}\gdef\@doiabbr{pharmacy}\gdef\@ISSN{2226-4787}}
\DeclareOption{philosophies}{\gdef\@journal{philosophies}\gdef\@journalfull{Philosophies}\gdef\@journalshort{Philosophies}\gdef\@doiabbr{philosophies}\gdef\@ISSN{2409-9287}}
\DeclareOption{photochem}{\gdef\@journal{photochem}\gdef\@journalfull{Photochem}\gdef\@journalshort{Photochem}\gdef\@doiabbr{photochem}\gdef\@ISSN{2673-7256}\gdef\@continuouspages{yes}}
\DeclareOption{photonics}{\gdef\@journal{photonics}\gdef\@journalfull{Photonics}\gdef\@journalshort{Photonics}\gdef\@doiabbr{photonics}\gdef\@ISSN{2304-6732}}
\DeclareOption{phycology}{\gdef\@journal{phycology}\gdef\@journalfull{Phycology}\gdef\@journalshort{Phycology}\gdef\@doiabbr{phycology}\gdef\@ISSN{2673-9410}\gdef\@continuouspages{yes}}
\DeclareOption{physchem}{\gdef\@journal{physchem}\gdef\@journalfull{Physchem}\gdef\@journalshort{Physchem}\gdef\@doiabbr{physchem}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{physics}{\gdef\@journal{physics}\gdef\@journalfull{Physics}\gdef\@journalshort{Physics}\gdef\@doiabbr{physics}\gdef\@ISSN{2624-8174}\gdef\@continuouspages{yes}}
\DeclareOption{physiologia}{\gdef\@journal{physiologia}\gdef\@journalfull{Physiologia}\gdef\@journalshort{Physiologia}\gdef\@doiabbr{physiologia}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{plants}{\gdef\@journal{plants}\gdef\@journalfull{Plants}\gdef\@journalshort{Plants}\gdef\@doiabbr{plants}\gdef\@ISSN{2223-7747}}
\DeclareOption{plasma}{\gdef\@journal{plasma}\gdef\@journalfull{Plasma}\gdef\@journalshort{Plasma}\gdef\@doiabbr{plasma}\gdef\@ISSN{2571-6182}\gdef\@continuouspages{yes}}
\DeclareOption{pollutants}{\gdef\@journal{pollutants}\gdef\@journalfull{Pollutants}\gdef\@journalshort{Pollutants}\gdef\@doiabbr{pollutants}\gdef\@ISSN{2673-4672}\gdef\@continuouspages{yes}}
\DeclareOption{polymers}{\gdef\@journal{polymers}\gdef\@journalfull{Polymers}\gdef\@journalshort{Polymers}\gdef\@doiabbr{polym}\gdef\@ISSN{2073-4360}}
\DeclareOption{polysaccharides}{\gdef\@journal{polysaccharides}\gdef\@journalfull{Polysaccharides}\gdef\@journalshort{Polysaccharides}\gdef\@doiabbr{polysaccharides}\gdef\@ISSN{2673-4176}\gdef\@continuouspages{yes}}
\DeclareOption{poultry}{\gdef\@journal{poultry}\gdef\@journalfull{Poultry}\gdef\@journalshort{Poultry}\gdef\@doiabbr{poultry}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{powders}{\gdef\@journal{powders}\gdef\@journalfull{Powders}\gdef\@journalshort{Powders}\gdef\@doiabbr{powders}\gdef\@ISSN{2674-0516}\gdef\@continuouspages{yes}}
\DeclareOption{preprints}{\gdef\@journal{preprints}\gdef\@journalfull{Preprints}\gdef\@journalshort{Preprints}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{proceedings}{\gdef\@journal{proceedings}\gdef\@journalfull{Proceedings}\gdef\@journalshort{Proceedings}\gdef\@doiabbr{proceedings}\gdef\@ISSN{2504-3900}}
\DeclareOption{processes}{\gdef\@journal{processes}\gdef\@journalfull{Processes}\gdef\@journalshort{Processes}\gdef\@doiabbr{pr}\gdef\@ISSN{2227-9717}}
\DeclareOption{prosthesis}{\gdef\@journal{prosthesis}\gdef\@journalfull{Prosthesis}\gdef\@journalshort{Prosthesis}\gdef\@doiabbr{prosthesis}\gdef\@ISSN{2673-1592}\gdef\@continuouspages{yes}}
\DeclareOption{proteomes}{\gdef\@journal{proteomes}\gdef\@journalfull{Proteomes}\gdef\@journalshort{Proteomes}\gdef\@doiabbr{proteomes}\gdef\@ISSN{2227-7382}}
\DeclareOption{psf}{\gdef\@journal{psf}\gdef\@journalfull{Physical Sciences Forum}\gdef\@journalshort{Phys. Sci. Forum}\gdef\@doiabbr{psf}\gdef\@ISSN{2673-9984}}
\DeclareOption{psych}{\gdef\@journal{psych}\gdef\@journalfull{Psych}\gdef\@journalshort{Psych}\gdef\@doiabbr{psych}\gdef\@ISSN{2624-8611}\gdef\@continuouspages{yes}}
\DeclareOption{psychiatryint}{\gdef\@journal{psychiatryint}\gdef\@journalfull{Psychiatry International}\gdef\@journalshort{Psychiatry Int.}\gdef\@doiabbr{psychiatryint}\gdef\@ISSN{2673-5318}\gdef\@continuouspages{yes}}
\DeclareOption{publications}{\gdef\@journal{publications}\gdef\@journalfull{Publications}\gdef\@journalshort{Publications}\gdef\@doiabbr{publications}\gdef\@ISSN{2304-6775}}
\DeclareOption{quantumrep}{\gdef\@journal{quantumrep}\gdef\@journalfull{Quantum Reports}\gdef\@journalshort{Quantum Rep.}\gdef\@doiabbr{quantum}\gdef\@ISSN{2624-960X}\gdef\@continuouspages{yes}}
\DeclareOption{quaternary}{\gdef\@journal{quaternary}\gdef\@journalfull{Quaternary}\gdef\@journalshort{Quaternary}\gdef\@doiabbr{quat}\gdef\@ISSN{2571-550X}}
\DeclareOption{qubs}{\gdef\@journal{qubs}\gdef\@journalfull{Quantum Beam Science}\gdef\@journalshort{Quantum Beam Sci.}\gdef\@doiabbr{qubs}\gdef\@ISSN{2412-382X}}
\DeclareOption{radiation}{\gdef\@journal{radiation}\gdef\@journalfull{Radiation}\gdef\@journalshort{Radiation}\gdef\@doiabbr{radiation}\gdef\@ISSN{2673-592X}\gdef\@continuouspages{yes}}
\DeclareOption{reactions}{\gdef\@journal{reactions}\gdef\@journalfull{Reactions}\gdef\@journalshort{Reactions}\gdef\@doiabbr{reactions}\gdef\@ISSN{2624-781X}\gdef\@continuouspages{yes}}
\DeclareOption{recycling}{\gdef\@journal{recycling}\gdef\@journalfull{Recycling}\gdef\@journalshort{Recycling}\gdef\@doiabbr{recycling}\gdef\@ISSN{2313-4321}}
\DeclareOption{regeneration}{\gdef\@journal{regeneration}\gdef\@journalfull{Regeneration}\gdef\@journalshort{Regeneration}\gdef\@doiabbr{regeneration}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{religions}{\gdef\@journal{religions}\gdef\@journalfull{Religions}\gdef\@journalshort{Religions}\gdef\@doiabbr{rel}\gdef\@ISSN{2077-1444}}
\DeclareOption{remotesensing}{\gdef\@journal{remotesensing}\gdef\@journalfull{Remote Sensing}\gdef\@journalshort{Remote Sens.}\gdef\@doiabbr{rs}\gdef\@ISSN{2072-4292}}
\DeclareOption{reports}{\gdef\@journal{reports}\gdef\@journalfull{Reports}\gdef\@journalshort{Reports}\gdef\@doiabbr{reports}\gdef\@ISSN{2571-841X}}
\DeclareOption{reprodmed}{\gdef\@journal{reprodmed}\gdef\@journalfull{Reproductive Medicine}\gdef\@journalshort{Reprod. Med.}\gdef\@doiabbr{reprodmed}\gdef\@ISSN{2673-3897}\gdef\@continuouspages{yes}}
\DeclareOption{resources}{\gdef\@journal{resources}\gdef\@journalfull{Resources}\gdef\@journalshort{Resources}\gdef\@doiabbr{resources}\gdef\@ISSN{2079-9276}}
\DeclareOption{rheumato}{\gdef\@journal{rheumato}\gdef\@journalfull{Rheumato}\gdef\@journalshort{Rheumato}\gdef\@doiabbr{rheumato}\gdef\@ISSN{2674-0621}\gdef\@continuouspages{yes}}
\DeclareOption{risks}{\gdef\@journal{risks}\gdef\@journalfull{Risks}\gdef\@journalshort{Risks}\gdef\@doiabbr{risks}\gdef\@ISSN{2227-9091}}
\DeclareOption{robotics}{\gdef\@journal{robotics}\gdef\@journalfull{Robotics}\gdef\@journalshort{Robotics}\gdef\@doiabbr{robotics}\gdef\@ISSN{2218-6581}}
\DeclareOption{ruminants}{\gdef\@journal{ruminants}\gdef\@journalfull{Ruminants}\gdef\@journalshort{Ruminants}\gdef\@doiabbr{ruminants}\gdef\@ISSN{2673-933X}\gdef\@continuouspages{yes}}
\DeclareOption{safety}{\gdef\@journal{safety}\gdef\@journalfull{Safety}\gdef\@journalshort{Safety}\gdef\@doiabbr{safety}\gdef\@ISSN{2313-576X}}
\DeclareOption{sci}{\gdef\@journal{sci}\gdef\@journalfull{Sci}\gdef\@journalshort{Sci}\gdef\@doiabbr{sci}\gdef\@ISSN{2413-4155}}
\DeclareOption{scipharm}{\gdef\@journal{scipharm}\gdef\@journalfull{Scientia Pharmaceutica}\gdef\@journalshort{Sci. Pharm.}\gdef\@doiabbr{scipharm}\gdef\@ISSN{2218-0532}}
\DeclareOption{seeds}{\gdef\@journal{seeds}\gdef\@journalfull{Seeds}\gdef\@journalshort{Seeds}\gdef\@doiabbr{seeds}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{sensors}{\gdef\@journal{sensors}\gdef\@journalfull{Sensors}\gdef\@journalshort{Sensors}\gdef\@doiabbr{s}\gdef\@ISSN{1424-8220}}
\DeclareOption{separations}{\gdef\@journal{separations}\gdef\@journalfull{Separations}\gdef\@journalshort{Separations}\gdef\@doiabbr{separations}\gdef\@ISSN{2297-8739}}
\DeclareOption{sexes}{\gdef\@journal{sexes}\gdef\@journalfull{Sexes}\gdef\@journalshort{Sexes}\gdef\@doiabbr{sexes}\gdef\@ISSN{2411-5118}\gdef\@continuouspages{yes}}
\DeclareOption{signals}{\gdef\@journal{signals}\gdef\@journalfull{Signals}\gdef\@journalshort{Signals}\gdef\@doiabbr{signals}\gdef\@ISSN{2624-6120}\gdef\@continuouspages{yes}}
\DeclareOption{sinusitis}{\gdef\@journal{sinusitis}\gdef\@journalfull{Sinusitis}\gdef\@journalshort{Sinusitis}\gdef\@doiabbr{sinusitis}\gdef\@ISSN{2309-107X}\gdef\@continuouspages{yes}}
\DeclareOption{skins}{\gdef\@journal{skins}\gdef\@journalfull{Skins}\gdef\@journalshort{Skins}\gdef\@doiabbr{skins}\gdef\@ISSN{}}
\DeclareOption{smartcities}{\gdef\@journal{smartcities}\gdef\@journalfull{Smart Cities}\gdef\@journalshort{Smart Cities}\gdef\@doiabbr{smartcities}\gdef\@ISSN{2624-6511}\gdef\@continuouspages{yes}}
\DeclareOption{sna}{\gdef\@journal{sna}\gdef\@journalfull{Sinusitis and Asthma}\gdef\@journalshort{Sinusitis Asthma}\gdef\@doiabbr{sna}\gdef\@ISSN{2624-7003}}
\DeclareOption{societies}{\gdef\@journal{societies}\gdef\@journalfull{Societies}\gdef\@journalshort{Societies}\gdef\@doiabbr{soc}\gdef\@ISSN{2075-4698}}
\DeclareOption{socsci}{\gdef\@journal{socsci}\gdef\@journalfull{Social Sciences}\gdef\@journalshort{Soc. Sci.}\gdef\@doiabbr{socsci}\gdef\@ISSN{2076-0760}}
\DeclareOption{software}{\gdef\@journal{software}\gdef\@journalfull{Software}\gdef\@journalshort{Software}\gdef\@doiabbr{software}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{soilsystems}{\gdef\@journal{soilsystems}\gdef\@journalfull{Soil Systems}\gdef\@journalshort{Soil Syst.}\gdef\@doiabbr{soilsystems}\gdef\@ISSN{2571-8789}}
\DeclareOption{solar}{\gdef\@journal{solar}\gdef\@journalfull{Solar}\gdef\@journalshort{Solar}\gdef\@doiabbr{solar}\gdef\@ISSN{2673-9941}\gdef\@continuouspages{yes}}
\DeclareOption{solids}{\gdef\@journal{solids}\gdef\@journalfull{Solids}\gdef\@journalshort{Solids}\gdef\@doiabbr{solids}\gdef\@ISSN{2673-6497}\gdef\@continuouspages{yes}}
\DeclareOption{sports}{\gdef\@journal{sports}\gdef\@journalfull{Sports}\gdef\@journalshort{Sports}\gdef\@doiabbr{sports}\gdef\@ISSN{2075-4663}}
\DeclareOption{standards}{\gdef\@journal{standards}\gdef\@journalfull{Standards}\gdef\@journalshort{Standards}\gdef\@doiabbr{standards}\gdef\@ISSN{2305-6703}\gdef\@continuouspages{yes}}
\DeclareOption{stats}{\gdef\@journal{stats}\gdef\@journalfull{Stats}\gdef\@journalshort{Stats}\gdef\@doiabbr{stats}\gdef\@ISSN{2571-905X}\gdef\@continuouspages{yes}}
\DeclareOption{stresses}{\gdef\@journal{stresses}\gdef\@journalfull{Stresses}\gdef\@journalshort{Stresses}\gdef\@doiabbr{stresses}\gdef\@ISSN{2673-7140}\gdef\@continuouspages{yes}}
\DeclareOption{surfaces}{\gdef\@journal{surfaces}\gdef\@journalfull{Surfaces}\gdef\@journalshort{Surfaces}\gdef\@doiabbr{surfaces}\gdef\@ISSN{2571-9637}\gdef\@continuouspages{yes}}
\DeclareOption{surgeries}{\gdef\@journal{surgeries}\gdef\@journalfull{Surgeries}\gdef\@journalshort{Surgeries}\gdef\@doiabbr{surgeries}\gdef\@ISSN{2017-2017}\gdef\@continuouspages{yes}}
\DeclareOption{suschem}{\gdef\@journal{suschem}\gdef\@journalfull{Sustainable Chemistry}\gdef\@journalshort{Sustain. Chem.}\gdef\@doiabbr{suschem}\gdef\@ISSN{2673-4079}\gdef\@continuouspages{yes}}
\DeclareOption{sustainability}{\gdef\@journal{sustainability}\gdef\@journalfull{Sustainability}\gdef\@journalshort{Sustainability}\gdef\@doiabbr{su}\gdef\@ISSN{2071-1050}}
\DeclareOption{symmetry}{\gdef\@journal{symmetry}\gdef\@journalfull{Symmetry}\gdef\@journalshort{Symmetry}\gdef\@doiabbr{sym}\gdef\@ISSN{2073-8994}}
\DeclareOption{synbio}{\gdef\@journal{synbio}\gdef\@journalfull{Synbio}\gdef\@journalshort{Synbio}\gdef\@doiabbr{synbio}\gdef\@ISSN{2674-0583}\gdef\@continuouspages{yes}}
\DeclareOption{systems}{\gdef\@journal{systems}\gdef\@journalfull{Systems}\gdef\@journalshort{Systems}\gdef\@doiabbr{systems}\gdef\@ISSN{2079-8954}}
\DeclareOption{taxonomy}{\gdef\@journal{taxonomy}\gdef\@journalfull{Taxonomy}\gdef\@journalshort{Taxonomy}\gdef\@doiabbr{taxonomy}\gdef\@ISSN{2673-6500}\gdef\@continuouspages{yes}}
\DeclareOption{technologies}{\gdef\@journal{technologies}\gdef\@journalfull{Technologies}\gdef\@journalshort{Technologies}\gdef\@doiabbr{technologies}\gdef\@ISSN{2227-7080}}
\DeclareOption{telecom}{\gdef\@journal{telecom}\gdef\@journalfull{Telecom}\gdef\@journalshort{Telecom}\gdef\@doiabbr{telecom}\gdef\@ISSN{2673-4001}\gdef\@continuouspages{yes}}
\DeclareOption{test}{\gdef\@journal{test}\gdef\@journalfull{Test}\gdef\@journalshort{Test}\gdef\@doiabbr{}\gdef\@ISSN{}}
\DeclareOption{textiles}{\gdef\@journal{textiles}\gdef\@journalfull{Textiles}\gdef\@journalshort{Textiles}\gdef\@doiabbr{textiles}\gdef\@ISSN{2673-7248}\gdef\@continuouspages{yes}}
\DeclareOption{thermo}{\gdef\@journal{thermo}\gdef\@journalfull{Thermo}\gdef\@journalshort{Thermo}\gdef\@doiabbr{thermo}\gdef\@ISSN{2673-7264}\gdef\@continuouspages{yes}}
\DeclareOption{tomography}{\gdef\@journal{tomography}\gdef\@journalfull{Tomography}\gdef\@journalshort{Tomography}\gdef\@doiabbr{tomography}\gdef\@ISSN{2379-139X}\gdef\@continuouspages{yes}}
\DeclareOption{tourismhosp}{\gdef\@journal{tourismhosp}\gdef\@journalfull{Tourism and Hospitality}\gdef\@journalshort{Tour. Hosp.}\gdef\@doiabbr{tourhosp}\gdef\@ISSN{2673-5768}\gdef\@continuouspages{yes}}
\DeclareOption{toxics}{\gdef\@journal{toxics}\gdef\@journalfull{Toxics}\gdef\@journalshort{Toxics}\gdef\@doiabbr{toxics}\gdef\@ISSN{2305-6304}}
\DeclareOption{toxins}{\gdef\@journal{toxins}\gdef\@journalfull{Toxins}\gdef\@journalshort{Toxins}\gdef\@doiabbr{toxins}\gdef\@ISSN{2072-6651}}
\DeclareOption{transplantology}{\gdef\@journal{transplantology}\gdef\@journalfull{Transplantology}\gdef\@journalshort{Transplantology}\gdef\@doiabbr{transplantology}\gdef\@ISSN{2673-3943}\gdef\@continuouspages{yes}}
\DeclareOption{transportation}{\gdef\@journal{transportation}\gdef\@journalfull{Transportation}\gdef\@journalshort{Transportation}\gdef\@doiabbr{transportation}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{traumacare}{\gdef\@journal{traumacare}\gdef\@journalfull{Trauma Care}\gdef\@journalshort{Trauma Care}\gdef\@doiabbr{traumacare}\gdef\@ISSN{2673-866X}\gdef\@continuouspages{yes}}
\DeclareOption{traumas}{\gdef\@journal{traumas}\gdef\@journalfull{Traumas}\gdef\@journalshort{Traumas}\gdef\@doiabbr{traumas}\gdef\@ISSN{2673-7477}\gdef\@continuouspages{yes}}
\DeclareOption{tropicalmed}{\gdef\@journal{tropicalmed}\gdef\@journalfull{Tropical Medicine and Infectious Disease}\gdef\@journalshort{Trop. Med. Infect. Dis.}\gdef\@doiabbr{tropicalmed}\gdef\@ISSN{2414-6366}}
\DeclareOption{universe}{\gdef\@journal{universe}\gdef\@journalfull{Universe}\gdef\@journalshort{Universe}\gdef\@doiabbr{universe}\gdef\@ISSN{2218-1997}}
\DeclareOption{urbansci}{\gdef\@journal{urbansci}\gdef\@journalfull{Urban Science}\gdef\@journalshort{Urban Sci.}\gdef\@doiabbr{urbansci}\gdef\@ISSN{2413-8851}}
\DeclareOption{uro}{\gdef\@journal{uro}\gdef\@journalfull{Uro}\gdef\@journalshort{Uro}\gdef\@doiabbr{uro}\gdef\@ISSN{2673-4397}\gdef\@continuouspages{yes}}
\DeclareOption{vaccines}{\gdef\@journal{vaccines}\gdef\@journalfull{Vaccines}\gdef\@journalshort{Vaccines}\gdef\@doiabbr{vaccines}\gdef\@ISSN{2076-393X}}
\DeclareOption{vehicles}{\gdef\@journal{vehicles}\gdef\@journalfull{Vehicles}\gdef\@journalshort{Vehicles}\gdef\@doiabbr{vehicles}\gdef\@ISSN{2624-8921}\gdef\@continuouspages{yes}}
\DeclareOption{venereology}{\gdef\@journal{venereology}\gdef\@journalfull{Venereology}\gdef\@journalshort{Venereology}\gdef\@doiabbr{venereology}\gdef\@ISSN{2674-0710}\gdef\@continuouspages{yes}}
\DeclareOption{vetsci}{\gdef\@journal{vetsci}\gdef\@journalfull{Veterinary Sciences}\gdef\@journalshort{Vet. Sci.}\gdef\@doiabbr{vetsci}\gdef\@ISSN{2306-7381}}
\DeclareOption{vibration}{\gdef\@journal{vibration}\gdef\@journalfull{Vibration}\gdef\@journalshort{Vibration}\gdef\@doiabbr{vibration}\gdef\@ISSN{2571-631X}\gdef\@continuouspages{yes}}
\DeclareOption{viruses}{\gdef\@journal{viruses}\gdef\@journalfull{Viruses}\gdef\@journalshort{Viruses}\gdef\@doiabbr{v}\gdef\@ISSN{1999-4915}}
\DeclareOption{vision}{\gdef\@journal{vision}\gdef\@journalfull{Vision}\gdef\@journalshort{Vision}\gdef\@doiabbr{vision}\gdef\@ISSN{2411-5150}}
\DeclareOption{waste}{\gdef\@journal{waste}\gdef\@journalfull{Waste}\gdef\@journalshort{Waste}\gdef\@doiabbr{waste}\gdef\@ISSN{}\gdef\@continuouspages{yes}}
\DeclareOption{water}{\gdef\@journal{water}\gdef\@journalfull{Water}\gdef\@journalshort{Water}\gdef\@doiabbr{w}\gdef\@ISSN{2073-4441}}
\DeclareOption{wem}{\gdef\@journal{wem}\gdef\@journalfull{Wildlife Ecology and Management}\gdef\@journalshort{Wildl. Ecol. Manag.}\gdef\@doiabbr{}\gdef\@ISSN{1234-4321}}
\DeclareOption{wevj}{\gdef\@journal{wevj}\gdef\@journalfull{World Electric Vehicle Journal}\gdef\@journalshort{World Electr. Veh. J.}\gdef\@doiabbr{wevj}\gdef\@ISSN{2032-6653}}
\DeclareOption{wind}{\gdef\@journal{wind}\gdef\@journalfull{Wind}\gdef\@journalshort{Wind}\gdef\@doiabbr{wind}\gdef\@ISSN{2674-032X}\gdef\@continuouspages{yes}}
\DeclareOption{women}{\gdef\@journal{women}\gdef\@journalfull{Women}\gdef\@journalshort{Women}\gdef\@doiabbr{women}\gdef\@ISSN{2673-4184}\gdef\@continuouspages{yes}}
\DeclareOption{world}{\gdef\@journal{world}\gdef\@journalfull{World}\gdef\@journalshort{World}\gdef\@doiabbr{world}\gdef\@ISSN{2673-4060}\gdef\@continuouspages{yes}}
\DeclareOption{youth}{\gdef\@journal{youth}\gdef\@journalfull{Youth}\gdef\@journalshort{Youth}\gdef\@doiabbr{youth}\gdef\@ISSN{2673-995X}\gdef\@continuouspages{yes}}
\DeclareOption{zoonoses}{\gdef\@journal{zoonoses}\gdef\@journalfull{Zoonoses}\gdef\@journalshort{Zoonoses}\gdef\@doiabbr{zoonoses}\gdef\@ISSN{2673-9968}\gdef\@continuouspages{yes}}

### 2021-10-04 manuscript/Manuscript.Rmd
MDPI manuscript
cf rticles package

@@
 status: submit
-bibliography: mybibfile.bib
+bibliography: synth.bib
 appendix: appendix.tex
@@
 conflictsofinterest: |
-  Declare conflicts of interest or state 'The authors declare no conflict of 
-  interest.' Authors must identify and declare any personal circumstances or
-  interest that may be perceived as inappropriately influencing the
-  representation or interpretation of reported research results. Any role of the
-  funding sponsors in the design of the study; in the collection, analyses or 
-  interpretation of data in the writing of the manuscript, or in the decision to 
-  publish the results must be declared in this section. If there is no role, 
-  please state 'The founding sponsors had no role in the design of the study; 
-  in the collection, analyses, or interpretation of data; in the writing of the 
-  manuscript, an in the decision to publish the results'.
+  'The authors declare no conflict of interest.' 
 sampleavailability: |
@@
 
-# Version
-
-This Rmd-skeleton uses the mdpi Latex template published 2019/02. 
-However, the official template gets more frequently updated than the 'rticles'
-package. Therefore, please make sure prior to paper submission, that you're 
-using the most recent .cls, .tex and .bst files 
-(available [here](http://www.mdpi.com/authors/latex)).
-
 # Introduction
 
-The introduction should briefly place the study in a broad context and highlight why it is important.
-It should define the purpose of the work and its significance.
-The current state of the research field should be reviewed carefully and key publications cited.
-Please highlight controversial and diverging hypotheses when necessary.
-Finally, briefly mention the main aim of the work and highlight the principal conclusions.
-As far as possible, please keep the introduction comprehensible to scientists outside your particular field of research.
-Citing a journal paper [@bertrand-krajewski_distribution_1998; @leutnant_stormwater_2016].
-And now citing a book reference @gujer_systems_2008.
-Please use the command [@leutnant_stormwater_2016] for the following MDPI journals, which use author-date citation: Administrative Sciences, Arts, Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws, Religions, Risks, Social Sciences.
+Open science, including open data, has been marked as the future of science [@gewin_data_2016], and the advantages of publicly available research data are numerous [@molloy_open_2011; @walport_brest_sharing_2011].
+Collecting research data requires an enormous investment both in terms of time and monetary resources.
+Openly accessible research data bears the potential of increasing the scientific returns for the same data collection effort.
+Additionally, the fact that public funds are used for data collection results in increasing demand for the collected data.
+Nevertheless, the possibilities to distribute research data directly are often very limited due to restrictions on data privacy and data confidentiality.
+Although these regulations are much needed, privacy constraints are also ranked among the toughest challenges to overcome in the advancement of modern day social science research [@lazer_life_2009].
+
+Anonymizing research data might seem a quick and appealing approach to limit the unique identification of participants.
+However, this approach is not sufficient to fulfil contemporary privacy and confidentiality requirements [@ohm_broken_2009; @national_putting_2007].
+Over the years, several other techniques have been used to increase the confidentiality of research data, such as categorizing continuous variables, top coding values above an upper bound or adding random noise to the observed values [@drechsler_synthetic_2011].
+However, these methods may distort the true data relation between variables, thereby reducing the data quality and the scientific returns for re-using the same data for further research.
+
+An alternative solution has been proposed separately by @rubin_statistical_disclosure_1993 and @little_statistical_1993.
+Although their approaches differ to some extent, the overarching procedure is to use bonafide observed data to generate multiply imputed synthetic data sets that can be freely disclosed.
+While in practice, one could see this as replacing the observed data values by multiple draws from the posterior predictive distribution of the observed data, based on some imputation model, Rubin would argue that these synthetic data values are merely draws from the same true data generating model.
+In that sense, the observed data is never replaced, but the population is resampled from the information captured in the (incomplete) sample.
+Using this approach, the researcher could replace the observed data set as a whole with multiple synthetic versions.
+Alternatively, the researcher could opt to only replace a subset of the observed data.
+For example, one can choose to only replace dimensions in the data that could be compared with publicly available data sets or registers.
+Likewise, synthetisation could be limited to those values that are disclosive, such as high incomes or high turnovers.
+
+Conceptually, the synthetic data framework is based upon the building blocks of multiple imputation of missing data, as proposed by @rubin_multiple_1987.
+Instead of replacing just the missing values with multiple draws from the posterior predictive distribution, one could easily *overimpute* any observed sensitive values.
+Similarly to multiple imputation of missing data, the multiple synthetic data sets allow for correct statistical inferences, despite the fact that the analyses do not use the "true" value.
+The analyses over multiple synthetic data sets should be pooled into a single inference, so that the researcher can draw valid conclusions from the pooled results.
+To that respect, the variance should reflect the added variability that is induced by the imputation procedure.
+
+Potentially, this approach could fulfill the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints.
+However, there is no such thing as a free lunch: data collectors have to put effort in creating high-quality synthetic data.
+Also, the quality of the synthetic data is highly dependent on the imputation models, and using flawed models to generate synthetic data might bias subsequent analyses.
+Conversely, if the models used to create the synthetic data are able to preserve the relationships between the variables as in the original data, the synthetic data can be nearly as informative as the observed data.
+Thus, to fully exploit the benefits of synthetic data, the effort to actually create these high-quality data sets should be kept at a minimum.
+
+To mitigate additional effort of creating synthetic data sets on behalf of the researcher, software aimed at multiple imputation of missing data can be employed.
+Especially if researchers used this software at an earlier stage in the research process, or acquired familiarity with it during earlier projects, the additional burden of creating synthetic data sets is relatively small.
+The R-package `mice` [@mice] implements multiple imputation of missing data in a straightforward and user-friendly manner.
+However, the functionality of `mice` is not restricted to the imputation of missing data, but allows to impute any value in the data: even observed values.
+Consequently, `mice` can be utilized for the creation of multiply imputed synthetic data sets.
+
+After creating the multiply imputed synthetic data sets, the goal is to obtain valid statistical inferences in the spirit of @rubin_multiple_1987 and @neyman1934.
+In the missing data framework, this is done by performing statistical analyses on all imputed data sets, and pooling the results of the analyses according to Rubin's rules [@rubin_multiple_1987, pp.76].
+In the synthetic data framework, the same procedure is followed, but with a slight twist: there are no values that remain constant over the synthetic data sets.
+The procedure of drawing valid inferences from multiple synthetic data sets is therefore slightly different.
+
+In this manuscript we detail a workflow for synthesizing data with `mice`.
+First, the `mice` algorithm for the creation of synthetic data will be shortly explained.
+The aim is to generate synthetic sets that reassure the privacy and confidentiality of the participants.
+Second, a straightforward workflow for imputation of synthetic data with `mice` will be demonstrated.
+Third, we demonstrate the validity of the procedure through statistical simulation.
+
+# Generating synthetic data with `mice`
+
+The `mice` package [@mice] in `R` [@Rproject] has been developed for multiple imputation of missing data.
+In this context, the aim is to replace missing values due to nonresponse by plausible values from the posterior predictive distribution of the variable containing the missings.
+Doing so, `mice` makes use of fully conditional specification [FCS; @vanbuuren_fully_2006], which breaks down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, where $k$ denotes the number of columns in the data.
+Using FCS, a model is constructed for every incomplete variable and the missing values $Y_{j, mis}$ are then imputed with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ on a variable-by-variable basis.
+Note that the predictor matrix $Y_{-j}$ may contain yet imputed values from an earlier imputation step, and thus will be updated after every iteration.
+This procedure is applied $m$ times, resulting in $m$ completed data sets $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $\textbf{D}^{(l)} = (\textbf{Y}_{obs}, Y^{(l)}_{mis})$.
+
+In `mice`, the generation of multiply imputed data sets to solve for unobserved values is straightforward.
+The following pseudocode details the multiple imputation of the `mice::boys` data set [@fredriks_boys_2000] into the object `imp` with `m = 10` imputated sets and `maxit = 7` iterations for the algorithm to converge, using the default imputations methods for each column data class.
+
+```{r eval = FALSE}
+library(mice)
+imp <- mice(boys, 
+            m = 10,
+            maxit = 7)
+```
+
+It is straightforward to extended the imputation approach to generate synthetic values.
+Rather than imputing missing data, the observed values are then replaced by synthetic draws from the posterior predictive distribution.
+For simplicity, assume that the data is completely observed (i.e., $\textbf{Y} = \textbf{Y}_{obs}$).
+Following the notation of @reiter_raghunathan_multiple_2007, let for $n$ units denote $Z_i = 1$ if any of the values of unit $i = 1, 2, \dots, n$ are to be replaced by imputations, and $Z_i = 0$ otherwise, with $\textbf{Z} = (Z_1, Z_2, \dots, Z_n)$.
+Accordingly, the data consists of values that are to be replaced and values that are to be kept (i.e., $\textbf{Y} = (\textbf{Y}_{rep}, \textbf{Y}_{nrep})$.
+Now, instead of imputing $\textbf{Y}_{mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, $\textbf{Y}_{rep}$ is imputed from the posterior distribution of $P(Y^{(l)}_{j, rep} | \textbf{Y}^{(l)}_{-j}, \textbf{Z}, \theta)$, where $l$ is an indicator for the synthetic data set ($l = 1, 2, \dots, m$).
+Note that synthetic values that are imputed at an earlier step can be used for imputing variable $j$.
+This process results in the synthetic data $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$.
+
+For example, overimputing synthetic values for both the observed and missing cells in the `mice::boys` data set into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution.
+
+```{r eval = FALSE}
+syn <- mice(boys, 
+            m = 10,
+            maxit = 7, 
+            where = matrix(TRUE, 
+                           nrow = nrow(boys),
+                           ncol = ncol(boys)))
+```
+
+where the argument `where` requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix) containing logicals $z_{ij}$ that indicate which cells are selected to have their values replaced by draws from the posterior predictive distribution.
+This approach allows to *overimpute* a subset of the observed data, or - as in the above example - the observed data as a whole, resulting in a data set that partly or completely consists of synthetic data values.
+
+Choosing an adequate imputation model to impute the data is paramount, as a flawed imputation model may drastically impact the validity of inferences.
+Imputation models should be as flexible as possible to capture most of the patterns in the data, and to model possibly unanticipated data characteristics [@murray_multiple_2018; @rubin_18years_1996].
+Parametric methods, albeit easy to implement in practice, may be too restrictive to capture generally complex patterns in the data, especially in the case of nonlinear relations and interactions between multiple variables.
+Classification and regression trees [CART; @breiman_cart_1984] allow to model more complex patterns in the data, and have therefore been suggested as an appropriate imputation method [@reiter_cart_2005; @burgette_reiter_cart_2010; @doove_buuren_recursive_2014].
+Loosely speaking, CART sequentially splits the predictor space into non-overlapping regions in such a way that the within-region variance is as small as possible after every split.
+As such, CART does not impose any parametric distribution on the data, making it a widely applicable method that allows for a large variety of relationships within the data [@islr_2013].
+Given these appealing characteristics and the call for the use of flexible methods when multiply imputing data, we will focus our illustrations and evaluations of `mice` to method `mice.impute.cart()`, realized by:
+
+```{r eval = FALSE}
+syn <- mice(boys, 
+            m = 10,
+            maxit = 7, 
+            method = "cart",
+            where = matrix(TRUE, 
+                           nrow = nrow(boys),
+                           ncol = ncol(boys)))
+```
+
+In a nutshell, the above code shows the simplicity of creating $m = 10$ synthetic data sets using `mice`.
+In practice, however, one should take some additional complicating factors into account.
+For example, one should account for deterministic relations in the data.
+Additionally, relations between variables may be described best using a different model than `CART`.
+Such factors are data dependent and should be considered by the imputer.
+In the next section, we will describe how the `boys` data can be adequately imputed.
+Additionally, we will show through simulations that this approach yields valid inferences.
 
@@
 
-Materials and Methods should be described with sufficient details to allow others to replicate and build on published results.
-Please note that publication of your manuscript implicates that you must make all materials, data, computer code, and protocols associated with the publication available to readers.
-Please disclose at the submission stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while well-established methods can be briefly described and appropriately cited.
+We demonstrate the suitability of using `mice` for synthesization using a simulation study on the `mice::boys` data set.
+This data set consists of the values of $`r nrow(mice::boys)`$ Dutch boys on the following $`r ncol(mice::boys)`$ variables:
 
-Research manuscripts reporting large datasets that are deposited in a publicly available database should specify where the data have been deposited and provide the relevant accession numbers.
-If the accession numbers have not yet been obtained at the time of submission, please state that they will be provided during review.
-They must be provided prior to publication.
+| column | description                |
+|--------|----------------------------|
+| age    | age in years               |
+| hgt    | height (cm)                |
+| wgt    | weight (kg)                |
+| bmi    | body mass index            |
+| hc     | head circumference (cm)    |
+| gen    | genital Tanner stage G1-G5 |
+| phb    | pubic hair Tanner P1-P6    |
+| tv     | testicular volume (ml)     |
+| reg    | region                     |
 
-Interventionary studies involving animals or humans, and other studies require ethical approval must list the authority that provided approval and the corresponding ethical approval code.
+Unfortunately, this data set does not differ from the vast majority of collected data sets, in the sense that it suffers from missing data.
+For simplicity, the data is completed using the default `mice` imputation model for all predictors except `bmi`, which is passively imputed using its deterministic relation with weight and height.
+
+```{r, include = FALSE}
+library(mice)
+library(tibble)
+library(magrittr)
+library(tidyverse)
+library(furrr)
+library(knitr)
+library(kableExtra)
+library(psych)
+library(purrr)
+library(dplyr)
+library(knitr)
+library(kableExtra)
+```
+
+```{r, results = FALSE, message = FALSE, warning = FALSE}
+# create a single imputed, completely observed `boys` data set
+set.seed(123)
+
+meth <- make.method(boys)
+meth["bmi"] <- "~ I(wgt / (hgt / 100)^2)"
+pred <- make.predictorMatrix(boys)
+pred[c("hgt", "wgt"), "bmi"] <- 0
+
+imp <- mice(boys, 
+            m = 1,
+            maxit = 10,
+            method = meth,
+            predictorMatrix = pred)
+
+data <- complete(imp)
+```
+
+## Simulation methods
+
+To induce sampling variance, 1000 bootstrap samples of the `boys` data have been synthesized with $m = 5$ imputations for every data cell.
+Synthetic values are generated using the `CART` imputation method for all columns, except for `bmi`.
+The deterministic relation `bmi` which will be synthesized passively based on the synthetic values for `hgt` and `wgt` to preserve the relation in the synthetic data.
+Additional parameters that come with the use of `mice.impute.cart()` are the complexity parameter `cp` and the minimum number of observations in any terminal node `minbucket`, that both constrain the flexibility of the imputation model.
+The values of the parameters `cp` and `minbucket` ought to adhere to the call for imputation models that are as flexible as possible.
+Appropriate values for these parameters, as well as the input for the `predictorMatrix`, depend on the data at hand.
+In the current example, the complexity parameter is specified at `cp = 1e-08` rather than the default value `1e-04`, and the minimum number of observations in each terminal node is set at `minbucket` $= 3$ rather than the default value $5$.
+By allowing for more complexity in the imputation model, bias in the estimates from the synthetic data set is reduced.
+Additionally, since the missingness pattern is monotone, the number of iterations can be set to `maxit = 1`.
+
+To assess the performance of `mice` for synthesizing data, we compare the bootstrapped samples with the synthetic versions of these bootstrapped samples.
+Specifically, univariate descriptive statistics, the correlation matrix, and two linear regression models as well as one ordered logistic regression model will be considered.
+Subsequently, the bias in the parameters and the $95\%$ confidence interval coverage of the synthetic data will be examined.
+Similarly to multiple imputation of missing data, correct inferences from synthetic data requires correct pooling over the multiply imputed data sets.
+
+Obtaining a final point estimate of the parameter of interest $Q$ after imputation is fairly easy and no different from pooling in the case of missing data [@rubin_multiple_1987].
+One can calculate the average of the $m$ point estimates $q^{(l)}$
+$$
+\bar{q}_m = \sum_{l = 1}^m \frac{q^{(l)}}{m}.
+$$
+with $l = 1, \dots, m$.
+
+Similarly to the missing data case, variances, and subsequently confidence intervals, should incorporate the increase in variance that is due to imputation [@reiter_partially_inference_2003; @drechsler_synthetic_2011].
+Yet, the increase in variance due to imputation differs according to whether missing values are imputed or observed data is overimputed with missing values.
+Whereas the variance estimate after imputation of missing data needs to account for the fact that a certain amount of information in the data is missing, variance estimation from synthetic data does not suffer from this issue.
+The adjusted variance estimate that follows from using multiple synthetic data sets only suffers from the fact that a finite number of $m$ synthetic data sets are used to resemble the observed data.
+Hence, the according variance estimate for synthetic data as developed by @reiter_partially_inference_2003 yields
+$$
+T = \bar{u}_m + \frac{b_m}{m},
+$$
+
+with between-imputation variance
+
+$$
+b_m = \sum_{l = 1}^m \frac{(q^{(l)} - \bar{q}_m)^2}{(m - 1)}, \\
+$$
+and sampling variance
+
+$$
+\bar{u}_m = \sum_{l = 1} \frac{u^{(l)}}{m},
+$$
+where $u^{(l)}$ denotes the variance estimate in the $l$th synthetic data set.
 
 # Results
+```{r, message = FALSE, warning = FALSE, cache = TRUE, cache.lazy = FALSE}
+plan(multisession) # increase speed through futures
+
+true_model_age <- lm(age ~ wgt + hgt, data) # model 1
+true_model_wgt <- lm(wgt ~ age + hgt, data) # model 2
+true_model_gen <- MASS::polr(gen ~ age + hc + reg, data, Hess = TRUE) # model 3
+
+coefs_age <- broom::tidy(true_model_age)$estimate # extract coefficients of model 1
+coefs_wgt <- broom::tidy(true_model_wgt)$estimate # extract coefficients of model 2
+coefs_gen <- broom::tidy(true_model_gen)$estimate # extract coefficients of model 3
+
+nsim <- 1000 # use 1000 iterations
+
+bootstrap_samples <- 
+  modelr::bootstrap(data = data, n = nsim) %$% 
+  strap %>% 
+  map(as_tibble)
+
+post <- make.post(data)
+post["bmi"] <- "imp[[j]][, i] <- imp[['wgt']][, i] / (imp[['hgt']][, i] / 100)^2"
+
+synthetic_samples <- 
+  bootstrap_samples %>%
+  future_map(function(x) {
+    x %>% mice(m = 5, 
+               maxit = 1,
+               method = "cart",
+               minbucket = 3,
+               cp = 1e-08,
+               predictorMatrix = pred,
+               post = post,
+               where = matrix(TRUE, nrow(data), ncol(data)),
+               print = F)
+}, .options = furrr_options(seed = as.integer(123)))
+```
 

### 2021-10-04 manuscript/Manuscript.tex
MDPI manuscript
cf rticles package

@@
 % see https://stackoverflow.com/a/47122900
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 
@@
 
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+
 \begin{document}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\hypertarget{version}{%
-\section{Version}\label{version}}
-
-This Rmd-skeleton uses the mdpi Latex template published 2019/02.
-However, the official template gets more frequently updated than the
-`rticles' package. Therefore, please make sure prior to paper
-submission, that you're using the most recent .cls, .tex and .bst files
-(available \href{http://www.mdpi.com/authors/latex}{here}).
 
@@
 
-The introduction should briefly place the study in a broad context and
-highlight why it is important. It should define the purpose of the work
-and its significance. The current state of the research field should be
-reviewed carefully and key publications cited. Please highlight
-controversial and diverging hypotheses when necessary. Finally, briefly
-mention the main aim of the work and highlight the principal
-conclusions. As far as possible, please keep the introduction
-comprehensible to scientists outside your particular field of research.
-Citing a journal paper
-\citep{bertrand-krajewski_distribution_1998, leutnant_stormwater_2016}.
-And now citing a book reference \citet{gujer_systems_2008}. Please use
-the command \citep{leutnant_stormwater_2016} for the following MDPI
-journals, which use author-date citation: Administrative Sciences, Arts,
-Econometrics, Economies, Genealogy, Humanities, IJFS, JRFM, Laws,
-Religions, Risks, Social Sciences.
+Open science, including open data, has been marked as the future of
+science \citep{gewin_data_2016}, and the advantages of publicly
+available research data are numerous
+\citep{molloy_open_2011, walport_brest_sharing_2011}. Collecting
+research data requires an enormous investment both in terms of time and
+monetary resources. Openly accessible research data bears the potential
+of increasing the scientific returns for the same data collection
+effort. Additionally, the fact that public funds are used for data
+collection results in increasing demand for the collected data.
+Nevertheless, the possibilities to distribute research data directly are
+often very limited due to restrictions on data privacy and data
+confidentiality. Although these regulations are much needed, privacy
+constraints are also ranked among the toughest challenges to overcome in
+the advancement of modern day social science research
+\citep{lazer_life_2009}.
+
+Anonymizing research data might seem a quick and appealing approach to
+limit the unique identification of participants. However, this approach
+is not sufficient to fulfil contemporary privacy and confidentiality
+requirements \citep{ohm_broken_2009, national_putting_2007}. Over the
+years, several other techniques have been used to increase the
+confidentiality of research data, such as categorizing continuous
+variables, top coding values above an upper bound or adding random noise
+to the observed values \citep{drechsler_synthetic_2011}. However, these
+methods may distort the true data relation between variables, thereby
+reducing the data quality and the scientific returns for re-using the
+same data for further research.
+
+An alternative solution has been proposed separately by
+\citet{rubin_statistical_disclosure_1993} and
+\citet{little_statistical_1993}. Although their approaches differ to
+some extent, the overarching procedure is to use bonafide observed data
+to generate multiply imputed synthetic data sets that can be freely
+disclosed. While in practice, one could see this as replacing the
+observed data values by multiple draws from the posterior predictive
+distribution of the observed data, based on some imputation model, Rubin
+would argue that these synthetic data values are merely draws from the
+same true data generating model. In that sense, the observed data is
+never replaced, but the population is resampled from the information
+captured in the (incomplete) sample. Using this approach, the researcher
+could replace the observed data set as a whole with multiple synthetic
+versions. Alternatively, the researcher could opt to only replace a
+subset of the observed data. For example, one can choose to only replace
+dimensions in the data that could be compared with publicly available
+data sets or registers. Likewise, synthetisation could be limited to
+those values that are disclosive, such as high incomes or high
+turnovers.
+
+Conceptually, the synthetic data framework is based upon the building
+blocks of multiple imputation of missing data, as proposed by
+\citet{rubin_multiple_1987}. Instead of replacing just the missing
+values with multiple draws from the posterior predictive distribution,
+one could easily \emph{overimpute} any observed sensitive values.
+Similarly to multiple imputation of missing data, the multiple synthetic
+data sets allow for correct statistical inferences, despite the fact
+that the analyses do not use the ``true'' value. The analyses over
+multiple synthetic data sets should be pooled into a single inference,
+so that the researcher can draw valid conclusions from the pooled
+results. To that respect, the variance should reflect the added
+variability that is induced by the imputation procedure.
+
+Potentially, this approach could fulfill the needs for openly accessibly
+data, without running into barriers with regard to privacy and
+confidentiality constraints. However, there is no such thing as a free
+lunch: data collectors have to put effort in creating high-quality
+synthetic data. Also, the quality of the synthetic data is highly
+dependent on the imputation models, and using flawed models to generate
+synthetic data might bias subsequent analyses. Conversely, if the models
+used to create the synthetic data are able to preserve the relationships
+between the variables as in the original data, the synthetic data can be
+nearly as informative as the observed data. Thus, to fully exploit the
+benefits of synthetic data, the effort to actually create these
+high-quality data sets should be kept at a minimum.
+
+To mitigate additional effort of creating synthetic data sets on behalf
+of the researcher, software aimed at multiple imputation of missing data
+can be employed. Especially if researchers used this software at an
+earlier stage in the research process, or acquired familiarity with it
+during earlier projects, the additional burden of creating synthetic
+data sets is relatively small. The R-package \texttt{mice} \citep{mice}
+implements multiple imputation of missing data in a straightforward and
+user-friendly manner. However, the functionality of \texttt{mice} is not
+restricted to the imputation of missing data, but allows to impute any
+value in the data: even observed values. Consequently, \texttt{mice} can
+be utilized for the creation of multiply imputed synthetic data sets.
+
+After creating the multiply imputed synthetic data sets, the goal is to
+obtain valid statistical inferences in the spirit of
+\citet{rubin_multiple_1987} and \citet{neyman1934}. In the missing data
+framework, this is done by performing statistical analyses on all
+imputed data sets, and pooling the results of the analyses according to
+Rubin's rules \citep[pp.76]{rubin_multiple_1987}. In the synthetic data
+framework, the same procedure is followed, but with a slight twist:
+there are no values that remain constant over the synthetic data sets.
+The procedure of drawing valid inferences from multiple synthetic data
+sets is therefore slightly different.
+
+In this manuscript we detail a workflow for synthesizing data with
+\texttt{mice}. First, the \texttt{mice} algorithm for the creation of
+synthetic data will be shortly explained. The aim is to generate
+synthetic sets that reassure the privacy and confidentiality of the
+participants. Second, a straightforward workflow for imputation of
+synthetic data with \texttt{mice} will be demonstrated. Third, we
+demonstrate the validity of the procedure through statistical
+simulation.
+
+\hypertarget{generating-synthetic-data-with-mice}{%
+\section{\texorpdfstring{Generating synthetic data with
+\texttt{mice}}{Generating synthetic data with mice}}\label{generating-synthetic-data-with-mice}}
+
+The \texttt{mice} package \citep{mice} in \texttt{R} \citep{Rproject}
+has been developed for multiple imputation of missing data. In this
+context, the aim is to replace missing values due to nonresponse by
+plausible values from the posterior predictive distribution of the
+variable containing the missings. Doing so, \texttt{mice} makes use of
+fully conditional specification {[}FCS; \citet{vanbuuren_fully_2006}{]},
+which breaks down the multivariate distribution of the data
+\(\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})\) into
+\(j = 1, 2, \dots, k\) univariate conditional densities, where \(k\)
+denotes the number of columns in the data. Using FCS, a model is
+constructed for every incomplete variable and the missing values
+\(Y_{j, mis}\) are then imputed with draws from the posterior predictive
+distribution of \(P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)\) on a
+variable-by-variable basis. Note that the predictor matrix \(Y_{-j}\)
+may contain yet imputed values from an earlier imputation step, and thus
+will be updated after every iteration. This procedure is applied \(m\)
+times, resulting in \(m\) completed data sets
+\(\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})\),
+with \(\textbf{D}^{(l)} = (\textbf{Y}_{obs}, Y^{(l)}_{mis})\).
+
+In \texttt{mice}, the generation of multiply imputed data sets to solve
+for unobserved values is straightforward. The following pseudocode
+details the multiple imputation of the \texttt{mice::boys} data set
+\citep{fredriks_boys_2000} into the object \texttt{imp} with
+\texttt{m\ =\ 10} imputated sets and \texttt{maxit\ =\ 7} iterations for
+the algorithm to converge, using the default imputations methods for
+each column data class.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(mice)}
+\NormalTok{imp }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(boys, }
+            \AttributeTok{m =} \DecValTok{10}\NormalTok{,}
+            \AttributeTok{maxit =} \DecValTok{7}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+It is straightforward to extended the imputation approach to generate
+synthetic values. Rather than imputing missing data, the observed values
+are then replaced by synthetic draws from the posterior predictive
+distribution. For simplicity, assume that the data is completely
+observed (i.e., \(\textbf{Y} = \textbf{Y}_{obs}\)). Following the
+notation of \citet{reiter_raghunathan_multiple_2007}, let for \(n\)
+units denote \(Z_i = 1\) if any of the values of unit
+\(i = 1, 2, \dots, n\) are to be replaced by imputations, and
+\(Z_i = 0\) otherwise, with \(\textbf{Z} = (Z_1, Z_2, \dots, Z_n)\).
+Accordingly, the data consists of values that are to be replaced and
+values that are to be kept (i.e.,
+\(\textbf{Y} = (\textbf{Y}_{rep}, \textbf{Y}_{nrep})\). Now, instead of
+imputing \(\textbf{Y}_{mis}\) with draws from the posterior predictive
+distribution of \(P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)\) as in the
+missing data case, \(\textbf{Y}_{rep}\) is imputed from the posterior
+distribution of
+\(P(Y^{(l)}_{j, rep} | \textbf{Y}^{(l)}_{-j}, \textbf{Z}, \theta)\),
+where \(l\) is an indicator for the synthetic data set
+(\(l = 1, 2, \dots, m\)). Note that synthetic values that are imputed at
+an earlier step can be used for imputing variable \(j\). This process
+results in the synthetic data
+\(\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})\).
+
+For example, overimputing synthetic values for both the observed and
+missing cells in the \texttt{mice::boys} data set into the object
+\texttt{syn}, given the same imputation parameters as before, can be
+realized by the following code execution.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{syn }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(boys, }
+            \AttributeTok{m =} \DecValTok{10}\NormalTok{,}
+            \AttributeTok{maxit =} \DecValTok{7}\NormalTok{, }
+            \AttributeTok{where =} \FunctionTok{matrix}\NormalTok{(}\ConstantTok{TRUE}\NormalTok{, }
+                           \AttributeTok{nrow =} \FunctionTok{nrow}\NormalTok{(boys),}
+                           \AttributeTok{ncol =} \FunctionTok{ncol}\NormalTok{(boys)))}
+\end{Highlighting}
+\end{Shaded}
+
+where the argument \texttt{where} requires a matrix of the same
+dimensions as the data, (i.e., a \(n \times k\) matrix) containing
+logicals \(z_{ij}\) that indicate which cells are selected to have their
+values replaced by draws from the posterior predictive distribution.
+This approach allows to \emph{overimpute} a subset of the observed data,
+or - as in the above example - the observed data as a whole, resulting
+in a data set that partly or completely consists of synthetic data
+values.
+
+Choosing an adequate imputation model to impute the data is paramount,
+as a flawed imputation model may drastically impact the validity of
+inferences. Imputation models should be as flexible as possible to
+capture most of the patterns in the data, and to model possibly
+unanticipated data characteristics
+\citep{murray_multiple_2018, rubin_18years_1996}. Parametric methods,
+albeit easy to implement in practice, may be too restrictive to capture
+generally complex patterns in the data, especially in the case of
+nonlinear relations and interactions between multiple variables.
+Classification and regression trees {[}CART;
+\citet{breiman_cart_1984}{]} allow to model more complex patterns in the
+data, and have therefore been suggested as an appropriate imputation
+method
+\citep{reiter_cart_2005, burgette_reiter_cart_2010, doove_buuren_recursive_2014}.
+Loosely speaking, CART sequentially splits the predictor space into
+non-overlapping regions in such a way that the within-region variance is
+as small as possible after every split. As such, CART does not impose
+any parametric distribution on the data, making it a widely applicable
+method that allows for a large variety of relationships within the data
+\citep{islr_2013}. Given these appealing characteristics and the call
+for the use of flexible methods when multiply imputing data, we will
+focus our illustrations and evaluations of \texttt{mice} to method
+\texttt{mice.impute.cart()}, realized by:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{syn }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(boys, }
+            \AttributeTok{m =} \DecValTok{10}\NormalTok{,}
+            \AttributeTok{maxit =} \DecValTok{7}\NormalTok{, }
+            \AttributeTok{method =} \StringTok{"cart"}\NormalTok{,}
+            \AttributeTok{where =} \FunctionTok{matrix}\NormalTok{(}\ConstantTok{TRUE}\NormalTok{, }
+                           \AttributeTok{nrow =} \FunctionTok{nrow}\NormalTok{(boys),}
+                           \AttributeTok{ncol =} \FunctionTok{ncol}\NormalTok{(boys)))}
+\end{Highlighting}
+\end{Shaded}
+
+In a nutshell, the above code shows the simplicity of creating
+\(m = 10\) synthetic data sets using \texttt{mice}. In practice,
+however, one should take some additional complicating factors into
+account. For example, one should account for deterministic relations in
+the data. Additionally, relations between variables may be described
+best using a different model than \texttt{CART}. Such factors are data
+dependent and should be considered by the imputer. In the next section,
+we will describe how the \texttt{boys} data can be adequately imputed.
+Additionally, we will show through simulations that this approach yields
+valid inferences.
 
@@
 
-Materials and Methods should be described with sufficient details to
-allow others to replicate and build on published results. Please note
-that publication of your manuscript implicates that you must make all
-materials, data, computer code, and protocols associated with the
-publication available to readers. Please disclose at the submission
-stage any restrictions on the availability of materials or information.
-New methods and protocols should be described in detail while
-well-established methods can be briefly described and appropriately
-cited.
+We demonstrate the suitability of using \texttt{mice} for synthesization
+using a simulation study on the \texttt{mice::boys} data set. This data
+set consists of the values of \(748\) Dutch boys on the following \(9\)
+variables:
 
-Research manuscripts reporting large datasets that are deposited in a
-publicly available database should specify where the data have been
-deposited and provide the relevant accession numbers. If the accession
-numbers have not yet been obtained at the time of submission, please
-state that they will be provided during review. They must be provided
-prior to publication.
+\begin{longtable}[]{@{}ll@{}}
+\toprule
+column & description \\
+\midrule
+\endhead
+age & age in years \\
+hgt & height (cm) \\
+wgt & weight (kg) \\
+bmi & body mass index \\
+hc & head circumference (cm) \\
+gen & genital Tanner stage G1-G5 \\
+phb & pubic hair Tanner P1-P6 \\
+tv & testicular volume (ml) \\
+reg & region \\
+\bottomrule
+\end{longtable}
 
-Interventionary studies involving animals or humans, and other studies
-require ethical approval must list the authority that provided approval
-and the corresponding ethical approval code.
+Unfortunately, this data set does not differ from the vast majority of
+collected data sets, in the sense that it suffers from missing data. For
+simplicity, the data is completed using the default \texttt{mice}
+imputation model for all predictors except \texttt{bmi}, which is
+passively imputed using its deterministic relation with weight and
+height.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# create a single imputed, completely observed \textasciigrave{}boys\textasciigrave{} data set}
+\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
+
+\NormalTok{meth }\OtherTok{\textless{}{-}} \FunctionTok{make.method}\NormalTok{(boys)}
+\NormalTok{meth[}\StringTok{"bmi"}\NormalTok{] }\OtherTok{\textless{}{-}} \StringTok{"\textasciitilde{} I(wgt / (hgt / 100)\^{}2)"}
+\NormalTok{pred }\OtherTok{\textless{}{-}} \FunctionTok{make.predictorMatrix}\NormalTok{(boys)}
+\NormalTok{pred[}\FunctionTok{c}\NormalTok{(}\StringTok{"hgt"}\NormalTok{, }\StringTok{"wgt"}\NormalTok{), }\StringTok{"bmi"}\NormalTok{] }\OtherTok{\textless{}{-}} \DecValTok{0}
+
+\NormalTok{imp }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(boys, }
+            \AttributeTok{m =} \DecValTok{1}\NormalTok{,}
+            \AttributeTok{maxit =} \DecValTok{10}\NormalTok{,}
+            \AttributeTok{method =}\NormalTok{ meth,}
+            \AttributeTok{predictorMatrix =}\NormalTok{ pred)}
+
+\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{complete}\NormalTok{(imp)}
+\end{Highlighting}
+\end{Shaded}
+
+\hypertarget{simulation-methods}{%
+\subsection{Simulation methods}\label{simulation-methods}}
+
+To induce sampling variance, 1000 bootstrap samples of the \texttt{boys}
+data will be synthesized with \(m = 5\) imputations. Synthetic values
+are generated using the \texttt{CART} imputation method for all columns,
+except for \texttt{bmi}. The deterministic relation \texttt{bmi} which
+will be synthesized passively based on the synthetic values for
+\texttt{hgt} and \texttt{wgt} to preserve the relation in the synthetic
+data. Additional parameters that come with the use of
+\texttt{mice.impute.cart()} are the complexity parameter \texttt{cp} and
+the minimum number of observations in any terminal node
+\texttt{minbucket}, that both constrain the flexibility of the
+imputation model. The values of the parameters \texttt{cp} and
+\texttt{minbucket} ought to adhere to the call for imputation models
+that are as flexible as possible. Appropriate values for these
+parameters, as well as the input for the \texttt{predictorMatrix},
+depend on the data at hand. In the current example, the complexity
+parameter is specified at \texttt{cp\ =\ 1e-08} rather than the default
+value \texttt{1e-04}, and the minimum number of observations in each
+terminal node is set at \texttt{minbucket} \(= 3\) rather than the
+default value \(5\). By allowing for more complexity in the imputation
+model, bias in the estimates from the synthetic data set is reduced.
+Additionally, since the missingness pattern is monotone, the number of
+iterations can be set to \texttt{maxit\ =\ 1}.
+
+To assess the performance of \texttt{mice} for synthesizing data, we
+compare the bootstrapped samples with the synthetic versions of these
+bootstrapped samples. Specifically, univariate descriptive statistics,
+the correlation matrix, and two linear regression models as well as one
+ordered logistic regression model will be considered. Subsequently, the
+bias in the parameters and the \(95\%\) confidence interval coverage of
+the synthetic data will be examined. Similarly to multiple imputation of
+missing data, correct inferences from synthetic data requires correct
+pooling over the multiply imputed data sets.
+
+Obtaining a final point estimate of the parameter of interest \(Q\)
+after imputation is fairly easy and no different from pooling in the
+case of missing data \citep{rubin_multiple_1987}. One can calculate the
+average of the \(m\) point estimates \(q^{(l)}\) \[
+\bar{q}_m = \sum_{l = 1}^m \frac{q^{(l)}}{m}.
+\] with \(l = 1, \dots, m\).
+
+Similarly to the missing data case, variances, and subsequently
+confidence intervals, should incorporate the increase in variance that
+is due to imputation
+\citep{reiter_partially_inference_2003, drechsler_synthetic_2011}. Yet,
+the increase in variance due to imputation differs according to whether
+missing values are imputed or observed data is overimputed with missing
+values. Whereas the variance estimate after imputation of missing data
+needs to account for the fact that a certain amount of information in
+the data is missing, variance estimation from synthetic data does not
+suffer from this issue. The adjusted variance estimate that follows from
+using multiple synthetic data sets only suffers from the fact that a
+finite number of \(m\) synthetic data sets are used to resemble the
+observed data. Hence, the according variance estimate for synthetic data
+as developed by \citet{reiter_partially_inference_2003} yields \[
+T = \bar{u}_m + \frac{b_m}{m},
+\]
+
+with between-imputation variance
+
+\[
+b_m = \sum_{l = 1}^m \frac{(q^{(l)} - \bar{q}_m)^2}{(m - 1)}, \\
+\] and sampling variance
+
+\[
+\bar{u}_m = \sum_{l = 1} \frac{u^{(l)}}{m},
+\] with \(u^{(l)}\) reflecting the variance estimate in the \(l\)th
+synthetic data set.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\conflictsofinterest{Declare conflicts of interest or state `The authors
-declare no conflict of interest.' Authors must identify and declare any
-personal circumstances or interest that may be perceived as
-inappropriately influencing the representation or interpretation of
-reported research results. Any role of the funding sponsors in the
-design of the study; in the collection, analyses or interpretation of
-data in the writing of the manuscript, or in the decision to publish the
-results must be declared in this section. If there is no role, please
-state `The founding sponsors had no role in the design of the study; in
-the collection, analyses, or interpretation of data; in the writing of
-the manuscript, an in the decision to publish the results'.}
+\conflictsofinterest{`The authors declare no conflict of interest.'}
 
@@
 \externalbibliography{yes}
-\bibliography{mybibfile.bib}
+\bibliography{synth.bib}
 

### 2021-10-04 manuscript/Manuscript.tex
update with cached sims

@@
 To induce sampling variance, 1000 bootstrap samples of the \texttt{boys}
-data will be synthesized with \(m = 5\) imputations. Synthetic values
-are generated using the \texttt{CART} imputation method for all columns,
-except for \texttt{bmi}. The deterministic relation \texttt{bmi} which
-will be synthesized passively based on the synthetic values for
-\texttt{hgt} and \texttt{wgt} to preserve the relation in the synthetic
-data. Additional parameters that come with the use of
-\texttt{mice.impute.cart()} are the complexity parameter \texttt{cp} and
-the minimum number of observations in any terminal node
+data have been synthesized with \(m = 5\) imputations for every data
+cell. Synthetic values are generated using the \texttt{CART} imputation
+method for all columns, except for \texttt{bmi}. The deterministic
+relation \texttt{bmi} which will be synthesized passively based on the
+synthetic values for \texttt{hgt} and \texttt{wgt} to preserve the
+relation in the synthetic data. Additional parameters that come with the
+use of \texttt{mice.impute.cart()} are the complexity parameter
+\texttt{cp} and the minimum number of observations in any terminal node
 \texttt{minbucket}, that both constrain the flexibility of the
@@
 \bar{u}_m = \sum_{l = 1} \frac{u^{(l)}}{m},
-\] with \(u^{(l)}\) reflecting the variance estimate in the \(l\)th
+\] where \(u^{(l)}\) denotes the variance estimate in the \(l\)th
 synthetic data set.
@@
 \section{Results}\label{results}}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{plan}\NormalTok{(multisession) }\CommentTok{\# increase speed through futures}
+
+\NormalTok{true\_model\_age }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(age }\SpecialCharTok{\textasciitilde{}}\NormalTok{ wgt }\SpecialCharTok{+}\NormalTok{ hgt, data) }\CommentTok{\# model 1}
+\NormalTok{true\_model\_wgt }\OtherTok{\textless{}{-}} \FunctionTok{lm}\NormalTok{(wgt }\SpecialCharTok{\textasciitilde{}}\NormalTok{ age }\SpecialCharTok{+}\NormalTok{ hgt, data) }\CommentTok{\# model 2}
+\NormalTok{true\_model\_gen }\OtherTok{\textless{}{-}}\NormalTok{ MASS}\SpecialCharTok{::}\FunctionTok{polr}\NormalTok{(gen }\SpecialCharTok{\textasciitilde{}}\NormalTok{ age }\SpecialCharTok{+}\NormalTok{ hc }\SpecialCharTok{+}\NormalTok{ reg, data, }\AttributeTok{Hess =} \ConstantTok{TRUE}\NormalTok{) }\CommentTok{\# model 3}
+
+\NormalTok{coefs\_age }\OtherTok{\textless{}{-}}\NormalTok{ broom}\SpecialCharTok{::}\FunctionTok{tidy}\NormalTok{(true\_model\_age)}\SpecialCharTok{$}\NormalTok{estimate }\CommentTok{\# extract coefficients of model 1}
+\NormalTok{coefs\_wgt }\OtherTok{\textless{}{-}}\NormalTok{ broom}\SpecialCharTok{::}\FunctionTok{tidy}\NormalTok{(true\_model\_wgt)}\SpecialCharTok{$}\NormalTok{estimate }\CommentTok{\# extract coefficients of model 2}
+\NormalTok{coefs\_gen }\OtherTok{\textless{}{-}}\NormalTok{ broom}\SpecialCharTok{::}\FunctionTok{tidy}\NormalTok{(true\_model\_gen)}\SpecialCharTok{$}\NormalTok{estimate }\CommentTok{\# extract coefficients of model 3}
+
+\NormalTok{nsim }\OtherTok{\textless{}{-}} \DecValTok{1000} \CommentTok{\# use 1000 iterations}
+
+\NormalTok{bootstrap\_samples }\OtherTok{\textless{}{-}} 
+\NormalTok{  modelr}\SpecialCharTok{::}\FunctionTok{bootstrap}\NormalTok{(}\AttributeTok{data =}\NormalTok{ data, }\AttributeTok{n =}\NormalTok{ nsim) }\SpecialCharTok{\%$\%} 
+\NormalTok{  strap }\SpecialCharTok{\%\textgreater{}\%} 
+  \FunctionTok{map}\NormalTok{(as\_tibble)}
+
+\NormalTok{post }\OtherTok{\textless{}{-}} \FunctionTok{make.post}\NormalTok{(data)}
+\NormalTok{post[}\StringTok{"bmi"}\NormalTok{] }\OtherTok{\textless{}{-}} \StringTok{"imp[[j]][, i] \textless{}{-} imp[[\textquotesingle{}wgt\textquotesingle{}]][, i] / (imp[[\textquotesingle{}hgt\textquotesingle{}]][, i] / 100)\^{}2"}
+
+\NormalTok{synthetic\_samples }\OtherTok{\textless{}{-}} 
+\NormalTok{  bootstrap\_samples }\SpecialCharTok{\%\textgreater{}\%}
+  \FunctionTok{future\_map}\NormalTok{(}\ControlFlowTok{function}\NormalTok{(x) \{}
+\NormalTok{    x }\SpecialCharTok{\%\textgreater{}\%} \FunctionTok{mice}\NormalTok{(}\AttributeTok{m =} \DecValTok{5}\NormalTok{, }
+               \AttributeTok{maxit =} \DecValTok{1}\NormalTok{,}
+               \AttributeTok{method =} \StringTok{"cart"}\NormalTok{,}
+               \AttributeTok{minbucket =} \DecValTok{3}\NormalTok{,}
+               \AttributeTok{cp =} \FloatTok{1e{-}08}\NormalTok{,}
+               \AttributeTok{predictorMatrix =}\NormalTok{ pred,}
+               \AttributeTok{post =}\NormalTok{ post,}
+               \AttributeTok{where =} \FunctionTok{matrix}\NormalTok{(}\ConstantTok{TRUE}\NormalTok{, }\FunctionTok{nrow}\NormalTok{(data), }\FunctionTok{ncol}\NormalTok{(data)),}
+               \AttributeTok{print =}\NormalTok{ F)}
+\NormalTok{\}, }\AttributeTok{.options =} \FunctionTok{furrr\_options}\NormalTok{(}\AttributeTok{seed =} \FunctionTok{as.integer}\NormalTok{(}\DecValTok{123}\NormalTok{)))}
+\end{Highlighting}
+\end{Shaded}
 

### 2021-10-05 manuscript/Manuscript.Rmd
final draft

@@
     affil: 1,*
-    orcid: 0000-0003-3293-2315
+    orcid: 0000-0002-2408-7820
   - name: Gerko Vink
@@
 appendix: appendix.tex
-simplesummary: |
-  A Simple summary goes here.
 abstract: |
-  A single paragraph of about 200 words maximum. For research articles, 
-  abstracts should give a pertinent overview of the work. We strongly encourage
-  authors to use the following style of structured abstracts, but without 
-  headings: 1) Background: Place the question addressed in a broad context and
-  highlight the purpose of the study; 2) Methods: Describe briefly the main
-  methods or treatments applied; 3) Results: Summarize the article's main 
-  findings; and 4) Conclusion: Indicate the main conclusions or interpretations. 
-  The abstract should be an objective representation of the article, it must not 
-  contain results which are not presented and substantiated in the main text and 
-  should not exaggerate the main conclusions.
+  Synthetic data sets can greatly improve the dissemination of data 
+  and further analysis of private data. Generating and analyzing synthetic data 
+  sets is straightforward, yet adopting a synthetic data analysis pipeline is 
+  often ignored by applied researchers. We outline a simple procedure for 
+  generating and alayzing synthetic data sets with `mice` in `R`. We demonstrate 
+  in simulation that the analysis results obtained on synthetic data 
+  obtained with `mice` yields unbiased and valid inferences, and leads to synthetic 
+  records that cannot be distinguished from the true data records. The ease of use 
+  when synthesizing data with `mice`, together with the validity of inferences 
+  obtained through this procedure opens up a wealth of possibilities for data 
+  dissemination and further research of initially private data. 
 keywords: |
-  keyword 1; keyword 2; keyword 3 (list three to ten pertinent keywords specific 
-  to the article, yet reasonably common within the subject discipline.).
+  mice; imputation; synthetic data.
 acknowledgement: |
-  All sources of funding of the study should be disclosed. Please clearly 
-  indicate grants that you have received in support of your research work. 
-  Clearly state if you received funds for covering the costs to publish in open 
-  access.
+  We are grateful to Mirthe Hendriks and Stijn van den Broek for replicating the 
+  simulation study on an independent data set. 
 authorcontributions: |
-  For research articles with several authors, a short paragraph specifying their 
-  individual contributions must be provided. The following statements should be 
-  used ``X.X. and Y.Y. conceive and designed the experiments; X.X. performed the 
-  experiments; X.X. and Y.Y. analyzed the data; W.W. contributed 
-  reagents/materials/analysis tools; Y.Y. wrote the paper.'' Authorship must be
-  limited to those who have contributed substantially to the work reported.
+  The authors contributed equally to this work.
 conflictsofinterest: |
-  'The authors declare no conflict of interest.' 
+  The authors declare no conflict of interest. 
 sampleavailability: |
-  Samples of the compounds ...... are available from the authors.
-abbreviations:
-  - short: MDPI
-    long: Multidisciplinary Digital Publishing Institute
-  - short: DOAJ
-    long: Directory of open access journals
-  - short: TLA
-    long: Three letter acronym
-  - short: LD 
-    long: linear dichroism
+  A full simulation archive is available from https://github.com/amices/Federated_imputation/tree/master/manuscript.
 output: rticles::mdpi_article
@@
 
-| column | description                |
-|--------|----------------------------|
-| age    | age in years               |
-| hgt    | height (cm)                |
-| wgt    | weight (kg)                |
-| bmi    | body mass index            |
-| hc     | head circumference (cm)    |
-| gen    | genital Tanner stage G1-G5 |
-| phb    | pubic hair Tanner P1-P6    |
-| tv     | testicular volume (ml)     |
-| reg    | region                     |
+\begin{table}[H]
+\caption{Description of the features in the \texttt{mice::boys} data set.}
+\centering
+\begin{tabular}{rl}
+\hline
+column & description                \\ 
+\hline
+age    & age in years               \\ 
+hgt    & height (cm)                \\ 
+wgt    & weight (kg)                \\ 
+bmi    & body mass index            \\ 
+hc     & head circumference (cm)    \\ 
+gen    & genital Tanner stage G1-G5 \\ 
+phb    & pubic hair Tanner P1-P6    \\ 
+tv     & testicular volume (ml)     \\ 
+reg    & region                     \\ 
+\hline
+\end{tabular}
+\end{table}
 
 Unfortunately, this data set does not differ from the vast majority of collected data sets, in the sense that it suffers from missing data.
-For simplicity, the data is completed using the default `mice` imputation model for all predictors except `bmi`, which is passively imputed using its deterministic relation with weight and height.
+For simplicity, we complete the missing values using the default `mice` imputation model for all predictors except `bmi`, which is passively imputed using its deterministic relation with `wgt` and `hgt`.
 
@@
 
-```{r, results = FALSE, message = FALSE, warning = FALSE}
+```{r true-data, results = FALSE, message = FALSE, warning = FALSE, cache = TRUE}
 # create a single imputed, completely observed `boys` data set
@@
 By allowing for more complexity in the imputation model, bias in the estimates from the synthetic data set is reduced.
-Additionally, since the missingness pattern is monotone, the number of iterations can be set to `maxit = 1`.
+Additionally, since the synthesis pattern is monotone, the number of iterations can be set to `maxit = 1`.
 
@@
 $$
-\bar{q}_m = \sum_{l = 1}^m \frac{q^{(l)}}{m}.
+\bar{q}_m = \sum_{l = 1}^m \frac{q^{(l)}}{m},
 $$
@@
 # Results
-```{r, message = FALSE, warning = FALSE, cache = TRUE, cache.lazy = FALSE}
+```{r simulation, message = FALSE, warning = FALSE, cache = TRUE, cache.lazy = FALSE, echo = FALSE}
 plan(multisession) # increase speed through futures
@@
 ```
+We evaluate the synthetic data with respect to the *true* data set on the basis of three aims.
+We believe that every reliable and valid data synthetisation effort in statistical data analysis should be able to yield 1) unbiased univariate statistical properties, 2) unbiased bivariate properties, 3) unbiased and valid multivariate inferences and 4) synthetic data that cannot be distinguished from real data.
+We consider the evaluation of the synthetic data simulations in the above order.
 
-This section may be divided by subheadings.
-It should provide a concise and precise description of the experimental results, their interpretation as well as the experimental conclusions that can be drawn.
+## Univariate estimates
+The univariate descriptives for the original data and the synthetic data can be found in Table 2. 
+```{r univariate-statistics, echo = FALSE, cache = TRUE, results = FALSE}
+library(xtable)
+true <- psych::describe(data)
 
-## Subsection Heading Here
+synth <- synthetic_samples %>% 
+  map(~.x %>% complete("all") %>% 
+        map(~.x %>% describe()) %>% Reduce("+", .) / synthetic_samples[[1]]$m) %>% 
+  Reduce("+", .) / length(synthetic_samples)
+rownames(true) <- paste("original", rownames(true), sep = " ")
+rownames(synth) <- paste("synthetic", rownames(synth), sep = " ")
 
-Subsection text here.
+bind_rows(true, setNames(synth, names(true))) %>% 
+           arrange(vars) %>% .[, c(2:5, 8:9, 11:12)] %>% round(3) %>% 
+  xtable
+```
+<!-- % latex table generated in R 4.1.0 by xtable 1.8-4 package -->
+<!-- % Mon Oct  4 16:47:59 2021 -->
+\begin{table}[ht]
+\caption{Univariate descriptives for the true data and $m=5$ pooled univariate descriptives for the synthetic data over 1000 simulations.}
+\centering
+\begin{tabular}{rrrrrrrrr}
+  \hline
+ & n & mean & sd & median & min & max & skew & kurtosis \\ 
+  \hline
+original age & 748 & 9.16 & 6.89 & 10.50 & 0.04 & 21.18 & -0.03 & -1.56 \\ 
+  synthetic age & 748 & 9.15 & 6.89 & 10.49 & 0.04 & 20.96 & -0.03 & -1.55 \\ 
+  original hgt & 748 & 131.10 & 46.52 & 145.75 & 50.00 & 198.00 & -0.30 & -1.47 \\ 
+  synthetic hgt & 748 & 131.06 & 46.50 & 145.32 & 50.69 & 197.16 & -0.30 & -1.47 \\ 
+  original wgt & 748 & 37.12 & 26.03 & 34.55 & 3.14 & 117.40 & 0.38 & -1.03 \\ 
+  synthetic wgt & 748 & 37.09 & 26.00 & 34.44 & 3.35 & 112.26 & 0.38 & -1.03 \\ 
+  original bmi & 748 & 18.04 & 3.04 & 17.45 & 11.73 & 31.74 & 1.14 & 1.79 \\ 
+  synthetic bmi & 748 & 18.05 & 3.08 & 17.48 & 11.49 & 32.37 & 1.11 & 1.85 \\ 
+  original hc & 748 & 51.62 & 5.86 & 53.10 & 33.70 & 65.00 & -0.91 & 0.12 \\ 
+  synthetic hc & 748 & 51.61 & 5.86 & 53.18 & 34.38 & 62.85 & -0.91 & 0.12 \\ 
+  original gen* & 748 & 2.53 & 1.59 & 2.00 & 1.00 & 5.00 & 0.52 & -1.36 \\ 
+  synthetic gen* & 748 & 2.53 & 1.59 & 2.00 & 1.00 & 5.00 & 0.52 & -1.35 \\ 
+  original phb* & 748 & 2.75 & 1.86 & 2.00 & 1.00 & 6.00 & 0.56 & -1.25 \\ 
+  synthetic phb* & 748 & 2.75 & 1.86 & 2.00 & 1.00 & 6.00 & 0.56 & -1.24 \\ 
+  original tv & 748 & 8.43 & 8.12 & 3.00 & 1.00 & 25.00 & 0.85 & -0.78 \\ 
+  synthetic tv & 748 & 8.42 & 8.11 & 3.19 & 1.00 & 25.00 & 0.85 & -0.77 \\ 
+  original reg* & 748 & 3.02 & 1.14 & 3.00 & 1.00 & 5.00 & -0.08 & -0.77 \\ 
+  synthetic reg* & 748 & 3.02 & 1.14 & 3.00 & 1.00 & 5.00 & -0.08 & -0.76 \\ 
+   \hline
+\end{tabular}
+\end{table}
+We see from Table 1 that the synthetic data estimates closely resemble the true data estimates.
 
-### Subsubsection Heading Here
+## Bivariate estimates
+An often used bivariate statistic is Pearson's correlation coefficient.
+When evaluating this correlation coefficient on the numeric columns in the `boys` data set, we find that biases are very small.
+The results are displayed in Table 3.
+```{r bivariate-statistics, echo = FALSE, cache = TRUE, results = FALSE}
+true <- data %>% select(-gen, -phb, -reg) %>% cor
 
-Bulleted lists look like this:
+fisher.trans <- function(x) 1/2 * log((1 + x) / (1 - x))
+fisher.backtrans <- function(x) (exp(2 * x) - 1) / (exp(2 * x) + 1)
+retrieve.cor <- function(mids){
+  out <- mids %>%
+  mice::complete("all") %>%
+  map(select, -phb, -gen, -reg) %>%  
+  map(stats::cor) %>%
+  map(fisher.trans) %>% 
+    Reduce("+", .) / mids$m
+  out %<>%   fisher.backtrans()
+  diag(out) <- 1
+  return(out)
+}
 
-* First bullet
-* Second bullet
-* Third bullet
+synth <- synthetic_samples %>%
+  map(~.x %>% retrieve.cor) %>%
+  Reduce("+", .) / length(synthetic_samples)
 
-Numbered lists can be added as follows:
+corbias <- apply(cbind(round(c(true), 3), round(c(true - synth), 3)), 1, function(x) paste(x[1], " (", x[2], ")", sep = "" )) %>% 
+  matrix(6, 6)
+diag(corbias) <- 1
+dimnames(corbias) <- dimnames(true)
+true - synth
+xtable(corbias)
+```
+<!-- % latex table generated in R 4.1.0 by xtable 1.8-4 package -->
+<!-- % Mon Oct  4 17:57:32 2021 -->
+\begin{table}[H]
+\caption{Bivariate correlations of the numerical columns in the true data with in parentheses the corresponding bias of the $m=5$ pooled synthetic correlations over 1000 simulations.
+All estimates are rounded to 3 decimal places.
+}
+\centering
+\begin{tabular}{rcccccc}
+  \hline
+ & age & hgt & wgt & bmi & hc & tv \\ 
+  \hline
+age & 1 & 0.976 (0.001) & 0.950 (0.000) & 0.627 (0.009) & 0.853 (0.000) & 0.810 (0.002) \\ 
+  hgt & 0.976 (0.001) & 1 & 0.944 (0.001) & 0.596 (0.013) & 0.907 (0.000) & 0.754 (0.000) \\ 
+  wgt & 0.950 (0.000) & 0.944 (0.001) & 1 & 0.791 (0.009) & 0.834 (0.000) & 0.817 (0.000) \\ 
+  bmi & 0.627 (0.009) & 0.596 (0.013) & 0.791 (0.009) & 1 & 0.588 (0.009) & 0.610 (0.007) \\ 
+  hc & 0.853 (0.000) & 0.907 (0.000) & 0.834 (0.000) & 0.588 (0.009) & 1 & 0.623 (0.000) \\ 
+  tv & 0.810 (0.002) & 0.754 (0.000) & 0.817 (0.000) & 0.610 (0.007) & 0.623 (0.000) & 1 \\ 
+   \hline
+\end{tabular}
+\end{table}
+We see that the correlations obtained from synthetic data are unbiased with respect to the true data set.
 
-1. First item
-2. Second item
-3. Third item
+## Multivariate model inferences
 
-The text continues here.
+```{r multiv_model1, cache = TRUE, echo = FALSE, results=FALSE}
+# true data estimate
+true <- data %$% lm(hgt ~ age + phb) %>% coef()
 
-All figures and tables should be cited in the main text as Figure 1, Table 1, etc.
+# bootstrap coverage
+boot <- bootstrap_samples %>% 
+  map(~.x %$% 
+        lm(hgt ~ age + phb) %>% 
+        broom::tidy(conf.int = TRUE) %>% 
+        mutate(boot.cov = conf.low < true & true < conf.high,
+               true = true, 
+               boot.bias = estimate - true) %>% 
+        column_to_rownames("term")) %>% 
+  Reduce("+", .) / length(bootstrap_samples)
 
-\begin{figure}[H]
+# bootstrap coverage
+synth <- synthetic_samples %>%
+  map(~.x %>% 
+        with(lm(hgt ~ age + phb)) %>% 
+        mice:::pool.syn() %>% 
+        summary(conf.int = TRUE) %>% 
+        mutate(synth.cov = `2.5 %` < true & true < `97.5 %`,
+               true = true, 
+               synth.bias = estimate - true) %>% 
+        column_to_rownames("term")) %>% 
+  Reduce("+", .) / length(synthetic_samples)
+
+cbind(boot %>% select(true, boot.bias, boot.cov),
+      synth %>% select(synth.bias, synth.cov)) %>% xtable(digits = 3)
+```
+First, we evaluate the performance of our synthetic simulation set on a linear model where `hgt` is modeled by a continuous predictor `age` and an ordered categorical predictor `phb`.
+The results for this simulation can be found in Table 4.
+
+\begin{table}[ht]
+\caption{Simulation results for a linear regression model with continuous and ordered categorical predictors.
+The model evaluated is `hgt ~ age + phb`.
+Depicted are the true data estimate and the bias from the true data estimate and the coverage rate of the 95\% confidence interval for the bootstrap and synthetic data sets.}
 \centering
-\includegraphics[width=3 cm]{logo-mdpi}
-\caption{This is a figure, Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.}
-\end{figure}
-
-\begin{table}[H]
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
-\centering
-%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
-\begin{tabular}{ccc}
-\toprule
-\textbf{Title 1}	& \textbf{Title 2}	& \textbf{Title 3}\\
-\midrule
-entry 1		& data			& data\\
-entry 2		& data			& data\\
-\bottomrule
+\begin{tabular}{rrrrrr}
+  \hline
+  & & \multicolumn{2}{c}{Bootstrap} & \multicolumn{2}{c}{Synthetic}\\
+ term & estimate & bias & cov & bias & cov \\ 
+  \hline
+(Intercept) & 63.087 & -0.001 & 0.970 & 0.405 & 0.958 \\ 
+  age & 7.174 & 0.000 & 0.958 & -0.033 & 0.947 \\ 
+  phb.L & -12.250 & 0.008 & 0.950 & 0.582 & 0.927 \\ 
+  phb.Q & -1.376 & -0.022 & 0.926 & 0.112 & 0.934 \\ 
+  phb.C & -3.564 & 0.051 & 0.915 & 0.301 & 0.912 \\ 
+  phb\verb|^|4 & -0.431 & 0.016 & 0.930 & 0.106 & 0.940 \\ 
+  phb\verb|^|5 & 2.064 & 0.060 & 0.941 & 0.077 & 0.943 \\ 
+   \hline
 \end{tabular}
@@
 
-This is an example of an equation:
+We see that the finite nature of the true data set together with the design-based simulation setup yields slight undercoverage for the polynomial functions.
+This finding is observed in both the bootstrap coverages (i.e.
+the fraction of 95% confidence intervals that cover the true data parameters) and the synthetic data coverages, indicating that the undercoverage stems from the simulation setup.
 
-\begin{equation}
-\mathbb{S}
-\end{equation}
-<!-- If the documentclass option "submit" is chosen, please insert a blank line before and after any math environment (equation and eqnarray environments).
-This ensures correct linenumbering.
-The blank line should be removed when the documentclass option is changed to "accept" because the text following an equation should not be a new paragraph.
--->
+Second, we evaluate a proportional odds logistic regression model wherein ordered categorical column `gen` is modeled by continuous predictors `age` and `hc`, and categorical predictor `reg`.
+The results for this model evaluation are shown in Table 5.
 
-<!-- Please punctuate equations as regular text. Theorem-type environments (including propositions, lemmas, corollaries etc.) can be formatted as follows: -->
-Example of a theorem:
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
+```{r multiv_model2, cache = TRUE, echo = FALSE, results=FALSE}
+# true data estimate
+true <- data %$% MASS::polr(gen ~ age + hc + reg, Hess = TRUE) %>% broom::tidy(conf.int = TRUE) %>% column_to_rownames("term") %>% select(estimate)
 
-The text continues here. Proofs must be formatted as follows:
+# bootstrap coverage
+boot <- bootstrap_samples %>% 
+  map(~.x %$% 
+        MASS::polr(gen ~ age + hc + reg, Hess = TRUE) %>% 
+        broom::tidy(conf.int = TRUE) %>% 
+        mutate(true = true$estimate, 
+               boot.cov = conf.low < true & true < conf.high,
+               boot.cov2 = (estimate - 1.96*std.error) < true & true < (estimate + 1.96 * std.error), 
+               boot.bias = estimate - true) %>% 
+        select(-coef.type) %>% 
+        column_to_rownames("term")) %>% 
+  Reduce("+", .) / length(bootstrap_samples)
 
-Example of a proof:
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
-\end{proof}
-The text continues here.
+# synthetic coverage
+synth <- synthetic_samples %>%
+  map(~.x %>% 
+        with(MASS::polr(gen ~ age + hc + reg, Hess = TRUE)) %>% 
+        mice:::pool.syn() %>% 
+        summary(conf.int = TRUE) %>% 
+        mutate(true = true$estimate, 
+               synth.cov = `2.5 %` < true & true < `97.5 %`,
+               synth.bias = estimate - true) %>% 
+        column_to_rownames("term")) %>% 
+  Reduce("+", .) / length(synthetic_samples)
+
+cbind(boot %>% select(true, boot.bias, boot.cov),
+      synth %>% select(synth.bias, synth.cov)) %>% xtable(digits = 3)
+```
+```{r echo = FALSE, results=FALSE}
+library(xtable)
+cbind(boot %>% select(true, boot.bias, boot.cov2),
+      synth %>% select(synth.bias, synth.cov)) %>% xtable(digits = 3)
+```
+
+<!-- % latex table generated in R 4.1.0 by xtable 1.8-4 packag -->
+<!-- % Mon Oct  4 23:32:01 2021 -->
+\begin{table}[H]
+\caption{Simulation results for a proportional odds logistic regression model with continuous and ordered categorical predictors.
+The model evaluated is `gen ~ age + hc + reg`.
+Depicted are the true data estimate and the bias from the true data estimate and the coverage rate of the 95\% confidence interval for the bootstrap and synthetic data sets.}
+\centering
+\begin{tabular}{rrrrrr}
+  \hline
+ & & \multicolumn{2}{c}{Bootstrap} & \multicolumn{2}{c}{Synthetic}\\
+ term & estimate & bias & cov & bias & cov \\ 
+  \hline
+  age & 0.461 & 0.004 & 0.942 & 0.002 & 0.939 \\
+  hc & -0.188 & -0.000 & 0.929 & -0.004 & 0.945 \\
+  regeast & -0.339 & 0.012 & 0.960 & 0.092 & 0.957\\
+  regwest & 0.486 & 0.009 & 0.952 & -0.122 & 0.944\\
+  regsouth & 0.646 & 0.012 & 0.966 & -0.152 & 0.943 \\
+  regcity & -0.069 & 0.012 & 0.940 & 0.001 & 0.972 \\
+  G1$|$G2 & -6.322 & 0.032 & 0.934 & -0.254 & 0.946 \\
+  G2$|$G3 & -4.501 & 0.052 & 0.936 & -0.246 & 0.945 \\
+  G3$|$G4 & -3.842 & 0.058 & 0.937 & -0.244 & 0.948 \\
+  G4$|$G5 & -2.639 & 0.064 & 0.936 & -0.253 & 0.947 \\
+   \hline
+\end{tabular}
+\end{table}
+These results demonstrate that the synthetic data analysis yields valid inferences with low bias.
+
+## Data discrimination
+When we combine the original and synthetic data, can we predict which rows come from the synthetic data set?
+If so, then our synthetic data procedure would be redundant, since the synthetic set differs from the observed set.
+To evaluate whether we can distinguish between the true data and the synthetic data, we combine the rows from each simulation synthetic data set with the rows from the true data.
+We then run a logistic regression model to predict group membership: i.e.
+does a row belong to the true data or synthetic data.
+As predictors we take all columns in the data.
+The pooled parameter estimates over all simulations can be found in Table 6.
+
+```{r discriminate, cache = TRUE, results=FALSE, echo = FALSE}
+out <- synthetic_samples %>%
+  map(~.x %>% 
+        complete("all") %>%  
+        map(~.x %>% 
+              rbind(data) %>% 
+              mutate(indic = as.factor(c(rep(0, 748), rep(1, 748)))) %$% 
+              glm(indic ~ wgt + hgt + age + hc + gen + phb + tv + reg + bmi, family=binomial(link = "logit"))) %>% 
+        pool() %>%  
+        summary() %>% 
+        column_to_rownames("term")) %>% 
+  Reduce("+", .) / length(synthetic_samples)
+
+out %>% xtable
+
+library(caret)
+do_fun <- function(x){
+  dat <- x %>% 
+    rbind(data) %>% 
+    mutate(indic = as.factor(c(rep(0, 748), rep(1, 748))))
+  fit <- dat %$% 
+    glm(indic ~ wgt + hgt + age + hc + gen + phb + tv + reg + bmi, family=binomial(link = "logit")) %>% 
+    predict(type = "response") %>% rbinom(1496, 1, prob = .)
+  CM <- confusionMatrix(factor(fit), factor(dat$indic))
+  c(CM$overall, CM$byClass)
+}
+out2 <- synthetic_samples %>%
+  map(~.x %>% 
+        complete("all") %>%  
+        map(~.x %>% do_fun()) %>% 
+        do.call("rbind", .) %>% colMeans()) %>% 
+  do.call("rbind", .) %>% colMeans() %>% .[c(1, 18, 2,  7, 8, 9, 15)]
+```
+```{r echo = FALSE, results=FALSE}
+library(xtable)
+out2 %>% as.matrix() %>% xtable(digits = 5)
+```
+
+<!-- % latex table generated in R 4.1.0 by xtable 1.8-4 package -->
+<!-- % Tue Oct  5 02:25:08 2021 -->
+\begin{table}[H]
+\caption{Simulation results for a logistic regression model aimed at discriminating between synthetic records and true records.}
+\centering
+\begin{tabular}{rrrrrr}
+  \hline
+ term & estimate & std.error & statistic & df & p.value \\
+  \hline
+  (Intercept) & 0.22 & 1.15 & 0.19 & 521.93 & 0.60 \\ 
+  wgt & 0.00 & 0.02 & 0.25 & 420.19 & 0.60 \\
+  hgt & -0.00 & 0.01 & -0.18 & 359.73 & 0.60 \\
+  age & -0.00 & 0.05 & -0.00 & 345.73 & 0.62 \\ 
+  hc & 0.00 & 0.03 & 0.11 & 415.44 & 0.61\\
+  gen.L & -0.00 & 0.42 & -0.00 & 164.76 & 0.65 \\
+  gen.Q & -0.01 & 0.21 & -0.04 & 203.38 & 0.63 \\
+  gen.C & -0.00 & 0.16 & -0.02 & 239.63 & 0.64 \\
+  gen\verb|^|4 & 0.01 & 0.21 & 0.01 & 237.41 & 0.63 \\
+  phb.L & -0.02 & 0.44 & -0.04 & 156.54 & 0.64 \\
+  phb.Q & -0.01 & 0.22 & -0.02 & 198.20 & 0.64 \\
+  phb.C & 0.00 & 0.18 & 0.00 & 211.17 & 0.62 \\
+  phb\verb|^|4 & 0.00 & 0.18 & 0.02 & 228.51 & 0.64\\
+  phb\verb|^|5 & 0.00 & 0.20 & 0.02 & 248.57 & 0.63\\
+  tv & 0.00 & 0.02 & 0.01 & 264.26 & 0.63\\
+  regeast & -0.00 & 0.23 & 0.01 & 210.90 & 0.64 \\ 
+  regwest & -0.00 & 0.22 & -0.00 & 221.14 & 0.63 \\ 
+  regsouth & -0.01 & 0.22 & -0.02 & 226.10 & 0.64 \\ 
+  regcity & 0.01 & 0.27 & 0.03 & 204.15 & 0.64 \\ 
+  bmi & -0.02 & 0.06 & -0.26 & 320.18 & 0.61 \\
+   \hline
+\end{tabular}
+\end{table}
+
+From these pooled results we can see that the effects for all predictors are close to zero and non-significant.
+When we take the predicted values from the simulated models and compare them with the *real* values, we obtain the summary statistics in Table 7.
+
+\begin{table}[H]
+\caption{Confusion statistics for a prediction model aimed at discriminating between synthetic records and true records.}
+\centering
+\begin{tabular}{rr}
+  \hline
+& estimate\\
+  \hline
+ Accuracy & 0.50381 \\
+ Balanced Accuracy & 0.50381 \\
+ Kappa & 0.00762 \\
+ McnemarPValue & 0.63187 \\
+ Sensitivity & 0.50368 \\
+ Specificity & 0.50394 \\
+ Prevalence & 0.50000 \\
+   \hline
+\end{tabular}
+\end{table}
+
+The accuracy of the predictive modeling effort is not better than random selection and the Kappa coefficient indicates that a perfect prediction model is far from realized.
+The accuracy is quite balanced as there is no skewness over sensitivity and specificity.
+These findings indicate that the synthetic data is indistinguishable from the true data.
 
@@
 
-Authors should discuss the results and how they can be interpreted in perspective of previous studies and of the working hypotheses.
-The findings and their implications should be discussed in the broadest context possible.
-Future research directions may also be highlighted.
+We demonstrate that generating synthetic data sets with `mice` in `R` is a straightforward process that fits well in a data analysis pipeline.
+The multiple synthetic sets yield valid inferences about the true underlying data generating mechanism, thereby capturing the nature of the original data.
+This makes the multiple synthetisation procedure with `mice` suitable for further dissemination of synthetic data sets.
 
-# Conclusion
+To non-statisticians, the procedure of generating multiple synthetic sets may seem overly complicated.
+We would like to emphasize that analyzing a single synthesized set, while perhaps unbiased, would underestimate the variance properties that are so important in drawing statistical inferences from finite data sets.
+After all, we are often not interested in the sample at hand, but in the underlying data generating mechanism, such as the population.
+Properly capturing the uncertainty of synthetic data sets, just like with incomplete data sets, is therefore paramount.
 
-This section is not mandatory, but can be added to the manuscript if the discussion is unusually long or complex.
+Analyzing multiple synthetic sets has another clear benefit over analyzing just a single synthesized data set: the risk for data disclosure is much lower.
+Instead of having just one synthetic realization, a set of multiple synthetic values that could have been are generated from the posterior predictive distribution.
+This means that both properties that might belong to individual participants, as well as properties that might not belong to those participants can be introduced in the synthetic values.
+Because we are not interested in the individual data sets, but rather in the inference obtained over the multiple data sets, the likelihood of data properties distributed over participants is aggregated to represent the true data generating model.
 
-# Patents
+That said, while the fields of data disclosure control and data synthetisation originated decades ago, it is more relevant today than ever.
+In our study we outline a standard research workflow where the goal is to synthesize a complete data set.
+To simplify the simulation we adopted a bootstrapping scheme to induce sampling variance in order to conform to the combination procedure defined by @reiter_partially_inference_2003.
+Ideally, one would like to omit the bootstrap from the synthetization to adopt a scheme where the sampled data itself serves as a reference: much like the procedure outlined in @vink2014pooling for incomplete data simulation.
+The corresponding pooling rules have not been derived yet and the incorporation in data analysis workflows would require proper attention from developers alike.
 
-This section is not mandatory, but may be added if there are patents resulting from the work reported in this manuscript.
+It is important to note that in our simulations we used a single iteration.
+A single iteration is sufficient only when the true data is completely observed [IBRAHIM ref needed].
+If both observed and unobserved values are to be synthesized, then more iterations and a careful investigation into the convergence of the algorithm are in order.
+Synthetic data generation with `mice` is therein no different than multiple imputation with `mice`.
+
+There are other developments that can generate synthetic data sets.
+For example, the `synthpop` @synthpop package in `R` would yield valid synthetic data sets, but requires the true data to be completely observed.
+To avoid this, one could adopt a two-step approach wherein the incomplete values are multiply imputed before synthetization.
+Given $m$ multiple imputations and synthetizations, at least $m^2$ synthetic data sets are then in order.
+The flexibility with `mice` is that both unobserved and observed data values can be synthesized at once, without the need for a two-step approach.
+With `mice` $m$ synthetic sets are sufficient.
+
+The ease of use when synthesizing data with `mice` in `R`, together with the validity of inferences obtained through this procedure opens up a wealth of possibilities for data dissemination and further research of initially private data.

### 2021-10-05 manuscript/Manuscript.tex
final draft

--- 2021-10-04 manuscript/Manuscript.tex
@@
 \Author{Thom
-Volker$^{1,*}$\href{https://orcid.org/0000-0003-3293-2315}{\orcidicon}, Gerko
+Volker$^{1,*}$\href{https://orcid.org/0000-0002-2408-7820}{\orcidicon}, Gerko
 Vink$^{1,
@@
 % Simple summary
-\simplesumm{A Simple summary goes here.}
 
 % Abstract (Do not insert blank lines, i.e. \\)
-\abstract{A single paragraph of about 200 words maximum. For research
-articles, abstracts should give a pertinent overview of the work. We
-strongly encourage authors to use the following style of structured
-abstracts, but without headings: 1) Background: Place the question
-addressed in a broad context and highlight the purpose of the study; 2)
-Methods: Describe briefly the main methods or treatments applied; 3)
-Results: Summarize the article's main findings; and 4) Conclusion:
-Indicate the main conclusions or interpretations. The abstract should be
-an objective representation of the article, it must not contain results
-which are not presented and substantiated in the main text and should
-not exaggerate the main conclusions.}
+\abstract{Synthetic data sets can greatly improve the dissemination of
+data and further analysis of private data. Generating and analyzing
+synthetic data sets is straightforward, yet adopting a synthetic data
+analysis pipeline is often ignored by applied researchers. We outline a
+simple procedure for generating and alayzing synthetic data sets with
+\texttt{mice} in \texttt{R}. We demonstrate in simulation that the
+analysis results obtained on synthetic data obtained with \texttt{mice}
+yields unbiased and valid inferences, and leads to synthetic records
+that cannot be distinguished from the true data records. The ease of use
+when synthesizing data with \texttt{mice}, together with the validity of
+inferences obtained through this procedure opens up a wealth of
+possibilities for data dissemination and further research of initially
+private data.}
 
 % Keywords
-\keyword{keyword 1; keyword 2; keyword 3 (list three to ten pertinent
-keywords specific to the article, yet reasonably common within the
-subject discipline.).}
+\keyword{mice; imputation; synthetic data.}
 
@@
 
-\begin{longtable}[]{@{}ll@{}}
-\toprule
+\begin{table}[H]
+\caption{Description of the features in the \texttt{mice::boys} data set.}
+\centering
+\begin{tabular}{rl}
+\hline
 column & description                \\ 
-\midrule
-\endhead
+\hline
 age    & age in years               \\ 
@@
 reg    & region                     \\ 
-\bottomrule
-\end{longtable}
+\hline
+\end{tabular}
+\end{table}
 
@@
 collected data sets, in the sense that it suffers from missing data. For
-simplicity, the data is completed using the default \texttt{mice}
-imputation model for all predictors except \texttt{bmi}, which is
-passively imputed using its deterministic relation with weight and
-height.
+simplicity, we complete the missing values using the default
+\texttt{mice} imputation model for all predictors except \texttt{bmi},
+which is passively imputed using its deterministic relation with
+\texttt{wgt} and \texttt{hgt}.
 
@@
 model, bias in the estimates from the synthetic data set is reduced.
-Additionally, since the missingness pattern is monotone, the number of
+Additionally, since the synthesis pattern is monotone, the number of
 iterations can be set to \texttt{maxit\ =\ 1}.
@@
 average of the \(m\) point estimates \(q^{(l)}\) \[
-\bar{q}_m = \sum_{l = 1}^m \frac{q^{(l)}}{m}.
+\bar{q}_m = \sum_{l = 1}^m \frac{q^{(l)}}{m},
 \] with \(l = 1, \dots, m\).
@@
 
-This section may be divided by subheadings. It should provide a concise
-and precise description of the experimental results, their
-interpretation as well as the experimental conclusions that can be
-drawn.
+We evaluate the synthetic data with respect to the \emph{true} data set
+on the basis of three aims. We believe that every reliable and valid
+data synthetisation effort in statistical data analysis should be able
+to yield 1) unbiased univariate statistical properties, 2) unbiased
+bivariate properties, 3) unbiased and valid multivariate inferences and
+4) synthetic data that cannot be distinguished from real data. We
+consider the evaluation of the synthetic data simulations in the above
+order.
 
-\hypertarget{subsection-heading-here}{%
-\subsection{Subsection Heading Here}\label{subsection-heading-here}}
+\hypertarget{univariate-estimates}{%
+\subsection{Univariate estimates}\label{univariate-estimates}}
 
-Subsection text here.
+The univariate descriptives for the original data and the synthetic data
+can be found in Table 2.
 
-\hypertarget{subsubsection-heading-here}{%
-\subsubsection{Subsubsection Heading
-Here}\label{subsubsection-heading-here}}
-
-Bulleted lists look like this:
-
-\begin{itemize}
-\tightlist
-\item
-  First bullet
-\item
-  Second bullet
-\item
-  Third bullet
-\end{itemize}
-
-Numbered lists can be added as follows:
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  First item
-\item
-  Second item
-\item
-  Third item
-\end{enumerate}
-
-The text continues here.
-
-All figures and tables should be cited in the main text as Figure 1,
-Table 1, etc.
-
-\begin{figure}[H]
+\begin{table}[ht]
+\caption{Univariate descriptives for the true data and $m=5$ pooled univariate descriptives for the synthetic data over 1000 simulations.}
 \centering
-\includegraphics[width=3 cm]{logo-mdpi}
-\caption{This is a figure, Schemes follow the same formatting.
-If there are multiple panels, they should be listed as: (\textbf{a}) Description of what is contained in the first panel.
-(\textbf{b}) Description of what is contained in the second panel.
-Figures should be placed in the main text near to the first time they are cited.
-A caption on a single line should be centered.}
-\end{figure}
-
-\begin{table}[H]
-\caption{This is a table caption. Tables should be placed in the main text near to the first time they are cited.}
-\centering
-%% \tablesize{} %% You can specify the fontsize here, e.g.  \tablesize{\footnotesize}. If commented out \small will be used.
-\begin{tabular}{ccc}
-\toprule
-\textbf{Title 1}    & \textbf{Title 2}  & \textbf{Title 3}\\
-\midrule
-entry 1     & data          & data\\
-entry 2     & data          & data\\
-\bottomrule
+\begin{tabular}{rrrrrrrrr}
+  \hline
+ & n & mean & sd & median & min & max & skew & kurtosis \\ 
+  \hline
+original age & 748 & 9.16 & 6.89 & 10.50 & 0.04 & 21.18 & -0.03 & -1.56 \\ 
+  synthetic age & 748 & 9.15 & 6.89 & 10.49 & 0.04 & 20.96 & -0.03 & -1.55 \\ 
+  original hgt & 748 & 131.10 & 46.52 & 145.75 & 50.00 & 198.00 & -0.30 & -1.47 \\ 
+  synthetic hgt & 748 & 131.06 & 46.50 & 145.32 & 50.69 & 197.16 & -0.30 & -1.47 \\ 
+  original wgt & 748 & 37.12 & 26.03 & 34.55 & 3.14 & 117.40 & 0.38 & -1.03 \\ 
+  synthetic wgt & 748 & 37.09 & 26.00 & 34.44 & 3.35 & 112.26 & 0.38 & -1.03 \\ 
+  original bmi & 748 & 18.04 & 3.04 & 17.45 & 11.73 & 31.74 & 1.14 & 1.79 \\ 
+  synthetic bmi & 748 & 18.05 & 3.08 & 17.48 & 11.49 & 32.37 & 1.11 & 1.85 \\ 
+  original hc & 748 & 51.62 & 5.86 & 53.10 & 33.70 & 65.00 & -0.91 & 0.12 \\ 
+  synthetic hc & 748 & 51.61 & 5.86 & 53.18 & 34.38 & 62.85 & -0.91 & 0.12 \\ 
+  original gen* & 748 & 2.53 & 1.59 & 2.00 & 1.00 & 5.00 & 0.52 & -1.36 \\ 
+  synthetic gen* & 748 & 2.53 & 1.59 & 2.00 & 1.00 & 5.00 & 0.52 & -1.35 \\ 
+  original phb* & 748 & 2.75 & 1.86 & 2.00 & 1.00 & 6.00 & 0.56 & -1.25 \\ 
+  synthetic phb* & 748 & 2.75 & 1.86 & 2.00 & 1.00 & 6.00 & 0.56 & -1.24 \\ 
+  original tv & 748 & 8.43 & 8.12 & 3.00 & 1.00 & 25.00 & 0.85 & -0.78 \\ 
+  synthetic tv & 748 & 8.42 & 8.11 & 3.19 & 1.00 & 25.00 & 0.85 & -0.77 \\ 
+  original reg* & 748 & 3.02 & 1.14 & 3.00 & 1.00 & 5.00 & -0.08 & -0.77 \\ 
+  synthetic reg* & 748 & 3.02 & 1.14 & 3.00 & 1.00 & 5.00 & -0.08 & -0.76 \\ 
+   \hline
 \end{tabular}
@@
 
-This is an example of an equation:
+We see from Table 1 that the synthetic data estimates closely resemble
+the true data estimates.
 
-\begin{equation}
-\mathbb{S}
-\end{equation}
+\hypertarget{bivariate-estimates}{%
+\subsection{Bivariate estimates}\label{bivariate-estimates}}
 
-Example of a theorem:
+An often used bivariate statistic is Pearson's correlation coefficient.
+When evaluating this correlation coefficient on the numeric columns in
+the \texttt{boys} data set, we find that biases are very small. The
+results are displayed in Table 3.
 
-\begin{Theorem}
-Example text of a theorem.
-\end{Theorem}
+\begin{table}[H]
+\caption{Bivariate correlations of the numerical columns in the true data with in parentheses the corresponding bias of the $m=5$ pooled synthetic correlations over 1000 simulations.
+All estimates are rounded to 3 decimal places.
+}
+\centering
+\begin{tabular}{rcccccc}
+  \hline
+ & age & hgt & wgt & bmi & hc & tv \\ 
+  \hline
+age & 1 & 0.976 (0.001) & 0.950 (0.000) & 0.627 (0.009) & 0.853 (0.000) & 0.810 (0.002) \\ 
+  hgt & 0.976 (0.001) & 1 & 0.944 (0.001) & 0.596 (0.013) & 0.907 (0.000) & 0.754 (0.000) \\ 
+  wgt & 0.950 (0.000) & 0.944 (0.001) & 1 & 0.791 (0.009) & 0.834 (0.000) & 0.817 (0.000) \\ 
+  bmi & 0.627 (0.009) & 0.596 (0.013) & 0.791 (0.009) & 1 & 0.588 (0.009) & 0.610 (0.007) \\ 
+  hc & 0.853 (0.000) & 0.907 (0.000) & 0.834 (0.000) & 0.588 (0.009) & 1 & 0.623 (0.000) \\ 
+  tv & 0.810 (0.002) & 0.754 (0.000) & 0.817 (0.000) & 0.610 (0.007) & 0.623 (0.000) & 1 \\ 
+   \hline
+\end{tabular}
+\end{table}
 
-The text continues here. Proofs must be formatted as follows:
+We see that the correlations obtained from synthetic data are unbiased
+with respect to the true data set.
 
-Example of a proof:
+\hypertarget{multivariate-model-inferences}{%
+\subsection{Multivariate model
+inferences}\label{multivariate-model-inferences}}
 
-\begin{proof}[Proof of Theorem 1]
-Text of the proof. Note that the phrase `of Theorem 1' is optional if it is clear which theorem is being referred to.
-\end{proof}
+First, we evaluate the performance of our synthetic simulation set on a
+linear model where \texttt{hgt} is modeled by a continuous predictor
+\texttt{age} and an ordered categorical predictor \texttt{phb}. The
+results for this simulation can be found in Table 4.
 
-The text continues here.
+\begin{table}[ht]
+\caption{Simulation results for a linear regression model with continuous and ordered categorical predictors.
+The model evaluated is `hgt ~ age + phb`.
+Depicted are the true data estimate and the bias from the true data estimate and the coverage rate of the 95\% confidence interval for the bootstrap and synthetic data sets.}
+\centering
+\begin{tabular}{rrrrrr}
+  \hline
+  & & \multicolumn{2}{c}{Bootstrap} & \multicolumn{2}{c}{Synthetic}\\
+ term & estimate & bias & cov & bias & cov \\ 
+  \hline
+(Intercept) & 63.087 & -0.001 & 0.970 & 0.405 & 0.958 \\ 
+  age & 7.174 & 0.000 & 0.958 & -0.033 & 0.947 \\ 
+  phb.L & -12.250 & 0.008 & 0.950 & 0.582 & 0.927 \\ 
+  phb.Q & -1.376 & -0.022 & 0.926 & 0.112 & 0.934 \\ 
+  phb.C & -3.564 & 0.051 & 0.915 & 0.301 & 0.912 \\ 
+  phb\verb|^|4 & -0.431 & 0.016 & 0.930 & 0.106 & 0.940 \\ 
+  phb\verb|^|5 & 2.064 & 0.060 & 0.941 & 0.077 & 0.943 \\ 
+   \hline
+\end{tabular}
+\end{table}
+
+We see that the finite nature of the true data set together with the
+design-based simulation setup yields slight undercoverage for the
+polynomial functions. This finding is observed in both the bootstrap
+coverages (i.e.~the fraction of 95\% confidence intervals that cover the
+true data parameters) and the synthetic data coverages, indicating that
+the undercoverage stems from the simulation setup.
+
+Second, we evaluate a proportional odds logistic regression model
+wherein ordered categorical column \texttt{gen} is modeled by continuous
+predictors \texttt{age} and \texttt{hc}, and categorical predictor
+\texttt{reg}. The results for this model evaluation are shown in Table
+5.
+
+\begin{table}[H]
+\caption{Simulation results for a proportional odds logistic regression model with continuous and ordered categorical predictors.
+The model evaluated is `gen ~ age + hc + reg`.
+Depicted are the true data estimate and the bias from the true data estimate and the coverage rate of the 95\% confidence interval for the bootstrap and synthetic data sets.}
+\centering
+\begin{tabular}{rrrrrr}
+  \hline
+ & & \multicolumn{2}{c}{Bootstrap} & \multicolumn{2}{c}{Synthetic}\\
+ term & estimate & bias & cov & bias & cov \\ 
+  \hline
+  age & 0.461 & 0.004 & 0.942 & 0.002 & 0.939 \\
+  hc & -0.188 & -0.000 & 0.929 & -0.004 & 0.945 \\
+  regeast & -0.339 & 0.012 & 0.960 & 0.092 & 0.957\\
+  regwest & 0.486 & 0.009 & 0.952 & -0.122 & 0.944\\
+  regsouth & 0.646 & 0.012 & 0.966 & -0.152 & 0.943 \\
+  regcity & -0.069 & 0.012 & 0.940 & 0.001 & 0.972 \\
+  G1$|$G2 & -6.322 & 0.032 & 0.934 & -0.254 & 0.946 \\
+  G2$|$G3 & -4.501 & 0.052 & 0.936 & -0.246 & 0.945 \\
+  G3$|$G4 & -3.842 & 0.058 & 0.937 & -0.244 & 0.948 \\
+  G4$|$G5 & -2.639 & 0.064 & 0.936 & -0.253 & 0.947 \\
+   \hline
+\end{tabular}
+\end{table}
+
+These results demonstrate that the synthetic data analysis yields valid
+inferences with low bias.
+
+\hypertarget{data-discrimination}{%
+\subsection{Data discrimination}\label{data-discrimination}}
+
+When we combine the original and synthetic data, can we predict which
+rows come from the synthetic data set? If so, then our synthetic data
+procedure would be redundant, since the synthetic set differs from the
+observed set. To evaluate whether we can distinguish between the true
+data and the synthetic data, we combine the rows from each simulation
+synthetic data set with the rows from the true data. We then run a
+logistic regression model to predict group membership: i.e.~does a row
+belong to the true data or synthetic data. As predictors we take all
+columns in the data. The pooled parameter estimates over all simulations
+can be found in Table 6.
+
+\begin{table}[H]
+\caption{Simulation results for a logistic regression model aimed at discriminating between synthetic records and true records.}
+\centering
+\begin{tabular}{rrrrrr}
+  \hline
+ term & estimate & std.error & statistic & df & p.value \\
+  \hline
+  (Intercept) & 0.22 & 1.15 & 0.19 & 521.93 & 0.60 \\ 
+  wgt & 0.00 & 0.02 & 0.25 & 420.19 & 0.60 \\
+  hgt & -0.00 & 0.01 & -0.18 & 359.73 & 0.60 \\
+  age & -0.00 & 0.05 & -0.00 & 345.73 & 0.62 \\ 
+  hc & 0.00 & 0.03 & 0.11 & 415.44 & 0.61\\
+  gen.L & -0.00 & 0.42 & -0.00 & 164.76 & 0.65 \\
+  gen.Q & -0.01 & 0.21 & -0.04 & 203.38 & 0.63 \\
+  gen.C & -0.00 & 0.16 & -0.02 & 239.63 & 0.64 \\
+  gen\verb|^|4 & 0.01 & 0.21 & 0.01 & 237.41 & 0.63 \\
+  phb.L & -0.02 & 0.44 & -0.04 & 156.54 & 0.64 \\
+  phb.Q & -0.01 & 0.22 & -0.02 & 198.20 & 0.64 \\
+  phb.C & 0.00 & 0.18 & 0.00 & 211.17 & 0.62 \\
+  phb\verb|^|4 & 0.00 & 0.18 & 0.02 & 228.51 & 0.64\\
+  phb\verb|^|5 & 0.00 & 0.20 & 0.02 & 248.57 & 0.63\\
+  tv & 0.00 & 0.02 & 0.01 & 264.26 & 0.63\\
+  regeast & -0.00 & 0.23 & 0.01 & 210.90 & 0.64 \\ 
+  regwest & -0.00 & 0.22 & -0.00 & 221.14 & 0.63 \\ 
+  regsouth & -0.01 & 0.22 & -0.02 & 226.10 & 0.64 \\ 
+  regcity & 0.01 & 0.27 & 0.03 & 204.15 & 0.64 \\ 
+  bmi & -0.02 & 0.06 & -0.26 & 320.18 & 0.61 \\
+   \hline
+\end{tabular}
+\end{table}
+
+From these pooled results we can see that the effects for all predictors
+are close to zero and non-significant. When we take the predicted values
+from the simulated models and compare them with the \emph{real} values,
+we obtain the summary statistics in Table 7.
+
+\begin{table}[H]
+\caption{Confusion statistics for a prediction model aimed at discriminating between synthetic records and true records.}
+\centering
+\begin{tabular}{rr}
+  \hline
+& estimate\\
+  \hline
+ Accuracy & 0.50381 \\
+ Balanced Accuracy & 0.50381 \\
+ Kappa & 0.00762 \\
+ McnemarPValue & 0.63187 \\
+ Sensitivity & 0.50368 \\
+ Specificity & 0.50394 \\
+ Prevalence & 0.50000 \\
+   \hline
+\end{tabular}
+\end{table}
+
+The accuracy of the predictive modeling effort is not better than random
+selection and the Kappa coefficient indicates that a perfect prediction
+model is far from realized. The accuracy is quite balanced as there is
+no skewness over sensitivity and specificity. These findings indicate
+that the synthetic data is indistinguishable from the true data.
 
@@
 
-Authors should discuss the results and how they can be interpreted in
-perspective of previous studies and of the working hypotheses. The
-findings and their implications should be discussed in the broadest
-context possible. Future research directions may also be highlighted.
+We demonstrate that generating synthetic data sets with \texttt{mice} in
+\texttt{R} is a straightforward process that fits well in a data
+analysis pipeline. The multiple synthetic sets yield valid inferences
+about the true underlying data generating mechanism, thereby capturing
+the nature of the original data. This makes the multiple synthetisation
+procedure with \texttt{mice} suitable for further dissemination of
+synthetic data sets.
 
-\hypertarget{conclusion}{%
-\section{Conclusion}\label{conclusion}}
+To non-statisticians, the procedure of generating multiple synthetic
+sets may seem overly complicated. We would like to emphasize that
+analyzing a single synthesized set, while perhaps unbiased, would
+underestimate the variance properties that are so important in drawing
+statistical inferences from finite data sets. After all, we are often
+not interested in the sample at hand, but in the underlying data
+generating mechanism, such as the population. Properly capturing the
+uncertainty of synthetic data sets, just like with incomplete data sets,
+is therefore paramount.
 
-This section is not mandatory, but can be added to the manuscript if the
-discussion is unusually long or complex.
+Analyzing multiple synthetic sets has another clear benefit over
+analyzing just a single synthesized data set: the risk for data
+disclosure is much lower. Instead of having just one synthetic
+realization, a set of multiple synthetic values that could have been are
+generated from the posterior predictive distribution. This means that
+both properties that might belong to individual participants, as well as
+properties that might not belong to those participants can be introduced
+in the synthetic values. Because we are not interested in the individual
+data sets, but rather in the inference obtained over the multiple data
+sets, the likelihood of data properties distributed over participants is
+aggregated to represent the true data generating model.
 
-\hypertarget{patents}{%
-\section{Patents}\label{patents}}
+That said, while the fields of data disclosure control and data
+synthetisation originated decades ago, it is more relevant today than
+ever. In our study we outline a standard research workflow where the
+goal is to synthesize a complete data set. To simplify the simulation we
+adopted a bootstrapping scheme to induce sampling variance in order to
+conform to the combination procedure defined by
+\citet{reiter_partially_inference_2003}. Ideally, one would like to omit
+the bootstrap from the synthetization to adopt a scheme where the
+sampled data itself serves as a reference: much like the procedure
+outlined in \citet{vink2014pooling} for incomplete data simulation. The
+corresponding pooling rules have not been derived yet and the
+incorporation in data analysis workflows would require proper attention
+from developers alike.
 
-This section is not mandatory, but may be added if there are patents
-resulting from the work reported in this manuscript.
+It is important to note that in our simulations we used a single
+iteration. A single iteration is sufficient only when the true data is
+completely observed {[}IBRAHIM ref needed{]}. If both observed and
+unobserved values are to be synthesized, then more iterations and a
+careful investigation into the convergence of the algorithm are in
+order. Synthetic data generation with \texttt{mice} is therein no
+different than multiple imputation with \texttt{mice}.
+
+There are other developments that can generate synthetic data sets. For
+example, the \texttt{synthpop} \citet{synthpop} package in \texttt{R}
+would yield valid synthetic data sets, but requires the true data to be
+completely observed. To avoid this, one could adopt a two-step approach
+wherein the incomplete values are multiply imputed before
+synthetization. Given \(m\) multiple imputations and synthetizations, at
+least \(m^2\) synthetic data sets are then in order. The flexibility
+with \texttt{mice} is that both unobserved and observed data values can
+be synthesized at once, without the need for a two-step approach. With
+\texttt{mice} \(m\) synthetic sets are sufficient.
+
+The ease of use when synthesizing data with \texttt{mice} in \texttt{R},
+together with the validity of inferences obtained through this procedure
+opens up a wealth of possibilities for data dissemination and further
+research of initially private data.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{All sources of funding of the study should be
-disclosed. Please clearly indicate grants that you have received in
-support of your research work. Clearly state if you received funds for
-covering the costs to publish in open access.}
+\acknowledgments{We are grateful to Mirthe Hendriks and Stijn van den
+Broek for replicating the simulation study on an independent data set.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\authorcontributions{For research articles with several authors, a short
-paragraph specifying their individual contributions must be provided.
-The following statements should be used ``X.X. and Y.Y. conceive and
-designed the experiments; X.X. performed the experiments; X.X. and Y.Y.
-analyzed the data; W.W. contributed reagents/materials/analysis tools;
-Y.Y. wrote the paper.'\,' Authorship must be limited to those who have
-contributed substantially to the work reported.}
+\authorcontributions{The authors contributed equally to this work.}
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\conflictsofinterest{`The authors declare no conflict of interest.'}
+\conflictsofinterest{The authors declare no conflict of interest.}
 
@@
 %% optional
-\abbreviations{The following abbreviations are used in this manuscript:\\
-
-\noindent
-\begin{tabular}{@{}ll}
-MDPI & Multidisciplinary Digital Publishing Institute \\
-DOAJ & Directory of open access journals \\
-TLA & Three letter acronym \\
-LD & linear dichroism \\
-\end{tabular}}
 
@@
 %% optional
-\sampleavailability{Samples of the compounds \ldots\ldots{} are
-available from the authors.}
+\sampleavailability{A full simulation archive is available from
+\url{https://github.com/amices/Federated_imputation/tree/master/manuscript}.}
 

### 2021-10-05 mice_synthesizing/paper.Rmd
update manuscript
final draft

@@
 }, .options = furrr_options(seed = as.integer(123)))
+```
 
+```{r cache = TRUE}
 true_age <- 
@@
 
+Iets over meerdere data sets en disclosure risk. een cel can in theorie eigenschappen krijgen toegewezen die niet wenselijk zijn. dat is één van de mogelijkheden van what could have been.
+
 That said, while the field of data synthetisation originated decades ago, it is more relevant today than ever.
@@
 With `mice` $m$ synthetic sets are sufficient.
+
+itereren. als missingness en synth, dan moet je itereren.
 

### 2021-10-05 manuscript/Manuscript.Rmd
contribution dagger updated

@@
   - name: Thom Volker
-    affil: 1,*
+    affil: 1,*, \dagger
     orcid: 0000-0002-2408-7820
@@
       Utrecht University - 
-      Department of Methodology and Statistics
-      Padualaan 14, 3584CH Utrecht, the Netherlands
+      Department of Methodology and Statistics. 
+      Padualaan 14. 3584CH Utrecht, the Netherlands
 # firstnote to eighthnote

### 2021-10-05 manuscript/Manuscript.tex
contribution dagger updated

@@
 % Authors, for the paper (add full first names)
-\Author{Thom
-Volker$^{1,*}$\href{https://orcid.org/0000-0002-2408-7820}{\orcidicon}, Gerko
+\Author{Thom Volker$^{1,*,
+\dagger}$\href{https://orcid.org/0000-0002-2408-7820}{\orcidicon}, Gerko
 Vink$^{1,
@@
 $^{1}$ \quad Utrecht University - Department of Methodology and
-Statistics Padualaan 14, 3584CH Utrecht, the Netherlands; \\
+Statistics. Padualaan 14. 3584CH Utrecht, the Netherlands; \\
 }

### 2021-10-06 manuscript/Manuscript.tex

@@
 data and further analysis of private data. Generating and analyzing
-synthetic data sets is straightforward, yet adopting a synthetic data
-analysis pipeline is often ignored by applied researchers. We outline a
-simple procedure for generating and alayzing synthetic data sets with
-\texttt{mice} in \texttt{R}. We demonstrate in simulation that the
-analysis results obtained on synthetic data obtained with \texttt{mice}
-yields unbiased and valid inferences, and leads to synthetic records
-that cannot be distinguished from the true data records. The ease of use
-when synthesizing data with \texttt{mice}, together with the validity of
-inferences obtained through this procedure opens up a wealth of
-possibilities for data dissemination and further research of initially
-private data.}
+synthetic data sets is straightforward, yet a synthetic data analysis
+pipeline is seldom adopted by applied researchers. We outline a simple
+procedure for generating and analyzing synthetic data sets with
+\texttt{mice} in \texttt{R}. We demonstrate using simulations that the
+analysis results obtained on synthetic data yields unbiased and valid
+inferences, and leads to synthetic records that cannot be distinguished
+from the true data records. The ease of use when synthesizing data with
+\texttt{mice}, together with the validity of inferences obtained through
+this procedure opens up a wealth of possibilities for data dissemination
+and further research of initially private data.}
 
@@
 effort. Additionally, the fact that public funds are used for data
-collection results in increasing demand for the collected data.
-Nevertheless, the possibilities to distribute research data directly are
-often very limited due to restrictions on data privacy and data
-confidentiality. Although these regulations are much needed, privacy
-constraints are also ranked among the toughest challenges to overcome in
-the advancement of modern day social science research
+collection results in increasing demand for access to the collected
+data. Nevertheless, the possibilities to distribute research data
+directly are often very limited due to restrictions on data privacy and
+data confidentiality. Although these regulations are much needed,
+privacy constraints are also ranked among the toughest challenges to
+overcome in the advancement of modern day social science research
 \citep{lazer_life_2009}.
@@
 lunch: data collectors have to put effort in creating high-quality
-synthetic data. Also, the quality of the synthetic data is highly
-dependent on the imputation models, and using flawed models to generate
-synthetic data might bias subsequent analyses. Conversely, if the models
-used to create the synthetic data are able to preserve the relationships
-between the variables as in the original data, the synthetic data can be
-nearly as informative as the observed data. Thus, to fully exploit the
-benefits of synthetic data, the effort to actually create these
-high-quality data sets should be kept at a minimum.
+synthetic data. The quality of the synthetic data is highly dependent on
+the imputation models, and using flawed models to generate synthetic
+data might bias subsequent analyses
+\citep{reiter2004simultaneous, grund2021using, jiang2021balancing}.
+Conversely, if the models used to create the synthetic data are able to
+preserve the relationships between the variables as in the original
+data, the synthetic data can be nearly as informative as the observed
+data. Thus, to fully exploit the benefits of synthetic data, additional
+complications to actually create these high-quality data sets should be
+kept at a minimum.
 
-To mitigate additional effort of creating synthetic data sets on behalf
-of the researcher, software aimed at multiple imputation of missing data
-can be employed. Especially if researchers used this software at an
-earlier stage in the research process, or acquired familiarity with it
-during earlier projects, the additional burden of creating synthetic
-data sets is relatively small. The R-package \texttt{mice} \citep{mice}
-implements multiple imputation of missing data in a straightforward and
-user-friendly manner. However, the functionality of \texttt{mice} is not
-restricted to the imputation of missing data, but allows to impute any
-value in the data: even observed values. Consequently, \texttt{mice} can
-be utilized for the creation of multiply imputed synthetic data sets.
+To mitigate unnecessary challenges related to creating synthetic data
+sets on behalf of the researcher, software aimed at multiple imputation
+of missing data can be employed. Especially if researchers acquired
+familiarity with this software during earlier projects, or used it
+earlier during the research process, the additional burden of creating
+synthetic data sets is relatively small. The R-package \texttt{mice}
+\citep{mice} implements multiple imputation of missing data in a
+straightforward and user-friendly manner. However, the functionality of
+\texttt{mice} is not restricted to the imputation of missing data, but
+allows to impute any value in the data: even observed values.
+Consequently, \texttt{mice} can be utilized for the creation of multiply
+imputed synthetic data sets.
 
-After creating the multiply imputed synthetic data sets, the goal is to
+After creating multiply imputed synthetic data sets, the goal is to
 obtain valid statistical inferences in the spirit of
@@
 imputed data sets, and pooling the results of the analyses according to
-Rubin's rules \citep[pp.76]{rubin_multiple_1987}. In the synthetic data
+Rubin's rules \citep[p.~76]{rubin_multiple_1987}. In the synthetic data
 framework, the same procedure is followed, but with a slight twist:
@@
 The \texttt{mice} package \citep{mice} in \texttt{R} \citep{Rproject}
-has been developed for multiple imputation of missing data. In this
-context, the aim is to replace missing values due to nonresponse by
-plausible values from the posterior predictive distribution of the
-variable containing the missings. Doing so, \texttt{mice} makes use of
-fully conditional specification {[}FCS; \citet{vanbuuren_fully_2006}{]},
-which breaks down the multivariate distribution of the data
+has been developed for multiple imputation to overcome problems related
+to nonresponse. In that context, the aim is to replace missing values
+with plausible values from the posterior predictive distribution of that
+variable. In \texttt{mice}, this is accomplished using fully conditional
+specification (FCS) \citep{vanbuuren_fully_2006}, which breaks down the
+multivariate distribution of the data
 \(\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})\) into
@@
 
-It is straightforward to extended the imputation approach to generate
+It is straightforward to extend the imputation approach to generate
 synthetic values. Rather than imputing missing data, the observed values
@@
 values replaced by draws from the posterior predictive distribution.
-This approach allows to \emph{overimpute} a subset of the observed data,
-or - as in the above example - the observed data as a whole, resulting
-in a data set that partly or completely consists of synthetic data
-values.
+This approach allows to overimpute a subset of the observed data, or as
+in the above example, the observed data as a whole, resulting in a data
+set that partially or completely consists of synthetic data values.
 
@@
 as a flawed imputation model may drastically impact the validity of
-inferences. Imputation models should be as flexible as possible to
-capture most of the patterns in the data, and to model possibly
-unanticipated data characteristics
+inferences \citep{grund2021using, jiang2021balancing}. Imputation models
+should be as flexible as possible to capture most of the patterns in the
+data, and to model possibly unanticipated data characteristics
 \citep{murray_multiple_2018, rubin_18years_1996}. Parametric methods,
@@
 nonlinear relations and interactions between multiple variables.
-Classification and regression trees {[}CART;
-\citet{breiman_cart_1984}{]} allow to model more complex patterns in the
-data, and have therefore been suggested as an appropriate imputation
-method
+Classification and regression trees \citep[CART;][]{breiman_cart_1984}
+allow to model more complex patterns in the data, and have therefore
+been suggested as an appropriate imputation method
 \citep{reiter_cart_2005, burgette_reiter_cart_2010, doove_buuren_recursive_2014}.
@@
 
-We demonstrate the suitability of using \texttt{mice} for synthesization
+We demonstrate the suitability of using \texttt{mice} for synthetisation
 using a simulation study on the \texttt{mice::boys} data set. This data
@@
 which is passively imputed using its deterministic relation with
-\texttt{wgt} and \texttt{hgt}.
+\texttt{wgt} and \texttt{hgt}. Specifically, the imputed values are used
+to calculate the exact \texttt{bmi} values that correspond with
+\texttt{hgt} and \texttt{wgt}.
 
@@
 
-To induce sampling variance, 1000 bootstrap samples of the \texttt{boys}
-data have been synthesized with \(m = 5\) imputations for every data
-cell. Synthetic values are generated using the \texttt{CART} imputation
-method for all columns, except for \texttt{bmi}. The deterministic
-relation \texttt{bmi} which will be synthesized passively based on the
-synthetic values for \texttt{hgt} and \texttt{wgt} to preserve the
-relation in the synthetic data. Additional parameters that come with the
-use of \texttt{mice.impute.cart()} are the complexity parameter
-\texttt{cp} and the minimum number of observations in any terminal node
+Usually, one would draw samples from a population that can be
+synthesized to evaluate the performance of the synthesization methods.
+As we only have access to a single sample, 1000 bootstrap samples of the
+\texttt{boys} data have been synthesized with \(m = 5\) imputations for
+every data cell to induce an appropriate amount of sampling variance.
+Synthetic values are generated using the \texttt{CART} imputation method
+for all columns, except for \texttt{bmi}. The deterministic relation
+\texttt{bmi} which will be synthesized passively based on the synthetic
+values for \texttt{hgt} and \texttt{wgt} to preserve the relation in the
+synthetic data. Additional parameters that come with the use of
+\texttt{mice.impute.cart()} are the complexity parameter \texttt{cp} and
+the minimum number of observations in any terminal node
 \texttt{minbucket}, that both constrain the flexibility of the
@@
 Additionally, since the synthesis pattern is monotone, the number of
-iterations can be set to \texttt{maxit\ =\ 1}.
+iterations can be set to \texttt{maxit\ =\ 1} \citep[e.g.,][Ch.
+3]{drechsler_synthetic_2011}.
 
@@
 bias in the parameters and the \(95\%\) confidence interval coverage of
-the synthetic data will be examined. Similarly to multiple imputation of
-missing data, correct inferences from synthetic data requires correct
+the synthetic data will be examined. Similar to multiple imputation of
+missing data, correct inferences from synthetic data require correct
 pooling over the multiply imputed data sets.
@@
 
-Similarly to the missing data case, variances, and subsequently
+Also similarly to the missing data case, variances, and subsequently
 confidence intervals, should incorporate the increase in variance that
@@
 \begin{table}[ht]
-\caption{Univariate descriptives for the true data and $m=5$ pooled univariate descriptives for the synthetic data over 1000 simulations.}
+\caption{Univariate descriptives for the true data and $m=5$ pooled univariate descriptives for the synthetic data over 1000 simulations. Variable names followed by a $^*$ are categorical.}
 \centering
@@
 We see from Table 1 that the synthetic data estimates closely resemble
-the true data estimates.
+the true data estimates. All sample statistics of interest show
+negligible bias over the 1000 synthetic data sets. Hence, univariately
+the imputation model proves adequate.
 
@@
 We see that the correlations obtained from synthetic data are unbiased
-with respect to the true data set.
+with respect to the true data set. The largest absolute bias over 1000
+simulations equals 0.013, indicating that the imputation model is
+capable of preserving the bivariate relations in the data.
 
@@
 \caption{Simulation results for a linear regression model with continuous and ordered categorical predictors.
-The model evaluated is `hgt ~ age + phb`.
+The model evaluated is \texttt{hgt $\sim$ age + phb}.
 Depicted are the true data estimate and the bias from the true data estimate and the coverage rate of the 95\% confidence interval for the bootstrap and synthetic data sets.}
@@
 We see that the finite nature of the true data set together with the
-design-based simulation setup yields slight undercoverage for the
-polynomial functions. This finding is observed in both the bootstrap
-coverages (i.e.~the fraction of 95\% confidence intervals that cover the
-true data parameters) and the synthetic data coverages, indicating that
-the undercoverage stems from the simulation setup.
+design-based simulation setup yields slight undercoverage for the dummy
+variables of \texttt{phb}. This finding is observed in both the
+bootstrap coverages (i.e.~the fraction of 95\% confidence intervals that
+cover the true data parameters) and the synthetic data coverages. Hence,
+it is likely that this undercoverage stems from the simulation setup,
+rather than the imputation procedure. Besides the undercoverage, there
+is a tiny bit of bias in the estimated coefficients of the variable
+\texttt{phb} that occurs in the synthetic estimates, but not in the
+observed estimates. Yet, since the bias is relatively small and does not
+result in confidence invalidity, it seems fair to assume that the
+introduced bias is not that problematic.
 
@@
 \caption{Simulation results for a proportional odds logistic regression model with continuous and ordered categorical predictors.
-The model evaluated is `gen ~ age + hc + reg`.
+The model evaluated is \texttt{gen $\sim$ age + hc + reg}.
 Depicted are the true data estimate and the bias from the true data estimate and the coverage rate of the 95\% confidence interval for the bootstrap and synthetic data sets.}
@@
 
-These results demonstrate that the synthetic data analysis yields valid
-inferences with low bias.
+These results demonstrate that the synthetic data analysis yields
+inferences that are on par with inferences from the analyses directly on
+the bootstrapped datasets. Hence, for the regression coefficients as
+well as the intercepts, the analyses on the synthetic data yield valid
+results. Nevertheless, a small amount of bias is introduced in the
+estimated intercepts of the synthetic data. However, the corresponding
+confidence interval coverage rates are actually somewhat higher than the
+confidence interval coverage rates of the bootstrapped data. Therefore,
+the corresponding inferences do not seem to be affected by this small
+bias.
 
@@
 \texttt{R} is a straightforward process that fits well in a data
-analysis pipeline. The multiple synthetic sets yield valid inferences
-about the true underlying data generating mechanism, thereby capturing
-the nature of the original data. This makes the multiple synthetisation
-procedure with \texttt{mice} suitable for further dissemination of
-synthetic data sets.
+analysis pipeline. The approach is hardly different from using multiple
+imputation to solve problems related to missing data, and hence can be
+expected to be familiar to applied researchers. The multiple synthetic
+sets yield valid inferences on the true underlying data generating
+mechanism, thereby capturing the nature of the original data. This makes
+the multiple synthetisation procedure with \texttt{mice} suitable for
+further dissemination of synthetic data sets.
 
-To non-statisticians, the procedure of generating multiple synthetic
-sets may seem overly complicated. We would like to emphasize that
-analyzing a single synthesized set, while perhaps unbiased, would
-underestimate the variance properties that are so important in drawing
-statistical inferences from finite data sets. After all, we are often
-not interested in the sample at hand, but in the underlying data
-generating mechanism, such as the population. Properly capturing the
-uncertainty of synthetic data sets, just like with incomplete data sets,
-is therefore paramount.
+To some, the procedure of generating multiple synthetic sets may seem
+overly complicated. We would like to emphasize that analyzing a single
+synthesized set, while perhaps unbiased, would underestimate the
+variance properties that are so important in drawing statistical
+inferences from finite data sets. After all, we are often not interested
+in the sample at hand, but aim to make inferences about the underlying
+data generating mechanism as reflected in the population. Properly
+capturing the uncertainty of synthetic data sets, just like with
+incomplete data sets, is therefore paramount.
 
-Analyzing multiple synthetic sets has another clear benefit over
-analyzing just a single synthesized data set: the risk for data
-disclosure is much lower. Instead of having just one synthetic
-realization, a set of multiple synthetic values that could have been are
-generated from the posterior predictive distribution. This means that
-both properties that might belong to individual participants, as well as
-properties that might not belong to those participants can be introduced
-in the synthetic values. Because we are not interested in the individual
-data sets, but rather in the inference obtained over the multiple data
-sets, the likelihood of data properties distributed over participants is
-aggregated to represent the true data generating model.
+Besides capturing uncertainty of synthetic data, it is important that
+imputers pay close attention to disclosure risks that remain after
+creating synthetic data sets. Creating synthetic data, unless generated
+from a completely parametric distribution, does not remove all potential
+disclosure risks. For example, if the values that ought to be replaced
+get the exact same value imputed, the synthetisation procedure has no
+use.
+
+Additionally, if not all variables in the data are synthesized, but the
+variables that are synthesized can be linked to open access data, a
+disclosure risk may remain \citep{drechsler2011empirical}. If the open
+access data allows for identification, and the corresponding
+observations in the synthetic data can be identified, the variables that
+are not synthesized may provide information that should not have been
+disseminated. The associated problems generally decrease when the
+sensitive variables are synthesized as well. Still, it is important to
+remain critical regarding the extent to which the synthetic data might
+be disclosive. The practical development of easy to use software to
+identify which observations are at risk of disclosure is an area of
+future work that can improve these issues. Subsequently, the
+implementation of ways to overcome such problems, for example by record
+swapping as suggested by \citet{jiang2021balancing}, once detected is
+welcomed.
 
@@
 iteration. A single iteration is sufficient only when the true data is
-completely observed {[}IBRAHIM ref needed{]}. If both observed and
-unobserved values are to be synthesized, then more iterations and a
-careful investigation into the convergence of the algorithm are in
-order. Synthetic data generation with \texttt{mice} is therein no
-different than multiple imputation with \texttt{mice}.
+completely observed, or when the missingness pattern is monotone
+\citep{drechsler_synthetic_2011}. If both observed and unobserved values
+are to be synthesized, then more iterations and a careful investigation
+into the convergence of the algorithm are in order. Synthetic data
+generation with \texttt{mice} is therein no different than multiple
+imputation with \texttt{mice}.
 
 There are other developments that can generate synthetic data sets. For
-example, the \texttt{synthpop} \citet{synthpop} package in \texttt{R}
+example, the \texttt{synthpop} \citep{synthpop} package in \texttt{R}
 would yield valid synthetic data sets, but requires the true data to be
@@
 wherein the incomplete values are multiply imputed before
-synthetization. Given \(m\) multiple imputations and synthetizations, at
-least \(m^2\) synthetic data sets are then in order. The flexibility
-with \texttt{mice} is that both unobserved and observed data values can
-be synthesized at once, without the need for a two-step approach. With
-\texttt{mice} \(m\) synthetic sets are sufficient.
+synthetization. Given \(m\) multiple imputations and \(r\)
+synthetizations, at least \(m \times r\) synthetic data sets are then in
+order. However, this approach requires that researchers first impute the
+missingness using a different package, and then use \texttt{synthpop} to
+create synthetic data sets, while \texttt{mice} allows to do both.
+Additionally, the flexibility with \texttt{mice} is that both unobserved
+and observed data values could be synthesized at once, without the need
+for a two-step approach. Then, using \texttt{mice}, \(m\) synthetic sets
+are sufficient. As of today, no pooling rules for one-step imputation of
+missingness and synthetisation have been developed, but the derivation
+of those would further reduce the burden of creating synthetic data
+sets.
 

### 2021-10-26 manuscript/Manuscript.Rmd
Start revising paper.

@@
   and further analysis of private data. Generating and analyzing synthetic data 
-  sets is straightforward, yet adopting a synthetic data analysis pipeline is 
-  often ignored by applied researchers. We outline a simple procedure for 
-  generating and alayzing synthetic data sets with `mice` in `R`. We demonstrate 
-  in simulation that the analysis results obtained on synthetic data 
-  obtained with `mice` yields unbiased and valid inferences, and leads to synthetic 
+  sets is straightforward, yet a synthetic data analysis pipeline is 
+  seldom adopted by applied researchers. We outline a simple procedure for 
+  generating and analyzing synthetic data sets with `mice` in `R`. We demonstrate 
+  using simulations that the analysis results obtained on synthetic data 
+  yields unbiased and valid inferences, and leads to synthetic 
   records that cannot be distinguished from the true data records. The ease of use 
@@
   We are grateful to Mirthe Hendriks and Stijn van den Broek for replicating the 
-  simulation study on an independent data set. 
+  simulation study on an independent data set. Additionally, we thank Hanne Oberman, [[NOT ANONYMOUS REVIEWER]] and an anonymous reviewer for their stimulating comments.
 authorcontributions: |
@@
 
+# ADD REVIEWER NAME
+
 # Introduction
@@
 Collecting research data requires an enormous investment both in terms of time and monetary resources.
-Openly accessible research data bears the potential of increasing the scientific returns for the same data collection effort.
-Additionally, the fact that public funds are used for data collection results in increasing demand for the collected data.
+Disseminating the research data bears the potential of increasing the scientific returns for the same data collection effort tremendously.
+Additionally, the fact that public funds are used for data collection results in increasing demand for access to the collected data.
 Nevertheless, the possibilities to distribute research data directly are often very limited due to restrictions on data privacy and data confidentiality.
@@
 Conceptually, the synthetic data framework is based upon the building blocks of multiple imputation of missing data, as proposed by @rubin_multiple_1987.
-Instead of replacing just the missing values with multiple draws from the posterior predictive distribution, one could easily *overimpute* any observed sensitive values.
+Instead of replacing just the missing values with multiple draws from the posterior predictive distribution, one could easily replace any observed sensitive values.
 Similarly to multiple imputation of missing data, the multiple synthetic data sets allow for correct statistical inferences, despite the fact that the analyses do not use the "true" value.
@@
 However, there is no such thing as a free lunch: data collectors have to put effort in creating high-quality synthetic data.
-Also, the quality of the synthetic data is highly dependent on the imputation models, and using flawed models to generate synthetic data might bias subsequent analyses.
+The quality of the synthetic data is highly dependent on the imputation models, and using flawed models to generate synthetic data might bias subsequent analyses [@reiter2004simultaneous; @grund2021using; @jiang2021balancing].
 Conversely, if the models used to create the synthetic data are able to preserve the relationships between the variables as in the original data, the synthetic data can be nearly as informative as the observed data.
-Thus, to fully exploit the benefits of synthetic data, the effort to actually create these high-quality data sets should be kept at a minimum.
+Thus, to fully exploit the benefits of synthetic data, additional complications to actually create these high-quality data sets should be kept at a minimum.
 
-To mitigate additional effort of creating synthetic data sets on behalf of the researcher, software aimed at multiple imputation of missing data can be employed.
-Especially if researchers used this software at an earlier stage in the research process, or acquired familiarity with it during earlier projects, the additional burden of creating synthetic data sets is relatively small.
+To mitigate unnecessary challenges related to creating synthetic data sets on behalf of the researcher, software aimed at multiple imputation of missing data can be employed.
+Especially if researchers acquired familiarity with this software during earlier projects, or used it earlier during the research process, the additional burden of creating synthetic data sets is relatively small.
 The R-package `mice` [@mice] implements multiple imputation of missing data in a straightforward and user-friendly manner.
 However, the functionality of `mice` is not restricted to the imputation of missing data, but allows to impute any value in the data: even observed values.
-Consequently, `mice` can be utilized for the creation of multiply imputed synthetic data sets.
+Consequently, `mice` can be used for the creation of multiply imputed synthetic data sets.
 
-After creating the multiply imputed synthetic data sets, the goal is to obtain valid statistical inferences in the spirit of @rubin_multiple_1987 and @neyman1934.
-In the missing data framework, this is done by performing statistical analyses on all imputed data sets, and pooling the results of the analyses according to Rubin's rules [@rubin_multiple_1987, pp.76].
+After creating multiply imputed synthetic data sets, the goal is to obtain valid statistical inferences in the spirit of @rubin_multiple_1987 and @neyman1934.
+In the missing data framework, this is done by performing statistical analyses on all imputed data sets, and pooling the results of the analyses according to Rubin's rules [@rubin_multiple_1987, p.
+76].
 In the synthetic data framework, the same procedure is followed, but with a slight twist: there are no values that remain constant over the synthetic data sets.
@@
 
-The `mice` package [@mice] in `R` [@Rproject] has been developed for multiple imputation of missing data.
-In this context, the aim is to replace missing values due to nonresponse by plausible values from the posterior predictive distribution of the variable containing the missings.
-Doing so, `mice` makes use of fully conditional specification [FCS; @vanbuuren_fully_2006], which breaks down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, where $k$ denotes the number of columns in the data.
+The `mice` package [@mice] in `R` [@Rproject] has been developed for multiple imputation to overcome problems related to nonresponse.
+In that context, the aim is to replace missing values with plausible values from the posterior predictive distribution of that variable.
+In `mice`, this is accomplished using fully conditional specification (FCS) [@vanbuuren_fully_2006], which breaks down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, where $k$ denotes the number of columns in the data.
 Using FCS, a model is constructed for every incomplete variable and the missing values $Y_{j, mis}$ are then imputed with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ on a variable-by-variable basis.
@@
 In `mice`, the generation of multiply imputed data sets to solve for unobserved values is straightforward.
-The following pseudocode details the multiple imputation of the `mice::boys` data set [@fredriks_boys_2000] into the object `imp` with `m = 10` imputated sets and `maxit = 7` iterations for the algorithm to converge, using the default imputations methods for each column data class.
+The following pseudocode details the multiple imputation of the `mice::boys` data set [@fredriks_boys_2000] into the object `imp` with `m = 10` imputated sets and `maxit = 7` iterations for the algorithm to converge, using the default imputations methods given each column's data class.
 
@@
 
-It is straightforward to extended the imputation approach to generate synthetic values.
+It is straightforward to extend the imputation approach to generate synthetic values.
 Rather than imputing missing data, the observed values are then replaced by synthetic draws from the posterior predictive distribution.
 For simplicity, assume that the data is completely observed (i.e., $\textbf{Y} = \textbf{Y}_{obs}$).
-Following the notation of @reiter_raghunathan_multiple_2007, let for $n$ units denote $Z_i = 1$ if any of the values of unit $i = 1, 2, \dots, n$ are to be replaced by imputations, and $Z_i = 0$ otherwise, with $\textbf{Z} = (Z_1, Z_2, \dots, Z_n)$.
+Following the notation of @reiter_raghunathan_multiple_2007, let, given $n$ observations, $Z_i = 1$ if any of the values of unit $i = 1, 2, \dots, n$, are to be replaced by imputations, and $Z_i = 0$ otherwise, with $\textbf{Z} = (Z_1, Z_2, \dots, Z_n)$.
 Accordingly, the data consists of values that are to be replaced and values that are to be kept (i.e., $\textbf{Y} = (\textbf{Y}_{rep}, \textbf{Y}_{nrep})$.
 Now, instead of imputing $\textbf{Y}_{mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, $\textbf{Y}_{rep}$ is imputed from the posterior distribution of $P(Y^{(l)}_{j, rep} | \textbf{Y}^{(l)}_{-j}, \textbf{Z}, \theta)$, where $l$ is an indicator for the synthetic data set ($l = 1, 2, \dots, m$).
-Note that synthetic values that are imputed at an earlier step can be used for imputing variable $j$.
+The synthetic values that are imputed at an earlier step can be used for imputing variable $j$.
 This process results in the synthetic data $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$.
+Note that, given a completely observed data set, iterating over the posterior predictive distribution is not required.
 
-For example, overimputing synthetic values for both the observed and missing cells in the `mice::boys` data set into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution.
+If the goal is to create synthetic versions of a data set that suffers from missingness, the imputation procedure becomes more complex.
+A two-step imputation procedure has been proposed by @reiter2004simultaneous.
+In the first step, the missing data is imputed according to the principles of multiple imputation for missing data, while in a second step, the synthetic data is imputed conform the corresponding procedure.
+Intuitively, these steps could be combined using `mice`, conditioning the imputations on both the missingness and the values that are to be synthesized.
+In practice, replacing observed and missing cells in the `mice::boys` data set by synthetic values into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution.
 
@@
 
-where the argument `where` requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix) containing logicals $z_{ij}$ that indicate which cells are selected to have their values replaced by draws from the posterior predictive distribution.
-This approach allows to *overimpute* a subset of the observed data, or - as in the above example - the observed data as a whole, resulting in a data set that partly or completely consists of synthetic data values.
+Here, the argument `where` requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix) containing logicals $z_{ij}$ that indicate which cells are selected to have their values replaced by draws from the posterior predictive distribution.
+This approach allows to replace a subset of the observed data, or as in the aforementioned example, the observed data as a whole, resulting in a data set that partially or completely consists of synthetic data values.
+However, because the validity of this approach when the data suffers from missingness has not been investigated yet, we restrict ourselves in the following sections to a completely observed data set.However, because the validity of this approach has not been investigated yet, we restrict ourselves in the followi
 
-Choosing an adequate imputation model to impute the data is paramount, as a flawed imputation model may drastically impact the validity of inferences.
+Choosing an adequate imputation model to impute the data is paramount, as a flawed imputation model may drastically impact the validity of inferences [@grund2021using; @jiang2021balancing].
 Imputation models should be as flexible as possible to capture most of the patterns in the data, and to model possibly unanticipated data characteristics [@murray_multiple_2018; @rubin_18years_1996].
 Parametric methods, albeit easy to implement in practice, may be too restrictive to capture generally complex patterns in the data, especially in the case of nonlinear relations and interactions between multiple variables.
-Classification and regression trees [CART; @breiman_cart_1984] allow to model more complex patterns in the data, and have therefore been suggested as an appropriate imputation method [@reiter_cart_2005; @burgette_reiter_cart_2010; @doove_buuren_recursive_2014].
+Classification and regression trees [CART\; @breiman_cart_1984] allow to model more complex patterns in the data, and have therefore been suggested as an appropriate imputation method [@reiter_cart_2005; @burgette_reiter_cart_2010; @doove_buuren_recursive_2014].
 Loosely speaking, CART sequentially splits the predictor space into non-overlapping regions in such a way that the within-region variance is as small as possible after every split.
@@
 
-We demonstrate the suitability of using `mice` for synthesization using a simulation study on the `mice::boys` data set.
+We demonstrate the suitability of using `mice` for synthetisation using a simulation study on the `mice::boys` data set.
 This data set consists of the values of $`r nrow(mice::boys)`$ Dutch boys on the following $`r ncol(mice::boys)`$ variables:
@@
 For simplicity, we complete the missing values using the default `mice` imputation model for all predictors except `bmi`, which is passively imputed using its deterministic relation with `wgt` and `hgt`.
+Specifically, the imputed values are used to calculate the exact `bmi` values that correspond with `hgt` and `wgt`.
 
@@
 
-To induce sampling variance, 1000 bootstrap samples of the `boys` data have been synthesized with $m = 5$ imputations for every data cell.
+Usually, one would draw samples from a population that can be synthesized to evaluate the performance of the synthesization methods.
+As we only have access to a single sample, 1000 bootstrap samples of the `boys` data have been synthesized with $m = 5$ imputations for every data cell to induce an appropriate amount of sampling variance.
 Synthetic values are generated using the `CART` imputation method for all columns, except for `bmi`.
@@
 By allowing for more complexity in the imputation model, bias in the estimates from the synthetic data set is reduced.
-Additionally, since the synthesis pattern is monotone, the number of iterations can be set to `maxit = 1`.
+Additionally, since the synthesis pattern is monotone, the number of iterations can be set to `maxit = 1` [e.g., @drechsler_synthetic_2011, Ch.
+3].
 
@@
 Subsequently, the bias in the parameters and the $95\%$ confidence interval coverage of the synthetic data will be examined.
-Similarly to multiple imputation of missing data, correct inferences from synthetic data requires correct pooling over the multiply imputed data sets.
+Similar to multiple imputation of missing data, correct inferences from synthetic data require correct pooling over the multiply imputed data sets.
 
@@
 
-Similarly to the missing data case, variances, and subsequently confidence intervals, should incorporate the increase in variance that is due to imputation [@reiter_partially_inference_2003; @drechsler_synthetic_2011].
-Yet, the increase in variance due to imputation differs according to whether missing values are imputed or observed data is overimputed with missing values.
+Also similarly to the missing data case, variances, and subsequently confidence intervals, should incorporate the increase in variance that is due to imputation [@reiter_partially_inference_2003; @drechsler_synthetic_2011].
+Yet, the increase in variance due to imputation differs according to whether missing values are imputed or observed data is replaced by synthetic values.
 Whereas the variance estimate after imputation of missing data needs to account for the fact that a certain amount of information in the data is missing, variance estimation from synthetic data does not suffer from this issue.
@@
 # Results
+
 ```{r simulation, message = FALSE, warning = FALSE, cache = TRUE, cache.lazy = FALSE, echo = FALSE}
@@
 ## Univariate estimates
+
 The univariate descriptives for the original data and the synthetic data can be found in Table 2.
+
 ```{r univariate-statistics, echo = FALSE, cache = TRUE, results = FALSE}
@@
   Reduce("+", .) / length(synthetic_samples)
-rownames(true) <- paste("original", rownames(true), sep = " ")
+rownames(true) <- paste("observed", rownames(true), sep = " ")
 rownames(synth) <- paste("synthetic", rownames(synth), sep = " ")
@@
 We see from Table 1 that the synthetic data estimates closely resemble the true data estimates.
+All sample statistics of interest show negligible bias over the 1000 synthetic data sets.
+Hence, univariately the imputation model proves adequate.
 
 ## Bivariate estimates
+
 An often used bivariate statistic is Pearson's correlation coefficient.
@@
 The results are displayed in Table 3.
+
 ```{r bivariate-statistics, echo = FALSE, cache = TRUE, results = FALSE}
@@
 \end{table}
+
 We see that the correlations obtained from synthetic data are unbiased with respect to the true data set.
+The largest absolute bias over 1000 simulations equals 0.013, indicating that the imputation model is capable of preserving the bivariate relations in the data.
 
@@
 ```
+
 First, we evaluate the performance of our synthetic simulation set on a linear model where `hgt` is modeled by a continuous predictor `age` and an ordered categorical predictor `phb`.
@@
 
-We see that the finite nature of the true data set together with the design-based simulation setup yields slight undercoverage for the polynomial functions.
+We see that the finite nature of the true data set together with the design-based simulation setup yields slight undercoverage for the dummy variables of `phb`.
 This finding is observed in both the bootstrap coverages (i.e.
-the fraction of 95% confidence intervals that cover the true data parameters) and the synthetic data coverages, indicating that the undercoverage stems from the simulation setup.
+the fraction of 95% confidence intervals that cover the true data parameters) and the synthetic data coverages.
+Hence, it is likely that this undercoverage stems from the simulation setup, rather than the imputation procedure.
+Besides the undercoverage, there is a tiny bit of bias in the estimated coefficients of the variable `phb` that occurs in the synthetic estimates, but not in the observed estimates.
+Yet, since the bias is relatively small and does not result in confidence invalidity, it seems fair to assume that the introduced bias is not that problematic.
 
@@
 \end{table}
-These results demonstrate that the synthetic data analysis yields valid inferences with low bias.
+
+These results demonstrate that the synthetic data analysis yields inferences that are on par with inferences from the analyses directly on the bootstrapped datasets.
+Hence, for the regression coefficients as well as the intercepts, the analyses on the synthetic data yield valid results.
+Nevertheless, a small amount of bias is introduced in the estimated intercepts of the synthetic data.
+However, the corresponding confidence interval coverage rates are actually somewhat higher than the confidence interval coverage rates of the bootstrapped data.
+Therefore, the corresponding inferences do not seem to be affected by this small bias.
 
 ## Data discrimination
+
 When we combine the original and synthetic data, can we predict which rows come from the synthetic data set?
@@
 We demonstrate that generating synthetic data sets with `mice` in `R` is a straightforward process that fits well in a data analysis pipeline.
-The multiple synthetic sets yield valid inferences about the true underlying data generating mechanism, thereby capturing the nature of the original data.
+The approach is hardly different from using multiple imputation to solve problems related to missing data, and hence can be expected to be familiar to applied researchers.
+The multiple synthetic sets yield valid inferences on the true underlying data generating mechanism, thereby capturing the nature of the original data.
 This makes the multiple synthetisation procedure with `mice` suitable for further dissemination of synthetic data sets.
 
-To non-statisticians, the procedure of generating multiple synthetic sets may seem overly complicated.
+To some, the procedure of generating multiple synthetic sets may seem overly complicated.
 We would like to emphasize that analyzing a single synthesized set, while perhaps unbiased, would underestimate the variance properties that are so important in drawing statistical inferences from finite data sets.
-After all, we are often not interested in the sample at hand, but in the underlying data generating mechanism, such as the population.
+After all, we are often not interested in the sample at hand, but aim to make inferences about the underlying data generating mechanism as reflected in the population.
 Properly capturing the uncertainty of synthetic data sets, just like with incomplete data sets, is therefore paramount.
 
-Analyzing multiple synthetic sets has another clear benefit over analyzing just a single synthesized data set: the risk for data disclosure is much lower.
-Instead of having just one synthetic realization, a set of multiple synthetic values that could have been are generated from the posterior predictive distribution.
-This means that both properties that might belong to individual participants, as well as properties that might not belong to those participants can be introduced in the synthetic values.
-Because we are not interested in the individual data sets, but rather in the inference obtained over the multiple data sets, the likelihood of data properties distributed over participants is aggregated to represent the true data generating model.
+Besides capturing uncertainty of synthetic data, it is important that imputers pay close attention to disclosure risks that remain after creating synthetic data sets.
+Creating synthetic data, unless generated from a completely parametric distribution, does not remove all potential disclosure risks.
+For example, if the values that ought to be replaced get the exact same value imputed, the synthetisation procedure has no use.
+
+Additionally, if not all variables in the data are synthesized, but the variables that are synthesized can be linked to open access data, a disclosure risk may remain [@drechsler2011empirical].
+If the open access data allows for identification, and the corresponding observations in the synthetic data can be identified, the variables that are not synthesized may provide information that should not have been disseminated.
+The associated problems generally decrease when the sensitive variables are synthesized as well.
+Still, it is important to remain critical regarding the extent to which the synthetic data might be disclosive.
+The practical development of easy to use software to identify which observations are at risk of disclosure is an area of future work that can improve these issues.
+Subsequently, the implementation of ways to overcome such problems once detected, for example by record swapping as suggested by @jiang2021balancing, is welcomed.
 
@@
 To simplify the simulation we adopted a bootstrapping scheme to induce sampling variance in order to conform to the combination procedure defined by @reiter_partially_inference_2003.
-Ideally, one would like to omit the bootstrap from the synthetization to adopt a scheme where the sampled data itself serves as a reference: much like the procedure outlined in @vink2014pooling for incomplete data simulation.
+Ideally, one would like to omit the bootstrap from the synthetisation to adopt a scheme where the sampled data itself serves as a reference: much like the procedure outlined in @vink2014pooling for incomplete data simulation.
 The corresponding pooling rules have not been derived yet and the incorporation in data analysis workflows would require proper attention from developers alike.
 
+There exist other software that is capable of creating synthetic data.
+For example, the `synthpop` [@synthpop] package in `R` pioneered in the field of synthetic data generation in `R`, and contains many functionalities to create and evaluate synthetic data sets.
+However, although `synthpop` is capable to synthesize regardless of missing data, it cannot solve eventual missingness problems.
+If the data for synthetisation contains missing values, the missingness will be considered as a property of the data, and the corresponding synthetic data sets will contain missing values as well.
+If the goal is to impute and synthesize a data set, a two-step approach must be used, in which the missing values are imputed using a different package, like `mice`, after which `synthpop` can be used to synthesize the imputed data.
+Then, given $m$ multiple imputations and $r$ synthetisations, at least $m \times r$ synthetic data sets are in order, after which the data can be analysed and the analyses can be pooled using rules developed by @reiter2004simultaneous.
+However, such an approach would be computationally inefficient and practically cumbersome, because the architectures of both packages differ.
+
+The appealing nature of `mice` therefore lays in its ability to solve both the missingness problem and create synthetic versions of the data.
+Eventually, the flexibility with `mice` is that both unobserved and observed data values could be synthesized at once, without the need for a two-step approach.
+Using `mice`, $m$ synthetic sets would sufficient.
+However, as of today, no pooling rules for one-step imputation of missingness and synthetisation have been developed.
+The derivation of those would yield a massive theoretical improve to further reduce the burden of creating synthetic data sets.
+More practically, the `synthpop` package contains functionality that would be highly beneficial to users in `mice`, while `mice` is likely to contain functionality that would be beneficial to `synthpop`.
+Although efforts have been made to bridge gaps between the packages [e.g., @miceadds_3.11-6], further improvements could be made in that respect.
+Specifically, `synthpop` contains a wide variety of functions that can be used to assess the quality of synthetic data [e.g., see ADD SNOKE REFERENCE + ARXIV], while `mice` contains methods to impute multilevel data.
+Being able to use such functionality interchangeably would greatly benefit the public.
+
 It is important to note that in our simulations we used a single iteration.
-A single iteration is sufficient only when the true data is completely observed [IBRAHIM ref needed].
+A single iteration is sufficient only when the true data is completely observed, or when the missingness pattern is monotone [@drechsler_synthetic_2011].
 If both observed and unobserved values are to be synthesized, then more iterations and a careful investigation into the convergence of the algorithm are in order.
-Synthetic data generation with `mice` is therein no different than multiple imputation with `mice`.
-
-There are other developments that can generate synthetic data sets.
-For example, the `synthpop` @synthpop package in `R` would yield valid synthetic data sets, but requires the true data to be completely observed.
-To avoid this, one could adopt a two-step approach wherein the incomplete values are multiply imputed before synthetization.
-Given $m$ multiple imputations and synthetizations, at least $m^2$ synthetic data sets are then in order.
-The flexibility with `mice` is that both unobserved and observed data values can be synthesized at once, without the need for a two-step approach.
-With `mice` $m$ synthetic sets are sufficient.
+Synthetic data generation with `mice` is therein no different than multiple imputation.
 

### 2021-10-26 manuscript/Manuscript.tex
Start revising paper.

@@
 
+\hypertarget{add-reviewer-name}{%
+\section{ADD REVIEWER NAME}\label{add-reviewer-name}}
+
 \hypertarget{introduction}{%
@@
 research data requires an enormous investment both in terms of time and
-monetary resources. Openly accessible research data bears the potential
-of increasing the scientific returns for the same data collection
-effort. Additionally, the fact that public funds are used for data
+monetary resources. Disseminating the research data bears the potential
+of increasing the scientific returns for the same data collection effort
+tremendously. Additionally, the fact that public funds are used for data
 collection results in increasing demand for access to the collected
@@
 values with multiple draws from the posterior predictive distribution,
-one could easily \emph{overimpute} any observed sensitive values.
-Similarly to multiple imputation of missing data, the multiple synthetic
-data sets allow for correct statistical inferences, despite the fact
-that the analyses do not use the ``true'' value. The analyses over
-multiple synthetic data sets should be pooled into a single inference,
-so that the researcher can draw valid conclusions from the pooled
-results. To that respect, the variance should reflect the added
-variability that is induced by the imputation procedure.
+one could easily replace any observed sensitive values. Similarly to
+multiple imputation of missing data, the multiple synthetic data sets
+allow for correct statistical inferences, despite the fact that the
+analyses do not use the ``true'' value. The analyses over multiple
+synthetic data sets should be pooled into a single inference, so that
+the researcher can draw valid conclusions from the pooled results. To
+that respect, the variance should reflect the added variability that is
+induced by the imputation procedure.
 
@@
 allows to impute any value in the data: even observed values.
-Consequently, \texttt{mice} can be utilized for the creation of multiply
+Consequently, \texttt{mice} can be used for the creation of multiply
 imputed synthetic data sets.
@@
 \texttt{m\ =\ 10} imputated sets and \texttt{maxit\ =\ 7} iterations for
-the algorithm to converge, using the default imputations methods for
-each column data class.
+the algorithm to converge, using the default imputations methods given
+each column's data class.
 
@@
 observed (i.e., \(\textbf{Y} = \textbf{Y}_{obs}\)). Following the
-notation of \citet{reiter_raghunathan_multiple_2007}, let for \(n\)
-units denote \(Z_i = 1\) if any of the values of unit
-\(i = 1, 2, \dots, n\) are to be replaced by imputations, and
+notation of \citet{reiter_raghunathan_multiple_2007}, let, given \(n\)
+observations, \(Z_i = 1\) if any of the values of unit
+\(i = 1, 2, \dots, n\), are to be replaced by imputations, and
 \(Z_i = 0\) otherwise, with \(\textbf{Z} = (Z_1, Z_2, \dots, Z_n)\).
@@
 where \(l\) is an indicator for the synthetic data set
-(\(l = 1, 2, \dots, m\)). Note that synthetic values that are imputed at
-an earlier step can be used for imputing variable \(j\). This process
+(\(l = 1, 2, \dots, m\)). The synthetic values that are imputed at an
+earlier step can be used for imputing variable \(j\). This process
 results in the synthetic data
 \(\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})\).
-
-For example, overimputing synthetic values for both the observed and
-missing cells in the \texttt{mice::boys} data set into the object
-\texttt{syn}, given the same imputation parameters as before, can be
-realized by the following code execution.
+Note that, given a completely observed data set, iterating over the
+posterior predictive distribution is not required.
+
+If the goal is to create synthetic versions of a data set that suffers
+from missingness, the imputation procedure becomes more complex. A
+two-step imputation procedure has been proposed by
+\citet{reiter2004simultaneous}. In the first step, the missing data is
+imputed according to the principles of multiple imputation for missing
+data, while in a second step, the synthetic data is imputed conform the
+corresponding procedure. Intuitively, these steps could be combined
+using \texttt{mice}, conditioning the imputations on both the
+missingness and the values that are to be synthesized. In practice,
+replacing observed and missing cells in the \texttt{mice::boys} data set
+by synthetic values into the object \texttt{syn}, given the same
+imputation parameters as before, can be realized by the following code
+execution.
 
@@
 
-where the argument \texttt{where} requires a matrix of the same
+Here, the argument \texttt{where} requires a matrix of the same
 dimensions as the data, (i.e., a \(n \times k\) matrix) containing
@@
 values replaced by draws from the posterior predictive distribution.
-This approach allows to overimpute a subset of the observed data, or as
-in the above example, the observed data as a whole, resulting in a data
-set that partially or completely consists of synthetic data values.
+This approach allows to replace a subset of the observed data, or as in
+the aforementioned example, the observed data as a whole, resulting in a
+data set that partially or completely consists of synthetic data values.
+However, because the validity of this approach when the data suffers
+from missingness has not been investigated yet, we restrict ourselves in
+the following sections to a completely observed data set.However,
+because the validity of this approach has not been investigated yet, we
+restrict ourselves in the followi
 
@@
 the increase in variance due to imputation differs according to whether
-missing values are imputed or observed data is overimputed with missing
+missing values are imputed or observed data is replaced by synthetic
 values. Whereas the variance estimate after imputation of missing data
@@
 future work that can improve these issues. Subsequently, the
-implementation of ways to overcome such problems, for example by record
-swapping as suggested by \citet{jiang2021balancing}, once detected is
-welcomed.
+implementation of ways to overcome such problems once detected, for
+example by record swapping as suggested by \citet{jiang2021balancing},
+is welcomed.
 
@@
 \citet{reiter_partially_inference_2003}. Ideally, one would like to omit
-the bootstrap from the synthetization to adopt a scheme where the
+the bootstrap from the synthetisation to adopt a scheme where the
 sampled data itself serves as a reference: much like the procedure
@@
 from developers alike.
+
+There exist other software that is capable of creating synthetic data.
+For example, the \texttt{synthpop} \citep{synthpop} package in
+\texttt{R} pioneered in the field of synthetic data generation in
+\texttt{R}, and contains many functionalities to create and evaluate
+synthetic data sets. However, although \texttt{synthpop} is capable to
+synthesize regardless of missing data, it cannot solve eventual
+missingness problems. If the data for synthetisation contains missing
+values, the missingness will be considered as a property of the data,
+and the corresponding synthetic data sets will contain missing values as
+well. If the goal is to impute and synthesize a data set, a two-step
+approach must be used, in which the missing values are imputed using a
+different package, like \texttt{mice}, after which \texttt{synthpop} can
+be used to synthesize the imputed data. Then, given \(m\) multiple
+imputations and \(r\) synthetisations, at least \(m \times r\) synthetic
+data sets are in order, after which the data can be analysed and the
+analyses can be pooled using rules developed by
+\citet{reiter2004simultaneous}. However, such an approach would be
+computationally inefficient and practically cumbersome, because the
+architectures of both packages differ.
+
+The appealing nature of \texttt{mice} therefore lays in its ability to
+solve both the missingness problem and create synthetic versions of the
+data. Eventually, the flexibility with \texttt{mice} is that both
+unobserved and observed data values could be synthesized at once,
+without the need for a two-step approach. Using \texttt{mice}, \(m\)
+synthetic sets would sufficient. However, as of today, no pooling rules
+for one-step imputation of missingness and synthetisation have been
+developed. The derivation of those would yield a massive theoretical
+improve to further reduce the burden of creating synthetic data sets.
+More practically, the \texttt{synthpop} package contains functionality
+that would be highly beneficial to users in \texttt{mice}, while
+\texttt{mice} is likely to contain functionality that would be
+beneficial to \texttt{synthpop}. Although efforts have been made to
+bridge gaps between the packages \citep[e.g.,][]{miceadds_3.11-6},
+further improvements could be made in that respect. Specifically,
+\texttt{synthpop} contains a wide variety of functions that can be used
+to assess the quality of synthetic data {[}e.g., see ADD SNOKE REFERENCE
++ ARXIV{]}, while \texttt{mice} contains methods to impute multilevel
+data. Being able to use such functionality interchangeably would greatly
+benefit the public.
 
@@
 generation with \texttt{mice} is therein no different than multiple
-imputation with \texttt{mice}.
-
-There are other developments that can generate synthetic data sets. For
-example, the \texttt{synthpop} \citep{synthpop} package in \texttt{R}
-would yield valid synthetic data sets, but requires the true data to be
-completely observed. To avoid this, one could adopt a two-step approach
-wherein the incomplete values are multiply imputed before
-synthetization. Given \(m\) multiple imputations and \(r\)
-synthetizations, at least \(m \times r\) synthetic data sets are then in
-order. However, this approach requires that researchers first impute the
-missingness using a different package, and then use \texttt{synthpop} to
-create synthetic data sets, while \texttt{mice} allows to do both.
-Additionally, the flexibility with \texttt{mice} is that both unobserved
-and observed data values could be synthesized at once, without the need
-for a two-step approach. Then, using \texttt{mice}, \(m\) synthetic sets
-are sufficient. As of today, no pooling rules for one-step imputation of
-missingness and synthetisation have been developed, but the derivation
-of those would further reduce the burden of creating synthetic data
-sets.
+imputation.
 
@@
 \acknowledgments{We are grateful to Mirthe Hendriks and Stijn van den
-Broek for replicating the simulation study on an independent data set.}
+Broek for replicating the simulation study on an independent data set.
+Additionally, we thank Hanne Oberman, {[}{[}NOT ANONYMOUS REVIEWER{]}{]}
+and an anonymous reviewer for their stimulating comments.}
 

### 2021-10-27 manuscript/Blind/Submitted/cover letter.tex
Gerko

 \documentstyle{letter}
 \begin{document}
 \pagestyle{empty}

Dear Editor,\\
\newline

We would like to submit the attached manuscript, ”Anonymiced shareable data: Using mice to create and analyze multiply imputed synthetic data sets” for consideration for possible publication in the special issue on \emph{Computational Aspects, Statistical Algorithms and Software in Psychometrics} in \texttt{Psych}. The manuscript outlines a procedure to generate synthetic data sets with \texttt{mice} in {R}. The proposed workflow yields valid univariate and multivariate estimates and allows for valid inference on synthetic data sets generated with \texttt{mice}. We believe that the procedure in our manuscript solves an important problem for applied research and the readership of \texttt{Psych}.

The paper has not been published or accepted for publication elsewhere. It is not under consideration at another journal or at Sociological Methods and Research.

Sincerely, 
\newline\\  
Thom Volker\\
Gerko Vink\\
\newline

Contact Information:\\
Thom Volker\\
Utrecht University\\
Department of Methodology and Statistics\\
PO Box 80140\\
3508 TC Utrecht\\
The Netherlands\\
e-mail: t.b.volker@uu.nl\\

 \end{document}

### 2021-10-27 manuscript/Manuscript.Rmd
Incorporate reviewer comments.

@@
   We are grateful to Mirthe Hendriks and Stijn van den Broek for replicating the 
-  simulation study on an independent data set. Additionally, we thank Hanne Oberman, [[NOT ANONYMOUS REVIEWER]] and an anonymous reviewer for their stimulating comments.
+  simulation study on an independent data set. Additionally, we thank Hanne Oberman and two anonymous reviewers for their stimulating comments.
 authorcontributions: |
@@
 ---
-
-# ADD REVIEWER NAME
 
@@
 Although their approaches differ to some extent, the overarching procedure is to use bonafide observed data to generate multiply imputed synthetic data sets that can be freely disclosed.
-While in practice, one could see this as replacing the observed data values by multiple draws from the posterior predictive distribution of the observed data, based on some imputation model, Rubin would argue that these synthetic data values are merely draws from the same true data generating model.
+While in practice, one could see this as replacing the observed data values by multiple draws from the predictive distribution of the observed data, based on some imputation model, Rubin would argue that these synthetic data values are merely draws from the same true data generating model.
 In that sense, the observed data is never replaced, but the population is resampled from the information captured in the (incomplete) sample.
@@
 Conceptually, the synthetic data framework is based upon the building blocks of multiple imputation of missing data, as proposed by @rubin_multiple_1987.
-Instead of replacing just the missing values with multiple draws from the posterior predictive distribution, one could easily replace any observed sensitive values.
+Instead of replacing just the missing values, one could easily replace any observed sensitive values by multiple draws from the posterior predictive distribution - or a non-Bayesian predictive distribution.
+We will refer to both of these as predictive distributions.
 Similarly to multiple imputation of missing data, the multiple synthetic data sets allow for correct statistical inferences, despite the fact that the analyses do not use the "true" value.
@@
 
-Potentially, this approach could fulfill the needs for openly accessibly data, without running into barriers with regard to privacy and confidentiality constraints.
+Potentially, this approach could fulfil the needs for openly accessible data, without running into barriers with regard to privacy and confidentiality constraints.
 However, there is no such thing as a free lunch: data collectors have to put effort in creating high-quality synthetic data.
-The quality of the synthetic data is highly dependent on the imputation models, and using flawed models to generate synthetic data might bias subsequent analyses [@reiter2004simultaneous; @grund2021using; @jiang2021balancing].
-Conversely, if the models used to create the synthetic data are able to preserve the relationships between the variables as in the original data, the synthetic data can be nearly as informative as the observed data.
-Thus, to fully exploit the benefits of synthetic data, additional complications to actually create these high-quality data sets should be kept at a minimum.
+The quality of the synthetic data is highly dependent on the imputation models, and using flawed imputation models might bias subsequent analyses [@reiter2004simultaneous; @grund2021using; @jiang2021balancing].
+Conversely, if the models used to synthesize the data are able to preserve the relationships between the variables as in the original data, the synthetic data can be nearly as informative as the observed data.
+To fully exploit the benefits of synthetic data, complicating aspects of creating high-quality synthetic data sets should be kept at a minimum, while keeping the accuracy of the models as high as possible.
 
@@
 
+Generally, there are three ways to impute data: joint modeling, sequential modeling and fully conditional specification [@murray_multiple_2018; @ludtke2020regression; @grund2021using].
+With joint modeling, the entire joint distribution of the data is specified as a single multivariate distribution, and the imputations are drawn from this model.
+This strategy is implemented in, among others, the `R`-package `jomo` [@jomo] to deal with missing data.
+However, when the structure of the data increases in complexity, specifying a single multivariate distribution can become cumbersome.
+A more flexible solution has been proposed in sequential regression imputation, in which the multivariate distribution is separated into univariate distributions for every variable.
+Every single variable is then imputed conditional on a model containing only the variables in the sequence located before the variable to be imputed.
+This approach has been implemented in the R-packages `mdmb` [@mdmb] for imputation of missing data and `synthpop` [@synthpop] for imputation of synthetic data.
+
 The `mice` package [@mice] in `R` [@Rproject] has been developed for multiple imputation to overcome problems related to nonresponse.
-In that context, the aim is to replace missing values with plausible values from the posterior predictive distribution of that variable.
+In that context, the aim is to replace missing values with plausible values from the predictive distribution of that variable.
 In `mice`, this is accomplished using fully conditional specification (FCS) [@vanbuuren_fully_2006], which breaks down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, where $k$ denotes the number of columns in the data.
-Using FCS, a model is constructed for every incomplete variable and the missing values $Y_{j, mis}$ are then imputed with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ on a variable-by-variable basis.
+Using FCS, a model is constructed for every incomplete variable and the missing values $Y_{j, mis}$ are then imputed with draws from the predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ on a variable-by-variable basis.
 Note that the predictor matrix $Y_{-j}$ may contain yet imputed values from an earlier imputation step, and thus will be updated after every iteration.
@@
 In `mice`, the generation of multiply imputed data sets to solve for unobserved values is straightforward.
-The following pseudocode details the multiple imputation of the `mice::boys` data set [@fredriks_boys_2000] into the object `imp` with `m = 10` imputated sets and `maxit = 7` iterations for the algorithm to converge, using the default imputations methods given each column's data class.
+The following pseudocode details multiple imputation of any data set that contains missingness into the object `imp` with `m = 10` imputated sets and `maxit = 7` iterations for the algorithm to converge, using the default imputations methods.
 
@@
 library(mice)
-imp <- mice(boys, 
+imp <- mice(data.with.missings, 
             m = 10,
@@
 
-It is straightforward to extend the imputation approach to generate synthetic values.
-Rather than imputing missing data, the observed values are then replaced by synthetic draws from the posterior predictive distribution.
+The imputation approach in `mice` can be easily extended to generate synthetic values.
+Rather than imputing missing data, observed values are then replaced by synthetic draws from the predictive distribution.
 For simplicity, assume that the data is completely observed (i.e., $\textbf{Y} = \textbf{Y}_{obs}$).
@@
 Accordingly, the data consists of values that are to be replaced and values that are to be kept (i.e., $\textbf{Y} = (\textbf{Y}_{rep}, \textbf{Y}_{nrep})$.
-Now, instead of imputing $\textbf{Y}_{mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, $\textbf{Y}_{rep}$ is imputed from the posterior distribution of $P(Y^{(l)}_{j, rep} | \textbf{Y}^{(l)}_{-j}, \textbf{Z}, \theta)$, where $l$ is an indicator for the synthetic data set ($l = 1, 2, \dots, m$).
+Now, instead of imputing $\textbf{Y}_{mis}$ with draws from the predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, $\textbf{Y}_{rep}$ is imputed from the posterior distribution of $P(Y^{(l)}_{j, rep} | \textbf{Y}^{(l)}_{-j}, \textbf{Z}, \theta)$, where $l$ is an indicator for the synthetic data set ($l = 1, 2, \dots, m$).
 The synthetic values that are imputed at an earlier step can be used for imputing variable $j$.
 This process results in the synthetic data $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$.
-Note that, given a completely observed data set, iterating over the posterior predictive distribution is not required.
+Note that, given a completely observed data set, iterating over the predictive distribution is not required.
+
+Hence, creating synthetic values for a completely observed data set into the object `syn`, given the same imputation parameters as specified above, can be realized as follows:
+
+```{r eval = FALSE}
+library(mice)
+imp <- mice(data.to.synthesize, 
+            m = 10,
+            maxit = 1,
+            where = matrix(TRUE,
+                           nrow = nrow(data.to.synthesize),
+                           ncol = ncol(data.to.synthetize)))
+```
+
+Here, the argument `where` requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix) containing logicals $z_{ij}$ that indicate which cells are selected to have their values replaced by draws from the predictive distribution.
+This approach allows to replace a subset of the observed data (e.g., by only specifying those cells that are to be replaced as `TRUE` in the `where`-matrix, leaving the rest to `FALSE`), or as in the aforementioned example, the observed data as a whole, resulting in a data set that partially or completely consists of synthetic data values.
+Note that because the data is completely observed, iterating over the predictive distribution is not required.
 
@@
 In the first step, the missing data is imputed according to the principles of multiple imputation for missing data, while in a second step, the synthetic data is imputed conform the corresponding procedure.
-Intuitively, these steps could be combined using `mice`, conditioning the imputations on both the missingness and the values that are to be synthesized.
-In practice, replacing observed and missing cells in the `mice::boys` data set by synthetic values into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution.
+Ideally, these steps could be combined using `mice`, conditioning the imputations on both the missingness and the values that are to be synthesized.
+In practice, replacing observed and missing cells in a data set by synthetic values into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution.
 
 ```{r eval = FALSE}
-syn <- mice(boys, 
+syn <- mice(data.with.missings.to.synthesize, 
             m = 10,
@@
             where = matrix(TRUE, 
-                           nrow = nrow(boys),
-                           ncol = ncol(boys)))
+                           nrow = nrow(data.with.missings.to.synthesize),
+                           ncol = ncol(data.with.missings.to.synthesize)))
 ```
 
-Here, the argument `where` requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix) containing logicals $z_{ij}$ that indicate which cells are selected to have their values replaced by draws from the posterior predictive distribution.
-This approach allows to replace a subset of the observed data, or as in the aforementioned example, the observed data as a whole, resulting in a data set that partially or completely consists of synthetic data values.
-However, because the validity of this approach when the data suffers from missingness has not been investigated yet, we restrict ourselves in the following sections to a completely observed data set.However, because the validity of this approach has not been investigated yet, we restrict ourselves in the followi
+However, because the validity of this approach when the data suffers from missingness has not been investigated yet, we restrict ourselves in the following sections to a completely observed data set.
 
@@
 Imputation models should be as flexible as possible to capture most of the patterns in the data, and to model possibly unanticipated data characteristics [@murray_multiple_2018; @rubin_18years_1996].
-Parametric methods, albeit easy to implement in practice, may be too restrictive to capture generally complex patterns in the data, especially in the case of nonlinear relations and interactions between multiple variables.
-Classification and regression trees [CART\; @breiman_cart_1984] allow to model more complex patterns in the data, and have therefore been suggested as an appropriate imputation method [@reiter_cart_2005; @burgette_reiter_cart_2010; @doove_buuren_recursive_2014].
+Generally, multiple methods can be feasible, including joint modeling, sequential regression and FCS, all with different parameter specifications, depending on the imputation problem at hand [@ludtke2020regression; @yucel2018sequential; @murray2016multiple].
+Various simulations have shown that the most accurate imputation procedure may vary over different imputation problems [@hanne_review_2021].
+Hence, a one-size-fits-all solution does probably not exist.
+
+However, one of the methods that has shown a reasonable performance over multiple simulations uses FCS in combination with classification and regression trees [CART\; @breiman_cart_1984; @reiter_cart_2005; @burgette_reiter_cart_2010; @doove_buuren_recursive_2014; @raab_practical_2016].
+Due to its non-parametric nature, CART allows to model more complex patterns (e.g., interactions and non-linear relationships) in the data.
 Loosely speaking, CART sequentially splits the predictor space into non-overlapping regions in such a way that the within-region variance is as small as possible after every split.
@@
 ```{r eval = FALSE}
-syn <- mice(boys, 
+syn <- mice(data.to.synthesize, 
             m = 10,
-            maxit = 7, 
+            maxit = 1, 
             method = "cart",
@@
 Such factors are data dependent and should be considered by the imputer.
-In the next section, we will describe how the `boys` data can be adequately imputed.
+In the next section, we will describe how the `mice::boys` data [fredriks_boys_2000] can be adequately synthesized.
 Additionally, we will show through simulations that this approach yields valid inferences.
@@
 
-Usually, one would draw samples from a population that can be synthesized to evaluate the performance of the synthesization methods.
+Usually, one would draw samples from a population that can be synthesized to evaluate the performance of the synthetisation methods.
 As we only have access to a single sample, 1000 bootstrap samples of the `boys` data have been synthesized with $m = 5$ imputations for every data cell to induce an appropriate amount of sampling variance.
-Synthetic values are generated using the `CART` imputation method for all columns, except for `bmi`.
+This approach precludes us from knowing the *true* data-generating model, and in this sense provides a more stringent test of the applicability of `mice` for real-life synthetisation procedures.
+Specifically, every bootstrapped sample is treated as an actual sample from a population that is synthesized using `mice`, using a model that is built to approximate the true data-generating mechanisms as closely as possible.
+As relationships in realistic data are generally more complex than relationships in parametrically simulated data, achieving good performance on a real data set is likely to be more indicative of practical applicability than good performance on a parametrically simulated data set.
+
+In the simulations, synthetic values are generated using the `CART` imputation method for all columns, except for `bmi`.
 The deterministic relation `bmi` which will be synthesized passively based on the synthetic values for `hgt` and `wgt` to preserve the relation in the synthetic data.
@@
 One can calculate the average of the $m$ point estimates $q^{(l)}$
+
 $$
@@
 Hence, the according variance estimate for synthetic data as developed by @reiter_partially_inference_2003 yields
+
 $$
@@
 where $u^{(l)}$ denotes the variance estimate in the $l$th synthetic data set.
+These pooling rules are implemented in `mice` as the function `pool.syn`.
+@reiter_kinney_2012 proved that synthesizing data from the posterior predictive distribution is not required for these pooling rules to hold.
+In fact, the parameters of an imputation model can be fixed to their maximum likelihood estimates or their posterior modes, and synthetic values can be drawn after plugging these values into the imputation models.
+This observation as been taken a step further by @raab_practical_2016, who developed pooling rules that do not require multiple synthetic data sets and performed highly similar to the aforementioned pooling rules.
+However, we adhere to the originally proposed pooling rules by @reiter_partially_inference_2003, who defined the total variance in terms of sampling variance and between-imputation variance.
 
@@
 ```
+
 We evaluate the synthetic data with respect to the *true* data set on the basis of three aims.
@@
 
-The univariate descriptives for the original data and the synthetic data can be found in Table 2.
+The sampling distribution of the means of the continuous variables for both the bootstrapped and the synthetic data can be found in Figure 1, while the number of observations per category in the bootstrapped data and the averaged number of observations per category over the synthetic data sets can be found in Figure 2.
 
@@
 rownames(synth) <- paste("synthetic", rownames(synth), sep = " ")
+
+boot_stats_cont <- bootstrap_samples %>% 
+  map_dfr(~.x %>% 
+            select(where(is.numeric)) %>% 
+            pivot_longer(everything()) %>%
+            group_by(name) %>%
+            summarize(mean = mean(value)))
+
+syn_stats_cont <- synthetic_samples  %>%
+  map_dfr(~.x %>%
+            complete("long") %>%
+            select(c(age, hgt, wgt, bmi, hc, tv)) %>%
+            colMeans) %>%
+  pivot_longer(everything(), values_to = "mean")
+
+bind_rows(Boostrapped = boot_stats_cont, 
+          Synthetic = syn_stats_cont, 
+          .id = "Class") %>%
+  ggplot(aes(x = mean, col = Class, fill = Class)) +
+  geom_density(alpha = 0.5) +
+  facet_wrap(~name, scales = "free") +
+  theme_minimal() +
+  scale_fill_brewer(palette = "Set1") +
+  scale_color_brewer(palette = "Set1") +
+  labs(x = "Mean",
+       title = "Empirical sampling distribution of the mean.")
+```
+
+Both figures show that the marginal distributions of the bootstrapped data and the synthetic data are highly similar.
+Additionally, the univariate descriptives for the original data and the synthetic data can be found in Table 2.
+
+```{r univariate-statistics-II, echo = FALSE, cache = TRUE, results = FALSE}
+boot_stats_cat <- bootstrap_samples %>%
+  map_dfr(~.x %>%
+            select(!where(is.numeric)) %>%
+            mutate(across(everything(), as.character)) %>%
+            pivot_longer(everything()) %>% 
+            group_by(name, value) %>%
+            summarize(`Number of observations` = n(), .groups = "drop"))
+
+syn_stats_cat <- synthetic_samples %>%
+  map_dfr(~.x %>%
+            complete("long") %>%
+            select(c(gen, phb, reg)) %>%
+            mutate(across(everything(), as.character)) %>%
+            pivot_longer(everything()) %>%
+            group_by(name, value) %>%
+            summarize(`Number of observations` = n() / 5, .groups = "drop"))
+
+bind_rows(Boostrapped = boot_stats_cat, 
+          Synthetic = syn_stats_cat, 
+          .id = "Class") %>%
+  ggplot(aes(y = value, x = `Number of observations`, col = Class, group = Class)) +
+  geom_point(alpha = 0.1, position = position_jitterdodge(jitter.width = 0.2)) +
+  facet_wrap(~name, scales = "free") +
+  theme_minimal() +
+  scale_color_brewer(palette = "Set1") +
+  labs(x = "Number of observations per category",
+       title = "Distribution of data over different categories.")
 
@@
 \end{table}
+
 We see from Table 1 that the synthetic data estimates closely resemble the true data estimates.
@@
 
-We demonstrate that generating synthetic data sets with `mice` in `R` is a straightforward process that fits well in a data analysis pipeline.
+We demonstrate that generating synthetic data sets with `mice` using CART in `R` is a straightforward process that fits well in a data analysis pipeline.
 The approach is hardly different from using multiple imputation to solve problems related to missing data, and hence can be expected to be familiar to applied researchers.
@@
 This makes the multiple synthetisation procedure with `mice` suitable for further dissemination of synthetic data sets.
+It is important to note that in our simulations we used a single iteration and relied on CART as the imputation method.
+A single iteration is sufficient only when the true data is completely observed, or when the missingness pattern is monotone [@drechsler_synthetic_2011].
+If both observed and unobserved values are to be synthesized, then more iterations and a careful investigation into the convergence of the algorithm are in order.
+Synthetic data generation is therein no different than multiple imputation.
 
-To some, the procedure of generating multiple synthetic sets may seem overly complicated.
+However, when creating synthetic data with `mice`, close attention should be paid to three distinct aspects of the data: incorporating the additional uncertainty that is due synthesizing (part of) the data, potential disclosure risk that remain after synthesizing the data, and the utility of the synthetic data.
+First, the procedure of generating multiple synthetic sets may seem overly complicated.
 We would like to emphasize that analyzing a single synthesized set, while perhaps unbiased, would underestimate the variance properties that are so important in drawing statistical inferences from finite data sets.
@@
 Properly capturing the uncertainty of synthetic data sets, just like with incomplete data sets, is therefore paramount.
+To achieve this, we adopted a bootstrap scheme in our simulations, to represent sampling from a superpopulation.
+However, when a single sample should be the reference, in the sense that the sample reflects the population one wishes to make inferences about, adjusted pooling rules are required that are similar to the procedure outlined in @vink2014pooling.
+The corresponding pooling rules have not been derived yet and the incorporation in data analysis workflows would require proper attention from developers alike.
 
-Besides capturing uncertainty of synthetic data, it is important that imputers pay close attention to disclosure risks that remain after creating synthetic data sets.
+Second, it is important that imputers pay close attention to disclosure risks that remain after creating synthetic data sets.
 Creating synthetic data, unless generated from a completely parametric distribution, does not remove all potential disclosure risks.
 For example, if the values that ought to be replaced get the exact same value imputed, the synthetisation procedure has no use.
-
 Additionally, if not all variables in the data are synthesized, but the variables that are synthesized can be linked to open access data, a disclosure risk may remain [@drechsler2011empirical].
@@
 
-That said, while the fields of data disclosure control and data synthetisation originated decades ago, it is more relevant today than ever.
-In our study we outline a standard research workflow where the goal is to synthesize a complete data set.
-To simplify the simulation we adopted a bootstrapping scheme to induce sampling variance in order to conform to the combination procedure defined by @reiter_partially_inference_2003.
-Ideally, one would like to omit the bootstrap from the synthetisation to adopt a scheme where the sampled data itself serves as a reference: much like the procedure outlined in @vink2014pooling for incomplete data simulation.
-The corresponding pooling rules have not been derived yet and the incorporation in data analysis workflows would require proper attention from developers alike.
+Third, the utility of the synthetic data should receive considerable scrutiny.
+After all, synthetic data is generated to allow third parties without access to the data to make accurate inference.
+If the quality of the synthetic data is very poor, such accurate inferences are impossible.
+We showed that CART proved to be an adequate method for the data at hand.
+However, it may well be that for some problems, using CART for imputation is not the optimal strategy.
+We already demonstrated that imputing deterministic relationships should not be based on CART.
+However, due to the variety in possible imputation methods that have proved to perform well in varying circumstances, providing a single solution to all imputation problems seems impossible.
+If required, imputers could build up their imputation models in complexity.
+Nevertheless, similarly to past research [e.g., @burgette_reiter_cart_2010; @doove_buuren_recursive_2014; @raab_practical_2016], we showed that CART provides adequate results in general, and therefore serves as a good starting point.
 
-There exist other software that is capable of creating synthetic data.
-For example, the `synthpop` [@synthpop] package in `R` pioneered in the field of synthetic data generation in `R`, and contains many functionalities to create and evaluate synthetic data sets.
+After imputation, the quality of the synthetic data can be assessed using various utility measures.
+The simplest way to assess data quality is through visual inspection.
+However, visualizing more than two dimensions quickly becomes cumbersome, which makes it hard to assess the accuracy of multivariate relations.
+Trying to predict whether the data is observed or synthetic allows to get an intuition of the quality of the data.
+This procedure has been advanced by @snoke2018general, who proposed a measure of distributional similarity based on the mean squared error of propensity scores indicating class belonging for both observed and synthetic data.
+This method has been implemented in the `R`-package `synthpop` [@synthpop], who pioneered in the field of synthetic data generation in `R`.
+
 However, although `synthpop` is capable to synthesize regardless of missing data, it cannot solve eventual missingness problems.
@@
 Although efforts have been made to bridge gaps between the packages [e.g., @miceadds_3.11-6], further improvements could be made in that respect.
-Specifically, `synthpop` contains a wide variety of functions that can be used to assess the quality of synthetic data [e.g., see ADD SNOKE REFERENCE + ARXIV], while `mice` contains methods to impute multilevel data.
+Specifically, `synthpop` contains a wide variety of functions that can be used to assess the quality of synthetic data [e.g., @snoke2018general], while `mice` contains methods to impute multilevel data.
 Being able to use such functionality interchangeably would greatly benefit the public.
 
-It is important to note that in our simulations we used a single iteration.
-A single iteration is sufficient only when the true data is completely observed, or when the missingness pattern is monotone [@drechsler_synthetic_2011].
-If both observed and unobserved values are to be synthesized, then more iterations and a careful investigation into the convergence of the algorithm are in order.
-Synthetic data generation with `mice` is therein no different than multiple imputation.
-
 The ease of use when synthesizing data with `mice` in `R`, together with the validity of inferences obtained through this procedure opens up a wealth of possibilities for data dissemination and further research of initially private data.

### 2021-10-27 manuscript/Manuscript.tex
Incorporate reviewer comments.

@@
 
-\hypertarget{add-reviewer-name}{%
-\section{ADD REVIEWER NAME}\label{add-reviewer-name}}
-
 \hypertarget{introduction}{%
@@
 disclosed. While in practice, one could see this as replacing the
-observed data values by multiple draws from the posterior predictive
-distribution of the observed data, based on some imputation model, Rubin
-would argue that these synthetic data values are merely draws from the
-same true data generating model. In that sense, the observed data is
-never replaced, but the population is resampled from the information
-captured in the (incomplete) sample. Using this approach, the researcher
-could replace the observed data set as a whole with multiple synthetic
+observed data values by multiple draws from the predictive distribution
+of the observed data, based on some imputation model, Rubin would argue
+that these synthetic data values are merely draws from the same true
+data generating model. In that sense, the observed data is never
+replaced, but the population is resampled from the information captured
+in the (incomplete) sample. Using this approach, the researcher could
+replace the observed data set as a whole with multiple synthetic
 versions. Alternatively, the researcher could opt to only replace a
@@
 \citet{rubin_multiple_1987}. Instead of replacing just the missing
-values with multiple draws from the posterior predictive distribution,
-one could easily replace any observed sensitive values. Similarly to
-multiple imputation of missing data, the multiple synthetic data sets
-allow for correct statistical inferences, despite the fact that the
-analyses do not use the ``true'' value. The analyses over multiple
-synthetic data sets should be pooled into a single inference, so that
-the researcher can draw valid conclusions from the pooled results. To
-that respect, the variance should reflect the added variability that is
-induced by the imputation procedure.
-
-Potentially, this approach could fulfill the needs for openly accessibly
+values, one could easily replace any observed sensitive values by
+multiple draws from the posterior predictive distribution - or a
+non-Bayesian predictive distribution. We will refer to both of these as
+predictive distributions. Similarly to multiple imputation of missing
+data, the multiple synthetic data sets allow for correct statistical
+inferences, despite the fact that the analyses do not use the ``true''
+value. The analyses over multiple synthetic data sets should be pooled
+into a single inference, so that the researcher can draw valid
+conclusions from the pooled results. To that respect, the variance
+should reflect the added variability that is induced by the imputation
+procedure.
+
+Potentially, this approach could fulfil the needs for openly accessible
 data, without running into barriers with regard to privacy and
@@
 synthetic data. The quality of the synthetic data is highly dependent on
-the imputation models, and using flawed models to generate synthetic
-data might bias subsequent analyses
+the imputation models, and using flawed imputation models might bias
+subsequent analyses
 \citep{reiter2004simultaneous, grund2021using, jiang2021balancing}.
-Conversely, if the models used to create the synthetic data are able to
+Conversely, if the models used to synthesize the data are able to
 preserve the relationships between the variables as in the original
 data, the synthetic data can be nearly as informative as the observed
-data. Thus, to fully exploit the benefits of synthetic data, additional
-complications to actually create these high-quality data sets should be
-kept at a minimum.
+data. To fully exploit the benefits of synthetic data, complicating
+aspects of creating high-quality synthetic data sets should be kept at a
+minimum, while keeping the accuracy of the models as high as possible.
 
@@
 
+Generally, there are three ways to impute data: joint modeling,
+sequential modeling and fully conditional specification
+\citep{murray_multiple_2018, ludtke2020regression, grund2021using}. With
+joint modeling, the entire joint distribution of the data is specified
+as a single multivariate distribution, and the imputations are drawn
+from this model. This strategy is implemented in, among others, the
+\texttt{R}-package \texttt{jomo} \citep{jomo} to deal with missing data.
+However, when the structure of the data increases in complexity,
+specifying a single multivariate distribution can become cumbersome. A
+more flexible solution has been proposed in sequential regression
+imputation, in which the multivariate distribution is separated into
+univariate distributions for every variable. Every single variable is
+then imputed conditional on a model containing only the variables in the
+sequence located before the variable to be imputed. This approach has
+been implemented in the R-packages \texttt{mdmb} \citep{mdmb} for
+imputation of missing data and \texttt{synthpop} \citep{synthpop} for
+imputation of synthetic data.
+
 The \texttt{mice} package \citep{mice} in \texttt{R} \citep{Rproject}
@@
 to nonresponse. In that context, the aim is to replace missing values
-with plausible values from the posterior predictive distribution of that
-variable. In \texttt{mice}, this is accomplished using fully conditional
+with plausible values from the predictive distribution of that variable.
+In \texttt{mice}, this is accomplished using fully conditional
 specification (FCS) \citep{vanbuuren_fully_2006}, which breaks down the
@@
 constructed for every incomplete variable and the missing values
-\(Y_{j, mis}\) are then imputed with draws from the posterior predictive
+\(Y_{j, mis}\) are then imputed with draws from the predictive
 distribution of \(P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)\) on a
@@
 for unobserved values is straightforward. The following pseudocode
-details the multiple imputation of the \texttt{mice::boys} data set
-\citep{fredriks_boys_2000} into the object \texttt{imp} with
-\texttt{m\ =\ 10} imputated sets and \texttt{maxit\ =\ 7} iterations for
-the algorithm to converge, using the default imputations methods given
-each column's data class.
+details multiple imputation of any data set that contains missingness
+into the object \texttt{imp} with \texttt{m\ =\ 10} imputated sets and
+\texttt{maxit\ =\ 7} iterations for the algorithm to converge, using the
+default imputations methods.
 
@@
 \FunctionTok{library}\NormalTok{(mice)}
-\NormalTok{imp }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(boys, }
+\NormalTok{imp }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(data.with.missings, }
             \AttributeTok{m =} \DecValTok{10}\NormalTok{,}
@@
 
-It is straightforward to extend the imputation approach to generate
-synthetic values. Rather than imputing missing data, the observed values
-are then replaced by synthetic draws from the posterior predictive
+The imputation approach in \texttt{mice} can be easily extended to
+generate synthetic values. Rather than imputing missing data, observed
+values are then replaced by synthetic draws from the predictive
 distribution. For simplicity, assume that the data is completely
@@
 \(\textbf{Y} = (\textbf{Y}_{rep}, \textbf{Y}_{nrep})\). Now, instead of
-imputing \(\textbf{Y}_{mis}\) with draws from the posterior predictive
+imputing \(\textbf{Y}_{mis}\) with draws from the predictive
 distribution of \(P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)\) as in the
@@
 Note that, given a completely observed data set, iterating over the
-posterior predictive distribution is not required.
+predictive distribution is not required.
+
+Hence, creating synthetic values for a completely observed data set into
+the object \texttt{syn}, given the same imputation parameters as
+specified above, can be realized as follows:
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\FunctionTok{library}\NormalTok{(mice)}
+\NormalTok{imp }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(data.to.synthesize, }
+            \AttributeTok{m =} \DecValTok{10}\NormalTok{,}
+            \AttributeTok{maxit =} \DecValTok{1}\NormalTok{,}
+            \AttributeTok{where =} \FunctionTok{matrix}\NormalTok{(}\ConstantTok{TRUE}\NormalTok{,}
+                           \AttributeTok{nrow =} \FunctionTok{nrow}\NormalTok{(data.to.synthesize),}
+                           \AttributeTok{ncol =} \FunctionTok{ncol}\NormalTok{(data.to.synthetize)))}
+\end{Highlighting}
+\end{Shaded}
+
+Here, the argument \texttt{where} requires a matrix of the same
+dimensions as the data, (i.e., a \(n \times k\) matrix) containing
+logicals \(z_{ij}\) that indicate which cells are selected to have their
+values replaced by draws from the predictive distribution. This approach
+allows to replace a subset of the observed data (e.g., by only
+specifying those cells that are to be replaced as \texttt{TRUE} in the
+\texttt{where}-matrix, leaving the rest to \texttt{FALSE}), or as in the
+aforementioned example, the observed data as a whole, resulting in a
+data set that partially or completely consists of synthetic data values.
+Note that because the data is completely observed, iterating over the
+predictive distribution is not required.
 
@@
 data, while in a second step, the synthetic data is imputed conform the
-corresponding procedure. Intuitively, these steps could be combined
-using \texttt{mice}, conditioning the imputations on both the
-missingness and the values that are to be synthesized. In practice,
-replacing observed and missing cells in the \texttt{mice::boys} data set
-by synthetic values into the object \texttt{syn}, given the same
-imputation parameters as before, can be realized by the following code
-execution.
+corresponding procedure. Ideally, these steps could be combined using
+\texttt{mice}, conditioning the imputations on both the missingness and
+the values that are to be synthesized. In practice, replacing observed
+and missing cells in a data set by synthetic values into the object
+\texttt{syn}, given the same imputation parameters as before, can be
+realized by the following code execution.
 
@@
 \begin{Highlighting}[]
-\NormalTok{syn }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(boys, }
+\NormalTok{syn }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(data.with.missings.to.synthesize, }
             \AttributeTok{m =} \DecValTok{10}\NormalTok{,}
@@
             \AttributeTok{where =} \FunctionTok{matrix}\NormalTok{(}\ConstantTok{TRUE}\NormalTok{, }
-                           \AttributeTok{nrow =} \FunctionTok{nrow}\NormalTok{(boys),}
-                           \AttributeTok{ncol =} \FunctionTok{ncol}\NormalTok{(boys)))}
+                           \AttributeTok{nrow =} \FunctionTok{nrow}\NormalTok{(data.with.missings.to.synthesize),}
+                           \AttributeTok{ncol =} \FunctionTok{ncol}\NormalTok{(data.with.missings.to.synthesize)))}
 \end{Highlighting}
@@
 
-Here, the argument \texttt{where} requires a matrix of the same
-dimensions as the data, (i.e., a \(n \times k\) matrix) containing
-logicals \(z_{ij}\) that indicate which cells are selected to have their
-values replaced by draws from the posterior predictive distribution.
-This approach allows to replace a subset of the observed data, or as in
-the aforementioned example, the observed data as a whole, resulting in a
-data set that partially or completely consists of synthetic data values.
 However, because the validity of this approach when the data suffers
 from missingness has not been investigated yet, we restrict ourselves in
-the following sections to a completely observed data set.However,
-because the validity of this approach has not been investigated yet, we
-restrict ourselves in the followi
+the following sections to a completely observed data set.
 
@@
 data, and to model possibly unanticipated data characteristics
-\citep{murray_multiple_2018, rubin_18years_1996}. Parametric methods,
-albeit easy to implement in practice, may be too restrictive to capture
-generally complex patterns in the data, especially in the case of
-nonlinear relations and interactions between multiple variables.
-Classification and regression trees \citep[CART;][]{breiman_cart_1984}
-allow to model more complex patterns in the data, and have therefore
-been suggested as an appropriate imputation method
-\citep{reiter_cart_2005, burgette_reiter_cart_2010, doove_buuren_recursive_2014}.
+\citep{murray_multiple_2018, rubin_18years_1996}. Generally, multiple
+methods can be feasible, including joint modeling, sequential regression
+and FCS, all with different parameter specifications, depending on the
+imputation problem at hand
+\citep{ludtke2020regression, yucel2018sequential, murray2016multiple}.
+Various simulations have shown that the most accurate imputation
+procedure may vary over different imputation problems
+\citep{hanne_review_2021}. Hence, a one-size-fits-all solution does
+probably not exist.
+
+However, one of the methods that has shown a reasonable performance over
+multiple simulations uses FCS in combination with classification and
+regression trees
+\citep[CART;][]{breiman_cart_1984, reiter_cart_2005, burgette_reiter_cart_2010, doove_buuren_recursive_2014, raab_practical_2016}.
+Due to its non-parametric nature, CART allows to model more complex
+patterns (e.g., interactions and non-linear relationships) in the data.
 Loosely speaking, CART sequentially splits the predictor space into
@@
 \begin{Highlighting}[]
-\NormalTok{syn }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(boys, }
+\NormalTok{syn }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(data.to.synthesize, }
             \AttributeTok{m =} \DecValTok{10}\NormalTok{,}
-            \AttributeTok{maxit =} \DecValTok{7}\NormalTok{, }
+            \AttributeTok{maxit =} \DecValTok{1}\NormalTok{, }
             \AttributeTok{method =} \StringTok{"cart"}\NormalTok{,}
@@
 dependent and should be considered by the imputer. In the next section,
-we will describe how the \texttt{boys} data can be adequately imputed.
-Additionally, we will show through simulations that this approach yields
-valid inferences.
+we will describe how the \texttt{mice::boys} data
+{[}fredriks\_boys\_2000{]} can be adequately synthesized. Additionally,
+we will show through simulations that this approach yields valid
+inferences.
 
@@
 Usually, one would draw samples from a population that can be
-synthesized to evaluate the performance of the synthesization methods.
+synthesized to evaluate the performance of the synthetisation methods.
 As we only have access to a single sample, 1000 bootstrap samples of the
@@
 every data cell to induce an appropriate amount of sampling variance.
-Synthetic values are generated using the \texttt{CART} imputation method
-for all columns, except for \texttt{bmi}. The deterministic relation
-\texttt{bmi} which will be synthesized passively based on the synthetic
-values for \texttt{hgt} and \texttt{wgt} to preserve the relation in the
-synthetic data. Additional parameters that come with the use of
-\texttt{mice.impute.cart()} are the complexity parameter \texttt{cp} and
-the minimum number of observations in any terminal node
-\texttt{minbucket}, that both constrain the flexibility of the
-imputation model. The values of the parameters \texttt{cp} and
-\texttt{minbucket} ought to adhere to the call for imputation models
-that are as flexible as possible. Appropriate values for these
-parameters, as well as the input for the \texttt{predictorMatrix},
-depend on the data at hand. In the current example, the complexity
-parameter is specified at \texttt{cp\ =\ 1e-08} rather than the default
-value \texttt{1e-04}, and the minimum number of observations in each
-terminal node is set at \texttt{minbucket} \(= 3\) rather than the
-default value \(5\). By allowing for more complexity in the imputation
-model, bias in the estimates from the synthetic data set is reduced.
-Additionally, since the synthesis pattern is monotone, the number of
-iterations can be set to \texttt{maxit\ =\ 1} \citep[e.g.,][Ch.
-3]{drechsler_synthetic_2011}.
+This approach precludes us from knowing the \emph{true} data-generating
+model, and in this sense provides a more stringent test of the
+applicability of \texttt{mice} for real-life synthetisation procedures.
+Specifically, every bootstrapped sample is treated as an actual sample
+from a population that is synthesized using \texttt{mice}, using a model
+that is built to approximate the true data-generating mechanisms as
+closely as possible. As relationships in realistic data are generally
+more complex than relationships in parametrically simulated data,
+achieving good performance on a real data set is likely to be more
+indicative of practical applicability than good performance on a
+parametrically simulated data set.
+
+In the simulations, synthetic values are generated using the
+\texttt{CART} imputation method for all columns, except for
+\texttt{bmi}. The deterministic relation \texttt{bmi} which will be
+synthesized passively based on the synthetic values for \texttt{hgt} and
+\texttt{wgt} to preserve the relation in the synthetic data. Additional
+parameters that come with the use of \texttt{mice.impute.cart()} are the
+complexity parameter \texttt{cp} and the minimum number of observations
+in any terminal node \texttt{minbucket}, that both constrain the
+flexibility of the imputation model. The values of the parameters
+\texttt{cp} and \texttt{minbucket} ought to adhere to the call for
+imputation models that are as flexible as possible. Appropriate values
+for these parameters, as well as the input for the
+\texttt{predictorMatrix}, depend on the data at hand. In the current
+example, the complexity parameter is specified at \texttt{cp\ =\ 1e-08}
+rather than the default value \texttt{1e-04}, and the minimum number of
+observations in each terminal node is set at \texttt{minbucket} \(= 3\)
+rather than the default value \(5\). By allowing for more complexity in
+the imputation model, bias in the estimates from the synthetic data set
+is reduced. Additionally, since the synthesis pattern is monotone, the
+number of iterations can be set to \texttt{maxit\ =\ 1}
+\citep[e.g.,][Ch. 3]{drechsler_synthetic_2011}.
 
@@
 case of missing data \citep{rubin_multiple_1987}. One can calculate the
-average of the \(m\) point estimates \(q^{(l)}\) \[
+average of the \(m\) point estimates \(q^{(l)}\)
+
+\[
 \bar{q}_m = \sum_{l = 1}^m \frac{q^{(l)}}{m},
@@
 observed data. Hence, the according variance estimate for synthetic data
-as developed by \citet{reiter_partially_inference_2003} yields \[
+as developed by \citet{reiter_partially_inference_2003} yields
+
+\[
 T = \bar{u}_m + \frac{b_m}{m},
@@
 \] where \(u^{(l)}\) denotes the variance estimate in the \(l\)th
-synthetic data set.
+synthetic data set. These pooling rules are implemented in \texttt{mice}
+as the function \texttt{pool.syn}. \citet{reiter_kinney_2012} proved
+that synthesizing data from the posterior predictive distribution is not
+required for these pooling rules to hold. In fact, the parameters of an
+imputation model can be fixed to their maximum likelihood estimates or
+their posterior modes, and synthetic values can be drawn after plugging
+these values into the imputation models. This observation as been taken
+a step further by \citet{raab_practical_2016}, who developed pooling
+rules that do not require multiple synthetic data sets and performed
+highly similar to the aforementioned pooling rules. However, we adhere
+to the originally proposed pooling rules by
+\citet{reiter_partially_inference_2003}, who defined the total variance
+in terms of sampling variance and between-imputation variance.
 
@@
 
-The univariate descriptives for the original data and the synthetic data
-can be found in Table 2.
+The sampling distribution of the means of the continuous variables for
+both the bootstrapped and the synthetic data can be found in Figure 1,
+while the number of observations per category in the bootstrapped data
+and the averaged number of observations per category over the synthetic
+data sets can be found in Figure 2.
+
+\includegraphics{Manuscript_files/figure-latex/univariate-statistics-1.pdf}
+
+Both figures show that the marginal distributions of the bootstrapped
+data and the synthetic data are highly similar. Additionally, the
+univariate descriptives for the original data and the synthetic data can
+be found in Table 2.
+
+\includegraphics{Manuscript_files/figure-latex/univariate-statistics-II-1.pdf}
 
@@
 
-We demonstrate that generating synthetic data sets with \texttt{mice} in
-\texttt{R} is a straightforward process that fits well in a data
-analysis pipeline. The approach is hardly different from using multiple
-imputation to solve problems related to missing data, and hence can be
-expected to be familiar to applied researchers. The multiple synthetic
-sets yield valid inferences on the true underlying data generating
-mechanism, thereby capturing the nature of the original data. This makes
-the multiple synthetisation procedure with \texttt{mice} suitable for
-further dissemination of synthetic data sets.
-
-To some, the procedure of generating multiple synthetic sets may seem
-overly complicated. We would like to emphasize that analyzing a single
-synthesized set, while perhaps unbiased, would underestimate the
-variance properties that are so important in drawing statistical
-inferences from finite data sets. After all, we are often not interested
-in the sample at hand, but aim to make inferences about the underlying
-data generating mechanism as reflected in the population. Properly
-capturing the uncertainty of synthetic data sets, just like with
-incomplete data sets, is therefore paramount.
-
-Besides capturing uncertainty of synthetic data, it is important that
-imputers pay close attention to disclosure risks that remain after
-creating synthetic data sets. Creating synthetic data, unless generated
-from a completely parametric distribution, does not remove all potential
-disclosure risks. For example, if the values that ought to be replaced
-get the exact same value imputed, the synthetisation procedure has no
-use.
-
-Additionally, if not all variables in the data are synthesized, but the
-variables that are synthesized can be linked to open access data, a
-disclosure risk may remain \citep{drechsler2011empirical}. If the open
-access data allows for identification, and the corresponding
-observations in the synthetic data can be identified, the variables that
-are not synthesized may provide information that should not have been
-disseminated. The associated problems generally decrease when the
-sensitive variables are synthesized as well. Still, it is important to
-remain critical regarding the extent to which the synthetic data might
-be disclosive. The practical development of easy to use software to
-identify which observations are at risk of disclosure is an area of
-future work that can improve these issues. Subsequently, the
-implementation of ways to overcome such problems once detected, for
-example by record swapping as suggested by \citet{jiang2021balancing},
-is welcomed.
-
-That said, while the fields of data disclosure control and data
-synthetisation originated decades ago, it is more relevant today than
-ever. In our study we outline a standard research workflow where the
-goal is to synthesize a complete data set. To simplify the simulation we
-adopted a bootstrapping scheme to induce sampling variance in order to
-conform to the combination procedure defined by
-\citet{reiter_partially_inference_2003}. Ideally, one would like to omit
-the bootstrap from the synthetisation to adopt a scheme where the
-sampled data itself serves as a reference: much like the procedure
-outlined in \citet{vink2014pooling} for incomplete data simulation. The
-corresponding pooling rules have not been derived yet and the
-incorporation in data analysis workflows would require proper attention
-from developers alike.
-
-There exist other software that is capable of creating synthetic data.
-For example, the \texttt{synthpop} \citep{synthpop} package in
-\texttt{R} pioneered in the field of synthetic data generation in
-\texttt{R}, and contains many functionalities to create and evaluate
-synthetic data sets. However, although \texttt{synthpop} is capable to
-synthesize regardless of missing data, it cannot solve eventual
-missingness problems. If the data for synthetisation contains missing
-values, the missingness will be considered as a property of the data,
-and the corresponding synthetic data sets will contain missing values as
-well. If the goal is to impute and synthesize a data set, a two-step
-approach must be used, in which the missing values are imputed using a
-different package, like \texttt{mice}, after which \texttt{synthpop} can
-be used to synthesize the imputed data. Then, given \(m\) multiple
-imputations and \(r\) synthetisations, at least \(m \times r\) synthetic
-data sets are in order, after which the data can be analysed and the
-analyses can be pooled using rules developed by
-\citet{reiter2004simultaneous}. However, such an approach would be
-computationally inefficient and practically cumbersome, because the
-architectures of both packages differ.
+We demonstrate that generating synthetic data sets with \texttt{mice}
+using CART in \texttt{R} is a straightforward process that fits well in
+a data analysis pipeline. The approach is hardly different from using
+multiple imputation to solve problems related to missing data, and hence
+can be expected to be familiar to applied researchers. The multiple
+synthetic sets yield valid inferences on the true underlying data
+generating mechanism, thereby capturing the nature of the original data.
+This makes the multiple synthetisation procedure with \texttt{mice}
+suitable for further dissemination of synthetic data sets. It is
+important to note that in our simulations we used a single iteration and
+relied on CART as the imputation method. A single iteration is
+sufficient only when the true data is completely observed, or when the
+missingness pattern is monotone \citep{drechsler_synthetic_2011}. If
+both observed and unobserved values are to be synthesized, then more
+iterations and a careful investigation into the convergence of the
+algorithm are in order. Synthetic data generation is therein no
+different than multiple imputation.
+
+However, when creating synthetic data with \texttt{mice}, close
+attention should be paid to three distinct aspects of the data:
+incorporating the additional uncertainty that is due synthesizing (part
+of) the data, potential disclosure risk that remain after synthesizing
+the data, and the utility of the synthetic data. First, the procedure of
+generating multiple synthetic sets may seem overly complicated. We would
+like to emphasize that analyzing a single synthesized set, while perhaps
+unbiased, would underestimate the variance properties that are so
+important in drawing statistical inferences from finite data sets. After
+all, we are often not interested in the sample at hand, but aim to make
+inferences about the underlying data generating mechanism as reflected
+in the population. Properly capturing the uncertainty of synthetic data
+sets, just like with incomplete data sets, is therefore paramount. To
+achieve this, we adopted a bootstrap scheme in our simulations, to
+represent sampling from a superpopulation. However, when a single sample
+should be the reference, in the sense that the sample reflects the
+population one wishes to make inferences about, adjusted pooling rules
+are required that are similar to the procedure outlined in
+\citet{vink2014pooling}. The corresponding pooling rules have not been
+derived yet and the incorporation in data analysis workflows would
+require proper attention from developers alike.
+
+Second, it is important that imputers pay close attention to disclosure
+risks that remain after creating synthetic data sets. Creating synthetic
+data, unless generated from a completely parametric distribution, does
+not remove all potential disclosure risks. For example, if the values
+that ought to be replaced get the exact same value imputed, the
+synthetisation procedure has no use. Additionally, if not all variables
+in the data are synthesized, but the variables that are synthesized can
+be linked to open access data, a disclosure risk may remain
+\citep{drechsler2011empirical}. If the open access data allows for
+identification, and the corresponding observations in the synthetic data
+can be identified, the variables that are not synthesized may provide
+information that should not have been disseminated. The associated
+problems generally decrease when the sensitive variables are synthesized
+as well. Still, it is important to remain critical regarding the extent
+to which the synthetic data might be disclosive. The practical
+development of easy to use software to identify which observations are
+at risk of disclosure is an area of future work that can improve these
+issues. Subsequently, the implementation of ways to overcome such
+problems once detected, for example by record swapping as suggested by
+\citet{jiang2021balancing}, is welcomed.
+
+Third, the utility of the synthetic data should receive considerable
+scrutiny. After all, synthetic data is generated to allow third parties
+without access to the data to make accurate inference. If the quality of
+the synthetic data is very poor, such accurate inferences are
+impossible. We showed that CART proved to be an adequate method for the
+data at hand. However, it may well be that for some problems, using CART
+for imputation is not the optimal strategy. We already demonstrated that
+imputing deterministic relationships should not be based on CART.
+However, due to the variety in possible imputation methods that have
+proved to perform well in varying circumstances, providing a single
+solution to all imputation problems seems impossible. If required,
+imputers could build up their imputation models in complexity.
+Nevertheless, similarly to past research
+\citep[e.g.,][]{burgette_reiter_cart_2010, doove_buuren_recursive_2014, raab_practical_2016},
+we showed that CART provides adequate results in general, and therefore
+serves as a good starting point.
+
+After imputation, the quality of the synthetic data can be assessed
+using various utility measures. The simplest way to assess data quality
+is through visual inspection. However, visualizing more than two
+dimensions quickly becomes cumbersome, which makes it hard to assess the
+accuracy of multivariate relations. Trying to predict whether the data
+is observed or synthetic allows to get an intuition of the quality of
+the data. This procedure has been advanced by \citet{snoke2018general},
+who proposed a measure of distributional similarity based on the mean
+squared error of propensity scores indicating class belonging for both
+observed and synthetic data. This method has been implemented in the
+\texttt{R}-package \texttt{synthpop} \citep{synthpop}, who pioneered in
+the field of synthetic data generation in \texttt{R}.
+
+However, although \texttt{synthpop} is capable to synthesize regardless
+of missing data, it cannot solve eventual missingness problems. If the
+data for synthetisation contains missing values, the missingness will be
+considered as a property of the data, and the corresponding synthetic
+data sets will contain missing values as well. If the goal is to impute
+and synthesize a data set, a two-step approach must be used, in which
+the missing values are imputed using a different package, like
+\texttt{mice}, after which \texttt{synthpop} can be used to synthesize
+the imputed data. Then, given \(m\) multiple imputations and \(r\)
+synthetisations, at least \(m \times r\) synthetic data sets are in
+order, after which the data can be analysed and the analyses can be
+pooled using rules developed by \citet{reiter2004simultaneous}. However,
+such an approach would be computationally inefficient and practically
+cumbersome, because the architectures of both packages differ.
 
@@
 \texttt{synthpop} contains a wide variety of functions that can be used
-to assess the quality of synthetic data {[}e.g., see ADD SNOKE REFERENCE
-+ ARXIV{]}, while \texttt{mice} contains methods to impute multilevel
-data. Being able to use such functionality interchangeably would greatly
-benefit the public.
-
-It is important to note that in our simulations we used a single
-iteration. A single iteration is sufficient only when the true data is
-completely observed, or when the missingness pattern is monotone
-\citep{drechsler_synthetic_2011}. If both observed and unobserved values
-are to be synthesized, then more iterations and a careful investigation
-into the convergence of the algorithm are in order. Synthetic data
-generation with \texttt{mice} is therein no different than multiple
-imputation.
+to assess the quality of synthetic data
+\citep[e.g.,][]{snoke2018general}, while \texttt{mice} contains methods
+to impute multilevel data. Being able to use such functionality
+interchangeably would greatly benefit the public.
 
@@
 Broek for replicating the simulation study on an independent data set.
-Additionally, we thank Hanne Oberman, {[}{[}NOT ANONYMOUS REVIEWER{]}{]}
-and an anonymous reviewer for their stimulating comments.}
+Additionally, we thank Hanne Oberman and two anonymous reviewers for
+their stimulating comments.}
 

### 2021-10-27 manuscript/Blind/Manuscript.Rmd

--- 2021-10-26 manuscript/Manuscript.Rmd
@@
 title: "Anony*mice*d shareable data: Using *mice* to create and analyze multiply imputed synthetic data sets"
-author:
-  - name: Thom Volker
-    affil: 1,*, \dagger
-    orcid: 0000-0002-2408-7820
-  - name: Gerko Vink
-    affil: 1, \dagger
-    orcid: 0000-0001-9767-1924
-affiliation:
-  - num: 1
-    address: |
-      Utrecht University - 
-      Department of Methodology and Statistics. 
-      Padualaan 14. 3584CH Utrecht, the Netherlands
+
 # firstnote to eighthnote
@@
   These authors contributed equally to this work.
-correspondence: |
-  t.b.volker@uu.nl.
 journal: psych
@@
   mice; imputation; synthetic data.
-acknowledgement: |
-  We are grateful to Mirthe Hendriks and Stijn van den Broek for replicating the 
-  simulation study on an independent data set. Additionally, we thank Hanne Oberman, [[NOT ANONYMOUS REVIEWER]] and an anonymous reviewer for their stimulating comments.
 authorcontributions: |
@@
 sampleavailability: |
-  A full simulation archive is available from https://github.com/amices/Federated_imputation/tree/master/manuscript.
+  A full simulation archive is available from the zip-enclosed RMD file
 output: rticles::mdpi_article
 ---
-
-# ADD REVIEWER NAME
 
@@
 Collecting research data requires an enormous investment both in terms of time and monetary resources.
-Disseminating the research data bears the potential of increasing the scientific returns for the same data collection effort tremendously.
+Openly accessible research data bears the potential of increasing the scientific returns for the same data collection effort.
 Additionally, the fact that public funds are used for data collection results in increasing demand for access to the collected data.
@@
 Conceptually, the synthetic data framework is based upon the building blocks of multiple imputation of missing data, as proposed by @rubin_multiple_1987.
-Instead of replacing just the missing values with multiple draws from the posterior predictive distribution, one could easily replace any observed sensitive values.
+Instead of replacing just the missing values with multiple draws from the posterior predictive distribution, one could easily *overimpute* any observed sensitive values.
 Similarly to multiple imputation of missing data, the multiple synthetic data sets allow for correct statistical inferences, despite the fact that the analyses do not use the "true" value.
@@
 However, the functionality of `mice` is not restricted to the imputation of missing data, but allows to impute any value in the data: even observed values.
-Consequently, `mice` can be used for the creation of multiply imputed synthetic data sets.
+Consequently, `mice` can be utilized for the creation of multiply imputed synthetic data sets.
 
@@
 In `mice`, the generation of multiply imputed data sets to solve for unobserved values is straightforward.
-The following pseudocode details the multiple imputation of the `mice::boys` data set [@fredriks_boys_2000] into the object `imp` with `m = 10` imputated sets and `maxit = 7` iterations for the algorithm to converge, using the default imputations methods given each column's data class.
+The following pseudocode details the multiple imputation of the `mice::boys` data set [@fredriks_boys_2000] into the object `imp` with `m = 10` imputated sets and `maxit = 7` iterations for the algorithm to converge, using the default imputations methods for each column data class.
 
@@
 For simplicity, assume that the data is completely observed (i.e., $\textbf{Y} = \textbf{Y}_{obs}$).
-Following the notation of @reiter_raghunathan_multiple_2007, let, given $n$ observations, $Z_i = 1$ if any of the values of unit $i = 1, 2, \dots, n$, are to be replaced by imputations, and $Z_i = 0$ otherwise, with $\textbf{Z} = (Z_1, Z_2, \dots, Z_n)$.
+Following the notation of @reiter_raghunathan_multiple_2007, let for $n$ units denote $Z_i = 1$ if any of the values of unit $i = 1, 2, \dots, n$ are to be replaced by imputations, and $Z_i = 0$ otherwise, with $\textbf{Z} = (Z_1, Z_2, \dots, Z_n)$.
 Accordingly, the data consists of values that are to be replaced and values that are to be kept (i.e., $\textbf{Y} = (\textbf{Y}_{rep}, \textbf{Y}_{nrep})$.
 Now, instead of imputing $\textbf{Y}_{mis}$ with draws from the posterior predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, $\textbf{Y}_{rep}$ is imputed from the posterior distribution of $P(Y^{(l)}_{j, rep} | \textbf{Y}^{(l)}_{-j}, \textbf{Z}, \theta)$, where $l$ is an indicator for the synthetic data set ($l = 1, 2, \dots, m$).
-The synthetic values that are imputed at an earlier step can be used for imputing variable $j$.
+Note that synthetic values that are imputed at an earlier step can be used for imputing variable $j$.
 This process results in the synthetic data $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$.
-Note that, given a completely observed data set, iterating over the posterior predictive distribution is not required.
 
-If the goal is to create synthetic versions of a data set that suffers from missingness, the imputation procedure becomes more complex.
-A two-step imputation procedure has been proposed by @reiter2004simultaneous.
-In the first step, the missing data is imputed according to the principles of multiple imputation for missing data, while in a second step, the synthetic data is imputed conform the corresponding procedure.
-Intuitively, these steps could be combined using `mice`, conditioning the imputations on both the missingness and the values that are to be synthesized.
-In practice, replacing observed and missing cells in the `mice::boys` data set by synthetic values into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution.
+For example, overimputing synthetic values for both the observed and missing cells in the `mice::boys` data set into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution.
 
@@
 
-Here, the argument `where` requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix) containing logicals $z_{ij}$ that indicate which cells are selected to have their values replaced by draws from the posterior predictive distribution.
-This approach allows to replace a subset of the observed data, or as in the aforementioned example, the observed data as a whole, resulting in a data set that partially or completely consists of synthetic data values.
-However, because the validity of this approach when the data suffers from missingness has not been investigated yet, we restrict ourselves in the following sections to a completely observed data set.However, because the validity of this approach has not been investigated yet, we restrict ourselves in the followi
+where the argument `where` requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix) containing logicals $z_{ij}$ that indicate which cells are selected to have their values replaced by draws from the posterior predictive distribution.
+This approach allows to overimpute a subset of the observed data, or as in the above example, the observed data as a whole, resulting in a data set that partially or completely consists of synthetic data values.
 
@@
 Also similarly to the missing data case, variances, and subsequently confidence intervals, should incorporate the increase in variance that is due to imputation [@reiter_partially_inference_2003; @drechsler_synthetic_2011].
-Yet, the increase in variance due to imputation differs according to whether missing values are imputed or observed data is replaced by synthetic values.
+Yet, the increase in variance due to imputation differs according to whether missing values are imputed or observed data is overimputed with missing values.
 Whereas the variance estimate after imputation of missing data needs to account for the fact that a certain amount of information in the data is missing, variance estimation from synthetic data does not suffer from this issue.
@@
 # Results
-
 ```{r simulation, message = FALSE, warning = FALSE, cache = TRUE, cache.lazy = FALSE, echo = FALSE}
@@
 The practical development of easy to use software to identify which observations are at risk of disclosure is an area of future work that can improve these issues.
-Subsequently, the implementation of ways to overcome such problems once detected, for example by record swapping as suggested by @jiang2021balancing, is welcomed.
+Subsequently, the implementation of ways to overcome such problems, for example by record swapping as suggested by @jiang2021balancing, once detected is welcomed.
 
@@
 To simplify the simulation we adopted a bootstrapping scheme to induce sampling variance in order to conform to the combination procedure defined by @reiter_partially_inference_2003.
-Ideally, one would like to omit the bootstrap from the synthetisation to adopt a scheme where the sampled data itself serves as a reference: much like the procedure outlined in @vink2014pooling for incomplete data simulation.
+Ideally, one would like to omit the bootstrap from the synthetization to adopt a scheme where the sampled data itself serves as a reference: much like the procedure outlined in @vink2014pooling for incomplete data simulation.
 The corresponding pooling rules have not been derived yet and the incorporation in data analysis workflows would require proper attention from developers alike.
-
-There exist other software that is capable of creating synthetic data.
-For example, the `synthpop` [@synthpop] package in `R` pioneered in the field of synthetic data generation in `R`, and contains many functionalities to create and evaluate synthetic data sets.
-However, although `synthpop` is capable to synthesize regardless of missing data, it cannot solve eventual missingness problems.
-If the data for synthetisation contains missing values, the missingness will be considered as a property of the data, and the corresponding synthetic data sets will contain missing values as well.
-If the goal is to impute and synthesize a data set, a two-step approach must be used, in which the missing values are imputed using a different package, like `mice`, after which `synthpop` can be used to synthesize the imputed data.
-Then, given $m$ multiple imputations and $r$ synthetisations, at least $m \times r$ synthetic data sets are in order, after which the data can be analysed and the analyses can be pooled using rules developed by @reiter2004simultaneous.
-However, such an approach would be computationally inefficient and practically cumbersome, because the architectures of both packages differ.
-
-The appealing nature of `mice` therefore lays in its ability to solve both the missingness problem and create synthetic versions of the data.
-Eventually, the flexibility with `mice` is that both unobserved and observed data values could be synthesized at once, without the need for a two-step approach.
-Using `mice`, $m$ synthetic sets would sufficient.
-However, as of today, no pooling rules for one-step imputation of missingness and synthetisation have been developed.
-The derivation of those would yield a massive theoretical improve to further reduce the burden of creating synthetic data sets.
-More practically, the `synthpop` package contains functionality that would be highly beneficial to users in `mice`, while `mice` is likely to contain functionality that would be beneficial to `synthpop`.
-Although efforts have been made to bridge gaps between the packages [e.g., @miceadds_3.11-6], further improvements could be made in that respect.
-Specifically, `synthpop` contains a wide variety of functions that can be used to assess the quality of synthetic data [e.g., see ADD SNOKE REFERENCE + ARXIV], while `mice` contains methods to impute multilevel data.
-Being able to use such functionality interchangeably would greatly benefit the public.
 
@@
 If both observed and unobserved values are to be synthesized, then more iterations and a careful investigation into the convergence of the algorithm are in order.
-Synthetic data generation with `mice` is therein no different than multiple imputation.
+Synthetic data generation with `mice` is therein no different than multiple imputation with `mice`.
+
+There are other developments that can generate synthetic data sets.
+For example, the `synthpop` [@synthpop] package in `R` would yield valid synthetic data sets, but requires the true data to be completely observed.
+To avoid this, one could adopt a two-step approach wherein the incomplete values are multiply imputed before synthetization.
+Given $m$ multiple imputations and $r$ synthetizations, at least $m \times r$ synthetic data sets are then in order.
+However, this approach requires that researchers first impute the missingness using a different package, and then use `synthpop` to create synthetic data sets, while `mice` allows to do both.
+Additionally, the flexibility with `mice` is that both unobserved and observed data values could be synthesized at once, without the need for a two-step approach.
+Then, using `mice`, $m$ synthetic sets are sufficient.
+As of today, no pooling rules for one-step imputation of missingness and synthetisation have been developed, but the derivation of those would further reduce the burden of creating synthetic data sets.
 

### 2021-10-27 manuscript/Blind/Manuscript.tex

--- 2021-10-06 manuscript/Manuscript.tex
@@
 % Authors, for the paper (add full first names)
-\Author{Thom Volker$^{1,*,
-\dagger}$\href{https://orcid.org/0000-0002-2408-7820}{\orcidicon}, Gerko
-Vink$^{1,
-\dagger}$\href{https://orcid.org/0000-0001-9767-1924}{\orcidicon}}
+\Author{}
 
 % Authors, for metadata in PDF
-\AuthorNames{Thom Volker, Gerko Vink}
+\AuthorNames{}
 
@@
 \address{%
-$^{1}$ \quad Utrecht University - Department of Methodology and
-Statistics. Padualaan 14. 3584CH Utrecht, the Netherlands; \\
 }
 % Contact information of the corresponding author
-\corres{Correspondence: \href{mailto:t.b.volker@uu.nl}{\nolinkurl{t.b.volker@uu.nl}}.}
+\corres{Correspondence: }
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\acknowledgments{We are grateful to Mirthe Hendriks and Stijn van den
-Broek for replicating the simulation study on an independent data set.}
 
@@
 %% optional
-\sampleavailability{A full simulation archive is available from
-\url{https://github.com/amices/Federated_imputation/tree/master/manuscript}.}
+\sampleavailability{A full simulation archive is available from the
+zip-enclosed RMD file}
 

### 2021-10-27 manuscript/Manuscript.Rmd

@@
 This procedure has been advanced by @snoke2018general, who proposed a measure of distributional similarity based on the mean squared error of propensity scores indicating class belonging for both observed and synthetic data.
-This method has been implemented in the `R`-package `synthpop` [@synthpop], who pioneered in the field of synthetic data generation in `R`.
+Additionally, if one knows the analyses that will be carried out by the synthetic data users, it is possible to compare the results on the observed and the synthetic data, allowing to assess the accuracy of the synthetisation method.
+Both of these methods have been implemented in the `R`-package `synthpop` [@synthpop], who pioneered in the field of synthetic data generation in `R`.
 

### 2021-10-27 manuscript/Manuscript.tex

@@
 squared error of propensity scores indicating class belonging for both
-observed and synthetic data. This method has been implemented in the
-\texttt{R}-package \texttt{synthpop} \citep{synthpop}, who pioneered in
-the field of synthetic data generation in \texttt{R}.
+observed and synthetic data. Additionally, if one knows the analyses
+that will be carried out by the synthetic data users, it is possible to
+compare the results on the observed and the synthetic data, allowing to
+assess the accuracy of the synthetisation method. Both of these methods
+have been implemented in the \texttt{R}-package \texttt{synthpop}
+\citep{synthpop}, who pioneered in the field of synthetic data
+generation in \texttt{R}.
 

### 2021-11-01 manuscript/Manuscript.Rmd
update Gerko

@@
   We are grateful to Mirthe Hendriks and Stijn van den Broek for replicating the 
-  simulation study on an independent data set. Additionally, we thank Hanne Oberman and two anonymous reviewers for their stimulating comments.
+  simulation study on an independent data set. Additionally, we thank Hanne Oberman and two anonymous reviewers for their helpful and insightful comments.
 authorcontributions: |
@@
 Anonymizing research data might seem a quick and appealing approach to limit the unique identification of participants.
-However, this approach is not sufficient to fulfil contemporary privacy and confidentiality requirements [@ohm_broken_2009; @national_putting_2007].
+However, this approach is not sufficient to fulfill contemporary privacy and confidentiality requirements [@ohm_broken_2009; @national_putting_2007].
 Over the years, several other techniques have been used to increase the confidentiality of research data, such as categorizing continuous variables, top coding values above an upper bound or adding random noise to the observed values [@drechsler_synthetic_2011].
@@
 This strategy is implemented in, among others, the `R`-package `jomo` [@jomo] to deal with missing data.
-However, when the structure of the data increases in complexity, specifying a single multivariate distribution can become cumbersome.
-A more flexible solution has been proposed in sequential regression imputation, in which the multivariate distribution is separated into univariate distributions for every variable.
-Every single variable is then imputed conditional on a model containing only the variables in the sequence located before the variable to be imputed.
+However, when the structure of the data increases in complexity, specifying a single multivariate distribution that would fit the observed data can become challenging.
+A more flexible solution has been proposed in sequential regression imputation, in which the multivariate distribution is separated into univariate conditional distributions.
+Every single variable is then imputed conditionally on a model containing only the variables in the sequence located before the variable to be imputed.
 This approach has been implemented in the R-packages `mdmb` [@mdmb] for imputation of missing data and `synthpop` [@synthpop] for imputation of synthetic data.
@@
 library(mice)
-imp <- mice(data.to.synthesize, 
+syn <- mice(data.to.synthesize, 
             m = 10,
@@
 
-However, one of the methods that has shown a reasonable performance over multiple simulations uses FCS in combination with classification and regression trees [CART\; @breiman_cart_1984; @reiter_cart_2005; @burgette_reiter_cart_2010; @doove_buuren_recursive_2014; @raab_practical_2016].
+However, one of the methods that has shown a reasonable and consistent performance over multiple simulations using FCS in combination with classification and regression trees [CART\; @breiman_cart_1984; @reiter_cart_2005; @burgette_reiter_cart_2010; @doove_buuren_recursive_2014; @raab_practical_2016].
 Due to its non-parametric nature, CART allows to model more complex patterns (e.g., interactions and non-linear relationships) in the data.
@@
 Such factors are data dependent and should be considered by the imputer.
-In the next section, we will describe how the `mice::boys` data [fredriks_boys_2000] can be adequately synthesized.
+In the next section, we will describe how the `mice::boys` data [@fredriks_boys_2000] can be adequately synthesized.
 Additionally, we will show through simulations that this approach yields valid inferences.
@@
 All sample statistics of interest show negligible bias over the 1000 synthetic data sets.
-Hence, univariately the imputation model proves adequate.
+Hence, univariately the synthetisation model proves adequate.
 

### 2021-11-01 manuscript/Manuscript.tex
update Gerko

@@
 limit the unique identification of participants. However, this approach
-is not sufficient to fulfil contemporary privacy and confidentiality
+is not sufficient to fulfill contemporary privacy and confidentiality
 requirements \citep{ohm_broken_2009, national_putting_2007}. Over the
@@
 However, when the structure of the data increases in complexity,
-specifying a single multivariate distribution can become cumbersome. A
-more flexible solution has been proposed in sequential regression
-imputation, in which the multivariate distribution is separated into
-univariate distributions for every variable. Every single variable is
-then imputed conditional on a model containing only the variables in the
-sequence located before the variable to be imputed. This approach has
-been implemented in the R-packages \texttt{mdmb} \citep{mdmb} for
-imputation of missing data and \texttt{synthpop} \citep{synthpop} for
-imputation of synthetic data.
+specifying a single multivariate distribution that would fit the
+observed data can become challenging. A more flexible solution has been
+proposed in sequential regression imputation, in which the multivariate
+distribution is separated into univariate conditional distributions.
+Every single variable is then imputed conditionally on a model
+containing only the variables in the sequence located before the
+variable to be imputed. This approach has been implemented in the
+R-packages \texttt{mdmb} \citep{mdmb} for imputation of missing data and
+\texttt{synthpop} \citep{synthpop} for imputation of synthetic data.
 
@@
 \FunctionTok{library}\NormalTok{(mice)}
-\NormalTok{imp }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(data.to.synthesize, }
+\NormalTok{syn }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(data.to.synthesize, }
             \AttributeTok{m =} \DecValTok{10}\NormalTok{,}
@@
 
-However, one of the methods that has shown a reasonable performance over
-multiple simulations uses FCS in combination with classification and
-regression trees
+However, one of the methods that has shown a reasonable and consistent
+performance over multiple simulations using FCS in combination with
+classification and regression trees
 \citep[CART;][]{breiman_cart_1984, reiter_cart_2005, burgette_reiter_cart_2010, doove_buuren_recursive_2014, raab_practical_2016}.
@@
 we will describe how the \texttt{mice::boys} data
-{[}fredriks\_boys\_2000{]} can be adequately synthesized. Additionally,
+\citep{fredriks_boys_2000} can be adequately synthesized. Additionally,
 we will show through simulations that this approach yields valid
@@
 negligible bias over the 1000 synthetic data sets. Hence, univariately
-the imputation model proves adequate.
+the synthetisation model proves adequate.
 
@@
 can be found in Table 6.
+
+\begin{verbatim}
+## Loading required package: lattice
+\end{verbatim}
+
+\begin{verbatim}
+## 
+## Attaching package: 'caret'
+\end{verbatim}
+
+\begin{verbatim}
+## The following object is masked from 'package:future':
+## 
+##     cluster
+\end{verbatim}
+
+\begin{verbatim}
+## The following object is masked from 'package:purrr':
+## 
+##     lift
+\end{verbatim}
 
@@
 Additionally, we thank Hanne Oberman and two anonymous reviewers for
-their stimulating comments.}
+their helpful and insightful comments.}
 

### 2021-11-01 manuscript/Manuscript.Rmd
textchanges gerko

@@
 
-Potentially, this approach could fulfil the needs for openly accessible data, without running into barriers with regard to privacy and confidentiality constraints.
+Potentially, this approach could fulfill the needs for openly accessible data, without running into barriers with regard to privacy and confidentiality constraints.
 However, there is no such thing as a free lunch: data collectors have to put effort in creating high-quality synthetic data.
@@
 
-However, when creating synthetic data with `mice`, close attention should be paid to three distinct aspects of the data: incorporating the additional uncertainty that is due synthesizing (part of) the data, potential disclosure risk that remain after synthesizing the data, and the utility of the synthetic data.
+However, when creating synthetic data with `mice`, close attention should be paid to three distinct aspects of the data: incorporating the additional uncertainty that is due to synthesizing (part of) the data, potential disclosure risks that remain after synthesizing the data, and the utility of the synthetic data.
 First, the procedure of generating multiple synthetic sets may seem overly complicated.
@@
 Third, the utility of the synthetic data should receive considerable scrutiny.
-After all, synthetic data is generated to allow third parties without access to the data to make accurate inference.
-If the quality of the synthetic data is very poor, such accurate inferences are impossible.
+After all, synthetic data is generated to allow third parties without access to the data to draw valid inferences.
+If the quality of the synthetic data is very poor, the validity of inferences is at stake.
 We showed that CART proved to be an adequate method for the data at hand.
@@
 We already demonstrated that imputing deterministic relationships should not be based on CART.
-However, due to the variety in possible imputation methods that have proved to perform well in varying circumstances, providing a single solution to all imputation problems seems impossible.
-If required, imputers could build up their imputation models in complexity.
+However, due to the variety in possible imputation methods that have proved to perform well in varying circumstances, providing a single solution to all synthesis problems seems impossible.
+If required, imputers could build up their synthesis models in complexity.
 Nevertheless, similarly to past research [e.g., @burgette_reiter_cart_2010; @doove_buuren_recursive_2014; @raab_practical_2016], we showed that CART provides adequate results in general, and therefore serves as a good starting point.
@@
 However, visualizing more than two dimensions quickly becomes cumbersome, which makes it hard to assess the accuracy of multivariate relations.
-Trying to predict whether the data is observed or synthetic allows to get an intuition of the quality of the data.
+Trying to predict whether the data is observed or synthetic allows to get an intuition of the quality of the synthesis.
 This procedure has been advanced by @snoke2018general, who proposed a measure of distributional similarity based on the mean squared error of propensity scores indicating class belonging for both observed and synthetic data.
@@
 
-However, although `synthpop` is capable to synthesize regardless of missing data, it cannot solve eventual missingness problems.
+While `synthpop` is capable to synthesize regardless of missing data, it is not developed to solve missingness problems.
 If the data for synthetisation contains missing values, the missingness will be considered as a property of the data, and the corresponding synthetic data sets will contain missing values as well.
-If the goal is to impute and synthesize a data set, a two-step approach must be used, in which the missing values are imputed using a different package, like `mice`, after which `synthpop` can be used to synthesize the imputed data.
+If the goal is to solve for the missingness and synthesize the data set, a two-step approach must be used, in which the missing values are imputed using a different package, like `mice`.
+After this, `synthpop` can be used to synthesize the imputed data.
 Then, given $m$ multiple imputations and $r$ synthetisations, at least $m \times r$ synthetic data sets are in order, after which the data can be analysed and the analyses can be pooled using rules developed by @reiter2004simultaneous.
@@
 Eventually, the flexibility with `mice` is that both unobserved and observed data values could be synthesized at once, without the need for a two-step approach.
-Using `mice`, $m$ synthetic sets would sufficient.
+Using `mice`, $m$ synthetic sets would be sufficient.
 However, as of today, no pooling rules for one-step imputation of missingness and synthetisation have been developed.
-The derivation of those would yield a massive theoretical improve to further reduce the burden of creating synthetic data sets.
-More practically, the `synthpop` package contains functionality that would be highly beneficial to users in `mice`, while `mice` is likely to contain functionality that would be beneficial to `synthpop`.
-Although efforts have been made to bridge gaps between the packages [e.g., @miceadds_3.11-6], further improvements could be made in that respect.
-Specifically, `synthpop` contains a wide variety of functions that can be used to assess the quality of synthetic data [e.g., @snoke2018general], while `mice` contains methods to impute multilevel data.
-Being able to use such functionality interchangeably would greatly benefit the public.
+The derivation of those would yield a massive theoretical improvement to further reduce the burden of creating synthetic data sets.
 
-The ease of use when synthesizing data with `mice` in `R`, together with the validity of inferences obtained through this procedure opens up a wealth of possibilities for data dissemination and further research of initially private data.
+That said, the fields of synthetic data and multiple imputation are very much in development.
+Although efforts have been made to bridge gaps between these fields, such as in the `miceadds` package [@miceadds_3.11-6] which links functionality between between `synthpop` and `mice`, further improvements could be made in that respect.
+Specifically, `synthpop` contains a comprehensive suite of functions that can be used to assess the quality of synthetic data [e.g., @snoke2018general], while `mice` contains methodology to allow for flexible synthesis of intricate data structures, such as multilevel data.
+Being able to use such functionality interchangeably would greatly benefit data analysist.
+
+The added possibility of synthesizing data with `mice` in `R`, together with the validity of inferences obtained through this procedure opens up a wealth of possibilities for data dissemination and further research of initially private data to applied `R` users.

### 2021-11-01 manuscript/Manuscript.tex
textchanges gerko

@@
 
-Potentially, this approach could fulfil the needs for openly accessible
+Potentially, this approach could fulfill the needs for openly accessible
 data, without running into barriers with regard to privacy and
@@
 attention should be paid to three distinct aspects of the data:
-incorporating the additional uncertainty that is due synthesizing (part
-of) the data, potential disclosure risk that remain after synthesizing
-the data, and the utility of the synthetic data. First, the procedure of
-generating multiple synthetic sets may seem overly complicated. We would
-like to emphasize that analyzing a single synthesized set, while perhaps
-unbiased, would underestimate the variance properties that are so
-important in drawing statistical inferences from finite data sets. After
-all, we are often not interested in the sample at hand, but aim to make
-inferences about the underlying data generating mechanism as reflected
-in the population. Properly capturing the uncertainty of synthetic data
-sets, just like with incomplete data sets, is therefore paramount. To
-achieve this, we adopted a bootstrap scheme in our simulations, to
-represent sampling from a superpopulation. However, when a single sample
-should be the reference, in the sense that the sample reflects the
-population one wishes to make inferences about, adjusted pooling rules
-are required that are similar to the procedure outlined in
-\citet{vink2014pooling}. The corresponding pooling rules have not been
-derived yet and the incorporation in data analysis workflows would
-require proper attention from developers alike.
+incorporating the additional uncertainty that is due to synthesizing
+(part of) the data, potential disclosure risks that remain after
+synthesizing the data, and the utility of the synthetic data. First, the
+procedure of generating multiple synthetic sets may seem overly
+complicated. We would like to emphasize that analyzing a single
+synthesized set, while perhaps unbiased, would underestimate the
+variance properties that are so important in drawing statistical
+inferences from finite data sets. After all, we are often not interested
+in the sample at hand, but aim to make inferences about the underlying
+data generating mechanism as reflected in the population. Properly
+capturing the uncertainty of synthetic data sets, just like with
+incomplete data sets, is therefore paramount. To achieve this, we
+adopted a bootstrap scheme in our simulations, to represent sampling
+from a superpopulation. However, when a single sample should be the
+reference, in the sense that the sample reflects the population one
+wishes to make inferences about, adjusted pooling rules are required
+that are similar to the procedure outlined in \citet{vink2014pooling}.
+The corresponding pooling rules have not been derived yet and the
+incorporation in data analysis workflows would require proper attention
+from developers alike.
 
@@
 scrutiny. After all, synthetic data is generated to allow third parties
-without access to the data to make accurate inference. If the quality of
-the synthetic data is very poor, such accurate inferences are
-impossible. We showed that CART proved to be an adequate method for the
-data at hand. However, it may well be that for some problems, using CART
-for imputation is not the optimal strategy. We already demonstrated that
+without access to the data to draw valid inferences. If the quality of
+the synthetic data is very poor, the validity of inferences is at stake.
+We showed that CART proved to be an adequate method for the data at
+hand. However, it may well be that for some problems, using CART for
+imputation is not the optimal strategy. We already demonstrated that
 imputing deterministic relationships should not be based on CART.
@@
 proved to perform well in varying circumstances, providing a single
-solution to all imputation problems seems impossible. If required,
-imputers could build up their imputation models in complexity.
+solution to all synthesis problems seems impossible. If required,
+imputers could build up their synthesis models in complexity.
 Nevertheless, similarly to past research
@@
 is observed or synthetic allows to get an intuition of the quality of
-the data. This procedure has been advanced by \citet{snoke2018general},
-who proposed a measure of distributional similarity based on the mean
-squared error of propensity scores indicating class belonging for both
-observed and synthetic data. Additionally, if one knows the analyses
-that will be carried out by the synthetic data users, it is possible to
-compare the results on the observed and the synthetic data, allowing to
-assess the accuracy of the synthetisation method. Both of these methods
-have been implemented in the \texttt{R}-package \texttt{synthpop}
-\citep{synthpop}, who pioneered in the field of synthetic data
-generation in \texttt{R}.
-
-However, although \texttt{synthpop} is capable to synthesize regardless
-of missing data, it cannot solve eventual missingness problems. If the
-data for synthetisation contains missing values, the missingness will be
+the synthesis. This procedure has been advanced by
+\citet{snoke2018general}, who proposed a measure of distributional
+similarity based on the mean squared error of propensity scores
+indicating class belonging for both observed and synthetic data.
+Additionally, if one knows the analyses that will be carried out by the
+synthetic data users, it is possible to compare the results on the
+observed and the synthetic data, allowing to assess the accuracy of the
+synthetisation method. Both of these methods have been implemented in
+the \texttt{R}-package \texttt{synthpop} \citep{synthpop}, who pioneered
+in the field of synthetic data generation in \texttt{R}.
+
+While \texttt{synthpop} is capable to synthesize regardless of missing
+data, it is not developed to solve missingness problems. If the data for
+synthetisation contains missing values, the missingness will be
 considered as a property of the data, and the corresponding synthetic
-data sets will contain missing values as well. If the goal is to impute
-and synthesize a data set, a two-step approach must be used, in which
-the missing values are imputed using a different package, like
-\texttt{mice}, after which \texttt{synthpop} can be used to synthesize
-the imputed data. Then, given \(m\) multiple imputations and \(r\)
-synthetisations, at least \(m \times r\) synthetic data sets are in
-order, after which the data can be analysed and the analyses can be
-pooled using rules developed by \citet{reiter2004simultaneous}. However,
-such an approach would be computationally inefficient and practically
-cumbersome, because the architectures of both packages differ.
+data sets will contain missing values as well. If the goal is to solve
+for the missingness and synthesize the data set, a two-step approach
+must be used, in which the missing values are imputed using a different
+package, like \texttt{mice}. After this, \texttt{synthpop} can be used
+to synthesize the imputed data. Then, given \(m\) multiple imputations
+and \(r\) synthetisations, at least \(m \times r\) synthetic data sets
+are in order, after which the data can be analysed and the analyses can
+be pooled using rules developed by \citet{reiter2004simultaneous}.
+However, such an approach would be computationally inefficient and
+practically cumbersome, because the architectures of both packages
+differ.
 
@@
 without the need for a two-step approach. Using \texttt{mice}, \(m\)
-synthetic sets would sufficient. However, as of today, no pooling rules
-for one-step imputation of missingness and synthetisation have been
-developed. The derivation of those would yield a massive theoretical
-improve to further reduce the burden of creating synthetic data sets.
-More practically, the \texttt{synthpop} package contains functionality
-that would be highly beneficial to users in \texttt{mice}, while
-\texttt{mice} is likely to contain functionality that would be
-beneficial to \texttt{synthpop}. Although efforts have been made to
-bridge gaps between the packages \citep[e.g.,][]{miceadds_3.11-6},
-further improvements could be made in that respect. Specifically,
-\texttt{synthpop} contains a wide variety of functions that can be used
-to assess the quality of synthetic data
-\citep[e.g.,][]{snoke2018general}, while \texttt{mice} contains methods
-to impute multilevel data. Being able to use such functionality
-interchangeably would greatly benefit the public.
-
-The ease of use when synthesizing data with \texttt{mice} in \texttt{R},
-together with the validity of inferences obtained through this procedure
-opens up a wealth of possibilities for data dissemination and further
-research of initially private data.
+synthetic sets would be sufficient. However, as of today, no pooling
+rules for one-step imputation of missingness and synthetisation have
+been developed. The derivation of those would yield a massive
+theoretical improvement to further reduce the burden of creating
+synthetic data sets.
+
+That said, the fields of synthetic data and multiple imputation are very
+much in development. Although efforts have been made to bridge gaps
+between these fields, such as in the \texttt{miceadds} package
+\citep{miceadds_3.11-6} which links functionality between between
+\texttt{synthpop} and \texttt{mice}, further improvements could be made
+in that respect. Specifically, \texttt{synthpop} contains a
+comprehensive suite of functions that can be used to assess the quality
+of synthetic data \citep[e.g.,][]{snoke2018general}, while \texttt{mice}
+contains methodology to allow for flexible synthesis of intricate data
+structures, such as multilevel data. Being able to use such
+functionality interchangeably would greatly benefit data analysist.
+
+The added possibility of synthesizing data with \texttt{mice} in
+\texttt{R}, together with the validity of inferences obtained through
+this procedure opens up a wealth of possibilities for data dissemination
+and further research of initially private data to applied \texttt{R}
+users.
 

### 2021-11-01 manuscript/Manuscript.Rmd
Update manuscript

--- 2021-11-01 manuscript/Manuscript.Rmd
@@
 The sampling distribution of the means of the continuous variables for both the bootstrapped and the synthetic data can be found in Figure 1, while the number of observations per category in the bootstrapped data and the averaged number of observations per category over the synthetic data sets can be found in Figure 2.
+Both figures show that the marginal distributions of the bootstrapped data and the synthetic data are highly similar.
+Additionally, the univariate descriptives for the original data and the synthetic data can be found in Table 2.
 
-```{r univariate-statistics, echo = FALSE, cache = TRUE, results = FALSE}
+```{r univariate-statistics, echo = FALSE, cache = TRUE, results = FALSE, fig.cap="Empirical sampling distribution of the bootstrapped and synthetic means of the continuous variables in the boys data."}
+
 library(xtable)
+
 true <- psych::describe(data)
@@
   facet_wrap(~name, scales = "free") +
-  theme_minimal() +
+  theme_classic() +
+  theme(legend.position = "bottom") +
   scale_fill_brewer(palette = "Set1") +
@@
   labs(x = "Mean",
-       title = "Empirical sampling distribution of the mean.")
+       y = "Density",
+       title = "")
 ```
 
-Both figures show that the marginal distributions of the bootstrapped data and the synthetic data are highly similar.
-Additionally, the univariate descriptives for the original data and the synthetic data can be found in Table 2.
-
-```{r univariate-statistics-II, echo = FALSE, cache = TRUE, results = FALSE}
+```{r univariate-statistics-II, echo = FALSE, cache = TRUE, results = FALSE, fig.cap = "Empirical sampling distribution of the number within each category of the categorical variables in the bootstrapped and synthetic boys data."}
 boot_stats_cat <- bootstrap_samples %>%
@@
           .id = "Class") %>%
-  ggplot(aes(y = value, x = `Number of observations`, col = Class, group = Class)) +
-  geom_point(alpha = 0.1, position = position_jitterdodge(jitter.width = 0.2)) +
+  ggplot(aes(y = value, x = `Number of observations`, fill = Class)) +
+  geom_boxplot(position = "dodge", width = 0.8) +
   facet_wrap(~name, scales = "free") +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
+  theme_classic() +
+  theme(legend.position = "bottom") +
+  scale_fill_brewer(palette = "Set1") +
   labs(x = "Number of observations per category",
-       title = "Distribution of data over different categories.")
+       y = "Category",
+       title = "")
+```
 
+```{r, include = FALSE}
 bind_rows(true, setNames(synth, names(true))) %>% 

### 2021-11-01 manuscript/Manuscript.tex
Update manuscript

--- 2021-11-01 manuscript/Manuscript.tex
@@
 and the averaged number of observations per category over the synthetic
-data sets can be found in Figure 2.
-
+data sets can be found in Figure 2. Both figures show that the marginal
+distributions of the bootstrapped data and the synthetic data are highly
+similar. Additionally, the univariate descriptives for the original data
+and the synthetic data can be found in Table 2.
+
+\begin{figure}
+\centering
 \includegraphics{Manuscript_files/figure-latex/univariate-statistics-1.pdf}
-
-Both figures show that the marginal distributions of the bootstrapped
-data and the synthetic data are highly similar. Additionally, the
-univariate descriptives for the original data and the synthetic data can
-be found in Table 2.
-
+\caption{Empirical sampling distribution of the bootstrapped and
+synthetic means of the continuous variables in the boys data.}
+\end{figure}
+
+\begin{figure}
+\centering
 \includegraphics{Manuscript_files/figure-latex/univariate-statistics-II-1.pdf}
+\caption{Empirical sampling distribution of the number within each
+category of the categorical variables in the bootstrapped and synthetic
+boys data.}
+\end{figure}
 
@@
 can be found in Table 6.
-
-\begin{verbatim}
-## Loading required package: lattice
-\end{verbatim}
-
-\begin{verbatim}
-## 
-## Attaching package: 'caret'
-\end{verbatim}
-
-\begin{verbatim}
-## The following object is masked from 'package:future':
-## 
-##     cluster
-\end{verbatim}
-
-\begin{verbatim}
-## The following object is masked from 'package:purrr':
-## 
-##     lift
-\end{verbatim}
 

### 2021-11-01 manuscript/Manuscript.Rmd

@@
 $$
-
 with between-imputation variance
@@
 The sampling distribution of the means of the continuous variables for both the bootstrapped and the synthetic data can be found in Figure 1, while the number of observations per category in the bootstrapped data and the averaged number of observations per category over the synthetic data sets can be found in Figure 2.
-Both figures show that the marginal distributions of the bootstrapped data and the synthetic data are highly similar.
-Additionally, the univariate descriptives for the original data and the synthetic data can be found in Table 2.
 
@@
 
+Both figures show that the marginal distributions of the bootstrapped data and the synthetic data are highly similar.
+Additionally, the univariate descriptives for the original data and the synthetic data can be found in Table 2.
+
 ```{r, include = FALSE}
+library(xtable)
 bind_rows(true, setNames(synth, names(true))) %>% 

### 2021-11-01 manuscript/Manuscript.tex
Famous final words

@@
 % Authors, for the paper (add full first names)
-\Author{Thom Volker$^{1,*,
+\Author{Thom Benjamin Volker$^{1,*,
 \dagger}$\href{https://orcid.org/0000-0002-2408-7820}{\orcidicon}, Gerko
@@
 % Authors, for metadata in PDF
-\AuthorNames{Thom Volker, Gerko Vink}
+\AuthorNames{Thom Benjamin Volker, Gerko Vink}
 
@@
 % Abstract (Do not insert blank lines, i.e. \\)
-\abstract{Synthetic data sets can greatly improve the dissemination of
-data and further analysis of private data. Generating and analyzing
-synthetic data sets is straightforward, yet a synthetic data analysis
-pipeline is seldom adopted by applied researchers. We outline a simple
-procedure for generating and analyzing synthetic data sets with
-\texttt{mice} in \texttt{R}. We demonstrate using simulations that the
-analysis results obtained on synthetic data yields unbiased and valid
-inferences, and leads to synthetic records that cannot be distinguished
-from the true data records. The ease of use when synthesizing data with
-\texttt{mice}, together with the validity of inferences obtained through
-this procedure opens up a wealth of possibilities for data dissemination
-and further research of initially private data.}
+\abstract{Synthetic data sets simultaneously allow for the dissemination
+of research data while protection the privacy and confidentiality of
+respondents. Generating and analyzing synthetic data sets is
+straightforward, yet a synthetic data analysis pipeline is seldom
+adopted by applied researchers. We outline a simple procedure for
+generating and analyzing synthetic data sets with the multiple
+imputation software \texttt{mice} in \texttt{R}. We demonstrate using
+simulations that the analysis results obtained on synthetic data yield
+unbiased and valid inferences, and leads to synthetic records that
+cannot be distinguished from the true data records. The ease of use when
+synthesizing data with \texttt{mice}, together with the validity of
+inferences obtained through this procedure opens up a wealth of
+possibilities for data dissemination and further research of initially
+private data.}
 
 % Keywords
-\keyword{mice; imputation; synthetic data.}
+\keyword{mice; multiple imputation; synthetic data; statistical
+disclosure control; privacy.}
 
@@
 multiple draws from the posterior predictive distribution - or a
-non-Bayesian predictive distribution. We will refer to both of these as
-predictive distributions. Similarly to multiple imputation of missing
-data, the multiple synthetic data sets allow for correct statistical
-inferences, despite the fact that the analyses do not use the ``true''
-value. The analyses over multiple synthetic data sets should be pooled
-into a single inference, so that the researcher can draw valid
-conclusions from the pooled results. To that respect, the variance
-should reflect the added variability that is induced by the imputation
-procedure.
+non-Bayesian predictive distribution (both of these will be referred to
+as predictive distributions). Similarly to multiple imputation of
+missing data, the multiple synthetic data sets allow for correct
+statistical inferences, despite the fact that the analyses do not use
+the \emph{true} value. The analyses over multiple synthetic data sets
+should be pooled into a single inference, so that the researcher can
+draw valid conclusions from the pooled results. To that respect, the
+variance should reflect the added variability that is induced by the
+imputation procedure.
 
@@
 
-The \texttt{mice} package \citep{mice} in \texttt{R} \citep{Rproject}
-has been developed for multiple imputation to overcome problems related
-to nonresponse. In that context, the aim is to replace missing values
-with plausible values from the predictive distribution of that variable.
-In \texttt{mice}, this is accomplished using fully conditional
-specification (FCS) \citep{vanbuuren_fully_2006}, which breaks down the
+Fully conditional specification (FCS) has been implemented in the
+\texttt{mice} package \citep{mice, vanbuuren_fully_2006} in \texttt{R}
+\citep{Rproject}, which has been developed for multiple imputation to
+overcome problems related to nonresponse. In that context, the aim is to
+replace missing values with plausible values from the predictive
+distribution of that variable. This is achieved by breaking down the
 multivariate distribution of the data
@@
 \(\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})\),
-with \(\textbf{D}^{(l)} = (\textbf{Y}_{obs}, Y^{(l)}_{mis})\).
+with \(\textbf{D}^{(l)} = (\textbf{Y}_{obs}, \textbf{Y}^{(l)}_{mis})\).
 
@@
 \(i = 1, 2, \dots, n\), are to be replaced by imputations, and
-\(Z_i = 0\) otherwise, with \(\textbf{Z} = (Z_1, Z_2, \dots, Z_n)\).
-Accordingly, the data consists of values that are to be replaced and
-values that are to be kept (i.e.,
+\(Z_i = 0\) otherwise, with \(Z = (Z_1, Z_2, \dots, Z_n)\). Accordingly,
+the data consists of values that are to be replaced and values that are
+to be kept (i.e.,
 \(\textbf{Y} = (\textbf{Y}_{rep}, \textbf{Y}_{nrep})\). Now, instead of
@@
 missing data case, \(\textbf{Y}_{rep}\) is imputed from the posterior
-distribution of
-\(P(Y^{(l)}_{j, rep} | \textbf{Y}^{(l)}_{-j}, \textbf{Z}, \theta)\),
+distribution of \(P(Y^{(l)}_{j, rep} | \textbf{Y}_{-j}, Z, \theta)\),
 where \(l\) is an indicator for the synthetic data set
-(\(l = 1, 2, \dots, m\)). The synthetic values that are imputed at an
-earlier step can be used for imputing variable \(j\). This process
-results in the synthetic data
+(\(l = 1, 2, \dots, m\)). This process results in the synthetic data
 \(\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})\).
-Note that, given a completely observed data set, iterating over the
-predictive distribution is not required.
 
@@
 \begin{Highlighting}[]
-\FunctionTok{library}\NormalTok{(mice)}
 \NormalTok{syn }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(data.to.synthesize, }
@@
 values replaced by draws from the predictive distribution. This approach
-allows to replace a subset of the observed data (e.g., by only
-specifying those cells that are to be replaced as \texttt{TRUE} in the
+allows to replace a subset of the observed data (e.g., by specifying
+only those cells that are to be replaced as \texttt{TRUE} in the
 \texttt{where}-matrix, leaving the rest to \texttt{FALSE}), or as in the
@@
 Various simulations have shown that the most accurate imputation
-procedure may vary over different imputation problems
-\citep{hanne_review_2021}. Hence, a one-size-fits-all solution does
-probably not exist.
+procedure may vary over different imputation problems \citep[e.g., see][
+for an overview]{hanne_review_2021}. Hence, a one-size-fits-all solution
+does probably not exist.
 
 However, one of the methods that has shown a reasonable and consistent
-performance over multiple simulations using FCS in combination with
-classification and regression trees
-\citep[CART;][]{breiman_cart_1984, reiter_cart_2005, burgette_reiter_cart_2010, doove_buuren_recursive_2014, raab_practical_2016}.
-Due to its non-parametric nature, CART allows to model more complex
-patterns (e.g., interactions and non-linear relationships) in the data.
-Loosely speaking, CART sequentially splits the predictor space into
-non-overlapping regions in such a way that the within-region variance is
-as small as possible after every split. As such, CART does not impose
-any parametric distribution on the data, making it a widely applicable
-method that allows for a large variety of relationships within the data
-\citep{islr_2013}. Given these appealing characteristics and the call
-for the use of flexible methods when multiply imputing data, we will
-focus our illustrations and evaluations of \texttt{mice} to method
-\texttt{mice.impute.cart()}, realized by:
+performance over multiple simulations
+\citep[e.g.,][]{reiter_cart_2005, burgette_reiter_cart_2010, doove_buuren_recursive_2014, raab_practical_2016}
+is FCS in combination with classification and regression trees
+\citep[CART;][]{breiman_cart_1984}. Due to its non-parametric nature,
+CART allows to model complex patterns (e.g., interactions and non-linear
+relationships) in the data. Loosely speaking, CART sequentially splits
+the predictor space into non-overlapping regions in such a way that the
+within-region variance is as small as possible after every split. As
+such, CART does not impose any parametric distribution on the data,
+making it a widely applicable method that allows for a large variety of
+relationships within the data to be modeled \citep{islr_2013}. Given
+these appealing characteristics and the call for the use of flexible
+methods when multiply imputing data, we will focus our illustrations and
+evaluations of \texttt{mice} to method \texttt{mice.impute.cart()},
+realized by:
 
@@
 dependent and should be considered by the imputer. In the next section,
-we will describe how the \texttt{mice::boys} data
-\citep{fredriks_boys_2000} can be adequately synthesized. Additionally,
-we will show through simulations that this approach yields valid
-inferences.
+we will describe how a completely observed version of the
+\texttt{mice::boys} data \citep{fredriks_boys_2000} can be adequately
+synthesized. Additionally, we will show through simulations that this
+approach yields valid inferences.
 
@@
 collected data sets, in the sense that it suffers from missing data. For
-simplicity, we complete the missing values using the default
-\texttt{mice} imputation model for all predictors except \texttt{bmi},
-which is passively imputed using its deterministic relation with
-\texttt{wgt} and \texttt{hgt}. Specifically, the imputed values are used
-to calculate the exact \texttt{bmi} values that correspond with
-\texttt{hgt} and \texttt{wgt}.
+simplicity, we solve the missingness problem using a single imputation
+with the default \texttt{mice} imputation model for all predictors
+except \texttt{bmi}, which is passively imputed using its deterministic
+relation with \texttt{wgt} and \texttt{hgt}. Specifically, the imputed
+values are used to calculate the exact \texttt{bmi} values that
+correspond with \texttt{hgt} and \texttt{wgt}.
 
@@
 Specifically, every bootstrapped sample is treated as an actual sample
-from a population that is synthesized using \texttt{mice}, using a model
-that is built to approximate the true data-generating mechanisms as
-closely as possible. As relationships in realistic data are generally
-more complex than relationships in parametrically simulated data,
-achieving good performance on a real data set is likely to be more
-indicative of practical applicability than good performance on a
-parametrically simulated data set.
+from a population. These bootstrap samples will be synthesized using
+\texttt{mice}, using a model that is built to approximate the true
+data-generating mechanisms as closely as possible. As relationships in
+realistic data are generally more complex than relationships in
+parametrically simulated data, achieving good performance on a real data
+set is likely to be more indicative of practical applicability than good
+performance on samples from a known multivariate probability density
+function.
 
@@
 T = \bar{u}_m + \frac{b_m}{m},
-\]
-
-with between-imputation variance
+\] with between-imputation variance
 
@@
 \[
-\bar{u}_m = \sum_{l = 1} \frac{u^{(l)}}{m},
+\bar{u}_m = \sum_{l = 1}^m \frac{u^{(l)}}{m},
 \] where \(u^{(l)}\) denotes the variance estimate in the \(l\)th
@@
 rules that do not require multiple synthetic data sets and performed
-highly similar to the aforementioned pooling rules. However, we adhere
-to the originally proposed pooling rules by
-\citet{reiter_partially_inference_2003}, who defined the total variance
-in terms of sampling variance and between-imputation variance.
+highly similar to the aforementioned pooling rules. However, because
+these pooling rules can only be used when the complete data (rather than
+a subset of the data) is synthesized, we adhere to the originally
+proposed pooling rules by \citet{reiter_partially_inference_2003}, who
+defined the total variance in terms of sampling variance and
+between-imputation variance.
 
@@
 
-We evaluate the synthetic data with respect to the \emph{true} data set
+The synthetic data is evaluated with respect to the \emph{true} data set
 on the basis of three aims. We believe that every reliable and valid
@@
 
+The univariate descriptives for the original data and the synthetic data
+can be found in Table 2. From this table, it can be seen that the
+synthetic data estimates closely resemble the true data estimates. All
+sample statistics of interest show negligible bias over the 1000
+synthetic data sets.
+
 The sampling distribution of the means of the continuous variables for
@@
 and the averaged number of observations per category over the synthetic
-data sets can be found in Figure 2. Both figures show that the marginal
-distributions of the bootstrapped data and the synthetic data are highly
-similar. Additionally, the univariate descriptives for the original data
-and the synthetic data can be found in Table 2.
+data sets can be found in Figure 2.
+
+Both figures show that the marginal distributions of the bootstrapped
+data and the synthetic data are highly similar. The sampling
+distributions of these parameters hardly seem to differ. Hence, both the
+numeric and graphical results show that univariately the synthetisation
+model proves adequate.
 
@@
 \includegraphics{Manuscript_files/figure-latex/univariate-statistics-II-1.pdf}
-\caption{Empirical sampling distribution of the number within each
-category of the categorical variables in the bootstrapped and synthetic
-boys data.}
+\caption{Empirical sampling distribution of the number of observations
+within each category of the categorical variables in the bootstrapped
+and synthetic boys data.}
 \end{figure}
@@
 \begin{table}[ht]
-\caption{Univariate descriptives for the true data and $m=5$ pooled univariate descriptives for the synthetic data over 1000 simulations. Variable names followed by a $^*$ are categorical.}
+\caption{Univariate descriptives for the true data and $m=5$ pooled univariate descriptives for the synthetic data over 1000 simulations. Variable names followed by an asterix ($^*$) are categorical.}
 \centering
@@
 
-We see from Table 1 that the synthetic data estimates closely resemble
-the true data estimates. All sample statistics of interest show
-negligible bias over the 1000 synthetic data sets. Hence, univariately
-the synthetisation model proves adequate.
-
 \hypertarget{bivariate-estimates}{%
@@
 When evaluating this correlation coefficient on the numeric columns in
-the \texttt{boys} data set, we find that biases are very small. The
-results are displayed in Table 3.
+the \texttt{boys} data set, the differences between the correlations in
+the synthetic and bootstrapped data are very small. These results are
+displayed in Table 3.
 
@@
 
-We see that the correlations obtained from synthetic data are unbiased
-with respect to the true data set. The largest absolute bias over 1000
-simulations equals 0.013, indicating that the imputation model is
-capable of preserving the bivariate relations in the data.
+The correlations obtained from synthetic data are unbiased with respect
+to the true data set. The largest bias over 1000 simulations equals
+0.013, indicating that the imputation model is capable of preserving the
+bivariate relations in the data.
 
@@
 
-However, when creating synthetic data with \texttt{mice}, close
-attention should be paid to three distinct aspects of the data:
-incorporating the additional uncertainty that is due to synthesizing
-(part of) the data, potential disclosure risks that remain after
-synthesizing the data, and the utility of the synthetic data. First, the
-procedure of generating multiple synthetic sets may seem overly
-complicated. We would like to emphasize that analyzing a single
-synthesized set, while perhaps unbiased, would underestimate the
+When creating synthetic data with \texttt{mice}, close attention should
+be paid to three distinct factors: (i) the additional uncertainty that
+is due to synthesizing (part of) the data should be incorporated, (ii)
+potential disclosure risks that remain after synthesizing the data
+should be assessed, and (iii) the utility of the synthetic data should
+be examined. First, the procedure of generating multiple synthetic sets
+may seem overly complicated. We would like to emphasize that analyzing a
+single synthesized set, while perhaps unbiased, would underestimate the
 variance properties that are so important in drawing statistical
@@
 must be used, in which the missing values are imputed using a different
-package, like \texttt{mice}. After this, \texttt{synthpop} can be used
+package, like \texttt{mice}. Subsequently, \texttt{synthpop} can be used
 to synthesize the imputed data. Then, given \(m\) multiple imputations
@@
 The appealing nature of \texttt{mice} therefore lays in its ability to
-solve both the missingness problem and create synthetic versions of the
-data. Eventually, the flexibility with \texttt{mice} is that both
-unobserved and observed data values could be synthesized at once,
-without the need for a two-step approach. Using \texttt{mice}, \(m\)
-synthetic sets would be sufficient. However, as of today, no pooling
-rules for one-step imputation of missingness and synthetisation have
-been developed. The derivation of those would yield a massive
-theoretical improvement to further reduce the burden of creating
-synthetic data sets.
+both solve the missingness problem and create synthetic versions of the
+data. Eventually, the flexibility with \texttt{mice} is that unobserved
+and observed data values could be synthesized at once, without the need
+for a two-step approach. Using \texttt{mice}, \(m\) synthetic sets would
+be sufficient. However, as of today, no pooling rules for one-step
+imputation of missingness and synthetisation have been developed. The
+derivation of those would yield a massive theoretical improvement to
+further reduce the burden of creating synthetic data sets.
 
@@
 comprehensive suite of functions that can be used to assess the quality
-of synthetic data \citep[e.g.,][]{snoke2018general}, while \texttt{mice}
-contains methodology to allow for flexible synthesis of intricate data
-structures, such as multilevel data. Being able to use such
-functionality interchangeably would greatly benefit data analysist.
+of synthetic data \citep[e.g., see][]{snoke2018general}, while
+\texttt{mice} contains methodology to allow for flexible synthesis of
+intricate data structures, such as multilevel data. Being able to use
+such functionality interchangeably would greatly benefit data analysts.
 
@@
 Broek for replicating the simulation study on an independent data set.
-Additionally, we thank Hanne Oberman and two anonymous reviewers for
-their helpful and insightful comments.}
+Additionally, we thank Hanne Oberman, two anonymous reviewers and the
+editor for their helpful and insightful comments.}
 

### 2021-11-01 manuscript/Manuscript.Rmd

@@
 author:
-  - name: Thom Volker
+  - name: Thom Benjamin Volker
     affil: 1,*, \dagger
@@
 abstract: |
-  Synthetic data sets can greatly improve the dissemination of data 
-  and further analysis of private data. Generating and analyzing synthetic data 
-  sets is straightforward, yet a synthetic data analysis pipeline is 
-  seldom adopted by applied researchers. We outline a simple procedure for 
-  generating and analyzing synthetic data sets with `mice` in `R`. We demonstrate 
-  using simulations that the analysis results obtained on synthetic data 
-  yields unbiased and valid inferences, and leads to synthetic 
-  records that cannot be distinguished from the true data records. The ease of use 
-  when synthesizing data with `mice`, together with the validity of inferences 
-  obtained through this procedure opens up a wealth of possibilities for data 
-  dissemination and further research of initially private data. 
+  Synthetic data sets simultaneously allow for the dissemination of research data
+  while protection the privacy and confidentiality of respondents. Generating 
+  and analyzing synthetic data sets is straightforward, yet a synthetic data analysis 
+  pipeline is seldom adopted by applied researchers. We outline a simple procedure 
+  for generating and analyzing synthetic data sets with the multiple imputation
+  software `mice` in `R`. We demonstrate using simulations that the analysis 
+  results obtained on synthetic data yield unbiased and valid inferences, and 
+  leads to synthetic records that cannot be distinguished from the true data records. 
+  The ease of use when synthesizing data with `mice`, together with the validity of 
+  inferences obtained through this procedure opens up a wealth of possibilities for 
+  data dissemination and further research of initially private data. 
 keywords: |
-  mice; imputation; synthetic data.
+  mice; multiple imputation; synthetic data; statistical disclosure control; privacy.
 acknowledgement: |
   We are grateful to Mirthe Hendriks and Stijn van den Broek for replicating the 
-  simulation study on an independent data set. Additionally, we thank Hanne Oberman and two anonymous reviewers for their helpful and insightful comments.
+  simulation study on an independent data set. Additionally, we thank Hanne Oberman, 
+  two anonymous reviewers and the editor for their helpful and insightful comments.
 authorcontributions: |
@@
 Conceptually, the synthetic data framework is based upon the building blocks of multiple imputation of missing data, as proposed by @rubin_multiple_1987.
-Instead of replacing just the missing values, one could easily replace any observed sensitive values by multiple draws from the posterior predictive distribution - or a non-Bayesian predictive distribution.
-We will refer to both of these as predictive distributions.
-Similarly to multiple imputation of missing data, the multiple synthetic data sets allow for correct statistical inferences, despite the fact that the analyses do not use the "true" value.
+Instead of replacing just the missing values, one could easily replace any observed sensitive values by multiple draws from the posterior predictive distribution - or a non-Bayesian predictive distribution (both of these will be referred to as predictive distributions).
+Similarly to multiple imputation of missing data, the multiple synthetic data sets allow for correct statistical inferences, despite the fact that the analyses do not use the *true* value.
 The analyses over multiple synthetic data sets should be pooled into a single inference, so that the researcher can draw valid conclusions from the pooled results.
@@
 
-The `mice` package [@mice] in `R` [@Rproject] has been developed for multiple imputation to overcome problems related to nonresponse.
+Fully conditional specification (FCS) has been implemented in the `mice` package [@mice; @vanbuuren_fully_2006] in `R` [@Rproject], which has been developed for multiple imputation to overcome problems related to nonresponse.
 In that context, the aim is to replace missing values with plausible values from the predictive distribution of that variable.
-In `mice`, this is accomplished using fully conditional specification (FCS) [@vanbuuren_fully_2006], which breaks down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, where $k$ denotes the number of columns in the data.
+This is achieved by breaking down the multivariate distribution of the data $\textbf{Y} = (\textbf{Y}_{obs}, \textbf{Y}_{mis})$ into $j = 1, 2, \dots, k$ univariate conditional densities, where $k$ denotes the number of columns in the data.
 Using FCS, a model is constructed for every incomplete variable and the missing values $Y_{j, mis}$ are then imputed with draws from the predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ on a variable-by-variable basis.
 Note that the predictor matrix $Y_{-j}$ may contain yet imputed values from an earlier imputation step, and thus will be updated after every iteration.
-This procedure is applied $m$ times, resulting in $m$ completed data sets $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $\textbf{D}^{(l)} = (\textbf{Y}_{obs}, Y^{(l)}_{mis})$.
+This procedure is applied $m$ times, resulting in $m$ completed data sets $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$, with $\textbf{D}^{(l)} = (\textbf{Y}_{obs}, \textbf{Y}^{(l)}_{mis})$.
 
@@
 For simplicity, assume that the data is completely observed (i.e., $\textbf{Y} = \textbf{Y}_{obs}$).
-Following the notation of @reiter_raghunathan_multiple_2007, let, given $n$ observations, $Z_i = 1$ if any of the values of unit $i = 1, 2, \dots, n$, are to be replaced by imputations, and $Z_i = 0$ otherwise, with $\textbf{Z} = (Z_1, Z_2, \dots, Z_n)$.
+Following the notation of @reiter_raghunathan_multiple_2007, let, given $n$ observations, $Z_i = 1$ if any of the values of unit $i = 1, 2, \dots, n$, are to be replaced by imputations, and $Z_i = 0$ otherwise, with $Z = (Z_1, Z_2, \dots, Z_n)$.
 Accordingly, the data consists of values that are to be replaced and values that are to be kept (i.e., $\textbf{Y} = (\textbf{Y}_{rep}, \textbf{Y}_{nrep})$.
-Now, instead of imputing $\textbf{Y}_{mis}$ with draws from the predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, $\textbf{Y}_{rep}$ is imputed from the posterior distribution of $P(Y^{(l)}_{j, rep} | \textbf{Y}^{(l)}_{-j}, \textbf{Z}, \theta)$, where $l$ is an indicator for the synthetic data set ($l = 1, 2, \dots, m$).
-The synthetic values that are imputed at an earlier step can be used for imputing variable $j$.
+Now, instead of imputing $\textbf{Y}_{mis}$ with draws from the predictive distribution of $P(Y_{j, mis} | \textbf{Y}_{obs}, \theta)$ as in the missing data case, $\textbf{Y}_{rep}$ is imputed from the posterior distribution of $P(Y^{(l)}_{j, rep} | \textbf{Y}_{-j}, Z, \theta)$, where $l$ is an indicator for the synthetic data set ($l = 1, 2, \dots, m$).
 This process results in the synthetic data $\textbf{D} = (\textbf{D}^{(1)}, \textbf{D}^{(2)}, \dots, \textbf{D}^{(m)})$.
-Note that, given a completely observed data set, iterating over the predictive distribution is not required.
 
@@
 ```{r eval = FALSE}
-library(mice)
 syn <- mice(data.to.synthesize, 
@@
 Here, the argument `where` requires a matrix of the same dimensions as the data, (i.e., a $n \times k$ matrix) containing logicals $z_{ij}$ that indicate which cells are selected to have their values replaced by draws from the predictive distribution.
-This approach allows to replace a subset of the observed data (e.g., by only specifying those cells that are to be replaced as `TRUE` in the `where`-matrix, leaving the rest to `FALSE`), or as in the aforementioned example, the observed data as a whole, resulting in a data set that partially or completely consists of synthetic data values.
+This approach allows to replace a subset of the observed data (e.g., by specifying only those cells that are to be replaced as `TRUE` in the `where`-matrix, leaving the rest to `FALSE`), or as in the aforementioned example, the observed data as a whole, resulting in a data set that partially or completely consists of synthetic data values.
 Note that because the data is completely observed, iterating over the predictive distribution is not required.
@@
 Generally, multiple methods can be feasible, including joint modeling, sequential regression and FCS, all with different parameter specifications, depending on the imputation problem at hand [@ludtke2020regression; @yucel2018sequential; @murray2016multiple].
-Various simulations have shown that the most accurate imputation procedure may vary over different imputation problems [@hanne_review_2021].
+Various simulations have shown that the most accurate imputation procedure may vary over different imputation problems [e.g., see @hanne_review_2021 for an overview].
 Hence, a one-size-fits-all solution does probably not exist.
 
-However, one of the methods that has shown a reasonable and consistent performance over multiple simulations using FCS in combination with classification and regression trees [CART\; @breiman_cart_1984; @reiter_cart_2005; @burgette_reiter_cart_2010; @doove_buuren_recursive_2014; @raab_practical_2016].
-Due to its non-parametric nature, CART allows to model more complex patterns (e.g., interactions and non-linear relationships) in the data.
+However, one of the methods that has shown a reasonable and consistent performance over multiple simulations [e.g., @reiter_cart_2005; @burgette_reiter_cart_2010; @doove_buuren_recursive_2014; @raab_practical_2016] is FCS in combination with classification and regression trees [CART\; @breiman_cart_1984].
+Due to its non-parametric nature, CART allows to model complex patterns (e.g., interactions and non-linear relationships) in the data.
 Loosely speaking, CART sequentially splits the predictor space into non-overlapping regions in such a way that the within-region variance is as small as possible after every split.
-As such, CART does not impose any parametric distribution on the data, making it a widely applicable method that allows for a large variety of relationships within the data [@islr_2013].
+As such, CART does not impose any parametric distribution on the data, making it a widely applicable method that allows for a large variety of relationships within the data to be modeled [@islr_2013].
 Given these appealing characteristics and the call for the use of flexible methods when multiply imputing data, we will focus our illustrations and evaluations of `mice` to method `mice.impute.cart()`, realized by:
@@
 Such factors are data dependent and should be considered by the imputer.
-In the next section, we will describe how the `mice::boys` data [@fredriks_boys_2000] can be adequately synthesized.
+In the next section, we will describe how a completely observed version of the `mice::boys` data [@fredriks_boys_2000] can be adequately synthesized.
 Additionally, we will show through simulations that this approach yields valid inferences.
@@
 Unfortunately, this data set does not differ from the vast majority of collected data sets, in the sense that it suffers from missing data.
-For simplicity, we complete the missing values using the default `mice` imputation model for all predictors except `bmi`, which is passively imputed using its deterministic relation with `wgt` and `hgt`.
+For simplicity, we solve the missingness problem using a single imputation with the default `mice` imputation model for all predictors except `bmi`, which is passively imputed using its deterministic relation with `wgt` and `hgt`.
 Specifically, the imputed values are used to calculate the exact `bmi` values that correspond with `hgt` and `wgt`.
@@
 This approach precludes us from knowing the *true* data-generating model, and in this sense provides a more stringent test of the applicability of `mice` for real-life synthetisation procedures.
-Specifically, every bootstrapped sample is treated as an actual sample from a population that is synthesized using `mice`, using a model that is built to approximate the true data-generating mechanisms as closely as possible.
-As relationships in realistic data are generally more complex than relationships in parametrically simulated data, achieving good performance on a real data set is likely to be more indicative of practical applicability than good performance on a parametrically simulated data set.
+Specifically, every bootstrapped sample is treated as an actual sample from a population.
+These bootstrap samples will be synthesized using `mice`, using a model that is built to approximate the true data-generating mechanisms as closely as possible.
+As relationships in realistic data are generally more complex than relationships in parametrically simulated data, achieving good performance on a real data set is likely to be more indicative of practical applicability than good performance on samples from a known multivariate probability density function.
 
@@
 $$
-\bar{u}_m = \sum_{l = 1} \frac{u^{(l)}}{m},
+\bar{u}_m = \sum_{l = 1}^m \frac{u^{(l)}}{m},
 $$
@@
 This observation as been taken a step further by @raab_practical_2016, who developed pooling rules that do not require multiple synthetic data sets and performed highly similar to the aforementioned pooling rules.
-However, we adhere to the originally proposed pooling rules by @reiter_partially_inference_2003, who defined the total variance in terms of sampling variance and between-imputation variance.
+However, because these pooling rules can only be used when the complete data (rather than a subset of the data) is synthesized, we adhere to the originally proposed pooling rules by @reiter_partially_inference_2003, who defined the total variance in terms of sampling variance and between-imputation variance.
 
@@
 
-We evaluate the synthetic data with respect to the *true* data set on the basis of three aims.
+The synthetic data is evaluated with respect to the *true* data set on the basis of three aims.
 We believe that every reliable and valid data synthetisation effort in statistical data analysis should be able to yield 1) unbiased univariate statistical properties, 2) unbiased bivariate properties, 3) unbiased and valid multivariate inferences and 4) synthetic data that cannot be distinguished from real data.
@@
 
+The univariate descriptives for the original data and the synthetic data can be found in Table 2.
+From this table, it can be seen that the synthetic data estimates closely resemble the true data estimates.
+All sample statistics of interest show negligible bias over the 1000 synthetic data sets.
+
 The sampling distribution of the means of the continuous variables for both the bootstrapped and the synthetic data can be found in Figure 1, while the number of observations per category in the bootstrapped data and the averaged number of observations per category over the synthetic data sets can be found in Figure 2.
+
+Both figures show that the marginal distributions of the bootstrapped data and the synthetic data are highly similar.
+The sampling distributions of these parameters hardly seem to differ.
+Hence, both the numeric and graphical results show that univariately the synthetisation model proves adequate.
 
@@
 
-```{r univariate-statistics-II, echo = FALSE, cache = TRUE, results = FALSE, fig.cap = "Empirical sampling distribution of the number within each category of the categorical variables in the bootstrapped and synthetic boys data."}
+```{r univariate-statistics-II, echo = FALSE, cache = TRUE, results = FALSE, fig.cap = "Empirical sampling distribution of the number of observations within each category of the categorical variables in the bootstrapped and synthetic boys data."}
 boot_stats_cat <- bootstrap_samples %>%
@@
 
-Both figures show that the marginal distributions of the bootstrapped data and the synthetic data are highly similar.
-Additionally, the univariate descriptives for the original data and the synthetic data can be found in Table 2.
-
 ```{r, include = FALSE}
@@
 
-We see from Table 1 that the synthetic data estimates closely resemble the true data estimates.
-All sample statistics of interest show negligible bias over the 1000 synthetic data sets.
-Hence, univariately the synthetisation model proves adequate.
-
 ## Bivariate estimates
@@
 An often used bivariate statistic is Pearson's correlation coefficient.
-When evaluating this correlation coefficient on the numeric columns in the `boys` data set, we find that biases are very small.
-The results are displayed in Table 3.
+When evaluating this correlation coefficient on the numeric columns in the `boys` data set, the differences between the correlations in the synthetic and bootstrapped data are very small.
+These results are displayed in Table 3.
 
@@
 
-We see that the correlations obtained from synthetic data are unbiased with respect to the true data set.
-The largest absolute bias over 1000 simulations equals 0.013, indicating that the imputation model is capable of preserving the bivariate relations in the data.
+The correlations obtained from synthetic data are unbiased with respect to the true data set.
+The largest bias over 1000 simulations equals 0.013, indicating that the imputation model is capable of preserving the bivariate relations in the data.
 
@@
 
-However, when creating synthetic data with `mice`, close attention should be paid to three distinct aspects of the data: incorporating the additional uncertainty that is due to synthesizing (part of) the data, potential disclosure risks that remain after synthesizing the data, and the utility of the synthetic data.
+When creating synthetic data with `mice`, close attention should be paid to three distinct factors: (i) the additional uncertainty that is due to synthesizing (part of) the data should be incorporated, (ii) potential disclosure risks that remain after synthesizing the data should be assessed, and (iii) the utility of the synthetic data should be examined.
 First, the procedure of generating multiple synthetic sets may seem overly complicated.
@@
 If the goal is to solve for the missingness and synthesize the data set, a two-step approach must be used, in which the missing values are imputed using a different package, like `mice`.
-After this, `synthpop` can be used to synthesize the imputed data.
+Subsequently, `synthpop` can be used to synthesize the imputed data.
 Then, given $m$ multiple imputations and $r$ synthetisations, at least $m \times r$ synthetic data sets are in order, after which the data can be analysed and the analyses can be pooled using rules developed by @reiter2004simultaneous.
@@
 
-The appealing nature of `mice` therefore lays in its ability to solve both the missingness problem and create synthetic versions of the data.
-Eventually, the flexibility with `mice` is that both unobserved and observed data values could be synthesized at once, without the need for a two-step approach.
+The appealing nature of `mice` therefore lays in its ability to both solve the missingness problem and create synthetic versions of the data.
+Eventually, the flexibility with `mice` is that unobserved and observed data values could be synthesized at once, without the need for a two-step approach.
 Using `mice`, $m$ synthetic sets would be sufficient.
@@
 Although efforts have been made to bridge gaps between these fields, such as in the `miceadds` package [@miceadds_3.11-6] which links functionality between between `synthpop` and `mice`, further improvements could be made in that respect.
-Specifically, `synthpop` contains a comprehensive suite of functions that can be used to assess the quality of synthetic data [e.g., @snoke2018general], while `mice` contains methodology to allow for flexible synthesis of intricate data structures, such as multilevel data.
-Being able to use such functionality interchangeably would greatly benefit data analysist.
+Specifically, `synthpop` contains a comprehensive suite of functions that can be used to assess the quality of synthetic data [e.g., see @snoke2018general], while `mice` contains methodology to allow for flexible synthesis of intricate data structures, such as multilevel data.
+Being able to use such functionality interchangeably would greatly benefit data analysts.
 

### 2021-11-02 manuscript/Manuscript.Rmd
Add final revisions

@@
 Ideally, these steps could be combined using `mice`, conditioning the imputations on both the missingness and the values that are to be synthesized.
-In practice, replacing observed and missing cells in a data set by synthetic values into the object `syn`, given the same imputation parameters as before, can be realized by the following code execution.
+In practice, replacing observed and missing cells in a data set by synthetic values into the object `syn.mis`, given the same imputation parameters as before, can be realized by the following code execution.
 
 ```{r eval = FALSE}
-syn <- mice(data.with.missings.to.synthesize, 
+syn.mis <- mice(data.with.missings.to.synthesize, 
                 m = 10,
@@
 where $u^{(l)}$ denotes the variance estimate in the $l$th synthetic data set.
-These pooling rules are implemented in `mice` as the function `pool.syn`.
+These pooling rules are implemented in `mice` as the function `pool.syn()`.
+Returning to our previous example, pooling the parameter estimates of a linear model in which the dependent variable `DV` is regressed on predictors `IV1` and `IV2` fitted on each of the synthetic data sets is as straightforward as the following code block.
+
+```{r, eval = FALSE}
+fits <- with(syn, lm(DV ~ IV1 + IV2))
+pool.syn(fits)
+```
+
 @reiter_kinney_2012 proved that synthesizing data from the posterior predictive distribution is not required for these pooling rules to hold.
@@
 
-The sampling distribution of the means of the continuous variables for both the bootstrapped and the synthetic data can be found in Figure 1, while the number of observations per category in the bootstrapped data and the averaged number of observations per category over the synthetic data sets can be found in Figure 2.
-
-Both figures show that the marginal distributions of the bootstrapped data and the synthetic data are highly similar.
-The sampling distributions of these parameters hardly seem to differ.
-Hence, both the numeric and graphical results show that univariately the synthetisation model proves adequate.
-
-```{r univariate-statistics, echo = FALSE, cache = TRUE, results = FALSE, fig.cap="Empirical sampling distribution of the bootstrapped and synthetic means of the continuous variables in the boys data."}
-
+```{r univ-stats, include = FALSE, cache = TRUE}
 library(xtable)
@@
 
-boot_stats_cont <- bootstrap_samples %>% 
-  map_dfr(~.x %>% 
-            select(where(is.numeric)) %>% 
-            pivot_longer(everything()) %>%
-            group_by(name) %>%
-            summarize(mean = mean(value)))
-
-syn_stats_cont <- synthetic_samples  %>%
-  map_dfr(~.x %>%
-            complete("long") %>%
-            select(c(age, hgt, wgt, bmi, hc, tv)) %>%
-            colMeans) %>%
-  pivot_longer(everything(), values_to = "mean")
-
-bind_rows(Boostrapped = boot_stats_cont, 
-          Synthetic = syn_stats_cont, 
-          .id = "Class") %>%
-  ggplot(aes(x = mean, col = Class, fill = Class)) +
-  geom_density(alpha = 0.5) +
-  facet_wrap(~name, scales = "free") +
-  theme_classic() +
-  theme(legend.position = "bottom") +
-  scale_fill_brewer(palette = "Set1") +
-  scale_color_brewer(palette = "Set1") +
-  labs(x = "Mean",
-       y = "Density",
-       title = "")
-```
-
-```{r univariate-statistics-II, echo = FALSE, cache = TRUE, results = FALSE, fig.cap = "Empirical sampling distribution of the number of observations within each category of the categorical variables in the bootstrapped and synthetic boys data."}
-boot_stats_cat <- bootstrap_samples %>%
-  map_dfr(~.x %>%
-            select(!where(is.numeric)) %>%
-            mutate(across(everything(), as.character)) %>%
-            pivot_longer(everything()) %>% 
-            group_by(name, value) %>%
-            summarize(`Number of observations` = n(), .groups = "drop"))
-
-syn_stats_cat <- synthetic_samples %>%
-  map_dfr(~.x %>%
-            complete("long") %>%
-            select(c(gen, phb, reg)) %>%
-            mutate(across(everything(), as.character)) %>%
-            pivot_longer(everything()) %>%
-            group_by(name, value) %>%
-            summarize(`Number of observations` = n() / 5, .groups = "drop"))
-
-bind_rows(Boostrapped = boot_stats_cat, 
-          Synthetic = syn_stats_cat, 
-          .id = "Class") %>%
-  ggplot(aes(y = value, x = `Number of observations`, fill = Class)) +
-  geom_boxplot(position = "dodge", width = 0.8) +
-  facet_wrap(~name, scales = "free") +
-  theme_classic() +
-  theme(legend.position = "bottom") +
-  scale_fill_brewer(palette = "Set1") +
-  labs(x = "Number of observations per category",
-       y = "Category",
-       title = "")
-```
-
-```{r, include = FALSE}
-library(xtable)
 bind_rows(true, setNames(synth, names(true))) %>% 
@@
 ```
+
 <!-- % latex table generated in R 4.1.0 by xtable 1.8-4 package -->
@@
 \end{table}
+
+```{r univariate-statistics, echo = FALSE, cache = TRUE, results = FALSE, fig.cap="Empirical sampling distribution of the bootstrapped and synthetic means of the continuous variables in the boys data."}
+
+boot_stats_cont <- bootstrap_samples %>% 
+  map_dfr(~.x %>% 
+            select(where(is.numeric)) %>% 
+            pivot_longer(everything()) %>%
+            group_by(name) %>%
+            summarize(mean = mean(value)))
+
+syn_stats_cont <- synthetic_samples  %>%
+  map_dfr(~.x %>%
+            complete("long") %>%
+            select(c(age, hgt, wgt, bmi, hc, tv)) %>%
+            colMeans) %>%
+  pivot_longer(everything(), values_to = "mean")
+
+bind_rows(Bootstrapped = boot_stats_cont, 
+          Synthetic = syn_stats_cont, 
+          .id = "Class") %>%
+  ggplot(aes(x = mean, col = Class, fill = Class)) +
+  geom_density(alpha = 0) +
+  facet_wrap(~name, scales = "free") +
+  theme_classic() +
+  theme(legend.position = "bottom") +
+  scale_fill_brewer(palette = "Set1", direction = -1) +
+  scale_color_brewer(palette = "Set1", direction = -1) +
+  labs(x = "Mean",
+       y = "Density",
+       title = "")
+```
+
+```{r univariate-statistics-II, echo = FALSE, cache = TRUE, results = FALSE, fig.cap = "Empirical sampling distribution of the number of observations within each category of the categorical variables in the bootstrapped and synthetic boys data."}
+boot_stats_cat <- bootstrap_samples %>%
+  map_dfr(~.x %>%
+            select(!where(is.numeric)) %>%
+            mutate(across(everything(), as.character)) %>%
+            pivot_longer(everything()) %>% 
+            group_by(name, value) %>%
+            summarize(`Number of observations` = n(), .groups = "drop"))
+
+syn_stats_cat <- synthetic_samples %>%
+  map_dfr(~.x %>%
+            complete("long") %>%
+            select(c(gen, phb, reg)) %>%
+            mutate(across(everything(), as.character)) %>%
+            pivot_longer(everything()) %>%
+            group_by(name, value) %>%
+            summarize(`Number of observations` = n() / 5, .groups = "drop"))
+
+bind_rows(Bootstrapped = boot_stats_cat, 
+          Synthetic = syn_stats_cat, 
+          .id = "Class") %>%
+  ggplot(aes(y = value, x = `Number of observations`, fill = Class)) +
+  geom_boxplot(position = "dodge", width = 0.8) +
+  facet_wrap(~name, scales = "free") +
+  theme_classic() +
+  theme(legend.position = "bottom") +
+  scale_fill_brewer(palette = "Set1", direction = -1) +
+  labs(x = "Number of observations per category",
+       y = "Category",
+       title = "")
+```
+
+The sampling distribution of the means of the continuous variables for both the bootstrapped and the synthetic data can be found in Figure 1, while the number of observations per category in the bootstrapped data and the averaged number of observations per category over the synthetic data sets can be found in Figure 2.
+
+Both figures show that the marginal distributions of the bootstrapped data and the synthetic data are highly similar.
+The sampling distributions of these parameters hardly seem to differ.
+Hence, both the numeric and graphical results show that univariately the synthetisation model proves adequate.
 

### 2021-11-02 manuscript/Manuscript.tex
Add final revisions

@@
 and missing cells in a data set by synthetic values into the object
-\texttt{syn}, given the same imputation parameters as before, can be
+\texttt{syn.mis}, given the same imputation parameters as before, can be
 realized by the following code execution.
@@
 \begin{Highlighting}[]
-\NormalTok{syn }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(data.with.missings.to.synthesize, }
+\NormalTok{syn.mis }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(data.with.missings.to.synthesize, }
                 \AttributeTok{m =} \DecValTok{10}\NormalTok{,}
@@
 synthetic data set. These pooling rules are implemented in \texttt{mice}
-as the function \texttt{pool.syn}. \citet{reiter_kinney_2012} proved
-that synthesizing data from the posterior predictive distribution is not
-required for these pooling rules to hold. In fact, the parameters of an
-imputation model can be fixed to their maximum likelihood estimates or
-their posterior modes, and synthetic values can be drawn after plugging
-these values into the imputation models. This observation as been taken
-a step further by \citet{raab_practical_2016}, who developed pooling
-rules that do not require multiple synthetic data sets and performed
-highly similar to the aforementioned pooling rules. However, because
-these pooling rules can only be used when the complete data (rather than
-a subset of the data) is synthesized, we adhere to the originally
-proposed pooling rules by \citet{reiter_partially_inference_2003}, who
-defined the total variance in terms of sampling variance and
-between-imputation variance.
+as the function \texttt{pool.syn()}. Returning to our previous example,
+pooling the parameter estimates of a linear model in which the dependent
+variable \texttt{DV} is regressed on predictors \texttt{IV1} and
+\texttt{IV2} fitted on each of the synthetic data sets is as
+straightforward as the following code block.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{fits }\OtherTok{\textless{}{-}} \FunctionTok{with}\NormalTok{(syn, }\FunctionTok{lm}\NormalTok{(DV }\SpecialCharTok{\textasciitilde{}}\NormalTok{ IV1 }\SpecialCharTok{+}\NormalTok{ IV2))}
+\FunctionTok{pool.syn}\NormalTok{(fits)}
+\end{Highlighting}
+\end{Shaded}
+
+\citet{reiter_kinney_2012} proved that synthesizing data from the
+posterior predictive distribution is not required for these pooling
+rules to hold. In fact, the parameters of an imputation model can be
+fixed to their maximum likelihood estimates or their posterior modes,
+and synthetic values can be drawn after plugging these values into the
+imputation models. This observation as been taken a step further by
+\citet{raab_practical_2016}, who developed pooling rules that do not
+require multiple synthetic data sets and performed highly similar to the
+aforementioned pooling rules. However, because these pooling rules can
+only be used when the complete data (rather than a subset of the data)
+is synthesized, we adhere to the originally proposed pooling rules by
+\citet{reiter_partially_inference_2003}, who defined the total variance
+in terms of sampling variance and between-imputation variance.
 
@@
 synthetic data sets.
-
-The sampling distribution of the means of the continuous variables for
-both the bootstrapped and the synthetic data can be found in Figure 1,
-while the number of observations per category in the bootstrapped data
-and the averaged number of observations per category over the synthetic
-data sets can be found in Figure 2.
-
-Both figures show that the marginal distributions of the bootstrapped
-data and the synthetic data are highly similar. The sampling
-distributions of these parameters hardly seem to differ. Hence, both the
-numeric and graphical results show that univariately the synthetisation
-model proves adequate.
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/univariate-statistics-1.pdf}
-\caption{Empirical sampling distribution of the bootstrapped and
-synthetic means of the continuous variables in the boys data.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{Manuscript_files/figure-latex/univariate-statistics-II-1.pdf}
-\caption{Empirical sampling distribution of the number of observations
-within each category of the categorical variables in the bootstrapped
-and synthetic boys data.}
-\end{figure}
 
@@
 \end{table}
+
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/univariate-statistics-1.pdf}
+\caption{Empirical sampling distribution of the bootstrapped and
+synthetic means of the continuous variables in the boys data.}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics{Manuscript_files/figure-latex/univariate-statistics-II-1.pdf}
+\caption{Empirical sampling distribution of the number of observations
+within each category of the categorical variables in the bootstrapped
+and synthetic boys data.}
+\end{figure}
+
+The sampling distribution of the means of the continuous variables for
+both the bootstrapped and the synthetic data can be found in Figure 1,
+while the number of observations per category in the bootstrapped data
+and the averaged number of observations per category over the synthetic
+data sets can be found in Figure 2.
+
+Both figures show that the marginal distributions of the bootstrapped
+data and the synthetic data are highly similar. The sampling
+distributions of these parameters hardly seem to differ. Hence, both the
+numeric and graphical results show that univariately the synthetisation
+model proves adequate.
 

### 2021-11-03 manuscript/Manuscript.Rmd

@@
 
-```{r true-data, results = FALSE, message = FALSE, warning = FALSE, cache = TRUE}
+```{r true-data, include = FALSE, message = FALSE, warning = FALSE, cache = TRUE}
 # create a single imputed, completely observed `boys` data set

### 2021-11-03 manuscript/Submitted/Manuscript/Manuscript.Rmd

--- 2021-10-27 manuscript/Blind/Manuscript.Rmd
@@
 title: "Anony*mice*d shareable data: Using *mice* to create and analyze multiply imputed synthetic data sets"
-
+author:
+  - name: Thom Volker
+    affil: 1,*, \dagger
+    orcid: 0000-0002-2408-7820
+  - name: Gerko Vink
+    affil: 1, \dagger
+    orcid: 0000-0001-9767-1924
+affiliation:
+  - num: 1
+    address: |
+      Utrecht University - 
+      Department of Methodology and Statistics. 
+      Padualaan 14. 3584CH Utrecht, the Netherlands
 # firstnote to eighthnote
@@
   These authors contributed equally to this work.
+correspondence: |
+  t.b.volker@uu.nl.
 journal: psych
@@
   mice; imputation; synthetic data.
+acknowledgement: |
+  We are grateful to Mirthe Hendriks and Stijn van den Broek for replicating the 
+  simulation study on an independent data set. 
 authorcontributions: |
@@
 sampleavailability: |
-  A full simulation archive is available from the zip-enclosed RMD file
+  A full simulation archive is available from https://github.com/amices/Federated_imputation/tree/master/manuscript.
 output: rticles::mdpi_article

### 2021-11-03 manuscript/blind_rev/Manuscript.Rmd
Blind revisions.

--- 2021-11-03 manuscript/Manuscript.Rmd
@@
 title: "Anony*mice*d shareable data: Using *mice* to create and analyze multiply imputed synthetic data sets"
-author:
-  - name: Thom Benjamin Volker
-    affil: 1,*, \dagger
-    orcid: 0000-0002-2408-7820
-  - name: Gerko Vink
-    affil: 1, \dagger
-    orcid: 0000-0001-9767-1924
-affiliation:
-  - num: 1
-    address: |
-      Utrecht University - 
-      Department of Methodology and Statistics. 
-      Padualaan 14. 3584CH Utrecht, the Netherlands
-# firstnote to eighthnote
 firstnote: |
   These authors contributed equally to this work.
-correspondence: |
-  t.b.volker@uu.nl.
 journal: psych
@@
 sampleavailability: |
-  A full simulation archive is available from https://github.com/amices/Federated_imputation/tree/master/manuscript.
+  A full simulation archive is available from the zip-enclosed .Rmd file.
 output: rticles::mdpi_article

### 2021-11-03 manuscript/blind_rev/Manuscript.tex
Blind revisions.

--- 2021-11-02 manuscript/Manuscript.tex
@@
 % Authors, for the paper (add full first names)
-\Author{Thom Benjamin Volker$^{1,*,
-\dagger}$\href{https://orcid.org/0000-0002-2408-7820}{\orcidicon}, Gerko
-Vink$^{1,
-\dagger}$\href{https://orcid.org/0000-0001-9767-1924}{\orcidicon}}
+\Author{}
 
 % Authors, for metadata in PDF
-\AuthorNames{Thom Benjamin Volker, Gerko Vink}
+\AuthorNames{}
 
@@
 correspond with \texttt{hgt} and \texttt{wgt}.
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# create a single imputed, completely observed \textasciigrave{}boys\textasciigrave{} data set}
-\FunctionTok{set.seed}\NormalTok{(}\DecValTok{123}\NormalTok{)}
-
-\NormalTok{meth }\OtherTok{\textless{}{-}} \FunctionTok{make.method}\NormalTok{(boys)}
-\NormalTok{meth[}\StringTok{"bmi"}\NormalTok{] }\OtherTok{\textless{}{-}} \StringTok{"\textasciitilde{} I(wgt / (hgt / 100)\^{}2)"}
-\NormalTok{pred }\OtherTok{\textless{}{-}} \FunctionTok{make.predictorMatrix}\NormalTok{(boys)}
-\NormalTok{pred[}\FunctionTok{c}\NormalTok{(}\StringTok{"hgt"}\NormalTok{, }\StringTok{"wgt"}\NormalTok{), }\StringTok{"bmi"}\NormalTok{] }\OtherTok{\textless{}{-}} \DecValTok{0}
-
-\NormalTok{imp }\OtherTok{\textless{}{-}} \FunctionTok{mice}\NormalTok{(boys, }
-            \AttributeTok{m =} \DecValTok{1}\NormalTok{,}
-            \AttributeTok{maxit =} \DecValTok{10}\NormalTok{,}
-            \AttributeTok{method =}\NormalTok{ meth,}
-            \AttributeTok{predictorMatrix =}\NormalTok{ pred)}
-
-\NormalTok{data }\OtherTok{\textless{}{-}} \FunctionTok{complete}\NormalTok{(imp)}
-\end{Highlighting}
-\end{Shaded}
 
@@
 %% optional
-\sampleavailability{A full simulation archive is available from
-\url{https://github.com/amices/Federated_imputation/tree/master/manuscript}.}
+\sampleavailability{A full simulation archive is available from the
+zip-enclosed .Rmd file.}
 
